### 2017-01-16 Paper/paper.tex
Paper files

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}

\title[AGN luminosity function]{Evolution of the AGN UV luminosity function}

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Max Planck Institute for Astronomy,
  K\"onigstuhl 17, D-69117 Heidelberg, Germany\\ $^3$Department of
  Physics, Broida Hall, UC Santa Barbara, Santa Barbara, CA 93106-9530
  USA}

\date{Accepted ---. Received ---; in original form ---}

\pubyear{2016}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
  eget nisi augue. Vivamus quis purus quis massa tempor posuere non
  quis magna. Aenean eleifend, metus eget facilisis faucibus, turpis
  erat suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse
  luctus eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec
  massa ultrices, porttitor nulla at, euismod diam. In ultricies
  malesuada mauris ac facilisis. Nulla quis suscipit diam, vitae
  semper tortor. Proin nec nulla at massa egestas porta. Cras ac arcu
  in velit placerat facilisis fringilla in sem. Mauris finibus, mauris
  ut pretium malesuada, massa urna mattis nibh, at placerat ligula
  elit ac odio.  Nunc vel leo arcu. Nullam sagittis tincidunt
  interdum. Mauris sed lacus cursus, dapibus enim non, sagittis
  leo. Aliquam sit amet ex ut quam iaculis sollicitudin. Vivamus ut
  pharetra dolor. Vivamus id nibh leo. Vestibulum consectetur eu lorem
  eu tincidunt. Sed eget nibh orci. Pellentesque sit amet blandit
  massa, vel tempor neque.
\end{abstract}

\begin{keywords}
quasars
\end{keywords}

%% \section{Introduction}

%% Possible outline of paper:

%% \begin{enumerate}
%% \item Introduction 
%% \item Data set
%% \item QLF 
%%   \begin{enumerate}
%%   \item at specific redshifts 
%%   \item global model 
%%   \end{enumerate}
%% \item Contribution to reionizatin 
%% \item Conclusion 
%% \end{enumerate}

%% \noindent Optional possibilities:

%% \begin{enumerate}
%% \item Bolometric LF
%% \item PLE, PDE, etc?
%% \item Quantitative model fit test 
%% \item BH growth 
%% \item Comparison with galaxies 
%% \end{enumerate}

\section{Luminosity function}

In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the luminosity
    function as \citep{2000MNRAS.311..433P}
  \begin{equation}
    \phi \equiv \frac{N}{V_\mathrm{bin}},
  \end{equation}
  where $N$ is the number of quasars with magnitude
  $M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
  $z_\mathrm{min}\leq z<z_\mathrm{max}$, and
  \begin{equation}
    V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
    \label{eqn:vi}
  \end{equation}
  is the effective volume of the bin.  Here $f(M,z)$ is the quasar
  selection probability, which includes incompleteness.  Inclusion of
  the selection probability in Equation~(\ref{eqn:vi}) accounts for
  what have been referred to as ``incomplete bins'' in the literature.
  The comoving volume element $dV/dz$ is given by
  \begin{equation}
    \frac{dV}{dz}=\frac{dV}{dz\,d\Omega}\cdot A\cdot\frac{4\pi}{41253},
  \end{equation}
  where $A$ is the survey area in deg$^2$, and \citep{1999astro.ph..5116H}
  \begin{equation}
    \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}{(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
    \label{eqn:dvdzdo}
  \end{equation}
  denotes the comoving volume element per unit solid angle.  The
  luminosity distance $d_L$ is given by
  \begin{equation}
    d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}{\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
    \label{eqn:dl}
  \end{equation}
  Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat
  Universe ($\Omega_k=0$).  The luminosity function $\phi$ has units
  of $\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
  integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
  simply summing over the ``tiles'' of the selection function map.  We
  do not interpolate between the redshift and luminosity values of
  neighbouring tiles.  This may result in $V_i=0$ for some quasars, in
  which case we remove them from our analysis.  Figure~\ref{fig:boss}
  shows the luminosity function derived in this way for the BOSS DR9
  colour-selected sample of 23,301 quasars, in comparison with the
  published luminosity function of \citet{2013ApJ...773...14R}.
  Figure~\ref{fig:sdss} shows the luminosity function of a sample of
  15,179 quasars from the SDSS DR3 in comparison with the published
  luminosity function of \citet{2006AJ....131.2766R}.

  % Describe how we derive error bars.

  \section{Fitting procedure}

  We model the quasar luminosity function as a double power law given
  by \citep[e.g.,][]{2013ApJ...773...14R}
  \begin{equation}
    \phi(M) = \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}},
\label{eqn:dpl}
\end{equation}
where all magnitudes are absolute magnitudes at rest-frame 1450~{\AA}.
The luminosity function $\phi$ gives the comoving number density of
quasars per unit magnitude.  It usually has units of
mag$^{-1}$cMpc$^{-3}$.  Equation~(\ref{eqn:dpl}) has four free
parameters: the amplitude $\phi_*$, the ``break'' $M_*$, the faint-end
slope $\beta$, and the bright-end slope $\alpha$.  The likelihood
function can be written as \citep{2001AJ....121...54F}
\begin{equation}
  \mathcal{L}=\prod_{i,j}\frac{e^{-\mu_{ij}}\mu_{ij}^{n_{ij}}}{n_{ij}!},
  \label{eqn:lhood}
\end{equation}
where $n_{ij}$ is the number of quasars observed in the $(M_i, z_j)$
bin, and
\begin{equation}
  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_i}^{z_{i+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{equation}
is the average number of quasars expected in the $(M_i, z_j)$ bin
given the luminosity function $\phi(M,z)$.  To obtain the maximum
likelihood solution for the luminosity functin parameters, we minimise
the function
\begin{equation}
  S = -2\ln\mathcal{L}.
\end{equation}
In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
Equation~(\ref{eqn:lhood}) can be simplified and we can write
\begin{multline}
  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
\end{multline}
where $N$ is the total number of quasars in the sample and the integral in the second term on the right hand side is now on the full range of $M$ and $z$.

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
  \end{center}
  \caption{Comparison of LF derived by our method with the published
    LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
    sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
    these, 231 quasars have $V_i=0$ and are dropped from the
    analysis.}
  \label{fig:boss}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2013ApJ...768..105M} for SDSS DR3.  There are 15,343
    quasars in this sample, of which 155 quasars have $z<0.3$ and 9
    quasars have $z>5$.  Of the remaining 15179 quasars with
    $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
    analysis.  As a result, the green points above contain 15,119
    quasars.  The red circles contain 14,953 quasars.}
  \label{fig:sdss}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
    quasars in their DR7 sample and 52 quasars in the Stripe 82
    sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
    The published samples of \citet{2013ApJ...768..105M} have 146 and
    51 quasars.}
  \label{fig:mcgreer}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
  \end{center}
  \caption{Comparison with the published LF of
    \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
    quasars in their two samples (NDWFS and DLS).}
  \label{fig:mcgreer}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth]{qsos.pdf}
  \end{center}
  \caption{Quasar samples.}
  \label{fig:qsos}
\end{figure*}

\begin{landscape}
  \begin{table}
    % In published version of this table, we could remove file names and add data homogenisation in Notes.
    % Add z ~ 7 qso when you add it to analysis
    \caption{Quasar data sets}
    \label{tab:samples}
    \begin{tabular}{cccllcclll}
      \hline
      & ID & $z$ & Survey & Reference & Number & Area & Sample file & Selection map file & Notes \\
      & & & & & of quasars & (deg$^2$) & & & \\
      \hline
      1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \texttt{dr7z2p2\_sample.dat} & \texttt{dr7z2p2\_selfunc.dat} &  \\
      2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \texttt{croom09sgp\_sample.dat} & \texttt{croom09sgp\_selfunc.dat} & \\ 
      3. &  2 & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \texttt{croom09ngp\_sample.dat} & \texttt{croom09ngp\_selfunc.dat} & \\
      4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \texttt{bossdr9color.dat} & \texttt{ross13\_selfunc2.dat} & \\
      5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & \texttt{dr7z3p7\_sample.dat} & \texttt{dr7z3p7\_selfunc.dat} & Sample restricted to $z<4.7$ \\
      6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & \texttt{yang16\_sample.dat} & \texttt{yang16\_sel.dat} & Overlaps with 8 for $M_{1450}>-26.73$? \\
      7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \texttt{mcgreer13\_dr7sample.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
      8. &  4 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \texttt{mcgreer13\_s82sample.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
      9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \texttt{mcgreer13\_dr7extend.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
      10. & 4 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \texttt{mcgreer13\_s82extend.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
      11. & 3 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_ndwfs\_old.dat} & \\
%         &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\ 
      12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_dls\_old.dat} & \\
%      &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\
      13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & \texttt{giallongo15\_sample.dat} & \texttt{giallongo15\_sel.dat} &  \\
      14. & 9 & 5.9--6.1 & SDSS Deep & \citet{2008AJ....135.1057J} & 6 & 260.0 & \texttt{jiang08\_sample.dat} & \texttt{jiang08\_sel.dat} \\
      15. & 5 & 5.8--6.0 & --- Deep & \citet{2009AJ....138..305J} & 4 & 195.0 & \texttt{jiang09\_sample.dat} & \texttt{jiang09\_sel.dat} \\
      16. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \texttt{jiang16main\_sample.dat} & \texttt{jiang16main\_selfunc.dat} \\
      17. & 16 & 5.8--6.4 & --- Main & \citet{2006AJ....131.1203F} & 14 & 6600.0 & \texttt{fan06\_sample.dat} & \texttt{fan06\_sel.dat} & Any overlap with 18? \\
      18. & 19 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \texttt{jiang16overlap\_sample.dat} & \texttt{jiang16overlap\_selfunc.dat} \\
      19. & 20 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \texttt{jiang16s82\_sample.dat} & \texttt{jiang16s82\_selfunc.dat} \\
      20. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \texttt{willott10\_cfhqsdeepsample.dat} & \texttt{willott10\_cfhqsdeepsel.dat} \\
      21. & 21 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \texttt{willott10\_cfhqsvwsample.dat} & \texttt{willott10\_cfhqsvwsel.dat} \\
      22. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \texttt{kashikawa15\_sample.dat} & \texttt{kashikawa15\_sel.dat} \\

    \end{tabular}
  \end{table}
\end{landscape}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.495}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.881}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.252}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.626}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.987}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.254}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.  Something wrong with Croom's SGP data?}
\end{figure*}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.348}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.446}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.548}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.645}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.746}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.901}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.119}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.333}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.831}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.196}.pdf} \\

      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.837}.pdf} &
      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z6.001}.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Individual fits.}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
  \end{center}
  \caption{Parameter evolution from individual fits.  Giallongo's qsos not included.}
\end{figure*}

\section*{Acknowledgements}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
eget nisi augue. Vivamus quis purus quis massa tempor posuere non quis
magna. Aenean eleifend, metus eget facilisis faucibus, turpis erat
suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse luctus
eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec massa
ultrices, porttitor nulla at, euismod diam. In ultricies

\bibliographystyle{mnras}
\bibliography{refs}

\bsp
\label{lastpage}
\end{document}

### 2017-04-25 lfg.py
Revert to older global model

@@ -40,35 +40,20 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/kashikawa15_sel.dat', 0.05, 0.05, 6.5, 11),
              ('Data_new/giallongo15_sel.dat', 0.0, 0.0, 0.047, 7)]
 
-lfg = lf(quasar_files=qlumfiles, selection_maps=selnfiles, pnum=[3,2,3,4])
+lfg = lf(quasar_files=qlumfiles, selection_maps=selnfiles, pnum=[3,2,2,3])
 
-# g = np.array([-7.73388053, 1.06477161, -0.11304974,
-#               -22.75923587, -0.96452704,
-#               -3.22779072, -0.27456505,
-#               -1.53566144, 0.02274886, -0.0125998]) 
-
-g = np.array([-8.4312489, 1.48352466, -0.14255848, -23.07419422,  -0.91502736, -3.79904767,  0.0485053,  -0.02002263, -2.85724627,  1.03598097, -0.13644424,  0.00469155])
-
+g = np.array([-7.73388053, 1.06477161, -0.11304974,
+              -22.75923587, -0.96452704,
+              -3.22779072, -0.27456505,
+              -1.53566144, 0.02274886, -0.0125998]) 
+      
 method = 'Nelder-Mead'
 b = lfg.bestfit(g, method=method)
 print b
 
-lfg.prior_min_values = np.array([-11.0, -5.0, -5.0,
-                                 -30.0, -10.0,
-                                 -5.0, -5.0, -5.0, 
-                                 -5.0, -2.0, -2.0, -2.0])
-lfg.prior_max_values = np.array([-4.0, 5.0, 2.0,
-                                 -10.0, 5.0,
-                                 -1.0, 5.0, 5.0, 
-                                 5.0, 2.0, 2.0, 2.0])
+lfg.prior_min_values = np.array([-11.0, -5.0, -5.0, -30.0, -10.0, -5.0, -5.0, -5.0, -2.0, -2.0])
+lfg.prior_max_values = np.array([-4.0, 5.0, 2.0, -10.0, 5.0, -1.0, 5.0, 5.0, 2.0, 2.0])
 assert(np.all(lfg.prior_min_values < lfg.prior_max_values))
-
[…]

### 2017-04-25 composite.py
Restrict Chebyshev redshift domain to z>3.7

@@ -164,7 +164,8 @@ class lf:
         """Redshift evolution of QLF parameters."""
         
         # return T(p, domain=[0.,7.])(1+z)
-        return T(p)(1+z)
+        # return T(p)(1+z)
+        return T(p, domain=[3.7,7.])(1+z)
         
     def getparams(self, theta):
 

### 2017-04-25 drawlf.py
Plot posterior median as best-fit

@@ -33,7 +33,8 @@ def plot_posterior_sample_lfs(lf, ax, mags, **kwargs):
 
 def plot_bestfit_lf(lf, ax, mags, **kwargs):
 
-    phi_fit = lf.log10phi(lf.bf.x, mags)
+    bf = np.median(lf.samples, axis=0)
+    phi_fit = lf.log10phi(bf, mags)
     ax.plot(mags, phi_fit, **kwargs)
     ax.plot(mags, phi_fit, lw=1, c='k', zorder=kwargs['zorder'])
 

### 2017-04-25 individual.py
Convert nqso list to ndarray

@@ -255,7 +255,7 @@ class lf:
 
     def lfnorm(self, theta):
 
-        ns = [x.nqso(self, theta) for x in self.maps]
+        ns = np.array([x.nqso(self, theta) for x in self.maps])
         return sum(ns) 
 
     def neglnlike(self, theta):

### 2017-04-25 lfg.py
Restrict global fit to high z

@@ -3,11 +3,44 @@ import numpy as np
 from composite import lf
 from summary_fromFile import summary_plot as sp
 
-qlumfiles = ['Data_new/dr7z2p2_sample.dat',
-             'Data_new/croom09sgp_sample.dat',
-             'Data_new/croom09ngp_sample.dat',
-             'Data_new/bossdr9color.dat',
-             'Data_new/dr7z3p7_sample.dat',
+# qlumfiles = ['Data_new/dr7z2p2_sample.dat',
+#              'Data_new/croom09sgp_sample.dat',
+#              'Data_new/croom09ngp_sample.dat',
+#              'Data_new/bossdr9color.dat',
+#              'Data_new/dr7z3p7_sample.dat',
+#              'Data_new/glikman11debug.dat',
+#              'Data_new/yang16_sample.dat',
+#              'Data_new/mcgreer13_dr7sample.dat',
+#              'Data_new/mcgreer13_s82sample.dat',
+#              'Data_new/mcgreer13_dr7extend.dat',
+#              'Data_new/mcgreer13_s82extend.dat',
+#              'Data_new/jiang16main_sample.dat',
+#              'Data_new/jiang16overlap_sample.dat',
+#              'Data_new/jiang16s82_sample.dat',
+#              'Data_new/willott10_cfhqsdeepsample.dat',
+#              'Data_new/willott10_cfhqsvwsample.dat',
+#              'Data_new/kashikawa15_sample.dat',
+#              'Data_new/giallongo15_sample.dat']
+
+# selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
+#              ('Data_new/croom09sgp_selfunc.dat', 0.3, 0.05, 64.2, 15),
+#              ('Data_new/croom09ngp_selfunc.dat', 0.3, 0.05, 127.7, 15),
+#              ('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1),
+#              ('Data_new/dr7z3p7_selfunc.dat', 0.1, 0.05, 6248.0, 13),
[…]

### 2017-04-25 summary_cfit.py
Restrict to z > 3.6

@@ -20,8 +20,6 @@ zlims=(0.0,7.0)
 zmin, zmax = zlims
 z = np.linspace(zmin, zmax, num=50)
 
-
-        
 def plot_phi_star(fig, composite, sample=False):
 
     mpl.rcParams['font.size'] = '14'
@@ -41,6 +39,15 @@ def plot_phi_star(fig, composite, sample=False):
         ax.plot(z, phi, color='k', zorder=2)
 
     zmean, zl, zu, u, l, c = np.loadtxt('phi_star.dat', unpack=True)
+
+    select = zmean > 3.6
+    zl = zl[select]
+    zu = zu[select]
+    u = u[select]
+    l = l[select]
+    c = c[select]
+    zmean = zmean[select]
+
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -98,6 +105,15 @@ def plot_m_star(fig, composite, sample=False):
         ax.plot(z, M, color='k', zorder=4)
     
     zmean, zl, zu, u, l, c = np.loadtxt('M_star.dat', unpack=True)
+
+    select = zmean > 3.6
+    zl = zl[select]
+    zu = zu[select]
+    u = u[select]
+    l = l[select]
+    c = c[select]
+    zmean = zmean[select]
+    
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -153,6 +169,15 @@ def plot_alpha(fig, composite, sample=False):
         ax.plot(z, alpha, color='k', zorder=4)
     
     zmean, zl, zu, u, l, c = np.loadtxt('alpha.dat', unpack=True)
+
+    select = zmean > 3.6
+    zl = zl[select]
+    zu = zu[select]
+    u = u[select]
+    l = l[select]
+    c = c[select]
+    zmean = zmean[select]
+    
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -171,12 +196,12 @@ def plot_alpha(fig, composite, sample=False):
 
     zc = np.linspace(0, 7, 500)
 
-    coeffs = chebfit(zmean+1.0, c, 2)
+    coeffs = chebfit(zmean+1.0, c, 1)
     print coeffs
     plt.plot(zc, T(coeffs)(zc+1), lw=2, c='goldenrod')
 
-    def func(z, p0, p1, p2):
-        return T([p0, p1, p2])(z)
+    def func(z, p0, p1):
+        return T([p0, p1])(z)
 
[…]

### 2017-04-25 summary_fromFile.py
Plot wide bins

@@ -42,7 +42,7 @@ def plot_phi_star(fig, composite, sample=False):
         phi = composite.atz(z, composite.getparams(composite.bf.x)[0])
         ax.plot(z, phi, color='g', zorder=2, dashes=[7,2])
         
-    zmean, zl, zu, u, l, c = np.loadtxt('phi_star_fineBins.dat', unpack=True)
+    zmean, zl, zu, u, l, c = np.loadtxt('phi_star.dat', unpack=True)
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -106,7 +106,7 @@ def plot_m_star(fig, composite, sample=False):
         M = composite.atz(z, composite.getparams(composite.bf.x)[1])
         ax.plot(z, M, color='g', zorder=2, dashes=[7,2])
     
-    zmean, zl, zu, u, l, c = np.loadtxt('M_star_fineBins.dat', unpack=True)
+    zmean, zl, zu, u, l, c = np.loadtxt('M_star.dat', unpack=True)
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -167,7 +167,7 @@ def plot_alpha(fig, composite, sample=False):
         ax.plot(z, alpha, color='g', zorder=2, dashes=[7,2],
                 label='Likelihood maximum')
     
-    zmean, zl, zu, u, l, c = np.loadtxt('alpha_fineBins.dat', unpack=True)
+    zmean, zl, zu, u, l, c = np.loadtxt('alpha.dat', unpack=True)
     left = zmean-zl
     right = zu-zmean
     uperr = u-c
@@ -236,7 +236,7 @@ def plot_beta(fig, composite, sample=False):
         beta = composite.atz(z, composite.getparams(composite.bf.x)[3])
         ax.plot(z, beta, color='g', zorder=2, dashes=[7,2])
     
-    zmean, zl, zu, u, l, c = np.loadtxt('beta_fineBins.dat', unpack=True)
+    zmean, zl, zu, u, l, c = np.loadtxt('beta.dat', unpack=True)
     left = zmean-zl
     right = zu-zmean
     uperr = u-c

### 2017-04-25 Paper/paper.tex
Update text

@@
 \usepackage{pdflscape}
+\usepackage{siunitx}
 
@@
   We model the quasar luminosity function as a double power law given
-  by \citep[e.g.,][]{2013ApJ...773...14R}
+  by \citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
   \begin{equation}
@@
 In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
-Equation~(\ref{eqn:lhood}) can be simplified and we can write
+Equation~(\ref{eqn:lhood}) can be simplified and we can write \citep{1983ApJ...269...35M}
 \begin{multline}
@@
 \end{multline}
-where $N$ is the total number of quasars in the sample and the integral in the second term on the right hand side is now on the full range of $M$ and $z$.
+where $N$ is the total number of quasars in the sample and the
+integral in the second term on the right hand side is now on the full
+range of $M$ and $z$.
+
+\section{Hydrogen photoionization rate}
+
+We assume that all quasars have a universal SED, which can be
+parameterised in some fashion.  \citet{2015MNRAS.449.4204L} have
+parameterised the quasar SED as a power law with a break at 912~{\AA},
+\begin{equation}
+f_\nu\propto\begin{cases}
+               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
+               \nu^{-1.70\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
+               \end{cases}
+\label{eqn:sed}
+\end{equation}
+Here $f_\nu$ is the flux density, with units of ergs s$^{-1}$
+cm$^{-2}$ Hz$^{-1}$, although it is often simply called flux.  Note
+that although $f_\nu$ is often the quantity of interest, e.g., when
+calculating the hydrogen ionizing emissivity of quasars, what is shown
+in spectra is often $f_\lambda$, the flux density
+in \emph{wavelength}, which has units of ergs s$^{-1}$
+cm$^{-2}$ \AA$^{-1}$.  If the flux density in frequency is power law,
+then the flux density in wavelength is also power law.  The power law
+index of the flux density in wavelength, $\alpha_\lambda$, is related
+to the power law index of the flux density in frequency, $\alpha_\nu$,
+by $\alpha_\lambda=-(\alpha_\nu+2)$.  From Equation~(\ref{eqn:sed}),
+we can now see that $\alpha_\lambda=-0.3$ in the extreme UV (EUV;
+600~{\AA}$<\lambda<$912~{\AA}) and $\alpha_\lambda=-1.39$ in the far
+UV (FUV; $\lambda>$912~{\AA}).  The quasar SED that we have adopted is
+steep in FUV and shallow in EUV.
+
+How sensible is it to assume that the quasar SED of
+Equation~(\ref{eqn:sed}) is universal?  Of the four published
+composite quasar SEDs (see references in
+\citealt{2015MNRAS.449.4204L}), three agree with
+Equation~(\ref{eqn:sed}).  There is one published composite quasar SED
+that does not agree with Equation~(\ref{eqn:sed}).  This is the
+composite of \citet{2004ApJ...615..135S}, which uses more than 100
+quasars at $z<0.1$.  The EUV slope of this SED is $-0.56$.  (This
+means that the power law index of the flux density in wavelength is
+$-1.44$, so that the spectrum actually becomes even steeper in the
+EUV.  See Figure 8 of \citealt{2015MNRAS.449.4204L}.)  The quasars
+considered by \citet{2004ApJ...615..135S} are much fainter that those
+considered by \citet{2015MNRAS.449.4204L}, which means that it is
+possible that faint quasars have a steep EUV spectrum.  So we could
+say that for faint quasars,
+\begin{equation}
+f_\nu\propto\begin{cases}
+               \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
+               \nu^{-0.56\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
+               \end{cases}
+\label{eqn:sed_faint}
+\end{equation}
+Here, ``faint'' is defined as $M_i(z=2)>-26$.  $M_i(z=2)$ can be
+related to the bolometric luminosity of the quasar (see Figure 9 of
+\citealt{2015MNRAS.449.4204L}.)
+
+The rate of emission of photons of frequency $\nu$ by quasars can be
+written as
+\begin{equation}
+\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu}.
+\end{equation}
+The units of $\dot n_\nu$ are s$^{-1}$~cMpc$^{-3}$~Hz$^{-1}$.  Here
+the integral is over some range of magnitudes, the monochromatic
+luminosity $L_\nu(M)$ is related to the (absolute AB) magnitude
+by \citep{1983ApJ...266..713O}
+\begin{equation}
+M_\nu = -2.5\log_{10}L_\nu+51.60,
+\end{equation}
+and $\phi$ is the luminosity function from Equation~(\ref{eqn:dpl}).
+The luminosity at 1~Ry is related to that at 1450~\AA\ by
+Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint})
+\begin{equation}
+  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61}
+\end{equation}
+The corresponding volume emissivity is conventionally written
+as 
+\begin{equation}
+\epsilon_\nu = \dot n_\nu h\nu (1+z)^3.
+\label{eqn:epsilon}
+\end{equation}
+This is a \emph{physical} density.  The units of $\epsilon_\nu$ are
+erg~s$^{-1}$~pMpc$^{-3}$~Hz$^{-1}$.  This emissivity can now be used
+to calculate the ionizing flux and photoionization rate contributed by
+quasars.  The frequency dependence above 1~Ry is given by
+Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
+\nu_{912}$
+\begin{equation}
+  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
+  \label{eqn:epsilon_freq}
+\end{equation}
+where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$ (Equation~\ref{eqn:sed_faint}).
+
+The emissivity calculated in Equation~(\ref{eqn:epsilon}) is a source
+property.  We are now interested in what flux this emissivity produces
+in the surrounding intergalactic medium.  This brings in the medium's
+properties also, via the radiative transfer equation.  The flux is
+\citep{2012ApJ...746..125H}
+\begin{multline}
+  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}\frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
+  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
+  \label{eqn:flux}
+\end{multline}
+where
+\begin{equation}
+  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
+\end{equation}
+We estimate the effective optical depth as
+\begin{equation}
+  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
+\end{equation}
+where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$ and the column density
+distribution $f(N_\mathrm{HI}, z)$ is taken to be a power law \citep{2013MNRAS.436.1023B}
+\begin{equation}
+  f(N_\mathrm{HI}, z) = \frac{A}{N_\mathrm{LL}}\left(\frac{N_\mathrm{HI}}{N_\mathrm{LL}}\right)^{-\beta_N}\left(\frac{1+z}{4.5}\right)^{-\beta_z},
+\end{equation}
+with $A=0.93$, $\beta_N=1.33$, $\beta_z=1.92$, and
+$N_\mathrm{LL}=10^{17.2}$~cm$^{-2}$.  The hydrogen photoionization
+rate is then given by
+\begin{equation}
+  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j(\nu,z)}{h\nu} \sigma(\nu),
+\end{equation}
+
+\subsection{Local source approximation}
+
+In the local source approximation, Equation~(\ref{eqn:flux}) becomes
+\begin{equation}
+  j(\nu_0, z_0) = \frac{1}{4\pi}\lambda_\mathrm{mfp}(\nu_0, z_0)\epsilon(\nu_0, z_0),
+\end{equation}
+where $\lambda_\mathrm{mfp}$ is the mean free path.  The hydrogen
+photoionization rate is given by
+\begin{equation}
+  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j_\nu}{h\nu} \sigma(\nu),
+  \label{eqn:gammapi}
+\end{equation}
+where $\sigma$ is the ionization cross-section
+\begin{equation}
+  \sigma(\nu) = \sigma_0\left(\frac{\nu}{\nu_{912}}\right)^{-3},
+  \label{eqn:sigma}
+\end{equation}
+with $\sigma_0=6.3\times 10^{-18}$~cm$^2$ \citep{2006agna.book.....O}.
+In the redshift range $z=2.3$--$5.5$, the mean free path is measured
+to be \citep{2014MNRAS.445.1745W}
+\begin{equation}
+  \lambda_\mathrm{mfp}(\nu, z)= \lambda_0\left(\frac{1+z}{5}\right)^{-5.4}\left(\frac{\nu}{\nu_{912}}\right)^{1.5},
+  \label{eqn:mfp}
+\end{equation}
+where the frequency dependence comes from the assumed column density
+distribution $f(N_\mathrm{HI})\propto N_\mathrm{HI}^{-1.5}$.  We
+extrapolate the redshift dependence in Equation~(\ref{eqn:mfp}) at
+$z<2.3$ and $z>5.5$.  Combining Equations~(\ref{eqn:epsilon_freq}),
+(\ref{eqn:sigma}), and (\ref{eqn:mfp}), Equation~(\ref{eqn:gammapi})
+gives
+\begin{multline}
+  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg s^{-1} Hz^{-1} cMpc^{-3}}}\right)\\
+  \times\left(\frac{1}{1.5-\alpha}\right)\left(\frac{1+z}{5}\right)^{-2.4}.
+\end{multline}
+Note that this equation refers to the \emph{comoving} emissivity.  The
+local source approximation works well for $z>3$ \citep{2013MNRAS.436.1023B}.
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{qsos.pdf}
+  \end{center}
+  \caption{Quasar samples.}
+  \label{fig:qsos}
+\end{figure*}
+
+\begin{table*}
+  % In published version of this table, we could remove file names and add data homogenisation in Notes.
+  % Add z ~ 7 qso when you add it to analysis
+  % See data.tex for a version of this table that includes file names
+  \caption{Quasar data sets}
+  \label{tab:samples}
+  \begin{tabular}{crcllrSl}
+    \hline
+    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
+    & & & & & of quasars & {(deg$^2$)} & \\
+    \hline
+    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
+    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
+    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
+    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
+    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
+    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
+    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
+    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
+    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
+    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
+    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
+    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
+    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
+    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
+    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
+    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
+    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
+    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
+    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
+  \end{tabular}
+\end{table*}
 
@@
   \caption{Comparison with the published LF of
-    \citet{2013ApJ...768..105M} for SDSS DR3.  There are 15,343
+    \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
     quasars in this sample, of which 155 quasars have $z<0.3$ and 9
@@
 
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
+%%   \end{center}
+%%   \caption{Comparison with the published LF of
+%%     \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
+%%     quasars in their two samples (NDWFS and DLS).}
+%%   \label{fig:mcgreer}
+%% \end{figure*}
+
 \begin{figure*}
   \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
+    \includegraphics[width=\textwidth]{glikman3.pdf}
   \end{center}
-  \caption{Comparison with the published LF of
-    \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
-    quasars in their two samples (NDWFS and DLS).}
-  \label{fig:mcgreer}
+  \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
+    and (b) use her volume calculations.  Panels (c)--(e) use our
+    volume calculations.  Various corrections incorporated by Gabor
+    are in panels (c)--(e).  Red open circles in all panels are
+    Glikman's published values; I cannot reproduce them in any of the
+    panels.  All luminosity function in this version of the draft use
+    Gabor's October data from panel (d).}
+  \label{fig:glikman}
 \end{figure*}
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{qsos.pdf}
+    \includegraphics[width=\textwidth]{giallongo2.pdf}
   \end{center}
-  \caption{Quasar samples.}
-  \label{fig:qsos}
-\end{figure*}
-
-\begin{landscape}
-  \begin{table}
-    % In published version of this table, we could remove file names and add data homogenisation in Notes.
-    % Add z ~ 7 qso when you add it to analysis
-    \caption{Quasar data sets}
-    \label{tab:samples}
-    \begin{tabular}{cccllcclll}
-      \hline
-      & ID & $z$ & Survey & Reference & Number & Area & Sample file & Selection map file & Notes \\
-      & & & & & of quasars & (deg$^2$) & & & \\
-      \hline
-      1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \texttt{dr7z2p2\_sample.dat} & \texttt{dr7z2p2\_selfunc.dat} &  \\
-      2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \texttt{croom09sgp\_sample.dat} & \texttt{croom09sgp\_selfunc.dat} & \\ 
-      3. &  2 & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \texttt{croom09ngp\_sample.dat} & \texttt{croom09ngp\_selfunc.dat} & \\
-      4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \texttt{bossdr9color.dat} & \texttt{ross13\_selfunc2.dat} & \\
-      5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & \texttt{dr7z3p7\_sample.dat} & \texttt{dr7z3p7\_selfunc.dat} & Sample restricted to $z<4.7$ \\
-      6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & \texttt{yang16\_sample.dat} & \texttt{yang16\_sel.dat} & Overlaps with 8 for $M_{1450}>-26.73$? \\
-      7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \texttt{mcgreer13\_dr7sample.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
-      8. &  4 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \texttt{mcgreer13\_s82sample.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
-      9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \texttt{mcgreer13\_dr7extend.dat} & \texttt{mcgreer13\_dr7selfunc.dat} & \\
-      10. & 4 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \texttt{mcgreer13\_s82extend.dat} & \texttt{mcgreer13\_s82selfunc.dat} & \\
-      11. & 3 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_ndwfs\_old.dat} & \\
-%         &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\ 
-      12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \texttt{glikman11qso.dat} & \texttt{glikman11\_selfunc\_dls\_old.dat} & \\
-%      &  &  &  &  &  &  & \texttt{glikman11debug.dat} & \texttt{glikman11\_selfunc\_ndwfs.dat} & \\
-      13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & \texttt{giallongo15\_sample.dat} & \texttt{giallongo15\_sel.dat} &  \\
-      14. & 9 & 5.9--6.1 & SDSS Deep & \citet{2008AJ....135.1057J} & 6 & 260.0 & \texttt{jiang08\_sample.dat} & \texttt{jiang08\_sel.dat} \\
-      15. & 5 & 5.8--6.0 & --- Deep & \citet{2009AJ....138..305J} & 4 & 195.0 & \texttt{jiang09\_sample.dat} & \texttt{jiang09\_sel.dat} \\
-      16. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \texttt{jiang16main\_sample.dat} & \texttt{jiang16main\_selfunc.dat} \\
-      17. & 16 & 5.8--6.4 & --- Main & \citet{2006AJ....131.1203F} & 14 & 6600.0 & \texttt{fan06\_sample.dat} & \texttt{fan06\_sel.dat} & Any overlap with 18? \\
-      18. & 19 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \texttt{jiang16overlap\_sample.dat} & \texttt{jiang16overlap\_selfunc.dat} \\
-      19. & 20 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \texttt{jiang16s82\_sample.dat} & \texttt{jiang16s82\_selfunc.dat} \\
-      20. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \texttt{willott10\_cfhqsdeepsample.dat} & \texttt{willott10\_cfhqsdeepsel.dat} \\
-      21. & 21 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \texttt{willott10\_cfhqsvwsample.dat} & \texttt{willott10\_cfhqsvwsel.dat} \\
-      22. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \texttt{kashikawa15\_sample.dat} & \texttt{kashikawa15\_sel.dat} \\
-
-    \end{tabular}
-  \end{table}
-\end{landscape}
-
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.495}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z0.881}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.252}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.626}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z1.987}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.254}.pdf} \\
-    \end{tabular}
-  \end{center}
-  \caption{Individual fits.  Something wrong with Croom's SGP data?}
+  \caption{Giallongo's LF when selection function is taken to be
+    $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
+    additional correction is required, which has been incorporated in
+    our LFs.}
+  \label{fig:giallongo}
 \end{figure*}
@@
   \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.348}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.446}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.548}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.645}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.746}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z2.901}.pdf} \\
-    \end{tabular}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
   \end{center}
-  \caption{Individual fits.}
+  \caption{Luminosity function for $z=0.3$ to $2.6$.}
+  \label{fig:mosaic}
 \end{figure*}
@@
   \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.119}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.333}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z3.831}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.196}.pdf} \\
-
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z4.837}.pdf} &
-      \includegraphics[width=0.4\textwidth,keepaspectratio]{{lf_z6.001}.pdf} \\
-    \end{tabular}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
   \end{center}
-  \caption{Individual fits.}
+  \caption{Luminosity function for $z=2.6$ to $6.5$.}
+  \label{fig:mosaic2}
 \end{figure*}
@@
   \end{center}
-  \caption{Parameter evolution from individual fits.  Giallongo's qsos not included.}
+  \caption{Parameter evolution from individual fits.  Coloured points
+    show results when Giallongo quasars are not included.  Black
+    points show results when Giallongo quasars are included.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{gammapi.pdf}
+  \end{center}
+  \caption{Hydrogen photoionization rate}
+  \label{fig:gammapi}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{emissivity.pdf}
+  \end{center}
+  \caption{LyC emissivity.}
+  \label{fig:gammapi}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{evolution_global.pdf}
+  \end{center}
+  \caption{One possible global fit with a 12-parameter model.  Each
+    double power law parameter has a 4th-order Chebyshev polynomial
+    form.  Black points show result from Manti et al.~2017.}
+  \label{fig:global_fit}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
+  \end{center}
+  \caption{Shouldn't there be cosmic downsizing?}
+  \label{fig:rhoqso}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+  \end{center}
+  \caption{Same as Figure~\ref{fig:rhoqso} but now with the global model.  This global model is the same as that shown in Figure~\ref{fig:global_fit}.}
+  \label{fig:rhoqso_withGlobal}
+\end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle.png}
+%%   \end{center}
+%%   \caption{Posteriors corresponding to Figure~\ref{fig:global_fit}.}
+%%   \label{fig:triangle}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[height=\textheight]{chains.pdf}
+%%   \end{center}
+%%   \caption{MCMC chains corresponding to Figure~\ref{fig:global_fit}.}
+%%   \label{fig:chains}
+%% \end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{evolution_cleaned.pdf}
+  \end{center}
+  \caption{Parameter evolution after making two changes to the
+    analysis: (1) use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and
+    (2) use only $p>0.9$ quasars in the $z>3.7$ sample of Richards.
+    The individual fits with these changes are shown in Figures
+    \ref{fig:mosaic} and \ref{fig:mosaic2}.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{evolution_model1.pdf}
+  \end{center}
+  \caption{My current global fit.  I am trying to understand why it is
+    so bad.  See Figures~17--21 for more on this.  Note that now I am
+    only trying to fit quasars with $z=0.6$--$2.2$ and $2.8$--$5.5$.
+    I am trying to fit straight lines for $M_*$ and $\alpha$ and
+    quadratics for $\phi_*$ and $\beta$.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_model1.pdf}
+  \end{center}
+  \caption{The global fit is quite good at $z\sim 1$--$2$.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth,keepaspectratio]{mosaic2_model1.pdf}
+  \end{center}
+  \caption{Previous figure continued.}
+\end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[height=\textheight,keepaspectratio]{chains_model1.pdf}
+%%   \end{center}
+%%   \caption{MCMC chains for the global model of Figures~16--18.}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle_model1.png}
+%%   \end{center}
+%%   \caption{Posteriors for the global model of Figures~16--18.}
+%% \end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_model1.pdf}
+  \end{center}
+  \caption{Quasar number density in the global model of Figure~16.}
 \end{figure*}

### 2017-06-12 Paper/paper.tex
Update plots

@@
   \end{center}
-  \caption{Luminosity function for $z=0.3$ to $2.6$.}
+  \caption{Individual luminosity function fits for $z=0.3$ to $2.6$.}
   \label{fig:mosaic}
@@
   \end{center}
-  \caption{Luminosity function for $z=2.6$ to $6.5$.}
+  \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
   \label{fig:mosaic2}
@@
   \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_allz.pdf}
   \end{center}
-  \caption{Parameter evolution from individual fits.  Coloured points
-    show results when Giallongo quasars are not included.  Black
-    points show results when Giallongo quasars are included.}
+  \caption{AGN number density evolution, showing the systematic offset in BOSS quasars.}
+  \label{fig:rhoqso_allz}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{evolution_alldata.pdf}
+  \end{center}
+  \caption{Parameter evolution from individual fits in
+    Figures~\ref{fig:mosaic} and \ref{fig:mosaic2}.  Parameters from
+    BOSS quasars are seen to be systematically offset. \textbf{[Show
+        $z < 0.6$ point also?]}}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
+  \end{center}
+  \caption{AGN number density evolution with some BOSS quasars
+    removed.}
+  \label{fig:rhoqso}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{evolution_seldata.pdf}
+  \end{center}
+  \caption{Parameter evolution with some BOSS quasars removed.  We (1)
+    use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and (2) use only
+    $p>0.9$ quasars in the $z>3.7$ sample of Richards.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_withGlobal.pdf}
+  \end{center}
+  \caption{Individual and composite luminosity function fits for
+    $z=0.3$ to $2.6$.  They do not agree for $2.2 < z < 2.6$ because
+    composite fit does not consider quasars at those redshifts.}
+  \label{fig:mosaic_withGlobal}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2_withGlobal.pdf}
+  \end{center}
+  \caption{Individual and composite luminosity function fits for
+    $z=2.6$ to $6.5$.  They do not agree for $2.6 < z < 2.8$ because
+    composite fit does not consider quasars at those redshifts.}
+  \label{fig:mosaic2_withGlobal}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{evolution_global.pdf}
+  \end{center}
+  \caption{Luminosity function parameter evolution in the global model.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+  \end{center}
+  \caption{AGN number density evolution in the global model.}
+  \label{fig:rhoqso}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
+    \end{tabular}
+  \end{center}
+  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
+    Model luminosity functions are integrated down to $M_{1450}=-18$
+    in the left panel and $-20$ in the right panel.}
+  \label{fig:gammapi}
 \end{figure*}
@@
   \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{emissivity.pdf}
+    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
   \end{center}
-  \caption{LyC emissivity.}
-  \label{fig:gammapi}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{evolution_global.pdf}
-  \end{center}
-  \caption{One possible global fit with a 12-parameter model.  Each
-    double power law parameter has a 4th-order Chebyshev polynomial
-    form.  Black points show result from Manti et al.~2017.}
-  \label{fig:global_fit}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
-  \end{center}
-  \caption{Shouldn't there be cosmic downsizing?}
-  \label{fig:rhoqso}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
-  \end{center}
-  \caption{Same as Figure~\ref{fig:rhoqso} but now with the global model.  This global model is the same as that shown in Figure~\ref{fig:global_fit}.}
-  \label{fig:rhoqso_withGlobal}
-\end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle.png}
-%%   \end{center}
-%%   \caption{Posteriors corresponding to Figure~\ref{fig:global_fit}.}
-%%   \label{fig:triangle}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[height=\textheight]{chains.pdf}
-%%   \end{center}
-%%   \caption{MCMC chains corresponding to Figure~\ref{fig:global_fit}.}
-%%   \label{fig:chains}
-%% \end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{evolution_cleaned.pdf}
-  \end{center}
-  \caption{Parameter evolution after making two changes to the
-    analysis: (1) use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and
-    (2) use only $p>0.9$ quasars in the $z>3.7$ sample of Richards.
-    The individual fits with these changes are shown in Figures
-    \ref{fig:mosaic} and \ref{fig:mosaic2}.}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{evolution_model1.pdf}
-  \end{center}
-  \caption{My current global fit.  I am trying to understand why it is
-    so bad.  See Figures~17--21 for more on this.  Note that now I am
-    only trying to fit quasars with $z=0.6$--$2.2$ and $2.8$--$5.5$.
-    I am trying to fit straight lines for $M_*$ and $\alpha$ and
-    quadratics for $\phi_*$ and $\beta$.}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_model1.pdf}
-  \end{center}
-  \caption{The global fit is quite good at $z\sim 1$--$2$.}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.7\textwidth,keepaspectratio]{mosaic2_model1.pdf}
-  \end{center}
-  \caption{Previous figure continued.}
-\end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[height=\textheight,keepaspectratio]{chains_model1.pdf}
-%%   \end{center}
-%%   \caption{MCMC chains for the global model of Figures~16--18.}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{triangle_model1.png}
-%%   \end{center}
-%%   \caption{Posteriors for the global model of Figures~16--18.}
-%% \end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_model1.pdf}
-  \end{center}
-  \caption{Quasar number density in the global model of Figure~16.}
+  \caption{Parameter evolution from individual fits.  Coloured points
+    show results when Giallongo quasars are not included.  Black
+    points show results when Giallongo quasars are included.}
 \end{figure*}

### 2017-06-20 rtg2.py
Check Gamma_HI calculation by reproducing HM12 result

@@ -147,7 +147,7 @@ def draw_j(j, w, z):
 
 wmin = 5.0
 wmax = 5.0e3
-ws = np.logspace(0.0, 4.0, num=1000)
+ws = np.logspace(0.0, 4.0, num=10000)
 nu = 2.998e18/ws 
 hplanck = 6.626069e-27 # erg s
 
@@ -155,7 +155,7 @@ j = np.zeros_like(nu)
 
 zmax = 15.0
 zmin = 0.0
-dz = 0.01
+dz = 0.1
 n = (zmax-zmin)/dz+1
 zs = np.linspace(zmax, zmin, num=n)
 
@@ -192,8 +192,19 @@ for z in zs:
 
     gs.append(g_hm12)
 
-    # print z, g, g_hm12, g_hm12/g
+    print z, g, g_hm12, g_hm12/g
 
+check_gamma_HM12 = False
+if check_gamma_HM12:
+    for z in zs:
+
+        nu_local = 2.998e18/(ws*(1.0+z))
+        j_hm12 = bkgintens_HM12(ws*(1.0+z), z*np.ones_like(ws), grid=False)
+        n = 4.0*np.pi*j_hm12/(hplanck*nu_local)
+        s = np.array([sigma_HI(x) for x in nu_local])
+        
+        g_hm12 = -np.trapz(n*s, x=nu_local) # s^-1
+        gs.append(g_hm12)
     
 def draw_g(z, g):
 
@@ -256,3 +267,34 @@ def draw_g(z, g):
 
 gs = np.array(gs)
 draw_g(zs,gs)
+
+def check_emissivity():
+
+    fig = plt.figure(figsize=(7, 7), dpi=100)
+    ax = fig.add_subplot(1, 1, 1)
+
+    ax.tick_params('both', which='major', length=7, width=1)
+    ax.tick_params('both', which='minor', length=5, width=1)
+    ax.tick_params('x', which='major', pad=6)
+
+    ax.set_ylabel(r'$j_\nu$ [$10^{-22}$ erg s$^{-1}$ Hz$^{-1}$ sr$^{-1}$ cm$^{-2}$]')
+    ax.set_xlabel(r'$\lambda$')
+
+    ax.set_yscale('log')
+    ax.set_xscale('log')
+    ax.set_ylim(1.0e-7, 1.0e3)
+    ax.set_xlim(5.0, 4.0e3)
+
+    ax.plot(w, j/1.0e-22, lw=2, c='k')
[…]

### 2017-06-20 rtg2.py
Plot HM12 emissivity

@@ -147,7 +147,7 @@ def draw_j(j, w, z):
 
 wmin = 5.0
 wmax = 5.0e3
-ws = np.logspace(0.0, 4.0, num=10000)
+ws = np.logspace(0.0, 4.0, num=100)
 nu = 2.998e18/ws 
 hplanck = 6.626069e-27 # erg s
 
@@ -192,7 +192,7 @@ for z in zs:
 
     gs.append(g_hm12)
 
-    print z, g, g_hm12, g_hm12/g
+    # print z, g, g_hm12, g_hm12/g
 
 check_gamma_HM12 = False
 if check_gamma_HM12:
@@ -265,8 +265,8 @@ def draw_g(z, g):
 
     return
 
-gs = np.array(gs)
-draw_g(zs,gs)
+# gs = np.array(gs)
+# draw_g(zs,gs)
 
 def check_emissivity():
 
@@ -277,24 +277,58 @@ def check_emissivity():
     ax.tick_params('both', which='minor', length=5, width=1)
     ax.tick_params('x', which='major', pad=6)
 
-    ax.set_ylabel(r'$j_\nu$ [$10^{-22}$ erg s$^{-1}$ Hz$^{-1}$ sr$^{-1}$ cm$^{-2}$]')
-    ax.set_xlabel(r'$\lambda$')
+    ax.set_ylabel(r'comoving emissivity per log bandwidth [$10^{39}$~erg s$^{-1}$ cMpc$^{-3}$]', fontsize=14)
+    ax.set_xlabel(r'$E$~[eV]', fontsize=14)
 
     ax.set_yscale('log')
     ax.set_xscale('log')
-    ax.set_ylim(1.0e-7, 1.0e3)
-    ax.set_xlim(5.0, 4.0e3)
+    
+    ax.set_ylim(0.3, 3000.0)
+    ax.set_xlim(1.0, 60.0)
 
-    ax.plot(w, j/1.0e-22, lw=2, c='k')
-    j_hm12 = bkgintens_HM12(w, z*np.ones_like(w), grid=False)
-    ax.plot(w, j_hm12/1.0e-22, lw=2, c='tomato')
+    locs = (1.0, 5.0, 10.0, 50.0)
+    labels = ('1', '5', '10', '50')
+    plt.xticks(locs, labels)
 
-    ax.axvline(1216.0, lw=1, c='k', dashes=[7,2])
[…]

### 2017-06-20 rtg2.py
Plot galaxies-only HM12 emissivity

@@ -268,7 +268,33 @@ def draw_g(z, g):
 # gs = np.array(gs)
 # draw_g(zs,gs)
 
-def check_emissivity():
+def qso_emissivity_hm12(nu, z):
+
+    """HM12 qso comoving emissivity.
+
+    This is given by equations (37) and (38) of HM12.
+
+    """
+
+    w = 2.998e18/nu
+    nu_912 = 2.998e18/912.0
+    nu_1300 = 2.998e18/1300.0
+    
+    a = 10.0**24.6 * (1.0+z)**4.68 * np.exp(-0.28*z)/(np.exp(1.77*z)+26.3)
+    b = a * (nu_1300/nu_912)**-1.57
+
+    if w > 1300.0:
+        e = b*(nu/nu_1300)**-0.44
+    else:
+        e = a*(nu/nu_912)**-1.57
+
+    return e
+
+def plot_qso_emissivity():
+
+    """Plot HM12 qso emissivity. 
+    
+    """
 
     fig = plt.figure(figsize=(7, 7), dpi=100)
     ax = fig.add_subplot(1, 1, 1)
@@ -277,7 +303,62 @@ def check_emissivity():
     ax.tick_params('both', which='minor', length=5, width=1)
     ax.tick_params('x', which='major', pad=6)
 
-    ax.set_ylabel(r'comoving emissivity per log bandwidth [$10^{39}$~erg s$^{-1}$ cMpc$^{-3}$]', fontsize=14)
+    ax.set_ylabel(r'emissivity [$10^{39}$~erg s$^{-1}$ Hz$^{-1}$ cMpc$^{-3}$]')
+    ax.set_xlabel(r'$\nu$~[Hz]')
+
+    ax.set_yscale('log')
+    ax.set_xscale('log')
+    
+    nu = np.logspace(13.0,17.0,num=10000)
+
+    z = 1.1
+    e = np.array([qso_emissivity_hm12(x, z) for x in nu])
+    ax.plot(nu, e, lw=2, c='k', label='$z=1.1$') 
+    
+    z = 3.0
+    e = np.array([qso_emissivity_hm12(x, z) for x in nu])
+    ax.plot(nu, e, lw=2, c='r', label='$z=3.0$') 
+
+    z = 4.9
+    e = np.array([qso_emissivity_hm12(x, z) for x in nu])
+    ax.plot(nu, e, lw=2, c='g', label='$z=4.9$') 
+
+    z = 8.1
[…]

### 2017-06-21 rtg2.py
Implement HM12 HI column density distribution

@@ -68,7 +68,95 @@ def f(N_HI, z):
     beta_z = 1.92
     N_LL = 10.0**17.2 # cm^-2 
 
-    return (A/N_LL) * ((N_HI/N_LL)**(-beta_N)) * (((1.0+z)/4.5)**beta_z) # cm^2 
+    return (A/N_LL) * ((N_HI/N_LL)**(-beta_N)) * (((1.0+z)/4.5)**beta_z) # cm^2
+
+def f_HM12(N_HI, z):
+
+    logNHI = np.log10(N_HI)
+
+    if z < 1.56:
+        if 11.0 <= log10NHI < 15.0:
+            a = 1.73e8 
+            b = 2
+            g = 0.16
+        elif 15.0 <= log10NHI < 17.5:
+            a = 5.49e15 
+            b = 2.0
+            g = 0.16 
+        elif 17.5 <= log10NHI < 19.0:
+            f17p5 = 5.49e15 * (1+z)**0.16 * N_HI**-2
+            f19 = 1.28 * (1+z)**0.16 * N_HI**-1.05
+            r = 19.0/17.5
+            b = np.log10(f17p5/f19)/np.log10(r)
+            a = f17p5 * N_HI**b
+            return a * N_HI**-b
+        elif 19.0 <= log10NHI < 20.3:
+            a = 1.28
+            b = 1.05 # Not specified by HM12; assuming same as high z
+            g = 0.16 
+        elif 20.3 <= log10NHI:
+            a = 2.47e19 
+            b = 2.0 # Not specified by HM12; assuming same as high z
+            g = 0.16 
+        return a * (1+z)**g * N_HI**-b
+    
+    elif 1.56 <= z < 5.5:
+        if 11.0 <= log10NHI < 15.0:
+            a = 1.2e7
+            b = 1.5
+            g = 3.0
+        elif 15.0 <= log10NHI < 17.5:
+            a = 3.8e14
+            b = 2.0
+            g = 3.0
+        elif 17.5 <= log10NHI < 19.0:
+            f17p5 = 3.8e14 * (1+z)**3 * N_HI**-2
+            f19 = 0.45 * (1+z)**1.27 * N_HI**-1.05
+            r = 19.0/17.5
+            b = np.log10(f17p5/f19)/np.log10(r)
+            a = f17p5 * N_HI**b
+            return a * N_HI**-b
+        elif 19.0 <= log10NHI < 20.3:
+            a = 0.45
+            b = 1.05
+            g = 1.27
[…]

### 2017-06-21 rtg2.py
Debug HM12 CDDF

@@ -72,7 +72,7 @@ def f(N_HI, z):
 
 def f_HM12(N_HI, z):
 
-    logNHI = np.log10(N_HI)
+    log10NHI = np.log10(N_HI)
 
     if z < 1.56:
         if 11.0 <= log10NHI < 15.0:
@@ -84,11 +84,10 @@ def f_HM12(N_HI, z):
             b = 2.0
             g = 0.16 
         elif 17.5 <= log10NHI < 19.0:
-            f17p5 = 5.49e15 * (1+z)**0.16 * N_HI**-2
-            f19 = 1.28 * (1+z)**0.16 * N_HI**-1.05
-            r = 19.0/17.5
-            b = np.log10(f17p5/f19)/np.log10(r)
-            a = f17p5 * N_HI**b
+            f17p5 = 5.49e15 * (1+z)**0.16 * (10.0**17.5)**-2
+            f19 = 1.28 * (1+z)**0.16 * (10.0**19)**-1.05
+            b = np.log10(f17p5/f19)/1.5
+            a = f17p5 * (10.0**17.5)**b
             return a * N_HI**-b
         elif 19.0 <= log10NHI < 20.3:
             a = 1.28
@@ -110,11 +109,10 @@ def f_HM12(N_HI, z):
             b = 2.0
             g = 3.0
         elif 17.5 <= log10NHI < 19.0:
-            f17p5 = 3.8e14 * (1+z)**3 * N_HI**-2
-            f19 = 0.45 * (1+z)**1.27 * N_HI**-1.05
-            r = 19.0/17.5
-            b = np.log10(f17p5/f19)/np.log10(r)
-            a = f17p5 * N_HI**b
+            f17p5 = 3.8e14 * (1+z)**3 * (10.0**17.5)**-2
+            f19 = 0.45 * (1+z)**1.27 * (10.0**19)**-1.05
+            b = np.log10(f17p5/f19)/1.5
+            a = f17p5 * (10.0**17.5)**b
             return a * N_HI**-b
         elif 19.0 <= log10NHI < 20.3:
             a = 0.45
@@ -137,12 +135,11 @@ def f_HM12(N_HI, z):
             g = 9.9
         elif 17.5 <= log10NHI < 19.0:
             # f(N_HI) for log10NHI >= 17.5 not specified by HM12 at
-            # these redshifts.  I am assuming same behaviour as low z. 
-            f17p5 = 9.35e8 * (1+z)**2 * N_HI**-9.9
[…]

### 2017-06-21 rtg2.py
Plot HM12 CDDF

@@ -153,8 +153,50 @@ def f_HM12(N_HI, z):
 
     return 0.0
 
-vf_HM12 = np.vectorize(f_HM12, otypes=[np.float]) 
+vf_HM12 = np.vectorize(f_HM12, otypes=[np.float])
 
+def plot_f():
+
+    fig = plt.figure(figsize=(7, 7), dpi=100)
+    ax = fig.add_subplot(1, 1, 1)
+
+    ax.tick_params('both', which='major', length=7, width=1)
+    ax.tick_params('both', which='minor', length=5, width=1)
+    ax.tick_params('x', which='major', pad=6)
+
+    ax.set_ylabel(r'$\log_{10} f(N_\mathrm{HI},z)$')
+    ax.set_xlabel(r'$\log_{10}(N_\mathrm{HI}/\mathrm{cm}^{-2})$') 
+
+    ax.set_ylim(-25.0, -7.0)
+    ax.set_xlim(11.0, 21.5)
+
+    locs = range(-24, -6, 2)
+    labels = ['$'+str(x)+'$' for x in locs]
+    plt.yticks(locs, labels)
+
+    n = np.logspace(11.0,23.0,num=1000)
+    z = 3.5
+    f = vf_HM12(n, z)
+    ax.plot(np.log10(n), np.log10(f), lw=2, c='k', label='$z=3.5$') 
+    
+    z = 2.0
+    f = vf_HM12(n, z)
+    ax.plot(np.log10(n), np.log10(f/50), lw=2, c='r', label='$z=2$') 
+
+    z = 5.0
+    f = vf_HM12(n, z)
+    ax.plot(np.log10(n), np.log10(f*50), lw=2, c='b', label='$z=5$')
+
+    plt.legend(loc='lower left', fontsize=12, handlelength=3,
+               frameon=False, framealpha=0.0, labelspacing=.1,
+               handletextpad=0.1, borderpad=0.1, scatterpoints=1)
+
+    
+    plt.savefig('f.pdf'.format(z),bbox_inches='tight')
+    plt.close('all')
+    
+plot_f()
+    
 def sigma_HI(nu):
 
     """Calculate the HI ionization cross-section.  

### 2017-06-21 rtg2.py
Debug HM12 CDDF
Slopes were wrong.

@@ -77,7 +77,7 @@ def f_HM12(N_HI, z):
     if z < 1.56:
         if 11.0 <= log10NHI < 15.0:
             a = 1.73e8 
-            b = 2
+            b = 1.5
             g = 0.16
         elif 15.0 <= log10NHI < 17.5:
             a = 5.49e15 
@@ -136,7 +136,7 @@ def f_HM12(N_HI, z):
         elif 17.5 <= log10NHI < 19.0:
             # f(N_HI) for log10NHI >= 17.5 not specified by HM12 at
             # these redshifts.  I am assuming same behaviour as low z.
-            f17p5 = 9.35e8 * (1+z)**9.9 * (10.0**17.5)**-3
+            f17p5 = 9.35e8 * (1+z)**9.9 * (10.0**17.5)**-2
             f19 = 0.45 * (1+z)**1.27 * (10.0**19)**-1.05
             b = np.log10(f17p5/f19)/1.5
             a = f17p5 * (10.0**17.5)**b

### 2017-06-21 rtg2.py
PEP 8

@@ -157,6 +157,12 @@ vf_HM12 = np.vectorize(f_HM12, otypes=[np.float])
 
 def plot_f():
 
+    """Plot HM12 HI column density distribution.
+
+    Compare result to left panel of Figure 1 of HM12. 
+
+    """
+
     fig = plt.figure(figsize=(7, 7), dpi=100)
     ax = fig.add_subplot(1, 1, 1)
 
@@ -181,11 +187,11 @@ def plot_f():
     
     z = 2.0
     f = vf_HM12(n, z)
-    ax.plot(np.log10(n), np.log10(f/50), lw=2, c='r', label='$z=2$') 
+    ax.plot(np.log10(n), np.log10(f/50), lw=2, c='r', label='$z=2.0$') 
 
     z = 5.0
     f = vf_HM12(n, z)
-    ax.plot(np.log10(n), np.log10(f*50), lw=2, c='b', label='$z=5$')
+    ax.plot(np.log10(n), np.log10(f*50), lw=2, c='b', label='$z=5.0$')
 
     plt.legend(loc='lower left', fontsize=12, handlelength=3,
                frameon=False, framealpha=0.0, labelspacing=.1,

### 2017-06-21 rtg2.py
Plot evolution of HM12 CDDF

@@ -200,9 +200,59 @@ def plot_f():
     
     plt.savefig('f.pdf'.format(z),bbox_inches='tight')
     plt.close('all')
+
+# plot_f()
+
+def plot_f_vs_z():
+
+    """Plot HM12 HI column density distribution evolution. 
+
+    Just to confirm continuity.
+
+    """
+
+    fig = plt.figure(figsize=(7, 7), dpi=100)
+    ax = fig.add_subplot(1, 1, 1)
+
+    ax.tick_params('both', which='major', length=7, width=1)
+    ax.tick_params('both', which='minor', length=5, width=1)
+    ax.tick_params('x', which='major', pad=6)
+
+    ax.set_ylabel(r'$\log_{10} f(N_\mathrm{HI},z)$')
+    ax.set_xlabel(r'$z$') 
+
+    n = 1.0e12
+    z = np.linspace(0,7,num=100)
+    f = vf_HM12(n, z)
+    ax.plot(z, np.log10(f), lw=2, c='g', label='$N_\mathrm{HI}=10^{12} \mathrm{cm}^{-2}$') 
     
-plot_f()
+    n = 1.0e16
+    z = np.linspace(0,7,num=100)
+    f = vf_HM12(n, z)
+    ax.plot(z, np.log10(f), lw=2, c='k', label='$N_\mathrm{HI}=10^{16} \mathrm{cm}^{-2}$') 
+
+    n = 1.0e18
+    z = np.linspace(0,7,num=100)
+    f = vf_HM12(n, z)
+    ax.plot(z, np.log10(f), lw=2, c='b', label='$N_\mathrm{HI}=10^{20} \mathrm{cm}^{-2}$') 
     
+    n = 1.0e20
+    z = np.linspace(0,7,num=100)
+    f = vf_HM12(n, z)
+    ax.plot(z, np.log10(f), lw=2, c='r', label='$N_\mathrm{HI}=10^{20} \mathrm{cm}^{-2}$') 
+
+    n = 1.0e22
+    z = np.linspace(0,7,num=100)
+    f = vf_HM12(n, z)
+    ax.plot(z, np.log10(f), lw=2, c='brown', label='$N_\mathrm{HI}=10^{22} \mathrm{cm}^{-2}$') 
+    
+    plt.legend(loc='lower left', fontsize=12, handlelength=3,
+               frameon=False, framealpha=0.0, labelspacing=.1,
[…]

### 2017-07-06 Paper/paper.tex
Add photoionisation rate plot for two luminosity cutoffs
Update figures
Update text

@@
 \usepackage{siunitx}
+\def\lya{Ly$\alpha$~}
 
@@
 %% \end{enumerate}
+
+\section{Introduction}
+
+The luminosity function of active galactic nuclei (AGN) and its
+evolution over cosmological time scales has been a matter of central
+interest of a large body of work over the last four decades
+\citep[e.g.,][]{1978A&A....68...17M, 1983ApJ...269..352S,
+  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
+  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
+  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
+  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
+  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
+  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
+  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J,
+  2017MNRAS.466.1160M}.  Determination of the AGN luminosity function
+constrains models of the build-up of supermassive black holes
+\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the
+incidence of supermassive black holes in most galaxies, the tight
+scaling relations observed to exist between the mass of these black
+holes and properties of their host galaxies
+\citep{2013ARA&A..51..511K, 2013ApJ...764..184M}, and the increasing
+consensus that AGN activity feeds back on the host galaxy evolution,
+the AGN luminosity function also constrains models of galaxy
+formation.  Finally, thanks to their relative brightness and high
+Lyman continuum escape fraction, the luminosity function of AGN
+determines their influence on the temperature and ionization state of
+the intergalactic medium (IGM) over large scales, possibly even
+primarily driving hydrogen and helium reionization.
+
+The claimed discovery of 19 low-luminosity ($M_{1450}>-22.6$) AGN
+between redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G}
+using a novel X-ray/NIR selection criterion, has renewed the interest
+in the evolution of the UV luminosity function of AGN.  This finding
+suggested that the faint end of the quasar UV luminosity function is
+steeper at these redshifts than previously thought
+\citep{2007ApJ...654..731H, 2012ApJ...746..125H}.  Using far-UV
+spectral slopes from composite spectra of low-redshift quasars, and
+assuming a Lyman continuum escape fraction of 100\%,
+\citet{2015AA...578A..83G} argued that AGN brighter than
+$M_{1450}=-18$ can potentially produce all of the metagalactic
+hydrogen photoionization rate inferred from the \lya forest at
+$4<z<6$.  Additional indications of a significant presence of AGN at
+high redshift ($z\sim 6$) have emerged.  First,
+\citet{2015MNRAS.447.3402B} reported a large scatter in the \lya
+opacity between different sightlines close to redshift
+$z=6$. \cite{2015MNRAS.453.2943C} showed that these opacity
+fluctuations extend to substantially larger scales ($\gtrsim 50\,
+h^{-1}$cMpc) than expected in reionization histories dominated by
+low-luminosity galaxies (see also \citealt{2016MNRAS.460.1328D}).
+\citet{2017MNRAS.465.3429C} further demonstrated that opacity
+fluctuations on such large scales arise naturally if there is a
+significant contribution ($\gtrsim 50\%$) of AGN to the ionising
+emissivity at the redshift of the observed opacity fluctuations ($z
+\sim 5.5$--$6$) as would be expected for a QSO luminosity that is
+consistent with the measurements of \citet{2015AA...578A..83G}.
+Second, measurements of the Lyman continuum escape fraction from
+high-redshift galaxies are still elusive.  Although high-redshift
+galaxies as faint as rest-frame UV magnitude $M_\mathrm{UV}=-12.5$
+($L\sim 10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and
+redshifts as high as $z=11.1$ \citep{2016ApJ...819..129O} have now
+been reported, the escape of Lyman continuum photons has been detected
+in only a small number of comparatively bright ($L>0.5L^*$)
+low-redshift ($z < 4$) galaxies.  In these galaxies, the escape
+fraction is typically found to be 2--20\% \citep{2010ApJ...725.1011V,
+  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
+  2016A&A...585A..48G, 2017MNRAS.468..389J, 2017MNRAS.465..316M} but
+reionization would require escape fraction of about 20\% in galaxies
+down to $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
+  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  Finally, incidence of
+high-redshift AGN is also consistent with the shallow bright-end
+slopes of the high-redshift ($z\sim 7$) UV luminosity function of
+galaxies relative to a Schechter-function representation
+\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
+  2015MNRAS.452.1817B} and the hard spectra of these bright galaxies
+\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
+
+However, these arguements in favour of a higher incidence of
+UV-emitting AGN at high redshit, have been contested by several
+observations.  \citet{2016arXiv160706467D} considered the effect of
+AGN-dominated reionization on the Ly$\alpha$ opacity at $z>5$,
+He~\textsc{ii} Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the
+thermal history of the IGM.  In agreement with
+\citet{2015MNRAS.453.2943C}, these authors found that AGN did provide
+a plausible explanation for the large fluctuations in the Ly$\alpha$
+opacity at $z>5$.  However, they found that reionization of
+He~\textsc{ii} occurs much earlier in these AGN-dominated models (see
+also \citealt{2016arXiv160602719M}).  For instance, in the model of
+\citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
+at $z=4.5$, compared to $z=3$ in the standard scenario
+\citep{2012ApJ...746..125H}.  This early Helium reionization could
+result in higher IGM temperatures due to the associated photoheating.
+The temperature of the IGM at mean density is enhanced in
+AGN-dominated models by factors of $\sim 2$ relative to the standard
+models for $z=3.5$--$5$, in conflict with measurements.  This
+inconsistency could be avoided by reducing the escape fraction of 4~Ry
+photons in AGN, but it is not clear if this can be achieved while
+requiring a 100\% escape fraction of 1~Ry photons in order to explain
+the Ly$\alpha$ opacity fluctuations.  Further evidence against
+AGN-dominated reionization models has emerged from metal-line
+absorbers at $z\sim 6$.  In their cosmological radiation
+hydrodynamical simulations, \citet{2016MNRAS.459.2299F} find that the
+hard spectral slopes of UV backgrounds in AGN-only reionization models
+produce too many C~\textsc{iv} absorption systems relative to
+Si~\textsc{iv} and C~\textsc{ii} at $z\sim 6$.  However, these
+simulations assume an $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
+\citep{2001AJ....122..549V, 2002ApJ...579..500T, 2012ApJ...746..125H}.
+This slope is marginally harder than recent measurements
+($L_\nu\propto\nu^{-1.7}$) from a stack of $z\sim 2.4$ quasars
+\citep{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also find
+that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
+measurements prefer a somewhat harder and more intense $>4$~Ry
+background than the standard model of \citet{2012ApJ...746..125H}.
+Using a large sample of X-ray-selected quasars in the redshift range
+$z=0$--$6$, \citet{2017MNRAS.465.1915R} find that the faint end of the
+AGN UV luminosity function at $z\sim 6$ is likely to be much shallower
+that that reported by \citet{2015AA...578A..83G}.  In their analysis,
+\citet{2017MNRAS.465.1915R} use an AGN obscuration optical depth
+($\log N_\mathrm{H}$) cut-off that reproduces low-redshift AGN UV
+luminosity functions and an X-ray-to-optical/UV luminosity ratio
+calibrated at redshifts $z=0.05$--$4$ \citep{2010A&A...512A..34L}.
+These authors argue that the apparent contradiction with the results
+of \citet{2015AA...578A..83G} could be explained by contamination
+from the AGN host galaxies.  It has also been recently argued that the
+Lyman continuum escape fraction of AGN might not be 100\% as is
+usually assumed \citep{2017MNRAS.465..302M}.  This may further reduce
+the contribution of AGN to reionization.
+
+We assume a flat cosmology with density parameters
+$\left(\Omega_\mathrm{m},\Omega_\Lambda\right)=\left(0.3,0.7\right)$
+and a Hubble constant $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$. Magnitudes
+are reported in the AB system \citep{1983ApJ...266..713O}, and
+observed magnitudes are point spread function (PSF) magnitudes
+\citep{2002AJ....123..485S} corrected for Galactic extinction
+\citep{1998ApJ...500..525S} unless otherwise noted.
+
+\section{Homogenised Quasar Sample}
+
+\subsection{Sample Selection}
+
+We started with compiling the samples of recent UV-optical quasar
+surveys. The restriction to UV-optical surveys was mainly driven by
+our science goal to characterise the UV luminosity function of Type~I
+quasars, but also by the still uncertain conversion from X-ray flux to
+UV flux, which adds unnecessary systematics for large
+samples. \textbf{References!} The individual surveys and their main
+characteristics are listed in
+Table~\ref{tab:samples}. Figure~\ref{fig:qsos} presents a redshift
+histogram of the contributing surveys.
+
+We included surveys based on a set of simple criteria:
+\begin{enumerate}
+\item Spectroscopic redshifts for the majority of targets.
+\item Accurate rest-frame UV-optical CCD photometry.
+\item Statistical power (sample size, coverage in $z$ and/or $M_{1450}$).
+\item A characterised selection function.
+\end{enumerate}
+As a prerequisite for a joint analysis of the QLF we obtained the
+survey selection functions in electronic form, either from the
+publication or from the authors. As a reference for future surveys we
+publish them here in modified and homogenised form
+(Section~\ref{sect:datahom}). \textbf{Maybe get the authors' consent.}
+
+Due to their selection criteria and their statistical power specific
+surveys contribute to distinct redshift ranges. At $z<2.2$ we
+considered quasars from the SDSS DR7 quasar catalogue
+\citep{2010AJ....139.2360S} and the 2SLAQ catalogue
+\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to XXX
+$z<2.2$ quasars selected with the final SDSS quasar selection
+algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a
+survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We adopted
+the SDSS targeting photometry corrected for Galactic extinction
+\citep{2010AJ....139.2360S}. To limit systematic uncertainties in the
+correction for host galaxy light \citep{2009MNRAS.392...19C} we
+restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from
+its spectroscopic survey footprint near the North Galactic Pole (NGP,
+XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX
+quasars in $64.2$\,deg$^2$). The small sample overlap between SDSS and
+2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
+
+At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
+colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
+\citep{2013ApJ...773...14R} due to several improvements compared to
+previous surveys. First, it covers a similar magnitude range as 2SLAQ
+but with $>20$ times as many quasars. Second, although the SDSS DR7
+sample provides better coverage of the bright end of the QLF at these
+redshifts, its selection function is highly dependent on the assumed
+incidence of (partial) Lyman limit systems in the IGM
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
+selection function considers these improvements, the uncertainty in
+the QLF remains dominated by assumptions in the selection function
+given the large sample size
+\citep{2013ApJ...773...14R}. Variability-selected quasar samples
+circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
+  2016A&A...587A..41P}, but may be affected by (i) single-epoch
+imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
+and (ii) uncertainties in the selection function caused by the limited
+number of known $z\ga 3$ quasars not selected by variability in the
+same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
+
+At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly
+  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
+survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
+$z>3.7$ limits the impact of systematic uncertainties in the
+\citet{2006AJ....131.2766R} SDSS selection function
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
+the results from surveys for faint $z\sim 4$ quasars in the COSMOS
+field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
+systematic errors in their selection functions\footnote{Both studies
+  simulated quasar colours with a mean IGM attenuation curve
+  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
+  continuum absorption, and therefore underpredicts the variance in
+  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
+    2011ApJ...728...23W}. Modelling the colour variance in these
+  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
+  quasars are near the edge of their colour selection region (see
+  their Figure~1), and \citet{2012ApJ...755..169M} require modest
+  attenuation of the $U$ band flux relative to the mid-infrared
+  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
+COSMOS sample have visually estimated photometric redshifts, and the
+spectroscopic subsample reveals that 40 per cent of the visually
+estimated redshifts are biased low
+($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
+unaccounted systematic redshift errors at least partly explain the
+discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
+and \citet{2012ApJ...755..169M}, which justifies our preference for
+the former sample.
+
+Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly
+selected quasars from the SDSS DR7 quasar catalogue
+\citep{2010AJ....139.2360S} and XX quasars from
+\citet{2011ApJ...728L..26G}. Although we do not include the highly
+debated \citet{2015AA...578A..83G} sample in our main analysis due to
+its rough selection function and lacking spectroscopy for 17 of the 22
+quasar candidates, we use it in Section~XX to constrain the faint end
+($M_{1450}>-23$) of the QLF at $z>4.1$. We restricted the
+\citet{2015AA...578A..83G} sample to the 19/22 sources considered in
+their QLF.
+
+At $4.7\le z<5.1$ we combined several recent surveys, accounting for
+sample overlap and updated selection functions. At the bright end of
+the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey
+\citep{2016ApJ...829...33Y} together with its selection function.
+%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit
+%their sample to $z<5.1$ to limit differential evolution of the QLF
+%across the redshift range.
+To avoid double-counting quasars contained both in
+\citet{2016ApJ...829...33Y} and the SDSS DR7 sample from
+\citet{2013ApJ...768..105M}, we used the latter only at
+$M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional
+$4.7\le z<5.1$ quasars selected in 6248\,deg$^2$. We used the updated
+$z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M}
+instead of the one from \citet{2006AJ....131.2766R}.
+%\footnote{We note that the major difference in the selection
+%functions must be due to different input parameters, since the single
+%color selection criterion in \citet{mcgreer} selects the vast
+%majority of the SDSS DR7 quasars.}.
+To these two bright-end samples we added the faint-end sample from the
+\citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly
+selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from
+\citet{2011ApJ...728L..26G}, adopting the respective selection
+functions. We did not consider the limit on the $z\sim 5$ QLF by
+\citet{2012ApJ...756..160I} due to systematic errors in their
+selection function\footnote{\citet{2012ApJ...756..160I} underestimated
+  the dispersion in rest-frame UV quasar colours with respect to SDSS
+  at all redshifts (their Figure~4). Contrary to their claim,
+  photometric errors have a small effect on the colour distribution of
+  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
+  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
+  a relative calibration error of $\sim 1$ per cent
+  \citep{2008ApJ...674.1217P}.}.
+
+The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M
+and L dwarf stars, resulting in a low and uncertain selection
+efficiency \citep{2013ApJ...768..105M}. WISE mid-infrared selection
+performs better \citep{2016ApJ...829...33Y}, but is restricted to the
+bright end of the quasar population. Our combined sample contains the
+remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars
+from the \citet{2013ApJ...768..105M} Stripe~82 survey. As we will show
+in Section~XX, the resulting QLF is consistent with those at lower and
+higher redshifts, indicating that the \citet{2013ApJ...768..105M}
+selection functions are quite reliable. \textbf{Check this!}
+
+Finally, we combined the samples from all spectroscopic $z\sim 6$
+quasar surveys with a determined selection function as of June
+2017. \citet{2016ApJ...833..222J} recently compiled all quasars
+discovered in several SDSS $z\sim 6$ surveys together with
+consistently derived selection functions. Their uniform sample
+consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10
+additional quasars in regions with two or more SDSS imaging scans
+(so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from
+SDSS Stripe~82 (277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W}
+provided a uniform sample of 16 quasars in the Very Wide Survey
+(494\,deg$^2$) and a single quasar in the Deep Survey
+($4.47$\,deg$^2$). The one quasar detected in both SDSS and CFHQS does
+not lead to underestimated statistical errors in the QLF. Lastly, we
+included the two objects from \citet{2015ApJ...798...28K}. One might
+be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line
+(half width at half maximum 427\,km\,s$^{-1}$), but
+\citet{2015ApJ...798...28K} note that 10/17 candidates do not have
+follow-up spectroscopy, hence their QLF may be underestimated. Since
+very small samples preclude a statistical correction via the selection
+function, complete spectroscopic follow-up of $z\sim 6$ candidates is
+essential. Although we will account for the slightly different
+redshift sensitivities for the different surveys, we will quote a
+nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{qsos.pdf}
+  \end{center}
+  \caption{Quasar samples.}
+  \label{fig:qsos}
+\end{figure*}
+
+\begin{table*}
+  % In published version of this table, we could remove file names and add data homogenisation in Notes.
+  % Add z ~ 7 qso when you add it to analysis
+  % See data.tex for a version of this table that includes file names
+  \caption{Quasar data sets}
+  \label{tab:samples}
+  \begin{tabular}{crcllrSl}
+    \hline
+    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
+    & & & & & of quasars & {(deg$^2$)} & \\
+    \hline
+    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
+    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
+    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
+    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
+    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
+    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
+    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
+    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
+    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
+    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
+    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
+    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
+    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
+    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
+    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
+    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
+    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
+    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
+    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
+  \end{tabular}
+\end{table*}
+
+%\clearpage
+\subsection{Sample Homogenisation}
+\label{sect:datahom}
+
+For a joint fit of the QLF it is necessary to homogenise the different
+survey samples in absolute magnitude, and to convert their selection
+functions to the same absolute magnitude system. For the analysis of
+the quasar UV emissivity and to be consistent with published work at
+$z>3$ we chose to convert all samples and selection functions to the
+absolute AB magnitude at a rest frame wavelength $\lambda=1450$\,\AA
+\begin{equation}\label{eq:absmag}
+M_{1450}\left(z\right) = m-5\log{\left(\frac{d_L\left(z\right)}{\mathrm{Mpc}}\right)}-25-K_{m,1450}\left(z\right),
+\end{equation}
+with the luminosity distance $d_L\left(z\right)$ to a quasar at
+redshift $z$, the apparent magnitude $m$ in a filter used in the
+survey, and the bandpass correction $K_{m,1450}\left(z\right)$
+\citep{1956AJ.....61...97H, 1968ApJ...154...21O, 2000A&A...353..861W,
+  2002astro.ph.10394H}. For the bandpass correction we used a
+combination of the \citet{2015MNRAS.449.4204L} quasar SED at
+$\lambda<2500$\,\AA, and the \citet{2001AJ....122..549V} quasar
+composite spectrum at longer wavelengths to cover the lowest
+redshifts.  The samples from SDSS and BOSS are defined in the SDSS $i$
+band, while 2SLAQ is defined in the $g$ band. At $z>4.7$ we adopted
+the SDSS $z$ band magnitude (in the following denoted $z_\mathrm{AB}$)
+for SDSS DR7 quasars to avoid additional corrections due to the
+Ly$\alpha$ forest. Figure~XX shows our bandpass corrections for SDSS,
+BOSS and 2SLAQ as a function of redshift. While the
+\citet{2015MNRAS.449.4204L} SED is for bright ($M_{1450}\simeq -27.2$)
+quasars, UV composite spectra including fainter quasars
+\citep{2002ApJ...565..773T, 2012ApJ...752..162S, 2014ApJ...794...75S}
+give similar values, such that our bandpass corrections likely remain
+applicable at $M_{1450}\la -24$. \textbf{What about even fainter AGN?}
+
+For the $z<2.2$ sample we corrected the SDSS $i$ and 2SLAQ $g$ band
+magnitudes for host galaxy contamination following
+\citet{2009MNRAS.392...19C}. Considering the different magnitude
+limits of 2SLAQ and SDSS, the modelled host galaxy contamination is
+small for $z>0.5$ quasars ($<0.1$\,mag in $g$, $<0.2$\,mag in $i$),
+and is negligible at $z>0.8$.  In case the band defining the magnitude
+limit of the survey undesirably overlaps with the Ly$\alpha$ forest
+\citep{2010ApJ...710.1498G, 2011ApJ...728L..26G, 2013ApJ...768..105M}
+we adopted their respective bandpass corrections to $M_{1450}$. In
+particular, for the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G}
+sample we recomputed $M_{1450}$ from the $R$ band photometry to be
+consistent with the selection function defined in $R$, and to avoid
+uncertainties in their spectrophotometry due to incomplete spectral
+coverage. For the remaining high-redshift surveys reporting $M_{1450}$
+obtained by various methods \citep{2010AJ....139..906W,
+  2015ApJ...798...28K, 2015AA...578A..83G, 2016ApJ...829...33Y,
+  2016ApJ...833..222J} we did not re-compute $M_{1450}$, but applied
+appropriate shifts to correct to our adopted cosmology.
+
+The selection functions were treated similarly, i.e.\ the photometric
+selection function of survey $j$ given in observed magnitudes
+$f_{\mathrm{p},j}\left(m,z\right)$ \citep{2006AJ....131.2766R,
+  2009MNRAS.392...19C, 2010ApJ...710.1498G, 2013ApJ...773...14R} was
+transformed to our absolute magnitudes
+$f_{\mathrm{p},j}\left(M_{1450},z\right)$ with
+Equation~\ref{eq:absmag}, while the ones given in $M_{1450}$ were
+adjusted to our cosmology. Note, however, that many surveys report
+additional sources of incompleteness that preclude a straightforward
+re-evaluation of the QLF.
+
+For 2SLAQ we corrected for magnitude-dependent spectroscopic coverage
+in the two survey areas \citep[$f_\mathrm{c,NGP}\left(g\right)$ and
+  $f_\mathrm{c,SGP}\left(g\right)$; Figure~4
+  in][]{2009MNRAS.392...19C} and spectroscopic redshift success
+\citep[$f_\mathrm{s,2SLAQ}\left(g\right)$; Figure~6b
+  in][]{2009MNRAS.392...19C} by multiplying them with the photometric
+selection function, resulting in two area-specific 2SLAQ selection
+functions
+$f_\mathrm{NGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,NGP}f_\mathrm{s,2SLAQ}$
+and
+$f_\mathrm{SGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,SGP}f_\mathrm{s,2SLAQ}$
+that are relevant for the QLF.  The $z<4.7$ SDSS photometric selection
+function was modified to include known imaging incompleteness to
+$f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
+\citep{2006AJ....131.2766R}. The BOSS colour-selected sample contains
+quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$
+\citep{2013ApJ...773...14R}, and we adopted
+$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
+presented two area-specific photometric selection functions due to
+different filters employed, and more follow-up spectroscopy was
+reported in \citet{2011ApJ...728L..26G}. We accounted for remaining
+spectroscopic incompleteness at $R>23$, yielding the final selection
+functions $f_\mathrm{NDWFS}$ and $f_\mathrm{DLS}$. The updated $z\sim
+5$ SDSS photometric selection function \citep{2013ApJ...768..105M} was
+modified to include imaging and spectroscopic incompleteness, yielding
+$f_{\mathrm{SDSS},z\sim 5}=0.95^2f_{\mathrm{p,SDSS},z\sim 5}$. In the
+deeper $z\sim 5$ SDSS Stripe~82 survey the spectroscopic
+incompleteness is larger and magnitude-dependent \citep[Figure~14
+  in][]{2013ApJ...768..105M}, resulting in $f_{\mathrm{S82},z\sim
+  5}=0.95f_{\mathrm{s,S82},z\sim
+  5}\left(i\right)f_{\mathrm{p,S82},z\sim 5}$. Likewise, imaging and
+magnitude-dependent spectroscopic incompleteness was factored into the
+\citet{2016ApJ...829...33Y} photometric selection function (their
+Figures~5 and 7), resulting in
+$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$. Finally,
+we obtained a rough estimate of the \citet{2015AA...578A..83G}
+selection function by taking
+$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
+Table~3).
+
+% BOSS:
+% - color selection function in Table 5 of Ross et al.
+(imag, z), sample contains QSOs with spectrocoverage completeness >0.85, mean spectrocoverage completeness 0.962 multiplied onto color selection function
+% - interpolate Beta's K correction (imag->1450A) and compute M1450 for our cosmology (sample and map)
+
+% 2SLAQ:
+% - low-luminosity AGN -> model and subtract host galaxy contribution, magnitudes only for nuclear component, host galaxy contribution <20% at z>0.4 for faintest sources in 2SLAQ (Croom et al.
+2009, MNRAS, 392, 19)
+% - several selection functions (morphological, color, spectroscopic coverage, spectroscopic success)
+% - Table 12: color selection function (available online), gmag is total PSF mag including host galaxy contribution, subtract gmag host galaxy contribution listed in Table 12, selection function extrapolated at bright end (lacking coverage of whole catalog)
+% - coverage completeness for NGP and SGP given in Fig 4 as a function of gmag, interpolated and multiplied into color selection function
+% - spectroscopic success as function of gmag in Fig 6b (only quality=1 redshifts considered), interpolated and multiplied onto color selection function
+% - convert g_agn to M1450 with L15 SED (valid for bright quasars, check with K correction for Telfer/Shull)
+% - sample: correct PSF gmag for Galactic extinction, subtract host galaxy light (Table 12), interpolate Beta's K correction (gmag->1450A) and compute M1450 for our cosmology
+% SDSS:
+% - Richards et al.
+selection function given in (z,imag) Fig 6 and Table 1, corrected for edge effects at magnitude limits (steep gradient) and NaN values, selection function corrected for imaging incompleteness (factor 0.95)
+% - imag in selection function converted to M1450 with L15 SED, conversion uncertain at z>4.7 due to Lya forest
+% - sample: targeting psf imag corrected for Galactic extinction (Schlegel) and converted to M1450 with L15 SED
+% - z<2.2: sample limited to i_dered<19.1, imag of sample and selection function corrected for host galaxy light (Table 12 in Croom et al 2009, given for imag and gmag)
+% Glikman:
+% - different selection functions for 2 sub-surveys, selection functions corrected for interpolation errors (values >1 reset to 1), selection functions given in (z,Rmag) Fig 7 of G10, converted to M1450 with their Rmag K correction (Fig 8 in G10)
+% - spectroscopic incompleteness (f_spec, given in G10 and updated in G11) incorporated into selection functions via linear fit to f_spec(Rmag) at Rmag>23 and constant otherwise
+% - sample M1450 recomputed from Rmag and K correction to be consistent with completeness map, M1450=Rmag-Kcorr-5*log10(d_L/Mpc)-25
+% McGreer:
+% - Stripe 82: selection function (Fig.
+11) modified to include photometric incompleteness (factor 0.95) and spectroscopic incompleteness (imag>20.8, Fig.
+14), M1450 in selection map and sample M1450 converted to our cosmology (adding 0.07)
+% - DR7: sample not listed in paper, M1450 computed from zmag (QSO continuum) and L15 SED, same procedure applied to S82 reveals L15 magnitudes are slightly brighter than M13 magnitudes (median 0.12mag) -> small change,
+%        M13 selection function corrected for photometric (factor 0.95) and spectroscopic (factor 0.95) incompleteness
+% Yang: selection function (Fig.
+5) modified to include image selection incompleteness (factor 0.97) and spectroscopic incompleteness (factor ~0.84 at zmag>19, Fig 7), M1450 in selection map and sample M1450 converted to our cosmology
+% Willott: selection map M1450 adjusted to our cosmology adding 0.05, slightly different cosmological parameters in Willott et al. (2007,2009,2010) -> M1450 converted
+% Jiang: selection functions unchanged, M1450 as given in paper
+% Kashikawa: map not corrected for spectroscopic incompleteness (sample size), M1450 as given in paper
+% Giallongo: selection function estimated from phi_obs and phi_corr (Table 3 of Giallongo et al.), M1450 as given in paper
 
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{qsos.pdf}
-  \end{center}
-  \caption{Quasar samples.}
-  \label{fig:qsos}
-\end{figure*}
-
-\begin{table*}
-  % In published version of this table, we could remove file names and add data homogenisation in Notes.
-  % Add z ~ 7 qso when you add it to analysis
-  % See data.tex for a version of this table that includes file names
-  \caption{Quasar data sets}
-  \label{tab:samples}
-  \begin{tabular}{crcllrSl}
-    \hline
-    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
-    & & & & & of quasars & {(deg$^2$)} & \\
-    \hline
-    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
-    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
-    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
-    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
-    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
-    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
-    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
-    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
-    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
-    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
-    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
-    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
-    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
-    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
-    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
-    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
-    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
-    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
-    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
-  \end{tabular}
-\end{table*}
-
-\begin{figure*}
-  \begin{center}
     \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
@@
     in the left panel and $-20$ in the right panel.}
-  \label{fig:gammapi}
+  \label{fig:emissivity}
 \end{figure*}
@@
   \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{gammapi.pdf}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{g_18.pdf}
+    \includegraphics[width=0.5\textwidth]{g_20.pdf}
+    \end{tabular}
   \end{center}
-  \caption{Hydrogen photoionization rate}
+  \caption{AGN contribution to the hydrogen photoionisation rate,
+    assuming 100\% escape fraction.  Model luminosity functions are
+    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
+    the right panel.}
   \label{fig:gammapi}

### 2017-07-10 Paper/paper.tex
Update text

@@
 
-We started with compiling the samples of recent UV-optical quasar
-surveys. The restriction to UV-optical surveys was mainly driven by
-our science goal to characterise the UV luminosity function of Type~I
-quasars, but also by the still uncertain conversion from X-ray flux to
-UV flux, which adds unnecessary systematics for large
-samples. \textbf{References!} The individual surveys and their main
-characteristics are listed in
-Table~\ref{tab:samples}. Figure~\ref{fig:qsos} presents a redshift
-histogram of the contributing surveys.
+We started with compiling the samples of recent UV-optical quasar surveys.
+The restriction to UV-optical surveys was mainly driven by our science goal to characterise the UV luminosity function of Type~I quasars, but also by the still uncertain conversion from X-ray flux to UV flux, which adds unnecessary systematics for large samples.
+\textbf{References!} The individual surveys and their main characteristics are listed in Table~\ref{tab:samples}.
+Figure~\ref{fig:qsos} presents a redshift histogram of the contributing surveys.
 
@@
 \end{enumerate}
-As a prerequisite for a joint analysis of the QLF we obtained the
-survey selection functions in electronic form, either from the
-publication or from the authors. As a reference for future surveys we
-publish them here in modified and homogenised form
-(Section~\ref{sect:datahom}). \textbf{Maybe get the authors' consent.}
+As a prerequisite for a joint analysis of the QLF we obtained the survey selection functions in electronic form, either from the publication or from the authors.
+As a reference for future surveys we publish them here in modified and homogenised form (Section~\ref{sect:datahom}).
+\textbf{Maybe get the authors' consent.}
 
-Due to their selection criteria and their statistical power specific
-surveys contribute to distinct redshift ranges. At $z<2.2$ we
-considered quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and the 2SLAQ catalogue
-\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to XXX
-$z<2.2$ quasars selected with the final SDSS quasar selection
-algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a
-survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We adopted
-the SDSS targeting photometry corrected for Galactic extinction
-\citep{2010AJ....139.2360S}. To limit systematic uncertainties in the
-correction for host galaxy light \citep{2009MNRAS.392...19C} we
-restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from
-its spectroscopic survey footprint near the North Galactic Pole (NGP,
-XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX
-quasars in $64.2$\,deg$^2$). The small sample overlap between SDSS and
-2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
+Due to their selection criteria and their statistical power specific surveys contribute to distinct redshift ranges.
+At $z<2.2$ we considered quasars from the SDSS DR7 quasar catalogue \citep{2010AJ....139.2360S} and the 2SLAQ catalogue \citep{2009MNRAS.392...19C}.
+We restricted the SDSS DR7 sample to XXX $z<2.2$ quasars selected with the final SDSS quasar selection algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}.
+We adopted the SDSS targeting photometry corrected for Galactic extinction \citep{2010AJ....139.2360S}.
+To limit systematic uncertainties in the correction for host galaxy light \citep{2009MNRAS.392...19C} we restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint near the North Galactic Pole (NGP, XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX quasars in $64.2$\,deg$^2$).
+The small sample overlap between SDSS and 2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
 
-At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
-colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
-\citep{2013ApJ...773...14R} due to several improvements compared to
-previous surveys. First, it covers a similar magnitude range as 2SLAQ
-but with $>20$ times as many quasars. Second, although the SDSS DR7
-sample provides better coverage of the bright end of the QLF at these
-redshifts, its selection function is highly dependent on the assumed
-incidence of (partial) Lyman limit systems in the IGM
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
-selection function considers these improvements, the uncertainty in
-the QLF remains dominated by assumptions in the selection function
-given the large sample size
-\citep{2013ApJ...773...14R}. Variability-selected quasar samples
-circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
-  2016A&A...587A..41P}, but may be affected by (i) single-epoch
-imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
-and (ii) uncertainties in the selection function caused by the limited
-number of known $z\ga 3$ quasars not selected by variability in the
-same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
+At $2.2<z<3.5$ we used a single sample of 23,301 uniformly colour-selected quasars from 2236\,deg$^2$ in BOSS DR9 \citep{2013ApJ...773...14R} due to several improvements compared to previous surveys.
+First, it covers a similar magnitude range as 2SLAQ but with $>20$ times as many quasars.
+Second, although the SDSS DR7 sample provides better coverage of the bright end of the QLF at these redshifts, its selection function is highly dependent on the assumed incidence of (partial) Lyman limit systems in the IGM \citep{2009ApJ...705L.113P, 2011ApJ...728...23W}.
+While the BOSS DR9 selection function considers these improvements, the uncertainty in the QLF remains dominated by assumptions in the selection function given the large sample size \citep{2013ApJ...773...14R}.
+Variability-selected quasar samples circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P, 2016A&A...587A..41P}, but may be affected by (i) single-epoch imaging incompleteness at the faint end \citep{2013ApJ...773...14R}, and (ii) uncertainties in the selection function caused by the limited number of known $z\ga 3$ quasars not selected by variability in the same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
 
-At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly
-  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
-survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
-$z>3.7$ limits the impact of systematic uncertainties in the
-\citet{2006AJ....131.2766R} SDSS selection function
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
-the results from surveys for faint $z\sim 4$ quasars in the COSMOS
-field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
-systematic errors in their selection functions\footnote{Both studies
-  simulated quasar colours with a mean IGM attenuation curve
-  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
-  continuum absorption, and therefore underpredicts the variance in
-  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
-    2011ApJ...728...23W}. Modelling the colour variance in these
-  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
-  quasars are near the edge of their colour selection region (see
-  their Figure~1), and \citet{2012ApJ...755..169M} require modest
-  attenuation of the $U$ band flux relative to the mid-infrared
-  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
-COSMOS sample have visually estimated photometric redshifts, and the
-spectroscopic subsample reveals that 40 per cent of the visually
-estimated redshifts are biased low
-($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
-unaccounted systematic redshift errors at least partly explain the
-discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
-and \citet{2012ApJ...755..169M}, which justifies our preference for
-the former sample.
+At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}.
+The lower cut $z>3.7$ limits the impact of systematic uncertainties in the \citet{2006AJ....131.2766R} SDSS selection function \citep{2009ApJ...705L.113P, 2011ApJ...728...23W}.
+We did not consider the results from surveys for faint $z\sim 4$ quasars in the COSMOS field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to systematic errors in their selection functions\footnote{Both studies simulated quasar colours with a mean IGM attenuation curve \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman continuum absorption, and therefore underpredicts the variance in quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I, 2011ApJ...728...23W}.
+Modelling the colour variance in these surveys is essential, as most of the \citet{2011ApJ...728L..25I} quasars are near the edge of their colour selection region (see their Figure~1), and \citet{2012ApJ...755..169M} require modest attenuation of the $U$ band flux relative to the mid-infrared flux.}.
+Furthermore, 30 per cent of the \citet{2012ApJ...755..169M} COSMOS sample have visually estimated photometric redshifts, and the spectroscopic subsample reveals that 40 per cent of the visually estimated redshifts are biased low ($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9).
+These unaccounted systematic redshift errors at least partly explain the discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G} and \citet{2012ApJ...755..169M}, which justifies our preference for the former sample.
 
-Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly
-selected quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and XX quasars from
-\citet{2011ApJ...728L..26G}. Although we do not include the highly
-debated \citet{2015AA...578A..83G} sample in our main analysis due to
-its rough selection function and lacking spectroscopy for 17 of the 22
-quasar candidates, we use it in Section~XX to constrain the faint end
-($M_{1450}>-23$) of the QLF at $z>4.1$. We restricted the
-\citet{2015AA...578A..83G} sample to the 19/22 sources considered in
-their QLF.
+Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly selected quasars from the SDSS DR7 quasar catalogue \citep{2010AJ....139.2360S} and XX quasars from \citet{2011ApJ...728L..26G}.
+Although we do not include the highly debated \citet{2015AA...578A..83G} sample in our main analysis due to its rough selection function and lacking spectroscopy for 17 of the 22 quasar candidates, we use it in Section~XX to constrain the faint end ($M_{1450}>-23$) of the QLF at $z>4.1$.
+We restricted the \citet{2015AA...578A..83G} sample to the 19/22 sources considered in their QLF.
 
-At $4.7\le z<5.1$ we combined several recent surveys, accounting for
-sample overlap and updated selection functions. At the bright end of
-the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} together with its selection function.
-%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit
-%their sample to $z<5.1$ to limit differential evolution of the QLF
-%across the redshift range.
-To avoid double-counting quasars contained both in
-\citet{2016ApJ...829...33Y} and the SDSS DR7 sample from
-\citet{2013ApJ...768..105M}, we used the latter only at
-$M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional
-$4.7\le z<5.1$ quasars selected in 6248\,deg$^2$. We used the updated
-$z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M}
-instead of the one from \citet{2006AJ....131.2766R}.
-%\footnote{We note that the major difference in the selection
-%functions must be due to different input parameters, since the single
-%color selection criterion in \citet{mcgreer} selects the vast
-%majority of the SDSS DR7 quasars.}.
-To these two bright-end samples we added the faint-end sample from the
-\citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly
-selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from
-\citet{2011ApJ...728L..26G}, adopting the respective selection
-functions. We did not consider the limit on the $z\sim 5$ QLF by
-\citet{2012ApJ...756..160I} due to systematic errors in their
-selection function\footnote{\citet{2012ApJ...756..160I} underestimated
-  the dispersion in rest-frame UV quasar colours with respect to SDSS
-  at all redshifts (their Figure~4). Contrary to their claim,
-  photometric errors have a small effect on the colour distribution of
-  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
-  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
-  a relative calibration error of $\sim 1$ per cent
-  \citep{2008ApJ...674.1217P}.}.
+At $4.7\le z<5.1$ we combined several recent surveys, accounting for sample overlap and updated selection functions.
+At the bright end of the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey \citep{2016ApJ...829...33Y} together with its selection function.
+%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit their sample to $z<5.1$ to limit differential evolution of the QLF across the redshift range.
+To avoid double-counting quasars contained both in \citet{2016ApJ...829...33Y} and the SDSS DR7 sample from \citet{2013ApJ...768..105M}, we used the latter only at $M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional $4.7\le z<5.1$ quasars selected in 6248\,deg$^2$.
+We used the updated $z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M} instead of the one from \citet{2006AJ....131.2766R}.
+%\footnote{We note that the major difference in the selection functions must be due to different input parameters, since the single color selection criterion in \citet{mcgreer} selects the vast majority of the SDSS DR7 quasars.}.
+To these two bright-end samples we added the faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from \citet{2011ApJ...728L..26G}, adopting the respective selection functions.
+We did not consider the limit on the $z\sim 5$ QLF by \citet{2012ApJ...756..160I} due to systematic errors in their selection function\footnote{\citet{2012ApJ...756..160I} underestimated the dispersion in rest-frame UV quasar colours with respect to SDSS at all redshifts (their Figure~4).
+Contrary to their claim, photometric errors have a small effect on the colour distribution of SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$ for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and a relative calibration error of $\sim 1$ per cent \citep{2008ApJ...674.1217P}.}.
 
-The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M
-and L dwarf stars, resulting in a low and uncertain selection
-efficiency \citep{2013ApJ...768..105M}. WISE mid-infrared selection
-performs better \citep{2016ApJ...829...33Y}, but is restricted to the
-bright end of the quasar population. Our combined sample contains the
-remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars
-from the \citet{2013ApJ...768..105M} Stripe~82 survey. As we will show
-in Section~XX, the resulting QLF is consistent with those at lower and
-higher redshifts, indicating that the \citet{2013ApJ...768..105M}
-selection functions are quite reliable. \textbf{Check this!}
+The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M and L dwarf stars, resulting in a low and uncertain selection efficiency \citep{2013ApJ...768..105M}.
+WISE mid-infrared selection performs better \citep{2016ApJ...829...33Y}, but is restricted to the bright end of the quasar population.
+Our combined sample contains the remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars from the \citet{2013ApJ...768..105M} Stripe~82 survey.
+As we will show in Section~XX, the resulting QLF is consistent with those at lower and higher redshifts, indicating that the \citet{2013ApJ...768..105M} selection functions are quite reliable.
+\textbf{Check this!}
 
-Finally, we combined the samples from all spectroscopic $z\sim 6$
-quasar surveys with a determined selection function as of June
-2017. \citet{2016ApJ...833..222J} recently compiled all quasars
-discovered in several SDSS $z\sim 6$ surveys together with
-consistently derived selection functions. Their uniform sample
-consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10
-additional quasars in regions with two or more SDSS imaging scans
-(so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from
-SDSS Stripe~82 (277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W}
-provided a uniform sample of 16 quasars in the Very Wide Survey
-(494\,deg$^2$) and a single quasar in the Deep Survey
-($4.47$\,deg$^2$). The one quasar detected in both SDSS and CFHQS does
-not lead to underestimated statistical errors in the QLF. Lastly, we
-included the two objects from \citet{2015ApJ...798...28K}. One might
-be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line
-(half width at half maximum 427\,km\,s$^{-1}$), but
-\citet{2015ApJ...798...28K} note that 10/17 candidates do not have
-follow-up spectroscopy, hence their QLF may be underestimated. Since
-very small samples preclude a statistical correction via the selection
-function, complete spectroscopic follow-up of $z\sim 6$ candidates is
-essential. Although we will account for the slightly different
-redshift sensitivities for the different surveys, we will quote a
-nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
+Finally, we combined the samples from all spectroscopic $z\sim 6$ quasar surveys with a determined selection function as of June 2017.
+\citet{2016ApJ...833..222J} recently compiled all quasars discovered in several SDSS $z\sim 6$ surveys together with consistently derived selection functions.
+Their uniform sample consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10 additional quasars in regions with two or more SDSS imaging scans (so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from SDSS Stripe~82 (277\,deg$^2$).
+The CFHQS \citep{2010AJ....139..906W} provided a uniform sample of 16 quasars in the Very Wide Survey (494\,deg$^2$) and a single quasar in the Deep Survey ($4.47$\,deg$^2$).
+The one quasar detected in both SDSS and CFHQS does not lead to underestimated statistical errors in the QLF.
+Lastly, we included the two objects from \citet{2015ApJ...798...28K}.
+One might be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line (half width at half maximum 427\,km\,s$^{-1}$), but \citet{2015ApJ...798...28K} note that 10/17 candidates do not have follow-up spectroscopy, hence their QLF may be underestimated.
+Since very small samples preclude a statistical correction via the selection function, complete spectroscopic follow-up of $z\sim 6$ candidates is essential.
+Although we will account for the slightly different redshift sensitivities for the different surveys, we will quote a nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
 
@@
 
-For a joint fit of the QLF it is necessary to homogenise the different
-survey samples in absolute magnitude, and to convert their selection
-functions to the same absolute magnitude system. For the analysis of
-the quasar UV emissivity and to be consistent with published work at
-$z>3$ we chose to convert all samples and selection functions to the
-absolute AB magnitude at a rest frame wavelength $\lambda=1450$\,\AA
+\begin{figure}
+    \includegraphics[width=\columnwidth]{kcorr.pdf}
+  \caption{Bandpass corrections $K_{m,1450}$ from a broadband magnitude $m=\{g,i,z_\mathrm{AB}\}$
+           to the monochromatic AB magnitude at 1450\,\AA\ as a function of redshift $z$ for the \citet{2015MNRAS.449.4204L}
+           quasar SED used in this work, and for two quasar composite spectra \citep{2001AJ....122..549V, 2002ApJ...565..773T}.
+           The redshift range has been restricted to exclude the Ly$\alpha$ forest and to account for the different
+           rest frame wavelength coverage of the spectra.}
+  \label{fig:kcorr}
+\end{figure}
+
+For a joint fit of the QLF it is necessary to homogenise the different survey samples in absolute magnitude, and to convert their selection functions to the same absolute magnitude system.
+For the analysis of the quasar UV emissivity and to be consistent with published work at $z>3$ we chose to convert all samples and selection functions to the absolute AB magnitude at a rest frame wavelength $\lambda=1450$\,\AA
 \begin{equation}\label{eq:absmag}
@@
 \end{equation}
-with the luminosity distance $d_L\left(z\right)$ to a quasar at
-redshift $z$, the apparent magnitude $m$ in a filter used in the
-survey, and the bandpass correction $K_{m,1450}\left(z\right)$
-\citep{1956AJ.....61...97H, 1968ApJ...154...21O, 2000A&A...353..861W,
-  2002astro.ph.10394H}. For the bandpass correction we used a
-combination of the \citet{2015MNRAS.449.4204L} quasar SED at
-$\lambda<2500$\,\AA, and the \citet{2001AJ....122..549V} quasar
-composite spectrum at longer wavelengths to cover the lowest
-redshifts.  The samples from SDSS and BOSS are defined in the SDSS $i$
-band, while 2SLAQ is defined in the $g$ band. At $z>4.7$ we adopted
-the SDSS $z$ band magnitude (in the following denoted $z_\mathrm{AB}$)
-for SDSS DR7 quasars to avoid additional corrections due to the
-Ly$\alpha$ forest. Figure~XX shows our bandpass corrections for SDSS,
-BOSS and 2SLAQ as a function of redshift. While the
-\citet{2015MNRAS.449.4204L} SED is for bright ($M_{1450}\simeq -27.2$)
-quasars, UV composite spectra including fainter quasars
-\citep{2002ApJ...565..773T, 2012ApJ...752..162S, 2014ApJ...794...75S}
-give similar values, such that our bandpass corrections likely remain
-applicable at $M_{1450}\la -24$. \textbf{What about even fainter AGN?}
+with the luminosity distance $d_L\left(z\right)$ to a quasar at redshift $z$, the apparent magnitude $m$ in a filter used in the survey, and the bandpass correction $K_{m,1450}\left(z\right)$ \citep{1956AJ.....61...97H, 1968ApJ...154...21O, 2000A&A...353..861W, 2002astro.ph.10394H}.
+For the bandpass correction we used a combination of the \citet{2015MNRAS.449.4204L} quasar SED at $\lambda<2500$\,\AA, and the \citet{2001AJ....122..549V} quasar composite spectrum at longer wavelengths to cover the lowest redshifts.
+The samples from SDSS and BOSS are defined in the SDSS $i$ band, while 2SLAQ is defined in the $g$ band.
+At $z>4.7$ we adopted the SDSS $z$ band magnitude (in the following denoted $z_\mathrm{AB}$) for SDSS DR7 quasars to avoid additional corrections due to the Ly$\alpha$ forest.
+Figure~\ref{fig:kcorr} shows our bandpass corrections for SDSS, BOSS and 2SLAQ as a function of redshift.
+We ignored the luminosity dependence of the bandpass correction due to the known anticorrelation of emission line equivalent width and luminosity \citep{1977ApJ...214..679B}.
+While the \citet{2015MNRAS.449.4204L} SED is for luminous ($M_{1450}\simeq -27.2$) quasars, UV composite spectra including fainter quasars \citep{2002ApJ...565..773T, 2012ApJ...752..162S, 2014ApJ...794...75S} give similar values, such that our bandpass corrections remain applicable at $M_{1450}\la -24$.
+Empirical luminosity-dependent bandpass corrections show a $\la 0.2$\,mag variation over $\sim 4$ orders of absolute magnitude depending on redshift and the filter, and with a $\sim 0.2$\,mag intrinsic scatter due to individual SED variations \citep{2013ApJ...773...14R, 2013ApJ...768..105M, 2013A&A...551A..29P}.
 
-For the $z<2.2$ sample we corrected the SDSS $i$ and 2SLAQ $g$ band
-magnitudes for host galaxy contamination following
-\citet{2009MNRAS.392...19C}. Considering the different magnitude
-limits of 2SLAQ and SDSS, the modelled host galaxy contamination is
-small for $z>0.5$ quasars ($<0.1$\,mag in $g$, $<0.2$\,mag in $i$),
-and is negligible at $z>0.8$.  In case the band defining the magnitude
-limit of the survey undesirably overlaps with the Ly$\alpha$ forest
-\citep{2010ApJ...710.1498G, 2011ApJ...728L..26G, 2013ApJ...768..105M}
-we adopted their respective bandpass corrections to $M_{1450}$. In
-particular, for the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G}
-sample we recomputed $M_{1450}$ from the $R$ band photometry to be
-consistent with the selection function defined in $R$, and to avoid
-uncertainties in their spectrophotometry due to incomplete spectral
-coverage. For the remaining high-redshift surveys reporting $M_{1450}$
-obtained by various methods \citep{2010AJ....139..906W,
-  2015ApJ...798...28K, 2015AA...578A..83G, 2016ApJ...829...33Y,
-  2016ApJ...833..222J} we did not re-compute $M_{1450}$, but applied
-appropriate shifts to correct to our adopted cosmology.
+For the $z<2.2$ sample we corrected the SDSS $i$ and 2SLAQ $g$ band magnitudes for host galaxy contamination following \citet{2009MNRAS.392...19C}.
+Considering the different magnitude limits of 2SLAQ and SDSS, the modelled host galaxy contamination is small for $z>0.5$ quasars ($<0.1$\,mag in $g$, $<0.2$\,mag in $i$), and is negligible at $z>0.8$.
+In case the band defining the magnitude limit of the survey undesirably overlaps with the Ly$\alpha$ forest \citep{2010ApJ...710.1498G, 2011ApJ...728L..26G, 2013ApJ...768..105M} we adopted their respective bandpass corrections to $M_{1450}$.
+In particular, for the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G} sample we recomputed $M_{1450}$ from the $R$ band photometry to be consistent with the selection function defined in $R$, and to avoid uncertainties in their spectrophotometry due to incomplete spectral coverage.
+Since the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G} $R$ band traces the rest frame UV, we assumed negligible host galaxy contamination for their faint quasars.
+For the remaining high-redshift surveys reporting $M_{1450}$ obtained by various methods \citep{2010AJ....139..906W, 2015ApJ...798...28K, 2015AA...578A..83G, 2016ApJ...829...33Y, 2016ApJ...833..222J} we did not re-compute $M_{1450}$, but applied appropriate shifts to correct to our adopted cosmology.
 
-The selection functions were treated similarly, i.e.\ the photometric
-selection function of survey $j$ given in observed magnitudes
-$f_{\mathrm{p},j}\left(m,z\right)$ \citep{2006AJ....131.2766R,
-  2009MNRAS.392...19C, 2010ApJ...710.1498G, 2013ApJ...773...14R} was
-transformed to our absolute magnitudes
-$f_{\mathrm{p},j}\left(M_{1450},z\right)$ with
-Equation~\ref{eq:absmag}, while the ones given in $M_{1450}$ were
-adjusted to our cosmology. Note, however, that many surveys report
-additional sources of incompleteness that preclude a straightforward
-re-evaluation of the QLF.
+The selection functions were treated similarly, i.e.\ the photometric selection function of survey $j$ given in observed magnitudes $f_{\mathrm{p},j}\left(m,z\right)$ \citep{2006AJ....131.2766R, 2009MNRAS.392...19C, 2010ApJ...710.1498G, 2013ApJ...773...14R} was transformed to our absolute magnitudes $f_{\mathrm{p},j}\left(M_{1450},z\right)$ with Equation~\ref{eq:absmag}, while the ones given in $M_{1450}$ were adjusted to our cosmology.
+Note, however, that many surveys report additional sources of incompleteness that preclude a straightforward re-evaluation of the QLF.
 
-For 2SLAQ we corrected for magnitude-dependent spectroscopic coverage
-in the two survey areas \citep[$f_\mathrm{c,NGP}\left(g\right)$ and
-  $f_\mathrm{c,SGP}\left(g\right)$; Figure~4
-  in][]{2009MNRAS.392...19C} and spectroscopic redshift success
-\citep[$f_\mathrm{s,2SLAQ}\left(g\right)$; Figure~6b
-  in][]{2009MNRAS.392...19C} by multiplying them with the photometric
-selection function, resulting in two area-specific 2SLAQ selection
-functions
-$f_\mathrm{NGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,NGP}f_\mathrm{s,2SLAQ}$
-and
-$f_\mathrm{SGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,SGP}f_\mathrm{s,2SLAQ}$
-that are relevant for the QLF.  The $z<4.7$ SDSS photometric selection
-function was modified to include known imaging incompleteness to
-$f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
-\citep{2006AJ....131.2766R}. The BOSS colour-selected sample contains
-quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$
-\citep{2013ApJ...773...14R}, and we adopted
-$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
-presented two area-specific photometric selection functions due to
-different filters employed, and more follow-up spectroscopy was
-reported in \citet{2011ApJ...728L..26G}. We accounted for remaining
-spectroscopic incompleteness at $R>23$, yielding the final selection
-functions $f_\mathrm{NDWFS}$ and $f_\mathrm{DLS}$. The updated $z\sim
-5$ SDSS photometric selection function \citep{2013ApJ...768..105M} was
-modified to include imaging and spectroscopic incompleteness, yielding
-$f_{\mathrm{SDSS},z\sim 5}=0.95^2f_{\mathrm{p,SDSS},z\sim 5}$. In the
-deeper $z\sim 5$ SDSS Stripe~82 survey the spectroscopic
-incompleteness is larger and magnitude-dependent \citep[Figure~14
-  in][]{2013ApJ...768..105M}, resulting in $f_{\mathrm{S82},z\sim
-  5}=0.95f_{\mathrm{s,S82},z\sim
-  5}\left(i\right)f_{\mathrm{p,S82},z\sim 5}$. Likewise, imaging and
-magnitude-dependent spectroscopic incompleteness was factored into the
-\citet{2016ApJ...829...33Y} photometric selection function (their
-Figures~5 and 7), resulting in
-$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$. Finally,
-we obtained a rough estimate of the \citet{2015AA...578A..83G}
-selection function by taking
-$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
-Table~3).
+For 2SLAQ we corrected for magnitude-dependent spectroscopic coverage in the two survey areas \citep[$f_\mathrm{c,NGP}\left(g\right)$ and $f_\mathrm{c,SGP}\left(g\right)$; Figure~4 in][]{2009MNRAS.392...19C} and spectroscopic redshift success \citep[$f_\mathrm{s,2SLAQ}\left(g\right)$; Figure~6b in][]{2009MNRAS.392...19C} by multiplying them with the photometric selection function, resulting in two area-specific 2SLAQ selection functions $f_\mathrm{NGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,NGP}f_\mathrm{s,2SLAQ}$ and $f_\mathrm{SGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,SGP}f_\mathrm{s,2SLAQ}$ that are relevant for the QLF.
+The $z<4.7$ SDSS photometric selection function was modified to include known imaging incompleteness to $f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$ \citep{2006AJ....131.2766R}.
+The BOSS colour-selected sample contains quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$ \citep{2013ApJ...773...14R}, and we adopted $f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$.
+\citet{2010ApJ...710.1498G} presented two area-specific photometric selection functions due to different filters employed, and more follow-up spectroscopy was reported in \citet{2011ApJ...728L..26G}.
+We accounted for remaining spectroscopic incompleteness at $R>23$, yielding the final selection functions $f_\mathrm{NDWFS}$ and $f_\mathrm{DLS}$.
+The updated $z\sim 5$ SDSS photometric selection function \citep{2013ApJ...768..105M} was modified to include imaging and spectroscopic incompleteness, yielding $f_{\mathrm{SDSS},z\sim 5}=0.95^2f_{\mathrm{p,SDSS},z\sim 5}$.
+In the deeper $z\sim 5$ SDSS Stripe~82 survey the spectroscopic incompleteness is larger and magnitude-dependent \citep[Figure~14 in][]{2013ApJ...768..105M}, resulting in $f_{\mathrm{S82},z\sim 5}=0.95f_{\mathrm{s,S82},z\sim 5}\left(i\right)f_{\mathrm{p,S82},z\sim 5}$.
+Likewise, imaging and magnitude-dependent spectroscopic incompleteness was factored into the \citet{2016ApJ...829...33Y} photometric selection function (their Figures~5 and 7), resulting in $f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
+Finally, we obtained a rough estimate of the \citet{2015AA...578A..83G} selection function by comparing the corrected and observed QLFs, i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their Table~3).
 
@@
     in the left panel and $-20$ in the right panel.}
-  \label{fig:emissivity}
+  \label{fig:gammapi}
 \end{figure*}

### 2017-07-11 drawlf.py
Change LF bin size to 0.2

@@ -130,7 +130,7 @@ def get_lf(lf, sid, z_plot):
     elif sid == 7:
         bins = np.array([-23.5, -21.5, -20.5, -19.5, -18.5])
     else:
-        bins = np.arange(-30.9, -17.3, 0.6)
+        bins = np.arange(-30.9, -17.3, 0.2)
 
     v1 = np.array([totBinVol(lf, x, bins, selmaps) for x in m])
 

### 2017-09-12 Paper/paper.tex
Wrap lines

--- 2017-07-06 Paper/paper.tex
@@
     19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
+    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 & \\
+    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
   \end{tabular}

### 2017-09-12 qhe.py
Calculate and plot Q_He

@@ -5,6 +5,9 @@ See also: q.py.
 """
 
 import numpy as np
+from scipy.integrate import odeint
+from scipy.interpolate import RectBivariateSpline
+
 if __name__ == '__main__':
     import matplotlib as mpl
     mpl.use('Agg') 
@@ -13,10 +16,11 @@ if __name__ == '__main__':
     mpl.rcParams['font.serif'] = 'cm'
     mpl.rcParams['font.size'] = '22'
     import matplotlib.pyplot as plt
-    from scipy.integrate import odeint
     import sys 
 
 hplanck = 6.62e-27
+c_angPerSec = 2.998e18
+nu0 = 3.288e15 # threshold freq for H I ionization; s^-1 (Hz)
 
 cosmo_params_MH15 = True 
 if cosmo_params_MH15:
@@ -29,6 +33,24 @@ else:
     omega_b = 0.0482
     omega_lambda = 0.692
     omega_nr = 0.308
+
+z_HM12 = np.loadtxt('z_HM12.txt')
+data_HM12 = np.loadtxt('hm12.txt')
+w_HM12 = data_HM12[:,0]
+e_HM12 = data_HM12[:,1:]
+
+# kx=1 and ky=1 required here to get good interpolation at the Lyman
+# break.  Also remember that you will most likely need the
+# 'grid=False' option while invoking emissivity_HM12.
+emissivity_HM12 = RectBivariateSpline(w_HM12, z_HM12, e_HM12, kx=1, ky=1)
+
+
+def em_hm12(w, z):
+
+    """HM12 Galaxies+QSO emissivity."""
+
+    return emissivity_HM12(w, z*np.ones_like(w), grid=False)
+
 
 Y_He = 0.24
 h = 0.678
@@ -51,6 +73,16 @@ def qso_emissivity_HM12(z):
     return 10.0**24.6 * (1.0+z)**4.68 * np.exp(-0.28*z)/(np.exp(1.77*z)+26.3) 
 
 
+def qso_emissivity_m18(z):
+
+     return 10.0**(26.462071*np.exp(-1.623373e-2*z)-3.47793833*np.exp(-8.282491e-1*z))
+
+
+def qso_emissivity_m20(z):
+
[…]

### 2017-09-13 Paper/paper.tex
Update text

--- 2017-07-06 Paper/paper.tex
@@
 
-%% \section{Introduction}
-
-%% Possible outline of paper:
-
-%% \begin{enumerate}
-%% \item Introduction 
-%% \item Data set
-%% \item QLF 
-%%   \begin{enumerate}
-%%   \item at specific redshifts 
-%%   \item global model 
-%%   \end{enumerate}
-%% \item Contribution to reionizatin 
-%% \item Conclusion 
-%% \end{enumerate}
-
-%% \noindent Optional possibilities:
-
-%% \begin{enumerate}
-%% \item Bolometric LF
-%% \item PLE, PDE, etc?
-%% \item Quantitative model fit test 
-%% \item BH growth 
-%% \item Comparison with galaxies 
-%% \end{enumerate}
+%% * Possible outline of paper:
+%% 
+%% Introduction 
+%% Data
+%% Method
+%%   Individual fits
+%%   Global fits
+%% Contribution to reionizatin 
+%% Conclusions
+%% 
+%% * Optional possibilities:
+%%
+%% Bolometric LF
+%% Public code description 
+%% More global models: PLE, PDE, Trenti, White-Conroy
+%% Goodness of fit 
+%% BH growth 
+%% Comparison with galaxy LF
+%% Comparison with previous work
 
@@
 \label{sect:datahom}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{kcorr.pdf}
+  \caption{Bandpass corrections $K_{m,1450}$ from a broadband magnitude $m=\{g,i,z_\mathrm{AB}\}$
+           to the monochromatic AB magnitude at 1450\,\AA\ as a function of redshift $z$ for the \citet{2015MNRAS.449.4204L}
+           quasar SED used in this work, and for two quasar composite spectra \citep{2001AJ....122..549V, 2002ApJ...565..773T}.
+           The redshift range has been restricted to exclude the Ly$\alpha$ forest and to account for the different
+           rest frame wavelength coverage of the spectra.}
+  \label{fig:kcorr}
+\end{figure}
 
@@
 for SDSS DR7 quasars to avoid additional corrections due to the
-Ly$\alpha$ forest. Figure~XX shows our bandpass corrections for SDSS,
-BOSS and 2SLAQ as a function of redshift. While the
-\citet{2015MNRAS.449.4204L} SED is for bright ($M_{1450}\simeq -27.2$)
-quasars, UV composite spectra including fainter quasars
+Ly$\alpha$ forest. Figure~\ref{fig:kcorr} shows our bandpass
+corrections for SDSS, BOSS and 2SLAQ as a function of redshift. We
+ignored the luminosity dependence of the bandpass correction due to
+the known anticorrelation of emission line equivalent width and
+luminosity \citep{1977ApJ...214..679B}.  While the
+\citet{2015MNRAS.449.4204L} SED is for luminous ($M_{1450}\simeq
+-27.2$) quasars, UV composite spectra including fainter quasars
 \citep{2002ApJ...565..773T, 2012ApJ...752..162S, 2014ApJ...794...75S}
-give similar values, such that our bandpass corrections likely remain
-applicable at $M_{1450}\la -24$. \textbf{What about even fainter AGN?}
+give similar values, such that our bandpass corrections remain
+applicable at $M_{1450}\la -24$. Empirical luminosity-dependent
+bandpass corrections show a $\la 0.2$\,mag variation over $\sim 4$
+orders of absolute magnitude depending on redshift and the filter, and
+with a $\sim 0.2$\,mag intrinsic scatter due to individual SED
+variations \citep{2013ApJ...773...14R, 2013ApJ...768..105M,
+  2013A&A...551A..29P}.
 
@@
 uncertainties in their spectrophotometry due to incomplete spectral
-coverage. For the remaining high-redshift surveys reporting $M_{1450}$
-obtained by various methods \citep{2010AJ....139..906W,
-  2015ApJ...798...28K, 2015AA...578A..83G, 2016ApJ...829...33Y,
-  2016ApJ...833..222J} we did not re-compute $M_{1450}$, but applied
-appropriate shifts to correct to our adopted cosmology.
+coverage. Since the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G}
+$R$ band traces the rest frame UV, we assumed negligible host galaxy
+contamination for their faint quasars. For the remaining high-redshift
+surveys reporting $M_{1450}$ obtained by various methods
+\citep{2010AJ....139..906W, 2015ApJ...798...28K, 2015AA...578A..83G,
+  2016ApJ...829...33Y, 2016ApJ...833..222J} we did not re-compute
+$M_{1450}$, but applied appropriate shifts to correct to our adopted
+cosmology.
 
@@
 we obtained a rough estimate of the \citet{2015AA...578A..83G}
-selection function by taking
-$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
-Table~3).
+selection function by comparing the corrected and observed QLFs,
+i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$
+(see their Table~3).
 
@@
 
+Given quasar luminosities and estimates for survey completeness, we
+begin our analysis by first deriving luminosity functions binned both
+in redshift and magnitude.  In this discussion all magnitudes are
+absolute magnitudes at rest-frame 1450~{\AA}.
+
+% Put that sentence about magnitudes in the introduction.
+
+\subsection{Binned luminosity function estimates}
+
 In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
@@
   the selection probability in Equation~(\ref{eqn:vi}) accounts for
-  what have been referred to as ``incomplete bins'' in the literature.
-  The comoving volume element $dV/dz$ is given by
+  what are sometimes called ``incomplete bins''
+  \citep{2006AJ....131.2766R}.  The comoving volume element $dV/dz$ is
+  given by
   \begin{equation}
@@
   \end{equation}
-  where $A$ is the survey area in deg$^2$, and \citep{1999astro.ph..5116H}
+  where $A$ is the survey area in deg$^2$, and 
   \begin{equation}
@@
   \end{equation}
-  denotes the comoving volume element per unit solid angle.  The
-  luminosity distance $d_L$ is given by
+  denotes the comoving volume element per unit solid angle
+  \citep{1999astro.ph..5116H}.  The luminosity distance $d_L$ is given
+  by
   \begin{equation}
@@
   integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
-  simply summing over the ``tiles'' of the selection function map.  We
-  do not interpolate between the redshift and luminosity values of
+  simply summing over the ``tiles'' of the selection function map,
+  without interpolating between the redshift and luminosity values of
   neighbouring tiles.  This may result in $V_i=0$ for some quasars, in
-  which case we remove them from our analysis.  Figure~\ref{fig:boss}
-  shows the luminosity function derived in this way for the BOSS DR9
-  colour-selected sample of 23,301 quasars, in comparison with the
-  published luminosity function of \citet{2013ApJ...773...14R}.
-  Figure~\ref{fig:sdss} shows the luminosity function of a sample of
-  15,179 quasars from the SDSS DR3 in comparison with the published
-  luminosity function of \citet{2006AJ....131.2766R}.
-
-  % Describe how we derive error bars.
-
-  \section{Fitting procedure}
-
-  We model the quasar luminosity function as a double power law given
-  by \citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
-  \begin{equation}
-    \phi(M) = \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}},
+  which case we remove them from our analysis.
+
+  In each bin, we estimate the uncertainty in the luminosity function
+  by assuming Poisson statistics \citep{1986ApJ...303..336G}.  The
+  resultant binned luminosity function estimates are shown by the
+  points in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  These
+  agree quite well with the published luminosity functions by these
+  surveys.
+
+  % Do we want to give the details of how good/bad this agreement
+  % actually is?
+
+  %% Figure~\ref{fig:boss}
+  %% shows the luminosity function derived in this way for the BOSS DR9
+  %% colour-selected sample of 23,301 quasars, in comparison with the
+  %% published luminosity function of \citet{2013ApJ...773...14R}.
+  %% Figure~\ref{fig:sdss} shows the luminosity function of a sample of
+  %% 15,179 quasars from the SDSS DR3 in comparison with the published
+  %% luminosity function of \citet{2006AJ....131.2766R}.
+
+\subsection{Luminosity function estimates in redshift bins}
+
+As our next step, we stop binning the quasars in luminosity, and only
+bin them in redshifts.  In each redshift bin, we model the quasar
+luminosity function as a double power law given by
+\citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
+\begin{equation}
+  \phi(M) =
+  \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}}.
   \label{eqn:dpl}
 \end{equation}
-where all magnitudes are absolute magnitudes at rest-frame 1450~{\AA}.  
-The luminosity function $\phi$ gives the comoving number density of
-quasars per unit magnitude.  It usually has units of
-mag$^{-1}$cMpc$^{-3}$.  Equation~(\ref{eqn:dpl}) has four free
-parameters: the amplitude $\phi_*$, the ``break'' $M_*$, the faint-end
-slope $\beta$, and the bright-end slope $\alpha$.  The likelihood
-function can be written as \citep{2001AJ....121...54F}
+Equation~(\ref{eqn:dpl}) has four free parameters: the amplitude
+$\phi_*$, the ``break'' $M_*$, the faint-end slope $\beta$, and the
+bright-end slope $\alpha$.  We obtain posterior probability
+distributions for these parameters using MCMC \citep[e.g.,][]{jaynes}.
+The joint posterior probability distribution of the model parameters
+is then written as
+\begin{multline}
+  p(\phi_*, M_*, \alpha, \beta | \{M_i, z_i\}) \propto \\ p(\phi_*, M_*, \alpha, \beta)p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta),
+\end{multline}
+where the constant of proportionality is independent of the luminosity
+function parameters, and $\{M_i, z_i\}$ denotes the complete quasar
+data.  We use a uniform prior distribution $p(\phi_*, M_*, \alpha,
+\beta)$ and assume that the likelihood
+\begin{equation}
+  \mathcal{L}\equiv p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta)
+\end{equation}
+is given by $\phi(M)$ with suitable normalisation.  That is the
+negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can be
+written as
+\begin{multline}
+  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz}.
+  \label{eqn:S}
+\end{multline}
+where $N$ is the total number of quasars in the sample and the
+integral in the second term on the right hand side is on the 
+surveyed range of $M$ and $z$.
+
+Another way of understanding the above likelihood is as limit of the
+Poisson likelihood in luminosity and redshift bins
+\citep{1983ApJ...269...35M, 2001AJ....121...54F}.  We can write the
+probability of observing $n_{ij}$ quasars in the $(M_i, z_j)$ bin as
+the Poisson distribution
 \begin{equation}
@@
 \end{equation}
-where $n_{ij}$ is the number of quasars observed in the $(M_i, z_j)$
-bin, and
-\begin{equation}
-  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_i}^{z_{i+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
+where 
+\begin{equation}
+  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_j}^{z_{j+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
 \end{equation}
 is the average number of quasars expected in the $(M_i, z_j)$ bin
-given the luminosity function $\phi(M,z)$.  To obtain the maximum
-likelihood solution for the luminosity functin parameters, we minimise
-the function
-\begin{equation}
-  S = -2\ln\mathcal{L}.
-\end{equation}
-In the limit of infinitesimal bins, $n_{ij}=0$ or $1$, in which case
-Equation~(\ref{eqn:lhood}) can be simplified and we can write \citep{1983ApJ...269...35M}
-\begin{multline}
-  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
-\end{multline}
-where $N$ is the total number of quasars in the sample and the
-integral in the second term on the right hand side is now on the full
-range of $M$ and $z$.
+given the luminosity function $\phi(M,z)$.  In the limit of
+infinitesimal bins, $n_{ij}=0$ or $1$, in which case
+Equation~(\ref{eqn:lhood}) can be simplified and we can get
+Equation~(\ref{eqn:S}).
+
+Our estimates for the luminosity function in several redshift bins are
+shown in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  The median
+of the posterior is shown as the best fit model.  Yellow curves show a
+random draw from the posterior.
+
+\subsection{Luminosity function estimate without binning}
+
+Finally, we obtain estimates of the luminosity function.
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
-  \end{center}
-  \caption{Comparison of LF derived by our method with the published
-    LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
-    sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
-    these, 231 quasars have $V_i=0$ and are dropped from the
-    analysis.}
-  \label{fig:boss}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
-  \end{center}
-  \caption{Comparison with the published LF of
-    \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
-    quasars in this sample, of which 155 quasars have $z<0.3$ and 9
-    quasars have $z>5$.  Of the remaining 15179 quasars with
-    $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
-    analysis.  As a result, the green points above contain 15,119
-    quasars.  The red circles contain 14,953 quasars.}
-  \label{fig:sdss}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
-  \end{center}
-  \caption{Comparison with the published LF of
-    \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
-    quasars in their DR7 sample and 52 quasars in the Stripe 82
-    sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
-    The published samples of \citet{2013ApJ...768..105M} have 146 and
-    51 quasars.}
-  \label{fig:mcgreer}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
+%%   \end{center}
+%%   \caption{Comparison of LF derived by our method with the published
+%%     LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
+%%     sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
+%%     these, 231 quasars have $V_i=0$ and are dropped from the
+%%     analysis.}
+%%   \label{fig:boss}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
+%%   \end{center}
+%%   \caption{Comparison with the published LF of
+%%     \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
+%%     quasars in this sample, of which 155 quasars have $z<0.3$ and 9
+%%     quasars have $z>5$.  Of the remaining 15179 quasars with
+%%     $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
+%%     analysis.  As a result, the green points above contain 15,119
+%%     quasars.  The red circles contain 14,953 quasars.}
+%%   \label{fig:sdss}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
+%%   \end{center}
+%%   \caption{Comparison with the published LF of
+%%     \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
+%%     quasars in their DR7 sample and 52 quasars in the Stripe 82
+%%     sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
+%%     The published samples of \citet{2013ApJ...768..105M} have 146 and
+%%     51 quasars.}
+%%   \label{fig:mcgreer}
+%% \end{figure*}
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth]{glikman3.pdf}
-  \end{center}
-  \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
-    and (b) use her volume calculations.  Panels (c)--(e) use our
-    volume calculations.  Various corrections incorporated by Gabor
-    are in panels (c)--(e).  Red open circles in all panels are
-    Glikman's published values; I cannot reproduce them in any of the
-    panels.  All luminosity function in this version of the draft use
-    Gabor's October data from panel (d).}
-  \label{fig:glikman}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth]{giallongo2.pdf}
-  \end{center}
-  \caption{Giallongo's LF when selection function is taken to be
-    $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
-    additional correction is required, which has been incorporated in
-    our LFs.}
-  \label{fig:giallongo}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth]{glikman3.pdf}
+%%   \end{center}
+%%   \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
+%%     and (b) use her volume calculations.  Panels (c)--(e) use our
+%%     volume calculations.  Various corrections incorporated by Gabor
+%%     are in panels (c)--(e).  Red open circles in all panels are
+%%     Glikman's published values; I cannot reproduce them in any of the
+%%     panels.  All luminosity function in this version of the draft use
+%%     Gabor's October data from panel (d).}
+%%   \label{fig:glikman}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth]{giallongo2.pdf}
+%%   \end{center}
+%%   \caption{Giallongo's LF when selection function is taken to be
+%%     $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
+%%     additional correction is required, which has been incorporated in
+%%     our LFs.}
+%%   \label{fig:giallongo}
+%% \end{figure*}
 
@@
     points show results when Giallongo quasars are included.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth,keepaspectratio]{q.pdf}
+  \end{center}
+  \caption{Helium reionization.}
 \end{figure*}

### 2017-09-18 Paper/paper.tex
Update text

@@
 
-Finally, we obtain estimates of the luminosity function.
+It is useful to go beyond the redshift bins of the previous section.
+This gives us continuous models of luminosity function evolution and
+is also relevant for extrapolation. We therefore obtain estimates of
+the luminosity function.
 
@@
   \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
+    % \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
+    \includegraphics[height=0.9\textheight,keepaspectratio]{mosaic_small.pdf}
   \end{center}
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
-  \end{center}
-  \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
-  \label{fig:mosaic2}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
+%%   \end{center}
+%%   \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
+%%   \label{fig:mosaic2}
+%% \end{figure*}
 

### 2017-09-18 Paper/paper.tex
Update text

@@
   resultant binned luminosity function estimates are shown by the
-  points in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  These
-  agree quite well with the published luminosity functions by these
-  surveys.
+  points in Figure~\ref{fig:mosaic}.  These agree quite well with the
+  published luminosity functions by these surveys.
 
@@
   %% luminosity function of \citet{2006AJ....131.2766R}.
+
+\begin{figure*}
+  \begin{center}
+    % \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
+    \includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small.pdf}
+  \end{center}
+  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.  The
+    symbols show our inferred binned luminosity functions.  In each
+    redshift bin, the black curve shows the best-fit double power law
+    model, which is represented by the median of the posterior
+    probability distribution function.  Yellow curves show a random
+    draw from the posterior probability distribution function.  As
+    discussed in the text, luminosity bins that show a decrease in the
+    luminosity function at the faint end are deemed to be incomplete
+    are are removed from our analysis while fitting the double power
+    law model.  These bins are represented by open symbols in this
+    figure.  Each panel shows the number of quasars in the respective
+    redshift bin.  The number in parenthesis indicates the total
+    number of quasars in the bin, before excluding incomplete
+    bins.}
+  \label{fig:mosaic}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{evolution_alldata.pdf}
+  \end{center}
+  \caption{Parameter evolution from individual fits in
+    Figures~\ref{fig:mosaic}.  Parameters from BOSS quasars are seen
+    to be systematically offset.}
+  \label{fig:evoln}
+\end{figure*}
 
@@
 where the constant of proportionality is independent of the luminosity
-function parameters, and $\{M_i, z_i\}$ denotes the complete quasar
-data.  We use a uniform prior distribution $p(\phi_*, M_*, \alpha,
-\beta)$ and assume that the likelihood
+function parameters, and $\{M_i, z_i\}$ denotes the magnitudes and
+redshifts of quasars falling in a redshift bin $[z_\mathrm{min},
+  z_\mathrm{max})$.  We use a uniform prior distribution $p(\phi_*,
+  M_*, \alpha, \beta)$ and assume that the likelihood
 \begin{equation}
@@
 \end{equation}
-is given by $\phi(M)$ with suitable normalisation.  That is the
-negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can be
+is given by $\phi(M)$ with suitable normalisation.  The negative
+logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can then be
 written as
@@
 \end{multline}
-where $N$ is the total number of quasars in the sample and the
-integral in the second term on the right hand side is on the 
-surveyed range of $M$ and $z$.
-
-Another way of understanding the above likelihood is as limit of the
+where $N$ is the total number of quasars in the redshift bin and the
+luminosity integral in the second term on the right hand side is on
+the surveyed range of $M$.
+
+The above likelihood can also be understood as the limit of the
 Poisson likelihood in luminosity and redshift bins
@@
 given the luminosity function $\phi(M,z)$.  In the limit of
-infinitesimal bins, $n_{ij}=0$ or $1$, in which case
-Equation~(\ref{eqn:lhood}) can be simplified and we can get
-Equation~(\ref{eqn:S}).
+infinitesimal bins, $n_{ij}=0$ or $1$, Equation~(\ref{eqn:lhood}) can
+be simplified and we get Equation~(\ref{eqn:S}).
 
 Our estimates for the luminosity function in several redshift bins are
-shown in Figures \ref{fig:mosaic} and \ref{fig:mosaic2}.  The median
-of the posterior is shown as the best fit model.  Yellow curves show a
-random draw from the posterior.
+shown in Figure~\ref{fig:mosaic}.  The median of the posterior is
+shown as the best fit model.  Yellow curves show a random draw from
+the posterior.  Consistent with previous studies, the double power law
+model provides an excellent description of the luminosity function
+model over almost the complete range of redshifts spanned by the data.
+It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
+seem to favour a single power law.  In this bin, we the resultant
+posterior distribution of the break magnitude $M_*$ is bimodal with
+favoured values at the faint ($M_*>-18$) and bright end of the data
+($M_*<-30$).  We consider only the latter possibility as consistent
+with the data at lower redshifts ($z<5.5$).  In light of the low
+redshift data, we use restricted priors in this redshift bins: we
+restrict the bright-end slope $\alpha$ to values less than $-4$.
+Other paramters continue to have wide uniform priors.
+
+As seen in Figure~\ref{fig:mosaic}, in several redshift bins the
+binned quasar luminosity function seems to show a decline at the faint
+end.  This is clearly seen, for example, in the 2SLAQ sample at $z<2$.
+We take this to be a systematic error: the decrease in the luminosity
+function is an indication of incompleteness in the quasar surveys that
+has not been accounted for by the reported completeness map.  We
+choose to discard such quasars from our analysis.  This behaviour is
+also seen in the SDSS quasar sample at $z<1.8$ and $z\sim 4$.  The
+discarded luminosity bins are shown in Figure~\ref{fig:mosaic} by open
+circles.  We can see that the surviving quasar sample is in excellent
+agreement with the double power law model at all redshifts.
+
+The values of the four double power law parameters in various redshift
+bins are shown in Figure~\ref{fig:evoln}.  We find interesting
+evolutionary trends in each of the four parameters.  The break
+luminosity $M_*$ evolves by more than eight magnitudes from redshift
+$z=0$ to $7$.  The amplitude of the luminosity function $\phi_*$
+evolves moderately from $z=0$ to $z\sim 3$ and then drops by six
+orders of magnitude to about $10^{-12}$ at $z\sim 7$.  The bright end
+slope $\alpha$ has significant scatter, but still shows a trend
+towards larger negative values---that is, steeper bright-end
+luminosity functions---at high redshifts.  Finally, the faint end of
+the luminosity function also shows signs of increasing steepness
+towards high redshifts.  Somewhat similar to the amplitude $\phi_*$,
+the faint-end slope $\beta$ also shows a break at $z\sim 3$.  It stays
+roughly constant up to this redshift, and the drops to increasingly
+negative values at high redshifts, indicating a steeper faint end.
+
+The behaviour of BOSS quasars in Figure~\ref{fig:evoln} is striking.
+In the redshift range covered by BOSS the values of the four double
+power law parameters deviate from the general trends.  The faint end
+of the luminosity function of the BOSS quasars is much shallower and
+the break luminosity is fainter by a magnitude.  The bright end of the
+luminosity function of quasars in this sample is also much flatter
+than that for other samples.  The conspicuousness of the deviation of
+the BOSS sample from the general trends makes it unlikely that the
+luminosity function evolution indicated by BOSS in the redshift range
+$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
+selection is known to be affected by a colour bias
+\citep{2011ApJ...728...23W}, as the quasar colour selection is
+contaminated by a population of blue stars.  We therefore deem the
+BOSS sample as affected by this systematic error.
+
+The open circles in Figure~\ref{fig:evoln} show the results of a
+similar analysis of the quasar UV luminosity function by
+\citep{2017MNRAS.466.1160M}.  Evidently, our results are quite
+different from the results of these authors.  While their analysis
+generally also reveals a steep faint end slop, the break luminosity
+evolution is dramatically different.  In their analysis the break
+luminosity tends to remain roughly constant $M_*\sim -24$ from $z=0$
+to $7$, but this does not seem to be indicated by the data shown in
+Figure~\ref{fig:mosaic}.  A possible reason behind their significanly
+different results could be a bias introduced by binning in
+luminosities and redshifts while fitting the luminosity function model.
 
@@
 
-It is useful to go beyond the redshift bins of the previous section.
-This gives us continuous models of luminosity function evolution and
-is also relevant for extrapolation. We therefore obtain estimates of
-the luminosity function.
+The smooth evolution of the luminosity function parameters apparant in
+Figure~\ref{fig:evoln} suggests that it should be possible to describe
+the quasar UV luminosity function evolution from $z\sim 7$ to $0$
+using far fewer number of parameters.  Such descriptions have been put
+forward in the literature for the X-ray and bolometric luminosity
+functions \citep[e.g.,][]{2007ApJ...654..731H, 2015MNRAS.451.1892A}.
+Such ``global'' descriptions of the luminosity function evolution are
+useful as they give a continuous description of the luminosity
+function.  This makes them valuable while developing an understanding
+of the physics behind the luminosity function. We therefore obtain
+estimates of the luminosity function in which the evolution of the
+four parameters of the double power law models in
+Equation~(\ref{eqn:dpl}) is parameterised to write
+\begin{align}
+  &\phi_*(z) = f_0(\{c_{0,i}\}, z)\nonumber\\
+  &M_*(z) = f_1(\{c_{1,i}\}, z)\nonumber\\
+  &\alpha(z) = f_2(\{c_{2,i}\}, z)\nonumber\\
+  &\beta(z) = f_3(\{c_{3,i}\}, z),
+\end{align}
+where the $c_i$'s are the new model parameters.  The joint posterior
+probability distribution of these parameters can be now written as
+\begin{equation}
+  p(\{c_i\} | \{M_i, z_i\}) \propto p(\{c_i\})p(\{M_i, z_i\} | \{c_i\}),
+\end{equation}
+where the likelihood 
+\begin{equation}
+  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_i\}),
+\end{equation}
+is now given by $\phi(M,z)$ with suitable normalisation.  Note that
+$\phi(M,z)$ is simply 
+\begin{multline}
+  \phi(M,z) = \phi_*(z) \left[10^{0.4(\alpha(z)+1)(M-M_*(z))}\right. \\ \left.+ 10^{0.4(\beta(z)+1)(M-M_*(z))}\right]^{-1}.
+\end{multline}
+The ngative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
+straightforward generalisation of Equation~(\ref{eqn:S}), so that
+\begin{multline}
+  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
+  \label{eqn:S2}
+\end{multline}
+where now $N$ is the total number of quasars included in the analysis,
+and the integrals in the second term on the right-hand side are over
+the complete surveyed range of luminosity and redshift.
 
@@
 
-\begin{figure*}
-  \begin{center}
-    % \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
-    \includegraphics[height=0.9\textheight,keepaspectratio]{mosaic_small.pdf}
-  \end{center}
-  \caption{Individual luminosity function fits for $z=0.3$ to $2.6$.}
-  \label{fig:mosaic}
-\end{figure*}
-
 %% \begin{figure*}
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{evolution_alldata.pdf}
-  \end{center}
-  \caption{Parameter evolution from individual fits in
-    Figures~\ref{fig:mosaic} and \ref{fig:mosaic2}.  Parameters from
-    BOSS quasars are seen to be systematically offset. \textbf{[Show
-        $z < 0.6$ point also?]}}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
     \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}

### 2017-09-20 Paper/paper.tex
Update text

@@
 
+\begin{figure*}
+  \begin{center}
+    \includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small_global.pdf}
+  \end{center}
+  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
+    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
+    binned luminosity functions.  In each redshift bin, the yellow
+    curves show the best-fit double power law luminosity function in
+    that redshift bin.  The green curves show the posterior
+    distribution of the global model.  The global model agrees very
+    well with the data in all redshift bins, except those spanned by
+    BOSS, as BOSS quasars are excluded from the global analysis.}
+  \label{fig:mosaic_global}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{evolution_global.pdf}
+  \end{center}
+  \caption{Luminosity function parameter evolution in the global
+    model.  The symbols show the best fit parameters with 68\%
+    uncertainties from the double power law fits to the data in
+    redshift bins.  These points are identical to those in
+    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
+    2$--$3$) are not shown.  In each panel, the black solid curve
+    shows the best fit global model, and the coloured curves show a
+    random sample drawn from the global posterior.}
+  \label{fig:evoln_global}
+\end{figure*}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+  \end{center}
+  \caption{AGN number density evolution in the global model.}
+  \label{fig:rhoqso}
+\end{figure}
+
 \subsection{Luminosity function estimate without binning}
@@
   &\beta(z) = f_3(\{c_{3,i}\}, z),
+\label{eqn:global}
 \end{align}
@@
 the complete surveyed range of luminosity and redshift.
+
+We consider models in which the evolution of the four double power law
+parameter is modelled independently as in
+Equations~(\ref{eqn:global}).  This approach has been termed as
+``flexible double power law'' by \citet{2015MNRAS.451.1892A}.  For the
+parameters $\phi_*$, $M_*$ and $\alpha$ we assume that the functions
+$f_i$s in Equations~(\ref{eqn:global}) are Chebyshev polynomials in
+$1+z$.  Thus the functions $f_i$s are written as
+\begin{equation}
+  f_i=\sum_{j=0}^{n_i}c_{i,j}T_j(1+z),
+  \label{eqn:cbs}
+\end{equation}
+where $c_{i,j}$ are the parameters that appear in
+Equations~(\ref{eqn:global}) and $T_j(1+z)$ are Chebyshev polynomials
+of the first kind.  We try successively higher orders of Chebyshev
+polynomials in order to arrive at a good fit with the data.  We find
+that $\phi_*$, $M_*$ and $\alpha$ prefer quadratic, cubic, and linear
+evolutions in $1+z$.
+
+The faint-end slope $\beta$ seems to require a break in its evolution
+at $z\sim 3$, as discussed in the previous section.  As a result, it
+is difficult to model the evolution of $\beta$ using the Chebyshev
+expansion of Equation~(\ref{eqn:cbs}).  Instead, we consider a double
+power law model for $\beta$ and write
+\begin{equation}
+  f_3(1+z)=h+\frac{f_0}{10^{a*\zeta}+10^{b*\zeta}},
+\end{equation}
+where
+\begin{equation}
+  \zeta = \log_{10}\left(\frac{1+z}{1+z_0}\right),
+\end{equation}
+thus resulting in a five-parameter model with parameters $h$, $f_0$,
+$z_0$, $a$ and $b$.  The parameters $a$ and $b$ thus determine the low
+and high redshift slopes of this evolution, with a break at redshift
+$z_0$.  This is similar to the model of \citet{2007ApJ...654..731H},
+who also favoured a broken power law model for the evolution of the
+faint-end slope of the bolometric luminosity function of quasars.
+
+Our resultant 14-parameter global model for the luminosity function
+evolution in shown in Figure~\ref{fig:mosaic_global}, in which the
+green curves show a random draw from the posterior probability
+distibution function.  For comparison, the symbols show the luminosity
+function binned in luminosity and redshift, and the yellow curves show
+the posterior distribution of the double power law luminosity
+functions in various redshift bins, as in Figure~\ref{fig:mosaic}.  We
+find that the global model is in excellent agreement with the binned
+models.  The agreement is poor for the BOSS quasars as these are not
+described by the global model, as discussed in the previous section.
+
+Figure~\ref{fig:evoln_global} shows the parameter evolution in the
+global model, by comparing it with the results from the fits in
+individual redshift bins shown in Figure~\ref{fig:evoln}.  The
+agreement between the two models is very good, showing an evolution
+towards a steep faint-end slope of the luminosity function at high
+redshifts, a rapid brightening of the break luminosity.  Note that the
+redshift bins with BOSS qsos are not shown in
+Figure~\ref{fig:evoln_global}, which explains the difference from
+Figure~\ref{fig:evoln}.
 
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_allz.pdf}
-  \end{center}
-  \caption{AGN number density evolution, showing the systematic offset in BOSS quasars.}
-  \label{fig:rhoqso_allz}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
-  \end{center}
-  \caption{AGN number density evolution with some BOSS quasars
-    removed.}
-  \label{fig:rhoqso}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth]{evolution_seldata.pdf}
-  \end{center}
-  \caption{Parameter evolution with some BOSS quasars removed.  We (1)
-    use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and (2) use only
-    $p>0.9$ quasars in the $z>3.7$ sample of Richards.}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_withGlobal.pdf}
-  \end{center}
-  \caption{Individual and composite luminosity function fits for
-    $z=0.3$ to $2.6$.  They do not agree for $2.2 < z < 2.6$ because
-    composite fit does not consider quasars at those redshifts.}
-  \label{fig:mosaic_withGlobal}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2_withGlobal.pdf}
-  \end{center}
-  \caption{Individual and composite luminosity function fits for
-    $z=2.6$ to $6.5$.  They do not agree for $2.6 < z < 2.8$ because
-    composite fit does not consider quasars at those redshifts.}
-  \label{fig:mosaic2_withGlobal}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth]{evolution_global.pdf}
-  \end{center}
-  \caption{Luminosity function parameter evolution in the global model.}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
-  \end{center}
-  \caption{AGN number density evolution in the global model.}
-  \label{fig:rhoqso}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_allz.pdf}
+%%   \end{center}
+%%   \caption{AGN number density evolution, showing the systematic offset in BOSS quasars.}
+%%   \label{fig:rhoqso_allz}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
+%%   \end{center}
+%%   \caption{AGN number density evolution with some BOSS quasars
+%%     removed.}
+%%   \label{fig:rhoqso}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth]{evolution_seldata.pdf}
+%%   \end{center}
+%%   \caption{Parameter evolution with some BOSS quasars removed.  We (1)
+%%     use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and (2) use only
+%%     $p>0.9$ quasars in the $z>3.7$ sample of Richards.}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_withGlobal.pdf}
+%%   \end{center}
+%%   \caption{Individual and composite luminosity function fits for
+%%     $z=0.3$ to $2.6$.  They do not agree for $2.2 < z < 2.6$ because
+%%     composite fit does not consider quasars at those redshifts.}
+%%   \label{fig:mosaic_withGlobal}
+%% \end{figure*}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic2_withGlobal.pdf}
+%%   \end{center}
+%%   \caption{Individual and composite luminosity function fits for
+%%     $z=2.6$ to $6.5$.  They do not agree for $2.6 < z < 2.8$ because
+%%     composite fit does not consider quasars at those redshifts.}
+%%   \label{fig:mosaic2_withGlobal}
+%% \end{figure*}
 

### 2017-09-20 Paper/paper.tex
Update text

@@
 
-\title[AGN luminosity function]{Evolution of the AGN UV luminosity function}
+\title[AGN luminosity function]{Evolution of the AGN UV luminosity function from redshift 7.5}
 
@@
 \begin{abstract}
-  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
-  eget nisi augue. Vivamus quis purus quis massa tempor posuere non
-  quis magna. Aenean eleifend, metus eget facilisis faucibus, turpis
-  erat suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse
-  luctus eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec
-  massa ultrices, porttitor nulla at, euismod diam. In ultricies
-  malesuada mauris ac facilisis. Nulla quis suscipit diam, vitae
-  semper tortor. Proin nec nulla at massa egestas porta. Cras ac arcu
-  in velit placerat facilisis fringilla in sem. Mauris finibus, mauris
-  ut pretium malesuada, massa urna mattis nibh, at placerat ligula
-  elit ac odio.  Nunc vel leo arcu. Nullam sagittis tincidunt
-  interdum. Mauris sed lacus cursus, dapibus enim non, sagittis
-  leo. Aliquam sit amet ex ut quam iaculis sollicitudin. Vivamus ut
-  pharetra dolor. Vivamus id nibh leo. Vestibulum consectetur eu lorem
-  eu tincidunt. Sed eget nibh orci. Pellentesque sit amet blandit
-  massa, vel tempor neque.
+We present the evolution UV/optical luminosity function of quasars
+from a homogeneous reanalysis of more than 85,000 spectroscopically
+selected quasars from redshift $z=0$ to $7.5$.  We derived luminosity
+functions when the observed quasar population is binned in luminosity
+and redshift, and then construct a continuous evolutionary model of
+the luminosity function spanning a range of redshifts.  We find that
+quasars selected from the BOSS survey at $z=2$--$3$ show a significant
+systematic offset from the general trends, possiblity due to the
+colour bias suffered by BOSS.  Some systematic errors also persist in
+the lowest-redshift quasar sample due to host galaxy effects. However,
+we find that it is possible to describe the luminosity function
+evolution from redshift $z=0$ to $7.5$ using a simple 14-parameter
+evolving double power law model.  The evolution of the number density
+of qsos shows the familiar downsizing effect, although the evolution
+in the faint quasar population is quite flat at high redshifts such
+that the the drop in their number density at high redshifts is much
+slower than that for bright quasars.  When integrated down to
+$M_{1450}=-20$ quasars can produce all of the hydrogen-ionizing
+photons in the intergalactic medium upto redshifts 3.5.  They fall
+short of the emissivity required to explain the Ly$\alpha$ data at
+higher redshifts, and are therefore unlikely to have singlehandedly
+driven hydrogen reionization.  This conclusion can be altered,
+however, if lower luminosity qsos (down to $M_{1450}=-18$) are assumed
+to exist and to have a unity escape fraction, in which case qsos can
+potentially produce all the hydrogen-ionizing flux at $z<7.5$.
+He~\textsc{ii} reionization in this model occurs between $z=3.2$ and
+$3.7$.
 \end{abstract}
@@
 \begin{keywords}
-quasars
+dark ages, reionization, firs stars -- intergalactic medium -- quasars: general -- galaxies: active 
 \end{keywords}
@@
   \end{center}
-  \caption{AGN number density evolution in the global model.}
+  \caption{AGN number density evolution in the global model.  Similar
+    to Figure~\ref{fig:evoln_global}, symbols show the best fit
+    parameters with 68\% uncertainties from the double power law fits
+    to the data in redshift bins.  Black solid curve shows the best
+    fit global model, and the coloured curves show a random sample
+    drawn from the global posterior.  \textbf{[Show rejected bins in
+        differnt symbols here.  Do not show the $-18$ case.  Cut the
+        figure off at 6.5.]}}
   \label{fig:rhoqso}
 \end{figure}
+
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
+    \end{tabular}
+  \end{center}
+  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
+    Model luminosity functions are integrated down to $M_{1450}=-18$
+    in the left panel and $-20$ in the right panel.}
+  \label{fig:e912}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{g_18.pdf}
+    \includegraphics[width=0.5\textwidth]{g_20.pdf}
+    \end{tabular}
+  \end{center}
+  \caption{AGN contribution to the hydrogen photoionisation rate,
+    assuming 100\% escape fraction.  Model luminosity functions are
+    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
+    the right panel.}
+  \label{fig:gammapi}
+\end{figure*}
 
@@
 
+The evolution of the comoving number density of quasars is shown in
+Figure~\ref{fig:rhoqso} when the luminosity function is integrated
+down to different limits.  Similar to Figure~\ref{fig:evoln_global},
+symbols show the best fit parameters with 68\% uncertainties from the
+double power law fits to the data in redshift bins.  Black solid curve
+shows the best fit global model, and the coloured curves show a random
+sample drawn from the global posterior.  Bins with BOSS qsos are not
+shown.  The number density of qsos down to the limit of spectroscopic
+data is about 1 per $10^5$ cMpc$^3$ at its peak.  This density rapidly
+increases at low redshifts and then drops gradually at high redshifts.
+Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
+which the number density of faint qsos peaks are lower redshifts than
+that of the bright qsos.  While the number density of qsos with
+$M_*<-27$ peaks at $z\sim 2.5$, the number density of qsos with
+$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
+spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
+at $z\sim 1$.
+
 \section{Hydrogen photoionization rate}
@@
 
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
-    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
-    \end{tabular}
-  \end{center}
-  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
-    Model luminosity functions are integrated down to $M_{1450}=-18$
-    in the left panel and $-20$ in the right panel.}
-  \label{fig:gammapi}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{g_18.pdf}
-    \includegraphics[width=0.5\textwidth]{g_20.pdf}
-    \end{tabular}
-  \end{center}
-  \caption{AGN contribution to the hydrogen photoionisation rate,
-    assuming 100\% escape fraction.  Model luminosity functions are
-    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
-    the right panel.}
-  \label{fig:gammapi}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \begin{tabular}{cc}
+%%     \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
+%%     \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
+%%     \end{tabular}
+%%   \end{center}
+%%   \caption{LyC emissivity of AGN assuming 100\% escape fraction.
+%%     Model luminosity functions are integrated down to $M_{1450}=-18$
+%%     in the left panel and $-20$ in the right panel.}
+%%   \label{fig:gammapi}
+%% \end{figure*}
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
-eget nisi augue. Vivamus quis purus quis massa tempor posuere non quis
-magna. Aenean eleifend, metus eget facilisis faucibus, turpis erat
-suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse luctus
-eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec massa
-ultrices, porttitor nulla at, euismod diam. In ultricies
+% Check spellings
+% Check notes for more names with add
+% Something to add for Joe and Gabor?
+We acknowledge useful discussions with James Aird, Manda Banerji,
+Tirthankar Roy Choudhury, Xiaohui Fan, Andrea Ferrara, Martin
+Haehnelt, Sergey Koposov, Richard McMahon, Ewald Puchwein, Gordon
+Richards, and Alberto Rorai for helpful discussions.  GK is supported
+by ERC Advanced Grant 320596 `The Emergence of Structure During the
+Epoch of Reionization'.
 

### 2017-09-20 drawlf.py
Reduce scatter point size

@@ -364,7 +364,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
         mags, left, right, logphi, uperr, downerr = get_lf(lf, i, z_plot)
         print mags[logphi>-100.0]
         print logphi[logphi>-100.0]
-        ax.scatter(mags, logphi, c=cs[i], edgecolor='None', zorder=4, s=36, label=dsl(i))
+        ax.scatter(mags, logphi, c=cs[i], edgecolor='None', zorder=4, s=20, label=dsl(i))
         ax.errorbar(mags, logphi, ecolor=cs[i], capsize=0,
                     xerr=np.vstack((left, right)), 
                     yerr=np.vstack((uperr, downerr)),
@@ -387,7 +387,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
                         xerr=np.vstack((left_all, right_all)), 
                         yerr=np.vstack((uperr_all, downerr_all)),
                         fmt='None', zorder=4)
-            ax.scatter(mags_all, logphi_all, c='#ffffff', edgecolor=cs[i], zorder=4, s=22.5, label=dsl(i)+' (rejected)')
+            ax.scatter(mags_all, logphi_all, c='#ffffff', edgecolor=cs[i], zorder=4, s=16, label=dsl(i)+' (rejected)')
 
     if showMockSample:
         for i in sids:

### 2017-09-20 individual.py
Correct qso exclusion at z ~ 2

@@ -126,8 +126,7 @@ def getqlums(lumfile, zlims=None):
         select = (((z_all>=0.6) & (z_all<0.8) & (mag_all<=-20.7)) | 
                   ((z_all>=0.8) & (z_all<1.2) & (mag_all<=-21.9)) |
                   ((z_all>=1.2) & (z_all<1.8) & (mag_all<=-22.5)) |
-                  ((z_all>=1.8) & (z_all<2.0) & (mag_all<=-23.1)) |
-                  ((z_all>=2.0) & (z_all<2.2)))
+                  ((z_all>=1.8) & (z_all<2.2) & (mag_all<=-23.1)))
         
     # if sid == 15:
     #     select = ((z_all < 2.2) & (mag_all <= m_cutoff_15))
@@ -233,8 +232,7 @@ class selmap:
             select = (((self.z_all>=0.6) & (self.z_all<0.8) & (self.m_all<=-20.7)) | 
                       ((self.z_all>=0.8) & (self.z_all<1.2) & (self.m_all<=-21.9)) |
                       ((self.z_all>=1.2) & (self.z_all<1.8) & (self.m_all<=-22.5)) |
-                      ((self.z_all>=1.8) & (self.z_all<2.0) & (self.m_all<=-23.1)) |
-                      ((self.z_all>=2.0) & (self.z_all<2.2)))
+                      ((self.z_all>=1.8) & (self.z_all<2.2) & (self.m_all<=-23.1)))
             
         if sample_id == 8:
             # Restrict McGreer's samples to faint quasars to avoid

### 2017-09-20 lfg.py
Add UKIDSS and Banados qsos

@@ -6,7 +6,7 @@ from summary import summary_plot as sp
 qlumfiles = ['Data_new/dr7z2p2_sample.dat',
              'Data_new/croom09sgp_sample.dat',
              'Data_new/croom09ngp_sample.dat',
-             # 'Data_new/bossdr9color.dat',
+           # 'Data_new/bossdr9color.dat',
              'Data_new/dr7z3p7_sample.dat',
              'Data_new/glikman11debug.dat',
              'Data_new/yang16_sample.dat',
@@ -21,12 +21,13 @@ qlumfiles = ['Data_new/dr7z2p2_sample.dat',
              'Data_new/willott10_cfhqsvwsample.dat',
              'Data_new/kashikawa15_sample.dat',
              'Data_new/giallongo15_sample.dat',
-             'Data_new/ukidss_sample.dat']
+             'Data_new/ukidss_sample.dat',
+             'Data_new/banados_sample.dat']
 
 selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/croom09sgp_selfunc.dat', 0.3, 0.05, 64.2, 15),
              ('Data_new/croom09ngp_selfunc.dat', 0.3, 0.05, 127.7, 15),
-             # ('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1),
+           # ('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1),
              ('Data_new/dr7z3p7_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/glikman11_selfunc_ndwfs.dat', 0.05, 0.02, 1.71, 6),
              ('Data_new/glikman11_selfunc_dls.dat', 0.05, 0.02, 2.05, 6),
@@ -40,7 +41,8 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/willott10_cfhqsvwsel.dat', 0.1, 0.025, 494.0, 10),
              ('Data_new/kashikawa15_sel.dat', 0.05, 0.05, 6.5, 11),
              ('Data_new/giallongo15_sel.dat', 0.0, 0.0, 0.047, 7),
-             ('Data_new/ukidss_sel.dat', 0.8, 0.45, 3370, 19)]
+             ('Data_new/ukidss_sel.dat', 0.8, 0.45, 3370.0, 19),
[…]

### 2017-09-20 mosaic.py
Change mosaic style

@@ -9,7 +9,7 @@ import matplotlib.pyplot as plt
 from drawlf import render 
 
 def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
-         nofirstylabel=True, nolastxlabel=True, legend=True):
+         nofirstylabel=True, nolastxlabel=True, nofirstxlabel=False, legend=False):
 
     """
 
@@ -23,9 +23,12 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     render(ax, lf, composite=composite)
 
     ax.set_xlim(-18.0, -30.0)
-    ax.set_ylim(-12.0, -3.0)
+    ax.set_ylim(-12.0, -2.0)
     # ax.set_xticks(np.arange(-31,-16, 2))
     ax.set_xticks(np.arange(-30, -16, 3))
+    ax.set_yticks(np.arange(-12, -1, 2))
+
+    ax.tick_params('both', which='major', length=3, width=1)
 
     if not yticklabels:
         ax.set_yticklabels('')
@@ -39,6 +42,17 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     if nolastxlabel:
         ax.get_xticklabels()[0].set_visible(False)
 
+    if nofirstxlabel:
+        ax.get_xticklabels()[-1].set_visible(False)
+
+    label = r'${:g}\leq z<{:g}$'.format(lf.zlims[0], lf.zlims[1])
+    plt.text(0.03, 0.05, label, horizontalalignment='left',
+             verticalalignment='center', transform=ax.transAxes, fontsize='10')
+
+    num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450_all.size)
+    plt.text(0.03, 0.12, num, horizontalalignment='left',
+             verticalalignment='center', transform=ax.transAxes, fontsize='10')
+    
     if legend:
         legend_title = r'${:g}\leq z<{:g}$'.format(lf.zlims[0], lf.zlims[1]) 
         l = plt.legend(loc='lower left', fontsize=8, handlelength=3,
@@ -51,16 +65,16 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     
 def draw(lfs, composite=None):
 
-    nplots_x = 3
-    nplots_y = 3
+    nplots_x = 4
+    nplots_y = 6
     nplots = nplots_x * nplots_y
 
[…]

### 2017-09-21 Paper/paper.tex
Update text

@@
 \begin{keywords}
-dark ages, reionization, firs stars -- intergalactic medium -- quasars: general -- galaxies: active 
+dark ages, reionization, first stars -- intergalactic medium --
+quasars: general -- galaxies: active
 \end{keywords}
@@
 %%
+%% Low-z photon under-production
 %% Bolometric LF
@@
     Model luminosity functions are integrated down to $M_{1450}=-18$
-    in the left panel and $-20$ in the right panel.}
+    in the left panel and $-20$ in the right panel.  For comparison,
+    various other published determinations of the 1~Ry emissivity of
+    quasars are also shown in both panels of Figure~\ref{fig:e912}.
+    The blue curve in these panels shows the AGN 1~Ry emissivity model
+    of \citet{2012ApJ...746..125H}, which is very similar to the model
+    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
+    show the determination from the fits of
+    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
+    to the 1~Ry emissivity evolution in the fits of
+    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
+    \citet{2015ApJ...813L...8M}.}
   \label{fig:e912}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{g_18.pdf}
-    \includegraphics[width=0.5\textwidth]{g_20.pdf}
-    \end{tabular}
-  \end{center}
-  \caption{AGN contribution to the hydrogen photoionisation rate,
-    assuming 100\% escape fraction.  Model luminosity functions are
-    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
-    the right panel.}
-  \label{fig:gammapi}
 \end{figure*}
@@
 \begin{equation}
-  f_3(1+z)=h+\frac{f_0}{10^{a*\zeta}+10^{b*\zeta}},
+  f_3(1+z)=h+\frac{f_0}{10^{a\zeta}+10^{b\zeta}},
 \end{equation}
@@
 
+% Add a table for the best fit parameter values?
+
 \section{Hydrogen photoionization rate}
 
-We assume that all quasars have a universal SED, which can be
-parameterised in some fashion.  \citet{2015MNRAS.449.4204L} have
-parameterised the quasar SED as a power law with a break at 912~{\AA},
+We can now calculate the contribution of quasars to the hydrogen
+photoionization rate in the intergalactic medium (IGM).  We assume
+that all quasars have a universal UV SED, parameterised by
+\citet{2015MNRAS.449.4204L} as a power law with a break at 912~{\AA},
 \begin{equation}
@@
 \end{equation}
-Here $f_\nu$ is the flux density, with units of ergs s$^{-1}$
-cm$^{-2}$ Hz$^{-1}$, although it is often simply called flux.  Note
-that although $f_\nu$ is often the quantity of interest, e.g., when
-calculating the hydrogen ionizing emissivity of quasars, what is shown
-in spectra is often $f_\lambda$, the flux density
-in \emph{wavelength}, which has units of ergs s$^{-1}$
-cm$^{-2}$ \AA$^{-1}$.  If the flux density in frequency is power law,
-then the flux density in wavelength is also power law.  The power law
-index of the flux density in wavelength, $\alpha_\lambda$, is related
-to the power law index of the flux density in frequency, $\alpha_\nu$,
-by $\alpha_\lambda=-(\alpha_\nu+2)$.  From Equation~(\ref{eqn:sed}),
-we can now see that $\alpha_\lambda=-0.3$ in the extreme UV (EUV;
-600~{\AA}$<\lambda<$912~{\AA}) and $\alpha_\lambda=-1.39$ in the far
-UV (FUV; $\lambda>$912~{\AA}).  The quasar SED that we have adopted is
-steep in FUV and shallow in EUV.
-
-How sensible is it to assume that the quasar SED of
-Equation~(\ref{eqn:sed}) is universal?  Of the four published
-composite quasar SEDs (see references in
-\citealt{2015MNRAS.449.4204L}), three agree with
-Equation~(\ref{eqn:sed}).  There is one published composite quasar SED
-that does not agree with Equation~(\ref{eqn:sed}).  This is the
+This fit was derived by \citet{2015MNRAS.449.4204L} from a composite
+spectrum of 53 quasars at $z\sim 2.4$.
+
+While four published composite quasar UV SEDs
+\citep{2002ApJ...565..773T, 2001AJ....122..549V, 2012ApJ...752..162S,
+  2014ApJ...794...75S} agree with Equation~(\ref{eqn:sed}), the
 composite of \citet{2004ApJ...615..135S}, which uses more than 100
-quasars at $z<0.1$.  The EUV slope of this SED is $-0.56$.  (This
-means that the power law index of the flux density in wavelength is
-$-1.44$, so that the spectrum actually becomes even steeper in the
-EUV.  See Figure 8 of \citealt{2015MNRAS.449.4204L}.)  The quasars
-considered by \citet{2004ApJ...615..135S} are much fainter that those
-considered by \citet{2015MNRAS.449.4204L}, which means that it is
-possible that faint quasars have a steep EUV spectrum.  So we could
-say that for faint quasars,
+quasars at $z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.
+The quasars considered by \citet{2004ApJ...615..135S} are fainter
+($M_i(z=2)>-26$) than those considered by \citet{2015MNRAS.449.4204L},
+which suggest that faint quasars may have a steeper EUV spectrum.  We
+therefore also consider an SED of the form
 \begin{equation}
@@
 \end{equation}
-Here, ``faint'' is defined as $M_i(z=2)>-26$.  $M_i(z=2)$ can be
-related to the bolometric luminosity of the quasar (see Figure 9 of
-\citealt{2015MNRAS.449.4204L}.)
+for qsos with $M_{1450}<-23$.
 
@@
 \end{equation}
-The units of $\dot n_\nu$ are s$^{-1}$~cMpc$^{-3}$~Hz$^{-1}$.  Here
-the integral is over some range of magnitudes, the monochromatic
-luminosity $L_\nu(M)$ is related to the (absolute AB) magnitude
-by \citep{1983ApJ...266..713O}
+Here the integral is over a suitable range of magnitudes, the
+monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
+magnitude by \citep{1983ApJ...266..713O}
 \begin{equation}
@@
 \begin{equation}
-  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61}
-\end{equation}
-The corresponding volume emissivity is conventionally written
-as 
+  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
+\end{equation}
+depending on the qso luminosity.  The corresponding physical volume
+emissivity is 
 \begin{equation}
@@
 \end{equation}
-This is a \emph{physical} density.  The units of $\epsilon_\nu$ are
-erg~s$^{-1}$~pMpc$^{-3}$~Hz$^{-1}$.  This emissivity can now be used
-to calculate the ionizing flux and photoionization rate contributed by
-quasars.  The frequency dependence above 1~Ry is given by
-Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
-\nu_{912}$
+Figure~\ref{fig:e912} shows the resultant 1~Ry emissivity when the
+luminosity function is integrated down to $M_{1450}=-20$ (right panel)
+and when it is integrated down to $M_{1450}=-18$ (left panel).
+Similar to the previous figures, the black open circles in this figure
+show the result form individual redshift bins, while the black curve
+shown the result from best-fit global model.  Yellow curves show a
+random sample from the global posterior distribution.  For comparison,
+various other published determinations of the 1~Ry emissivity of
+quasars are also shown in both panels of Figure~\ref{fig:e912}.  The
+blue curve in these panels shows the AGN 1~Ry emissivity model of
+\citet{2012ApJ...746..125H}, which is very similar to the model of
+\citet{2007ApJ...654..731H}.  The red symbols with error bars show the
+determination from the fits of \citet{2015AA...578A..83G}.  The maroon
+curve is the published fit to the 1~Ry emissivity evolution in the
+fits of \citet{2017MNRAS.466.1160M}.  The green curve is the model of
+\citet{2015ApJ...813L...8M}.  Note that the integration limits for
+these other models are not homogeneous.  \citet{2017MNRAS.466.1160M}
+integrate the luminosity function down to $M_{1450}=-19$, while
+\citet{2015AA...578A..83G} integrate down to $M_{1450}=-18$.
+\textbf{[What are the limits for HM12 and MH15?]}
+
+The 1~Ry emissivity increases rapidly from $z=0$ up to $z=2$ and then
+stays roughly constant until up to $z=3.5$.  At higher redshifts, due
+to the relatively steeper faint end slope of the luminosity function,
+the integration limit makes a large difference in the resultant
+emissivity.  For the conservative case, in which we integrate under
+the luminosity function down to $M_{1450}=-20$, the emissivity drops
+rapidly at $z>3.5$, and is only about 10--20\% higher than that in the
+\citet{2012ApJ...746..125H} model at $z\sim 6$.  However, in the model
+in which we integrate down to $M_{1450}=-18$, the emissivity is higher
+by a factor of almost 10 than that in the \citet{2012ApJ...746..125H}
+model at $z\sim 6$.  In this case, our derived emissivities are
+consistent with the values published by \citet{2015AA...578A..83G} at
+$z=4$--$6$, although they still fall short by a factor of $\sim 2$.
+Our derived emissivities are significantly smaller at $z>3.5$ than the
+model of \citet{2015ApJ...813L...8M}.
+
+The 1~Ry emissivity can now be used to calculate the ionizing flux and
+photoionization rate contributed by quasars.  The frequency dependence
+above 1~Ry is given by Equation~(\ref{eqn:sed}) or
+(\ref{eqn:sed_faint}), so that for $\nu > \nu_{912}$
 \begin{equation}
@@
 \end{equation}
+
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{g_18.pdf}
+    \includegraphics[width=0.5\textwidth]{g_20.pdf}
+    \end{tabular}
+  \end{center}
+  \caption{AGN contribution to the hydrogen photoionisation rate,
+    assuming 100\% escape fraction.  Model luminosity functions are
+    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
+    the right panel.}
+  \label{fig:gammapi}
+\end{figure*}
 
@@
 Haehnelt, Sergey Koposov, Richard McMahon, Ewald Puchwein, Gordon
-Richards, and Alberto Rorai for helpful discussions.  GK is supported
-by ERC Advanced Grant 320596 `The Emergence of Structure During the
-Epoch of Reionization'.
+Richards, and Alberto Rorai.  GK is supported by ERC Advanced Grant
+320596 `The Emergence of Structure During the Epoch of Reionization'.
 

### 2017-09-21 Paper/paper.tex
Update text

@@
 \end{equation}
-where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$ (Equation~\ref{eqn:sed_faint}).
-
-The emissivity calculated in Equation~(\ref{eqn:epsilon}) is a source
-property.  We are now interested in what flux this emissivity produces
-in the surrounding intergalactic medium.  This brings in the medium's
-properties also, via the radiative transfer equation.  The flux is
-\citep{2012ApJ...746..125H}
+where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
+(Equation~\ref{eqn:sed_faint}).  The corresponding flux in the IGM is
+written as a solution of the cosmological radiative transfer equation
+as \citep{2012ApJ...746..125H}
 \begin{multline}
@@
 \end{equation}
-We estimate the effective optical depth as
+Here the effective optical depth is estimated as
 \begin{equation}
@@
 \end{equation}
+where $\sigma$ is the photoionization cross-section.  The result is
+shown in Figure~\ref{fig:gammapi}, in which as before the solid black
+curve shows the hydrogen photoionisate rate in our best-fit global
+model, and the yellow curves show a random sample from the global
+posterior.  Also, as before, the right panel of
+Figure~\ref{fig:gammapi} shows the result when we only account for
+quasars brighter than $M_{1450}=-20$, while the left panel shows the
+result when the integration limit is $M_{1450}=-18$.  The red points
+with error bars in this figure show the measurements of
+\citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$ forest,
+and the orange points show the measurements by
+\citet{2011MNRAS.412.2543C} from quasar proximity zones.  The dashed
+green curve shows the hydrogen photoionisation rate evolution in the
+model of \citet{2012ApJ...746..125H}, while the solid green curve
+shows the contribution of quasars to it.
+
+The black open circles show the photoionisation rate values derived
+from our fits in the individual redshift bins.  However, note that
+unlike in the global model it is not possible to do the integral in
+Equation~(\ref{eqn:flux}) for these individual fits.  We can only
+derive the photoionisatoin rate by assuming what is known as the local
+source approximation, that is by assuming that the photons emitted at
+redshift $z$ are absorbed at the same redshift without propagation to
+large distances.
 
@@
     integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
-    the right panel.}
+    the right panel.  The solid black curve shows the hydrogen
+    photoionisate rate in our best-fit global model, and the yellow
+    curves show a random sample from the global posterior.  The red
+    points with error bars in this figure show the measurements of
+    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
+    forest, and the orange points show the measurements by
+    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
+    dashed green curve shows the hydrogen photoionisation rate
+    evolution in the model of \citet{2012ApJ...746..125H}, while the
+    solid green curve shows the contribution of quasars to it. }
   \label{fig:gammapi}
 \end{figure*}
-
-\subsection{Local source approximation}
 
@@
 Note that this equation refers to the \emph{comoving} emissivity.  The
-local source approximation works well for $z>3$ \citep{2013MNRAS.436.1023B}.
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{boss.pdf}
-%%   \end{center}
-%%   \caption{Comparison of LF derived by our method with the published
-%%     LF of \citet{2013ApJ...773...14R} for the BOSS DR9 color-selected
-%%     sample. There are 23,301 quasars in this sample ($2.2<z<3.5$).  Of
-%%     these, 231 quasars have $V_i=0$ and are dropped from the
-%%     analysis.}
-%%   \label{fig:boss}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{sdss.pdf}
-%%   \end{center}
-%%   \caption{Comparison with the published LF of
-%%     \citet{2006AJ....131.2766R} for SDSS DR3.  There are 15,343
-%%     quasars in this sample, of which 155 quasars have $z<0.3$ and 9
-%%     quasars have $z>5$.  Of the remaining 15179 quasars with
-%%     $0.3<z<5$, 60 quasars have $V_i=0$ and are dropped from the
-%%     analysis.  As a result, the green points above contain 15,119
-%%     quasars.  The red circles contain 14,953 quasars.}
-%%   \label{fig:sdss}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{mcgreer.pdf}
-%%   \end{center}
-%%   \caption{Comparison with the published LF of
-%%     \citet{2013ApJ...768..105M} for $4.7\leq z<5.1$.  There are 148
-%%     quasars in their DR7 sample and 52 quasars in the Stripe 82
-%%     sample. Of these 1 quasar from the Stripe 82 sample has $V_i=0$.
-%%     The published samples of \citet{2013ApJ...768..105M} have 146 and
-%%     51 quasars.}
-%%   \label{fig:mcgreer}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{glikman.pdf}
-%%   \end{center}
-%%   \caption{Comparison with the published LF of
-%%     \citet{2011ApJ...728L..26G} for $3.5<z<5.2$.  There are 24 
-%%     quasars in their two samples (NDWFS and DLS).}
-%%   \label{fig:mcgreer}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth]{glikman3.pdf}
-%%   \end{center}
-%%   \caption{Attempts at reproducing Glikman's published LF.  Panels (a)
-%%     and (b) use her volume calculations.  Panels (c)--(e) use our
-%%     volume calculations.  Various corrections incorporated by Gabor
-%%     are in panels (c)--(e).  Red open circles in all panels are
-%%     Glikman's published values; I cannot reproduce them in any of the
-%%     panels.  All luminosity function in this version of the draft use
-%%     Gabor's October data from panel (d).}
-%%   \label{fig:glikman}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth]{giallongo2.pdf}
-%%   \end{center}
-%%   \caption{Giallongo's LF when selection function is taken to be
-%%     $\phi_\mathrm{corr}/\phi$ from their paper.  This plots shows that
-%%     additional correction is required, which has been incorporated in
-%%     our LFs.}
-%%   \label{fig:giallongo}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
-%%   \end{center}
-%%   \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
-%%   \label{fig:mosaic2}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso_allz.pdf}
-%%   \end{center}
-%%   \caption{AGN number density evolution, showing the systematic offset in BOSS quasars.}
-%%   \label{fig:rhoqso_allz}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=0.6\textwidth,keepaspectratio]{rhoqso.pdf}
-%%   \end{center}
-%%   \caption{AGN number density evolution with some BOSS quasars
-%%     removed.}
-%%   \label{fig:rhoqso}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth]{evolution_seldata.pdf}
-%%   \end{center}
-%%   \caption{Parameter evolution with some BOSS quasars removed.  We (1)
-%%     use \emph{only} BOSS quasars for $z=2.2$--$3.5$, and (2) use only
-%%     $p>0.9$ quasars in the $z>3.7$ sample of Richards.}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_withGlobal.pdf}
-%%   \end{center}
-%%   \caption{Individual and composite luminosity function fits for
-%%     $z=0.3$ to $2.6$.  They do not agree for $2.2 < z < 2.6$ because
-%%     composite fit does not consider quasars at those redshifts.}
-%%   \label{fig:mosaic_withGlobal}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic2_withGlobal.pdf}
-%%   \end{center}
-%%   \caption{Individual and composite luminosity function fits for
-%%     $z=2.6$ to $6.5$.  They do not agree for $2.6 < z < 2.8$ because
-%%     composite fit does not consider quasars at those redshifts.}
-%%   \label{fig:mosaic2_withGlobal}
-%% \end{figure*}
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \begin{tabular}{cc}
-%%     \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
-%%     \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
-%%     \end{tabular}
-%%   \end{center}
-%%   \caption{LyC emissivity of AGN assuming 100\% escape fraction.
-%%     Model luminosity functions are integrated down to $M_{1450}=-18$
-%%     in the left panel and $-20$ in the right panel.}
-%%   \label{fig:gammapi}
-%% \end{figure*}
+local source approximation works well for $z>3$, as can be seen in
+Figure~\ref{fig:gammapi}, where the points from the individual fits
+are in much better agreement with the curves from the global model.
+At lower redshift, the photoionisation rate in the individual models
+is much higher than that in the global model, because the individual
+models overestimate the flux at these redshifts.
 
@@
 
-\begin{figure*}
+\begin{figure}
   \begin{center}
-    \includegraphics[width=0.7\textwidth,keepaspectratio]{q.pdf}
+    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
   \end{center}
   \caption{Helium reionization.}
-\end{figure*}
+\end{figure}
 

### 2017-09-22 bins.py
Add 0.2 < z < 0.6 qsos

@@ -42,20 +42,11 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'SDSS DR7 
 
 method = 'Nelder-Mead'
 
-# zls = [(0.6, 0.68), (0.68, 1.06), (1.06, 1.44), (1.44, 1.82), (1.82, 2.2),
-#        (2.2, 2.3), (2.3, 2.4), (2.4, 2.5), (2.5, 2.6), (2.6, 2.7), (2.7, 2.8),
-#        (2.8, 3.0), (3.0, 3.25), (3.25, 3.5), (3.7, 4.1), (4.1, 4.7),
-#        (4.7, 5.5), (5.5, 6.5)]
-
-zls = [(0.6, 0.8), (0.8, 1.0), (1.0, 1.2), (1.2, 1.4), (1.4, 1.6),
-       (1.6, 1.8), (1.8, 2.2), (2.2, 2.3), (2.3, 2.4), (2.4, 2.5),
-       (2.6, 2.7), (2.7, 2.8), (2.8, 2.9), (2.9, 3.0), (3.0, 3.1),
-       (3.1, 3.2), (3.2, 3.3), (3.3, 3.4), (3.4, 3.5), (3.7, 4.1),
-       (4.1, 4.7), (4.7, 5.5), (5.5, 6.5)]
-
-# zls = [(0.6, 0.68), (0.68, 1.06), (1.06, 1.44), (1.44, 1.82), (1.82, 2.2),
-#        (2.8, 3.0), (3.0, 3.25), (3.25, 3.5), (3.7, 4.1), (4.1, 4.7),
-#        (4.7, 5.5), (5.5, 6.5)]
+zls = [(0.2, 0.4), (0.4, 0.6), (0.6, 0.8), (0.8, 1.0), (1.0, 1.2),
+       (1.2, 1.4), (1.4, 1.6), (1.6, 1.8), (1.8, 2.2), (2.2, 2.3),
+       (2.3, 2.4), (2.4, 2.5), (2.6, 2.7), (2.7, 2.8), (2.8, 2.9),
+       (2.9, 3.0), (3.0, 3.1), (3.1, 3.2), (3.2, 3.3), (3.3, 3.4),
+       (3.4, 3.5), (3.7, 4.1), (4.1, 4.7), (4.7, 5.5), (5.5, 6.5)]
 
 lfs = [] 
 

### 2017-09-22 individual.py

@@ -104,7 +104,9 @@ def getqlums(lumfile, zlims=None):
 
 
     if sid == 13: 
-        select = ((((z_all>=0.6) & (z_all<0.8) & (mag_all<=-23.1)) | 
+        select = ((((z_all>=0.2) & (z_all<0.4) & (mag_all<=-20.3)) |
+                   ((z_all>=0.4) & (z_all<0.6) & (mag_all<=-21.3)) |
+                   ((z_all>=0.6) & (z_all<0.8) & (mag_all<=-23.1)) | 
                    ((z_all>=0.8) & (z_all<1.0) & (mag_all<=-23.7)) |
                    ((z_all>=1.0) & (z_all<1.2)) |
                    ((z_all>=1.2) & (z_all<1.4) & (mag_all<=-24.3)) |
@@ -113,24 +115,13 @@ def getqlums(lumfile, zlims=None):
                    ((z_all>=1.8) & (z_all<2.2))) |
                   ((z_all>=3.5) & (z_all<4.7) & (p_all>0.94)))
         
-    # if sid == 13:
-    #     # Restrict Richards sample (1) to z < 2.2 as there are
-    #     # only three qsos with z = 2.2; (2) to z >= 0.6 to avoid
-    #     # host galaxy contamination; (3) to m > -23 at low z to
-    #     # avoid incompleteness; and (4) to m < -26 at high z to
-    #     # avoid incompleteness.  Also see selmap below.
-    #     select = (((z_all<2.2) & (mag_all<=m_cutoff_13) )|
-    #               ((z_all>=3.5) & (z_all<4.7) & (p_all>0.94)))
-
     if sid == 15: 
-        select = (((z_all>=0.6) & (z_all<0.8) & (mag_all<=-20.7)) | 
+        select = (((z_all>=0.4) & (z_all<0.6)) |
+                  ((z_all>=0.6) & (z_all<0.8) & (mag_all<=-20.7)) | 
                   ((z_all>=0.8) & (z_all<1.2) & (mag_all<=-21.9)) |
                   ((z_all>=1.2) & (z_all<1.8) & (mag_all<=-22.5)) |
                   ((z_all>=1.8) & (z_all<2.2) & (mag_all<=-23.1)))
         
-    # if sid == 15:
-    #     select = ((z_all < 2.2) & (mag_all <= m_cutoff_15))
-
     if sid == 8:
         select = (mag_all > -26.73)
 
@@ -219,7 +210,9 @@ class selmap:
[…]

### 2017-09-22 lfi.py

@@ -110,19 +110,23 @@ lfi = lf(quasar_files=qlumfiles, selection_maps=selnfiles, zlims=zl)
 print '{:d} quasars in this bin.'.format(lfi.z.size)
 
 # g = (np.log10(1.e-6), -25.0, -3.0, -1.5)
-g = (np.log10(5.e-7), -22.0, -3.0, -1.5)
+g = (np.log10(1.e-6), -21.0, -3.0, -2.0)
 
 b = lfi.bestfit(g, method=method)
 print b
 
-lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
-if zmin > 5.4:
-    # Special priors for z = 6 data.
-    lfi.prior_max_values = np.array([-4.0, -20.0, -4.0, 0.0])
-    # Change result of optimize.minimize so that emcee works.
-    lfi.bf.x[2] = -5.0
-else:
-    lfi.prior_max_values = np.array([-4.0, -20.0, 0.0, 0.0])
+# lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
+# if zmin > 5.4:
+#     # Special priors for z = 6 data.
+#     lfi.prior_max_values = np.array([-4.0, -20.0, -4.0, 0.0])
+#     # Change result of optimize.minimize so that emcee works.
+#     lfi.bf.x[2] = -5.0
+# else:
+#     lfi.prior_max_values = np.array([-4.0, -20.0, 0.0, 0.0])
+# assert(np.all(lfi.prior_min_values < lfi.prior_max_values))
+
+lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -10.0])
+lfi.prior_max_values = np.array([-1.0, -15.0, 0.0, 10.0])
 assert(np.all(lfi.prior_min_values < lfi.prior_max_values))
 
 lfi.run_mcmc()
@@ -138,7 +142,9 @@ if WRITE_PARAMS:
                   + lfi.M_star + lfi.alpha + lfi.beta)
         f.write(('{:.3f}  '*len(output)).format(*output)) 
         f.write('\n')
-    
+
+lfi.chains()
+lfi.corner_plot()
 drawlf.draw(lfi, show_individual_fit=True)
 
 

### 2017-09-22 bins.py
Add z < 0.2 qsos

@@ -1,5 +1,7 @@
 import sys 
 import numpy as np
+import individual
+reload(individual)
 from individual import lf
 import mosaic
 
@@ -42,11 +44,12 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'SDSS DR7 
 
 method = 'Nelder-Mead'
 
-zls = [(0.2, 0.4), (0.4, 0.6), (0.6, 0.8), (0.8, 1.0), (1.0, 1.2),
-       (1.2, 1.4), (1.4, 1.6), (1.6, 1.8), (1.8, 2.2), (2.2, 2.3),
-       (2.3, 2.4), (2.4, 2.5), (2.6, 2.7), (2.7, 2.8), (2.8, 2.9),
-       (2.9, 3.0), (3.0, 3.1), (3.1, 3.2), (3.2, 3.3), (3.3, 3.4),
-       (3.4, 3.5), (3.7, 4.1), (4.1, 4.7), (4.7, 5.5), (5.5, 6.5)]
+zls = [(0.0, 0.2), (0.2, 0.4), (0.4, 0.6), (0.6, 0.8), (0.8, 1.0),
+       (1.0, 1.2), (1.2, 1.4), (1.4, 1.6), (1.6, 1.8), (1.8, 2.2),
+       (2.2, 2.3), (2.3, 2.4), (2.4, 2.5), (2.6, 2.7), (2.7, 2.8),
+       (2.8, 2.9), (2.9, 3.0), (3.0, 3.1), (3.1, 3.2), (3.2, 3.3),
+       (3.3, 3.4), (3.4, 3.5), (3.7, 4.1), (4.1, 4.7), (4.7, 5.5),
+       (5.5, 6.5)]
 
 lfs = [] 
 
@@ -68,17 +71,23 @@ for i, zl in enumerate(zls):
     b = lfi.bestfit(g, method=method)
     print b 
 
-    lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
-    zmin, zmax = zl 
+    if zmin < 0.3:
+        lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -10.0])
+    else:
+        lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
+
     if zmin > 5.4:
         # Special priors for z = 6 data.
         lfi.prior_max_values = np.array([-4.0, -20.0, -4.0, 0.0])
[…]

### 2017-09-22 individual.py

@@ -104,7 +104,8 @@ def getqlums(lumfile, zlims=None):
 
 
     if sid == 13: 
-        select = ((((z_all>=0.2) & (z_all<0.4) & (mag_all<=-20.3)) |
+        select = ((((z_all>=0.0) & (z_all<0.2) & (mag_all<=-20.7)) |
+                   ((z_all>=0.2) & (z_all<0.4) & (mag_all<=-20.3)) |
                    ((z_all>=0.4) & (z_all<0.6) & (mag_all<=-21.3)) |
                    ((z_all>=0.6) & (z_all<0.8) & (mag_all<=-23.1)) | 
                    ((z_all>=0.8) & (z_all<1.0) & (mag_all<=-23.7)) |
@@ -210,7 +211,8 @@ class selmap:
             select = ((self.z_all>=z_min) & (self.z_all<z_max))
 
         if sample_id == 13: 
-            select = ((((self.z_all>=0.2) & (self.z_all<0.4) & (self.m_all<=-20.4)) | 
+            select = ((((self.z_all>=0.0) & (self.z_all<0.2) & (self.m_all<=-20.7)) | 
+                       ((self.z_all>=0.2) & (self.z_all<0.4) & (self.m_all<=-20.4)) | 
                        ((self.z_all>=0.4) & (self.z_all<0.6) & (self.m_all<=-21.3)) | 
                        ((self.z_all>=0.6) & (self.z_all<0.8) & (self.m_all<=-23.1)) | 
                        ((self.z_all>=0.8) & (self.z_all<1.0) & (self.m_all<=-23.7)) |

### 2017-09-22 lfi.py

@@ -110,25 +110,29 @@ lfi = lf(quasar_files=qlumfiles, selection_maps=selnfiles, zlims=zl)
 print '{:d} quasars in this bin.'.format(lfi.z.size)
 
 # g = (np.log10(1.e-6), -25.0, -3.0, -1.5)
-g = (np.log10(1.e-6), -21.0, -3.0, -2.0)
+# g = (np.log10(1.e-6), -21.0, -3.0, -2.0)
+g = (np.log10(1.e-6), -25.0, -3.0, -1.5)
 
 b = lfi.bestfit(g, method=method)
 print b
 
-# lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
-# if zmin > 5.4:
-#     # Special priors for z = 6 data.
-#     lfi.prior_max_values = np.array([-4.0, -20.0, -4.0, 0.0])
-#     # Change result of optimize.minimize so that emcee works.
-#     lfi.bf.x[2] = -5.0
-# else:
-#     lfi.prior_max_values = np.array([-4.0, -20.0, 0.0, 0.0])
-# assert(np.all(lfi.prior_min_values < lfi.prior_max_values))
+if zmin < 0.3:
+    lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -10.0])
+else:
+    lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -4.0])
 
-lfi.prior_min_values = np.array([-14.0, -32.0, -7.0, -10.0])
-lfi.prior_max_values = np.array([-1.0, -15.0, 0.0, 10.0])
+if zmin > 5.4:
+    # Special priors for z = 6 data.
+    lfi.prior_max_values = np.array([-4.0, -20.0, -4.0, 0.0])
+    # Change result of optimize.minimize so that emcee works.
+    lfi.bf.x[2] = -5.0
+elif zmin < 0.3:
+    lfi.prior_max_values = np.array([-1.0, -15.0, 0.0, 15.0])
+else:
+    lfi.prior_max_values = np.array([-4.0, -20.0, 0.0, 0.0])
+
 assert(np.all(lfi.prior_min_values < lfi.prior_max_values))
-
+    
 lfi.run_mcmc()
 bf = np.median(lfi.samples, axis=0)
 print bf 

### 2017-09-22 bins.py
Add z < 0.6 bins

@@ -44,12 +44,11 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'SDSS DR7 
 
 method = 'Nelder-Mead'
 
-zls = [(0.0, 0.2), (0.2, 0.4), (0.4, 0.6), (0.6, 0.8), (0.8, 1.0),
-       (1.0, 1.2), (1.2, 1.4), (1.4, 1.6), (1.6, 1.8), (1.8, 2.2),
-       (2.2, 2.3), (2.3, 2.4), (2.4, 2.5), (2.6, 2.7), (2.7, 2.8),
-       (2.8, 2.9), (2.9, 3.0), (3.0, 3.1), (3.1, 3.2), (3.2, 3.3),
-       (3.3, 3.4), (3.4, 3.5), (3.7, 4.1), (4.1, 4.7), (4.7, 5.5),
-       (5.5, 6.5)]
+zls = [(0.1, 0.4), (0.4, 0.6), (0.6, 0.8), (0.8, 1.0), (1.0, 1.2),
+       (1.2, 1.4), (1.4, 1.6), (1.6, 1.8), (1.8, 2.2), (2.2, 2.3),
+       (2.3, 2.4), (2.4, 2.5), (2.6, 2.7), (2.7, 2.8), (2.8, 2.9),
+       (2.9, 3.0), (3.0, 3.1), (3.1, 3.2), (3.2, 3.3), (3.3, 3.4),
+       (3.4, 3.5), (3.7, 4.1), (4.1, 4.7), (4.7, 5.5), (5.5, 6.5)]
 
 lfs = [] 
 
@@ -68,6 +67,7 @@ for i, zl in enumerate(zls):
     print ' '
     
     g = (np.log10(1.e-6), -25.0, -3.0, -1.5)
+
     b = lfi.bestfit(g, method=method)
     print b 
 

### 2017-09-22 mosaic.py

@@ -65,7 +65,7 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     
 def draw(lfs, composite=None):
 
-    nplots_x = 4
+    nplots_x = 5
     nplots_y = 6
     nplots = nplots_x * nplots_y
 
@@ -97,7 +97,7 @@ def draw(lfs, composite=None):
     fig.subplots_adjust(left=l, bottom=b, right=r, top=t, wspace=wspace/hdim,
                         hspace=hspace/vdim)
 
-    for i in range(nplots-1):
+    for i in range(nplots-4):
 
         ax = fig.add_subplot(nplots_y, nplots_x, i+1)
         print 'plotting', i

### 2017-09-22 drawlf.py
Show 1-sigma region only

@@ -58,12 +58,20 @@ def lfsample(theta, n, mlims):
 
     return np.random.choice(sample, n)
     
-def plot_posterior_sample_lfs(lf, ax, mags, **kwargs):
+def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
 
-    random_thetas = lf.samples[np.random.randint(len(lf.samples), size=1000)]
-    for theta in random_thetas:
-        phi_fit = lf.log10phi(theta, mags)
-        ax.plot(mags, phi_fit, **kwargs)
+    nmags = 100
+    mags = np.linspace(*maglims, num=nmags)
+    nsample = 1000
+    rsample = lf.samples[np.random.randint(len(lf.samples), size=nsample)]
+    phi = np.zeros((nsample, nmags))
+    
+    for i, theta in enumerate(rsample):
+        phi[i] = lf.log10phi(theta, mags)
+
+    up = np.percentile(phi, 15.87, axis=0)
+    down = np.percentile(phi, 84.13, axis=0)
+    ax.fill_between(mags, down, y2=up, color='grey')
 
     return
 
@@ -71,8 +79,7 @@ def plot_bestfit_lf(lf, ax, mags, **kwargs):
 
     bf = np.median(lf.samples, axis=0)
     phi_fit = lf.log10phi(bf, mags)
-    ax.plot(mags, phi_fit, **kwargs)
-    ax.plot(mags, phi_fit, lw=1, c='k', zorder=kwargs['zorder'])
+    ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
 
     return
 
@@ -318,7 +325,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
 
     if show_individual_fit: 
         mag_plot = np.linspace(-32.0, -16.0, num=200) 
-        plot_posterior_sample_lfs(lf, ax, mag_plot, lw=1,
+        plot_posterior_sample_lfs(lf, ax, (-32.0, -16.0), lw=1,
                                        c='#ffbf00', alpha=0.1, zorder=2) 
         plot_bestfit_lf(lf, ax, mag_plot, lw=2,
                              c='#ffbf00', zorder=3, label='individual fit')

### 2017-09-22 mosaic.py
Modify figure layout

@@ -66,7 +66,7 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
 def draw(lfs, composite=None):
 
     nplots_x = 5
-    nplots_y = 6
+    nplots_y = 5
     nplots = nplots_x * nplots_y
 
     plot_number = 0
@@ -97,22 +97,20 @@ def draw(lfs, composite=None):
     fig.subplots_adjust(left=l, bottom=b, right=r, top=t, wspace=wspace/hdim,
                         hspace=hspace/vdim)
 
-    for i in range(nplots-4):
+    for i in range(nplots):
 
         ax = fig.add_subplot(nplots_y, nplots_x, i+1)
         print 'plotting', i
 
         idx_offset=0
         
-        if i in set([0,4,8,12,16]):
+        if i in set([0,5,10,15]):
             plot(lfs[i+idx_offset], ax, composite=composite, yticklabels=True)
-        elif i == 21:
+        elif i in set([21,22,23]):
             plot(lfs[i+idx_offset], ax, composite=composite, xticklabels=True)
-        elif i == 19:
-            plot(lfs[i+idx_offset], ax, composite=composite, xticklabels=True, nolastxlabel=False, nofirstxlabel=True)
         elif i == 20:
             plot(lfs[i+idx_offset], ax, composite=composite, yticklabels=True, xticklabels=True, nofirstylabel=False)
-        elif i == 22:
+        elif i == 24:
             plot(lfs[i+idx_offset], ax, composite=composite, xticklabels=True, nolastxlabel=False)
         else:
             plot(lfs[i+idx_offset], ax, composite=composite)

### 2018-01-08 Paper/paper.tex
Update text

@@
   \begin{center}
-    % \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
-    \includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small.pdf}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
+    %\includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small.pdf}
   \end{center}
@@
     number of quasars in the bin, before excluding incomplete
-    bins.}
+    bins. \textbf{[Remove redshift bins that were excluded from global
+        analysis.]}}
   \label{fig:mosaic}
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{evolution_alldata.pdf}
+    \includegraphics[width=0.7\textwidth]{evol_28sep.pdf}
   \end{center}
@@
   \begin{center}
-    \includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small_global.pdf}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
   \end{center}
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{evolution_global.pdf}
+    \includegraphics[width=0.7\textwidth]{evolution_global_9oct.pdf}
   \end{center}
@@
     \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
-    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_18_9oct.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_20_9oct.pdf}
     \end{tabular}
@@
 where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
-(Equation~\ref{eqn:sed_faint}).  The corresponding flux in the IGM is
+(Equation~\ref{eqn:sed_faint}).  The flux in the IGM is
 written as a solution of the cosmological radiative transfer equation
@@
     \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{g_18.pdf}
-    \includegraphics[width=0.5\textwidth]{g_20.pdf}
+    \includegraphics[width=0.5\textwidth]{g_18_10oct.pdf}
+    \includegraphics[width=0.5\textwidth]{g_20_10oct.pdf}
     \end{tabular}
@@
 
-\begin{figure*}
+\begin{figure}
   \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
+    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
   \end{center}
-  \caption{Parameter evolution from individual fits.  Coloured points
-    show results when Giallongo quasars are not included.  Black
-    points show results when Giallongo quasars are included.}
-\end{figure*}
+  \caption{Photon underproduction crisis.}
+\end{figure}
+
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
+%%   \end{center}
+%%   \caption{Parameter evolution from individual fits.  Coloured points
+%%     show results when Giallongo quasars are not included.  Black
+%%     points show results when Giallongo quasars are included.}
+%% \end{figure*}
 
@@
 \end{figure}
+
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal_dense.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff_ind.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+\section{Hydrogen and helium reionization}
+
+\section{Photon underproduction}
+
+\citet{2014ApJ...789L..32K} reported that the hydrogen photoionization
+rate required by simulations to match the observed HI column density
+distribution and the effective Ly$\alpha$ opacity at low redshifts
+($z\sim 0.1$) is a factor of five (check factor---it looks like about
+ten in the plot) higher than that predicted by the model of
+\citep{2012ApJ...746..125H}.  This deficit in the hydrogen
+photoionization rate at these redshifts, termed `photon
+underproduction crisis', has inspired models in which the excess
+photonization in explained by blazars (citation) or an evolution in
+the density structure of the IGM.  Subsequent simulations by
+\citet{2015ApJ...811....3S}, calibrated the observed HI column density
+distribution and the effective Ly$\alpha$ optical depth reduced the
+severity of the problem by
+
+\section{Conclusion}
+
+We have presented an analysis of the evolution of the UV luminosity
+function of AGN from redshift $z=0$ to $7.5$ using a combined
+homogenised sample of close to 90,000 UV-selected AGN.  We only
+consider quasars with spectroscopic redshifts and reliable
+completeness estimates.  These data span magnitudes down to
+$M_{1450}=-22$ at high redshifts ($z\gtrsim 3.5$).
+
+\begin{itemize}
+\item The AGN luminosity function prefers a double power law
+  description at all redshift, except possibly at very high redshifts
+  ($z\sim 6$) where only the faint-end of the luminosity function is
+  observed.
+
+\item The break magnitude $M_*$ of the double power law luminosity
+  function shows a steep brightening towards the high redshift.  The
+  break evolves from $M_*<-25$ at $z\sim 2$ to $M_*\sim -29$ at $z\sim
+  6$.  Correspondingly, the amplitude $\phi_*$ of the luminosity
+  function drops rapidly towards high redshifts from $\phi_*\sim
+  10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 2$ to $\phi_*<
+  10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The break magnitude
+  at $z=6$ is very bright, about $-30$, which is why the constraints
+  on the bright end slope at these redshifts are weak.
+
+\item The faint end slope $\beta$ of the luminosity function shows
+  increased steepening at high redshifts, consistent with the findings
+  of \citep{2015AA...578A..83G}.  The faint-end slope is $\beta\sim
+  -1.8$ at $z\sim 2$ and steepens to $\beta\sim-2.5$ at $z\sim 6$.
+  The bright-end slope $\alpha$ also shows moderate steepening towards
+  high redshifts.  However, the constraints on $\alpha$ are weak,
+  particularly at the high redshift because of the bright break
+  luminosity.
+
+\item A fourteen-parameter model accurately captures the redshift
+  evolution of the luminosity function.  In this model, the evolution
+  of the break magnitude $M_*$ is described by a cubic polynomial in
+  $1+z$, while the evolution of the luminosity function amplitude
+  follows a quadratic polynomial in $1+z$.  The evolution of the
+  bright-end slope $\alpha$ evolves linearly in $1+z$.  The evolution
+  of the faint-end slope $\beta$ is more complicated.  The faint-end
+  slope stays roughly constant at lower redshifts $z<3$, steepens
+  rapidly at $z\sim 3$--$4$, and then remains constant at higher
+  redshifts.
+
+\item An important finding of this work is that there are severe
+  systematic errors in observed luminosity function.  We find that the
+  most significant systematic bias is at redshift $z\sim 3$ in the
+  BOSS sample of quasars.  There is also some evidence of a systematic
+  bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$ there is
+  some indication of a systematic error in completeness estimates at
+  the faintest magnitudes $M_{1450}\sim -19$.
+
+\item In spite of the rapid steepening of the luminosity function at
+  high redshifts, our derived LyC emissivity from AGN is quite low.
+  This is because of the bright break luminosities, which results in a
+  reduced contribution of intermediate brightness quasars to the Lyc
+  emissivity as compared to some other determinations in the
+  literature.  The LyC emissivity increases with time and peaks at
+  $z\sim 2$.  At lower redshifts, the emissivity drops rapidly with
+  time.  When our luminoisty function model is extrapolated and
+  integrated down to $M_{1450}\sim -20$, the implied LyC emissivity is
+  comparable to that in the model of \citet{2007ApJ...654..731H} and
+  \citet{2012ApJ...746..125H}.  This indicates that hydrogen
+  reionization is unlikely to have caused by AGN alone.
+
+\item We derive photoionization rate by considering the HI column
+  density distribution used by \citep{2012ApJ...746..125H}.  We find
+  that the HI photoionization rate is significantly lower than that
+  required by the Lyman-$\alpha$ forest data at $z>2$.  Our hydrogen
+  photoionization rate estimates are also considerably lower (by a
+  factor of at least two) than that of \citet{2015AA...578A..83G}.  At
+  the lowest redshifts, we find that the hydrogen photoionization rate
+  is about a factor of two higher than the estimate of
+  \citet{2007ApJ...654..731H} and \citet{2012ApJ...746..125H}.  When
+  compared with the recent analysis of \citet{2017MNRAS.467.3172G},
+  this photoionisation rate appears to allevaite the photon
+  underproduction crisis.  Cite Kollmeier here.
+
+\item Helium reionization in our model occurs at redshift $z\sim
+  3$ or $z=3.5$ if the luminosity function is integrated down to
+  $M_{1450}=-20$ and $-18$, respectively.
+
+\item Our analysis allows us to analyse the X-ray selected quasars of
+  \citet{2015AA...578A..83G} in the larger context of UV-selected
+  quasars.  We find that the the faint-end luminosity function
+  measurements of \citet{2015AA...578A..83G} at $z=4$--$6$ are
+  consitent with the measurements of the luminosity function at
+  brighter luminosities.  Stil, our inferred value of the hydrogen
+  ionizing luminosity density from quasars at these redshifts is much
+  lower that the value derived by \citet{2015AA...578A..83G}.  This
+  difference arises due to the difference in the data used in the two
+  analyses at intermediate to bright luminosities.  
+\end{itemize}
 
@@
 
+% Add an appendix on comparison with Giallongo.
+
 \bibliographystyle{mnras}

### 2018-01-08 selmap.py

@@ -21,7 +21,7 @@ def plot_selmap(z, m, p, title='', filename='selmap.pdf',
     ax.tick_params('both', which='minor', length=3, width=1)
     ax.tick_params('x', which='major', pad=6)
 
-    s = plt.scatter(z, m, s=40, c=p, vmin=0.0, vmax=1.0,
+    s = plt.scatter(z, m, s=100, c=p, vmin=0.0, vmax=1.0,
                     edgecolor='none', marker='s',
                     rasterized=True, cmap=cm.jet)
 
@@ -33,8 +33,8 @@ def plot_selmap(z, m, p, title='', filename='selmap.pdf',
     plt.ylabel('$M_{1450}$')
     plt.title(title, y='1.01')
 
-    plt.xlim(0.0, 3.5)
-    plt.ylim(-30, -14)
+    plt.xlim(2.0, 4.0) 
+    plt.ylim(-30, -20)
 
     divider = make_axes_locatable(ax)
     cax = divider.append_axes("right", "5%", pad="3%")
@@ -45,14 +45,14 @@ def plot_selmap(z, m, p, title='', filename='selmap.pdf',
     plt.savefig(filename, bbox_inches='tight')
 
 
-map_file = 'Data_new/croom09sgp_selfunc.dat'
-qso_file = 'Data_new/croom09sgp_sample.dat'
+map_file = 'Data_new/ross13_selfunc2.dat' # 'Data_new/croom09sgp_selfunc.dat'
+qso_file = 'Data_new/bossdr9color.dat' # 'Data_new/croom09sgp_sample.dat'
 METHOD = 'linear'
 
 with open(map_file, 'r') as f:
     z, m, p = np.loadtxt(f, usecols=(1,2,3), unpack=True)
                          
-plot_selmap(z, m, p, title='2SLAQ SGP', filename='selmap_sgp.pdf',
+plot_selmap(z, m, p, title='BOSS colour-selected', filename='selmap_sgp.pdf',
             show_qsos=False, qso_file=qso_file)
 
 if METHOD == 'spline': 

### 2018-01-22 Paper/paper.tex
Update

@@
 \def\lya{Ly$\alpha$~}
+\usepackage{color}
+\definecolor{notecolor}{rgb}{0.8,0,0}
+\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
 
@@
 
-\section{Homogenised Quasar Sample}
-
-\subsection{Sample Selection}
-
-We started with compiling the samples of recent UV-optical quasar
-surveys. The restriction to UV-optical surveys was mainly driven by
-our science goal to characterise the UV luminosity function of Type~I
-quasars, but also by the still uncertain conversion from X-ray flux to
-UV flux, which adds unnecessary systematics for large
-samples. \textbf{References!} The individual surveys and their main
-characteristics are listed in
-Table~\ref{tab:samples}. Figure~\ref{fig:qsos} presents a redshift
-histogram of the contributing surveys.
-
-We included surveys based on a set of simple criteria:
-\begin{enumerate}
-\item Spectroscopic redshifts for the majority of targets.
-\item Accurate rest-frame UV-optical CCD photometry.
-\item Statistical power (sample size, coverage in $z$ and/or $M_{1450}$).
-\item A characterised selection function.
-\end{enumerate}
-As a prerequisite for a joint analysis of the QLF we obtained the
-survey selection functions in electronic form, either from the
-publication or from the authors. As a reference for future surveys we
-publish them here in modified and homogenised form
-(Section~\ref{sect:datahom}). \textbf{Maybe get the authors' consent.}
-
-Due to their selection criteria and their statistical power specific
-surveys contribute to distinct redshift ranges. At $z<2.2$ we
-considered quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and the 2SLAQ catalogue
-\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to XXX
-$z<2.2$ quasars selected with the final SDSS quasar selection
-algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a
-survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We adopted
-the SDSS targeting photometry corrected for Galactic extinction
-\citep{2010AJ....139.2360S}. To limit systematic uncertainties in the
-correction for host galaxy light \citep{2009MNRAS.392...19C} we
-restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from
-its spectroscopic survey footprint near the North Galactic Pole (NGP,
-XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX
-quasars in $64.2$\,deg$^2$). The small sample overlap between SDSS and
-2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
-
-At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
-colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
-\citep{2013ApJ...773...14R} due to several improvements compared to
-previous surveys. First, it covers a similar magnitude range as 2SLAQ
-but with $>20$ times as many quasars. Second, although the SDSS DR7
-sample provides better coverage of the bright end of the QLF at these
-redshifts, its selection function is highly dependent on the assumed
-incidence of (partial) Lyman limit systems in the IGM
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
-selection function considers these improvements, the uncertainty in
-the QLF remains dominated by assumptions in the selection function
-given the large sample size
-\citep{2013ApJ...773...14R}. Variability-selected quasar samples
-circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
-  2016A&A...587A..41P}, but may be affected by (i) single-epoch
-imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
-and (ii) uncertainties in the selection function caused by the limited
-number of known $z\ga 3$ quasars not selected by variability in the
-same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
-
-At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly
-  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
-survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
-$z>3.7$ limits the impact of systematic uncertainties in the
-\citet{2006AJ....131.2766R} SDSS selection function
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
-the results from surveys for faint $z\sim 4$ quasars in the COSMOS
-field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
-systematic errors in their selection functions\footnote{Both studies
-  simulated quasar colours with a mean IGM attenuation curve
-  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
-  continuum absorption, and therefore underpredicts the variance in
-  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
-    2011ApJ...728...23W}. Modelling the colour variance in these
-  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
-  quasars are near the edge of their colour selection region (see
-  their Figure~1), and \citet{2012ApJ...755..169M} require modest
-  attenuation of the $U$ band flux relative to the mid-infrared
-  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
-COSMOS sample have visually estimated photometric redshifts, and the
-spectroscopic subsample reveals that 40 per cent of the visually
-estimated redshifts are biased low
-($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
-unaccounted systematic redshift errors at least partly explain the
-discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
-and \citet{2012ApJ...755..169M}, which justifies our preference for
-the former sample.
-
-Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly
-selected quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and XX quasars from
-\citet{2011ApJ...728L..26G}. Although we do not include the highly
-debated \citet{2015AA...578A..83G} sample in our main analysis due to
-its rough selection function and lacking spectroscopy for 17 of the 22
-quasar candidates, we use it in Section~XX to constrain the faint end
-($M_{1450}>-23$) of the QLF at $z>4.1$. We restricted the
-\citet{2015AA...578A..83G} sample to the 19/22 sources considered in
-their QLF.
-
-At $4.7\le z<5.1$ we combined several recent surveys, accounting for
-sample overlap and updated selection functions. At the bright end of
-the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} together with its selection function.
-%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit
-%their sample to $z<5.1$ to limit differential evolution of the QLF
-%across the redshift range.
-To avoid double-counting quasars contained both in
-\citet{2016ApJ...829...33Y} and the SDSS DR7 sample from
-\citet{2013ApJ...768..105M}, we used the latter only at
-$M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional
-$4.7\le z<5.1$ quasars selected in 6248\,deg$^2$. We used the updated
-$z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M}
-instead of the one from \citet{2006AJ....131.2766R}.
-%\footnote{We note that the major difference in the selection
-%functions must be due to different input parameters, since the single
-%color selection criterion in \citet{mcgreer} selects the vast
-%majority of the SDSS DR7 quasars.}.
-To these two bright-end samples we added the faint-end sample from the
-\citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly
-selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from
-\citet{2011ApJ...728L..26G}, adopting the respective selection
-functions. We did not consider the limit on the $z\sim 5$ QLF by
-\citet{2012ApJ...756..160I} due to systematic errors in their
-selection function\footnote{\citet{2012ApJ...756..160I} underestimated
-  the dispersion in rest-frame UV quasar colours with respect to SDSS
-  at all redshifts (their Figure~4). Contrary to their claim,
-  photometric errors have a small effect on the colour distribution of
-  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
-  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
-  a relative calibration error of $\sim 1$ per cent
-  \citep{2008ApJ...674.1217P}.}.
-
-The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M
-and L dwarf stars, resulting in a low and uncertain selection
-efficiency \citep{2013ApJ...768..105M}. WISE mid-infrared selection
-performs better \citep{2016ApJ...829...33Y}, but is restricted to the
-bright end of the quasar population. Our combined sample contains the
-remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars
-from the \citet{2013ApJ...768..105M} Stripe~82 survey. As we will show
-in Section~XX, the resulting QLF is consistent with those at lower and
-higher redshifts, indicating that the \citet{2013ApJ...768..105M}
-selection functions are quite reliable. \textbf{Check this!}
-
-Finally, we combined the samples from all spectroscopic $z\sim 6$
-quasar surveys with a determined selection function as of June
-2017. \citet{2016ApJ...833..222J} recently compiled all quasars
-discovered in several SDSS $z\sim 6$ surveys together with
-consistently derived selection functions. Their uniform sample
-consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10
-additional quasars in regions with two or more SDSS imaging scans
-(so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from
-SDSS Stripe~82 (277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W}
-provided a uniform sample of 16 quasars in the Very Wide Survey
-(494\,deg$^2$) and a single quasar in the Deep Survey
-($4.47$\,deg$^2$). The one quasar detected in both SDSS and CFHQS does
-not lead to underestimated statistical errors in the QLF. Lastly, we
-included the two objects from \citet{2015ApJ...798...28K}. One might
-be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line
-(half width at half maximum 427\,km\,s$^{-1}$), but
-\citet{2015ApJ...798...28K} note that 10/17 candidates do not have
-follow-up spectroscopy, hence their QLF may be underestimated. Since
-very small samples preclude a statistical correction via the selection
-function, complete spectroscopic follow-up of $z\sim 6$ candidates is
-essential. Although we will account for the slightly different
-redshift sensitivities for the different surveys, we will quote a
-nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
-
 \begin{figure*}
@@
     \includegraphics[width=\textwidth]{qsos.pdf}
+    % data.py 
   \end{center}
@@
 
-%\clearpage
+\section{Homogenised Quasar Sample}
+
+\subsection{Sample Selection}
+
+We started with compiling the samples of recent UV-optical quasar
+surveys. The restriction to UV-optical surveys was mainly driven by
+our science goal to characterise the UV luminosity function of Type~I
+quasars, but also by the still uncertain conversion from X-ray flux to
+UV flux, which adds unnecessary systematics for large
+samples. \textbf{References!} The individual surveys and their main
+characteristics are listed in
+Table~\ref{tab:samples}. Figure~\ref{fig:qsos} presents a redshift
+histogram of the contributing surveys.
+
+We included surveys based on a set of simple criteria:
+\begin{enumerate}
+\item Spectroscopic redshifts for the majority of targets.
+\item Accurate rest-frame UV-optical CCD photometry.
+\item Statistical power (sample size, coverage in $z$ and/or $M_{1450}$).
+\item A characterised selection function.
+\end{enumerate}
+As a prerequisite for a joint analysis of the QLF we obtained the
+survey selection functions in electronic form, either from the
+publication or from the authors. As a reference for future surveys we
+publish them here in modified and homogenised form
+(Section~\ref{sect:datahom}). \textbf{Maybe get the authors' consent.}
+
+Due to their selection criteria and their statistical power specific
+surveys contribute to distinct redshift ranges. At $z<2.2$ we
+considered quasars from the SDSS DR7 quasar catalogue
+\citep{2010AJ....139.2360S} and the 2SLAQ catalogue
+\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to XXX
+$z<2.2$ quasars selected with the final SDSS quasar selection
+algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a
+survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We adopted
+the SDSS targeting photometry corrected for Galactic extinction
+\citep{2010AJ....139.2360S}. To limit systematic uncertainties in the
+correction for host galaxy light \citep{2009MNRAS.392...19C} we
+restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from
+its spectroscopic survey footprint near the North Galactic Pole (NGP,
+XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX
+quasars in $64.2$\,deg$^2$). The small sample overlap between SDSS and
+2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
+
+At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
+colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
+\citep{2013ApJ...773...14R} due to several improvements compared to
+previous surveys. First, it covers a similar magnitude range as 2SLAQ
+but with $>20$ times as many quasars. Second, although the SDSS DR7
+sample provides better coverage of the bright end of the QLF at these
+redshifts, its selection function is highly dependent on the assumed
+incidence of (partial) Lyman limit systems in the IGM
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
+selection function considers these improvements, the uncertainty in
+the QLF remains dominated by assumptions in the selection function
+given the large sample size
+\citep{2013ApJ...773...14R}. Variability-selected quasar samples
+circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
+  2016A&A...587A..41P}, but may be affected by (i) single-epoch
+imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
+and (ii) uncertainties in the selection function caused by the limited
+number of known $z\ga 3$ quasars not selected by variability in the
+same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
+
+At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly
+  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
+survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
+$z>3.7$ limits the impact of systematic uncertainties in the
+\citet{2006AJ....131.2766R} SDSS selection function
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
+the results from surveys for faint $z\sim 4$ quasars in the COSMOS
+field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
+systematic errors in their selection functions\footnote{Both studies
+  simulated quasar colours with a mean IGM attenuation curve
+  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
+  continuum absorption, and therefore underpredicts the variance in
+  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
+    2011ApJ...728...23W}. Modelling the colour variance in these
+  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
+  quasars are near the edge of their colour selection region (see
+  their Figure~1), and \citet{2012ApJ...755..169M} require modest
+  attenuation of the $U$ band flux relative to the mid-infrared
+  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
+COSMOS sample have visually estimated photometric redshifts, and the
+spectroscopic subsample reveals that 40 per cent of the visually
+estimated redshifts are biased low
+($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
+unaccounted systematic redshift errors at least partly explain the
+discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
+and \citet{2012ApJ...755..169M}, which justifies our preference for
+the former sample.
+
+Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly
+selected quasars from the SDSS DR7 quasar catalogue
+\citep{2010AJ....139.2360S} and XX quasars from
+\citet{2011ApJ...728L..26G}. Although we do not include the highly
+debated \citet{2015AA...578A..83G} sample in our main analysis due to
+its rough selection function and lacking spectroscopy for 17 of the 22
+quasar candidates, we use it in Section~XX to constrain the faint end
+($M_{1450}>-23$) of the QLF at $z>4.1$. We restricted the
+\citet{2015AA...578A..83G} sample to the 19/22 sources considered in
+their QLF.
+
+At $4.7\le z<5.1$ we combined several recent surveys, accounting for
+sample overlap and updated selection functions. At the bright end of
+the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey
+\citep{2016ApJ...829...33Y} together with its selection function.
+%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit
+%their sample to $z<5.1$ to limit differential evolution of the QLF
+%across the redshift range.
+To avoid double-counting quasars contained both in
+\citet{2016ApJ...829...33Y} and the SDSS DR7 sample from
+\citet{2013ApJ...768..105M}, we used the latter only at
+$M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional
+$4.7\le z<5.1$ quasars selected in 6248\,deg$^2$. We used the updated
+$z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M}
+instead of the one from \citet{2006AJ....131.2766R}.
+%\footnote{We note that the major difference in the selection
+%functions must be due to different input parameters, since the single
+%color selection criterion in \citet{mcgreer} selects the vast
+%majority of the SDSS DR7 quasars.}.
+To these two bright-end samples we added the faint-end sample from the
+\citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly
+selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from
+\citet{2011ApJ...728L..26G}, adopting the respective selection
+functions. We did not consider the limit on the $z\sim 5$ QLF by
+\citet{2012ApJ...756..160I} due to systematic errors in their
+selection function\footnote{\citet{2012ApJ...756..160I} underestimated
+  the dispersion in rest-frame UV quasar colours with respect to SDSS
+  at all redshifts (their Figure~4). Contrary to their claim,
+  photometric errors have a small effect on the colour distribution of
+  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
+  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
+  a relative calibration error of $\sim 1$ per cent
+  \citep{2008ApJ...674.1217P}.}.
+
+The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M
+and L dwarf stars, resulting in a low and uncertain selection
+efficiency \citep{2013ApJ...768..105M}. WISE mid-infrared selection
+performs better \citep{2016ApJ...829...33Y}, but is restricted to the
+bright end of the quasar population. Our combined sample contains the
+remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars
+from the \citet{2013ApJ...768..105M} Stripe~82 survey. As we will show
+in Section~XX, the resulting QLF is consistent with those at lower and
+higher redshifts, indicating that the \citet{2013ApJ...768..105M}
+selection functions are quite reliable. \textbf{Check this!}
+
+Finally, we combined the samples from all spectroscopic $z\sim 6$
+quasar surveys with a determined selection function as of June
+2017. \citet{2016ApJ...833..222J} recently compiled all quasars
+discovered in several SDSS $z\sim 6$ surveys together with
+consistently derived selection functions. Their uniform sample
+consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10
+additional quasars in regions with two or more SDSS imaging scans
+(so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from
+SDSS Stripe~82 (277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W}
+provided a uniform sample of 16 quasars in the Very Wide Survey
+(494\,deg$^2$) and a single quasar in the Deep Survey
+($4.47$\,deg$^2$). The one quasar detected in both SDSS and CFHQS does
+not lead to underestimated statistical errors in the QLF. Lastly, we
+included the two objects from \citet{2015ApJ...798...28K}. One might
+be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line
+(half width at half maximum 427\,km\,s$^{-1}$), but
+\citet{2015ApJ...798...28K} note that 10/17 candidates do not have
+follow-up spectroscopy, hence their QLF may be underestimated. Since
+very small samples preclude a statistical correction via the selection
+function, complete spectroscopic follow-up of $z\sim 6$ candidates is
+essential. Although we will account for the slightly different
+redshift sensitivities for the different surveys, we will quote a
+nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
+
 \subsection{Sample Homogenisation}
@@
     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
-    %\includegraphics[height=0.88\textheight,keepaspectratio]{mosaic_small.pdf}
+    % mosaic.py 
   \end{center}
@@
     number of quasars in the bin, before excluding incomplete
-    bins. \textbf{[Remove redshift bins that were excluded from global
-        analysis.]}}
+    bins.}
   \label{fig:mosaic}
@@
   \begin{center}
-    \includegraphics[width=0.7\textwidth]{evol_28sep.pdf}
+    \includegraphics[width=0.7\textwidth]{evolution_individuals.pdf}
+    % summary_fromFile.py 
   \end{center}
@@
     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
+    % mosaic.py 
   \end{center}
@@
   \begin{center}
-    \includegraphics[width=0.7\textwidth]{evolution_global_9oct.pdf}
+    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
+    % summary_fromFile.py 
   \end{center}
@@
     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+    % rhoqso.py -- draw_withGlobal()
   \end{center}
@@
     fit global model, and the coloured curves show a random sample
-    drawn from the global posterior.  \textbf{[Show rejected bins in
-        differnt symbols here.  Do not show the $-18$ case.  Cut the
-        figure off at 6.5.]}}
+    drawn from the global posterior. \gk{I still think we should show
+      the $-18$ case here.}}
   \label{fig:rhoqso}
@@
     \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{emissivity_18_9oct.pdf}
-    \includegraphics[width=0.5\textwidth]{emissivity_20_9oct.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity_21.pdf}
+    % gammapi.py -- draw_emissivity() 
     \end{tabular}
@@
 
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\textwidth]{g_18.pdf}
+    \includegraphics[width=0.5\textwidth]{g_21.pdf}
+    \end{tabular}
+  \end{center}
+  \caption{AGN contribution to the hydrogen photoionisation rate,
+    assuming 100\% escape fraction.  Model luminosity functions are
+    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
+    the right panel.  The solid black curve shows the hydrogen
+    photoionisate rate in our best-fit global model, and the yellow
+    curves show a random sample from the global posterior.  The red
+    points with error bars in this figure show the measurements of
+    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
+    forest, and the orange points show the measurements by
+    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
+    dashed green curve shows the hydrogen photoionisation rate
+    evolution in the model of \citet{2012ApJ...746..125H}, while the
+    solid green curve shows the contribution of quasars to it. \gk{Two
+      problems to be addressed in these plots: (a) there is a
+      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
+      but because our emissivity diverges at $z>7$, I had a to put an
+      arbitrary cut-off; (b) the plots are too messy; we probably
+      should show fewer things.}}
+  \label{fig:gammapi}
+\end{figure*}
+
 The 1~Ry emissivity can now be used to calculate the ionizing flux and
@@
 large distances.
-
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{g_18_10oct.pdf}
-    \includegraphics[width=0.5\textwidth]{g_20_10oct.pdf}
-    \end{tabular}
-  \end{center}
-  \caption{AGN contribution to the hydrogen photoionisation rate,
-    assuming 100\% escape fraction.  Model luminosity functions are
-    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
-    the right panel.  The solid black curve shows the hydrogen
-    photoionisate rate in our best-fit global model, and the yellow
-    curves show a random sample from the global posterior.  The red
-    points with error bars in this figure show the measurements of
-    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
-    forest, and the orange points show the measurements by
-    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
-    dashed green curve shows the hydrogen photoionisation rate
-    evolution in the model of \citet{2012ApJ...746..125H}, while the
-    solid green curve shows the contribution of quasars to it. }
-  \label{fig:gammapi}
-\end{figure*}
 
@@
   \end{center}
-  \caption{Photon underproduction crisis.}
+  \caption{Photon underproduction crisis.\label{fig:puc}}
 \end{figure}
@@
 
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal_dense.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff_ind.pdf}
+%%   \end{center}
+%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
+%% \end{figure}
+
+\section{Hydrogen and helium reionization}
+
+\section{Photon underproduction}
+
+Our derivation of the LyC emissivity of AGN allows us to see if the
+corresponding hydrogen photoionization rate is consistent with the
+measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
+\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
+in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
+% Define acronym CDDF.
+these redshifts, hydrodynamical cosmological simulations require a
+hydrogen photoionization rate that is a factor of five larger than
+that in the UV background (UVB) model of \citet{2012ApJ...746..125H}.
+% This factor looks more than five in our plot!
+Several recent studies in the literature have addressed this ``photon
+underproduction crisis''.  On the one hand, these studies emphasised
+the uncertainty in the \citet{2012ApJ...746..125H} UVB model at these
+redshifts due to the lack of certainty in the UV photon emissivities
+of galaxies and AGN \citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.
+On the other hand, they noted the uncertainty in the results of the
+cosmological simulations at these redshifts, due to effects such as
+AGN feedback and limited numerical resolution
+\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
+  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
+  2017ApJ...835..175G}.  A general conclusion of these studies was
+that the discrepancy between the photoionization rate required by the
+observed CDDF and predicted by the UVB model of
+\citet{2012ApJ...746..125H} is likely to be smaller than that found by
+\citet{2014ApJ...789L..32K}.  The discrepancy is about a factor of 2
+instead of 5.
+
+The black curve in Figure~\ref{fig:puc} shows the evolution of the
+hydrogen photoionization rate due to AGN in our best-fit global
+luminosity function model.  (Yellow shaded region around the black
+curve shows the small 68\% uncertainty.)  We find that the
+photoionisation rate in our model due to AGN alone is higher than that
+in the \citet{2012ApJ...746..125H} UVB model by a factor of 2.  This
+higher photoionisation rate is consistent with that derived by
+\citet{2015MNRAS.451L..30K} using the quasar luminosity function
+measurements of \citet{2009MNRAS.392...19C} and
+\citet{2013A&A...551A..29P}.  It is also consistent with the
+photoionization rate found by \citet{2017MNRAS.467.3172G}, who found
+that this photoionisation rate is sufficient to explain the CDDF
+measured by \citet{2016ApJ...817..111D}.
+
 \begin{figure}
@@
 
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal_dense.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff_ind.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
-
-\section{Hydrogen and helium reionization}
-
-\section{Photon underproduction}
-
-\citet{2014ApJ...789L..32K} reported that the hydrogen photoionization
-rate required by simulations to match the observed HI column density
-distribution and the effective Ly$\alpha$ opacity at low redshifts
-($z\sim 0.1$) is a factor of five (check factor---it looks like about
-ten in the plot) higher than that predicted by the model of
-\citep{2012ApJ...746..125H}.  This deficit in the hydrogen
-photoionization rate at these redshifts, termed `photon
-underproduction crisis', has inspired models in which the excess
-photonization in explained by blazars (citation) or an evolution in
-the density structure of the IGM.  Subsequent simulations by
-\citet{2015ApJ...811....3S}, calibrated the observed HI column density
-distribution and the effective Ly$\alpha$ optical depth reduced the
-severity of the problem by
-
-\section{Conclusion}
+\section{Conclusions}
 

### 2018-02-22 Paper/paper.tex
Update

@@
 \newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
+\def\HI{\hbox{H~$\scriptstyle\rm I$}}
+\def\HII{\hbox{H~$\scriptstyle\rm II$}}
+\def\nHI{{\rm HI}}
+\def\nH{{\rm H}}
+\def\nHII{{\rm HII}}
+\def\nHe{{\rm He}}
+\def\nHeI{{\rm HeI}}
+\def\nHeII{{\rm HeII}}
+\def\nHeIII{{\rm HeIII}}
+\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
+\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
+\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
+\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
+\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
+\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
 
@@
 
+We now consider the implications for hydrogen and helium reionization
+for the ionizing photon emissivity derived above.  This requires that
+we extrapolate the emissivity of Equation XX to higher redshifts.
+Unfortunately, the volume emissivity in our model cannot be
+extrapolated to higher redshifts.  The model of Hopkins suffered with
+the same problem.  \gk{Do we need to show two cases here?  One in
+  which we extrapolate the emissivity and another in which we stop
+  where data end.  There is perhaps a third possibility in which use
+  the current emissivity model upto where data end.}  The evolution of
+the volume averaged ionized fraction of hydrogen is given by
+\citep{2012ApJ...746..125H}
+\begin{equation}
+{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
+\langle t_{\rm rec}\rangle},
+\label{eq:qdot}
+\end{equation}
+and the corresponding equation doubly ionized Helium is
+\begin{equation}
+{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
+\langle t_{\rm rec,He}\rangle}.
+\label{eq:qHedot}
+\end{equation}
+We assume that the Helium is singly reionized together with hydrogen.
+In order to get the 4~Ry emissivity of quasars we use the SED from
+equation XX.  The recombination times are given by
+\begin{equation}
+\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
+\label{eq:trec}
+\end{equation}
+where $n$ is the volume averaged density of hydrogen and helium,
+respectively.  We assume that hydrogen and helium have similar
+clumping factors, given by \citep{2015ApJ...813L...8M}
+\begin{equation}
+  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
+\end{equation}
+For the helium recombination coeffienct, we use the fitting function
+provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
+coefficient, we use the fitting function provided by
+\citet{2011piim.book.....D}.
+
+The resultant reionization histories of hydrogen and helium are shown
+in Figure XX.  We also show the reionization histories from
+\citep{2012ApJ...746..125H} and \citep{2015ApJ...813L...8M} for
+comparison.  As expected from the emissivity result of the previous
+section, quasars cannot single handedly reionize hydrogen.  However
+they can reionise \HeII.  The Helium reionization completes at
+redshift $z=3.5$--$3.7$ depending on the luminosity down to which you
+integrate the quasar luminosity function.  This is consistent with the
+Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.
+
 \section{Photon underproduction}
@@
 in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
-% Define acronym CDDF.
-these redshifts, hydrodynamical cosmological simulations require a
-hydrogen photoionization rate that is a factor of five larger than
-that in the UV background (UVB) model of \citet{2012ApJ...746..125H}.
-% This factor looks more than five in our plot!
-Several recent studies in the literature have addressed this ``photon
-underproduction crisis''.  On the one hand, these studies emphasised
-the uncertainty in the \citet{2012ApJ...746..125H} UVB model at these
-redshifts due to the lack of certainty in the UV photon emissivities
-of galaxies and AGN \citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.
-On the other hand, they noted the uncertainty in the results of the
-cosmological simulations at these redshifts, due to effects such as
-AGN feedback and limited numerical resolution
-\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
-  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
-  2017ApJ...835..175G}.  A general conclusion of these studies was
-that the discrepancy between the photoionization rate required by the
-observed CDDF and predicted by the UVB model of
-\citet{2012ApJ...746..125H} is likely to be smaller than that found by
-\citet{2014ApJ...789L..32K}.  The discrepancy is about a factor of 2
-instead of 5.
+\gk{Define acronym CDDF.}  these redshifts, hydrodynamical
+cosmological simulations require a hydrogen photoionization rate that
+is a factor of five larger than that in the UV background (UVB) model
+of \citet{2012ApJ...746..125H}.  \gk{This factor looks more than five
+  in our plot!}  Several recent studies in the literature have
+addressed this ``photon underproduction crisis''.  On the one hand,
+these studies emphasised the uncertainty in the
+\citet{2012ApJ...746..125H} UVB model at these redshifts due to the
+lack of certainty in the UV photon emissivities of galaxies and AGN
+\citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.  On the other hand,
+they noted the uncertainty in the results of the cosmological
+simulations at these redshifts, due to effects such as AGN feedback
+and limited numerical resolution \citep{2015ApJ...811....3S,
+  2017MNRAS.467L..86V, 2017MNRAS.471.1056N, 2017ApJ...837..106O,
+  2017MNRAS.466..838G, 2017MNRAS.467.3172G, 2017ApJ...835..175G}.  A
+general conclusion of these studies was that the discrepancy between
+the photoionization rate required by the observed CDDF and predicted
+by the UVB model of \citet{2012ApJ...746..125H} is likely to be
+smaller than that found by \citet{2014ApJ...789L..32K}.  The
+discrepancy is about a factor of 2 instead of 5.
 
@@
 
-% Add an appendix on comparison with Giallongo.
+\appendix
+
+\section{Comparison with Giallongo sample}
+\label{sec:conv}
+
+In our analysis above, we did not include the 22 low-luminosity
+($M_{1450}>-22.6$) AGN between redshifts $z=4.1$ and $6.3$ reported by
+\citet{2015AA...578A..83G} using a novel X-ray/NIR selection
+criterion.  This was because we wanted to restrict our sample to
+quasars that have robust spectroscopic redshift determinations.  In
+their work, \citet{2015AA...578A..83G} found a steep faint-end of the
+luminosity function at these redshifts.  With this luminosity function
+they obtained a large value of hydrogen ionizing emissivity that could
+explain the \lya data singlehandedly.  In this section, we compare our
+results with \citet{2015AA...578A..83G}.  The black points in Figure
+XX show the parameters of the double power law luminosity function
+when the \citet{2015AA...578A..83G} sample is added to our analysis.
+The parameter values do not change significantly.  The
+\citet{2015AA...578A..83G} sample is thus consistent with the double
+power law luminosity function preferred by other data at comparable
+redshifts.  However, as we see in Figure XX, the total emissivity in
+our model is still significantly lower than that obtained by
+\citet{2015AA...578A..83G}.  Figure XX provides an explanation for
+this. The double power law fits favoured by \citet{2015AA...578A..83G}
+are quite different from our fits.  The character luminosity $M_*$
+favoured by \citet{2015AA...578A..83G} is much fainter ($\sim -23$ at
+$z = 5$) than that resulting out of our analysis ($\sim -29$ at $z =
+5$).  Figure XX suggests that this is because of the SDSS Stripe 82
+data \gk{citation} and because \citet{2015AA...578A..83G} ignore the
+Kashikawa and Willott samples \gk{citation}.  It is possible that our
+corrections to the Glikman data \gk{citation} also plays a role in
+this.  In sum, the differnce in our emissivities is not due to lack of
+faint quasars but because of the difference with Giallongo at
+intermediate luminosities.
 

### 2018-02-22 composite.py
Model 26

@@ -183,18 +183,15 @@ class lf:
 
         """Redshift evolution of QLF parameters."""
         
-        # return T(p)(np.log10(1+z))
         return T(p)(1+z)
-
+    
     def atz_beta(self, z, p):
 
         """Redshift evolution of QLF parameters."""
 
-        return T(p)(1+z)
-        
-        # h, f0, z0, a, b = p 
-        # zeta = np.log10((1.0+z)/(1.0+z0))
-        # return h + f0/(10.0**(a*zeta) + 10.0**(b*zeta))
+        h, f0, z0, a, b = p 
+        zeta = np.log10((1.0+z)/(1.0+z0))
+        return h + f0/(10.0**(a*zeta) + 10.0**(b*zeta))
 
     def getparams(self, theta):
 
@@ -216,8 +213,8 @@ class lf:
         log10phi_star = self.atz(z, params[0])
         M_star = self.atz(z, params[1])
         alpha = self.atz(z, params[2])
-        # beta = self.atz(z, params[3])
-        beta = self.atz_beta(z, params[3])
+        beta = self.atz(z, params[3])
+        # beta = self.atz_beta(z, params[3])
         
         phi = 10.0**log10phi_star / (10.0**(0.4*(alpha+1)*(mag-M_star)) +
                                      10.0**(0.4*(beta+1)*(mag-M_star)))

### 2018-02-22 lfg.py

@@ -6,7 +6,7 @@ from summary_fromFile import summary_plot as sp
 qlumfiles = ['Data_new/dr7z2p2_sample.dat',
              'Data_new/croom09sgp_sample.dat',
              'Data_new/croom09ngp_sample.dat',
-           # 'Data_new/bossdr9color.dat',
+            #'Data_new/bossdr9color.dat',
              'Data_new/dr7z3p7_sample.dat',
              'Data_new/glikman11debug.dat',
              'Data_new/yang16_sample.dat',
@@ -19,15 +19,15 @@ qlumfiles = ['Data_new/dr7z2p2_sample.dat',
              'Data_new/jiang16s82_sample.dat',
              'Data_new/willott10_cfhqsdeepsample.dat',
              'Data_new/willott10_cfhqsvwsample.dat',
-             'Data_new/kashikawa15_sample.dat',
+             'Data_new/kashikawa15_sample.dat']
              #'Data_new/giallongo15_sample.dat',
-             'Data_new/ukidss_sample.dat',
-             'Data_new/banados_sample.dat']
+             #'Data_new/ukidss_sample.dat',
+             #'Data_new/banados_sample.dat']
 
 selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/croom09sgp_selfunc.dat', 0.3, 0.05, 64.2, 15),
              ('Data_new/croom09ngp_selfunc.dat', 0.3, 0.05, 127.7, 15),
-           # ('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1),
+            #('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1),
              ('Data_new/dr7z3p7_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/glikman11_selfunc_ndwfs.dat', 0.05, 0.02, 1.71, 6),
              ('Data_new/glikman11_selfunc_dls.dat', 0.05, 0.02, 2.05, 6),
@@ -39,12 +39,12 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              ('Data_new/jiang16s82_selfunc.dat', 0.1, 0.05, 277.0, 18),
[…]

### 2018-02-22 summary_fromFile.py

@@ -177,6 +177,7 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False):
 
     if compOpt is not None:
         M = compOpt.atz(z, compOpt.getparams(compOpt.bf.x)[1])
+        print M
         ax.plot(z, M, color='g', zorder=2, dashes=[7,2])
 
     if composite is not None:
@@ -201,6 +202,27 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False):
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color=colors[1], edgecolor='None', zorder=6, s=40)
 
+    # zm, cm, uperr, downerr = np.loadtxt('Data/manti.txt',
+    #                                     usecols=(0,4,5,6), unpack=True)
+    # ax.errorbar(zm, cm, ecolor='grey', capsize=0,
+    #             yerr=np.vstack((uperr, downerr)),
+    #             fmt='None', zorder=4)
+    # ax.scatter(zm, cm, color='#ffffff', edgecolor='grey', zorder=4, s=30)
+
+    if cfit:
+        zc = np.linspace(0, 7, 500)
+        coeffs = chebfit(zmean+1, c, 2)
+        print coeffs
+        # plt.plot(zc, T(coeffs)(zc+1), lw=1, c='k', dashes=[7,2], zorder=3) 
+
+        def func(z, p0, p1, p2):
+            return T([p0, p1, p2])(z)
+
+        sigma = np.abs(u-l)
+        popt, pcov = curve_fit(func, zmean+1, c, sigma=sigma, p0=[coeffs])
+        print popt
+        plt.plot(zc, func(zc+1, *popt), lw=1, c='k', dashes=[7,2])
+
     zmean, zl, zu, u, l, c = getParam(individuals, 1, which='new', dtype='bad')
     left = zmean-zl
     right = zu-zmean
@@ -212,27 +234,6 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False):
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color='#ffffff', edgecolor=colors[1], zorder=6, s=35)
         
-    # zm, cm, uperr, downerr = np.loadtxt('Data/manti.txt',
-    #                                     usecols=(0,4,5,6), unpack=True)
-    # ax.errorbar(zm, cm, ecolor='grey', capsize=0,
-    #             yerr=np.vstack((uperr, downerr)),
[…]

### 2018-02-22 lfg.py
Model 27

@@ -44,7 +44,7 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              #('Data_new/ukidss_sel_3.dat', 0.1, 0.1, 3370.0, 19),
              #('Data_new/banados_sel_3.dat', 0.1, 0.1, 2500.0, 20)]
 
-case = 7
+case = 8
 
 if case == 0:
 
@@ -222,6 +222,19 @@ elif case == 7:
 
     g = np.array([-7.95061036, 1.15284665, -0.12037541,
                   -18.64592897, -4.52638114, 0.47207865, -0.01890026,
+                  -4.28592068, 1.13320416, -0.14003202, 
+                  -1.60670033, -0.02759287, -0.00685381])
+
+    method = 'Nelder-Mead'
+    b = lfg.bestfit(g, method=method)
+    print b
+
+elif case == 8:
+
+    lfg = lf(quasar_files=qlumfiles, selection_maps=selnfiles, pnum=[3,3,3,3])
+
+    g = np.array([-7.95061036, 1.15284665, -0.12037541,
+                  -22.58743676,  -1.20805348,   0.02333263,
                   -4.28592068, 1.13320416, -0.14003202, 
                   -1.60670033, -0.02759287, -0.00685381])
 

### 2018-02-22 summary_fromFile.py

@@ -209,10 +209,11 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False):
     #             fmt='None', zorder=4)
     # ax.scatter(zm, cm, color='#ffffff', edgecolor='grey', zorder=4, s=30)
 
+    cfit = True
     if cfit:
         zc = np.linspace(0, 7, 500)
         coeffs = chebfit(zmean+1, c, 2)
-        print coeffs
+        print 'cm=', coeffs
         # plt.plot(zc, T(coeffs)(zc+1), lw=1, c='k', dashes=[7,2], zorder=3) 
 
         def func(z, p0, p1, p2):

### 2018-02-23 lfg.py
Model 28

@@ -44,7 +44,7 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
              #('Data_new/ukidss_sel_3.dat', 0.1, 0.1, 3370.0, 19),
              #('Data_new/banados_sel_3.dat', 0.1, 0.1, 2500.0, 20)]
 
-case = 8
+case = 9
 
 if case == 0:
 
@@ -242,3 +242,35 @@ elif case == 8:
     b = lfg.bestfit(g, method=method)
     print b
 
+elif case == 8:
+
+    lfg = lf(quasar_files=qlumfiles, selection_maps=selnfiles, pnum=[3,2,3,3])
+
+    g = np.array([-7.95061036, 1.15284665, -0.12037541,
+                  -23.26763262,  -0.81679979,
+                  -4.28592068, 1.13320416, -0.14003202, 
+                  -1.60670033, -0.02759287, -0.00685381])
+
+    method = 'Nelder-Mead'
+    b = lfg.bestfit(g, method=method)
+    print b
+    
+elif case == 9:
+
+    lfg = lf(quasar_files=qlumfiles, selection_maps=selnfiles, pnum=[3,4,2,4])
+
+    g = np.array([-7.95061036, 1.15284665, -0.12037541,
+                  -18.64592897, -4.52638114, 0.47207865, -0.01890026,
+                  -3.35945526, -0.26211017,
+                  -2.19480099,  0.46906026, -0.07710908,  0.00297377])
+
+    method = 'Nelder-Mead'
+    b = lfg.bestfit(g, method=method)
+    print b
+
+array([ -7.89387141e+00,   1.24961557e+00,  -1.34104043e-01,   -1.62092084e+01,  -6.37733322e+00,   7.42609597e-01,     -3.23535832e-02,  -3.29121546e+00,  -2.30686425e-01,    -3.03009759e+00,   1.15077979e+00,  -1.62317962e-01,         6.23585369e-03])    
+    
+    lfg.prior_min_values = np.array([-10, 0, -5, -20, -10, 0, -2, -7, -5, -10, -10, -10, -10])
+    lfg.prior_max_values = np.array([-2, 10, 5, -10, -1, 2, 2, -1, 5, 10, 10, 10, 10])
+    assert(np.all(lfg.prior_min_values < lfg.prior_max_values))
+    lfg.run_mcmc()

### 2018-02-23 summary_fromFile.py

@@ -212,12 +212,12 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False):
     cfit = True
     if cfit:
         zc = np.linspace(0, 7, 500)
-        coeffs = chebfit(zmean+1, c, 2)
+        coeffs = chebfit(zmean+1, c, 1)
         print 'cm=', coeffs
         # plt.plot(zc, T(coeffs)(zc+1), lw=1, c='k', dashes=[7,2], zorder=3) 
 
-        def func(z, p0, p1, p2):
-            return T([p0, p1, p2])(z)
+        def func(z, p0, p1):
+            return T([p0, p1])(z)
 
         sigma = np.abs(u-l)
         popt, pcov = curve_fit(func, zmean+1, c, sigma=sigma, p0=[coeffs])
@@ -399,16 +399,16 @@ def plot_beta(fig, composite, individuals=None, compOpt=None, sample=False):
     cfit = True
     if cfit:
         zc = np.linspace(0, 7, 500)
-        coeffs = chebfit(zmean+1, c, 2)
+        coeffs = chebfit(zmean+1, c, 3)
         print coeffs
         # plt.plot(zc, T(coeffs)(zc+1), lw=1, c='k', dashes=[7,2], zorder=3)
 
-        def func(z, p0, p1, p2):
-                return T([p0, p1, p2])(z)
+        def func(z, p0, p1, p2, p3):
+                return T([p0, p1, p2, p3])(z)
 
         sigma = u - l 
         popt, pcov = curve_fit(func, zmean+1, c, sigma=sigma, p0=[coeffs])
-        print popt
+        print 'cb=', popt
         plt.plot(zc, func(zc+1, *popt), lw=1, c='r', dashes=[7,2])
 
     polyfit = False

### 2018-03-06 Paper/paper.tex
Add Table 2

@@
     21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
+    \hline
   \end{tabular}
@@
 
+\begin{table*}
+  % bins_tabulate.py; Nqso added by hand
+  \caption{Best-fit double power law luminosity function parameters in
+    various redshift bins.  The luminosity function parameters
+    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
+    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
+    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
+    z_\mathrm{max}$.  The number of quasars in each bin is given by
+    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
+    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
+    Errors indicate one-sigma (68.26\%) uncertainties.  These values
+    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
+    functions are shown in Figure~\ref{fig:mosaic}.  See
+    Section~\ref{sec:bins} for further details.}
+  \label{tab:bins}
+  \begin{tabular}{ccccrcccc}
+    \hline
+    $\langle z\rangle$ & $z_\mathrm{bin}$ & $z_\mathrm{min}$ & $z_\mathrm{max}$ & $N_\mathrm{qso}$ & $\log_{10}(\phi_*/$ & $M_*$ & $\alpha$ & $\beta$ \\
+    & & & & & cMpc$^{-3}$mag$^{-1}$) & & & \\
+    \hline
+    $0.31$ & $0.25$ & $0.10$ & $0.40$ & 3520 & $-5.62^{+0.09}_{-0.10}$ & $-21.37^{+0.21}_{-0.22}$ & $-2.94^{+0.09}_{-0.10}$ & $-1.22^{+0.18}_{-0.16}$ \\
+    $0.50$ & $0.50$ & $0.40$ & $0.60$ & 4555 & $-6.12^{+0.04}_{-0.04}$ & $-23.00^{+0.08}_{-0.08}$ & $-3.37^{+0.07}_{-0.08}$ & $-1.36^{+0.04}_{-0.04}$ \\
+    $0.72$ & $0.70$ & $0.60$ & $0.80$ & 3308 & $-6.42^{+0.09}_{-0.08}$ & $-24.03^{+0.15}_{-0.13}$ & $-3.55^{+0.12}_{-0.13}$ & $-1.75^{+0.05}_{-0.04}$ \\
+    $0.91$ & $0.90$ & $0.80$ & $1.00$ & 3922 & $-6.39^{+0.08}_{-0.07}$ & $-24.51^{+0.12}_{-0.11}$ & $-3.69^{+0.10}_{-0.11}$ & $-1.73^{+0.06}_{-0.05}$ \\
+    $1.10$ & $1.10$ & $1.00$ & $1.20$ & 6367 & $-6.53^{+0.03}_{-0.03}$ & $-25.14^{+0.04}_{-0.04}$ & $-4.17^{+0.08}_{-0.09}$ & $-1.73^{+0.02}_{-0.02}$ \\
+    $1.30$ & $1.30$ & $1.20$ & $1.40$ & 6479 & $-6.43^{+0.04}_{-0.04}$ & $-25.29^{+0.06}_{-0.06}$ & $-3.97^{+0.08}_{-0.08}$ & $-1.74^{+0.03}_{-0.03}$ \\
+    $1.50$ & $1.50$ & $1.40$ & $1.60$ & 7539 & $-6.51^{+0.03}_{-0.03}$ & $-25.68^{+0.04}_{-0.04}$ & $-4.28^{+0.08}_{-0.08}$ & $-1.75^{+0.02}_{-0.02}$ \\
+    $1.71$ & $1.70$ & $1.60$ & $1.80$ & 6788 & $-6.28^{+0.04}_{-0.04}$ & $-25.55^{+0.05}_{-0.05}$ & $-3.96^{+0.07}_{-0.07}$ & $-1.60^{+0.03}_{-0.03}$ \\
+    $1.98$ & $2.00$ & $1.80$ & $2.20$ & 10478 & $-6.72^{+0.03}_{-0.03}$ & $-26.26^{+0.04}_{-0.04}$ & $-4.20^{+0.07}_{-0.07}$ & $-1.87^{+0.02}_{-0.02}$ \\
+    $2.25$ & $2.25$ & $2.20$ & $2.30$ & 4102 & $-5.98^{+0.10}_{-0.09}$ & $-25.26^{+0.19}_{-0.18}$ & $-3.21^{+0.15}_{-0.16}$ & $-1.54^{+0.07}_{-0.06}$ \\
+    $2.35$ & $2.35$ & $2.30$ & $2.40$ & 4317 & $-6.28^{+0.09}_{-0.09}$ & $-25.63^{+0.17}_{-0.15}$ & $-3.39^{+0.17}_{-0.19}$ & $-1.64^{+0.06}_{-0.05}$ \\
+    $2.45$ & $2.45$ & $2.40$ & $2.50$ & 3403 & $-6.40^{+0.08}_{-0.07}$ & $-25.86^{+0.14}_{-0.13}$ & $-3.60^{+0.20}_{-0.21}$ & $-1.60^{+0.05}_{-0.05}$ \\
+    $2.65$ & $2.65$ & $2.60$ & $2.70$ & 1883 & $-5.98^{+0.06}_{-0.06}$ & $-25.15^{+0.14}_{-0.13}$ & $-3.13^{+0.12}_{-0.13}$ & $-1.05^{+0.09}_{-0.08}$ \\
+    $2.75$ & $2.75$ & $2.70$ & $2.80$ & 1135 & $-6.30^{+0.08}_{-0.07}$ & $-25.96^{+0.15}_{-0.13}$ & $-3.81^{+0.28}_{-0.31}$ & $-1.34^{+0.07}_{-0.06}$ \\
+    $2.85$ & $2.85$ & $2.80$ & $2.90$ & 1069 & $-6.46^{+0.12}_{-0.10}$ & $-26.23^{+0.23}_{-0.18}$ & $-3.60^{+0.36}_{-0.42}$ & $-1.46^{+0.08}_{-0.07}$ \\
+    $2.95$ & $2.95$ & $2.90$ & $3.00$ & 1104 & $-6.77^{+0.07}_{-0.06}$ & $-26.53^{+0.10}_{-0.09}$ & $-5.05^{+0.60}_{-0.64}$ & $-1.71^{+0.05}_{-0.04}$ \\
+    $3.05$ & $3.05$ & $3.00$ & $3.10$ & 1127 & $-6.77^{+0.08}_{-0.07}$ & $-26.48^{+0.12}_{-0.10}$ & $-4.71^{+0.46}_{-0.52}$ & $-1.70^{+0.06}_{-0.05}$ \\
+    $3.15$ & $3.15$ & $3.10$ & $3.20$ & 1041 & $-7.25^{+0.17}_{-0.12}$ & $-27.09^{+0.25}_{-0.18}$ & $-4.42^{+0.81}_{-1.23}$ & $-1.96^{+0.08}_{-0.06}$ \\
+    $3.25$ & $3.25$ & $3.20$ & $3.30$ & 815 & $-7.33^{+0.13}_{-0.13}$ & $-27.19^{+0.19}_{-0.23}$ & $-4.36^{+0.65}_{-0.76}$ & $-1.93^{+0.06}_{-0.06}$ \\
+    $3.34$ & $3.35$ & $3.30$ & $3.40$ & 510 & $-7.54^{+0.19}_{-0.21}$ & $-27.39^{+0.25}_{-0.37}$ & $-4.90^{+1.36}_{-1.35}$ & $-2.08^{+0.09}_{-0.07}$ \\
+    $3.44$ & $3.45$ & $3.40$ & $3.50$ & 155 & $-6.77^{+0.19}_{-0.20}$ & $-26.64^{+0.42}_{-0.35}$ & $-3.70^{+0.62}_{-0.80}$ & $-1.24^{+0.27}_{-0.22}$ \\
+    $3.88$ & $3.90$ & $3.70$ & $4.10$ & 628 & $-7.92^{+0.12}_{-0.10}$ & $-27.26^{+0.14}_{-0.12}$ & $-4.81^{+0.34}_{-0.39}$ & $-2.07^{+0.10}_{-0.09}$ \\
+    $4.35$ & $4.40$ & $4.10$ & $4.70$ & 442 & $-8.32^{+0.29}_{-0.26}$ & $-27.38^{+0.38}_{-0.31}$ & $-4.19^{+0.41}_{-0.47}$ & $-2.20^{+0.16}_{-0.13}$ \\
+    $4.92$ & $5.10$ & $4.70$ & $5.50$ & 263 & $-9.02^{+0.29}_{-0.22}$ & $-27.88^{+0.36}_{-0.27}$ & $-4.51^{+0.66}_{-0.83}$ & $-2.31^{+0.11}_{-0.08}$ \\
+    $6.00$ & $6.00$ & $5.50$ & $6.50$ & 66 & $-10.60^{+0.71}_{-1.06}$ & $-29.12^{+1.04}_{-1.78}$ & $-4.99^{+0.72}_{-1.22}$ & $-2.40^{+0.10}_{-0.08}$ \\
+    \hline
+  \end{tabular}
+\end{table*}
+
 \subsection{Luminosity function estimates in redshift bins}
+\label{sec:bins}
 
@@
 \end{document}
+
+%% Tables:
+%% Individual fit results
+%% Global models best fit parameters
+%% Emissivity (H and He)
+%% Photoionization rates (H and He)
+%%

### 2018-03-06 Paper/paper.tex
Update

@@
     shows the best fit global model, and the coloured curves show a
-    random sample drawn from the global posterior.}
+    random sample drawn from the global posterior. \gk{Cannot see
+      best-fit curves.  Add open and closed circles to legend.}}
   \label{fig:evoln_global}
@@
     drawn from the global posterior. \gk{I still think we should show
-      the $-18$ case here.}}
+      the $-18$ case here.  Mention magnitude limits.  Reduce
+      transarency.  Extend plot to at least redshift 7.5.  Increase
+      legend handle length to match other figure.}}
   \label{fig:rhoqso}
@@
 
-\begin{figure*}
+\begin{figure}
   \begin{center}
     \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
-    \includegraphics[width=0.5\textwidth]{emissivity_21.pdf}
+    \includegraphics[width=0.5\textwidth]{emissivity.pdf}
     % gammapi.py -- draw_emissivity() 
@@
     \citet{2017MNRAS.466.1160M}.  The green curve is the model of
-    \citet{2015ApJ...813L...8M}.}
+    \citet{2015ApJ...813L...8M}. \gk{Add uncertainties on these fits,
+      perhaps by using emcee.}}
   \label{fig:e912}
-\end{figure*}
+\end{figure}
 
@@
 
-% Add a table for the best fit parameter values?
+\begin{table}
+  \caption{Best-fit luminosity function evolution models.  These
+    parameters are defined in Equations XX.  See Section XX for
+    further details and the redshift range of validity of these
+    models.  Errors indicate one-sigma (68.26\%) uncertainties.  Model
+    2 is our preferred model.}
+  \label{tab:global}
+  \begin{tabular}{lrrr}
+    \hline 
+    Parameter & Model 1 & Model 2 & Model 3 \\
+    \hline
+    $c_{0,0}$ & $-7.559^{+0.131}_{-0.139}$ & $-7.084^{+0.136}_{-0.142}$ & $-6.842^{+0.077}_{-0.076}$ \\     
+    $c_{0,1}$ & $1.013^{+0.079}_{-0.072}$ & $0.753^{+0.080}_{-0.073}$ & $0.590^{+0.039}_{-0.041}$ \\        
+    $c_{0,2}$ & $-0.113^{+0.005}_{-0.005}$ & $-0.096^{+0.004}_{-0.005}$ & $-0.083^{+0.003}_{-0.003}$ \\
+    \\
+    $c_{1,0}$ & $-17.006^{+0.230}_{-0.243}$ & $-15.423^{+0.263}_{-0.261}$ & $-15.140^{+0.144}_{-0.136}$ \\  
+    $c_{1,1}$ & $-5.548^{+0.156}_{-0.143}$ & $-6.725^{+0.156}_{-0.171}$ & $-6.910^{+0.091}_{-0.093}$ \\     
+    $c_{1,2}$ & $0.588^{+0.016}_{-0.019}$ & $0.737^{+0.018}_{-0.015}$ & $0.750^{+0.012}_{-0.013}$ \\        
+    $c_{1,3}$ & $-0.023^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ \\
+    \\
+    $c_{2,0}$ & $-3.246^{+0.121}_{-0.123}$ & $-2.973^{+0.117}_{-0.133}$ & $-2.950^{+0.105}_{-0.097}$ \\     
+    $c_{2,1}$ & $-0.250^{+0.048}_{-0.050}$ & $-0.347^{+0.050}_{-0.050}$ & $-0.363^{+0.040}_{-0.043}$ \\
+    \\
+    $c_{3,0}$ & $-2.350^{+0.051}_{-0.060}$ & $-2.545^{+0.123}_{-0.290}$ & $-1.424^{+0.031}_{-0.031}$ \\     
+    $c_{3,1}$ & $0.647^{+0.072}_{-0.060}$ & $1.581^{+0.520}_{-0.264}$ & $-0.111^{+0.010}_{-0.010}$ \\       
+    $c_{3,2}$ & $3.857^{+0.092}_{-0.073}$ & $2.102^{+0.450}_{-0.283}$ & --- \\        
+    $c_{3,3}$ & $27.534^{+41.364}_{-9.405}$ & $1.965^{+0.461}_{-0.464}$ & --- \\      
+    $c_{3,4}$ & $-0.002^{+0.074}_{-0.082}$ & $-0.641^{+0.169}_{-0.154}$ & --- \\      
+    \hline 
+  \end{tabular}
+\end{table}
 
@@
   \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{g_18.pdf}
-    \includegraphics[width=0.5\textwidth]{g_21.pdf}
-    \end{tabular}
+    \includegraphics[scale=0.65]{g.pdf}
   \end{center}

### 2018-03-06 composite.py
Add new class for polynomial betas

@@ -160,6 +160,10 @@ class selmap:
             
 class lf:
 
+    """5-parameter model for beta; for polynomial model see lf_polyb below.
+
+    """
+
     def __init__(self, quasar_files=None, selection_maps=None, pnum=np.array([2,2,1,1])):
 
         self.pnum = pnum 
@@ -215,6 +219,183 @@ class lf:
         alpha = self.atz(z, params[2])
         #beta = self.atz(z, params[3])
         beta = self.atz_beta(z, params[3])
+        
+        phi = 10.0**log10phi_star / (10.0**(0.4*(alpha+1)*(mag-M_star)) +
+                                     10.0**(0.4*(beta+1)*(mag-M_star)))
+        return np.log10(phi)
+
+    def lfnorm(self, theta):
+
+        ns = np.array([x.nqso(self, theta) for x in self.maps])
+        return np.sum(ns) 
+        
+    def neglnlike(self, theta):
+
+        logphi = self.log10phi(theta, self.M1450, self.z) # Mpc^-3 mag^-1
+        logphi /= np.log10(np.e) # Convert to base e 
+
+        return -2.0*logphi.sum() + 2.0*self.lfnorm(theta)
+
+    def bestfit(self, guess, method='Nelder-Mead'):
+        result = op.minimize(self.neglnlike,
+                             guess,
+                             method=method, options={'maxfev': 20000,
+                                                     'maxiter': 20000,
+                                                     'disp': True})
+
+        if not result.success:
+            print 'Likelihood optimisation did not converge.'
+
+        self.bf = result 
+        return result
+    
+    def create_param_range(self):
+
+        half = self.bf.x/2.0
+        double = 2.0*self.bf.x
+        self.prior_min_values = np.where(half < double, half, double) 
+        self.prior_max_values = np.where(half > double, half, double)
+        assert(np.all(self.prior_min_values < self.prior_max_values))
+
+        return
+
+    def lnprior(self, theta):
+        """
+        Set up uniform priors.
+
+        """
+
+        params = self.getparams(theta)
+        alpha = params[2]
+        alpha_atz6 = self.atz(6.0, alpha) 
+        
+        if (np.all(theta < self.prior_max_values) and
+            np.all(theta > self.prior_min_values) and
+            alpha_atz6 < -4.0):
+            return 0.0 
+
+        return -np.inf
+
[…]

### 2018-03-06 summary_fromFile.py
Show multiple models

@@ -12,10 +12,10 @@ from scipy.optimize import curve_fit
 from scipy.interpolate import UnivariateSpline
 
 # These redshift bins are labelled "bad" and are plotted differently.
-# reject = [0, 1, 8, 9, 10, 11, 12, 13]
 reject = [0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20]
 
-colors = ['tomato', 'forestgreen', 'goldenrod', 'saddlebrown'] 
+# colors = ['tomato', 'forestgreen', 'goldenrod', 'saddlebrown']
+colors = ['k', 'k', 'k', 'k'] 
 nplots_x = 2
 nplots_y = 2
 nplots = 4
@@ -23,8 +23,59 @@ plot_number = 0
 
 zlims=(0.0,7.0)
 zmin, zmax = zlims
-z = np.linspace(zmin, zmax, num=50)
+z = np.linspace(zmin, zmax, num=500)
 cfit = False
+
+def plot_model(composite, param_number, ax):
+
+    if param_number == 0:
+        print 'phi'
+
+    nsample = 10000
+    np.random.seed()
+    rsample = composite.samples[np.random.randint(len(composite.samples), size=nsample)]
+    nzs = len(z) 
+    beta = np.zeros((nsample, nzs))
+
+    for i, theta in enumerate(rsample):
+        params = composite.getparams(theta)
+        if param_number < 3: 
+            beta[i] = composite.atz(z, params[param_number])
+        else:
+            beta[i] = composite.atz_beta(z, params[3]) 
+
+    up = np.percentile(beta, 15.87, axis=0)
+    down = np.percentile(beta, 84.13, axis=0)
+    
+    ax.fill_between(z, down, y2=up, color='turquoise', zorder=1, label='Model 2')
+
+    beta = np.median(beta, axis=0)
+    ax.plot(z, beta, color='turquoise', zorder=2, lw=1)
+    
+    return
+
+def plot_model_polyb(composite, param_number, ax):
+
+    nsample = 10000
+    np.random.seed()
+    rsample = composite.samples[np.random.randint(len(composite.samples), size=nsample)]
+    nzs = len(z) 
+    beta = np.zeros((nsample, nzs))
+
+    for i, theta in enumerate(rsample):
+        params = composite.getparams(theta)
+        beta[i] = composite.atz(z, params[param_number])
+
+    up = np.percentile(beta, 15.87, axis=0)
[…]

### 2018-03-08 Paper/paper.tex
Update

@@
 \def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
+\usepackage{supertabular}
 
@@
     well with the data in all redshift bins, except those spanned by
-    BOSS, as BOSS quasars are excluded from the global analysis.}
+    BOSS, as BOSS quasars are excluded from the global
+    analysis. \gk{Show all three models here.}}
   \label{fig:mosaic_global}
@@
   \begin{center}
+    % rtg2.draw_g_paper() 
     \includegraphics[scale=0.65]{g.pdf}
@@
     evolution in the model of \citet{2012ApJ...746..125H}, while the
-    solid green curve shows the contribution of quasars to it. \gk{Two
-      problems to be addressed in these plots: (a) there is a
-      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
-      but because our emissivity diverges at $z>7$, I had a to put an
-      arbitrary cut-off; (b) the plots are too messy; we probably
-      should show fewer things.}}
+    solid green curve shows the contribution of quasars to it. }
   \label{fig:gammapi}
@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
-  \end{center}
-  \caption{Photon underproduction crisis.\label{fig:puc}}
-\end{figure}
-
 %% \begin{figure*}
@@
 \section{Photon underproduction}
+
+\begin{figure}
+  \begin{center}
+    % rtg2.draw_g_puc()
+    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
+  \end{center}
+  \caption{Evolution of the hydrogen photoionisation rate at low
+    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
+\end{figure}
 
@@
   \end{center}
-  \caption{Helium reionization.}
+  \caption{Helium reionization. \gk{What is La Plante's luminosity
+      limit?  Why is his redshift of reionization lower than ours?
+      Waiting for Puchwein to give us his model.  Do we need a table
+      for Q evolution of H and He?  Should we tabulate Helium
+      photoionisation rate?}}
 \end{figure}
@@
 
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
+  \end{center}
+  \caption{Effect of including Giallongo qsos in our analysis.}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth]{giallongo_compare.pdf}
+  \end{center}
+  \caption{Comparison of our LFs with Giallongo's LFs.}
+\end{figure*}
+
+\section{Table of emissivities}
+\label{sec:tables}
+
+Table~\ref{tab:gamma} shows the LyC emissivities and the resultant
+hydrogen photoionisation rate due to quasars down to magnitudes
+$M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the curves
+shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
+photoionisation rate calculation assumes an HI column density given by
+\citet{2012ApJ...746..125H}.  See Sections XX and XX for further
+details.
+
+\begin{table*}
+  \caption{LyC emissivities and the resultant hydrogen photoionisation
+    rate due to quasars down to magnitudes $M_{1450}=-18$ and
+    $M_{1450}=-21$.  These numbers describe the curves shown in
+    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The photoionisation
+    rate calculation assumes an HI column density given by
+    \citet{2012ApJ...746..125H}.  See Sections XX and XX for further
+    details.  \gk{Do we need another table for the emissivities from
+      individual models?}}
+  \label{tab:gamma}
+  \begin{tabular}{ccccc}
+    \hline
+    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
+    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \hline
+    0.0 & 5.090e--14 & 2.822e--14 & 1.383e+23 & 7.011e+22 \\
+    0.1 & 7.036e--14 & 4.069e--14 & 2.231e+23 & 1.176e+23 \\
+    0.2 & 9.461e--14 & 5.690e--14 & 3.419e+23 & 1.877e+23 \\
+    0.3 & 1.248e--13 & 7.787e--14 & 5.019e+23 & 2.873e+23 \\
+    0.4 & 1.614e--13 & 1.041e--13 & 7.098e+23 & 4.240e+23 \\
+    0.5 & 2.051e--13 & 1.363e--13 & 9.717e+23 & 6.056e+23 \\
+    0.6 & 2.566e--13 & 1.750e--13 & 1.293e+24 & 8.401e+23 \\
+    0.7 & 3.164e--13 & 2.208e--13 & 1.676e+24 & 1.135e+24 \\
+    0.8 & 3.845e--13 & 2.736e--13 & 2.124e+24 & 1.495e+24 \\
+    0.9 & 4.605e--13 & 3.330e--13 & 2.636e+24 & 1.923e+24 \\
+    1.0 & 5.433e--13 & 3.980e--13 & 3.208e+24 & 2.419e+24 \\
+    1.1 & 6.309e--13 & 4.667e--13 & 3.835e+24 & 2.978e+24 \\
+    1.2 & 7.207e--13 & 5.367e--13 & 4.507e+24 & 3.589e+24 \\
+    1.3 & 8.092e--13 & 6.046e--13 & 5.216e+24 & 4.237e+24 \\
+    1.4 & 8.931e--13 & 6.675e--13 & 5.946e+24 & 4.902e+24 \\
+    1.5 & 9.715e--13 & 7.246e--13 & 6.684e+24 & 5.559e+24 \\
+    1.6 & 1.037e--12 & 7.693e--13 & 7.414e+24 & 6.185e+24 \\
+    1.7 & 1.087e--12 & 8.003e--13 & 8.117e+24 & 6.754e+24 \\
+    1.8 & 1.131e--12 & 8.246e--13 & 8.779e+24 & 7.245e+24 \\
+    1.9 & 1.163e--12 & 8.364e--13 & 9.384e+24 & 7.642e+24 \\
+    2.0 & 1.183e--12 & 8.386e--13 & 9.917e+24 & 7.932e+24 \\
+    2.1 & 1.195e--12 & 8.322e--13 & 1.037e+25 & 8.112e+24 \\
+    2.2 & 1.194e--12 & 8.156e--13 & 1.073e+25 & 8.184e+24 \\
+    2.3 & 1.187e--12 & 7.941e--13 & 1.099e+25 & 8.153e+24 \\
+    2.4 & 1.168e--12 & 7.636e--13 & 1.115e+25 & 8.030e+24 \\
+    2.5 & 1.145e--12 & 7.308e--13 & 1.121e+25 & 7.827e+24 \\
+    2.6 & 1.112e--12 & 6.915e--13 & 1.118e+25 & 7.558e+24 \\
+    2.7 & 1.075e--12 & 6.516e--13 & 1.105e+25 & 7.237e+24 \\
+    2.8 & 1.031e--12 & 6.080e--13 & 1.085e+25 & 6.877e+24 \\
+    2.9 & 9.835e--13 & 5.648e--13 & 1.057e+25 & 6.490e+24 \\
+    3.0 & 9.319e--13 & 5.207e--13 & 1.022e+25 & 6.087e+24 \\
+    3.1 & 8.780e--13 & 4.774e--13 & 9.824e+24 & 5.676e+24 \\
+    3.2 & 8.227e--13 & 4.354e--13 & 9.385e+24 & 5.267e+24 \\
+    3.3 & 7.658e--13 & 3.945e--13 & 8.914e+24 & 4.864e+24 \\
+    3.4 & 7.102e--13 & 3.565e--13 & 8.422e+24 & 4.473e+24 \\
+    3.5 & 6.545e--13 & 3.202e--13 & 7.916e+24 & 4.098e+24 \\
+    3.6 & 6.006e--13 & 2.865e--13 & 7.406e+24 & 3.740e+24 \\
+    3.7 & 5.487e--13 & 2.554e--13 & 6.898e+24 & 3.402e+24 \\
+    3.8 & 4.988e--13 & 2.265e--13 & 6.399e+24 & 3.085e+24 \\
+    3.9 & 4.521e--13 & 2.006e--13 & 5.912e+24 & 2.789e+24 \\
+    4.0 & 4.082e--13 & 1.769e--13 & 5.443e+24 & 2.515e+24 \\
+    4.1 & 3.671e--13 & 1.554e--13 & 4.993e+24 & 2.262e+24 \\
+    4.2 & 3.295e--13 & 1.363e--13 & 4.566e+24 & 2.029e+24 \\
+    4.3 & 2.948e--13 & 1.192e--13 & 4.163e+24 & 1.816e+24 \\
+    4.4 & 2.630e--13 & 1.039e--13 & 3.784e+24 & 1.622e+24 \\
+    4.5 & 2.342e--13 & 9.045e--14 & 3.431e+24 & 1.445e+24 \\
+    4.6 & 2.081e--13 & 7.854e--14 & 3.102e+24 & 1.286e+24 \\
+    4.7 & 1.845e--13 & 6.803e--14 & 2.798e+24 & 1.141e+24 \\
+    4.8 & 1.633e--13 & 5.883e--14 & 2.518e+24 & 1.011e+24 \\
+    4.9 & 1.444e--13 & 5.078e--14 & 2.262e+24 & 8.944e+23 \\
+    5.0 & 1.274e--13 & 4.373e--14 & 2.027e+24 & 7.898e+23 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+\begin{table*}
+  \contcaption{LyC emissivities and the resultant hydrogen
+    photoionisation rate due to quasars down to magnitudes
+    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
+    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
+    photoionisation rate calculation assumes an HI column density
+    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
+    further details.}
+  \label{tab:gamma}
+  \begin{tabular}{ccccc}
+    \hline
+    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
+    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \hline
+    5.1 & 1.121e--13 & 3.758e--14 & 1.813e+24 & 6.963e+23 \\
+    5.2 & 9.851e--14 & 3.222e--14 & 1.618e+24 & 6.129e+23 \\
+    5.3 & 8.622e--14 & 2.752e--14 & 1.442e+24 & 5.387e+23 \\
+    5.4 & 7.497e--14 & 2.333e--14 & 1.283e+24 & 4.728e+23 \\
+    5.5 & 6.433e--14 & 1.952e--14 & 1.139e+24 & 4.143e+23 \\
+    5.6 & 5.346e--14 & 1.579e--14 & 1.010e+24 & 3.626e+23 \\
+    5.7 & 4.420e--14 & 1.269e--14 & 8.942e+23 & 3.169e+23 \\
+    5.8 & 3.635e--14 & 1.014e--14 & 7.905e+23 & 2.766e+23 \\
+    5.9 & 2.971e--14 & 8.054e--15 & 6.978e+23 & 2.412e+23 \\
+    6.0 & 2.415e--14 & 6.354e--15 & 6.152e+23 & 2.100e+23 \\
+    6.1 & 1.952e--14 & 4.982e--15 & 5.416e+23 & 1.826e+23 \\
+    6.2 & 1.570e--14 & 3.883e--15 & 4.762e+23 & 1.587e+23 \\
+    6.3 & 1.255e--14 & 3.004e--15 & 4.182e+23 & 1.377e+23 \\
+    6.4 & 9.968e--15 & 2.310e--15 & 3.668e+23 & 1.193e+23 \\
+    6.5 & 7.880e--15 & 1.766e--15 & 3.214e+23 & 1.033e+23 \\
+    6.6 & 6.200e--15 & 1.343e--15 & 2.813e+23 & 8.940e+22 \\
+    6.7 & 4.853e--15 & 1.015e--15 & 2.459e+23 & 7.726e+22 \\
+    6.8 & 3.781e--15 & 7.634e--16 & 2.148e+23 & 6.670e+22 \\
+    6.9 & 2.936e--15 & 5.721e--16 & 1.874e+23 & 5.753e+22 \\
+    7.0 & 2.275e--15 & 4.277e--16 & 1.633e+23 & 4.958e+22 \\
+    7.1 & 1.760e--15 & 3.192e--16 & 1.422e+23 & 4.269e+22 \\
+    7.2 & 1.360e--15 & 2.379e--16 & 1.237e+23 & 3.672e+22 \\
+    7.3 & 1.052e--15 & 1.775e--16 & 1.075e+23 & 3.156e+22 \\
+    7.4 & 8.149e--16 & 1.327e--16 & 9.336e+22 & 2.710e+22 \\
+    7.5 & 6.325e--16 & 9.947e--17 & 8.100e+22 & 2.326e+22 \\
+    7.6 & 4.920e--16 & 7.477e--17 & 7.021e+22 & 1.994e+22 \\
+    7.7 & 3.843e--16 & 5.645e--17 & 6.082e+22 & 1.709e+22 \\
+    7.8 & 3.010e--16 & 4.278e--17 & 5.263e+22 & 1.463e+22 \\
+    7.9 & 2.365e--16 & 3.253e--17 & 4.552e+22 & 1.251e+22 \\
+    8.0 & 1.864e--16 & 2.483e--17 & 3.933e+22 & 1.070e+22 \\
+    8.1 & 1.473e--16 & 1.902e--17 & 3.396e+22 & 9.138e+21 \\
+    8.2 & 1.169e--16 & 1.462e--17 & 2.930e+22 & 7.800e+21 \\
+    8.3 & 9.297e--17 & 1.128e--17 & 2.527e+22 & 6.654e+21 \\
+    8.4 & 7.413e--17 & 8.725e--18 & 2.177e+22 & 5.673e+21 \\
+    8.5 & 5.924e--17 & 6.767e--18 & 1.874e+22 & 4.833e+21 \\
+    8.6 & 4.744e--17 & 5.260e--18 & 1.613e+22 & 4.115e+21 \\
+    8.7 & 3.809e--17 & 4.100e--18 & 1.387e+22 & 3.502e+21 \\
+    8.8 & 3.066e--17 & 3.205e--18 & 1.192e+22 & 2.978e+21 \\
+    8.9 & 2.472e--17 & 2.510e--18 & 1.024e+22 & 2.531e+21 \\
+    9.0 & 1.996e--17 & 1.969e--18 & 8.785e+21 & 2.149e+21 \\
+    9.1 & 1.614e--17 & 1.547e--18 & 7.536e+21 & 1.825e+21 \\
+    9.2 & 1.308e--17 & 1.218e--18 & 6.460e+21 & 1.548e+21 \\
+    9.3 & 1.061e--17 & 9.604e--19 & 5.535e+21 & 1.313e+21 \\
+    9.4 & 8.628e--18 & 7.588e--19 & 4.739e+21 & 1.112e+21 \\
+    9.5 & 7.022e--18 & 6.002e--19 & 4.056e+21 & 9.423e+20 \\
+    9.6 & 5.722e--18 & 4.753e--19 & 3.469e+21 & 7.978e+20 \\
+    9.7 & 4.667e--18 & 3.769e--19 & 2.966e+21 & 6.751e+20 \\
+    9.8 & 3.810e--18 & 2.991e--19 & 2.534e+21 & 5.709e+20 \\
+    9.9 & 3.116e--18 & 2.377e--19 & 2.164e+21 & 4.826e+20 \\
+    10.0 & 2.551e--18 & 1.892e--19 & 1.847e+21 & 4.078e+20 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+\begin{table*}
+  \contcaption{LyC emissivities and the resultant hydrogen
+    photoionisation rate due to quasars down to magnitudes
+    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
+    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
+    photoionisation rate calculation assumes an HI column density
+    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
+    further details.}
+  \label{tab:gamma}
+  \begin{tabular}{ccccc}
+    \hline
+    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
+    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \hline
+    10.1 & 2.091e--18 & 1.507e--19 & 1.576e+21 & 3.444e+20 \\
+    10.2 & 1.715e--18 & 1.201e--19 & 1.344e+21 & 2.907e+20 \\
+    10.3 & 1.407e--18 & 9.584e--20 & 1.145e+21 & 2.453e+20 \\
+    10.4 & 1.156e--18 & 7.650e--20 & 9.756e+20 & 2.069e+20 \\
+    10.5 & 9.500e--19 & 6.112e--20 & 8.307e+20 & 1.744e+20 \\
+    10.6 & 7.820e--19 & 4.890e--20 & 7.071e+20 & 1.470e+20 \\
+    10.7 & 6.441e--19 & 3.915e--20 & 6.015e+20 & 1.238e+20 \\
+    10.8 & 5.309e--19 & 3.136e--20 & 5.115e+20 & 1.042e+20 \\
+    10.9 & 4.377e--19 & 2.513e--20 & 4.348e+20 & 8.771e+19 \\
+    11.0 & 3.611e--19 & 2.015e--20 & 3.694e+20 & 7.378e+19 \\
+    11.1 & 2.980e--19 & 1.616e--20 & 3.137e+20 & 6.204e+19 \\
+    11.2 & 2.462e--19 & 1.297e--20 & 2.664e+20 & 5.215e+19 \\
+    11.3 & 2.036e--19 & 1.042e--20 & 2.260e+20 & 4.382e+19 \\
+    11.4 & 1.685e--19 & 8.378e--21 & 1.917e+20 & 3.681e+19 \\
+    11.5 & 1.394e--19 & 6.737e--21 & 1.626e+20 & 3.091e+19 \\
+    11.6 & 1.154e--19 & 5.419e--21 & 1.378e+20 & 2.594e+19 \\
+    11.7 & 9.559e--20 & 4.360e--21 & 1.168e+20 & 2.176e+19 \\
+    11.8 & 7.919e--20 & 3.509e--21 & 9.889e+19 & 1.825e+19 \\
+    11.9 & 6.564e--20 & 2.826e--21 & 8.372e+19 & 1.530e+19 \\
+    12.0 & 5.447e--20 & 2.278e--21 & 7.086e+19 & 1.283e+19 \\
+    12.1 & 4.521e--20 & 1.836e--21 & 5.995e+19 & 1.075e+19 \\
+    12.2 & 3.754e--20 & 1.481e--21 & 5.070e+19 & 9.002e+18 \\
+    12.3 & 3.117e--20 & 1.195e--21 & 4.287e+19 & 7.537e+18 \\
+    12.4 & 2.589e--20 & 9.637e--22 & 3.623e+19 & 6.309e+18 \\
+    12.5 & 2.151e--20 & 7.776e--22 & 3.061e+19 & 5.279e+18 \\
+    12.6 & 1.788e--20 & 6.275e--22 & 2.586e+19 & 4.416e+18 \\
+    12.7 & 1.487e--20 & 5.068e--22 & 2.183e+19 & 3.693e+18 \\
+    12.8 & 1.237e--20 & 4.095e--22 & 1.843e+19 & 3.087e+18 \\
+    12.9 & 1.029e--20 & 3.309e--22 & 1.555e+19 & 2.580e+18 \\
+    13.0 & 8.567e--21 & 2.674e--22 & 1.312e+19 & 2.156e+18 \\
+    13.1 & 7.131e--21 & 2.162e--22 & 1.106e+19 & 1.801e+18 \\
+    13.2 & 5.935e--21 & 1.747e--22 & 9.325e+18 & 1.503e+18 \\
+    13.3 & 4.940e--21 & 1.412e--22 & 7.859e+18 & 1.255e+18 \\
+    13.4 & 4.112e--21 & 1.141e--22 & 6.621e+18 & 1.047e+18 \\
+    13.5 & 3.424e--21 & 9.229e--23 & 5.577e+18 & 8.739e+17 \\
+    13.6 & 2.851e--21 & 7.465e--23 & 4.696e+18 & 7.289e+17 \\
+    13.7 & 2.374e--21 & 6.036e--23 & 3.953e+18 & 6.078e+17 \\
+    13.8 & 1.975e--21 & 4.879e--23 & 3.327e+18 & 5.067e+17 \\
+    13.9 & 1.643e--21 & 3.942e--23 & 2.799e+18 & 4.223e+17 \\
+    14.0 & 1.365e--21 & 3.182e--23 & 2.354e+18 & 3.518e+17 \\
+    14.1 & 1.133e--21 & 2.566e--23 & 1.980e+18 & 2.931e+17 \\
+    14.2 & 9.381e--22 & 2.066e--23 & 1.664e+18 & 2.441e+17 \\
+    14.3 & 7.750e--22 & 1.659e--23 & 1.399e+18 & 2.032e+17 \\
+    14.4 & 6.384e--22 & 1.330e--23 & 1.175e+18 & 1.691e+17 \\
+    14.5 & 5.229e--22 & 1.060e--23 & 9.873e+17 & 1.408e+17 \\
+    14.6 & 4.245e--22 & 8.375e--24 & 8.292e+17 & 1.171e+17 \\
+    14.7 & 3.395e--22 & 6.526e--24 & 6.962e+17 & 9.741e+16 \\
+    14.8 & 2.641e--22 & 4.951e--24 & 5.844e+17 & 8.100e+16 \\
+    14.9 & 1.935e--22 & 3.542e--24 & 4.904e+17 & 6.735e+16 \\
+    15.0 & 1.182e--22 & 2.116e--24 & 4.115e+17 & 5.598e+16 \\
+    \hline
+  \end{tabular}
+\end{table*}
+
+\section{Code and data}
+
+We make the homogenised quasar data and the code developing and
+analysing luminosity function models available at
+\url{https://github.com/gkulkarni/QLF} under the MIT open source
+software license.  \gk{Remember to make URL public and set appropriate
+  license upon publication of paper.}
+
 \bibliographystyle{mnras}

### 2018-03-09 Paper/paper.tex
Update text

@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
+  \end{center}
+  \caption{Evolution of the \HeIII\ ionization fraction in our model,
+    when the qso luminosity function is integrated down to
+    $M_{1450}=-21$ (black curve) and when it is extrapolated and
+    integrated down to $M_{1450}=-18$ (brown curve).  Other curves
+    show models of \citet[solid grey]{2012ApJ...746..125H},
+    \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
+      shaded region]{2016ApJ...828...90L},
+    \citet[blue]{2018arXiv180104931P}. \gk{Do we need to add any more
+      models from literature?}}
+\end{figure}
+
 We now consider the implications for hydrogen and helium reionization
@@
   the current emissivity model upto where data end.}  The evolution of
-the volume averaged ionized fraction of hydrogen is given by
-\citep{2012ApJ...746..125H}
+the volume averaged ionized fraction of hydrogen is given by \gk{Is
+  this really volume-weighted?}  \citep{2012ApJ...746..125H}
 \begin{equation}
@@
 \section{Photon underproduction}
-
-\begin{figure}
-  \begin{center}
-    % rtg2.draw_g_puc()
-    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
-  \end{center}
-  \caption{Evolution of the hydrogen photoionisation rate at low
-    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
-\end{figure}
 
@@
   \begin{center}
-    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
+    % rtg2.draw_g_puc()
+    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
   \end{center}
-  \caption{Helium reionization. \gk{What is La Plante's luminosity
-      limit?  Why is his redshift of reionization lower than ours?
-      Waiting for Puchwein to give us his model.  Do we need a table
-      for Q evolution of H and He?  Should we tabulate Helium
-      photoionisation rate?}}
+  \caption{Evolution of the hydrogen photoionisation rate at low
+    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
 \end{figure}
@@
 
-% Check spellings
-% Check notes for more names with add
-% Something to add for Joe and Gabor?
-We acknowledge useful discussions with James Aird, Manda Banerji,
-Tirthankar Roy Choudhury, Xiaohui Fan, Andrea Ferrara, Martin
-Haehnelt, Sergey Koposov, Richard McMahon, Ewald Puchwein, Gordon
-Richards, and Alberto Rorai.  GK is supported by ERC Advanced Grant
-320596 `The Emergence of Structure During the Epoch of Reionization'.
+It is a pleasure to acknowledge useful discussions with James Aird,
+Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou, Xiaohui
+Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul Hewett,
+Sergey Koposov, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
+Ewald Puchwein, Gordon Richards, Alberto Rorai, and Stephen Warren.
+GK acknowledges support from ERC Advanced Grant 320596 `The Emergence
+of Structure During the Epoch of Reionization'. \gk{Perhaps we need to
+  specially thank people who shared data with us.  Gabor, Joe: do you
+  need to add anything to acknowledgements?}
 
@@
 faint quasars but because of the difference with Giallongo at
-intermediate luminosities.
+intermediate luminosities.  However, our double power law fits are
+virtually identical to those shown in Figure~\ref{fig:mosaic}.
 
@@
   \end{center}
-  \caption{Effect of including Giallongo qsos in our analysis.}
+  \caption{Effect of the 19 qsos reported by
+    \citet{2015AA...578A..83G} on the best-fit double power law
+    luminosity function parameters in redshift bins from $z=0$ to $7$.
+    Black points show parameter values from Figure~\ref{fig:evoln}.
+    Red open circles show the parameter values obtained when the
+    sample of \citet{2015AA...578A..83G} is added to the analysis.  In
+    both cases, vertical error bars show one-sigma (68.26\%)
+    uncertainties, whereas horizontal error bars show widths of the
+    redshift bins.}
 \end{figure*}
@@
   \end{center}
-  \caption{Comparison of our LFs with Giallongo's LFs.}
+  \caption{Luminosity functions in three redshift bins at $z>4.1$.
+    Black curves in each panel show the best-fit double power law,
+    with the corresponding one-sigma (68.26\%) uncertainty shown by
+    the grey shaded area.  There are 451, 270, and 69 qsos in each
+    redshift bin from left to right, respectively.  These numbers are
+    higher than those in Figure~\ref{fig:mosaic} because they include,
+    respectively, 9, 7, and 3 qsos from \citet{2015AA...578A..83G}.
+    The magnitude bins containing these qsos are shown in purple.  The
+    red dashed curves show the double power law fits reported by
+    \citet{2015AA...578A..83G} at $z=4.25, 4.75,$ and
+    $5.75$.}
 \end{figure*}
@@
 software license.  \gk{Remember to make URL public and set appropriate
-  license upon publication of paper.}
+  license upon publication of paper.  Add requirement of citation to
+  license.}
 

### 2018-03-09 bins.py
Simplify labels

@@ -23,22 +23,22 @@ qlumfiles = ['Data_new/dr7z2p2_sample.dat',
              'Data_new/willott10_cfhqsvwsample.dat',
              'Data_new/kashikawa15_sample.dat']
 
-selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'SDSS DR7 Richards et al.\ 2006'),
-             ('Data_new/croom09sgp_selfunc.dat', 0.3, 0.05, 64.2, 15, r'2SLAQ Croom et al.\ 2009'),
-             ('Data_new/croom09ngp_selfunc.dat', 0.3, 0.05, 127.7, 15, r'2SLAQ Croom et al.\ 2009'),
-             ('Data_new/ross13_selfunc2.dat', 0.1, 0.05, 2236.0, 1, r'BOSS DR9 Ross et al.\ 2013'),
-             ('Data_new/dr7z3p7_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'SDSS DR7 Richards et al.\ 2006'),
-             ('Data_new/glikman11_selfunc_ndwfs.dat', 0.05, 0.02, 1.71, 6, r'NDWFS+DLS Glikman et al.\ 2011'),
-             ('Data_new/glikman11_selfunc_dls.dat', 0.05, 0.02, 2.05, 6, r'NDWFS+DLS Glikman et al.\ 2011'),
-             ('Data_new/yang16_sel.dat', 0.1, 0.05, 14555.0, 17, r'SDSS+WISE Yang et al.\ 2016'),
-             ('Data_new/mcgreer13_dr7selfunc.dat', 0.1, 0.05, 6248.0, 8, r'SDSS+S82 McGreer et al.\ 2013'),
-             ('Data_new/mcgreer13_s82selfunc.dat', 0.1, 0.05, 235.0, 8, r'SDSS+S82 McGreer et al.\ 2013'),
-             ('Data_new/jiang16main_selfunc.dat', 0.1, 0.05, 11240.0, 18, r'SDSS Jiang et al.\ 2016'),
-             ('Data_new/jiang16overlap_selfunc.dat', 0.1, 0.05, 4223.0, 18, r'SDSS Jiang et al.\ 2016'),
[…]

### 2018-03-09 drawlf.py
Change style for use with giallongo_compare.py

@@ -79,7 +79,7 @@ def plot_bestfit_lf(lf, ax, mags, **kwargs):
 
     bf = np.median(lf.samples, axis=0)
     phi_fit = lf.log10phi(bf, mags)
-    ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
+    ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'], label=kwargs['label'])
 
     return
 
@@ -164,7 +164,7 @@ def totBinVol_all(lf, m, mbins, selmaps):
 
 
 def get_lf(lf, sid, z_plot):
-
+    
     # Bin data.  This is only for visualisation and to compare
     # with reported binned values.  
 
@@ -330,7 +330,7 @@ def plot_giallongo_z5p75(lf, ax, mags):
     p = (log10phi_star_giallongo, M_star_giallongo, alpha, beta)
     
     phi_fit = lf.log10phi(p, mags)
-    ax.plot(mags, phi_fit, lw=3, c='r', zorder=100, label=r'Giallongo et al.\ 2015 fit at $z=5.75$')
+    ax.plot(mags, phi_fit, lw=2, c='r', zorder=100, label=r'Giallongo et al.\ 2015 fit at $z=5.75$', dashes=[7,2])
 
     return 
 
@@ -345,7 +345,7 @@ def plot_giallongo_z4p75(lf, ax, mags):
     p = (log10phi_star_giallongo, M_star_giallongo, alpha, beta)
     
     phi_fit = lf.log10phi(p, mags)
-    ax.plot(mags, phi_fit, lw=3, c='r', zorder=100, label=r'Giallongo et al.\ 2015 fit at $z=4.75$')
+    ax.plot(mags, phi_fit, lw=2, c='r', zorder=100, label=r'Giallongo et al.\ 2015 fit at $z=4.75$', dashes=[7,2])
 
     return 
 
@@ -360,7 +360,7 @@ def plot_giallongo_z4p25(lf, ax, mags):
     p = (log10phi_star_giallongo, M_star_giallongo, alpha, beta)
     
     phi_fit = lf.log10phi(p, mags)
-    ax.plot(mags, phi_fit, lw=3, c='r', zorder=100, label=r'Giallongo et al.\ 2015 fit at $z=4.25$')
[…]

### 2018-03-09 gammapi.py
Update plotting style for paper

@@ -475,6 +475,8 @@ def draw_emissivity(all_individuals, zlims, composite=None, select=False):
     u = np.array([x.emissivity[0] for x in individuals_good])
     l = np.array([x.emissivity[1] for x in individuals_good])
 
+    print c 
+
     em = c
     em_up = u - c
     em_low = c - l 
@@ -505,8 +507,16 @@ def draw_emissivity(all_individuals, zlims, composite=None, select=False):
     popt, pcov = curve_fit(func, zs, em, sigma=sigma, p0=[24.6, 4.68, 0.28, 1.77, 26.3])
     print popt
     z = np.linspace(0, 7)
-    plt.plot(z, func(z, *popt), lw=3, c='k')
 
+    dz = 0.1
+    zmax = 15.0
+    zmin = 0.0 
+    n = (zmax-zmin)/dz+1
+    z = np.linspace(zmax, zmin, num=n)
+    em18 =  func(z, *popt)
+    plt.plot(z, em18, lw=3, c='k')
+
+    
 
     for x in individuals_good:
         get_emissivity(x, x.z.mean(), Mfaint=-21.0)
@@ -539,8 +549,13 @@ def draw_emissivity(all_individuals, zlims, composite=None, select=False):
     sigma = u-l 
     popt, pcov = curve_fit(func, zs, em, sigma=sigma, p0=[24.6, 4.68, 0.28, 1.77, 26.3])
     print popt
-    z = np.linspace(0, 7)
-    plt.plot(z, func(z, *popt), lw=3, c='peru')
+    em21 = func(z, *popt)
+    plt.plot(z, em21, lw=3, c='peru')
+
+    tabulate = False
+    if tabulate:
+        for i in range(len(em21)):
+            print r'{:.1f}  {:.3e}  {:.3e}'.format(z[i], em18[i], em21[i])
 
     
     zg, eg, zg_lerr, zg_uerr, eg_lerr, eg_uerr = np.loadtxt('Data_new/giallongo15_emissivity.txt', unpack=True)

### 2018-03-12 Paper/paper.tex
Update text

@@
   USA}
-
+% Update Gabor's address to Potsdam
 \date{Accepted ---. Received ---; in original form ---}
@@
   \end{center}
-  \caption{Quasar samples.}
+  \caption{Redshift distribution of the XX quasars considered in this
+    analysis.  Shown here are the observed quasar numbers, without
+    correcting for incompleteness.  Further details on each of these
+    data sets are in Table~\ref{tab:samples} and
+    Section~\ref{sec:sample}.}
   \label{fig:qsos}
@@
   % See data.tex for a version of this table that includes file names
+  % Should we mark Giallongo, Mortlock, and Banados entries to say that these are sometimes excluded from analysis?
+  % Remove notes?
   \caption{Quasar data sets}
@@
     21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
+    22. & 20 & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 & \\
     \hline
@@
 \section{Homogenised Quasar Sample}
+\label{sec:sample}
 
@@
 Given quasar luminosities and estimates for survey completeness, we
-begin our analysis by first deriving luminosity functions binned both
-in redshift and magnitude.  In this discussion all magnitudes are
+are in a position to estimate the UV luminosity function of AGN.  We
+begin our analysis by first deriving luminosity functions in bins of
+redshift and magnitude.  In this discussion all magnitudes are
 absolute magnitudes at rest-frame 1450~{\AA}.
@@
   In each bin, we estimate the uncertainty in the luminosity function
-  by assuming Poisson statistics \citep{1986ApJ...303..336G}.  The
-  resultant binned luminosity function estimates are shown by the
-  points in Figure~\ref{fig:mosaic}.  These agree quite well with the
-  published luminosity functions by these surveys.
-
-  % Do we want to give the details of how good/bad this agreement
-  % actually is?
-
-  %% Figure~\ref{fig:boss}
-  %% shows the luminosity function derived in this way for the BOSS DR9
-  %% colour-selected sample of 23,301 quasars, in comparison with the
-  %% published luminosity function of \citet{2013ApJ...773...14R}.
-  %% Figure~\ref{fig:sdss} shows the luminosity function of a sample of
-  %% 15,179 quasars from the SDSS DR3 in comparison with the published
-  %% luminosity function of \citet{2006AJ....131.2766R}.
+  by assuming Poisson statistics \citep{1986ApJ...303..336G} for the
+  number of quasars in each bin.  The resultant binned luminosity
+  function estimates are shown by the points in
+  Figure~\ref{fig:mosaic}.
+
+  As seen in Figure~\ref{fig:mosaic}, the distribution of luminosity
+  function values in each redshift bin are suggestive of a double
+  power law form.  We will fit such a form below.  However, we also
+  see in several redshift bins of Figure~\ref{fig:mosaic} that the
+  luminosity function seems to show a decline at the faint end.  This
+  is clearly seen, for example, in the 2SLAQ sample at $z<2$ and in
+  the SDSS quasar sample at $z<1.8$ and $z\sim 4$.  We take this to be
+  a systematic error.  The decrease in the luminosity function is an
+  indication of further low-level incompleteness in the quasar surveys
+  that has not been captured by the reported completeness values.  We
+  choose to discard such bins from our analysis.  The discarded
+  luminosity bins are shown in Figure~\ref{fig:mosaic} by open
+  circles.
 
@@
   \end{center}
-  \caption{Parameter evolution from individual fits in
-    Figures~\ref{fig:mosaic}.  Parameters from BOSS quasars are seen
-    to be systematically offset.}
+  \caption{Evolution of the four double power law parameters from the
+    redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical error
+    bars show one-sigma (68.26\%) uncertainties, whereas horizontal
+    error bars show widths of the redshift bins.  We identify the
+    general evolutionary trends of each of these parameters from the
+    bins shown by the filled symbols.  The open symbols show bins that
+    appear to be offset from these trends, likely due to unknown
+    systematic errors.  The open circles at $z\sim 2$--$4$ show the
+    BOSS sample, while the bins at $z < 0.6$ contain AGN from the SDSS
+    and 2SLAQ data sets.  See Section~\ref{sec:bins} for further
+    details.}
   \label{fig:evoln}
@@
 
-\subsection{Luminosity function estimates in redshift bins}
+\subsection{Double power law fits}
 \label{sec:bins}
 
-As our next step, we stop binning the quasars in luminosity, and only
-bin them in redshifts.  In each redshift bin, we model the quasar
+As our next step, we combine magnitude bins by binning the quasars
+only in redshifts.  This allows us to estimate the luminosity function
+at each redshift.  In each redshift bin, we model the quasar
 luminosity function as a double power law given by
@@
 Equation~(\ref{eqn:dpl}) has four free parameters: the amplitude
-$\phi_*$, the ``break'' $M_*$, the faint-end slope $\beta$, and the
-bright-end slope $\alpha$.  We obtain posterior probability
-distributions for these parameters using MCMC \citep[e.g.,][]{jaynes}.
-The joint posterior probability distribution of the model parameters
-is then written as
+$\phi_*$, the break magnitude $M_*$, the faint-end slope $\beta$, and
+the bright-end slope $\alpha$.  By assuming broad, uniform priors, we
+obtain posterior probability distributions for these parameters using
+MCMC \citep[e.g.,][]{jaynes}.  The joint posterior probability
+distribution of the model parameters is then written as
 \begin{multline}
-  p(\phi_*, M_*, \alpha, \beta | \{M_i, z_i\}) \propto \\ p(\phi_*, M_*, \alpha, \beta)p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta),
+  p(\phi_*, M_*, \alpha, \beta | \{M_i, z_i\}) \propto \\ p(\phi_*, M_*,
+  \alpha, \beta)p(\{M_i, z_i\} | \phi_*, M_*, \alpha, \beta),
 \end{multline}
@@
 \begin{multline}
-  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz}.
+  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM
+  \int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz}.
   \label{eqn:S}
@@
 luminosity integral in the second term on the right hand side is on
-the surveyed range of $M$.
+the surveyed range of $M$.  We use the \texttt{emcee} code
+\citep{2013PASP..125..306F} for MCMC.
 
@@
 \begin{equation}
-  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_j}^{z_{j+1}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
+  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_j}^{z_{j+1}}dz\, \phi(M,z) f(M, z)
+  \,\frac{dV}{dz},
 \end{equation}
@@
 given the luminosity function $\phi(M,z)$.  In the limit of
-infinitesimal bins, $n_{ij}=0$ or $1$, Equation~(\ref{eqn:lhood}) can
-be simplified and we get Equation~(\ref{eqn:S}).
-
-Our estimates for the luminosity function in several redshift bins are
-shown in Figure~\ref{fig:mosaic}.  The median of the posterior is
-shown as the best fit model.  Yellow curves show a random draw from
-the posterior.  Consistent with previous studies, the double power law
-model provides an excellent description of the luminosity function
-model over almost the complete range of redshifts spanned by the data.
-It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
-seem to favour a single power law.  In this bin, we the resultant
-posterior distribution of the break magnitude $M_*$ is bimodal with
-favoured values at the faint ($M_*>-18$) and bright end of the data
-($M_*<-30$).  We consider only the latter possibility as consistent
-with the data at lower redshifts ($z<5.5$).  In light of the low
-redshift data, we use restricted priors in this redshift bins: we
-restrict the bright-end slope $\alpha$ to values less than $-4$.
-Other paramters continue to have wide uniform priors.
-
-As seen in Figure~\ref{fig:mosaic}, in several redshift bins the
-binned quasar luminosity function seems to show a decline at the faint
-end.  This is clearly seen, for example, in the 2SLAQ sample at $z<2$.
-We take this to be a systematic error: the decrease in the luminosity
-function is an indication of incompleteness in the quasar surveys that
-has not been accounted for by the reported completeness map.  We
-choose to discard such quasars from our analysis.  This behaviour is
-also seen in the SDSS quasar sample at $z<1.8$ and $z\sim 4$.  The
-discarded luminosity bins are shown in Figure~\ref{fig:mosaic} by open
-circles.  We can see that the surviving quasar sample is in excellent
-agreement with the double power law model at all redshifts.
-
-The values of the four double power law parameters in various redshift
-bins are shown in Figure~\ref{fig:evoln}.  We find interesting
-evolutionary trends in each of the four parameters.  The break
-luminosity $M_*$ evolves by more than eight magnitudes from redshift
-$z=0$ to $7$.  The amplitude of the luminosity function $\phi_*$
-evolves moderately from $z=0$ to $z\sim 3$ and then drops by six
-orders of magnitude to about $10^{-12}$ at $z\sim 7$.  The bright end
-slope $\alpha$ has significant scatter, but still shows a trend
-towards larger negative values---that is, steeper bright-end
-luminosity functions---at high redshifts.  Finally, the faint end of
-the luminosity function also shows signs of increasing steepness
-towards high redshifts.  Somewhat similar to the amplitude $\phi_*$,
-the faint-end slope $\beta$ also shows a break at $z\sim 3$.  It stays
-roughly constant up to this redshift, and the drops to increasingly
-negative values at high redshifts, indicating a steeper faint end.
-
-The behaviour of BOSS quasars in Figure~\ref{fig:evoln} is striking.
-In the redshift range covered by BOSS the values of the four double
-power law parameters deviate from the general trends.  The faint end
-of the luminosity function of the BOSS quasars is much shallower and
-the break luminosity is fainter by a magnitude.  The bright end of the
+infinitesimal bins, $n_{ij}=0$ or $1$, and Equation~(\ref{eqn:lhood})
+can be simplified to obtain Equation~(\ref{eqn:S}).
+
+Our estimates for the double power law luminosity function are shown
+in Figure~\ref{fig:mosaic} for 25 redshift bins.  The posterior median
+is shown as the best-fit model at each redshift, while the grey shaded
+region shows the one-sigma (68.26\%) uncertainty.  Consistent with
+previous studies, the double power law model provides an excellent
+description of the luminosity function model over almost the complete
+range of redshifts spanned by the data.  It is only in the highest
+redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
+power law.  In this bin, the resultant posterior distribution of the
+break magnitude $M_*$ is bimodal with favoured values at the faint
+($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
+literature the $z\sim 6$ AGN have been assumed to lie on the bright
+end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
+comparison with the luminosity function at lower redshifts ($z<5.5$)
+suggests that these AGN should instead be understood to describe the
+faint-end of a double power law.  Therefore, in light of the
+low-redshift data, we use restricted priors in this redshift bin: we
+restrict the bright-end slope $\alpha$ to values less than $-4$, which
+is equivalent to forcing $M_*$ to be at the bright end of the data.
+Other parameters continue to have wide uniform priors.  This also
+illustrates the importance of analysing the high-redshift AGN
+population in a wider context of AGN data.
+
+The redshift evolution of the four double power law parameters is
+shown in Figure~\ref{fig:evoln}.  These values have been tabulated in
+Table~\ref{tab:bins}.  We find interesting evolutionary trends in each
+of the four parameters.  The break luminosity $M_*$ evolves by more
+than eight magnitudes from redshift $z=0$ to $7$.  The amplitude of
+the luminosity function $\phi_*$ evolves moderately from $z=0$ to
+$z\sim 3$ and then drops by six orders of magnitude to about
+$10^{-12}$ at $z\sim 7$.  The bright end slope $\alpha$ has
+significant scatter, but still shows a trend towards larger negative
+values, i.e., steeper luminosity function bright ends, at high
+redshifts.  Finally, the faint end of the luminosity function also
+shows signs of increasing steepness towards high redshifts.  Somewhat
+similar to the amplitude $\phi_*$, the faint-end slope $\beta$ also
+shows a break at $z\sim 3$.  It stays roughly constant up to this
+redshift, and the drops to increasingly negative values of close to
+$-2.5$ at high redshifts, indicating a steeper faint end.
+
+Figure~\ref{fig:evoln} reveals further potentially systematic errors.
+The behaviour of BOSS quasars, shown by open circles in
+Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
+redshift range covered by BOSS the values of the four double power law
+parameters deviate from the general trends.  The faint end of the
+luminosity function of the BOSS quasars is much shallower and the
+break luminosity is fainter by a magnitude compared to the general
+trend expected from a smooth evolution.  The bright end of the
 luminosity function of quasars in this sample is also much flatter
@@
 selection is known to be affected by a colour bias
-\citep{2011ApJ...728...23W}, as the quasar colour selection is
-contaminated by a population of blue stars.  We therefore deem the
-BOSS sample as affected by this systematic error.
-
-The open circles in Figure~\ref{fig:evoln} show the results of a
-similar analysis of the quasar UV luminosity function by
-\citep{2017MNRAS.466.1160M}.  Evidently, our results are quite
-different from the results of these authors.  While their analysis
-generally also reveals a steep faint end slop, the break luminosity
-evolution is dramatically different.  In their analysis the break
-luminosity tends to remain roughly constant $M_*\sim -24$ from $z=0$
-to $7$, but this does not seem to be indicated by the data shown in
-Figure~\ref{fig:mosaic}.  A possible reason behind their significanly
-different results could be a bias introduced by binning in
-luminosities and redshifts while fitting the luminosity function model.
+\citep{2011ApJ...728...23W}, which can make estimating completeness
+difficult \citep{2006AJ....131.2766R}.  \gk{Gabor, could you please
+  check if I have written this paragraph OK?}
 
@@
 
-\subsection{Luminosity function estimate without binning}
+%--------------------
+
+\subsection{Evolution of the luminosity function}
 
@@
 \begin{multline}
-  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg s^{-1} Hz^{-1} cMpc^{-3}}}\right)\\
+  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}}\right)\\
   \times\left(\frac{1}{1.5-\alpha}\right)\left(\frac{1+z}{5}\right)^{-2.4}.
@@
 
-\section{Hydrogen and helium reionization}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
-  \end{center}
-  \caption{Evolution of the \HeIII\ ionization fraction in our model,
-    when the qso luminosity function is integrated down to
-    $M_{1450}=-21$ (black curve) and when it is extrapolated and
-    integrated down to $M_{1450}=-18$ (brown curve).  Other curves
-    show models of \citet[solid grey]{2012ApJ...746..125H},
-    \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
-      shaded region]{2016ApJ...828...90L},
-    \citet[blue]{2018arXiv180104931P}. \gk{Do we need to add any more
-      models from literature?}}
-\end{figure}
-
-We now consider the implications for hydrogen and helium reionization
-for the ionizing photon emissivity derived above.  This requires that
-we extrapolate the emissivity of Equation XX to higher redshifts.
-Unfortunately, the volume emissivity in our model cannot be
-extrapolated to higher redshifts.  The model of Hopkins suffered with
-the same problem.  \gk{Do we need to show two cases here?  One in
-  which we extrapolate the emissivity and another in which we stop
-  where data end.  There is perhaps a third possibility in which use
-  the current emissivity model upto where data end.}  The evolution of
-the volume averaged ionized fraction of hydrogen is given by \gk{Is
-  this really volume-weighted?}  \citep{2012ApJ...746..125H}
-\begin{equation}
-{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
-\langle t_{\rm rec}\rangle},
-\label{eq:qdot}
-\end{equation}
-and the corresponding equation doubly ionized Helium is
-\begin{equation}
-{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
-\langle t_{\rm rec,He}\rangle}.
-\label{eq:qHedot}
-\end{equation}
-We assume that the Helium is singly reionized together with hydrogen.
-In order to get the 4~Ry emissivity of quasars we use the SED from
-equation XX.  The recombination times are given by
-\begin{equation}
-\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
-\label{eq:trec}
-\end{equation}
-where $n$ is the volume averaged density of hydrogen and helium,
-respectively.  We assume that hydrogen and helium have similar
-clumping factors, given by \citep{2015ApJ...813L...8M}
-\begin{equation}
-  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
-\end{equation}
-For the helium recombination coeffienct, we use the fitting function
-provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
-coefficient, we use the fitting function provided by
-\citet{2011piim.book.....D}.
-
-The resultant reionization histories of hydrogen and helium are shown
-in Figure XX.  We also show the reionization histories from
-\citep{2012ApJ...746..125H} and \citep{2015ApJ...813L...8M} for
-comparison.  As expected from the emissivity result of the previous
-section, quasars cannot single handedly reionize hydrogen.  However
-they can reionise \HeII.  The Helium reionization completes at
-redshift $z=3.5$--$3.7$ depending on the luminosity down to which you
-integrate the quasar luminosity function.  This is consistent with the
-Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.
-
-\section{Photon underproduction}
+\subsection{Photon underproduction at $z=0$?}
 
@@
 
+\section{Helium reionization}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
+  \end{center}
+  \caption{Evolution of the \HeIII\ ionization fraction in our model,
+    when the qso luminosity function is integrated down to
+    $M_{1450}=-21$ (black curve) and when it is extrapolated and
+    integrated down to $M_{1450}=-18$ (brown curve).  Other curves
+    show models of \citet[solid grey]{2012ApJ...746..125H},
+    \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
+      shaded region]{2016ApJ...828...90L},
+    \citet[blue]{2018arXiv180104931P}. \gk{Do we need to add any more
+      models from literature?}}
+\end{figure}
+
+We now consider the implications for hydrogen and helium reionization
+for the ionizing photon emissivity derived above.  This requires that
+we extrapolate the emissivity of Equation XX to higher redshifts.
+Unfortunately, the volume emissivity in our model cannot be
+extrapolated to higher redshifts.  The model of Hopkins suffered with
+the same problem.  \gk{Do we need to show two cases here?  One in
+  which we extrapolate the emissivity and another in which we stop
+  where data end.  There is perhaps a third possibility in which use
+  the current emissivity model upto where data end.}  The evolution of
+the volume averaged ionized fraction of hydrogen is given by \gk{Is
+  this really volume-weighted?}  \citep{2012ApJ...746..125H}
+\begin{equation}
+{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
+\langle t_{\rm rec}\rangle},
+\label{eq:qdot}
+\end{equation}
+and the corresponding equation doubly ionized Helium is
+\begin{equation}
+{dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
+\langle t_{\rm rec,He}\rangle}.
+\label{eq:qHedot}
+\end{equation}
+We assume that the Helium is singly reionized together with hydrogen.
+In order to get the 4~Ry emissivity of quasars we use the SED from
+equation XX.  The recombination times are given by
+\begin{equation}
+\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
+\label{eq:trec}
+\end{equation}
+where $n$ is the volume averaged density of hydrogen and helium,
+respectively.  We assume that hydrogen and helium have similar
+clumping factors, given by \citep{2015ApJ...813L...8M}
+\begin{equation}
+  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
+\end{equation}
+For the helium recombination coeffienct, we use the fitting function
+provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
+coefficient, we use the fitting function provided by
+\citet{2011piim.book.....D}.
+
+The resultant reionization histories of hydrogen and helium are shown
+in Figure XX.  We also show the reionization histories from
+\citep{2012ApJ...746..125H} and \citep{2015ApJ...813L...8M} for
+comparison.  As expected from the emissivity result of the previous
+section, quasars cannot single handedly reionize hydrogen.  However
+they can reionise \HeII.  The Helium reionization completes at
+redshift $z=3.5$--$3.7$ depending on the luminosity down to which you
+integrate the quasar luminosity function.  This is consistent with the
+Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.
+
 \section{Conclusions}
@@
 
-It is a pleasure to acknowledge useful discussions with James Aird,
-Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou, Xiaohui
-Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul Hewett,
-Sergey Koposov, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
-Ewald Puchwein, Gordon Richards, Alberto Rorai, and Stephen Warren.
-GK acknowledges support from ERC Advanced Grant 320596 `The Emergence
-of Structure During the Epoch of Reionization'. \gk{Perhaps we need to
-  specially thank people who shared data with us.  Gabor, Joe: do you
-  need to add anything to acknowledgements?}
+We thank Eilat Glikman, Linhua Jiang, Nobunari Kashi\-kawa, Ian
+McGreer, Nick Ross, Chris Willott, and Jinyi Yang for sharing data and
+especially for sharing their quasar selection functions.  It is a
+pleasure to acknowledge useful discussions with James Aird, Eduardo
+Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
+Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul
+Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Donald Lynden-Bell,
+Roberto Maiolino, Richard McMahon, Daniel Mortlock, Ewald Puchwein,
+Gordon Richards, Alberto Rorai, Bram Venemans and Stephen Warren.  GK
+acknowledges support from ERC Advanced Grant 320596 `The Emergence of
+Structure During the Epoch of Reionization'. \gk{Joe, do you need to
+  add anything to acknowledgements?}
 

### 2018-03-21 qhe.py
Add LLSs

@@ -186,6 +186,21 @@ def alpha_B_HeII_HuiGnedin1997(T):
     return 1.26e-14 * reclambda**0.75 # cm^3 s^-1 
     
 
+def alpha_A_HeIII_HuiGnedin1997(T):
+    """Case A He III recombination coefficient.
+
+    Hui and Gnedin 1997 (MNRAS 292 27; Appendix A).
+
+    """
+
+    t_HeII = 6.31515E5 # K; He single ionization threshold 
+    reclambda = 2.0*t_HeII/T
+
+    return (2.0 * 1.269e-13 *
+            (reclambda**1.503 /
+             (1.0 + (reclambda/0.522)**0.470)**1.923)) # cm^3 s^-1
+
+
 def alpha_B_HeIII_HuiGnedin1997(T):
     """Case B He III recombination coefficient.
 
@@ -213,6 +228,17 @@ def trec_HII(z):
 
 
 def trec_HeIII(z):
+
+    chi = 0.083
+    temperature = 2.0e4 # K 
+    alpha_r = alpha_B_HeIII_HuiGnedin1997(temperature/4.0) # cm^3 s^-1
+
+    r = (1+2*chi) * (1+z)**3 * alpha_r * nH * cmbympccb * clumping_factor(z) # s^-1
+
+    return 1/r # s 
+
+
+def trec_HeIII_noclump(z):
 
     chi = 0.083
     temperature = 2.0e4 # K 
@@ -262,7 +288,71 @@ def dqdt_HeIII(q, z, emissivity):
     n = (emissivity(z)/(1.70*hplanck) *
          (4**-1.7 - 10.0**-1.7)) # s^-1 Mpc^-3 
     
+    # d = n*(1-q)/nHe - q/trec_HeIII(z) # s^-1
     d = n/nHe - q/trec_HeIII(z) # s^-1
+
+    return d * yrbys # yr
+
+def dqdt_HeIII_noclump(q, z, emissivity):
+
+    yrbys = 3.154e7 # yr/s conversion factor
+
+    # Integrate qso emissivity from 4 to 10 Ry 
+    n = (emissivity(z)/(1.70*hplanck) *
+         (4**-1.7 - 10.0**-1.7)) # s^-1 Mpc^-3 
+    
+    d = n/nHe - q/trec_HeIII_noclump(z) # s^-1
+
+    return d * yrbys # yr
+
[…]

### 2018-03-21 qhe.py
Plot 1-Q instead of Q

@@ -409,11 +409,18 @@ def dqdz_HeIII_bolton_cHM12(q, z, emissivity):
     return dqdt_HeIII_bolton_cHM12(q, z, emissivity)*dtdz(z)
 
 
-def laplante16(ax):
+def laplante16(ax, minus=False):
 
     zc, qc = np.loadtxt('Data_new/laplante16_c.dat', unpack=True)
     zl, ql = np.loadtxt('Data_new/laplante16_l.dat', unpack=True)
-    zu, qu = np.loadtxt('Data_new/laplante16_u.dat', unpack=True) 
+    zu, qu = np.loadtxt('Data_new/laplante16_u.dat', unpack=True)
+
+    if minus:
+        z = np.linspace(12, 2, 1000)
+        assert(np.all(np.diff(zc) > 0))
+        q = np.interp(z, zc, qc)
+        ax.plot(z, 1-q, c='orange', lw=2, label=r'La Plante \& Trac 2016', zorder=8)
+        return 
 
     z = np.linspace(12, 2, 1000)
     assert(np.all(np.diff(zl) > 0))
@@ -425,30 +432,54 @@ def laplante16(ax):
     assert(np.all(np.diff(zc) > 0))
     q = np.interp(z, zc, qc)
     ax.plot(z, q, c='#7F9E9A', lw=2, label=r'La Plante \& Trac 2016', zorder=8)
+    return 
     
     return
 
-def puchwein18(ax):
+def puchwein18(ax, minus=False):
+
 
     dat = np.loadtxt("Data_new/puchwein18_qheiii.txt")
+
+    if minus:
+        ax.plot(1.0/dat[:,0]-1.0, 1-dat[:,8]/7.894736842105262720e-02, lw=2,
+                c='steelblue', label=r'Puchwein et al.\ 2018', zorder=9)
+        return 
+    
     ax.plot(1.0/dat[:,0]-1.0, dat[:,8]/7.894736842105262720e-02, lw=2,
             c='steelblue', label=r'Puchwein et al.\ 2018', zorder=9)
+    return
 
-def mcquinn09(ax):    
+def mcquinn09(ax, minus=False):    
 
     data = np.loadtxt("Data_new/mcquinn09.txt")
     z = data[:,0]
     x = data[:,1]
+
+    if minus: 
+        ax.plot(z, 1-x, lw=2,
+                c='k', label=r'McQuinn et al.\ 2009', zorder=9)
+        return
[…]

### 2018-03-21 Paper/paper.tex

@@
   % Remove notes?
+  % Do we really need a sample ID column?
   \caption{Quasar data sets}
@@
 \subsection{Binned luminosity function estimates}
+\label{sec:binnedlf}
 
@@
   \end{center}
-  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.  The
-    symbols show our inferred binned luminosity functions.  In each
+  \caption{Luminosity function estimates in redshift bins from $z=0.1$
+    to $6.5$.  The symbols show our inferred binned luminosity
+    functions from various data sets: sample ID 13 (red), 15 (green),
+    1 (blue), 17 (yellow), 8 (brown), 6 (light blue), 18 (pink), 10
+    (orange), and 11 (grey).  See Table~\ref{tab:samples} for
+    references.  Open circles in corresponding colours indicate
+    excluded incomplete bins for the respective data sets.  In each
     redshift bin, the black curve shows the best-fit double power law
     model, which is represented by the median of the posterior
-    probability distribution function.  Yellow curves show a random
-    draw from the posterior probability distribution function.  As
-    discussed in the text, luminosity bins that show a decrease in the
-    luminosity function at the faint end are deemed to be incomplete
-    are are removed from our analysis while fitting the double power
-    law model.  These bins are represented by open symbols in this
-    figure.  Each panel shows the number of quasars in the respective
-    redshift bin.  The number in parenthesis indicates the total
-    number of quasars in the bin, before excluding incomplete
-    bins.}
+    probability distribution function.  The grey shaded area shows the
+    one-sigma (68.26\%) uncertainty.  Each panel shows the number of
+    quasars in the respective redshift bin.  The numbers in
+    parentheses indicate the total number of reported quasars in the
+    respective redshift bin, before excluding incomplete bins.  See
+    Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
+    details.}
   \label{fig:mosaic}
@@
       transarency.  Extend plot to at least redshift 7.5.  Increase
-      legend handle length to match other figure.}}
+      legend handle length to match other figure. Should we add French
+      curve fits to this?}}
   \label{fig:rhoqso}
@@
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
-    \begin{tabular}{cc}
-    \includegraphics[width=0.5\textwidth]{emissivity.pdf}
+    \includegraphics[scale=0.65]{emissivity.pdf}
     % gammapi.py -- draw_emissivity() 
-    \end{tabular}
   \end{center}
-  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
-    Model luminosity functions are integrated down to $M_{1450}=-18$
-    in the left panel and $-20$ in the right panel.  For comparison,
-    various other published determinations of the 1~Ry emissivity of
-    quasars are also shown in both panels of Figure~\ref{fig:e912}.
-    The blue curve in these panels shows the AGN 1~Ry emissivity model
-    of \citet{2012ApJ...746..125H}, which is very similar to the model
-    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
-    show the determination from the fits of
-    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
-    to the 1~Ry emissivity evolution in the fits of
-    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
-    \citet{2015ApJ...813L...8M}. \gk{Add uncertainties on these fits,
-      perhaps by using emcee.}}
+  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
+    fraction down to a limiting magnitude.  Brown points show the
+    emissivity when the best-fit double power law luminosity functions
+    at respective redshifts are integrated down to $M_{1450}=-18$.
+    Black points show the integration limit when the limit is assumed
+    to be $M_{1450}=-21$.  For comparison, various other published
+    models of the 1~Ry emissivity of AGN are also shown.  The blue
+    curve in these panels shows the AGN 912~\AA\ emissivity model of
+    \citet{2012ApJ...746..125H}, which is very similar to the model of
+    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
+    determination from the fits of \citet{2015AA...578A..83G}.  The
+    maroon curve is the published fit to the 1~Ry emissivity evolution
+    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
+    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
+    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
+      HM12 Lstar limits.  Mention that Akiyama open and filled circles
+      are very close.}}
   \label{fig:e912}
-\end{figure}
+\end{figure*}
 
@@
 spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
-at $z\sim 1$.
+at $z\sim 1$.  \gk{Discuss comparison of expected number of quasars at
+  redshift 7 with UKIDSS.}
 
@@
 integrate the luminosity function down to $M_{1450}=-19$, while
-\citet{2015AA...578A..83G} integrate down to $M_{1450}=-18$.
-\textbf{[What are the limits for HM12 and MH15?]}
+\citet{2015AA...578A..83G} integrate down to $M_{1450}=-18$.  \gk{Add
+  discussion about Madau and Khaire's integration limit from Gabor's 8
+  March email here.  Also discussion on McGreer's data from Gabor's 12
+  March email.}
 
@@
 
+\begin{figure}
+  \begin{center}
+    % rtg2.draw_g_puc()
+    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
+  \end{center}
+  \caption{Evolution of the hydrogen photoionisation rate at low
+    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
+\end{figure}
+
 The black curve in Figure~\ref{fig:puc} shows the evolution of the
@@
 
-\begin{figure}
-  \begin{center}
-    % rtg2.draw_g_puc()
-    \includegraphics[width=\columnwidth,keepaspectratio]{g_puc.pdf}
-  \end{center}
-  \caption{Evolution of the hydrogen photoionisation rate at low
-    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
-\end{figure}
+\gk{Add discussion about Schulze point from Gabor's 8 March email
+  here.}
 

### 2018-03-26 Paper/paper.tex
Update text

@@
   % Do we really need a sample ID column?
+  % Say in caption or text that sample 13 is restricted to $z<4.7$
+  % Also that sample 17 overlaps with 8 for $M_{1450}<-26.73$
+  % Also that in sample 7 we rescaled selection probabilities 
   \caption{Quasar data sets}
   \label{tab:samples}
-  \begin{tabular}{crcllrSl}
+  \begin{tabular}{crcllrS}
     \hline
-    & ID & $z$ & Survey & Reference & Number & {Area} & Notes \\
-    & & & & & of quasars & {(deg$^2$)} & \\
+    & ID & $z$ & Survey & Reference & Number & {Area} \\
+    & & & & & of quasars & {(deg$^2$)} \\
     \hline
-    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 & \\
-    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 & \\
-    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 & \\
-    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 & \\
-    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 & Restricted to $z<4.7$ \\
-    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 & Overlaps with 8 for $M_{1450}<-26.73$ \\
-    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 & \\
-    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 & \\
-    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 & \\
-    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 & \\
-    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 & \\
-    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 & \\
-    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 & Rescaled selection probabilities \\
-    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 & \\
-    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 & \\
-    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 & \\
-    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 & \\
-    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 & \\
-    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 & \\
-    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 & \\
-    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 & \\
-    22. & 20 & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 & \\
+    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 \\
+    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
+    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
+    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
+    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 \\
+    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
+    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 \\
+    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 \\
+    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 \\
+    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 \\
+    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
+    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
+    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
+    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
+    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
+    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
+    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
+    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
+    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
+    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
+    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 \\
+    22. & 20 & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
     \hline
@@
 
-%--------------------
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
+      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
+      % gammapi.py -- draw_emissivity()
+    \end{tabular}
+  \end{center}
+  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
+    fraction down to a limiting magnitude.  Brown points show the
+    emissivity when the best-fit double power law luminosity functions
+    at respective redshifts are integrated down to $M_{1450}=-18$.
+    Black points show the integration limit when the limit is assumed
+    to be $M_{1450}=-21$.  For comparison, various other published
+    models of the 1~Ry emissivity of AGN are also shown.  The blue
+    curve in these panels shows the AGN 912~\AA\ emissivity model of
+    \citet{2012ApJ...746..125H}, which is very similar to the model of
+    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
+    determination from the fits of \citet{2015AA...578A..83G}.  The
+    maroon curve is the published fit to the 1~Ry emissivity evolution
+    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
+    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
+    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
+      HM12 Lstar limits.  Mention that Akiyama open and filled circles
+      are very close.}}
+  \label{fig:e912_2}
+\end{figure*}
 
@@
 Figure~\ref{fig:evoln} suggests that it should be possible to describe
-the quasar UV luminosity function evolution from $z\sim 7$ to $0$
-using far fewer number of parameters.  Such descriptions have been put
-forward in the literature for the X-ray and bolometric luminosity
-functions \citep[e.g.,][]{2007ApJ...654..731H, 2015MNRAS.451.1892A}.
+the quasar UV luminosity function evolution out to $z\sim 7$ using far
+fewer number of parameters.  Such descriptions have been developed in
+the literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
+bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
 Such ``global'' descriptions of the luminosity function evolution are
 useful as they give a continuous description of the luminosity
-function.  This makes them valuable while developing an understanding
-of the physics behind the luminosity function. We therefore obtain
-estimates of the luminosity function in which the evolution of the
-four parameters of the double power law models in
-Equation~(\ref{eqn:dpl}) is parameterised to write
+function.  This allows one to reduce the bias introduced by binning
+the data in arbitrary redshift bins.  By potentially allowing for
+extrapolations beyond the redshift range spanned by the data, such
+models are valuable for understanding of the physics behind the
+luminosity function.  Ideally, one would want to use physically
+meaningful parameters that govern the formation and evolution of the
+AGN population.  Unfortunately, such physical parameterisation is yet
+to be developed.  We therefore set up an empirical parameterisation to
+describe the evolution of the four parameters of the double power law
+model in Equation~(\ref{eqn:dpl}) as 
 \begin{align}
@@
 \end{align}
-where the $c_i$'s are the new model parameters.  The joint posterior
-probability distribution of these parameters can be now written as
+where the $c_{j,i}$'s are the new model parameters, and the $f_j$'s
+are functions that vary smoothly with redshift $z$.  The joint
+posterior probability distribution of these parameters can be now
+written as
 \begin{equation}
@@
 is now given by $\phi(M,z)$ with suitable normalisation.  Note that
-$\phi(M,z)$ is simply 
+$\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
+parameters in that equation are redshift-dependent, so that
 \begin{multline}
@@
 \end{multline}
-The ngative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
-straightforward generalisation of Equation~(\ref{eqn:S}), so that
+The negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
+straightforward generalisation of Equation~(\ref{eqn:S}), given by 
 \begin{multline}
@@
 and the integrals in the second term on the right-hand side are over
-the complete surveyed range of luminosity and redshift.
-
-We consider models in which the evolution of the four double power law
-parameter is modelled independently as in
-Equations~(\ref{eqn:global}).  This approach has been termed as
-``flexible double power law'' by \citet{2015MNRAS.451.1892A}.  For the
-parameters $\phi_*$, $M_*$ and $\alpha$ we assume that the functions
-$f_i$s in Equations~(\ref{eqn:global}) are Chebyshev polynomials in
-$1+z$.  Thus the functions $f_i$s are written as
+the complete surveyed range of luminosity and redshift, instead of
+redshift and luminosity bins.  We consider models in which the
+evolution of the four double power law parameter is modelled
+independently as in Equations~(\ref{eqn:global}).  This approach has
+been termed as ``flexible double power law'' by
+\citet{2015MNRAS.451.1892A}.  We present three such models in this
+paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
+models differ in the way they describe the evolution of the faint-end
+slope $\beta$ and in the selection of the AGN data.  The models are
+defined as follows.
+
+\begin{itemize}
+
+\item In Model 1, the parameters $\phi_*$, $M_*$ and $\alpha$ we
+  assume that the functions $f_i$'s in Equations~(\ref{eqn:global})
+  are Chebyshev polynomials in $(1+z)$.  Thus the functions $f_i$s are
+  written as
   \begin{equation}
@@
   where $c_{i,j}$ are the parameters that appear in
-Equations~(\ref{eqn:global}) and $T_j(1+z)$ are Chebyshev polynomials
-of the first kind.  We try successively higher orders of Chebyshev
-polynomials in order to arrive at a good fit with the data.  We find
-that $\phi_*$, $M_*$ and $\alpha$ prefer quadratic, cubic, and linear
-evolutions in $1+z$.
-
-The faint-end slope $\beta$ seems to require a break in its evolution
-at $z\sim 3$, as discussed in the previous section.  As a result, it
-is difficult to model the evolution of $\beta$ using the Chebyshev
-expansion of Equation~(\ref{eqn:cbs}).  Instead, we consider a double
-power law model for $\beta$ and write
-\begin{equation}
-  f_3(1+z)=h+\frac{f_0}{10^{a\zeta}+10^{b\zeta}},
+  Equations~(\ref{eqn:global}) and $T_j(1+z)$ are Chebyshev
+  polynomials of the first kind.  We try successively higher orders of
+  Chebyshev polynomials in order to arrive at a good fit with the
+  data.  As we discuss below, we find that $\phi_*$, $M_*$ and
+  $\alpha$ prefer quadratic, cubic, and linear evolutions in $(1+z)$.
+  The faint-end slope $\beta$ seems to require a break in its
+  evolution at $z\sim 3$, as discussed in the previous section.  As a
+  result, it is difficult to model the evolution of $\beta$ using the
+  Chebyshev expansion of Equation~(\ref{eqn:cbs}).  Instead, we
+  consider a double power law model for $\beta$ and write \gk{Is this
+    really only four parameters?}
+  \begin{equation}
+    f_3(1+z)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
   \end{equation}
@@
   \begin{equation}
-  \zeta = \log_{10}\left(\frac{1+z}{1+z_0}\right),
-\end{equation}
-thus resulting in a five-parameter model with parameters $h$, $f_0$,
-$z_0$, $a$ and $b$.  The parameters $a$ and $b$ thus determine the low
-and high redshift slopes of this evolution, with a break at redshift
-$z_0$.  This is similar to the model of \citet{2007ApJ...654..731H},
-who also favoured a broken power law model for the evolution of the
-faint-end slope of the bolometric luminosity function of quasars.
-
-Our resultant 14-parameter global model for the luminosity function
-evolution in shown in Figure~\ref{fig:mosaic_global}, in which the
-green curves show a random draw from the posterior probability
-distibution function.  For comparison, the symbols show the luminosity
-function binned in luminosity and redshift, and the yellow curves show
-the posterior distribution of the double power law luminosity
-functions in various redshift bins, as in Figure~\ref{fig:mosaic}.  We
-find that the global model is in excellent agreement with the binned
-models.  The agreement is poor for the BOSS quasars as these are not
-described by the global model, as discussed in the previous section.
+    \zeta = \log_{10}\left(\frac{1+z}{1+c_{3,2}}\right),
+  \end{equation}
+  thus resulting in a five-parameter model with parameters $c_{3,i}$.
+  The parameters $c_{3,3}$ and $c_{3,4}$ thus determine the low and
+  high redshift slopes of this evolution, with a break at redshift
+  $c_{3,2}$.  This is similar to the model of
+  \citet{2007ApJ...654..731H}, who also favoured a broken power law
+  model for the evolution of the faint-end slope of the bolometric
+  luminosity function of quasars.  Model 1 thus has 14 parameters.
+  Excluding those deemed to be dominated by systematic errors, as
+  discussed in the previous section, all of the remaining AGN from
+  Table~\ref{tab:samples} are included while fitting this model.
+
+\item Model 2 parameterises the luminosity function evolution in the
+  same way as Model 1, so that the faint-end slope evolution is
+  described by a double power law while the evolution of the other
+  parameters $\phi_*$, $M_*$ and $\alpha$ is described by,
+  respectively, quadratic, cubic, and linear polynomials in $(1+z)$.
+  The total number of parameter is 14.  However, while fitting this
+  model, we drop samples 7, 19, and 20 from the analysis.  The
+  selection function for these samples are not yet well-characterised.
+  Removing them allows us to understand the effect this has on the
+  favoured evolution model.
+
+\item In Model 3, we again exclude samples 7, 19, and 20 from the
+  analysis.  We also continue to describe the evolution of $\phi_*$,
+  $M_*$ and $\alpha$ by quadratic, cubic, and linear polynomials in
+  $(1+z)$, respectively.  But in this model, the evolution of the
+  faint-end slope $\beta$ is also assumed to be linear in $(1+z)$.
+  This model thus has just 11 parameters.
+\end{itemize}
+
+Figure~\ref{fig:mosaic_global} shows the three models in comparison
+with the binned fits from the previous section.  The shaded regions
+show the one-sigma (68.26\%) uncertainty.  The symbols show the
+luminosity function binned in luminosity and redshift, and the yellow
+shaded regions show the posterior distribution of the double power law
+luminosity functions in various redshift bins, as in
+Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
+error are excluded from Figure~\ref{fig:mosaic_global}.  All three
+global models are in excellent agreement with the binned models,
+although Model~1 performs better.
 
 Figure~\ref{fig:evoln_global} shows the parameter evolution in the
-global model, by comparing it with the results from the fits in
-individual redshift bins shown in Figure~\ref{fig:evoln}.  The
-agreement between the two models is very good, showing an evolution
-towards a steep faint-end slope of the luminosity function at high
-redshifts, a rapid brightening of the break luminosity.  Note that the
-redshift bins with BOSS qsos are not shown in
-Figure~\ref{fig:evoln_global}, which explains the difference from
-Figure~\ref{fig:evoln}.
+global models, by comparing it with the results from the fits in
+individual redshift bins shown in Figure~\ref{fig:evoln}.  All three
+models capture the steepening of the faint end of the luminosity
+function towards higher redshifts.  The best-fit form of Model~1 is
+shown by the black curves in Figure~\ref{fig:evoln_global}.  The
+accompanying grey shaded area depicts the one-sigma (68.26\%)
+uncertainty.  The model is in excellent agreement with the results of
+the fits in redshift bins discussed in the previous section.  The
+deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
+is again strikingly apparent.  So is the deviation of the SDSS and
+2SLAQ quasars at $z<0.6$.  This is an indirect justification of the
+data selection discussion previously in Section~\ref{sec:bins}.
+Unfortunately, this model suffers with a remarkably sharp break in the
+evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
+seen in Figure~\ref{fig:evoln_global}, the data seem to require this
+break, although it seems unlikely that such a sharp break at this
+redshift would be physical.  Model 1 thus serves to emphasize the
+necessity of better quality data at these redshifts.  Models 2 and 3
+are shown in Figure~\ref{fig:evoln_global} by the green and orange
+curves, respectively.  The corresponding best-fit parameter values are
+tabulated in Table~\ref{tab:global}.
 
@@
 down to different limits.  Similar to Figure~\ref{fig:evoln_global},
-symbols show the best fit parameters with 68\% uncertainties from the
+symbols show the best-fit values with 68\% uncertainties from the
 double power law fits to the data in redshift bins.  Black solid curve
 shows the best fit global model, and the coloured curves show a random
-sample drawn from the global posterior.  Bins with BOSS qsos are not
-shown.  The number density of qsos down to the limit of spectroscopic
-data is about 1 per $10^5$ cMpc$^3$ at its peak.  This density rapidly
-increases at low redshifts and then drops gradually at high redshifts.
-Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
-which the number density of faint qsos peaks are lower redshifts than
-that of the bright qsos.  While the number density of qsos with
-$M_*<-27$ peaks at $z\sim 2.5$, the number density of qsos with
-$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
-spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
-at $z\sim 1$.  \gk{Discuss comparison of expected number of quasars at
-  redshift 7 with UKIDSS.}
+sample drawn from the global posterior.  This number density evolution
+again highlights the systematic error in data at $z\sim 3$.  The
+number density of AGN down to the limit of spectroscopic data
+($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
+density rapidly increases at low redshifts and then drops gradually at
+high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
+downsizing feature in which the number density of faint qsos peaks are
+lower redshifts than that of the bright qsos.  While the number
+density of qsos with $M_*<-27$ peaks at $z\sim 2.5$, the number
+density of qsos with $M_*<-24$ peaks at $z\sim 2$.  At the faintest
+luminosity at which spectroscopic data exist, $M_*<-21$, the number
+density of qsos peaks at $z\sim 1$.  However, the difference between
+our three models is dramatically evidencet in Figure~\ref{fig:rhoqso}.
+Model~1 prefers a decrease in the number density of faint quasars at
+$z\sim 3$ followed by an increase at higher redshift.  This is caused
+by the rapid steepening of the faint-end slope in this model at this
+redshift.  Figure~\ref{fig:rhoqso} reveals another property of these
+models: when extrapolated, the AGN number density diverges in all
+three models are high redshifts.  This is result of the steep
+faint-end slope at high redshifts combined with the rapid brightening
+of the break luminosity at $z\sim 3$.  While no data exist at redshift
+$z>7.5$, this divergent behaviour is shared by previous models in the
+literature.  Figure~\ref{fig:rhoqso} also shows that although Models 2
+and 3 exhibit regular behaviour in the evolution of the AGN number
+density at $z\sim 3$, they do not fit the $z\sim 4$--$5$ data as well
+as Model 1.  \gk{Discuss comparison of expected number of quasars at
+  redshift 7 with UKIDSS.  Also discuss our new fit?}
 

### 2018-03-27 Paper/paper.tex
Update text

@@
 
-\section{Hydrogen photoionization rate}
+\section{Contribution of AGN to reionization}
+
+\subsection{Hydrogen-ionizing emissivity}
 
@@
 which suggest that faint quasars may have a steeper EUV spectrum.  We
-therefore also consider an SED of the form
+therefore assume an SED of the form
 \begin{equation}
@@
 \end{equation}
-for qsos with $M_{1450}<-23$.
+for AGN with $M_{1450}<-23$.
 
@@
 \end{equation}
-depending on the qso luminosity.  The corresponding physical volume
+depending on the AGN luminosity.  The corresponding physical volume
 emissivity is 
@@
 \end{equation}
-Figure~\ref{fig:e912} shows the resultant 1~Ry emissivity when the
-luminosity function is integrated down to $M_{1450}=-20$ (right panel)
-and when it is integrated down to $M_{1450}=-18$ (left panel).
-Similar to the previous figures, the black open circles in this figure
-show the result form individual redshift bins, while the black curve
-shown the result from best-fit global model.  Yellow curves show a
-random sample from the global posterior distribution.  For comparison,
-various other published determinations of the 1~Ry emissivity of
-quasars are also shown in both panels of Figure~\ref{fig:e912}.  The
-blue curve in these panels shows the AGN 1~Ry emissivity model of
-\citet{2012ApJ...746..125H}, which is very similar to the model of
-\citet{2007ApJ...654..731H}.  The red symbols with error bars show the
-determination from the fits of \citet{2015AA...578A..83G}.  The maroon
-curve is the published fit to the 1~Ry emissivity evolution in the
-fits of \citet{2017MNRAS.466.1160M}.  The green curve is the model of
-\citet{2015ApJ...813L...8M}.  Note that the integration limits for
-these other models are not homogeneous.  \citet{2017MNRAS.466.1160M}
-integrate the luminosity function down to $M_{1450}=-19$, while
-\citet{2015AA...578A..83G} integrate down to $M_{1450}=-18$.  \gk{Add
-  discussion about Madau and Khaire's integration limit from Gabor's 8
-  March email here.  Also discussion on McGreer's data from Gabor's 12
-  March email.}
-
-The 1~Ry emissivity increases rapidly from $z=0$ up to $z=2$ and then
-stays roughly constant until up to $z=3.5$.  At higher redshifts, due
-to the relatively steeper faint end slope of the luminosity function,
-the integration limit makes a large difference in the resultant
-emissivity.  For the conservative case, in which we integrate under
-the luminosity function down to $M_{1450}=-20$, the emissivity drops
-rapidly at $z>3.5$, and is only about 10--20\% higher than that in the
-\citet{2012ApJ...746..125H} model at $z\sim 6$.  However, in the model
-in which we integrate down to $M_{1450}=-18$, the emissivity is higher
-by a factor of almost 10 than that in the \citet{2012ApJ...746..125H}
-model at $z\sim 6$.  In this case, our derived emissivities are
-consistent with the values published by \citet{2015AA...578A..83G} at
-$z=4$--$6$, although they still fall short by a factor of $\sim 2$.
-Our derived emissivities are significantly smaller at $z>3.5$ than the
-model of \citet{2015ApJ...813L...8M}.
+The open and filled black circles with errorbars in
+Figure~\ref{fig:e912} show the resultant 1~Ry emissivity when the
+luminosity function is integrated down to $M_{1450}<-21$ (open
+circles) and when it is integrated down to $M_{1450}<-18$ (filled
+circles).  Redshift bins that were removed from analysis due to large
+systematic errors are not shown.  Similar to the previous figures, the
+black open circles in this figure show the result form individual
+redshift bins, while the black curve shown the result from best-fit
+global model.  Due to the problems with the global luminosity function
+models discussed above, we avoid using them to describe the emissivity
+evolution.  Instead, we describe the emissivity evolution by the
+5-parameter functional form \citep{2012ApJ...746..125H}
+\begin{equation}
+  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
+  \label{eqn:e912fit}
+\end{equation}
+We fit this to the points shown in Figure~\ref{fig:e912} assuming a
+Gaussian likelihood in each bin.  The corresponding best-fit curves
+and the corresponding one-sigma uncertainty is shown in red
+($M_{1450}<-18$) and blue ($M_{1450}<-21$).  The best-fit form of
+Equation~\ref{eqn:e912fit} is given by 
+\begin{multline}
+  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
+\end{multline}
+for $M_{1450}<-18$, and by 
+\begin{multline}
+  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
+\end{multline}
+for $M_{1450}<-21$.  The 1~Ry emissivity increases rapidly from $z=0$
+up to $z=2$ and then stays roughly constant until up to $z=3.5$.  At
+higher redshifts, due to the relatively steeper faint end slope of the
+luminosity function, the integration limit makes a large difference in
+the resultant emissivity.  For the conservative case, in which we
+integrate under the luminosity function down to $M_{1450}=-20$, the
+emissivity drops rapidly at $z>3.5$For comparison, various other
+published determinations of the 1~Ry emissivity of quasars are also
+shown in both panels of Figure~\ref{fig:e912}.  We now comment on the
+comparison of our results with these measurements.
+\citet{2009A&A...507..781S} combined data from the Hamburg/ESO survey
+and the SDSS to measure a quasar luminosity function at $z=0$ in their
+$B_J$ band to minimize host galaxy contribution.  We convert their
+$B_J$ magnitudes (Vega system) to $M_{1450}$ (AB) as
+\begin{equation}
+  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
+\end{equation}
+In this magnitude system, the luminosity function reported by
+\citet{2009A&A...507..781S} has a very faint break luminosity of
+$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
+integrate this luminosity function down to our limiting magnitudes of
+$M_{1450}=-18$ and $-21$.  The resultant values are shown by the open
+and closed brown circles at $z=0$ in Figure~\ref{fig:e912}.  Our
+emissivity values at $z=0$ lie in between the
+\citet{2009A&A...507..781S} measurements.  The convergence in the
+emissivity is slower in their measurements than in our models because
+of the shallower faint-end slope at this redshift in our model
+($\beta\sim -1.22$).  We discuss the 1~Ry emissivity and the
+corresponding hydrogen photoionization rate at $z=0$ below.
+
+The brown dashed curve in Figure~\ref{fig:e912} shows the AGN 1~Ry
+emissivity model of \citet{2012ApJ...746..125H}, which based on the
+bolometric luminosity function model of \citet{2007ApJ...654..731H}.
+Their assumed emissivity agrees reasonably well with our
+$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912}
+shows the model presented by \citet{2015ApJ...813L...8M}.  This model
+disagrees with ours rather severely at almost all redshifts in the
+range considered here.  Note that a direct comparison with
+\citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M} is
+difficult because these models integrate the luminosity function to a
+fixed fraction of the break luminosity $L_*$ instead of a fixed
+absolute magnitude.  The chosen limite by \citet{2012ApJ...746..125H}
+and \citet{2015ApJ...813L...8M} is $0.01L_*$.  Using a limit that
+depends on the break luminosity can be problematic as different quasar
+surveys used to develop these emissivity models often report
+strikingly different break luminosity values.  Even when these samples
+are homogeneized appropriately, have such an integration limit is only
+justified if the faint-end slope of the luminosity function is
+sufficiently shallow.
+
+The grey dashed curve shows the emissivity model of
+\citet{2017MNRAS.466.1160M}.  These authors integrate the luminosity
+function down to $M_{1450}=-19$.  However, their model strongly
+disagrees with our inference, potentially due to biases resulting from
+combining binned luminosity function estimates from different sources
+inhomogeneously.  The green curves in Figure~\ref{fig:e912} show the
+luminosity function derived from a variability-selected sample
+observed using the Sloan telescope and the Multiple Mirror Telescope
+(MMT) by \citet{2013A&A...551A..29P}.  This sample of 1877 quasars
+does not overlap with the variability-selected sample reported by the
+BOSS survey \citep{2013ApJ...773...14R}.  \citet{2013A&A...551A..29P}
+assum constant luminosity function slopes with a break at $z=2.2$ and
+assume a pure luminosity evolution.  This leads to a discontinuity in
+the emissivity evolution in their model at $z=2.2$.  We convert their
+$g$-band magnitudes to $M_{1450}$ and integrate the resultant
+luminosity function down to our two chosen integration limits.  The
+result is shown in Figure~\ref{fig:e912} by the solid and dashed
+orange curves, which correspond to $M_{1450}<-21$ and $-18$,
+respectively.  For $M_{1450}<-21$, our models are in reasonable
+agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
+models disagree by 10--30\%.  Figure~\ref{fig:e912} also shows the
+model presented by \citet{2016A&A...587A..41P}.  We consider their
+PLE$+$LEDE model, in which the faint-end slope is assumed to stay
+constant with redshift.  Although the emissivity evolution in this
+model is continuous at $z=2.2$, it is not smooth.  This model agrees
+with our $M_{1450}<-18$ result to a better degree relative to the
+\citet{2013A&A...551A..29P} model.  We also compare our result with
+the PLE$+$LEDE luminosity function model presented by
+\citet{2017A&A...608A..64C} by reanalysing the
+\citet{2016A&A...587A..41P} sample with an improved $K$-correction
+implementation.  \citet{2017ApJ...847L..15O} recently fit a double
+power law luminosity function model to a combined binned samples of
+\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
+\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
+photometric redshift $z\sim 6$ reported by
+\citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
+orange rectangle in Figure~\ref{fig:e912}.  The lower side of the
+rectangle corresponds to the emissivity for the
+\citet{2017ApJ...847L..15O} model excluding the
+\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
+the emissivity is higher; this is shown by the upper end of the
+rectangle.  The open rectangle corresponds to $M_{1450}<-18$ and the
+closed rectangle corresponds to $M_{1450}<-21$.
+
+The red open cirles with error bars in Figure~\ref{fig:e912} show the
+determination from the fits of \citet{2015AA...578A..83G}.  These
+authors also choose a break luminosity-dependent integration limit of
+$0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their model.
+The resultant emissivities are factors of 2 to 3 higher than our
+determinations for $z=4$--$6$.  This is puzzling at first sight,
+because the AGN candidates reported by \citet{2015AA...578A..83G} are
+consistent with our luminosity function estimates obtained without
+these candidates (see Appendix~\ref{sec:conv}).  Our luminosity
+function are also somewhat steeper than those reported by
+\citet{2015AA...578A..83G}.  The discrepancy is explained by the
+difference in the two luminosity function models at intermediate
+magnitudes.  We find that the data prefer a much brighter break
+luminosity than that infered by \citet{2015AA...578A..83G}.  This
+reduces our emissivities relative to their estimates.  We go into this
+issue in further detail in Appendix~\ref{sec:conv}.
+
+\citet{2018AJ....155..131M} recently extended their previous Stripe~82
+AGN sample by 1.5 magnitude and fit a double power law luminosity
+function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
+$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
+$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
+than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
+LF to our cosmology and assumed our SED obtain the emissivities shown
+by the green circles in Figure~\ref{fig:e912}.  Again the open and
+filled circles corresponds to our two integration limits.  Our
+emissivity agrees with the measurement of \citet{2018AJ....155..131M}
+for $M_{1450}<-21$ but is higher than their measurement for
+$M_{1450}<-18$, which is not surprising due to the difference in the
+luminosity function slopes.  The emissivity derived from the
+luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
+in Figure~\ref{fig:e912}.  These authors report 1668 AGN candidates at
+$3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
+faint-end slope is very flat ($\beta=-1.3\pm 0.05$), inconsistent with
+our determination at all redshifts.  Their inferred emissivity is
+consistent with our estimate for $M_{1450}\sim -21$.  Their emissivity
+does not change significantly with the integration limit thanks to the
+shallow slope.  We also compare our emissivities with the
+determinations reported by \citet{2012ApJ...755..169M} at $z\sim 3.2$
+and $z\sim 4$.  Their emissivity in reasonably agreement with our
+model for $M_{1450}<-21$ at $z\sim 3.2$.  But their $M_{1450}<-18$
+emissivity disagrees with all other high-redshift estimates, possibly
+indicating a systematic error.  Our emissivity estimates are in good
+agreement with those of \citet{2018MNRAS.474.2904P}.  Mention
+Bongiorno.
 
@@
 \end{figure*}
+
+\subsection{Hydrogen photoionization rate}
 
@@
 
-\section{Helium reionization}
+\subsection{Helium reionization}
 
@@
 Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.
+Discuss Mitra et al. 2018 and Khaire and Srianand 2018.  See Gabor's
+email of 14 March 13:18.
 
@@
 \end{itemize}
+
+Some next steps at $z>4$: 1. include extended objects at faint
+magntiudes that could be impacted by host galaxy light, 2. take
+follow-up spectroscopy to confirm a fration of these as high-z broad
+line AGN, 3. carefully assess host galaxy contamination.  See Gabor's
+email of 14 March 13:18.
 

### 2018-03-28 Paper/paper.tex
Add Table B1

@@
 \def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
-\usepackage{supertabular}
+\usepackage{dcolumn}
+\newcolumntype{.}{D{.}{.}{2.6}}
 
@@
 details.
+
+\begin{table*}
+  % gammapi.py and tabulate_emissivities.py. 
+  \caption{The 912\,\AA\ and 1450\,\AA\ comoving emissivities
+    corresponding to the double power law luminosity function models
+    in redshift bins presented in Table~\ref{tab:bins} for two
+    integration limits.  These emissivities are shown in
+    Figure~\ref{fig:e912_2}.  The units are
+    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.}
+  \label{tab:emissivity_bins}
+  \begin{tabular}{cccc....}
+    \hline
+    $\langle z\rangle$ &
+    $z_\mathrm{bin}$ &
+    $z_\mathrm{min}$ &
+    $z_\mathrm{max}$ &
+    \multicolumn{1}{c}{$\epsilon_{912}$} &
+    \multicolumn{1}{c}{$\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\epsilon_{912}$} &
+    \multicolumn{1}{c}{$\epsilon_{1450}$} \\
+    &
+    &
+    &
+    &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} \\
+    \hline
+    0.31 & 0.25 & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.71^{+0.03}_{-0.03} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
+    0.50 & 0.50 & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.02}_{-0.02} & 0.58^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
+    0.72 & 0.70 & 0.60 & 0.80 & 1.73^{+0.06}_{-0.05} & 2.31^{+0.07}_{-0.06} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.02} \\
+    0.91 & 0.90 & 0.80 & 1.00 & 2.85^{+0.16}_{-0.16} & 3.77^{+0.20}_{-0.19} & 2.10^{+0.05}_{-0.05} & 2.79^{+0.06}_{-0.06} \\
+    1.10 & 1.10 & 1.00 & 1.20 & 3.71^{+0.11}_{-0.10} & 4.94^{+0.15}_{-0.13} & 2.91^{+0.05}_{-0.05} & 3.87^{+0.06}_{-0.06} \\
+    1.30 & 1.30 & 1.20 & 1.40 & 5.69^{+0.23}_{-0.24} & 7.52^{+0.32}_{-0.30} & 4.46^{+0.10}_{-0.09} & 5.91^{+0.11}_{-0.12} \\
+    1.50 & 1.50 & 1.40 & 1.60 & 7.04^{+0.22}_{-0.22} & 9.34^{+0.26}_{-0.31} & 5.59^{+0.09}_{-0.11} & 7.41^{+0.13}_{-0.13} \\
+    1.71 & 1.70 & 1.60 & 1.80 & 7.69^{+0.18}_{-0.18} & 10.23^{+0.24}_{-0.26} & 6.71^{+0.10}_{-0.11} & 8.90^{+0.13}_{-0.14} \\
+    1.98 & 2.00 & 1.80 & 2.20 & 10.59^{+0.36}_{-0.36} & 14.08^{+0.43}_{-0.42} & 7.93^{+0.13}_{-0.14} & 10.52^{+0.19}_{-0.17} \\
+    2.25 & 2.25 & 2.20 & 2.30 & 11.34^{+0.35}_{-0.37} & 14.97^{+0.48}_{-0.50} & 10.06^{+0.20}_{-0.20} & 13.37^{+0.26}_{-0.23} \\
+    2.35 & 2.35 & 2.30 & 2.40 & 9.30^{+0.30}_{-0.30} & 12.29^{+0.36}_{-0.35} & 8.02^{+0.15}_{-0.15} & 10.65^{+0.22}_{-0.20} \\
+    2.45 & 2.45 & 2.40 & 2.50 & 8.06^{+0.24}_{-0.24} & 10.67^{+0.30}_{-0.26} & 7.16^{+0.13}_{-0.15} & 9.49^{+0.17}_{-0.18} \\
+    2.65 & 2.65 & 2.60 & 2.70 & 6.55^{+0.16}_{-0.17} & 8.70^{+0.21}_{-0.20} & 6.46^{+0.15}_{-0.15} & 8.55^{+0.20}_{-0.20} \\
+    2.75 & 2.75 & 2.70 & 2.80 & 7.44^{+0.24}_{-0.22} & 9.93^{+0.30}_{-0.31} & 7.17^{+0.20}_{-0.20} & 9.51^{+0.27}_{-0.25} \\
+    2.85 & 2.85 & 2.80 & 2.90 & 7.94^{+0.28}_{-0.29} & 10.45^{+0.42}_{-0.41} & 7.48^{+0.29}_{-0.28} & 9.95^{+0.36}_{-0.35} \\
+    2.95 & 2.95 & 2.90 & 3.00 & 7.93^{+0.34}_{-0.34} & 10.51^{+0.45}_{-0.46} & 6.83^{+0.20}_{-0.21} & 9.09^{+0.28}_{-0.28} \\
+    3.05 & 3.05 & 3.00 & 3.10 & 7.18^{+0.38}_{-0.36} & 9.59^{+0.47}_{-0.50} & 6.24^{+0.20}_{-0.21} & 8.29^{+0.34}_{-0.30} \\
+    3.15 & 3.15 & 3.10 & 3.20 & 9.99^{+0.95}_{-1.03} & 13.14^{+1.38}_{-1.56} & 7.01^{+0.35}_{-0.35} & 9.34^{+0.41}_{-0.47} \\
+    3.25 & 3.25 & 3.20 & 3.30 & 8.27^{+0.94}_{-1.01} & 11.05^{+1.27}_{-1.17} & 6.06^{+0.35}_{-0.36} & 8.07^{+0.49}_{-0.50} \\
+    3.34 & 3.35 & 3.30 & 3.40 & 12.00^{+2.57}_{-2.55} & 16.10^{+3.44}_{-3.31} & 7.21^{+0.61}_{-0.74} & 9.59^{+0.91}_{-0.93} \\
+    3.44 & 3.45 & 3.40 & 3.50 & 4.47^{+0.52}_{-0.51} & 5.85^{+0.61}_{-0.64} & 4.37^{+0.45}_{-0.47} & 5.73^{+0.56}_{-0.67} \\
+    3.88 & 3.90 & 3.70 & 4.10 & 4.36^{+1.44}_{-1.39} & 5.76^{+1.98}_{-1.84} & 2.54^{+0.44}_{-0.44} & 3.45^{+0.72}_{-0.66} \\
+    4.35 & 4.40 & 4.10 & 4.70 & 4.13^{+2.15}_{-1.95} & 5.40^{+2.60}_{-2.57} & 1.81^{+0.58}_{-0.52} & 2.42^{+0.64}_{-0.68} \\
+    4.92 & 5.10 & 4.70 & 5.50 & 2.51^{+0.89}_{-0.86} & 3.45^{+1.28}_{-1.31} & 0.97^{+0.20}_{-0.18} & 1.29^{+0.25}_{-0.26} \\
+    6.00 & 6.00 & 5.50 & 6.50 & 0.65^{+0.30}_{-0.24} & 0.96^{+0.36}_{-0.37} & 0.21^{+0.04}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
+    \hline
+  \end{tabular}
+\end{table*}
 
@@
 
-We make the homogenised quasar data and the code developing and
-analysing luminosity function models available at
-\url{https://github.com/gkulkarni/QLF} under the MIT open source
-software license.  \gk{Remember to make URL public and set appropriate
-  license upon publication of paper.  Add requirement of citation to
-  license.}
+We make the code and data used in this work publicly available at
+\url{https://github.com/gkulkarni/QLF}.  This includes homogenised AGN
+catalogues and selection functions and the code used for developing
+and analysing luminosity function models.  \gk{Make URL public. Set
+  appropriate license.  Take permission from other authors.  Set up a
+  DOI.}
 

### 2018-03-29 Paper/paper.tex
Update Appendix B

@@
 \newcolumntype{.}{D{.}{.}{2.6}}
+\newcolumntype{d}{D{.}{.}{2.3}}
 
@@
 \subsection{Hydrogen-ionizing emissivity}
+\label{sec:e912}
 
@@
 \subsection{Hydrogen photoionization rate}
+\label{sec:gammahi}
 
@@
 
-\section{Table of emissivities}
+\section{Tables of emissivities and photoionisation rates}
 \label{sec:tables}
 
-Table~\ref{tab:gamma} shows the LyC emissivities and the resultant
-hydrogen photoionisation rate due to quasars down to magnitudes
-$M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the curves
-shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
-photoionisation rate calculation assumes an HI column density given by
-\citet{2012ApJ...746..125H}.  See Sections XX and XX for further
-details.
+Table~\ref{tab:emissivity_bins} shows the 912\,\AA\ and
+1450\,\AA\ comoving emissivities obtained in various redshift bins
+with the one-sigma (68.26\%) uncertainties.  Redshift bins severely
+affected by systematic errors are also shown.  The result of the model
+presented in Equation~(\ref{eqn:e912fit}), which describes the
+emissivity evolution using a smooth function, is tabulated in
+Table~\ref{tab:gamma2}, along with the hydrogen photoionization rate
+computed in Section~\ref{sec:gammahi}.  In both tables, we show
+results for our two integration limits of $M_{1450}<-18$ and
+$M_{1450}<-21$.  These tables describe the curves shown in
+Figures~\ref{fig:e912} and \ref{fig:gammapi}.  Note that the
+photoionisation rate calculation assumes an \HI\ column density
+distribution given by \citet{2012ApJ...746..125H} and extrapolates
+this to high redshifts.
 
@@
     Figure~\ref{fig:e912_2}.  The units are
-    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.}
+    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.  Uncertainties
+    are one-sigma (68.26\%).}
   \label{tab:emissivity_bins}
@@
 \begin{table*}
-  \caption{LyC emissivities and the resultant hydrogen photoionisation
-    rate due to quasars down to magnitudes $M_{1450}=-18$ and
-    $M_{1450}=-21$.  These numbers describe the curves shown in
-    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The photoionisation
-    rate calculation assumes an HI column density given by
-    \citet{2012ApJ...746..125H}.  See Sections XX and XX for further
-    details.  \gk{Do we need another table for the emissivities from
-      individual models?}}
-  \label{tab:gamma}
-  \begin{tabular}{ccccc}
+  % rtg2.py and tabulate_emissivities_global.py.
+  % Check these values once again.
+  \caption{The 912\,\AA\ and 1450\,\AA\ comoving emissivities obtained
+    by fitting Equation~(\ref{eqn:e912fit}) to the selected redshift
+    bins from Table~\ref{tab:emissivity_bins}, and the corresponding
+    hydrogen photoionisation rates with the one-sigma (68.26\%)
+    uncertainties.  The emissivities are extrapolated here up to
+    $z=15$.  Emissivity units are
+    erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$, and photoionisation rate
+    units are s$^{-1}$.  These values are shown in
+    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  See
+    Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.}
+  \label{tab:gamma2}
+  \begin{tabular}{d......}
     \hline
-    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
-    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \multicolumn{1}{c}{$z$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} & 
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} &
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} \\ 
+    &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} \\
     \hline
-    0.0 & 5.090e--14 & 2.822e--14 & 1.383e+23 & 7.011e+22 \\
-    0.1 & 7.036e--14 & 4.069e--14 & 2.231e+23 & 1.176e+23 \\
-    0.2 & 9.461e--14 & 5.690e--14 & 3.419e+23 & 1.877e+23 \\
-    0.3 & 1.248e--13 & 7.787e--14 & 5.019e+23 & 2.873e+23 \\
-    0.4 & 1.614e--13 & 1.041e--13 & 7.098e+23 & 4.240e+23 \\
-    0.5 & 2.051e--13 & 1.363e--13 & 9.717e+23 & 6.056e+23 \\
-    0.6 & 2.566e--13 & 1.750e--13 & 1.293e+24 & 8.401e+23 \\
-    0.7 & 3.164e--13 & 2.208e--13 & 1.676e+24 & 1.135e+24 \\
-    0.8 & 3.845e--13 & 2.736e--13 & 2.124e+24 & 1.495e+24 \\
-    0.9 & 4.605e--13 & 3.330e--13 & 2.636e+24 & 1.923e+24 \\
-    1.0 & 5.433e--13 & 3.980e--13 & 3.208e+24 & 2.419e+24 \\
-    1.1 & 6.309e--13 & 4.667e--13 & 3.835e+24 & 2.978e+24 \\
-    1.2 & 7.207e--13 & 5.367e--13 & 4.507e+24 & 3.589e+24 \\
-    1.3 & 8.092e--13 & 6.046e--13 & 5.216e+24 & 4.237e+24 \\
-    1.4 & 8.931e--13 & 6.675e--13 & 5.946e+24 & 4.902e+24 \\
-    1.5 & 9.715e--13 & 7.246e--13 & 6.684e+24 & 5.559e+24 \\
-    1.6 & 1.037e--12 & 7.693e--13 & 7.414e+24 & 6.185e+24 \\
-    1.7 & 1.087e--12 & 8.003e--13 & 8.117e+24 & 6.754e+24 \\
-    1.8 & 1.131e--12 & 8.246e--13 & 8.779e+24 & 7.245e+24 \\
-    1.9 & 1.163e--12 & 8.364e--13 & 9.384e+24 & 7.642e+24 \\
-    2.0 & 1.183e--12 & 8.386e--13 & 9.917e+24 & 7.932e+24 \\
-    2.1 & 1.195e--12 & 8.322e--13 & 1.037e+25 & 8.112e+24 \\
-    2.2 & 1.194e--12 & 8.156e--13 & 1.073e+25 & 8.184e+24 \\
-    2.3 & 1.187e--12 & 7.941e--13 & 1.099e+25 & 8.153e+24 \\
-    2.4 & 1.168e--12 & 7.636e--13 & 1.115e+25 & 8.030e+24 \\
-    2.5 & 1.145e--12 & 7.308e--13 & 1.121e+25 & 7.827e+24 \\
-    2.6 & 1.112e--12 & 6.915e--13 & 1.118e+25 & 7.558e+24 \\
-    2.7 & 1.075e--12 & 6.516e--13 & 1.105e+25 & 7.237e+24 \\
-    2.8 & 1.031e--12 & 6.080e--13 & 1.085e+25 & 6.877e+24 \\
-    2.9 & 9.835e--13 & 5.648e--13 & 1.057e+25 & 6.490e+24 \\
-    3.0 & 9.319e--13 & 5.207e--13 & 1.022e+25 & 6.087e+24 \\
-    3.1 & 8.780e--13 & 4.774e--13 & 9.824e+24 & 5.676e+24 \\
-    3.2 & 8.227e--13 & 4.354e--13 & 9.385e+24 & 5.267e+24 \\
-    3.3 & 7.658e--13 & 3.945e--13 & 8.914e+24 & 4.864e+24 \\
-    3.4 & 7.102e--13 & 3.565e--13 & 8.422e+24 & 4.473e+24 \\
-    3.5 & 6.545e--13 & 3.202e--13 & 7.916e+24 & 4.098e+24 \\
-    3.6 & 6.006e--13 & 2.865e--13 & 7.406e+24 & 3.740e+24 \\
-    3.7 & 5.487e--13 & 2.554e--13 & 6.898e+24 & 3.402e+24 \\
-    3.8 & 4.988e--13 & 2.265e--13 & 6.399e+24 & 3.085e+24 \\
-    3.9 & 4.521e--13 & 2.006e--13 & 5.912e+24 & 2.789e+24 \\
-    4.0 & 4.082e--13 & 1.769e--13 & 5.443e+24 & 2.515e+24 \\
-    4.1 & 3.671e--13 & 1.554e--13 & 4.993e+24 & 2.262e+24 \\
-    4.2 & 3.295e--13 & 1.363e--13 & 4.566e+24 & 2.029e+24 \\
-    4.3 & 2.948e--13 & 1.192e--13 & 4.163e+24 & 1.816e+24 \\
-    4.4 & 2.630e--13 & 1.039e--13 & 3.784e+24 & 1.622e+24 \\
-    4.5 & 2.342e--13 & 9.045e--14 & 3.431e+24 & 1.445e+24 \\
-    4.6 & 2.081e--13 & 7.854e--14 & 3.102e+24 & 1.286e+24 \\
-    4.7 & 1.845e--13 & 6.803e--14 & 2.798e+24 & 1.141e+24 \\
-    4.8 & 1.633e--13 & 5.883e--14 & 2.518e+24 & 1.011e+24 \\
-    4.9 & 1.444e--13 & 5.078e--14 & 2.262e+24 & 8.944e+23 \\
-    5.0 & 1.274e--13 & 4.373e--14 & 2.027e+24 & 7.898e+23 \\
+    0.0 & 23.36^{+0.38}_{-0.20} & 23.18^{+0.25}_{-0.22} & 23.01^{+0.23}_{-0.16} & 22.83^{+0.12}_{-0.15} & -13.38^{+0.10}_{-0.06} & -13.57^{+0.06}_{-0.05} \\
+    0.1 & 23.54^{+0.29}_{-0.16} & 23.35^{+0.18}_{-0.17} & 23.24^{+0.18}_{-0.13} & 23.06^{+0.09}_{-0.11} & -13.22^{+0.08}_{-0.06} & -13.41^{+0.05}_{-0.04} \\
+    0.2 & 23.71^{+0.21}_{-0.14} & 23.51^{+0.13}_{-0.12} & 23.45^{+0.14}_{-0.10} & 23.27^{+0.07}_{-0.09} & -13.07^{+0.06}_{-0.05} & -13.26^{+0.04}_{-0.03} \\
+    0.3 & 23.85^{+0.16}_{-0.10} & 23.66^{+0.10}_{-0.08} & 23.64^{+0.10}_{-0.07} & 23.46^{+0.05}_{-0.06} & -12.94^{+0.05}_{-0.04} & -13.12^{+0.03}_{-0.03} \\
+    0.4 & 23.99^{+0.11}_{-0.08} & 23.80^{+0.07}_{-0.06} & 23.81^{+0.07}_{-0.06} & 23.63^{+0.04}_{-0.04} & -12.82^{+0.04}_{-0.04} & -12.99^{+0.03}_{-0.02} \\
+    0.5 & 24.11^{+0.08}_{-0.06} & 23.93^{+0.05}_{-0.04} & 23.95^{+0.05}_{-0.04} & 23.78^{+0.03}_{-0.03} & -12.71^{+0.03}_{-0.03} & -12.87^{+0.02}_{-0.02} \\
+    0.6 & 24.23^{+0.05}_{-0.04} & 24.06^{+0.03}_{-0.02} & 24.09^{+0.04}_{-0.03} & 23.93^{+0.02}_{-0.02} & -12.60^{+0.03}_{-0.03} & -12.76^{+0.02}_{-0.02} \\
+    0.7 & 24.34^{+0.03}_{-0.03} & 24.18^{+0.02}_{-0.02} & 24.21^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.51^{+0.03}_{-0.03} & -12.66^{+0.02}_{-0.02} \\
+    0.8 & 24.44^{+0.03}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.32^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.42^{+0.03}_{-0.03} & -12.57^{+0.02}_{-0.02} \\
+    0.9 & 24.54^{+0.02}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.02}_{-0.01} & 24.29^{+0.01}_{-0.01} & -12.35^{+0.02}_{-0.03} & -12.48^{+0.02}_{-0.02} \\
+    1.0 & 24.63^{+0.02}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.02}_{-0.01} & 24.38^{+0.01}_{-0.01} & -12.28^{+0.02}_{-0.03} & -12.40^{+0.02}_{-0.02} \\
+    1.1 & 24.71^{+0.02}_{-0.02} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.47^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.03} & -12.33^{+0.02}_{-0.02} \\
+    1.2 & 24.78^{+0.02}_{-0.02} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.55^{+0.01}_{-0.01} & -12.16^{+0.03}_{-0.03} & -12.27^{+0.02}_{-0.02} \\
+    1.3 & 24.85^{+0.01}_{-0.02} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.11^{+0.03}_{-0.03} & -12.22^{+0.02}_{-0.02} \\
+    1.4 & 24.91^{+0.01}_{-0.02} & 24.82^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.18^{+0.02}_{-0.02} \\
+    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.74^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
+    1.6 & 24.99^{+0.02}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.02^{+0.03}_{-0.03} & -12.12^{+0.02}_{-0.02} \\
+    1.7 & 25.03^{+0.02}_{-0.02} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.00^{+0.03}_{-0.03} & -12.11^{+0.02}_{-0.02} \\
+    1.8 & 25.05^{+0.02}_{-0.02} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.02}_{-0.01} & 24.86^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.10^{+0.02}_{-0.02} \\
+    1.9 & 25.07^{+0.02}_{-0.02} & 24.99^{+0.01}_{-0.01} & 24.96^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.09^{+0.03}_{-0.03} \\
+    2.0 & 25.08^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.98^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.05} & -12.09^{+0.03}_{-0.03} \\
+    2.1 & 25.09^{+0.03}_{-0.02} & 25.01^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.02} & 24.91^{+0.02}_{-0.02} & -11.99^{+0.05}_{-0.05} & -12.10^{+0.03}_{-0.03} \\
+    2.2 & 25.09^{+0.03}_{-0.03} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.00^{+0.05}_{-0.06} & -12.11^{+0.04}_{-0.03} \\
+    2.3 & 25.09^{+0.04}_{-0.04} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.03} & -12.01^{+0.05}_{-0.07} & -12.12^{+0.04}_{-0.04} \\
+    2.4 & 25.08^{+0.04}_{-0.04} & 25.00^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.04} & 24.91^{+0.03}_{-0.03} & -12.03^{+0.06}_{-0.08} & -12.14^{+0.04}_{-0.04} \\
+    2.5 & 25.07^{+0.04}_{-0.05} & 24.99^{+0.03}_{-0.03} & 25.01^{+0.04}_{-0.04} & 24.89^{+0.03}_{-0.04} & -12.04^{+0.06}_{-0.08} & -12.16^{+0.05}_{-0.05} \\
+    2.6 & 25.06^{+0.05}_{-0.06} & 24.97^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.05} & 24.88^{+0.04}_{-0.04} & -12.06^{+0.07}_{-0.09} & -12.18^{+0.05}_{-0.05} \\
+    2.7 & 25.04^{+0.05}_{-0.07} & 24.96^{+0.04}_{-0.04} & 25.00^{+0.05}_{-0.05} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.10} & -12.21^{+0.05}_{-0.05} \\
+    2.8 & 25.02^{+0.06}_{-0.07} & 24.93^{+0.05}_{-0.04} & 24.99^{+0.06}_{-0.06} & 24.84^{+0.05}_{-0.04} & -12.11^{+0.07}_{-0.11} & -12.24^{+0.06}_{-0.06} \\
+    2.9 & 25.01^{+0.06}_{-0.08} & 24.91^{+0.05}_{-0.05} & 24.98^{+0.06}_{-0.07} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.12} & -12.27^{+0.06}_{-0.06} \\
+    3.0 & 24.98^{+0.06}_{-0.09} & 24.88^{+0.05}_{-0.05} & 24.96^{+0.06}_{-0.07} & 24.78^{+0.05}_{-0.05} & -12.17^{+0.08}_{-0.12} & -12.31^{+0.06}_{-0.07} \\
+    3.1 & 24.96^{+0.07}_{-0.10} & 24.85^{+0.05}_{-0.06} & 24.94^{+0.07}_{-0.08} & 24.75^{+0.06}_{-0.05} & -12.20^{+0.09}_{-0.13} & -12.35^{+0.07}_{-0.07} \\
+    3.2 & 24.93^{+0.07}_{-0.10} & 24.82^{+0.06}_{-0.06} & 24.91^{+0.07}_{-0.09} & 24.71^{+0.06}_{-0.05} & -12.23^{+0.09}_{-0.14} & -12.39^{+0.07}_{-0.08} \\
+    3.3 & 24.91^{+0.08}_{-0.11} & 24.79^{+0.06}_{-0.06} & 24.89^{+0.08}_{-0.09} & 24.68^{+0.06}_{-0.06} & -12.26^{+0.10}_{-0.15} & -12.43^{+0.07}_{-0.08} \\
+    3.4 & 24.88^{+0.08}_{-0.12} & 24.75^{+0.06}_{-0.07} & 24.86^{+0.08}_{-0.09} & 24.64^{+0.07}_{-0.06} & -12.30^{+0.10}_{-0.17} & -12.47^{+0.07}_{-0.09} \\
+    3.5 & 24.85^{+0.09}_{-0.14} & 24.72^{+0.07}_{-0.07} & 24.83^{+0.08}_{-0.10} & 24.59^{+0.07}_{-0.06} & -12.34^{+0.11}_{-0.18} & -12.52^{+0.08}_{-0.09} \\
+    3.6 & 24.82^{+0.10}_{-0.15} & 24.68^{+0.07}_{-0.08} & 24.80^{+0.09}_{-0.11} & 24.55^{+0.07}_{-0.06} & -12.38^{+0.11}_{-0.19} & -12.56^{+0.08}_{-0.10} \\
+    3.7 & 24.79^{+0.10}_{-0.16} & 24.64^{+0.07}_{-0.08} & 24.77^{+0.09}_{-0.11} & 24.51^{+0.07}_{-0.06} & -12.42^{+0.12}_{-0.20} & -12.61^{+0.08}_{-0.10} \\
+    3.8 & 24.75^{+0.10}_{-0.16} & 24.59^{+0.07}_{-0.09} & 24.73^{+0.10}_{-0.12} & 24.47^{+0.07}_{-0.07} & -12.46^{+0.12}_{-0.21} & -12.66^{+0.08}_{-0.11} \\
+    3.9 & 24.72^{+0.11}_{-0.17} & 24.55^{+0.07}_{-0.09} & 24.70^{+0.10}_{-0.13} & 24.42^{+0.07}_{-0.07} & -12.50^{+0.13}_{-0.22} & -12.72^{+0.08}_{-0.11} \\
+    4.0 & 24.68^{+0.11}_{-0.18} & 24.51^{+0.07}_{-0.09} & 24.66^{+0.10}_{-0.14} & 24.37^{+0.07}_{-0.08} & -12.54^{+0.13}_{-0.24} & -12.77^{+0.08}_{-0.12} \\
+    4.1 & 24.65^{+0.11}_{-0.20} & 24.46^{+0.07}_{-0.10} & 24.63^{+0.11}_{-0.16} & 24.33^{+0.06}_{-0.09} & -12.58^{+0.13}_{-0.25} & -12.82^{+0.08}_{-0.12} \\
+    4.2 & 24.61^{+0.12}_{-0.21} & 24.42^{+0.07}_{-0.10} & 24.58^{+0.12}_{-0.16} & 24.28^{+0.06}_{-0.10} & -12.63^{+0.14}_{-0.27} & -12.88^{+0.08}_{-0.12} \\
+    4.3 & 24.58^{+0.13}_{-0.23} & 24.37^{+0.07}_{-0.11} & 24.54^{+0.12}_{-0.17} & 24.23^{+0.07}_{-0.10} & -12.67^{+0.14}_{-0.29} & -12.94^{+0.09}_{-0.13} \\
+    4.4 & 24.54^{+0.12}_{-0.24} & 24.32^{+0.08}_{-0.11} & 24.50^{+0.13}_{-0.18} & 24.17^{+0.07}_{-0.11} & -12.72^{+0.14}_{-0.30} & -13.00^{+0.09}_{-0.13} \\
+    4.5 & 24.50^{+0.13}_{-0.26} & 24.27^{+0.08}_{-0.11} & 24.45^{+0.14}_{-0.19} & 24.12^{+0.07}_{-0.12} & -12.76^{+0.15}_{-0.32} & -13.06^{+0.09}_{-0.14} \\
+    4.6 & 24.46^{+0.13}_{-0.28} & 24.22^{+0.08}_{-0.12} & 24.40^{+0.15}_{-0.19} & 24.07^{+0.08}_{-0.12} & -12.81^{+0.15}_{-0.34} & -13.12^{+0.10}_{-0.14} \\
+    4.7 & 24.42^{+0.14}_{-0.30} & 24.16^{+0.09}_{-0.12} & 24.36^{+0.16}_{-0.21} & 24.01^{+0.08}_{-0.13} & -12.86^{+0.16}_{-0.36} & -13.18^{+0.11}_{-0.14} \\
+    4.8 & 24.38^{+0.15}_{-0.31} & 24.11^{+0.09}_{-0.13} & 24.31^{+0.17}_{-0.22} & 23.96^{+0.09}_{-0.14} & -12.91^{+0.17}_{-0.38} & -13.25^{+0.11}_{-0.15} \\
+    4.9 & 24.34^{+0.15}_{-0.33} & 24.05^{+0.10}_{-0.13} & 24.26^{+0.17}_{-0.24} & 23.90^{+0.09}_{-0.15} & -12.96^{+0.18}_{-0.39} & -13.32^{+0.12}_{-0.15} \\
+    5.0 & 24.30^{+0.16}_{-0.35} & 23.99^{+0.11}_{-0.13} & 24.21^{+0.17}_{-0.25} & 23.84^{+0.10}_{-0.17} & -13.01^{+0.19}_{-0.41} & -13.38^{+0.13}_{-0.16} \\
     \hline
@@
 \begin{table*}
-  \contcaption{LyC emissivities and the resultant hydrogen
-    photoionisation rate due to quasars down to magnitudes
-    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
-    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
-    photoionisation rate calculation assumes an HI column density
-    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
-    further details.}
-  \label{tab:gamma}
-  \begin{tabular}{ccccc}
+  \contcaption{}
+  \begin{tabular}{d......}
     \hline
-    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
-    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \multicolumn{1}{c}{$z$} &    
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} & 
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} &
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} \\ 
+    &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} \\
     \hline
-    5.1 & 1.121e--13 & 3.758e--14 & 1.813e+24 & 6.963e+23 \\
-    5.2 & 9.851e--14 & 3.222e--14 & 1.618e+24 & 6.129e+23 \\
-    5.3 & 8.622e--14 & 2.752e--14 & 1.442e+24 & 5.387e+23 \\
-    5.4 & 7.497e--14 & 2.333e--14 & 1.283e+24 & 4.728e+23 \\
-    5.5 & 6.433e--14 & 1.952e--14 & 1.139e+24 & 4.143e+23 \\
-    5.6 & 5.346e--14 & 1.579e--14 & 1.010e+24 & 3.626e+23 \\
-    5.7 & 4.420e--14 & 1.269e--14 & 8.942e+23 & 3.169e+23 \\
-    5.8 & 3.635e--14 & 1.014e--14 & 7.905e+23 & 2.766e+23 \\
-    5.9 & 2.971e--14 & 8.054e--15 & 6.978e+23 & 2.412e+23 \\
-    6.0 & 2.415e--14 & 6.354e--15 & 6.152e+23 & 2.100e+23 \\
-    6.1 & 1.952e--14 & 4.982e--15 & 5.416e+23 & 1.826e+23 \\
-    6.2 & 1.570e--14 & 3.883e--15 & 4.762e+23 & 1.587e+23 \\
-    6.3 & 1.255e--14 & 3.004e--15 & 4.182e+23 & 1.377e+23 \\
-    6.4 & 9.968e--15 & 2.310e--15 & 3.668e+23 & 1.193e+23 \\
-    6.5 & 7.880e--15 & 1.766e--15 & 3.214e+23 & 1.033e+23 \\
-    6.6 & 6.200e--15 & 1.343e--15 & 2.813e+23 & 8.940e+22 \\
-    6.7 & 4.853e--15 & 1.015e--15 & 2.459e+23 & 7.726e+22 \\
-    6.8 & 3.781e--15 & 7.634e--16 & 2.148e+23 & 6.670e+22 \\
-    6.9 & 2.936e--15 & 5.721e--16 & 1.874e+23 & 5.753e+22 \\
-    7.0 & 2.275e--15 & 4.277e--16 & 1.633e+23 & 4.958e+22 \\
-    7.1 & 1.760e--15 & 3.192e--16 & 1.422e+23 & 4.269e+22 \\
-    7.2 & 1.360e--15 & 2.379e--16 & 1.237e+23 & 3.672e+22 \\
-    7.3 & 1.052e--15 & 1.775e--16 & 1.075e+23 & 3.156e+22 \\
-    7.4 & 8.149e--16 & 1.327e--16 & 9.336e+22 & 2.710e+22 \\
-    7.5 & 6.325e--16 & 9.947e--17 & 8.100e+22 & 2.326e+22 \\
-    7.6 & 4.920e--16 & 7.477e--17 & 7.021e+22 & 1.994e+22 \\
-    7.7 & 3.843e--16 & 5.645e--17 & 6.082e+22 & 1.709e+22 \\
-    7.8 & 3.010e--16 & 4.278e--17 & 5.263e+22 & 1.463e+22 \\
-    7.9 & 2.365e--16 & 3.253e--17 & 4.552e+22 & 1.251e+22 \\
-    8.0 & 1.864e--16 & 2.483e--17 & 3.933e+22 & 1.070e+22 \\
-    8.1 & 1.473e--16 & 1.902e--17 & 3.396e+22 & 9.138e+21 \\
-    8.2 & 1.169e--16 & 1.462e--17 & 2.930e+22 & 7.800e+21 \\
-    8.3 & 9.297e--17 & 1.128e--17 & 2.527e+22 & 6.654e+21 \\
-    8.4 & 7.413e--17 & 8.725e--18 & 2.177e+22 & 5.673e+21 \\
-    8.5 & 5.924e--17 & 6.767e--18 & 1.874e+22 & 4.833e+21 \\
-    8.6 & 4.744e--17 & 5.260e--18 & 1.613e+22 & 4.115e+21 \\
-    8.7 & 3.809e--17 & 4.100e--18 & 1.387e+22 & 3.502e+21 \\
-    8.8 & 3.066e--17 & 3.205e--18 & 1.192e+22 & 2.978e+21 \\
-    8.9 & 2.472e--17 & 2.510e--18 & 1.024e+22 & 2.531e+21 \\
-    9.0 & 1.996e--17 & 1.969e--18 & 8.785e+21 & 2.149e+21 \\
-    9.1 & 1.614e--17 & 1.547e--18 & 7.536e+21 & 1.825e+21 \\
-    9.2 & 1.308e--17 & 1.218e--18 & 6.460e+21 & 1.548e+21 \\
-    9.3 & 1.061e--17 & 9.604e--19 & 5.535e+21 & 1.313e+21 \\
-    9.4 & 8.628e--18 & 7.588e--19 & 4.739e+21 & 1.112e+21 \\
-    9.5 & 7.022e--18 & 6.002e--19 & 4.056e+21 & 9.423e+20 \\
-    9.6 & 5.722e--18 & 4.753e--19 & 3.469e+21 & 7.978e+20 \\
-    9.7 & 4.667e--18 & 3.769e--19 & 2.966e+21 & 6.751e+20 \\
-    9.8 & 3.810e--18 & 2.991e--19 & 2.534e+21 & 5.709e+20 \\
-    9.9 & 3.116e--18 & 2.377e--19 & 2.164e+21 & 4.826e+20 \\
-    10.0 & 2.551e--18 & 1.892e--19 & 1.847e+21 & 4.078e+20 \\
+    5.1 & 24.26^{+0.17}_{-0.36} & 23.93^{+0.11}_{-0.14} & 24.16^{+0.18}_{-0.26} & 23.78^{+0.10}_{-0.19} & -13.06^{+0.20}_{-0.42} & -13.45^{+0.13}_{-0.16} \\
+    5.2 & 24.21^{+0.19}_{-0.37} & 23.88^{+0.12}_{-0.14} & 24.10^{+0.19}_{-0.27} & 23.72^{+0.11}_{-0.20} & -13.12^{+0.21}_{-0.44} & -13.52^{+0.14}_{-0.17} \\
+    5.3 & 24.17^{+0.20}_{-0.39} & 23.82^{+0.13}_{-0.15} & 24.05^{+0.19}_{-0.29} & 23.66^{+0.12}_{-0.22} & -13.17^{+0.22}_{-0.46} & -13.59^{+0.15}_{-0.18} \\
+    5.4 & 24.13^{+0.21}_{-0.41} & 23.76^{+0.13}_{-0.16} & 24.00^{+0.20}_{-0.30} & 23.60^{+0.12}_{-0.23} & -13.22^{+0.23}_{-0.47} & -13.67^{+0.16}_{-0.19} \\
+    5.5 & 24.09^{+0.22}_{-0.43} & 23.70^{+0.14}_{-0.17} & 23.94^{+0.21}_{-0.31} & 23.54^{+0.12}_{-0.24} & -13.29^{+0.24}_{-0.49} & -13.75^{+0.17}_{-0.20} \\
+    5.6 & 24.04^{+0.23}_{-0.45} & 23.63^{+0.16}_{-0.17} & 23.89^{+0.22}_{-0.33} & 23.48^{+0.12}_{-0.25} & -13.37^{+0.25}_{-0.51} & -13.85^{+0.18}_{-0.21} \\
+    5.7 & 24.00^{+0.24}_{-0.46} & 23.57^{+0.16}_{-0.18} & 23.84^{+0.23}_{-0.34} & 23.42^{+0.13}_{-0.26} & -13.45^{+0.26}_{-0.53} & -13.94^{+0.18}_{-0.22} \\
+    5.8 & 23.95^{+0.25}_{-0.48} & 23.51^{+0.16}_{-0.20} & 23.78^{+0.24}_{-0.35} & 23.35^{+0.14}_{-0.28} & -13.53^{+0.27}_{-0.55} & -14.04^{+0.19}_{-0.23} \\
+    5.9 & 23.91^{+0.26}_{-0.50} & 23.45^{+0.17}_{-0.20} & 23.73^{+0.24}_{-0.38} & 23.29^{+0.15}_{-0.30} & -13.62^{+0.28}_{-0.57} & -14.15^{+0.20}_{-0.24} \\
+    6.0 & 23.87^{+0.27}_{-0.52} & 23.38^{+0.18}_{-0.20} & 23.67^{+0.25}_{-0.40} & 23.23^{+0.15}_{-0.32} & -13.70^{+0.29}_{-0.58} & -14.26^{+0.21}_{-0.24} \\
+    6.1 & 23.82^{+0.29}_{-0.54} & 23.32^{+0.19}_{-0.21} & 23.61^{+0.27}_{-0.42} & 23.16^{+0.16}_{-0.34} & -13.80^{+0.31}_{-0.60} & -14.37^{+0.22}_{-0.25} \\
+    6.2 & 23.76^{+0.30}_{-0.56} & 23.25^{+0.20}_{-0.22} & 23.55^{+0.28}_{-0.42} & 23.10^{+0.16}_{-0.36} & -13.90^{+0.32}_{-0.62} & -14.48^{+0.23}_{-0.26} \\
+    6.3 & 23.71^{+0.32}_{-0.57} & 23.19^{+0.21}_{-0.23} & 23.49^{+0.29}_{-0.43} & 23.03^{+0.17}_{-0.38} & -14.00^{+0.34}_{-0.64} & -14.59^{+0.24}_{-0.28} \\
+    6.4 & 23.66^{+0.33}_{-0.59} & 23.13^{+0.22}_{-0.24} & 23.42^{+0.30}_{-0.44} & 22.96^{+0.18}_{-0.39} & -14.10^{+0.35}_{-0.66} & -14.71^{+0.25}_{-0.29} \\
+    6.5 & 23.62^{+0.34}_{-0.61} & 23.06^{+0.23}_{-0.25} & 23.36^{+0.31}_{-0.46} & 22.90^{+0.19}_{-0.40} & -14.20^{+0.36}_{-0.68} & -14.83^{+0.26}_{-0.31} \\
+    6.6 & 23.56^{+0.36}_{-0.62} & 23.00^{+0.24}_{-0.26} & 23.30^{+0.33}_{-0.48} & 22.83^{+0.19}_{-0.42} & -14.31^{+0.38}_{-0.69} & -14.96^{+0.27}_{-0.32} \\
+    6.7 & 23.52^{+0.37}_{-0.64} & 22.93^{+0.25}_{-0.28} & 23.23^{+0.34}_{-0.50} & 22.76^{+0.20}_{-0.44} & -14.42^{+0.39}_{-0.72} & -15.08^{+0.28}_{-0.34} \\
+    6.8 & 23.47^{+0.38}_{-0.67} & 22.87^{+0.26}_{-0.29} & 23.15^{+0.36}_{-0.51} & 22.70^{+0.20}_{-0.45} & -14.52^{+0.40}_{-0.74} & -15.22^{+0.29}_{-0.36} \\
+    6.9 & 23.42^{+0.40}_{-0.68} & 22.80^{+0.27}_{-0.30} & 23.08^{+0.39}_{-0.53} & 22.63^{+0.21}_{-0.47} & -14.64^{+0.41}_{-0.77} & -15.35^{+0.30}_{-0.37} \\
+    7.0 & 23.37^{+0.41}_{-0.71} & 22.73^{+0.28}_{-0.31} & 23.01^{+0.41}_{-0.54} & 22.56^{+0.22}_{-0.49} & -14.74^{+0.42}_{-0.79} & -15.48^{+0.32}_{-0.40} \\
+    7.1 & 23.33^{+0.41}_{-0.73} & 22.66^{+0.29}_{-0.33} & 22.94^{+0.42}_{-0.56} & 22.49^{+0.23}_{-0.52} & -14.86^{+0.43}_{-0.82} & -15.62^{+0.33}_{-0.42} \\
+    7.2 & 23.28^{+0.43}_{-0.76} & 22.60^{+0.29}_{-0.35} & 22.87^{+0.44}_{-0.57} & 22.42^{+0.23}_{-0.54} & -14.97^{+0.45}_{-0.85} & -15.75^{+0.34}_{-0.45} \\
+    7.3 & 23.22^{+0.45}_{-0.77} & 22.53^{+0.31}_{-0.36} & 22.80^{+0.47}_{-0.59} & 22.35^{+0.24}_{-0.57} & -15.09^{+0.47}_{-0.87} & -15.88^{+0.36}_{-0.47} \\
+    7.4 & 23.17^{+0.46}_{-0.80} & 22.46^{+0.32}_{-0.38} & 22.73^{+0.49}_{-0.60} & 22.29^{+0.25}_{-0.59} & -15.20^{+0.48}_{-0.90} & -16.02^{+0.37}_{-0.50} \\
+    7.5 & 23.13^{+0.47}_{-0.83} & 22.39^{+0.34}_{-0.39} & 22.67^{+0.51}_{-0.61} & 22.21^{+0.25}_{-0.62} & -15.30^{+0.49}_{-0.93} & -16.15^{+0.39}_{-0.52} \\
+    7.6 & 23.09^{+0.47}_{-0.87} & 22.32^{+0.35}_{-0.41} & 22.60^{+0.52}_{-0.63} & 22.14^{+0.26}_{-0.64} & -15.41^{+0.49}_{-0.97} & -16.29^{+0.41}_{-0.55} \\
+    7.7 & 23.04^{+0.48}_{-0.90} & 22.26^{+0.37}_{-0.42} & 22.53^{+0.54}_{-0.64} & 22.07^{+0.27}_{-0.66} & -15.52^{+0.50}_{-1.00} & -16.42^{+0.43}_{-0.57} \\
+    7.8 & 22.99^{+0.50}_{-0.92} & 22.19^{+0.38}_{-0.44} & 22.46^{+0.57}_{-0.65} & 22.00^{+0.28}_{-0.68} & -15.63^{+0.52}_{-1.02} & -16.55^{+0.45}_{-0.60} \\
+    7.9 & 22.94^{+0.51}_{-0.94} & 22.12^{+0.41}_{-0.46} & 22.38^{+0.58}_{-0.65} & 21.92^{+0.29}_{-0.70} & -15.74^{+0.53}_{-1.05} & -16.68^{+0.47}_{-0.63} \\
+    8.0 & 22.88^{+0.53}_{-0.97} & 22.05^{+0.43}_{-0.48} & 22.31^{+0.60}_{-0.66} & 21.85^{+0.30}_{-0.73} & -15.84^{+0.54}_{-1.07} & -16.80^{+0.50}_{-0.66} \\
+    8.1 & 22.83^{+0.54}_{-0.99} & 21.97^{+0.44}_{-0.49} & 22.24^{+0.61}_{-0.68} & 21.78^{+0.31}_{-0.76} & -15.95^{+0.56}_{-1.10} & -16.93^{+0.52}_{-0.68} \\
+    8.2 & 22.78^{+0.56}_{-1.02} & 21.90^{+0.46}_{-0.51} & 22.17^{+0.63}_{-0.70} & 21.71^{+0.32}_{-0.78} & -16.05^{+0.57}_{-1.12} & -17.06^{+0.54}_{-0.71} \\
+    8.3 & 22.73^{+0.57}_{-1.04} & 21.82^{+0.48}_{-0.52} & 22.10^{+0.65}_{-0.71} & 21.63^{+0.33}_{-0.81} & -16.15^{+0.58}_{-1.15} & -17.20^{+0.56}_{-0.72} \\
+    8.4 & 22.68^{+0.58}_{-1.07} & 21.74^{+0.50}_{-0.53} & 22.02^{+0.68}_{-0.72} & 21.56^{+0.33}_{-0.84} & -16.25^{+0.59}_{-1.18} & -17.33^{+0.58}_{-0.74} \\
+    8.5 & 22.63^{+0.59}_{-1.10} & 21.66^{+0.52}_{-0.54} & 21.94^{+0.71}_{-0.73} & 21.49^{+0.34}_{-0.86} & -16.35^{+0.61}_{-1.21} & -17.45^{+0.60}_{-0.76} \\
+    8.6 & 22.59^{+0.60}_{-1.13} & 21.59^{+0.53}_{-0.55} & 21.86^{+0.75}_{-0.73} & 21.41^{+0.35}_{-0.89} & -16.45^{+0.61}_{-1.24} & -17.57^{+0.61}_{-0.78} \\
+    8.7 & 22.54^{+0.61}_{-1.16} & 21.52^{+0.54}_{-0.57} & 21.78^{+0.78}_{-0.73} & 21.34^{+0.36}_{-0.92} & -16.55^{+0.63}_{-1.26} & -17.69^{+0.63}_{-0.80} \\
+    8.8 & 22.48^{+0.63}_{-1.18} & 21.45^{+0.56}_{-0.58} & 21.69^{+0.81}_{-0.73} & 21.26^{+0.37}_{-0.94} & -16.65^{+0.64}_{-1.28} & -17.82^{+0.64}_{-0.82} \\
+    8.9 & 22.42^{+0.65}_{-1.20} & 21.37^{+0.58}_{-0.59} & 21.61^{+0.84}_{-0.74} & 21.19^{+0.38}_{-0.97} & -16.75^{+0.66}_{-1.31} & -17.94^{+0.67}_{-0.84} \\
+    9.0 & 22.37^{+0.66}_{-1.23} & 21.30^{+0.60}_{-0.61} & 21.53^{+0.87}_{-0.75} & 21.11^{+0.39}_{-0.99} & -16.85^{+0.67}_{-1.33} & -18.06^{+0.69}_{-0.86} \\
+    9.1 & 22.33^{+0.67}_{-1.26} & 21.22^{+0.62}_{-0.62} & 21.45^{+0.90}_{-0.76} & 21.04^{+0.40}_{-1.02} & -16.94^{+0.68}_{-1.36} & -18.18^{+0.72}_{-0.89} \\
+    9.2 & 22.27^{+0.68}_{-1.28} & 21.15^{+0.65}_{-0.64} & 21.36^{+0.93}_{-0.77} & 20.96^{+0.41}_{-1.05} & -17.04^{+0.69}_{-1.38} & -18.30^{+0.74}_{-0.91} \\
+    9.3 & 22.22^{+0.69}_{-1.31} & 21.07^{+0.67}_{-0.66} & 21.29^{+0.95}_{-0.80} & 20.89^{+0.43}_{-1.08} & -17.14^{+0.71}_{-1.41} & -18.41^{+0.77}_{-0.93} \\
+    9.4 & 22.16^{+0.70}_{-1.33} & 21.00^{+0.69}_{-0.67} & 21.21^{+0.97}_{-0.82} & 20.81^{+0.44}_{-1.10} & -17.23^{+0.72}_{-1.43} & -18.53^{+0.79}_{-0.95} \\
+    9.5 & 22.11^{+0.72}_{-1.36} & 20.92^{+0.71}_{-0.68} & 21.13^{+1.00}_{-0.83} & 20.73^{+0.45}_{-1.13} & -17.33^{+0.74}_{-1.45} & -18.65^{+0.81}_{-0.96} \\
+    9.6 & 22.06^{+0.73}_{-1.38} & 20.84^{+0.73}_{-0.70} & 21.05^{+1.03}_{-0.85} & 20.65^{+0.46}_{-1.16} & -17.42^{+0.75}_{-1.47} & -18.77^{+0.83}_{-0.98} \\
+    9.7 & 22.00^{+0.74}_{-1.40} & 20.76^{+0.75}_{-0.72} & 20.97^{+1.06}_{-0.86} & 20.57^{+0.48}_{-1.18} & -17.52^{+0.76}_{-1.49} & -18.89^{+0.85}_{-1.01} \\
+    9.8 & 21.95^{+0.76}_{-1.42} & 20.69^{+0.77}_{-0.73} & 20.88^{+1.10}_{-0.88} & 20.49^{+0.49}_{-1.21} & -17.61^{+0.78}_{-1.51} & -19.01^{+0.87}_{-1.03} \\
+    9.9 & 21.90^{+0.76}_{-1.45} & 20.61^{+0.79}_{-0.75} & 20.80^{+1.13}_{-0.89} & 20.42^{+0.50}_{-1.24} & -17.70^{+0.79}_{-1.54} & -19.12^{+0.89}_{-1.06} \\
+    10.0 & 21.85^{+0.77}_{-1.48} & 20.53^{+0.81}_{-0.77} & 20.72^{+1.16}_{-0.90} & 20.34^{+0.51}_{-1.26} & -17.79^{+0.80}_{-1.57} & -19.23^{+0.91}_{-1.09} \\
     \hline
@@
 \begin{table*}
-  \contcaption{LyC emissivities and the resultant hydrogen
-    photoionisation rate due to quasars down to magnitudes
-    $M_{1450}=-18$ and $M_{1450}=-21$.  These numbers describe the
-    curves shown in Figures~\ref{fig:e912} and \ref{fig:gammapi}.  The
-    photoionisation rate calculation assumes an HI column density
-    given by \citet{2012ApJ...746..125H}.  See Sections XX and XX for
-    further details.}
-  \label{tab:gamma}
-  \begin{tabular}{ccccc}
+  \contcaption{}
+  \begin{tabular}{d......}
     \hline
-    $z$ & $\Gamma_\mathrm{HI} (M_{1450}<-18)$ & $\Gamma_\mathrm{HI} (M_{1450}<-21)$ & $\epsilon_{912} (M_{1450}<-18)$ & $\epsilon_{912} (M_{1450}<-21)$ \\
-    & [s$^{-1}$] & [s$^{-1}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] & [erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$] \\ 
+    \multicolumn{1}{c}{$z$} &    
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{1450}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} &
+    \multicolumn{1}{c}{$\log_{10}\epsilon_{912}$} & 
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} &
+    \multicolumn{1}{c}{$\log_{10}\Gamma_\mathrm{HI}$} \\ 
+    &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-18)$} &
+    \multicolumn{1}{c}{$(M_{1450}<-21)$} \\
     \hline
-    10.1 & 2.091e--18 & 1.507e--19 & 1.576e+21 & 3.444e+20 \\
-    10.2 & 1.715e--18 & 1.201e--19 & 1.344e+21 & 2.907e+20 \\
-    10.3 & 1.407e--18 & 9.584e--20 & 1.145e+21 & 2.453e+20 \\
-    10.4 & 1.156e--18 & 7.650e--20 & 9.756e+20 & 2.069e+20 \\
-    10.5 & 9.500e--19 & 6.112e--20 & 8.307e+20 & 1.744e+20 \\
-    10.6 & 7.820e--19 & 4.890e--20 & 7.071e+20 & 1.470e+20 \\
-    10.7 & 6.441e--19 & 3.915e--20 & 6.015e+20 & 1.238e+20 \\
-    10.8 & 5.309e--19 & 3.136e--20 & 5.115e+20 & 1.042e+20 \\
-    10.9 & 4.377e--19 & 2.513e--20 & 4.348e+20 & 8.771e+19 \\
-    11.0 & 3.611e--19 & 2.015e--20 & 3.694e+20 & 7.378e+19 \\
-    11.1 & 2.980e--19 & 1.616e--20 & 3.137e+20 & 6.204e+19 \\
-    11.2 & 2.462e--19 & 1.297e--20 & 2.664e+20 & 5.215e+19 \\
-    11.3 & 2.036e--19 & 1.042e--20 & 2.260e+20 & 4.382e+19 \\
-    11.4 & 1.685e--19 & 8.378e--21 & 1.917e+20 & 3.681e+19 \\
-    11.5 & 1.394e--19 & 6.737e--21 & 1.626e+20 & 3.091e+19 \\
-    11.6 & 1.154e--19 & 5.419e--21 & 1.378e+20 & 2.594e+19 \\
-    11.7 & 9.559e--20 & 4.360e--21 & 1.168e+20 & 2.176e+19 \\
-    11.8 & 7.919e--20 & 3.509e--21 & 9.889e+19 & 1.825e+19 \\
-    11.9 & 6.564e--20 & 2.826e--21 & 8.372e+19 & 1.530e+19 \\
-    12.0 & 5.447e--20 & 2.278e--21 & 7.086e+19 & 1.283e+19 \\
-    12.1 & 4.521e--20 & 1.836e--21 & 5.995e+19 & 1.075e+19 \\
-    12.2 & 3.754e--20 & 1.481e--21 & 5.070e+19 & 9.002e+18 \\
-    12.3 & 3.117e--20 & 1.195e--21 & 4.287e+19 & 7.537e+18 \\
-    12.4 & 2.589e--20 & 9.637e--22 & 3.623e+19 & 6.309e+18 \\
-    12.5 & 2.151e--20 & 7.776e--22 & 3.061e+19 & 5.279e+18 \\
-    12.6 & 1.788e--20 & 6.275e--22 & 2.586e+19 & 4.416e+18 \\
-    12.7 & 1.487e--20 & 5.068e--22 & 2.183e+19 & 3.693e+18 \\
-    12.8 & 1.237e--20 & 4.095e--22 & 1.843e+19 & 3.087e+18 \\
-    12.9 & 1.029e--20 & 3.309e--22 & 1.555e+19 & 2.580e+18 \\
-    13.0 & 8.567e--21 & 2.674e--22 & 1.312e+19 & 2.156e+18 \\
-    13.1 & 7.131e--21 & 2.162e--22 & 1.106e+19 & 1.801e+18 \\
-    13.2 & 5.935e--21 & 1.747e--22 & 9.325e+18 & 1.503e+18 \\
-    13.3 & 4.940e--21 & 1.412e--22 & 7.859e+18 & 1.255e+18 \\
-    13.4 & 4.112e--21 & 1.141e--22 & 6.621e+18 & 1.047e+18 \\
-    13.5 & 3.424e--21 & 9.229e--23 & 5.577e+18 & 8.739e+17 \\
-    13.6 & 2.851e--21 & 7.465e--23 & 4.696e+18 & 7.289e+17 \\
-    13.7 & 2.374e--21 & 6.036e--23 & 3.953e+18 & 6.078e+17 \\
-    13.8 & 1.975e--21 & 4.879e--23 & 3.327e+18 & 5.067e+17 \\
-    13.9 & 1.643e--21 & 3.942e--23 & 2.799e+18 & 4.223e+17 \\
-    14.0 & 1.365e--21 & 3.182e--23 & 2.354e+18 & 3.518e+17 \\
-    14.1 & 1.133e--21 & 2.566e--23 & 1.980e+18 & 2.931e+17 \\
-    14.2 & 9.381e--22 & 2.066e--23 & 1.664e+18 & 2.441e+17 \\
-    14.3 & 7.750e--22 & 1.659e--23 & 1.399e+18 & 2.032e+17 \\
-    14.4 & 6.384e--22 & 1.330e--23 & 1.175e+18 & 1.691e+17 \\
-    14.5 & 5.229e--22 & 1.060e--23 & 9.873e+17 & 1.408e+17 \\
-    14.6 & 4.245e--22 & 8.375e--24 & 8.292e+17 & 1.171e+17 \\
-    14.7 & 3.395e--22 & 6.526e--24 & 6.962e+17 & 9.741e+16 \\
-    14.8 & 2.641e--22 & 4.951e--24 & 5.844e+17 & 8.100e+16 \\
-    14.9 & 1.935e--22 & 3.542e--24 & 4.904e+17 & 6.735e+16 \\
-    15.0 & 1.182e--22 & 2.116e--24 & 4.115e+17 & 5.598e+16 \\
+    10.0 & 21.85^{+0.77}_{-1.48} & 20.53^{+0.81}_{-0.77} & 20.72^{+1.16}_{-0.90} & 20.34^{+0.51}_{-1.26} & -17.79^{+0.80}_{-1.57} & -19.23^{+0.91}_{-1.09} \\
+    10.1 & 21.80^{+0.80}_{-1.50} & 20.46^{+0.83}_{-0.79} & 20.63^{+1.19}_{-0.91} & 20.26^{+0.52}_{-1.29} & -17.88^{+0.83}_{-1.58} & -19.35^{+0.93}_{-1.11} \\
+    10.2 & 21.74^{+0.83}_{-1.52} & 20.38^{+0.85}_{-0.81} & 20.55^{+1.23}_{-0.93} & 20.18^{+0.53}_{-1.31} & -17.97^{+0.85}_{-1.60} & -19.46^{+0.96}_{-1.13} \\
+    10.3 & 21.69^{+0.85}_{-1.54} & 20.31^{+0.88}_{-0.83} & 20.47^{+1.26}_{-0.94} & 20.10^{+0.54}_{-1.34} & -18.07^{+0.87}_{-1.62} & -19.57^{+0.98}_{-1.16} \\
+    10.4 & 21.63^{+0.87}_{-1.56} & 20.23^{+0.90}_{-0.85} & 20.39^{+1.29}_{-0.95} & 20.03^{+0.55}_{-1.36} & -18.16^{+0.89}_{-1.64} & -19.69^{+1.01}_{-1.18} \\
+    10.5 & 21.58^{+0.89}_{-1.59} & 20.15^{+0.93}_{-0.87} & 20.31^{+1.31}_{-0.96} & 19.95^{+0.56}_{-1.39} & -18.25^{+0.90}_{-1.67} & -19.80^{+1.03}_{-1.21} \\
+    10.6 & 21.52^{+0.90}_{-1.62} & 20.07^{+0.95}_{-0.89} & 20.22^{+1.35}_{-0.97} & 19.87^{+0.58}_{-1.42} & -18.34^{+0.91}_{-1.69} & -19.91^{+1.05}_{-1.23} \\
+    10.7 & 21.47^{+0.90}_{-1.65} & 19.99^{+0.97}_{-0.90} & 20.13^{+1.38}_{-0.98} & 19.79^{+0.59}_{-1.44} & -18.43^{+0.92}_{-1.72} & -20.03^{+1.08}_{-1.25} \\
+    10.8 & 21.42^{+0.91}_{-1.67} & 19.91^{+0.99}_{-0.92} & 20.04^{+1.42}_{-0.99} & 19.71^{+0.60}_{-1.47} & -18.52^{+0.93}_{-1.74} & -20.15^{+1.10}_{-1.27} \\
+    10.9 & 21.36^{+0.93}_{-1.70} & 19.83^{+1.01}_{-0.94} & 19.95^{+1.46}_{-1.00} & 19.63^{+0.61}_{-1.50} & -18.62^{+0.95}_{-1.76} & -20.26^{+1.13}_{-1.29} \\
+    11.0 & 21.30^{+0.94}_{-1.72} & 19.75^{+1.04}_{-0.96} & 19.86^{+1.50}_{-1.01} & 19.55^{+0.62}_{-1.53} & -18.71^{+0.96}_{-1.78} & -20.38^{+1.16}_{-1.32} \\
+    11.1 & 21.24^{+0.96}_{-1.74} & 19.67^{+1.08}_{-0.98} & 19.78^{+1.53}_{-1.03} & 19.47^{+0.63}_{-1.56} & -18.81^{+0.98}_{-1.81} & -20.49^{+1.20}_{-1.34} \\
+    11.2 & 21.18^{+0.97}_{-1.76} & 19.59^{+1.12}_{-1.00} & 19.69^{+1.56}_{-1.04} & 19.39^{+0.64}_{-1.59} & -18.90^{+0.99}_{-1.82} & -20.60^{+1.24}_{-1.36} \\
+    11.3 & 21.12^{+0.99}_{-1.78} & 19.51^{+1.15}_{-1.01} & 19.60^{+1.60}_{-1.05} & 19.31^{+0.66}_{-1.62} & -18.99^{+1.01}_{-1.84} & -20.72^{+1.28}_{-1.39} \\
+    11.4 & 21.06^{+1.00}_{-1.79} & 19.43^{+1.20}_{-1.03} & 19.51^{+1.63}_{-1.06} & 19.23^{+0.67}_{-1.65} & -19.09^{+1.02}_{-1.85} & -20.83^{+1.32}_{-1.40} \\
+    11.5 & 21.00^{+1.02}_{-1.82} & 19.35^{+1.23}_{-1.05} & 19.42^{+1.67}_{-1.07} & 19.15^{+0.68}_{-1.68} & -19.18^{+1.04}_{-1.88} & -20.95^{+1.35}_{-1.42} \\
+    11.6 & 20.94^{+1.03}_{-1.84} & 19.27^{+1.27}_{-1.06} & 19.32^{+1.71}_{-1.08} & 19.07^{+0.69}_{-1.71} & -19.27^{+1.05}_{-1.90} & -21.07^{+1.39}_{-1.44} \\
+    11.7 & 20.88^{+1.05}_{-1.86} & 19.18^{+1.31}_{-1.08} & 19.23^{+1.75}_{-1.09} & 18.99^{+0.70}_{-1.74} & -19.37^{+1.07}_{-1.92} & -21.18^{+1.43}_{-1.45} \\
+    11.8 & 20.82^{+1.06}_{-1.88} & 19.10^{+1.35}_{-1.09} & 19.14^{+1.79}_{-1.10} & 18.91^{+0.71}_{-1.77} & -19.46^{+1.09}_{-1.94} & -21.30^{+1.46}_{-1.47} \\
+    11.9 & 20.76^{+1.08}_{-1.90} & 19.01^{+1.38}_{-1.10} & 19.04^{+1.83}_{-1.11} & 18.83^{+0.72}_{-1.80} & -19.56^{+1.10}_{-1.96} & -21.41^{+1.49}_{-1.48} \\
+    12.0 & 20.70^{+1.10}_{-1.93} & 18.93^{+1.41}_{-1.11} & 18.95^{+1.86}_{-1.13} & 18.75^{+0.73}_{-1.82} & -19.65^{+1.12}_{-1.98} & -21.52^{+1.52}_{-1.50} \\
+    12.1 & 20.64^{+1.12}_{-1.95} & 18.86^{+1.43}_{-1.14} & 18.87^{+1.90}_{-1.14} & 18.67^{+0.74}_{-1.85} & -19.74^{+1.14}_{-2.00} & -21.63^{+1.55}_{-1.52} \\
+    12.2 & 20.58^{+1.14}_{-1.97} & 18.78^{+1.46}_{-1.16} & 18.78^{+1.93}_{-1.16} & 18.59^{+0.76}_{-1.88} & -19.83^{+1.16}_{-2.03} & -21.74^{+1.57}_{-1.54} \\
+    12.3 & 20.52^{+1.16}_{-1.99} & 18.70^{+1.50}_{-1.18} & 18.69^{+1.96}_{-1.18} & 18.51^{+0.77}_{-1.91} & -19.92^{+1.18}_{-2.05} & -21.85^{+1.61}_{-1.56} \\
+    12.4 & 20.46^{+1.16}_{-2.02} & 18.62^{+1.53}_{-1.20} & 18.60^{+1.99}_{-1.20} & 18.42^{+0.78}_{-1.93} & -20.01^{+1.19}_{-2.08} & -21.96^{+1.64}_{-1.58} \\
+    12.5 & 20.41^{+1.17}_{-2.05} & 18.54^{+1.56}_{-1.22} & 18.52^{+2.02}_{-1.22} & 18.34^{+0.80}_{-1.96} & -20.10^{+1.20}_{-2.10} & -22.07^{+1.67}_{-1.60} \\
+    12.6 & 20.35^{+1.19}_{-2.07} & 18.46^{+1.59}_{-1.24} & 18.43^{+2.05}_{-1.24} & 18.25^{+0.81}_{-1.98} & -20.19^{+1.22}_{-2.12} & -22.18^{+1.70}_{-1.63} \\
+    12.7 & 20.29^{+1.21}_{-2.09} & 18.38^{+1.62}_{-1.26} & 18.35^{+2.07}_{-1.27} & 18.17^{+0.82}_{-2.01} & -20.28^{+1.24}_{-2.14} & -22.29^{+1.72}_{-1.65} \\
+    12.8 & 20.23^{+1.23}_{-2.12} & 18.29^{+1.65}_{-1.28} & 18.27^{+2.10}_{-1.29} & 18.09^{+0.83}_{-2.04} & -20.37^{+1.26}_{-2.16} & -22.41^{+1.76}_{-1.66} \\
+    12.9 & 20.17^{+1.25}_{-2.14} & 18.21^{+1.68}_{-1.29} & 18.19^{+2.12}_{-1.32} & 18.01^{+0.84}_{-2.07} & -20.46^{+1.28}_{-2.19} & -22.52^{+1.79}_{-1.68} \\
+    13.0 & 20.11^{+1.28}_{-2.16} & 18.12^{+1.71}_{-1.31} & 18.11^{+2.15}_{-1.35} & 17.92^{+0.85}_{-2.09} & -20.55^{+1.30}_{-2.21} & -22.64^{+1.82}_{-1.69} \\
+    13.1 & 20.05^{+1.30}_{-2.18} & 18.04^{+1.75}_{-1.32} & 18.02^{+2.18}_{-1.37} & 17.84^{+0.86}_{-2.12} & -20.64^{+1.31}_{-2.23} & -22.75^{+1.86}_{-1.71} \\
+    13.2 & 19.99^{+1.31}_{-2.21} & 17.95^{+1.79}_{-1.34} & 17.93^{+2.21}_{-1.39} & 17.76^{+0.88}_{-2.15} & -20.73^{+1.33}_{-2.26} & -22.86^{+1.89}_{-1.72} \\
+    13.3 & 19.93^{+1.32}_{-2.24} & 17.87^{+1.83}_{-1.36} & 17.84^{+2.24}_{-1.41} & 17.67^{+0.89}_{-2.17} & -20.81^{+1.34}_{-2.29} & -22.98^{+1.93}_{-1.74} \\
+    13.4 & 19.88^{+1.33}_{-2.27} & 17.79^{+1.86}_{-1.37} & 17.76^{+2.27}_{-1.43} & 17.59^{+0.91}_{-2.20} & -20.90^{+1.34}_{-2.32} & -23.09^{+1.96}_{-1.75} \\
+    13.5 & 19.83^{+1.34}_{-2.30} & 17.70^{+1.90}_{-1.39} & 17.66^{+2.30}_{-1.45} & 17.51^{+0.92}_{-2.23} & -20.98^{+1.35}_{-2.35} & -23.21^{+2.00}_{-1.77} \\
+    13.6 & 19.78^{+1.34}_{-2.33} & 17.62^{+1.93}_{-1.41} & 17.57^{+2.33}_{-1.46} & 17.42^{+0.93}_{-2.26} & -21.06^{+1.36}_{-2.38} & -23.32^{+2.03}_{-1.78} \\
+    13.7 & 19.72^{+1.35}_{-2.36} & 17.53^{+1.97}_{-1.42} & 17.48^{+2.36}_{-1.48} & 17.34^{+0.95}_{-2.29} & -21.15^{+1.37}_{-2.40} & -23.43^{+2.06}_{-1.79} \\
+    13.8 & 19.67^{+1.37}_{-2.38} & 17.45^{+2.00}_{-1.44} & 17.39^{+2.39}_{-1.50} & 17.25^{+0.96}_{-2.32} & -21.24^{+1.38}_{-2.43} & -23.54^{+2.09}_{-1.81} \\
+    13.9 & 19.61^{+1.38}_{-2.41} & 17.37^{+2.03}_{-1.46} & 17.30^{+2.42}_{-1.52} & 17.17^{+0.97}_{-2.35} & -21.32^{+1.39}_{-2.46} & -23.65^{+2.12}_{-1.83} \\
+    14.0 & 19.55^{+1.39}_{-2.44} & 17.29^{+2.06}_{-1.48} & 17.21^{+2.45}_{-1.54} & 17.09^{+0.99}_{-2.38} & -21.41^{+1.40}_{-2.48} & -23.76^{+2.15}_{-1.84} \\
+    14.1 & 19.50^{+1.40}_{-2.46} & 17.20^{+2.10}_{-1.50} & 17.12^{+2.48}_{-1.55} & 17.00^{+1.00}_{-2.41} & -21.49^{+1.41}_{-2.51} & -23.87^{+2.18}_{-1.86} \\
+    14.2 & 19.44^{+1.41}_{-2.50} & 17.12^{+2.13}_{-1.52} & 17.03^{+2.51}_{-1.56} & 16.92^{+1.01}_{-2.44} & -21.58^{+1.42}_{-2.54} & -23.98^{+2.21}_{-1.87} \\
+    14.3 & 19.39^{+1.42}_{-2.53} & 17.04^{+2.16}_{-1.54} & 16.94^{+2.54}_{-1.57} & 16.83^{+1.02}_{-2.47} & -21.66^{+1.43}_{-2.57} & -24.09^{+2.24}_{-1.89} \\
+    14.4 & 19.34^{+1.43}_{-2.56} & 16.96^{+2.19}_{-1.56} & 16.85^{+2.57}_{-1.58} & 16.75^{+1.04}_{-2.50} & -21.75^{+1.44}_{-2.60} & -24.20^{+2.26}_{-1.91} \\
+    14.5 & 19.29^{+1.44}_{-2.60} & 16.88^{+2.22}_{-1.58} & 16.76^{+2.60}_{-1.59} & 16.66^{+1.05}_{-2.53} & -21.84^{+1.45}_{-2.63} & -24.32^{+2.29}_{-1.93} \\
+    14.6 & 19.24^{+1.46}_{-2.63} & 16.80^{+2.25}_{-1.60} & 16.67^{+2.63}_{-1.60} & 16.58^{+1.06}_{-2.56} & -21.93^{+1.47}_{-2.66} & -24.43^{+2.32}_{-1.94} \\
+    14.7 & 19.18^{+1.47}_{-2.65} & 16.72^{+2.28}_{-1.62} & 16.57^{+2.66}_{-1.61} & 16.50^{+1.07}_{-2.59} & -22.03^{+1.48}_{-2.68} & -24.56^{+2.34}_{-1.96} \\
+    14.8 & 19.13^{+1.48}_{-2.69} & 16.64^{+2.31}_{-1.64} & 16.48^{+2.69}_{-1.63} & 16.41^{+1.09}_{-2.61} & -22.15^{+1.48}_{-2.71} & -24.69^{+2.37}_{-1.97} \\
+    14.9 & 19.08^{+1.48}_{-2.72} & 16.56^{+2.34}_{-1.66} & 16.39^{+2.72}_{-1.64} & 16.33^{+1.10}_{-2.64} & -22.28^{+1.48}_{-2.74} & -24.85^{+2.39}_{-1.99} \\
+    15.0 & 19.02^{+1.49}_{-2.75} & 16.48^{+2.37}_{-1.68} & 16.30^{+2.75}_{-1.66} & 16.24^{+1.11}_{-2.67} & -22.50^{+1.49}_{-2.76} & -25.08^{+2.41}_{-2.00} \\
     \hline
@@
 catalogues and selection functions and the code used for developing
-and analysing luminosity function models.  \gk{Make URL public. Set
-  appropriate license.  Take permission from other authors.  Set up a
-  DOI.}
+and analysing luminosity function models.
+%% Make URL public. Set appropriate license.  Take permission from
+%% other authors.  Set up a DOI.
 
@@
 \end{document}
-
-%% Tables:
-%% Individual fit results
-%% Global models best fit parameters
-%% Emissivity (H and He)
-%% Photoionization rates (H and He)
-%%

### 2018-03-30 Paper/paper.tex
Update text

@@
   Institute of Cosmology, University of Cambridge, Madingley Road,
-  Cambridge CB3 0HA, UK \\ $^2$Max Planck Institute for Astronomy,
-  K\"onigstuhl 17, D-69117 Heidelberg, Germany\\ $^3$Department of
-  Physics, Broida Hall, UC Santa Barbara, Santa Barbara, CA 93106-9530
-  USA}
+  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
+  Universit\"at Potsdam, Karl-Liebknecht-Str.\ 24/25, 14476 Potsdam,
+  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
+  Santa Barbara, CA 93106-9530 USA}
 % Update Gabor's address to Potsdam
@@
 
+%% Q notation is different on figure and in text.
+%% MH15 curve seems wrong; it should reionize at z ~ 4 or so.
 \begin{figure}
@@
   \caption{Evolution of the \HeIII\ ionization fraction in our model,
-    when the qso luminosity function is integrated down to
-    $M_{1450}=-21$ (black curve) and when it is extrapolated and
-    integrated down to $M_{1450}=-18$ (brown curve).  Other curves
-    show models of \citet[solid grey]{2012ApJ...746..125H},
+    when the AGN luminosity function is integrated down to
+    $M_{1450}=-21$ (blue curve) and $M_{1450}=-18$ (red curve).  The
+    shaded regions show the one-sigma (68.26\%) uncertainty.  Other
+    curves show models of \citet[solid grey]{2012ApJ...746..125H},
     \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
       shaded region]{2016ApJ...828...90L},
-    \citet[blue]{2018arXiv180104931P}. \gk{Do we need to add any more
-      models from literature?}}
+    \citet[blue]{2018arXiv180104931P},
+    \citet[brown]{2009ApJ...694..842M}, and
+    \citet[green]{2014MNRAS.445.4186C}.  Note that we derive
+    $Q_\nHeIII$ using Equation~(\ref{eqn:qHedot}), which ignores the
+    presence of \HeII\ Lyman-limit systems and becomes inaccurate
+    towards the end of \HeII\ reionization. \label{fig:qhe}}
 \end{figure}
 
-We now consider the implications for hydrogen and helium reionization
-for the ionizing photon emissivity derived above.  This requires that
-we extrapolate the emissivity of Equation XX to higher redshifts.
-Unfortunately, the volume emissivity in our model cannot be
-extrapolated to higher redshifts.  The model of Hopkins suffered with
-the same problem.  \gk{Do we need to show two cases here?  One in
-  which we extrapolate the emissivity and another in which we stop
-  where data end.  There is perhaps a third possibility in which use
-  the current emissivity model upto where data end.}  The evolution of
-the volume averaged ionized fraction of hydrogen is given by \gk{Is
-  this really volume-weighted?}  \citep{2012ApJ...746..125H}
-\begin{equation}
-{dQ_\nHII\over dt}={\dot n_{\rm ion}\over \langle n_\nH \rangle} -{Q_\nHII\over
-\langle t_{\rm rec}\rangle},
-\label{eq:qdot}
-\end{equation}
-and the corresponding equation doubly ionized Helium is
+We now consider the implications of our AGN luminosity function models
+for \HeII\ reionization.  We use the emissivity model developed in
+Section~\ref{sec:e912} for this purpose.  The evolution of the volume-
+averaged fraction $Q_\nHeIII$ of \HeIII\ is given by
+\citep{2012ApJ...746..125H}
 \begin{equation}
 {dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
-\langle t_{\rm rec,He}\rangle}.
-\label{eq:qHedot}
-\end{equation}
-We assume that the Helium is singly reionized together with hydrogen.
-In order to get the 4~Ry emissivity of quasars we use the SED from
-equation XX.  The recombination times are given by
-\begin{equation}
-\langle t_{\rm rec}\rangle=[\chi \langle n\rangle \alpha_B\,C]^{-1},
+\langle t_{\rm rec,He}\rangle},
+\label{eqn:qHedot}
+\end{equation}
+where $\dot n_{\rm ion,4}$ is the number density of photons with
+energy 4~Ry and above produced per unit time, $n_\nHe$ is the Helium
+number density, and $\langle t_{\rm rec,He}\rangle$ is an average
+recombination time scale for \HeIII.  We obtain the evolution of $\dot
+n_{\rm ion,4}$ for AGN with $M_\mathrm{1450}<-21$ and
+$M_\mathrm{1450}<-18$ by integrating the contribution of double power
+law luminosity function obtained in distinct redshifts bins and
+fitting \ref{eqn:e912fit} to the resultant \HeII-ionizing
+emissivities.  We extrapolate the resultant fit to $z>7$, although the
+contribution from this to \HeII-reionization is small.  The SEDs from
+Equation~(\ref{eqn:sed}) and (\ref{eqn:sed_faint}) are assumed for
+bright and faint AGN, respectively.  The recombination time scale in
+Equation~(\ref{eqn:qHedot}) is given by
+\begin{equation}
+\langle t_{\rm rec}\rangle=[(1+2\chi) \langle n_\nH\rangle \alpha_B\,C]^{-1},
 \label{eq:trec}
 \end{equation}
-where $n$ is the volume averaged density of hydrogen and helium,
-respectively.  We assume that hydrogen and helium have similar
-clumping factors, given by \citep{2015ApJ...813L...8M}
+where $n_\nH$ is the volume-averaged density of hydrogen, $\alpha_B$
+is the case-B \HeIII\ recombination rate, and $\chi=0.083$ is the
+cosmic number fraction of Helium.  We assume that the helium clumping
+factor $C$ is given by \citep{2015ApJ...813L...8M}
 \begin{equation}
@@
 \end{equation}
-For the helium recombination coeffienct, we use the fitting function
-provided by \citet{1997MNRAS.292...27H}.  For hydrogen recombination
-coefficient, we use the fitting function provided by
-\citet{2011piim.book.....D}.
-
-The resultant reionization histories of hydrogen and helium are shown
-in Figure XX.  We also show the reionization histories from
-\citep{2012ApJ...746..125H} and \citep{2015ApJ...813L...8M} for
-comparison.  As expected from the emissivity result of the previous
-section, quasars cannot single handedly reionize hydrogen.  However
-they can reionise \HeII.  The Helium reionization completes at
-redshift $z=3.5$--$3.7$ depending on the luminosity down to which you
-integrate the quasar luminosity function.  This is consistent with the
-Helium \lya opacity measurements of \citet{2016ApJ...825..144W}.
-Discuss Mitra et al. 2018 and Khaire and Srianand 2018.  See Gabor's
-email of 14 March 13:18.
+We use the fitting function provided by \citet{1997MNRAS.292...27H}
+for the recombination coefficient.  Note that
+Equation~\ref{eqn:qHedot} neglects the \HeII\ Lyman-limit systems that
+play an increasingly important role towards the end of Helium
+reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.  In the
+absence of these self-shielded systems of high-density \HeII,
+$Q_\nHeIII$ can continue to increase beyond unity.  We set it to one
+when this happens.  This can be corrected by accounting for the
+\HeII\ column density distribution and filtering the \HeII-ionizing
+radiation background through it.  Unfortunately, the \HeII\ column
+density distribution is itself uncertain.  We therefore consider our
+treatment of $Q_\nHeIII$ accurate enough for the purpose of this
+work.
+
+The resultant reionization histories of \HeII\ are shown in
+Figure~\ref{fig:qhe} for $M_\mathrm{1450}<-21$ and
+$M_\mathrm{1450}<-18$ in red and blue, respectively.  We find that
+Helium reionization is complete at $z\sim 3.2$ and $3.1$ in these
+models, respectively, with a one-sigma uncertainty of about $\Delta
+z\sim 0.2$.  This is likely consistent with the \HeII\ \lya effective
+optical depth measurements of \citet{2016ApJ...825..144W}, who find
+that the effective optical depth rises at $z>2.7$, but the incidence
+of low optical depth sightlines beyond this redshift implies that the
+substantial volume of \HeII\ was ionized already at $z=3.4$.
+\HeII\ reionization begins at $z\gtrsim 5$ in our models.  This could
+explain the transmissive sightlines reported by
+\citet{2016ApJ...825..144W}, although a comparison with their data
+requires a more detailed modelling of the IGM.
+
+In Figure~\ref{fig:qhe}, we also show the reionization histories from
+other models of \HeII\ reionization in the literature.  Helium
+reionization is delayed in the model of \citet{2012ApJ...746..125H}
+due to their reduced emissivity at $z\sim 3$.  In the
+\citet{2015ApJ...813L...8M} model, a significant \HeII\ fraction is
+ionized already at $z=6$ due to the very high emissivity assumed in
+this model.  In the radiation-hydrodynamic simulations by
+\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
+SDSS and COSMOS data at $z>3.5$ \citep{2012ApJ...755..169M,
+  2013ApJ...768..105M}, combined with a model for quasar light curves.
+The fiducial \HeII\ reionization history obtained by these authors is
+shown in Figure~\ref{fig:qhe} along with an estimate of the
+uncertainty.  Reionization ends considerably later in this model
+($z\sim 2.6$).  Our model curves are closest in agreement to the
+simulations of \citet{2009ApJ...694..842M} and the analytical model of
+\citet{2018arXiv180104931P}.  Still, reionization completes earlier in
+our model, partly due to the absence of \HeII\ Lyman-limit systems.
+Our redshift of reionization agrees more closely with that in the
+simulations presented by \citet{2014MNRAS.445.4186C}.
+
+Helium reionization has also been studied by
+\citet{2018MNRAS.473.1416M}, who constrained the evolution of the
+emissivity from AGN using the effect optical depth measurement of
+\citet{2016ApJ...825..144W}, combined with an analytical model of the
+IGM.  While a detailed comparison with their work is difficult because
+of reasons, \citet{2018MNRAS.473.1416M} find that the AGN emissivity
+has to drop considerably rapidly at $z>4$. \citet{2018arXiv180109693K}
+have recently presented a model of Helium reionization.  Reionization
+ends at redshift 2.8 in their model.  The AGN luminosity function used
+is by a combination of deteminations from various data sets
+\citep{2015MNRAS.451L..30K}.  The integration limits are inconsistent
+however as they are $0.01L_*$.  Resulting emissivity is comparable to
+our model at $z\sim 2$ but drops more rapidly towards higher
+redshifts.  For a steep EUV spectral index of $\alpha=-1.8$ their
+helium reionization redshift is $z=2.8$.  \citet{2016arXiv160706467D}
+considered the effect of AGN-dominated reionization on the Ly$\alpha$
+opacity at $z>5$, He~\textsc{ii} Ly$\alpha$ opacity at $z\sim
+3.1$--$3.3$, and the thermal history of the IGM.  In agreement with
+\citet{2015MNRAS.453.2943C}, these authors found that AGN did provide
+a plausible explanation for the large fluctuations in the Ly$\alpha$
+opacity at $z>5$.  However, they found that reionization of
+He~\textsc{ii} occurs much earlier in these AGN-dominated models (see
+also \citealt{2018MNRAS.473.1416M}).
 
@@
 acknowledges support from ERC Advanced Grant 320596 `The Emergence of
-Structure During the Epoch of Reionization'. \gk{Joe, do you need to
-  add anything to acknowledgements?}
+Structure During the Epoch of Reionization'.
+%% Joe, do you need to add anything to acknowledgements?
 
@@
 
-\section{Comparison with Giallongo sample}
+\section{Comparison with G15}
 \label{sec:conv}
-
-In our analysis above, we did not include the 22 low-luminosity
-($M_{1450}>-22.6$) AGN between redshifts $z=4.1$ and $6.3$ reported by
-\citet{2015AA...578A..83G} using a novel X-ray/NIR selection
-criterion.  This was because we wanted to restrict our sample to
-quasars that have robust spectroscopic redshift determinations.  In
-their work, \citet{2015AA...578A..83G} found a steep faint-end of the
-luminosity function at these redshifts.  With this luminosity function
-they obtained a large value of hydrogen ionizing emissivity that could
-explain the \lya data singlehandedly.  In this section, we compare our
-results with \citet{2015AA...578A..83G}.  The black points in Figure
-XX show the parameters of the double power law luminosity function
-when the \citet{2015AA...578A..83G} sample is added to our analysis.
-The parameter values do not change significantly.  The
-\citet{2015AA...578A..83G} sample is thus consistent with the double
-power law luminosity function preferred by other data at comparable
-redshifts.  However, as we see in Figure XX, the total emissivity in
-our model is still significantly lower than that obtained by
-\citet{2015AA...578A..83G}.  Figure XX provides an explanation for
-this. The double power law fits favoured by \citet{2015AA...578A..83G}
-are quite different from our fits.  The character luminosity $M_*$
-favoured by \citet{2015AA...578A..83G} is much fainter ($\sim -23$ at
-$z = 5$) than that resulting out of our analysis ($\sim -29$ at $z =
-5$).  Figure XX suggests that this is because of the SDSS Stripe 82
-data \gk{citation} and because \citet{2015AA...578A..83G} ignore the
-Kashikawa and Willott samples \gk{citation}.  It is possible that our
-corrections to the Glikman data \gk{citation} also plays a role in
-this.  In sum, the differnce in our emissivities is not due to lack of
-faint quasars but because of the difference with Giallongo at
-intermediate luminosities.  However, our double power law fits are
-virtually identical to those shown in Figure~\ref{fig:mosaic}.
+%% Define 'G15' somewhere above.
+In the double power law luminosity function models presented in
+distinct redshift bins in Section~\ref{sec:bins}, we did not include
+the 19 low-luminosity ($M_{1450}>-22.6$) AGN between redshifts $z=4.1$
+and $6.3$ reported by G15.  While this was done in order to restrict
+our sample to quasars with spectroscopic redshift determinations, it
+is instructive to consider how our results are affected if the G15 AGN
+are added to the analysis.  In their work, G15 found a shallower
+faint-end slope ($\beta\sim -1.5$ to $-1.8$) for the luminosity
+function at $4.1 < z < 6.3$, relative to our result from other AGN
+samples at these redshifts ($\beta\sim -2.0$ to $-2.5$).  Still, G15
+derived a higher 912\,\AA\ emissivity than our estimates
+(cf.\ Figure~\ref{fig:e912}), so that in their analysis AGN can
+produce all ionizing photons necessary to keep hydrogen ionized and
+explain the \lya data.  The black points in
+Figure~\ref{fig:params_giallongo} show the parameters of the double
+power law luminosity function from our analysis of
+Section~\ref{sec:bins}.  The red open circles show the parameter
+values obtained when the G15 sample is added to the analysis.  We find
+that the two results are highly consistent, showing that the G15
+sample is consistent with our double power law fit obtained from other
+AGN samples are comparable redshifts.  This is surprising as the
+integrated 912\,\AA\ emissivities in our model are smaller than those
+derived by G15.  Figure~\ref{fig:lf_giallongo} provides an
+explanation.  As seen in this figure, the double power law fits
+favoured by G15 (red dashed curves) are quite different from our fits
+(black curves).  The characteristic luminosity $M_*$ obtained by G15
+is much fainter ($\sim -23$ at $z = 5$) than that resulting out of our
+analysis ($\sim -29$ at $z = 5$).  Thus the 912\,\AA\ emissivities are
+enhanced in G15 because of the increase contribution from
+intermediate-luminosity AGN in their model.
+Figure~\ref{fig:lf_giallongo} suggests that this is possibly because
+of the inclusion of SDSS Stripe 82 data from
+\citet{2013ApJ...768..105M} and the AGN samples of
+\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in our
+analysis.  Additionally, the homogenisation of data in our work may
+also cause part of the difference.
 
@@
   \end{center}
-  \caption{Effect of the 19 qsos reported by
-    \citet{2015AA...578A..83G} on the best-fit double power law
-    luminosity function parameters in redshift bins from $z=0$ to $7$.
-    Black points show parameter values from Figure~\ref{fig:evoln}.
-    Red open circles show the parameter values obtained when the
-    sample of \citet{2015AA...578A..83G} is added to the analysis.  In
-    both cases, vertical error bars show one-sigma (68.26\%)
-    uncertainties, whereas horizontal error bars show widths of the
-    redshift bins.}
+  \caption{Effect of the 19 AGN reported by \citet{2015AA...578A..83G}
+    on the best-fit double power law luminosity function parameters in
+    redshift bins from $z=0$ to $7$.  Black points show parameter
+    values from Figure~\ref{fig:evoln}.  Red open circles show the
+    parameter values obtained when the sample of G15 is added to the
+    analysis.  In both cases, vertical error bars show one-sigma
+    (68.26\%) uncertainties, and horizontal error bars show widths of
+    the redshift bins. \label{fig:params_giallongo}}
 \end{figure*}
@@
     with the corresponding one-sigma (68.26\%) uncertainty shown by
-    the grey shaded area.  There are 451, 270, and 69 qsos in each
+    the grey shaded area.  There are 451, 270, and 69 AGN in each
     redshift bin from left to right, respectively.  These numbers are
     higher than those in Figure~\ref{fig:mosaic} because they include,
-    respectively, 9, 7, and 3 qsos from \citet{2015AA...578A..83G}.
-    The magnitude bins containing these qsos are shown in purple.  The
-    red dashed curves show the double power law fits reported by
-    \citet{2015AA...578A..83G} at $z=4.25, 4.75,$ and
-    $5.75$.}
+    respectively, 9, 7, and 3 AGN from G15.  The magnitude bins
+    containing these AGN are shown in purple.  The red dashed curves
+    show the double power law fits reported by G15 at $z=4.25, 4.75,$
+    and $5.75$. \label{fig:lf_giallongo}}
 \end{figure*}

### 2018-04-04 Paper/paper.tex
Update text

@@
 for \HeII\ reionization.  We use the emissivity model developed in
-Section~\ref{sec:e912} for this purpose.  The evolution of the volume-
-averaged fraction $Q_\nHeIII$ of \HeIII\ is given by
+Section~\ref{sec:e912} for this purpose.  The evolution of the
+volume-averaged fraction $Q_\nHeIII$ of \HeIII\ is given by
 \citep{2012ApJ...746..125H}
@@
 law luminosity function obtained in distinct redshifts bins and
-fitting \ref{eqn:e912fit} to the resultant \HeII-ionizing
+fitting Equation~(\ref{eqn:e912fit}) to the resultant \HeII-ionizing
 emissivities.  We extrapolate the resultant fit to $z>7$, although the
-contribution from this to \HeII-reionization is small.  The SEDs from
-Equation~(\ref{eqn:sed}) and (\ref{eqn:sed_faint}) are assumed for
-bright and faint AGN, respectively.  The recombination time scale in
+contribution from this extrapolated emissivity to \HeII-reionization
+is small.  As before, we assume the SEDs given by
+Equations~(\ref{eqn:sed}) and (\ref{eqn:sed_faint}) for bright and
+faint AGN, respectively.  The recombination time scale in
 Equation~(\ref{eqn:qHedot}) is given by
@@
 \end{equation}
-where $n_\nH$ is the volume-averaged density of hydrogen, $\alpha_B$
-is the case-B \HeIII\ recombination rate, and $\chi=0.083$ is the
-cosmic number fraction of Helium.  We assume that the helium clumping
-factor $C$ is given by \citep{2015ApJ...813L...8M}
-\begin{equation}
-  C = 2.8\left(\frac{1+z}{6}\right)^{-1.1}.
+where $n_\nH$ is the average physical number density of hydrogen,
+$\alpha_B$ is the case-B \HeIII\ recombination rate, and $\chi=0.083$
+is the cosmic number fraction of Helium.  We assume that the helium
+clumping factor $C$ is given by \citep{2015ApJ...813L...8M}
+\begin{equation}
+  C = 2.9\left(\frac{1+z}{6}\right)^{-1.1}.
 \end{equation}
 We use the fitting function provided by \citet{1997MNRAS.292...27H}
-for the recombination coefficient.  Note that
-Equation~\ref{eqn:qHedot} neglects the \HeII\ Lyman-limit systems that
-play an increasingly important role towards the end of Helium
-reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.  In the
-absence of these self-shielded systems of high-density \HeII,
+for the recombination coefficient.
+
+Note that Equation~(\ref{eqn:qHedot}) neglects the \HeII\ Lyman-limit
+systems that play an increasingly important role towards the end of
+Helium reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.
+In the absence of these self-shielded systems of high-density \HeII,
 $Q_\nHeIII$ can continue to increase beyond unity.  We set it to one
@@
 density distribution is itself uncertain.  We therefore consider our
-treatment of $Q_\nHeIII$ accurate enough for the purpose of this
-work.
+treatment of $Q_\nHeIII$ accurate enough for the purpose of this work.
 
 The resultant reionization histories of \HeII\ are shown in
-Figure~\ref{fig:qhe} for $M_\mathrm{1450}<-21$ and
-$M_\mathrm{1450}<-18$ in red and blue, respectively.  We find that
-Helium reionization is complete at $z\sim 3.2$ and $3.1$ in these
-models, respectively, with a one-sigma uncertainty of about $\Delta
-z\sim 0.2$.  This is likely consistent with the \HeII\ \lya effective
+Figure~\ref{fig:qhe} for $M_\mathrm{1450}<-18$ and
+$M_\mathrm{1450}<-21$ in red and blue, respectively.  We find that
+Helium reionization is complete, respectively, at $z\sim 3.2$ and
+$3.1$ in these models, with a one-sigma uncertainty of about $\Delta
+z\sim 0.2$.  Observational constraints on the \HeII\ reionization
+history are derived from measurements of the effective \HeII\ \lya
+optical depth \citep{2001Sci...293.1112K, 2004ApJ...600..570S,
+  2006A&A...455...91F, 2010ApJ...722.1312S, 2011ApJ...733L..24W,
+  2016ApJ...825..144W}.  While we do not compute the effective
+\HeII\ \lya optical depth in our model, the reionization histories
+shown in Figure~\ref{fig:qhe} may likely be consistent with the
 optical depth measurements of \citet{2016ApJ...825..144W}, who find
-that the effective optical depth rises at $z>2.7$, but the incidence
-of low optical depth sightlines beyond this redshift implies that the
-substantial volume of \HeII\ was ionized already at $z=3.4$.
-\HeII\ reionization begins at $z\gtrsim 5$ in our models.  This could
-explain the transmissive sightlines reported by
-\citet{2016ApJ...825..144W}, although a comparison with their data
-requires a more detailed modelling of the IGM.
+that the effective optical depth rises at $z>2.7$, but low optical
+depth sightlines continue to be seen beyond this redshift.  The
+incidence of these low opacity sightlines implies that the substantial
+volume of \HeII\ was ionized already at $z=3.4$.  \HeII\ reionization
+begins at $z\gtrsim 5$ in our models.  When we consider AGN with
+$M_\mathrm{1450}<-18$, the ionization fraction $Q_\nHeIII$ has a
+one-sigma spread of 0.8--1 at $z=3.4$.
 
 In Figure~\ref{fig:qhe}, we also show the reionization histories from
-other models of \HeII\ reionization in the literature.  Helium
-reionization is delayed in the model of \citet{2012ApJ...746..125H}
-due to their reduced emissivity at $z\sim 3$.  In the
-\citet{2015ApJ...813L...8M} model, a significant \HeII\ fraction is
-ionized already at $z=6$ due to the very high emissivity assumed in
-this model.  In the radiation-hydrodynamic simulations by
-\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
-SDSS and COSMOS data at $z>3.5$ \citep{2012ApJ...755..169M,
-  2013ApJ...768..105M}, combined with a model for quasar light curves.
-The fiducial \HeII\ reionization history obtained by these authors is
-shown in Figure~\ref{fig:qhe} along with an estimate of the
-uncertainty.  Reionization ends considerably later in this model
-($z\sim 2.6$).  Our model curves are closest in agreement to the
-simulations of \citet{2009ApJ...694..842M} and the analytical model of
-\citet{2018arXiv180104931P}.  Still, reionization completes earlier in
-our model, partly due to the absence of \HeII\ Lyman-limit systems.
-Our redshift of reionization agrees more closely with that in the
-simulations presented by \citet{2014MNRAS.445.4186C}.
+other models of \HeII\ reionization in the literature.  Our model
+curves are closest in agreement to the simulations of
+\citet{2009ApJ...694..842M} and the analytical model of
+\citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
+\HeII-ionizing emissivity of AGN by fitting the function form in
+Equation~(\ref{eqn:e912fit}) to the emissivities reported by
+\citet{2009A&A...507..781S}, \citet{2007A&A...472..443B}, and
+\citet{2012ApJ...755..169M}.  The resultant emissivity in the model of
+\citet{2018arXiv180104931P} is similar in shape but higher in
+amplitude than the emissivity in the \citet{2012ApJ...746..125H}
+model.  The \HeII-ionizing emissivity of \citet{2018arXiv180104931P}
+is closer to our inference for $M_\mathrm{1450}<-21$ than the model of
+\citet{2012ApJ...746..125H}.  (However, note that both these models
+suffer from inhomogeneous luminosity function integration limits, as
+the integration limit is set to a fixed fraction of the break
+luminosity (cf.\ discussion in Section~\ref{sec:e912}.)  A spectral
+index of $\alpha_\mathrm{UV}=-1.7$ is assumed.
+\citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
+evolving the \HeIII\ ionization fraction in a gas cloud with the mean
+cosmic baryonic density exposed to the average \HeII-ionizing flux.
+The ionizing flux is obtained by filtering the ionizing emissivity
+through an inhomogeneous IGM in which the column density distribution
+of \HeIII\ is derived from that of \HI\ in a manner similar to
+\citet{2012ApJ...746..125H}.  As a result, this model incorporates the
+effect of \HeII\ Lyman-limit systems, and the $Q_\nHeIII$ evolution in
+this model deviates from our predictions towards the end of
+reionization, as seen in Figure~\ref{fig:qhe}.  Comparing the
+emissivity model in the cosmological radiative transfer simulations of
+\citet{2009ApJ...694..842M} with our models is less straightforward.
+Quasars are modelled in the simulations of \citet{2009ApJ...694..842M}
+by relating quasar luminosities and lifetimes to halo masses following
+the galaxy-merger-induced quasar activity model of
+\citet{2005ApJ...630..705H}.  The resultant bolometric quasar
+luminosity functions are somewhat shallower than those of
+\citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
+index of $\alpha_\mathrm{UV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
+shows that the resultant reionization history in these simulations
+agrees with our model for $M_\mathrm{1450}<-21$, except towards the
+end of reionization, where, as before, \HeII\ Lyman-limit systems
+become important.
+
+Helium reionization is delayed in the model of
+\citet{2012ApJ...746..125H} due to their reduced emissivity at $z\sim
+3$.  In the \citet{2015ApJ...813L...8M} model, a significant
+\HeII\ fraction is ionized already at $z=6$ due to the very high
+emissivity assumed in this model.  In the radiation-hydrodynamic
+simulations by \citet{2016ApJ...828...90L}, the AGN population is
+calibrated to the SDSS and COSMOS data at $z>3.5$
+\citep{2012ApJ...755..169M, 2013ApJ...768..105M}, combined with a
+model for quasar light curves.  The fiducial \HeII\ reionization
+history obtained by these authors is shown in Figure~\ref{fig:qhe}
+along with an estimate of the uncertainty.  Reionization ends
+considerably later in this model ($z\sim 2.6$).  Our redshift of
+reionization agrees more closely with that in the simulations
+presented by \citet{2014MNRAS.445.4186C}.
 

### 2018-04-05 qhe.py
Finalise various model assumptions
Code is now also checked against HM12

@@ -7,6 +7,8 @@ See also: q.py.
 import numpy as np
 from scipy.integrate import odeint
 from scipy.interpolate import RectBivariateSpline
+import cosmolopy.distance as cd
+import cosmolopy.density as crho 
 
 if __name__ == '__main__':
     import matplotlib as mpl
@@ -16,7 +18,8 @@ if __name__ == '__main__':
     mpl.rcParams['font.serif'] = 'cm'
     mpl.rcParams['font.size'] = '22'
     import matplotlib.pyplot as plt
-    import sys 
+    import sys
+
 
 data = np.load('e1450_18.npz')
 z18 = data['z']
@@ -41,71 +44,48 @@ print 'data loaded'
 hplanck = 6.62e-27
 c_angPerSec = 2.998e18
 nu0 = 3.288e15 # threshold freq for H I ionization; s^-1 (Hz)
+msolkg = 1.988435e30 # solar mass; kg
+mH = 1.67372353855e-27 # kg; mass of hydrogen atom
+mHe = 6.64647616211e-27 # kg; mass of helium atom
+cmbympccb = 3.4036771916e-74 # (cm/Mpc)^3 conversion factor
+yrbys = 3.154e7 # yr/s conversion factor 
 
-cosmo_params_MH15 = True 
+cosmo_params_MH15 = True
 if cosmo_params_MH15:
     # Madau and Haardt 2015 parameters
     omega_b = 0.045
     omega_lambda = 0.7
     omega_nr = 0.3
+    Y_He = 0.24
+    h = 0.7
+    cosmo = {'omega_M_0': omega_nr,
+             'omega_lambda_0': omega_lambda,
+             'omega_k_0': omega_nr,
+             'omega_b_0': omega_b,
+             'h': h,
+             'X_H': 1-Y_He }
 else:
     # Sherwood parameters
     omega_b = 0.0482
     omega_lambda = 0.692
     omega_nr = 0.308
-
-z_HM12 = np.loadtxt('z_HM12.txt')
-data_HM12 = np.loadtxt('hm12.txt')
-w_HM12 = data_HM12[:,0]
-e_HM12 = data_HM12[:,1:]
-
-# kx=1 and ky=1 required here to get good interpolation at the Lyman
[…]

### 2018-04-05 rtg2.py
Tabulate values for paper

@@ -13,7 +13,7 @@ import gammapi
 from gammapi import get_gammapi_percentiles
 import matplotlib.patches as mpatches
 
-data = np.load('e1450_18.npz')
+data = np.load('e1450_18_2.npz')
 z18 = data['z']
 medianbright18 = data['medianbright']
 medianfaint18 = data['medianfaint']
@@ -22,7 +22,7 @@ upbright18 = data['upbright']
 downfaint18 = data['downfaint']
 upfaint18 = data['upfaint']
 
-data = np.load('e1450_21.npz')
+data = np.load('e1450_21_2.npz')
 z21 = data['z']
 medianbright21 = data['medianbright']
 medianfaint21 = data['medianfaint']
@@ -30,6 +30,18 @@ downbright21 = data['downbright']
 upbright21 = data['upbright']
 downfaint21 = data['downfaint']
 upfaint21 = data['upfaint']
+
+data = np.load('e912_18_2.npz')
+z18_912 = data['z']
+median18_912 = data['median']
+down18_912 = data['down']
+up18_912 = data['up']
+
+data = np.load('e912_21_2.npz')
+z21_912 = data['z']
+median21_912 = data['median']
+down21_912 = data['down']
+up21_912 = data['up']
 
 print 'data loaded'
 
@@ -1100,23 +1112,64 @@ def draw_g_paper():
     g18f = ax.fill_between(z, g_up/1.0e-12, y2=g_down/1.0e-12, color='red', zorder=5, alpha=0.6, edgecolor='None')
     g18, = plt.plot(z, g/1.0e-12, lw=2, c='red', zorder=5)
 
+    gamma18 = g
+    gamma18_up = g_up
+    gamma18_low = g_down 
+
     z, g = j(emissivity_21, zmax=15.0)
     z, g_down = j(emissivity_21_down, zmax=15.0)
     z, g_up = j(emissivity_21_up, zmax=15.0)
     g21f = ax.fill_between(z, g_up/1.0e-12, y2=g_down/1.0e-12, color='blue', zorder=5, alpha=0.6, edgecolor='None')
     g21, = plt.plot(z, g/1.0e-12, lw=2, c='blue', zorder=5)
     
-    # g18 = g
+    gamma21 = g
+    gamma21_up = g_up
+    gamma21_low = g_down 
 
-    # z, g = j(emissivity_21, zmax=15.0)
[…]

### 2018-04-05 tabulate_emissivities_global.py
Make tables for paper

@@ -1,0 +1,69 @@
+import numpy as np
+
+data = np.loadtxt('rtg2_data.txt')
+print data.shape
+
+z = data[:,0]
+
+e1450_18 = np.log10(data[:,1])
+e1450_18_up = np.log10(data[:,3])
+e1450_18_low = np.log10(data[:,2])
+
+de1450_18_plus = e1450_18_up - e1450_18
+de1450_18_minus = e1450_18 - e1450_18_low
+
+e1450_21 = np.log10(data[:,4])
+e1450_21_up = np.log10(data[:,6])
+e1450_21_low = np.log10(data[:,5])
+
+de1450_21_plus = e1450_21_up - e1450_21
+de1450_21_minus = e1450_21 - e1450_21_low
+
+e912_18 = np.log10(data[:,7])
+e912_18_up = np.log10(data[:,9])
+e912_18_low = np.log10(data[:,8])
+
+de912_18_plus = e912_18_up - e912_18
+de912_18_minus = e912_18 - e912_18_low
+
+e912_21 = np.log10(data[:,10])
+e912_21_up = np.log10(data[:,12])
+e912_21_low = np.log10(data[:,11])
+
+de912_21_plus = e912_21_up - e912_21
+de912_21_minus = e912_21 - e912_21_low
+
+g_18 = np.log10(data[:,13])
+g_18_up = np.log10(data[:,15])
+g_18_low = np.log10(data[:,14])
+
+dg_18_plus = g_18_up - g_18
+dg_18_minus = g_18 - g_18_low
+
+g_21 = np.log10(data[:,16])
+g_21_up = np.log10(data[:,18])
+g_21_low = np.log10(data[:,17])
+
+dg_21_plus = g_21_up - g_21
+dg_21_minus = g_21 - g_21_low
+
+fs = (r'{:.1f} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
+      r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} \\')
+
+for i in range(len(z)-1,-1,-1):
+
[…]

### 2018-04-06 Paper/paper.tex
Update text

@@
 
-%% Q notation is different on figure and in text.
-%% MH15 curve seems wrong; it should reionize at z ~ 4 or so.
 \begin{figure}
@@
     when the AGN luminosity function is integrated down to
-    $M_{1450}=-21$ (blue curve) and $M_{1450}=-18$ (red curve).  The
-    shaded regions show the one-sigma (68.26\%) uncertainty.  Other
-    curves show models of \citet[solid grey]{2012ApJ...746..125H},
-    \citet[dashed grey]{2015ApJ...813L...8M}, \citet[light blue and
-      shaded region]{2016ApJ...828...90L},
-    \citet[blue]{2018arXiv180104931P},
-    \citet[brown]{2009ApJ...694..842M}, and
+    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
+    (red curve and shaded region).  The shaded regions show the
+    one-sigma (68.26\%) uncertainty.  Other curves show models of
+    \citet[solid grey]{2012ApJ...746..125H}, \citet[dashed
+      grey]{2015ApJ...813L...8M}, \citet[brown with shaded
+      region]{2016ApJ...828...90L}, \citet[blue]{2018arXiv180104931P},
+    \citet[maroon]{2009ApJ...694..842M}, and
     \citet[green]{2014MNRAS.445.4186C}.  Note that we derive
@@
     presence of \HeII\ Lyman-limit systems and becomes inaccurate
-    towards the end of \HeII\ reionization. \label{fig:qhe}}
+    towards $Q_\nHeIII\sim 1$. \label{fig:qhe}}
 \end{figure}
@@
 contribution from this extrapolated emissivity to \HeII-reionization
-is small.  As before, we assume the SEDs given by
-Equations~(\ref{eqn:sed}) and (\ref{eqn:sed_faint}) for bright and
-faint AGN, respectively.  The recombination time scale in
+is small.  As before, we assume the SED given by
+Equations~(\ref{eqn:sed}), which has a spectral index of
+$\alpha_\mathrm{EUV}=-1.7$.  The recombination time scale in
 Equation~(\ref{eqn:qHedot}) is given by
@@
 \end{equation}
-where $n_\nH$ is the average physical number density of hydrogen,
-$\alpha_B$ is the case-B \HeIII\ recombination rate, and $\chi=0.083$
-is the cosmic number fraction of Helium.  We assume that the helium
-clumping factor $C$ is given by \citep{2015ApJ...813L...8M}
+where $\langle n_\nH\rangle$ is the average physical number density of
+hydrogen, $\alpha_B$ is the case-B \HeIII\ recombination rate, and
+$\chi=0.079$ is the cosmic number fraction of helium for a cosmic
+helium mass fraction of $Y_\mathrm{He}=0.24$.  The hydrogen number
+density is given by $\langle n_\nH\rangle=1.881\times
+10^{-7}(1+z)^3$~cm$^{-3}$.  We assume that the helium clumping factor
+$C$ is given by \citep{2015ApJ...813L...8M}
 \begin{equation}
@@
 
-Note that Equation~(\ref{eqn:qHedot}) neglects the \HeII\ Lyman-limit
-systems that play an increasingly important role towards the end of
-Helium reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.
-In the absence of these self-shielded systems of high-density \HeII,
-$Q_\nHeIII$ can continue to increase beyond unity.  We set it to one
-when this happens.  This can be corrected by accounting for the
-\HeII\ column density distribution and filtering the \HeII-ionizing
-radiation background through it.  Unfortunately, the \HeII\ column
-density distribution is itself uncertain.  We therefore consider our
-treatment of $Q_\nHeIII$ accurate enough for the purpose of this work.
+Equation~(\ref{eqn:qHedot}) neglects the \HeII\ Lyman-limit systems
+that play an increasingly important role towards the end of Helium
+reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.  In the
+absence of these self-shielded systems of high-density \HeII,
+$Q_\nHeIII$ can continue to increase beyond unity.  The mean free path
+of \HeII-ionizing photon diverges.  We set $Q_\nHeIII=1$ when this
+happens.  This can be corrected by accounting for the \HeII\ column
+density distribution and filtering the \HeII-ionizing radiation
+background through it.  Unfortunately, the \HeII\ column density
+distribution is itself uncertain \citep{2018arXiv180104931P}.  We
+consider our treatment of $Q_\nHeIII$ accurate enough for the purpose
+of this work, while noting that the redshift of \HeII\ reionization is
+likely an overestimate in our model.
 
@@
 Figure~\ref{fig:qhe} for $M_\mathrm{1450}<-18$ and
-$M_\mathrm{1450}<-21$ in red and blue, respectively.  We find that
-Helium reionization is complete, respectively, at $z\sim 3.2$ and
-$3.1$ in these models, with a one-sigma uncertainty of about $\Delta
-z\sim 0.2$.  Observational constraints on the \HeII\ reionization
-history are derived from measurements of the effective \HeII\ \lya
-optical depth \citep{2001Sci...293.1112K, 2004ApJ...600..570S,
-  2006A&A...455...91F, 2010ApJ...722.1312S, 2011ApJ...733L..24W,
-  2016ApJ...825..144W}.  While we do not compute the effective
-\HeII\ \lya optical depth in our model, the reionization histories
-shown in Figure~\ref{fig:qhe} may likely be consistent with the
-optical depth measurements of \citet{2016ApJ...825..144W}, who find
-that the effective optical depth rises at $z>2.7$, but low optical
-depth sightlines continue to be seen beyond this redshift.  The
-incidence of these low opacity sightlines implies that the substantial
-volume of \HeII\ was ionized already at $z=3.4$.  \HeII\ reionization
-begins at $z\gtrsim 5$ in our models.  When we consider AGN with
-$M_\mathrm{1450}<-18$, the ionization fraction $Q_\nHeIII$ has a
-one-sigma spread of 0.8--1 at $z=3.4$.
+$M_\mathrm{1450}<-21$.  When only AGN with $M_\mathrm{1450}<-21$ are
+accounted, Helium reionization is complete at $z\sim
+3.20^{+0.08}_{-0.12}$ where the uncertainty is one-sigma.  When the
+luminosity function is extrapolated down to $M_\mathrm{1450}<-18$,
+\HeII\ is reionized at $z=3.47^{+0.22}_{-0.26}$.  \HeII\ reionization
+begins at $z\gtrsim 5$ in both models.  Observational constraints on
+the \HeII\ reionization history are derived from measurements of the
+effective \HeII\ \lya optical depth \citep{2001Sci...293.1112K,
+  2004ApJ...600..570S, 2006A&A...455...91F, 2010ApJ...722.1312S,
+  2011ApJ...733L..24W, 2016ApJ...825..144W}.  These are considered to
+imply a redshift of \HeII\ reionization of $z=2.7$
+\citep{2011ApJ...733L..24W}.  While we do not compute the effective
+\HeII\ \lya optical depth in our model, the higher reionization
+redshifts in our models are partly explained by the absence of
+\HeII\ Lyman-limit systems, as discussed above.  Furthermore, the
+reionization histories shown in Figure~\ref{fig:qhe} may likely be
+consistent with the optical depth measurements of
+\citet{2016ApJ...825..144W}, who find that the effective optical depth
+rises at $z>2.7$, but low optical depth sightlines continue to be seen
+beyond this redshift.  The incidence of these low opacity sightlines
+implies that the substantial volume of \HeII\ was ionized already at
+$z=3.4$, consistent with our models.
 
@@
 other models of \HeII\ reionization in the literature.  Our model
-curves are closest in agreement to the simulations of
-\citet{2009ApJ...694..842M} and the analytical model of
+curve for $M_\mathrm{1450}<-21$ is closest in agreement to the
+simulations of \citet{2009ApJ...694..842M} and the analytical model of
 \citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
-\HeII-ionizing emissivity of AGN by fitting the function form in
+\HeII-ionizing emissivity of AGN by fitting the functional form in
 Equation~(\ref{eqn:e912fit}) to the emissivities reported by
@@
 the integration limit is set to a fixed fraction of the break
-luminosity (cf.\ discussion in Section~\ref{sec:e912}.)  A spectral
-index of $\alpha_\mathrm{UV}=-1.7$ is assumed.
+luminosity, as discussed above in Section~\ref{sec:e912}.)  A spectral
+index of $\alpha_\mathrm{EUV}=-1.7$ is assumed.
 \citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
@@
 \citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
-index of $\alpha_\mathrm{UV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
+index of $\alpha_\mathrm{EUV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
 shows that the resultant reionization history in these simulations
@@
 3$.  In the \citet{2015ApJ...813L...8M} model, a significant
-\HeII\ fraction is ionized already at $z=6$ due to the very high
-emissivity assumed in this model.  In the radiation-hydrodynamic
-simulations by \citet{2016ApJ...828...90L}, the AGN population is
-calibrated to the SDSS and COSMOS data at $z>3.5$
-\citep{2012ApJ...755..169M, 2013ApJ...768..105M}, combined with a
-model for quasar light curves.  The fiducial \HeII\ reionization
-history obtained by these authors is shown in Figure~\ref{fig:qhe}
-along with an estimate of the uncertainty.  Reionization ends
-considerably later in this model ($z\sim 2.6$).  Our redshift of
-reionization agrees more closely with that in the simulations
-presented by \citet{2014MNRAS.445.4186C}.
-
-Helium reionization has also been studied by
-\citet{2018MNRAS.473.1416M}, who constrained the evolution of the
-emissivity from AGN using the effect optical depth measurement of
-\citet{2016ApJ...825..144W}, combined with an analytical model of the
-IGM.  While a detailed comparison with their work is difficult because
-of reasons, \citet{2018MNRAS.473.1416M} find that the AGN emissivity
-has to drop considerably rapidly at $z>4$. \citet{2018arXiv180109693K}
-have recently presented a model of Helium reionization.  Reionization
-ends at redshift 2.8 in their model.  The AGN luminosity function used
-is by a combination of deteminations from various data sets
-\citep{2015MNRAS.451L..30K}.  The integration limits are inconsistent
-however as they are $0.01L_*$.  Resulting emissivity is comparable to
-our model at $z\sim 2$ but drops more rapidly towards higher
-redshifts.  For a steep EUV spectral index of $\alpha=-1.8$ their
-helium reionization redshift is $z=2.8$.  \citet{2016arXiv160706467D}
-considered the effect of AGN-dominated reionization on the Ly$\alpha$
-opacity at $z>5$, He~\textsc{ii} Ly$\alpha$ opacity at $z\sim
-3.1$--$3.3$, and the thermal history of the IGM.  In agreement with
-\citet{2015MNRAS.453.2943C}, these authors found that AGN did provide
-a plausible explanation for the large fluctuations in the Ly$\alpha$
-opacity at $z>5$.  However, they found that reionization of
-He~\textsc{ii} occurs much earlier in these AGN-dominated models (see
-also \citealt{2018MNRAS.473.1416M}).
+\HeII\ fraction is ionized already at $z=6$, and reionization is
+complete by $z=4.1$ due to the very high emissivity assumed in this
+model.  In the radiation-hydrodynamic simulations by
+\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
+SDSS \citep{2013ApJ...768..105M} and COSMOS
+\citep{2012ApJ...755..169M} data at $z>3.5$, combined with a model for
+quasar light curves.  The fiducial \HeII\ reionization history
+obtained by these authors is shown in Figure~\ref{fig:qhe} along with
+an estimate of the uncertainty.  Reionization ends considerably later
+in this model ($z\sim 2.6$).  The \HeII\ reionization history in our
+model for $M_\mathrm{1450}<-18$ agrees closely with that in the
+radiative transfer simulations presented by
+\citet{2014MNRAS.445.4186C}.  The AGN population in these simulations
+is `turned on' at $z=5$ and evolved assuming a pure luminosity
+evolution to match the inferred luminosity function of
+\citet{2011ApJ...728L..26G}.  The somewhat early reionization in the
+simulations of \citet{2014MNRAS.445.4186C} relative to most other
+models shown in Figure~\ref{fig:qhe} may be driven by the
+significantly higher emissivity from AGN with intermediate brightness
+($M_{1450}\sim -23$) in the model of \citet{2011ApJ...728L..26G}.
+However, the limited numerical resolution of these simulations may
+also play a role \citep{2014MNRAS.445.4186C}.
+
+An important constraint on \HeII\ reionization can be derived from the
+thermal history of the IGM.  \citet{2018MNRAS.473.1416M} constrained
+the evolution of the 912\,\AA\ emissivity of AGN by assuming a
+spectral index of $\alpha_\mathrm{EUV}=-1.57$ and using the
+measurements of the effective \HeII\ \lya optical depth
+\citep{2016ApJ...825..144W} and the IGM temperature
+\citep{2011MNRAS.410.1096B}.  \citet{2018MNRAS.473.1416M} found that
+although these data favour a reionization history in which \HeII\ is
+reionized at $z>4$, the 912\,\AA\ emissivity of AGN is nevertheless
+required to drop rapidly at $z>3$.  This emissivity evolution is much
+more rapid than that in our model for $M_\mathrm{1450}<-21$, with the
+caveat that the constraint derived by \citet{2018MNRAS.473.1416M} is
+model-dependent and assumes a shallower EUV spectrum.  A steeper
+spectrum with $\alpha_\mathrm{EUV}=-1.8$ was assumed in a recent model
+by \citet{2018arXiv180109693K}.  The resultant emissivity evolution is
+consistent with our model for $M_\mathrm{1450}<-21$, although somewhat
+more rapid at $z>2$.  The AGN luminosity function is derived by
+combining determinations from various data sets
+\citep{2015MNRAS.451L..30K}.  An inhomogeneous integration limit of
+$0.01L_*$ is applied to calculate the emissivity.  \HeII\ reionization
+ends at $z=2.8$ in the model of \citet{2018arXiv180109693K}.
+(\citealt{2017MNRAS.471..255K} argued that for their luminosity
+function model, spectra with $\alpha_\mathrm{EUV}>-1.6$ are unlikely
+to be consistent with the \HeII\ \lya data.)
+\citet{2017MNRAS.468.4691D} considered the effect of an AGN-dominated
+reionization on the \HI\ Ly$\alpha$ opacity at $z>5$,
+\HeII\ Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the thermal
+history of the IGM.  These authors found that that any scenario in
+which reionization of \HeII\ completes at $z>3$ is inconsistent with
+the measurements of the IGM temperature at $z=4$--$5$.  We leave the
+analysis of the IGM thermal history implied by our AGN luminosity
+models for future work.
 

### 2018-04-09 Paper/paper.tex
Update text

@@
   Santa Barbara, CA 93106-9530 USA}
-% Update Gabor's address to Potsdam
 \date{Accepted ---. Received ---; in original form ---}
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[scale=0.65]{emissivity.pdf}
-    % gammapi.py -- draw_emissivity() 
-  \end{center}
-  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
-    fraction down to a limiting magnitude.  Brown points show the
-    emissivity when the best-fit double power law luminosity functions
-    at respective redshifts are integrated down to $M_{1450}=-18$.
-    Black points show the integration limit when the limit is assumed
-    to be $M_{1450}=-21$.  For comparison, various other published
-    models of the 1~Ry emissivity of AGN are also shown.  The blue
-    curve in these panels shows the AGN 912~\AA\ emissivity model of
-    \citet{2012ApJ...746..125H}, which is very similar to the model of
-    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
-    determination from the fits of \citet{2015AA...578A..83G}.  The
-    maroon curve is the published fit to the 1~Ry emissivity evolution
-    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
-    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
-    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
-      HM12 Lstar limits.  Mention that Akiyama open and filled circles
-      are very close.}}
-  \label{fig:e912}
-\end{figure*}
+%% \begin{figure*}
+%%   \begin{center}
+%%     \includegraphics[scale=0.65]{emissivity.pdf}
+%%     % gammapi.py -- draw_emissivity() 
+%%   \end{center}
+%%   \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
+%%     fraction down to a limiting magnitude.  Brown points show the
+%%     emissivity when the best-fit double power law luminosity functions
+%%     at respective redshifts are integrated down to $M_{1450}=-18$.
+%%     Black points show the integration limit when the limit is assumed
+%%     to be $M_{1450}=-21$.  For comparison, various other published
+%%     models of the 1~Ry emissivity of AGN are also shown.  The blue
+%%     curve in these panels shows the AGN 912~\AA\ emissivity model of
+%%     \citet{2012ApJ...746..125H}, which is very similar to the model of
+%%     \citet{2007ApJ...654..731H}.  Red circles with error bars show the
+%%     determination from the fits of \citet{2015AA...578A..83G}.  The
+%%     maroon curve is the published fit to the 1~Ry emissivity evolution
+%%     in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
+%%     the model of \citet{2015ApJ...813L...8M}.  The grey and brown
+%%     curves show the best-fit form of Equation XX. \gk{Mention MH15 and
+%%       HM12 Lstar limits.  Mention that Akiyama open and filled circles
+%%       are very close.}}
+%%   \label{fig:e912}
+%% \end{figure*}
 
@@
 The open and filled black circles with errorbars in
-Figure~\ref{fig:e912} show the resultant 1~Ry emissivity when the
+Figure~\ref{fig:e912_2} show the resultant 1~Ry emissivity when the
 luminosity function is integrated down to $M_{1450}<-21$ (open
@@
 \end{equation}
-We fit this to the points shown in Figure~\ref{fig:e912} assuming a
+We fit this to the points shown in Figure~\ref{fig:e912_2} assuming a
 Gaussian likelihood in each bin.  The corresponding best-fit curves
@@
 published determinations of the 1~Ry emissivity of quasars are also
-shown in both panels of Figure~\ref{fig:e912}.  We now comment on the
+shown in both panels of Figure~\ref{fig:e912_2}.  We now comment on the
 comparison of our results with these measurements.
@@
 $M_{1450}=-18$ and $-21$.  The resultant values are shown by the open
-and closed brown circles at $z=0$ in Figure~\ref{fig:e912}.  Our
+and closed brown circles at $z=0$ in Figure~\ref{fig:e912_2}.  Our
 emissivity values at $z=0$ lie in between the
@@
 
-The brown dashed curve in Figure~\ref{fig:e912} shows the AGN 1~Ry
+The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 1~Ry
 emissivity model of \citet{2012ApJ...746..125H}, which based on the
@@
 Their assumed emissivity agrees reasonably well with our
-$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912}
+$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912_2}
 shows the model presented by \citet{2015ApJ...813L...8M}.  This model
@@
 combining binned luminosity function estimates from different sources
-inhomogeneously.  The green curves in Figure~\ref{fig:e912} show the
+inhomogeneously.  The green curves in Figure~\ref{fig:e912_2} show the
 luminosity function derived from a variability-selected sample
@@
 luminosity function down to our two chosen integration limits.  The
-result is shown in Figure~\ref{fig:e912} by the solid and dashed
+result is shown in Figure~\ref{fig:e912_2} by the solid and dashed
 orange curves, which correspond to $M_{1450}<-21$ and $-18$,
@@
 agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
-models disagree by 10--30\%.  Figure~\ref{fig:e912} also shows the
+models disagree by 10--30\%.  Figure~\ref{fig:e912_2} also shows the
 model presented by \citet{2016A&A...587A..41P}.  We consider their
@@
 \citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
-orange rectangle in Figure~\ref{fig:e912}.  The lower side of the
+orange rectangle in Figure~\ref{fig:e912_2}.  The lower side of the
 rectangle corresponds to the emissivity for the
@@
 
-The red open cirles with error bars in Figure~\ref{fig:e912} show the
+The red open cirles with error bars in Figure~\ref{fig:e912_2} show the
 determination from the fits of \citet{2015AA...578A..83G}.  These
@@
 LF to our cosmology and assumed our SED obtain the emissivities shown
-by the green circles in Figure~\ref{fig:e912}.  Again the open and
+by the green circles in Figure~\ref{fig:e912_2}.  Again the open and
 filled circles corresponds to our two integration limits.  Our
@@
 luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
-in Figure~\ref{fig:e912}.  These authors report 1668 AGN candidates at
+in Figure~\ref{fig:e912_2}.  These authors report 1668 AGN candidates at
 $3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
@@
 \subsection{Photon underproduction at $z=0$?}
-
-Our derivation of the LyC emissivity of AGN allows us to see if the
-corresponding hydrogen photoionization rate is consistent with the
-measured CDDF of the low-redshift ($z<0.5$) Ly$\alpha$ forest
-\citep{2016ApJ...817..111D}.  \citet{2014ApJ...789L..32K} argued that
-in order to match the CDDF observed by \citet{2016ApJ...817..111D} at
-\gk{Define acronym CDDF.}  these redshifts, hydrodynamical
+% Kollmeier number of ~10 times higher than HM12 in figure.
+
+It is instructive to closely examine if the corresponding hydrogen
+photoionization rate is consistent with the \HI\ column density
+distribution function measured from the \lya\ forest
+\citep{2016ApJ...817..111D} at low redshifts ($z<0.5$).
+\citet{2014ApJ...789L..32K} argued that in order to match the
+\HI\ column density distribution function observed by
+\citet{2016ApJ...817..111D} at these redshifts, hydrodynamical
 cosmological simulations require a hydrogen photoionization rate that
-is a factor of five larger than that in the UV background (UVB) model
-of \citet{2012ApJ...746..125H}.  \gk{This factor looks more than five
-  in our plot!}  Several recent studies in the literature have
-addressed this ``photon underproduction crisis''.  On the one hand,
-these studies emphasised the uncertainty in the
-\citet{2012ApJ...746..125H} UVB model at these redshifts due to the
-lack of certainty in the UV photon emissivities of galaxies and AGN
-\citep{2015MNRAS.451L..30K, 2015ApJ...811....3S}.  On the other hand,
-they noted the uncertainty in the results of the cosmological
-simulations at these redshifts, due to effects such as AGN feedback
-and limited numerical resolution \citep{2015ApJ...811....3S,
-  2017MNRAS.467L..86V, 2017MNRAS.471.1056N, 2017ApJ...837..106O,
-  2017MNRAS.466..838G, 2017MNRAS.467.3172G, 2017ApJ...835..175G}.  A
-general conclusion of these studies was that the discrepancy between
-the photoionization rate required by the observed CDDF and predicted
-by the UVB model of \citet{2012ApJ...746..125H} is likely to be
-smaller than that found by \citet{2014ApJ...789L..32K}.  The
-discrepancy is about a factor of 2 instead of 5.
+is a factor of five larger than that in the UV background model of
+\citet{2012ApJ...746..125H}.  Several recent studies have addressed
+this `photon underproduction crisis' \citep{2015MNRAS.451L..30K,
+  2015ApJ...811....3S, 2017MNRAS.467.3172G, 2017MNRAS.467.4802F,
+  2017MNRAS.466..838G, 2017MNRAS.467L..86V}.  On the one hand, these
+studies emphasised the uncertainty in the \citet{2012ApJ...746..125H}
+UVB model at these redshifts due to the lack of certainty in the UV
+photon emissivities of galaxies and AGN \citep{2015MNRAS.451L..30K,
+  2015ApJ...811....3S}.  On the other hand, they noted the uncertainty
+in the results of the cosmological simulations at these redshifts, due
+to effects such as AGN feedback and limited numerical resolution
+\citep{2015ApJ...811....3S, 2017MNRAS.467L..86V, 2017MNRAS.471.1056N,
+  2017ApJ...837..106O, 2017MNRAS.466..838G, 2017MNRAS.467.3172G,
+  2017ApJ...835..175G}.  A general conclusion of these studies was
+that the discrepancy between the photoionization rate required by the
+observed \HI\ column density distribution and predicted by the UVB
+model of \citet{2012ApJ...746..125H} is likely to be smaller than that
+found by \citet{2014ApJ...789L..32K}.
+
+%% The discrepancy is about a
+%% factor of two instead of five.
 
@@
   \caption{Evolution of the hydrogen photoionisation rate at low
-    redshifts (cf.\ Figure~\ref{fig:gammapi}).\label{fig:puc}}
+    redshifts, when the AGN luminosity function is integrated down to
+    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
+    (red curve and shaded region).  Shaded regions show the one-sigma
+    (68.26\%) uncertainty.  Also shown are the models and inferences
+    from \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
+    contribution in this model (dashed grey), \citet[dotted
+      green]{2015ApJ...813L...8M}, \citet[dashed
+      black]{2015ApJ...811....3S}, the QSO contribution from the model
+    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
+      grey]{2017ApJ...837..106O}, \citet[dashed
+      brown]{2018arXiv180104931P}, \citet[yellow
+      box]{2017MNRAS.467.4802F}, \citet[black
+      box]{2017MNRAS.467L..86V}, \citet[inverted
+      triangle]{2013MNRAS.436.1023B},
+    \citet[pentagon]{2014ApJ...789L..32K}, and
+    \citet[circle]{2017MNRAS.467.3172G}. Note that we use the the
+    \HI\ column density distribution model from
+    \citet{2012ApJ...746..125H} to derive the photoionization rate.
+    \label{fig:puc}}
 \end{figure}
 
-The black curve in Figure~\ref{fig:puc} shows the evolution of the
-hydrogen photoionization rate due to AGN in our best-fit global
-luminosity function model.  (Yellow shaded region around the black
-curve shows the small 68\% uncertainty.)  We find that the
-photoionisation rate in our model due to AGN alone is higher than that
-in the \citet{2012ApJ...746..125H} UVB model by a factor of 2.  This
-higher photoionisation rate is consistent with that derived by
-\citet{2015MNRAS.451L..30K} using the quasar luminosity function
-measurements of \citet{2009MNRAS.392...19C} and
-\citet{2013A&A...551A..29P}.  It is also consistent with the
-photoionization rate found by \citet{2017MNRAS.467.3172G}, who found
-that this photoionisation rate is sufficient to explain the CDDF
-measured by \citet{2016ApJ...817..111D}.
-
-\gk{Add discussion about Schulze point from Gabor's 8 March email
-  here.}
+Figure~\ref{fig:puc} shows the evolution of the \HI\ photoionization
+rate due to AGN in our model for luminosity function integration
+limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that this
+photoionization rate is derived by fitting the model from
+Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
+luminosity functions in various redshift bins.  While doing this, as
+discussed above, redshift bins that were interpreted as being affected
+by systematic errors were ignored.  As a result, the emissivity model
+used in calculating the photoionization rate is an extrapolation at
+$z<0.6$.  However, it is interesting to note that even if we disregard
+the $z<0.6$ data due to systematic errors, the extrapolated
+emissivities at these redshifts are consistent with the emissivities
+calculated from our luminosity function fits to these data for either
+of our chosen integration limits.  This can be seen in
+Figure~\ref{fig:e912_2}.  We find that the low-redshift
+\HI\ photoionization rate in our model is higher than that in the
+\citet{2012ApJ...746..125H} UVB model by a factor of 1.2 for
+$M_{1450}<-21$ and a factor of 2 for $M_{1450}<-18$.  The
+photoionization rate obtained when the faint AGN ($M_{1450}<-18$) are
+included is consistent with a variety of recent estimates.  This rate
+is in reasonable agreement with the photoionization rate found by
+\citet{2017MNRAS.467.3172G}, who found that this photoionisation rate
+is sufficient to explain the \HI\ column density distribution measured
+by \citet{2016ApJ...817..111D}, thus alleviating the photon
+underproduction problem without requiring additional contribution of
+hydrogen-ionizing photons from galaxies.  At $z<0.5$, this
+photoionization rate evolution in our model appears consistent also
+with that derived by \citet{2015MNRAS.451L..30K} using the quasar
+luminosity function measurements of \citet{2009MNRAS.392...19C} and
+\citet{2013A&A...551A..29P}, although the evolution is somewhat
+shallower in our model at $z>0.5$.  The model of
+\citet{2015ApJ...813L...8M} also agrees with our $M_{1450}<-18$
+inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
+\HI\ column density distribution measurements to cosmological
+simulations with an enhanced photoionization rate relative to the
+\citet{2012ApJ...746..125H} model to find that
+$\Gamma_\mathrm{HI}=4.6\times 10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$
+produces the observed \HI\ column densities.  This photoionization
+rate was achieved in the simulations of \citet{2015ApJ...811....3S} by
+a combination of quasars and galaxies (with an escape fraction of
+hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
+seen in Figure~\ref{fig:puc}, this photoionization rate agrees with
+our model at $z\sim 0$ for $M_{1450}<-18$, although it evolves
+somewhat more rapidly at higher redshifts.  The photoionization rate
+estimate by \citet{2017MNRAS.467.4802F} from the H$\alpha$ surface
+brightness of a $z\sim 0$ galaxy observed by VLT/MUSE is somewhat
+higher than even our $M_{1450}<-18$ determination.  However, it is
+possible that the \citet{2017MNRAS.467.4802F} estimate is an upper
+limit, as the contribution of local sources to the photoionization
+rate is neglected in their modelling.  The requirement of an enhanced
+photoionization rate at $z\sim 0$ relative to
+\citet{2012ApJ...746..125H} UVB model is also confirmed by the
+simulations presented by \citet{2017MNRAS.467L..86V},
+\citet{2017ApJ...837..106O}, and \citet{2018arXiv180104931P}.  But
+note that, as discussed above in Section~\ref{sec:e912}, a direct
+comparison of our results with the models of
+\citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K}, and
+\citet{2018arXiv180104931P} is difficult because of the inhomogenous
+redshift-dependent integration limits adopted by these authors.
 
@@
   \begin{center}
+    % qhe.py 
     \includegraphics[width=\columnwidth,keepaspectratio]{q.pdf}
@@
 derived a higher 912\,\AA\ emissivity than our estimates
-(cf.\ Figure~\ref{fig:e912}), so that in their analysis AGN can
+(cf.\ Figure~\ref{fig:e912_2}), so that in their analysis AGN can
 produce all ionizing photons necessary to keep hydrogen ionized and
@@
   \begin{center}
+    % summary_giallongo.py
     \includegraphics[width=0.7\textwidth]{evolution_g.pdf}
@@
   \begin{center}
+    % giallongo_compare.py 
     \includegraphics[width=\textwidth]{giallongo_compare.pdf}
@@
 $M_{1450}<-21$.  These tables describe the curves shown in
-Figures~\ref{fig:e912} and \ref{fig:gammapi}.  Note that the
+Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.  Note that the
 photoionisation rate calculation assumes an \HI\ column density
@@
     units are s$^{-1}$.  These values are shown in
-    Figures~\ref{fig:e912} and \ref{fig:gammapi}.  See
+    Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.  See
     Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.}

### 2018-04-10 Paper/paper.tex
Update text

@@
   \caption{AGN contribution to the hydrogen photoionisation rate,
-    assuming 100\% escape fraction.  Model luminosity functions are
-    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
-    the right panel.  The solid black curve shows the hydrogen
-    photoionisate rate in our best-fit global model, and the yellow
-    curves show a random sample from the global posterior.  The red
-    points with error bars in this figure show the measurements of
-    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
-    forest, and the orange points show the measurements by
-    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
-    dashed green curve shows the hydrogen photoionisation rate
-    evolution in the model of \citet{2012ApJ...746..125H}, while the
-    solid green curve shows the contribution of quasars to it. }
+    assuming unit escape fraction, when the AGN luminosity function is
+    integrated down to $M_{1450}=-21$ (blue curve and shaded region)
+    and $M_{1450}=-18$ (red curve and shaded region).  The shaded
+    regions show the one-sigma (68.26\%) uncertainty.  Also shown are
+    the photoionization rate measurements by \citet[filled
+      circles]{2013MNRAS.436.1023B}, \citet[inverted
+      triangles]{2011MNRAS.412.2543C}, and
+    \citet[pentagons]{2017MNRAS.467.3172G}, and models of
+    \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
+    contribution in this model (dashed grey), \citet[dashed
+      brown]{2015ApJ...813L...8M}, the QSO contribution from the model
+    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
+      grey]{2017ApJ...837..106O}, and \citet[dashed
+      grey]{2018arXiv180104931P}.}
   \label{fig:gammapi}
@@
 
-The 1~Ry emissivity can now be used to calculate the ionizing flux and
-photoionization rate contributed by quasars.  The frequency dependence
-above 1~Ry is given by Equation~(\ref{eqn:sed}) or
-(\ref{eqn:sed_faint}), so that for $\nu > \nu_{912}$
+The 912\,\AA\ emissivity can now be used to calculate the hydrogen
+ionizing flux and the hydrogen photoionization rate contributed by
+AGN.  This adds an additional layer of uncertainty as the \HI\ column
+density structure of the IGM has not been measured at all redshifts of
+interests, thereby requiring uncertain extrapolation.  The frequency
+dependence of the AGN SED above 1~Ry is given by
+Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
+\nu_{912}$
 \begin{equation}
@@
 where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
-(Equation~\ref{eqn:sed_faint}).  The flux in the IGM is
-written as a solution of the cosmological radiative transfer equation
-as \citep{2012ApJ...746..125H}
+(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
+($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
+IGM is written as a solution of the cosmological radiative transfer
+equation as \citep{2012ApJ...746..125H}
 \begin{multline}
-  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}\frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
+  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
+  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
   \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
@@
 \begin{equation}
-  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
-\end{equation}
-where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$ and the column density
-distribution $f(N_\mathrm{HI}, z)$ is taken to be a power law \citep{2013MNRAS.436.1023B}
-\begin{equation}
-  f(N_\mathrm{HI}, z) = \frac{A}{N_\mathrm{LL}}\left(\frac{N_\mathrm{HI}}{N_\mathrm{LL}}\right)^{-\beta_N}\left(\frac{1+z}{4.5}\right)^{-\beta_z},
-\end{equation}
-with $A=0.93$, $\beta_N=1.33$, $\beta_z=1.92$, and
-$N_\mathrm{LL}=10^{17.2}$~cm$^{-2}$.  The hydrogen photoionization
-rate is then given by
-\begin{equation}
-  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j(\nu,z)}{h\nu} \sigma(\nu),
-\end{equation}
-where $\sigma$ is the photoionization cross-section.  The result is
-shown in Figure~\ref{fig:gammapi}, in which as before the solid black
-curve shows the hydrogen photoionisate rate in our best-fit global
-model, and the yellow curves show a random sample from the global
-posterior.  Also, as before, the right panel of
-Figure~\ref{fig:gammapi} shows the result when we only account for
-quasars brighter than $M_{1450}=-20$, while the left panel shows the
-result when the integration limit is $M_{1450}=-18$.  The red points
-with error bars in this figure show the measurements of
-\citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$ forest,
-and the orange points show the measurements by
-\citet{2011MNRAS.412.2543C} from quasar proximity zones.  The dashed
-green curve shows the hydrogen photoionisation rate evolution in the
-model of \citet{2012ApJ...746..125H}, while the solid green curve
-shows the contribution of quasars to it.
-
-The black open circles show the photoionisation rate values derived
-from our fits in the individual redshift bins.  However, note that
-unlike in the global model it is not possible to do the integral in
-Equation~(\ref{eqn:flux}) for these individual fits.  We can only
-derive the photoionisatoin rate by assuming what is known as the local
-source approximation, that is by assuming that the photons emitted at
-redshift $z$ are absorbed at the same redshift without propagation to
-large distances.
-
-In the local source approximation, Equation~(\ref{eqn:flux}) becomes
-\begin{equation}
-  j(\nu_0, z_0) = \frac{1}{4\pi}\lambda_\mathrm{mfp}(\nu_0, z_0)\epsilon(\nu_0, z_0),
-\end{equation}
-where $\lambda_\mathrm{mfp}$ is the mean free path.  The hydrogen
-photoionization rate is given by
-\begin{equation}
-  \Gamma_\mathrm{HI}=4\pi\int_{\nu_{912}}^\infty d\nu \frac{j_\nu}{h\nu} \sigma(\nu),
-  \label{eqn:gammapi}
-\end{equation}
-where $\sigma$ is the ionization cross-section
-\begin{equation}
-  \sigma(\nu) = \sigma_0\left(\frac{\nu}{\nu_{912}}\right)^{-3},
-  \label{eqn:sigma}
-\end{equation}
-with $\sigma_0=6.3\times 10^{-18}$~cm$^2$ \citep{2006agna.book.....O}.
-In the redshift range $z=2.3$--$5.5$, the mean free path is measured
-to be \citep{2014MNRAS.445.1745W}
-\begin{equation}
-  \lambda_\mathrm{mfp}(\nu, z)= \lambda_0\left(\frac{1+z}{5}\right)^{-5.4}\left(\frac{\nu}{\nu_{912}}\right)^{1.5},
-  \label{eqn:mfp}
-\end{equation}
-where the frequency dependence comes from the assumed column density
-distribution $f(N_\mathrm{HI})\propto N_\mathrm{HI}^{-1.5}$.  We
-extrapolate the redshift dependence in Equation~(\ref{eqn:mfp}) at
-$z<2.3$ and $z>5.5$.  Combining Equations~(\ref{eqn:epsilon_freq}),
-(\ref{eqn:sigma}), and (\ref{eqn:mfp}), Equation~(\ref{eqn:gammapi})
-gives
-\begin{multline}
-  \Gamma_\mathrm{HI}=4.6\times 10^{-13} \mathrm{s}^{-1} \left(\frac{\epsilon_{912}}{10^{24}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}}\right)\\
-  \times\left(\frac{1}{1.5-\alpha}\right)\left(\frac{1+z}{5}\right)^{-2.4}.
-\end{multline}
-Note that this equation refers to the \emph{comoving} emissivity.  The
-local source approximation works well for $z>3$, as can be seen in
-Figure~\ref{fig:gammapi}, where the points from the individual fits
-are in much better agreement with the curves from the global model.
-At lower redshift, the photoionisation rate in the individual models
-is much higher than that in the global model, because the individual
-models overestimate the flux at these redshifts.
-
-%% \begin{figure*}
-%%   \begin{center}
-%%     \includegraphics[width=\textwidth,keepaspectratio]{evolution.pdf}
-%%   \end{center}
-%%   \caption{Parameter evolution from individual fits.  Coloured points
-%%     show results when Giallongo quasars are not included.  Black
-%%     points show results when Giallongo quasars are included.}
-%% \end{figure*}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal_dense.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
-
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_diff_ind.pdf}
-%%   \end{center}
-%%   \caption{Alternative presentation of Figure~\ref{fig:rhoqso}.}
-%% \end{figure}
+  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
+  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
+\end{equation}
+where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
+contribution of helium to the opacity.)  We assume the \HI\ column
+density distribution given by \citet{2012ApJ...746..125H}.  The
+\HI\ photoionization rate is then given by
+\begin{equation}
+  \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
+  \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
+\end{equation}
+where $\sigma$ is the photoionization cross-section.  We assume an
+upper limit of $z=15$ while integrating Equation~(\ref{eqn:flux}).
+The result is shown in Figure~\ref{fig:gammapi} for the luminosity
+function integration limits of $M_{1450}=-21$ and $-18$.  Also shown
+for comparison are the measurements of \citet{2013MNRAS.436.1023B},
+derived from the Lyman-$\alpha$ forest, and the measurements by
+\citet{2011MNRAS.412.2543C} from quasar proximity zones.  For an
+integration limit of $M_{1450}=-21$ the AGN contribution to the
+hydrogen photoionization rate falls short of 100\% across the redshift
+range.  It is marginally consistent with the measured photoionization
+rate at $z=2.4$.  The photoionization rate in our model for
+$M_{1450}=-21$ has the same evolution but a higher amplitude by a
+factor of $\sim 2$ as the QSO contribution to the \HI\ photoionization
+rate in the model of \citet{2012ApJ...746..125H}.  For both of our
+integration limits, the photoionisation rate peaks at $z\sim 2$.  For
+the integration limit of $M_{1450}=-18$, AGN can provide all the flux
+necessary to explain the observed \lya forest between $z=2.4$ and
+$3.2$, with a contribution from other sources necessary only at higher
+redshifts.  The photoionization rate in the $M_{1450}<-18$ case also
+agrees with the inference of \citet{2017MNRAS.467.3172G} from the
+low-redshift ($z<0.6$) \lya\ data.  We discuss this low-redshift
+evolution in greater detail in the next section.
+
+An important conclusion from Figure~\ref{fig:gammapi} is that the AGN
+contribution to hydrogen reionization is likely subdominant, although
+it can be non-negligible if faint AGN down to $M_{1450}=-18$ emit
+hydrogen-ionizing photons with our assumed SED and a unit escape
+fraction.  At $z=6.1$, AGN with $M_{1450}<-18$ contribute about $10\%$
+of the required \HI\ ionizing flux.  The contribution of
+$M_{1450}<-21$ at this redshift is $\sim 3\%$.  At $z=6$, our
+determinations are lower than those by \citet{2015AA...578A..83G} by
+almost an order of magnitude.  This difference arises from the
+difference in the inferred emissivities in our models relative to
+\citet{2015AA...578A..83G}, as discussed in the previous section.  The
+photoionization rate evolution in the model of
+\citet{2015ApJ...813L...8M} agrees with our determination at low
+redshifts ($z<0.5$) for $M_{1450}<-18$ but is much higher at $z>4$, as
+expected from the higher emissivities assumed by these authors.  At
+$3<z<6$ our model photoionization rates are understandably lower than
+those in the models of \citet{2017ApJ...837..106O} and
+\citet{2018arXiv180104931P} as these authors include contribution to
+the photoionization rate from galaxies in their models. The
+differences in our model from that of \citet{2015MNRAS.451L..30K} are
+a result of our differences from the reported emissivities of
+\citet{2009MNRAS.392...19C} and \citet{2013A&A...551A..29P}, which are
+used by \citet{2015MNRAS.451L..30K} to derive an emissivity evolution
+model.
 
@@
 found by \citet{2014ApJ...789L..32K}.
-
-%% The discrepancy is about a
-%% factor of two instead of five.
 

### 2018-04-10 Paper/paper.tex
Update text

@@
   \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
-    fraction down to a limiting magnitude.  Brown points show the
-    emissivity when the best-fit double power law luminosity functions
-    at respective redshifts are integrated down to $M_{1450}=-18$.
-    Black points show the integration limit when the limit is assumed
-    to be $M_{1450}=-21$.  For comparison, various other published
-    models of the 1~Ry emissivity of AGN are also shown.  The blue
-    curve in these panels shows the AGN 912~\AA\ emissivity model of
-    \citet{2012ApJ...746..125H}, which is very similar to the model of
-    \citet{2007ApJ...654..731H}.  Red circles with error bars show the
-    determination from the fits of \citet{2015AA...578A..83G}.  The
-    maroon curve is the published fit to the 1~Ry emissivity evolution
-    in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
-    the model of \citet{2015ApJ...813L...8M}.  The grey and brown
-    curves show the best-fit form of Equation XX. \gk{Mention MH15 and
-      HM12 Lstar limits.  Mention that Akiyama open and filled circles
-      are very close.}}
+    fraction down to a limiting magnitude for a luminosity function
+    integration limit of $M_{1450}=-18$ (left panel) and
+    $M_{1450}=-21$ (right panel).  Black filled circles with error
+    bars in both panels show the emissivity determinations in redshift
+    bin deemed to have low systematic errors.  Open circles show
+    emissivities for redshift bins that we remove from analysis due to
+    high systematic errors.  Solid red curves in both panels show the
+    best fit emissivity evolution model, with the shaded area showing
+    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
+    both panels are models by \citet[pentagon
+      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
+    \citet[square]{2015AA...578A..83G},
+    \citet[triangle]{2018PASJ...70S..34A},
+    \citet[circle]{2018AJ....155..131M},
+    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
+      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
+      curve]{2015ApJ...813L...8M}, \citet[dashed
+      brown]{2012ApJ...746..125H}, \citet[dashed
+      grey]{2017MNRAS.466.1160M}, \citet[dashed
+      blue]{2013A&A...551A..29P}, \citet[solid
+      cyan]{2016A&A...587A..41P}, and \citet[solid
+      blue]{2017A&A...608A..64C}}
   \label{fig:e912_2}
@@
 
+We now discuss the contribution of AGN to the hydrogen and helium
+reionization in our luminosity function model.  We first derive the
+expected evolution of the 912\,\AA\ emissivity of AGN in our model,
+and then use this to estimate the \HI\ photoionization rate and the
+average \HeIII\ fraction.
+
 \subsection{Hydrogen-ionizing emissivity}
@@
 
-We can now calculate the contribution of quasars to the hydrogen
-photoionization rate in the intergalactic medium (IGM).  We assume
-that all quasars have a universal UV SED, parameterised by
+We assume that all quasars have a universal UV SED, parameterised by
 \citet{2015MNRAS.449.4204L} as a power law with a break at 912~{\AA},
@@
 This fit was derived by \citet{2015MNRAS.449.4204L} from a composite
-spectrum of 53 quasars at $z\sim 2.4$.
-
-While four published composite quasar UV SEDs
-\citep{2002ApJ...565..773T, 2001AJ....122..549V, 2012ApJ...752..162S,
-  2014ApJ...794...75S} agree with Equation~(\ref{eqn:sed}), the
-composite of \citet{2004ApJ...615..135S}, which uses more than 100
-quasars at $z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.
-The quasars considered by \citet{2004ApJ...615..135S} are fainter
+spectrum of 53 quasars at $z\sim 2.4$.  While four published composite
+quasar UV SEDs \citep{2002ApJ...565..773T, 2001AJ....122..549V,
+  2012ApJ...752..162S, 2014ApJ...794...75S} agree with
+Equation~(\ref{eqn:sed}), the composite of
+\citet{2004ApJ...615..135S}, which uses more than 100 quasars at
+$z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.  The
+quasars considered by \citet{2004ApJ...615..135S} are fainter
 ($M_i(z=2)>-26$) than those considered by \citet{2015MNRAS.449.4204L},
@@
 \begin{equation}
-\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu}.
-\end{equation}
-Here the integral is over a suitable range of magnitudes, the
+\dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
+\end{equation}
+where the integral is over a suitable range of magnitudes, the
 monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
@@
 \end{equation}
-and $\phi$ is the luminosity function from Equation~(\ref{eqn:dpl}).
-The luminosity at 1~Ry is related to that at 1450~\AA\ by
-Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint})
+and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
+related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
+or (\ref{eqn:sed_faint})
 \begin{equation}
@@
 \end{equation}
-depending on the AGN luminosity.  The corresponding physical volume
+depending on the AGN luminosity.  The corresponding comoving volume
 emissivity is
 \begin{equation}
-\epsilon_\nu = \dot n_\nu h\nu (1+z)^3.
+\epsilon_\nu = \dot n_\nu h\nu.
 \label{eqn:epsilon}
 \end{equation}
-The open and filled black circles with errorbars in
-Figure~\ref{fig:e912_2} show the resultant 1~Ry emissivity when the
-luminosity function is integrated down to $M_{1450}<-21$ (open
-circles) and when it is integrated down to $M_{1450}<-18$ (filled
-circles).  Redshift bins that were removed from analysis due to large
-systematic errors are not shown.  Similar to the previous figures, the
-black open circles in this figure show the result form individual
-redshift bins, while the black curve shown the result from best-fit
-global model.  Due to the problems with the global luminosity function
-models discussed above, we avoid using them to describe the emissivity
-evolution.  Instead, we describe the emissivity evolution by the
-5-parameter functional form \citep{2012ApJ...746..125H}
+Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
+the luminosity function is integrated down to $M_{1450}<-21$ (right
+panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
+Redshift bins that were removed from analysis due to large systematic
+errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
+depending on the luminosity integration limit, at
+$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
+and decreased rapidly towards high redshifts.  A continuous
+description of this emissivity evolution is valuable in deriving the
+hydrogen photoionizing flux in the IGM.  In principle, the luminosity
+function evolution models discussed in the previous section provide
+such a description.  Unfortunately, as discussed above, all of these
+models suffer from pathologies such as non-monotonic or divergent AGN
+number densities, likely resulting from residual systematic errors in
+the data.  Therefore, here we describe the emissivity evolution by the
+five-parameter functional form used by \citet{2012ApJ...746..125H}
 \begin{equation}
@@
 \end{equation}
-We fit this to the points shown in Figure~\ref{fig:e912_2} assuming a
-Gaussian likelihood in each bin.  The corresponding best-fit curves
-and the corresponding one-sigma uncertainty is shown in red
-($M_{1450}<-18$) and blue ($M_{1450}<-21$).  The best-fit form of
-Equation~\ref{eqn:e912fit} is given by 
+We fit this model to the emissivity estimates in the redshift bins,
+shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
+the emissivity in each bin.  The resultant best-fit curves and the
+corresponding one-sigma uncertainties are shown in
+Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
+912\,\AA\ emissivities in various redshift bins and in these best-fit
+models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
+form of Equation~\ref{eqn:e912fit} is given by
 \begin{multline}
@@
 \end{multline}
-for $M_{1450}<-21$.  The 1~Ry emissivity increases rapidly from $z=0$
-up to $z=2$ and then stays roughly constant until up to $z=3.5$.  At
-higher redshifts, due to the relatively steeper faint end slope of the
-luminosity function, the integration limit makes a large difference in
-the resultant emissivity.  For the conservative case, in which we
-integrate under the luminosity function down to $M_{1450}=-20$, the
-emissivity drops rapidly at $z>3.5$For comparison, various other
-published determinations of the 1~Ry emissivity of quasars are also
-shown in both panels of Figure~\ref{fig:e912_2}.  We now comment on the
-comparison of our results with these measurements.
-\citet{2009A&A...507..781S} combined data from the Hamburg/ESO survey
-and the SDSS to measure a quasar luminosity function at $z=0$ in their
-$B_J$ band to minimize host galaxy contribution.  We convert their
-$B_J$ magnitudes (Vega system) to $M_{1450}$ (AB) as
-\begin{equation}
-  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
-\end{equation}
-In this magnitude system, the luminosity function reported by
-\citet{2009A&A...507..781S} has a very faint break luminosity of
-$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
-integrate this luminosity function down to our limiting magnitudes of
-$M_{1450}=-18$ and $-21$.  The resultant values are shown by the open
-and closed brown circles at $z=0$ in Figure~\ref{fig:e912_2}.  Our
-emissivity values at $z=0$ lie in between the
-\citet{2009A&A...507..781S} measurements.  The convergence in the
-emissivity is slower in their measurements than in our models because
-of the shallower faint-end slope at this redshift in our model
-($\beta\sim -1.22$).  We discuss the 1~Ry emissivity and the
-corresponding hydrogen photoionization rate at $z=0$ below.
-
-The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 1~Ry
-emissivity model of \citet{2012ApJ...746..125H}, which based on the
-bolometric luminosity function model of \citet{2007ApJ...654..731H}.
-Their assumed emissivity agrees reasonably well with our
-$M_{1450}<-21$ case.  The green dotten curve in Figure~\ref{fig:e912_2}
-shows the model presented by \citet{2015ApJ...813L...8M}.  This model
-disagrees with ours rather severely at almost all redshifts in the
-range considered here.  Note that a direct comparison with
-\citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M} is
-difficult because these models integrate the luminosity function to a
-fixed fraction of the break luminosity $L_*$ instead of a fixed
-absolute magnitude.  The chosen limite by \citet{2012ApJ...746..125H}
-and \citet{2015ApJ...813L...8M} is $0.01L_*$.  Using a limit that
-depends on the break luminosity can be problematic as different quasar
-surveys used to develop these emissivity models often report
-strikingly different break luminosity values.  Even when these samples
-are homogeneized appropriately, have such an integration limit is only
-justified if the faint-end slope of the luminosity function is
-sufficiently shallow.
-
-The grey dashed curve shows the emissivity model of
-\citet{2017MNRAS.466.1160M}.  These authors integrate the luminosity
-function down to $M_{1450}=-19$.  However, their model strongly
-disagrees with our inference, potentially due to biases resulting from
-combining binned luminosity function estimates from different sources
-inhomogeneously.  The green curves in Figure~\ref{fig:e912_2} show the
-luminosity function derived from a variability-selected sample
-observed using the Sloan telescope and the Multiple Mirror Telescope
-(MMT) by \citet{2013A&A...551A..29P}.  This sample of 1877 quasars
-does not overlap with the variability-selected sample reported by the
-BOSS survey \citep{2013ApJ...773...14R}.  \citet{2013A&A...551A..29P}
-assum constant luminosity function slopes with a break at $z=2.2$ and
-assume a pure luminosity evolution.  This leads to a discontinuity in
-the emissivity evolution in their model at $z=2.2$.  We convert their
-$g$-band magnitudes to $M_{1450}$ and integrate the resultant
-luminosity function down to our two chosen integration limits.  The
-result is shown in Figure~\ref{fig:e912_2} by the solid and dashed
-orange curves, which correspond to $M_{1450}<-21$ and $-18$,
-respectively.  For $M_{1450}<-21$, our models are in reasonable
-agreement at $z<2.2$.  At other redshifts and for $M_{1450}<-21$, the
-models disagree by 10--30\%.  Figure~\ref{fig:e912_2} also shows the
-model presented by \citet{2016A&A...587A..41P}.  We consider their
-PLE$+$LEDE model, in which the faint-end slope is assumed to stay
-constant with redshift.  Although the emissivity evolution in this
-model is continuous at $z=2.2$, it is not smooth.  This model agrees
-with our $M_{1450}<-18$ result to a better degree relative to the
-\citet{2013A&A...551A..29P} model.  We also compare our result with
-the PLE$+$LEDE luminosity function model presented by
-\citet{2017A&A...608A..64C} by reanalysing the
-\citet{2016A&A...587A..41P} sample with an improved $K$-correction
-implementation.  \citet{2017ApJ...847L..15O} recently fit a double
+for $M_{1450}<-21$.
+
+Before proceeding to derive a hydrogen photoionization rate estimate
+from these emissivities, we now comment on the comparison of our
+results with estimates from the literature.  Several of these are
+shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
+Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
+\citet{2012ApJ...746..125H}, which is based on the bolometric
+luminosity function model of \citet{2007ApJ...654..731H}.  Their
+assumed emissivity agrees reasonably well with our $M_{1450}<-21$
+case, although at its maximum the emissivity in the
+\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
+differences between the two models are much larger for $M_{1450}<-18$.
+Figure~\ref{fig:e912_2} also shows the model presented by
+\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
+severely at almost all redshifts in the range considered here, for
+both of our integration limits.  It is important to note here that a
+direct comparison of our model with \citet{2012ApJ...746..125H} and
+\citet{2015ApJ...813L...8M} is difficult because these models
+integrate the luminosity function to a fixed fraction of the break
+luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
+limite by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
+is $0.01L_*$.  Using a limit that depends on the break luminosity is
+problematic as different quasar surveys used to develop these
+emissivity models often report strikingly different break luminosity
+values.  Even when these samples are homogeneized appropriately, have
+such an integration limit is likely only justified if the faint-end
+slope of the luminosity function is sufficiently shallow.  This issue
+also affects some other models in the literature, such as those
+presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
+and \citet{2018arXiv180104931P}.
+
+\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
+$M_{1450}=-19$.  However, their model strongly disagrees with our
+inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
+biases resulting from inhomogeneously combining binned luminosity
+function estimates from different data sets.  The emissivity
+determinations from the luminosity function derived from a
+variability-selected sample observed using the Sloan telescope and the
+Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
+agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
+redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
+The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
+not included in our analysis, and therefore provides a cross-check.
+(This sample also does not overlap with the variability-selected
+sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
+\citet{2013A&A...551A..29P} assume constant double power law
+luminosity function slopes with a break at $z=2.2$ and assume a pure
+luminosity evolution.  This leads to a discontinuity in the emissivity
+evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
+convert their $g$-band magnitudes to $M_{1450}$ and integrate the
+resultant luminosity function down to our two chosen integration
+limits with our chosen SED for a direct comparison.
+Figure~\ref{fig:e912_2} also shows the model presented by
+\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
+which the faint-end slope is assumed to stay constant with redshift.
+Although the emissivity evolution in this model is continuous at
+$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
+smooth.  This model agrees with our $M_{1450}<-18$ result to a better
+degree relative to the \citet{2013A&A...551A..29P} model, bjt it
+results in a higher emissivity in the $M_{1450}<-21$ case.
+\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
+sample with an improved $K$-correction implementation, but, as seen in
+Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
+throughout the redshift range of their data.
+
+At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
 power law luminosity function model to a combined binned samples of
@@
 photometric redshift $z\sim 6$ reported by
-\citet{2018MNRAS.474.2904P}.  We show the resultant 1~Ry emissivity by
-orange rectangle in Figure~\ref{fig:e912_2}.  The lower side of the
-rectangle corresponds to the emissivity for the
+\citet{2018MNRAS.474.2904P}.  We show the resultant
+912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
+lower side of the rectangle corresponds to the emissivity for the
 \citet{2017ApJ...847L..15O} model excluding the
@@
 the emissivity is higher; this is shown by the upper end of the
-rectangle.  The open rectangle corresponds to $M_{1450}<-18$ and the
-closed rectangle corresponds to $M_{1450}<-21$.
-
-The red open cirles with error bars in Figure~\ref{fig:e912_2} show the
-determination from the fits of \citet{2015AA...578A..83G}.  These
-authors also choose a break luminosity-dependent integration limit of
-$0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their model.
-The resultant emissivities are factors of 2 to 3 higher than our
-determinations for $z=4$--$6$.  This is puzzling at first sight,
-because the AGN candidates reported by \citet{2015AA...578A..83G} are
-consistent with our luminosity function estimates obtained without
-these candidates (see Appendix~\ref{sec:conv}).  Our luminosity
-function are also somewhat steeper than those reported by
-\citet{2015AA...578A..83G}.  The discrepancy is explained by the
-difference in the two luminosity function models at intermediate
-magnitudes.  We find that the data prefer a much brighter break
-luminosity than that infered by \citet{2015AA...578A..83G}.  This
-reduces our emissivities relative to their estimates.  We go into this
-issue in further detail in Appendix~\ref{sec:conv}.
+rectangle.  Our emissivities broadly in agreement with the
+determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
+shows the determination from the fits of \citet{2015AA...578A..83G}.
+These authors also choose a break luminosity-dependent integration
+limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
+model.  The resultant emissivities are factors of 2 to 3 higher than
+our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
+puzzling at first sight, because the AGN candidates reported by
+\citet{2015AA...578A..83G} are consistent with our luminosity function
+estimates obtained without these candidates (see
+Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
+steeper than those reported by \citet{2015AA...578A..83G}.  The
+discrepancy is explained by the difference in the two luminosity
+function models at intermediate magnitudes.  We find that the data
+prefer a much brighter break luminosity than that inferred by
+\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
+their estimates.  We go into this issue in further detail in
+Appendix~\ref{sec:conv}.
 
@@
 than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
-LF to our cosmology and assumed our SED obtain the emissivities shown
-by the green circles in Figure~\ref{fig:e912_2}.  Again the open and
-filled circles corresponds to our two integration limits.  Our
-emissivity agrees with the measurement of \citet{2018AJ....155..131M}
-for $M_{1450}<-21$ but is higher than their measurement for
-$M_{1450}<-18$, which is not surprising due to the difference in the
-luminosity function slopes.  The emissivity derived from the
-luminosity function of \citet{2018PASJ...70S..34A} is shown in yellow
-in Figure~\ref{fig:e912_2}.  These authors report 1668 AGN candidates at
-$3.5<z<4.3$, of which 76 have spectroscopic redshifts.  Their reported
-faint-end slope is very flat ($\beta=-1.3\pm 0.05$), inconsistent with
-our determination at all redshifts.  Their inferred emissivity is
-consistent with our estimate for $M_{1450}\sim -21$.  Their emissivity
-does not change significantly with the integration limit thanks to the
-shallow slope.  We also compare our emissivities with the
-determinations reported by \citet{2012ApJ...755..169M} at $z\sim 3.2$
-and $z\sim 4$.  Their emissivity in reasonably agreement with our
-model for $M_{1450}<-21$ at $z\sim 3.2$.  But their $M_{1450}<-18$
-emissivity disagrees with all other high-redshift estimates, possibly
-indicating a systematic error.  Our emissivity estimates are in good
-agreement with those of \citet{2018MNRAS.474.2904P}.  Mention
-Bongiorno.
+LF to our cosmology and assuming our SED result in the emissivities
+shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
+measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
+higher than their measurement for $M_{1450}<-18$, which is not
+surprising due to the difference in the luminosity function slopes.
+The emissivity derived from the luminosity function of
+\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
+These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
+have spectroscopic redshifts.  Their reported faint-end slope is very
+flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
+all redshifts.  Their inferred emissivity is consistent with our
+estimate for $M_{1450}< -21$.  Their emissivity does not change
+significantly with the integration limit due to the shallow faint-end
+slope.  As a result, our $M_{1450}< -18$ determination of the
+emissivity is considerably higher than their estimate.  We also
+compare our emissivities with the determinations reported by
+\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
+emissivity in reasonable agreement with our model for $M_{1450}<-21$
+at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
+recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.
+
+At low redshifts, \citet{2009A&A...507..781S} combined data from the
+Hamburg/ESO survey and the SDSS to measure a quasar luminosity
+function at $z=0$ in their $B_J$ band to minimize host galaxy
+contribution.  We convert their $B_J$ magnitudes (Vega system) to
+$M_{1450}$ (AB) as
+\begin{equation}
+  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
+\end{equation}
+In this magnitude system, the luminosity function reported by
+\citet{2009A&A...507..781S} has a very faint break luminosity of
+$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
+integrate this luminosity function down to our limiting magnitudes of
+$M_{1450}=-18$ and $-21$.  The resultant values are shown in
+Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
+between the \citet{2009A&A...507..781S} measurements.  The convergence
+in the emissivity is slower in their measurements than in our models
+because of the shallower faint-end slope at this redshift in our model
+($\beta\sim -1.22$).
 

### 2018-04-13 Paper/paper.tex
Update text

@@
 \appendix
+
+\section{Comparison with other luminosity function determinations}
+
+Figure~\ref{fig:params_grand} compares the parameters of the double
+power law luminosity function from our analysis of
+Section~\ref{sec:bins} to values reported in the literature.  In
+general, our break luminosity is brighter and the faint-end slope is
+steeper than other determinations.  Note however that several results
+from the literature shown in Figure~\ref{fig:params_grand} make
+restrictive assumptions while fitting double power law models to data.
+For example, \citet{2013ApJ...768..105M} fix the bright-end slope
+$\alpha$ to $-4$ at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix
+the faint-end slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
+\citet{2017ApJ...847L..15O} fix the bright-end slope $\alpha$ to
+$-2.8$ at $z=5.5$--$6.5$.  \citet{2015AA...578A..83G} fix the
+faint-end slope and the break luminosity in their highest-redshift bin
+($z=5.0$--$6.5$).  The choice of data sets is also often different.
+For instance, \citet{2015AA...578A..83G} do not include the SDSS
+Stripe 82 data from \citet{2013ApJ...768..105M} and the AGN samples of
+\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in their
+analysis.  (We discuss the results of \citet{2015AA...578A..83G} in
+greater detail in Appendix~\ref{sec:conv}.)  Of the remaining
+determinations, our parameter values are closest to those reported by
+\citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.
+
+\begin{figure*}
+  \begin{center}
+    % summary_grand.py
+    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
+  \end{center}
+  \caption{A comparison of our inferred double power law parameter
+    values with those reported in the literature.  Black points show
+    our determinations from Figure~\ref{fig:evoln}.  Blue points show
+    other values, from \citet[triangles]{2012ApJ...755..169M},
+    \citet[squares]{2016ApJ...833..222J},
+    \citet[diamonds]{2011ApJ...728L..26G},
+    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
+      triangles]{2015AA...578A..83G},
+    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
+      triangles]{2017ApJ...847L..15O},
+    \citet[asterisks]{2016ApJ...829...33Y},
+    \citet[circles]{2013ApJ...773...14R}, and \citet[rightward
+      triangles]{2009A&A...507..781S}.  Where necessary, values from
+    the literature have been converted to our cosmology.
+    \label{fig:params_grand}}
+\end{figure*}
 

### 2018-04-16 Paper/paper.tex
Update text

@@
   Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
-  Universit\"at Potsdam, Karl-Liebknecht-Str.\ 24/25, 14476 Potsdam,
+  Universit\"at Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
   Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
@@
   \end{center}
-  \caption{Redshift distribution of the XX quasars considered in this
+  \caption{Redshift distribution of the 86,015 AGN considered in this
     analysis.  Shown here are the observed quasar numbers, without
@@
   \label{tab:bins}
-  \begin{tabular}{ccccrcccc}
+  \begin{tabular}{ccccr....}
     \hline
-    $\langle z\rangle$ & $z_\mathrm{bin}$ & $z_\mathrm{min}$ & $z_\mathrm{max}$ & $N_\mathrm{qso}$ & $\log_{10}(\phi_*/$ & $M_*$ & $\alpha$ & $\beta$ \\
-    & & & & & cMpc$^{-3}$mag$^{-1}$) & & & \\
+    $\langle z\rangle$ &
+    $z_\mathrm{bin}$ &
+    $z_\mathrm{min}$ &
+    $z_\mathrm{max}$ &
+    $N_\mathrm{qso}$ &
+    \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
+    \multicolumn{1}{c}{$M_*$} &
+    \multicolumn{1}{c}{$\alpha$} &
+    \multicolumn{1}{c}{$\beta$} \\
+
+    &
+    &
+    &
+    &
+    &
+    \multicolumn{1}{c}{cMpc$^{-3}$mag$^{-1}$)} &
+    &
+    & \\
     \hline
-    $0.31$ & $0.25$ & $0.10$ & $0.40$ & 3520 & $-5.62^{+0.09}_{-0.10}$ & $-21.37^{+0.21}_{-0.22}$ & $-2.94^{+0.09}_{-0.10}$ & $-1.22^{+0.18}_{-0.16}$ \\
-    $0.50$ & $0.50$ & $0.40$ & $0.60$ & 4555 & $-6.12^{+0.04}_{-0.04}$ & $-23.00^{+0.08}_{-0.08}$ & $-3.37^{+0.07}_{-0.08}$ & $-1.36^{+0.04}_{-0.04}$ \\
-    $0.72$ & $0.70$ & $0.60$ & $0.80$ & 3308 & $-6.42^{+0.09}_{-0.08}$ & $-24.03^{+0.15}_{-0.13}$ & $-3.55^{+0.12}_{-0.13}$ & $-1.75^{+0.05}_{-0.04}$ \\
-    $0.91$ & $0.90$ & $0.80$ & $1.00$ & 3922 & $-6.39^{+0.08}_{-0.07}$ & $-24.51^{+0.12}_{-0.11}$ & $-3.69^{+0.10}_{-0.11}$ & $-1.73^{+0.06}_{-0.05}$ \\
-    $1.10$ & $1.10$ & $1.00$ & $1.20$ & 6367 & $-6.53^{+0.03}_{-0.03}$ & $-25.14^{+0.04}_{-0.04}$ & $-4.17^{+0.08}_{-0.09}$ & $-1.73^{+0.02}_{-0.02}$ \\
-    $1.30$ & $1.30$ & $1.20$ & $1.40$ & 6479 & $-6.43^{+0.04}_{-0.04}$ & $-25.29^{+0.06}_{-0.06}$ & $-3.97^{+0.08}_{-0.08}$ & $-1.74^{+0.03}_{-0.03}$ \\
-    $1.50$ & $1.50$ & $1.40$ & $1.60$ & 7539 & $-6.51^{+0.03}_{-0.03}$ & $-25.68^{+0.04}_{-0.04}$ & $-4.28^{+0.08}_{-0.08}$ & $-1.75^{+0.02}_{-0.02}$ \\
-    $1.71$ & $1.70$ & $1.60$ & $1.80$ & 6788 & $-6.28^{+0.04}_{-0.04}$ & $-25.55^{+0.05}_{-0.05}$ & $-3.96^{+0.07}_{-0.07}$ & $-1.60^{+0.03}_{-0.03}$ \\
-    $1.98$ & $2.00$ & $1.80$ & $2.20$ & 10478 & $-6.72^{+0.03}_{-0.03}$ & $-26.26^{+0.04}_{-0.04}$ & $-4.20^{+0.07}_{-0.07}$ & $-1.87^{+0.02}_{-0.02}$ \\
-    $2.25$ & $2.25$ & $2.20$ & $2.30$ & 4102 & $-5.98^{+0.10}_{-0.09}$ & $-25.26^{+0.19}_{-0.18}$ & $-3.21^{+0.15}_{-0.16}$ & $-1.54^{+0.07}_{-0.06}$ \\
-    $2.35$ & $2.35$ & $2.30$ & $2.40$ & 4317 & $-6.28^{+0.09}_{-0.09}$ & $-25.63^{+0.17}_{-0.15}$ & $-3.39^{+0.17}_{-0.19}$ & $-1.64^{+0.06}_{-0.05}$ \\
-    $2.45$ & $2.45$ & $2.40$ & $2.50$ & 3403 & $-6.40^{+0.08}_{-0.07}$ & $-25.86^{+0.14}_{-0.13}$ & $-3.60^{+0.20}_{-0.21}$ & $-1.60^{+0.05}_{-0.05}$ \\
-    $2.65$ & $2.65$ & $2.60$ & $2.70$ & 1883 & $-5.98^{+0.06}_{-0.06}$ & $-25.15^{+0.14}_{-0.13}$ & $-3.13^{+0.12}_{-0.13}$ & $-1.05^{+0.09}_{-0.08}$ \\
-    $2.75$ & $2.75$ & $2.70$ & $2.80$ & 1135 & $-6.30^{+0.08}_{-0.07}$ & $-25.96^{+0.15}_{-0.13}$ & $-3.81^{+0.28}_{-0.31}$ & $-1.34^{+0.07}_{-0.06}$ \\
-    $2.85$ & $2.85$ & $2.80$ & $2.90$ & 1069 & $-6.46^{+0.12}_{-0.10}$ & $-26.23^{+0.23}_{-0.18}$ & $-3.60^{+0.36}_{-0.42}$ & $-1.46^{+0.08}_{-0.07}$ \\
-    $2.95$ & $2.95$ & $2.90$ & $3.00$ & 1104 & $-6.77^{+0.07}_{-0.06}$ & $-26.53^{+0.10}_{-0.09}$ & $-5.05^{+0.60}_{-0.64}$ & $-1.71^{+0.05}_{-0.04}$ \\
-    $3.05$ & $3.05$ & $3.00$ & $3.10$ & 1127 & $-6.77^{+0.08}_{-0.07}$ & $-26.48^{+0.12}_{-0.10}$ & $-4.71^{+0.46}_{-0.52}$ & $-1.70^{+0.06}_{-0.05}$ \\
-    $3.15$ & $3.15$ & $3.10$ & $3.20$ & 1041 & $-7.25^{+0.17}_{-0.12}$ & $-27.09^{+0.25}_{-0.18}$ & $-4.42^{+0.81}_{-1.23}$ & $-1.96^{+0.08}_{-0.06}$ \\
-    $3.25$ & $3.25$ & $3.20$ & $3.30$ & 815 & $-7.33^{+0.13}_{-0.13}$ & $-27.19^{+0.19}_{-0.23}$ & $-4.36^{+0.65}_{-0.76}$ & $-1.93^{+0.06}_{-0.06}$ \\
-    $3.34$ & $3.35$ & $3.30$ & $3.40$ & 510 & $-7.54^{+0.19}_{-0.21}$ & $-27.39^{+0.25}_{-0.37}$ & $-4.90^{+1.36}_{-1.35}$ & $-2.08^{+0.09}_{-0.07}$ \\
-    $3.44$ & $3.45$ & $3.40$ & $3.50$ & 155 & $-6.77^{+0.19}_{-0.20}$ & $-26.64^{+0.42}_{-0.35}$ & $-3.70^{+0.62}_{-0.80}$ & $-1.24^{+0.27}_{-0.22}$ \\
-    $3.88$ & $3.90$ & $3.70$ & $4.10$ & 628 & $-7.92^{+0.12}_{-0.10}$ & $-27.26^{+0.14}_{-0.12}$ & $-4.81^{+0.34}_{-0.39}$ & $-2.07^{+0.10}_{-0.09}$ \\
-    $4.35$ & $4.40$ & $4.10$ & $4.70$ & 442 & $-8.32^{+0.29}_{-0.26}$ & $-27.38^{+0.38}_{-0.31}$ & $-4.19^{+0.41}_{-0.47}$ & $-2.20^{+0.16}_{-0.13}$ \\
-    $4.92$ & $5.10$ & $4.70$ & $5.50$ & 263 & $-9.02^{+0.29}_{-0.22}$ & $-27.88^{+0.36}_{-0.27}$ & $-4.51^{+0.66}_{-0.83}$ & $-2.31^{+0.11}_{-0.08}$ \\
-    $6.00$ & $6.00$ & $5.50$ & $6.50$ & 66 & $-10.60^{+0.71}_{-1.06}$ & $-29.12^{+1.04}_{-1.78}$ & $-4.99^{+0.72}_{-1.22}$ & $-2.40^{+0.10}_{-0.08}$ \\
+    0.31 & 0.25 & 0.10 & 0.40 & 3520 & -5.62^{+0.09}_{-0.10} & -21.37^{+0.21}_{-0.22} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
+    0.50 & 0.50 & 0.40 & 0.60 & 4555 & -6.12^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.08} & -3.37^{+0.07}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
+    0.72 & 0.70 & 0.60 & 0.80 & 3308 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.15}_{-0.13} & -3.55^{+0.12}_{-0.13} & -1.75^{+0.05}_{-0.04} \\
+    0.91 & 0.90 & 0.80 & 1.00 & 3922 & -6.39^{+0.08}_{-0.07} & -24.51^{+0.12}_{-0.11} & -3.69^{+0.10}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
+    1.10 & 1.10 & 1.00 & 1.20 & 6367 & -6.53^{+0.03}_{-0.03} & -25.14^{+0.04}_{-0.04} & -4.17^{+0.08}_{-0.09} & -1.73^{+0.02}_{-0.02} \\
+    1.30 & 1.30 & 1.20 & 1.40 & 6479 & -6.43^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.06} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
+    1.50 & 1.50 & 1.40 & 1.60 & 7539 & -6.51^{+0.03}_{-0.03} & -25.68^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.75^{+0.02}_{-0.02} \\
+    1.71 & 1.70 & 1.60 & 1.80 & 6788 & -6.28^{+0.04}_{-0.04} & -25.55^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
+    1.98 & 2.00 & 1.80 & 2.20 & 10478 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.20^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
+    2.25 & 2.25 & 2.20 & 2.30 & 4102 & -5.98^{+0.10}_{-0.09} & -25.26^{+0.19}_{-0.18} & -3.21^{+0.15}_{-0.16} & -1.54^{+0.07}_{-0.06} \\
+    2.35 & 2.35 & 2.30 & 2.40 & 4317 & -6.28^{+0.09}_{-0.09} & -25.63^{+0.17}_{-0.15} & -3.39^{+0.17}_{-0.19} & -1.64^{+0.06}_{-0.05} \\
+    2.45 & 2.45 & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.13} & -3.60^{+0.20}_{-0.21} & -1.60^{+0.05}_{-0.05} \\
+    2.65 & 2.65 & 2.60 & 2.70 & 1883 & -5.98^{+0.06}_{-0.06} & -25.15^{+0.14}_{-0.13} & -3.13^{+0.12}_{-0.13} & -1.05^{+0.09}_{-0.08} \\
+    2.75 & 2.75 & 2.70 & 2.80 & 1135 & -6.30^{+0.08}_{-0.07} & -25.96^{+0.15}_{-0.13} & -3.81^{+0.28}_{-0.31} & -1.34^{+0.07}_{-0.06} \\
+    2.85 & 2.85 & 2.80 & 2.90 & 1069 & -6.46^{+0.12}_{-0.10} & -26.23^{+0.23}_{-0.18} & -3.60^{+0.36}_{-0.42} & -1.46^{+0.08}_{-0.07} \\
+    2.95 & 2.95 & 2.90 & 3.00 & 1104 & -6.77^{+0.07}_{-0.06} & -26.53^{+0.10}_{-0.09} & -5.05^{+0.60}_{-0.64} & -1.71^{+0.05}_{-0.04} \\
+    3.05 & 3.05 & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.10} & -4.71^{+0.46}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
+    3.15 & 3.15 & 3.10 & 3.20 & 1041 & -7.25^{+0.17}_{-0.12} & -27.09^{+0.25}_{-0.18} & -4.42^{+0.81}_{-1.23} & -1.96^{+0.08}_{-0.06} \\
+    3.25 & 3.25 & 3.20 & 3.30 & 815 & -7.33^{+0.13}_{-0.13} & -27.19^{+0.19}_{-0.23} & -4.36^{+0.65}_{-0.76} & -1.93^{+0.06}_{-0.06} \\
+    3.34 & 3.35 & 3.30 & 3.40 & 510 & -7.54^{+0.19}_{-0.21} & -27.39^{+0.25}_{-0.37} & -4.90^{+1.36}_{-1.35} & -2.08^{+0.09}_{-0.07} \\
+    3.44 & 3.45 & 3.40 & 3.50 & 155 & -6.77^{+0.19}_{-0.20} & -26.64^{+0.42}_{-0.35} & -3.70^{+0.62}_{-0.80} & -1.24^{+0.27}_{-0.22} \\
+    3.88 & 3.90 & 3.70 & 4.10 & 628 & -7.92^{+0.12}_{-0.10} & -27.26^{+0.14}_{-0.12} & -4.81^{+0.34}_{-0.39} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.40 & 4.10 & 4.70 & 442 & -8.32^{+0.29}_{-0.26} & -27.38^{+0.38}_{-0.31} & -4.19^{+0.41}_{-0.47} & -2.20^{+0.16}_{-0.13} \\
+    4.92 & 5.10 & 4.70 & 5.50 & 263 & -9.02^{+0.29}_{-0.22} & -27.88^{+0.36}_{-0.27} & -4.51^{+0.66}_{-0.83} & -2.31^{+0.11}_{-0.08} \\
+    6.00 & 6.00 & 5.50 & 6.50 & 66 & -10.60^{+0.71}_{-1.06} & -29.12^{+1.04}_{-1.78} & -4.99^{+0.72}_{-1.22} & -2.40^{+0.10}_{-0.08} \\
     \hline
@@
 \citep{2011ApJ...728...23W}, which can make estimating completeness
-difficult \citep{2006AJ....131.2766R}.  \gk{Gabor, could you please
-  check if I have written this paragraph OK?}
+difficult \citep{2006AJ....131.2766R}.
 
@@
   \end{center}
-  \caption{Luminosity function estimates from $z=0.3$ to $2.6$.
+  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
     Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
@@
     curves show the best-fit double power law luminosity function in
-    that redshift bin.  The green curves show the posterior
-    distribution of the global model.  The global model agrees very
-    well with the data in all redshift bins, except those spanned by
-    BOSS, as BOSS quasars are excluded from the global
-    analysis. \gk{Show all three models here.}}
+    that redshift bin.  Other curves show the three global evolution
+    models.  Shaded regions show the one-sigma (68.26\%)
+    uncertainties.}
   \label{fig:mosaic_global}
@@
   \caption{Luminosity function parameter evolution in the global
-    model.  The symbols show the best fit parameters with 68\%
-    uncertainties from the double power law fits to the data in
-    redshift bins.  These points are identical to those in
-    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
-    2$--$3$) are not shown.  In each panel, the black solid curve
-    shows the best fit global model, and the coloured curves show a
-    random sample drawn from the global posterior. \gk{Cannot see
-      best-fit curves.  Add open and closed circles to legend.}}
+    models.  The symbols show the best-fit parameters with one-sigma
+    (68.26\%) uncertainties in redshift bins from
+    Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected by
+    systematics and removed from the global analysis are shown in
+    grey.  In each panel, the solid curves and shaded regions show the
+    three best-fit global models with one-sigma uncertainties.
+    Model~1 provides a better fit, but requires a rapid change in the
+    faint-end slope at $z\sim 3.5$.}
   \label{fig:evoln_global}
@@
     \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
-    % rhoqso.py -- draw_withGlobal()
+    % rhoqso.py -- draw_withGlobal_multiple()
   \end{center}
-  \caption{AGN number density evolution in the global model.  Similar
-    to Figure~\ref{fig:evoln_global}, symbols show the best fit
-    parameters with 68\% uncertainties from the double power law fits
-    to the data in redshift bins.  Black solid curve shows the best
-    fit global model, and the coloured curves show a random sample
-    drawn from the global posterior. \gk{I still think we should show
-      the $-18$ case here.  Mention magnitude limits.  Reduce
-      transarency.  Extend plot to at least redshift 7.5.  Increase
-      legend handle length to match other figure. Should we add French
-      curve fits to this?}}
+  \caption{AGN number density evolution in the global model, when the
+    luminosity function is integrated (from top to bottom) down to
+    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
+    show the estimates from the best-fit double power law luminosity
+    functions in various redshift bins, with vertical error bars
+    denoting one-sigma (68.26\%) uncertainties.  Open circles show the
+    same in redshifts bins affected by systematics.  Curves show the
+    estimated density from the global models, with the accompanying
+    shaded regions denoting the one-sigma uncertainty. }
   \label{fig:rhoqso}
@@
       cyan]{2016A&A...587A..41P}, and \citet[solid
-      blue]{2017A&A...608A..64C}}
+      blue]{2017A&A...608A..64C}}.
   \label{fig:e912_2}
@@
 \subsection{Evolution of the luminosity function}
+\label{sec:global}
 
@@
 Figure~\ref{fig:evoln} suggests that it should be possible to describe
-the quasar UV luminosity function evolution out to $z\sim 7$ using far
-fewer number of parameters.  Such descriptions have been developed in
-the literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
+the quasar UV luminosity function evolution out to $z\sim 7$ using
+fewer parameters.  Such descriptions have been developed in the
+literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
 bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
-Such ``global'' descriptions of the luminosity function evolution are
-useful as they give a continuous description of the luminosity
-function.  This allows one to reduce the bias introduced by binning
-the data in arbitrary redshift bins.  By potentially allowing for
-extrapolations beyond the redshift range spanned by the data, such
-models are valuable for understanding of the physics behind the
-luminosity function.  Ideally, one would want to use physically
-meaningful parameters that govern the formation and evolution of the
-AGN population.  Unfortunately, such physical parameterisation is yet
-to be developed.  We therefore set up an empirical parameterisation to
+Such ``global'' models of the luminosity function evolution are useful
+as they give a continuous description of the luminosity function.
+This allows one to reduce the bias introduced by binning the data in
+arbitrary redshift bins.  By potentially allowing for extrapolations
+beyond the redshift range spanned by the data, such models are
+valuable for understanding of the physics behind the luminosity
+function.  Ideally, one would want to use physically meaningful
+parameters that govern the formation and evolution of the AGN
+population.  Unfortunately, such physical parameterisation is yet to
+be developed.  We therefore set up an empirical parameterisation to
 describe the evolution of the four parameters of the double power law
@@
 The negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
-straightforward generalisation of Equation~(\ref{eqn:S}), given by 
+a straightforward generalisation of Equation~(\ref{eqn:S}), given by
 \begin{multline}
@@
 redshift and luminosity bins.  We consider models in which the
-evolution of the four double power law parameter is modelled
-independently as in Equations~(\ref{eqn:global}).  This approach has
-been termed as ``flexible double power law'' by
-\citet{2015MNRAS.451.1892A}.  We present three such models in this
+evolution of the four double power law parameters is modelled
+independently as in Equations~(\ref{eqn:global}), an approach
+sometimes termed as ``flexible double power law''
+\citep{2015MNRAS.451.1892A}.  We present three such models in this
 paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
@@
 
-\item In Model 1, the parameters $\phi_*$, $M_*$ and $\alpha$ we
+\item In Model 1, for the parameters $\phi_*$, $M_*$ and $\alpha$ we
   assume that the functions $f_i$'s in Equations~(\ref{eqn:global})
@@
   Chebyshev expansion of Equation~(\ref{eqn:cbs}).  Instead, we
-  consider a double power law model for $\beta$ and write \gk{Is this
-    really only four parameters?}
+  consider a double power law model for $\beta$ and write 
   \begin{equation}
     f_3(1+z)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
+    \label{eqn:beta}
   \end{equation}
@@
 is again strikingly apparent.  So is the deviation of the SDSS and
-2SLAQ quasars at $z<0.6$.  This is an indirect justification of the
+2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
 data selection discussion previously in Section~\ref{sec:bins}.
@@
 down to different limits.  Similar to Figure~\ref{fig:evoln_global},
-symbols show the best-fit values with 68\% uncertainties from the
-double power law fits to the data in redshift bins.  Black solid curve
-shows the best fit global model, and the coloured curves show a random
-sample drawn from the global posterior.  This number density evolution
+symbols show the best-fit values with one-sigma uncertainties from the
+double power law fits to the data in redshift bins.  Solid curves and
+shaded regions show the global models.  This number density evolution
 again highlights the systematic error in data at $z\sim 3$.  The
@@
 high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
-downsizing feature in which the number density of faint qsos peaks are
-lower redshifts than that of the bright qsos.  While the number
-density of qsos with $M_*<-27$ peaks at $z\sim 2.5$, the number
-density of qsos with $M_*<-24$ peaks at $z\sim 2$.  At the faintest
-luminosity at which spectroscopic data exist, $M_*<-21$, the number
-density of qsos peaks at $z\sim 1$.  However, the difference between
-our three models is dramatically evidencet in Figure~\ref{fig:rhoqso}.
-Model~1 prefers a decrease in the number density of faint quasars at
-$z\sim 3$ followed by an increase at higher redshift.  This is caused
-by the rapid steepening of the faint-end slope in this model at this
-redshift.  Figure~\ref{fig:rhoqso} reveals another property of these
-models: when extrapolated, the AGN number density diverges in all
-three models are high redshifts.  This is result of the steep
-faint-end slope at high redshifts combined with the rapid brightening
-of the break luminosity at $z\sim 3$.  While no data exist at redshift
-$z>7.5$, this divergent behaviour is shared by previous models in the
-literature.  Figure~\ref{fig:rhoqso} also shows that although Models 2
-and 3 exhibit regular behaviour in the evolution of the AGN number
-density at $z\sim 3$, they do not fit the $z\sim 4$--$5$ data as well
-as Model 1.  \gk{Discuss comparison of expected number of quasars at
-  redshift 7 with UKIDSS.  Also discuss our new fit?}
+downsizing feature in which the number density of faint AGN peaks at
+lower redshifts than that of the bright AGN.  While the number density
+of AGN with $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN
+with $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at
+which spectroscopic data exist, $M_*<-21$, the number density of qsos
+peaks at $z\sim 1$.  However, the difference between our three models
+is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
+decrease in the number density of faint quasars at $z\sim 3$ followed
+by an increase at higher redshift.  This is caused by the rapid
+steepening of the faint-end slope in this model at this redshift.
+Figure~\ref{fig:rhoqso} reveals another property of these models: when
+extrapolated, the AGN number density diverges in all three models at
+high redshifts.  This is result of the steep faint-end slope at high
+redshifts combined with the rapid brightening of the break luminosity.
+While no data exist at redshift $z>7.5$, this divergent behaviour is
+shared by previous models in the literature
+\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
+although Models 2 and 3 exhibit regular behaviour in the evolution of
+the AGN number density at $z\sim 3$, they do not fit the $z\sim
+4$--$5$ data as well as Model 1.
 
@@
   \caption{Best-fit luminosity function evolution models.  These
-    parameters are defined in Equations XX.  See Section XX for
-    further details and the redshift range of validity of these
-    models.  Errors indicate one-sigma (68.26\%) uncertainties.  Model
-    2 is our preferred model.}
+    parameters are defined in Equations~(\ref{eqn:cbs}) and
+    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
+    details and the redshift range of validity of these models.
+    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
+    preferred model.}
   \label{tab:global}
@@
 We have presented an analysis of the evolution of the UV luminosity
-function of AGN from redshift $z=0$ to $7.5$ using a combined
-homogenised sample of close to 90,000 UV-selected AGN.  We only
-consider quasars with spectroscopic redshifts and reliable
-completeness estimates.  These data span magnitudes down to
-$M_{1450}=-22$ at high redshifts ($z\gtrsim 3.5$).
-
-\begin{itemize}
-\item The AGN luminosity function prefers a double power law
-  description at all redshift, except possibly at very high redshifts
-  ($z\sim 6$) where only the faint-end of the luminosity function is
-  observed.
-
-\item The break magnitude $M_*$ of the double power law luminosity
-  function shows a steep brightening towards the high redshift.  The
-  break evolves from $M_*<-25$ at $z\sim 2$ to $M_*\sim -29$ at $z\sim
-  6$.  Correspondingly, the amplitude $\phi_*$ of the luminosity
-  function drops rapidly towards high redshifts from $\phi_*\sim
-  10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 2$ to $\phi_*<
-  10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The break magnitude
-  at $z=6$ is very bright, about $-30$, which is why the constraints
-  on the bright end slope at these redshifts are weak.
-
-\item The faint end slope $\beta$ of the luminosity function shows
-  increased steepening at high redshifts, consistent with the findings
-  of \citep{2015AA...578A..83G}.  The faint-end slope is $\beta\sim
-  -1.8$ at $z\sim 2$ and steepens to $\beta\sim-2.5$ at $z\sim 6$.
-  The bright-end slope $\alpha$ also shows moderate steepening towards
-  high redshifts.  However, the constraints on $\alpha$ are weak,
-  particularly at the high redshift because of the bright break
-  luminosity.
-
-\item A fourteen-parameter model accurately captures the redshift
-  evolution of the luminosity function.  In this model, the evolution
-  of the break magnitude $M_*$ is described by a cubic polynomial in
-  $1+z$, while the evolution of the luminosity function amplitude
-  follows a quadratic polynomial in $1+z$.  The evolution of the
-  bright-end slope $\alpha$ evolves linearly in $1+z$.  The evolution
-  of the faint-end slope $\beta$ is more complicated.  The faint-end
-  slope stays roughly constant at lower redshifts $z<3$, steepens
-  rapidly at $z\sim 3$--$4$, and then remains constant at higher
-  redshifts.
-
-\item An important finding of this work is that there are severe
-  systematic errors in observed luminosity function.  We find that the
-  most significant systematic bias is at redshift $z\sim 3$ in the
-  BOSS sample of quasars.  There is also some evidence of a systematic
-  bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$ there is
-  some indication of a systematic error in completeness estimates at
-  the faintest magnitudes $M_{1450}\sim -19$.
-
-\item In spite of the rapid steepening of the luminosity function at
-  high redshifts, our derived LyC emissivity from AGN is quite low.
-  This is because of the bright break luminosities, which results in a
-  reduced contribution of intermediate brightness quasars to the Lyc
-  emissivity as compared to some other determinations in the
-  literature.  The LyC emissivity increases with time and peaks at
-  $z\sim 2$.  At lower redshifts, the emissivity drops rapidly with
-  time.  When our luminoisty function model is extrapolated and
-  integrated down to $M_{1450}\sim -20$, the implied LyC emissivity is
-  comparable to that in the model of \citet{2007ApJ...654..731H} and
-  \citet{2012ApJ...746..125H}.  This indicates that hydrogen
-  reionization is unlikely to have caused by AGN alone.
-
-\item We derive photoionization rate by considering the HI column
-  density distribution used by \citep{2012ApJ...746..125H}.  We find
-  that the HI photoionization rate is significantly lower than that
-  required by the Lyman-$\alpha$ forest data at $z>2$.  Our hydrogen
-  photoionization rate estimates are also considerably lower (by a
-  factor of at least two) than that of \citet{2015AA...578A..83G}.  At
-  the lowest redshifts, we find that the hydrogen photoionization rate
-  is about a factor of two higher than the estimate of
-  \citet{2007ApJ...654..731H} and \citet{2012ApJ...746..125H}.  When
-  compared with the recent analysis of \citet{2017MNRAS.467.3172G},
-  this photoionisation rate appears to allevaite the photon
-  underproduction crisis.  Cite Kollmeier here.
-
-\item Helium reionization in our model occurs at redshift $z\sim
-  3$ or $z=3.5$ if the luminosity function is integrated down to
-  $M_{1450}=-20$ and $-18$, respectively.
-
-\item Our analysis allows us to analyse the X-ray selected quasars of
-  \citet{2015AA...578A..83G} in the larger context of UV-selected
-  quasars.  We find that the the faint-end luminosity function
-  measurements of \citet{2015AA...578A..83G} at $z=4$--$6$ are
-  consitent with the measurements of the luminosity function at
-  brighter luminosities.  Stil, our inferred value of the hydrogen
-  ionizing luminosity density from quasars at these redshifts is much
-  lower that the value derived by \citet{2015AA...578A..83G}.  This
-  difference arises due to the difference in the data used in the two
-  analyses at intermediate to bright luminosities.  
-\end{itemize}
-
-Some next steps at $z>4$: 1. include extended objects at faint
-magntiudes that could be impacted by host galaxy light, 2. take
-follow-up spectroscopy to confirm a fration of these as high-z broad
-line AGN, 3. carefully assess host galaxy contamination.  See Gabor's
-email of 14 March 13:18.
+function of AGN from redshift $z=0$ to $7.5$ using a combined sample
+of close to 85,000 colour-selected AGN from 12 data sets, homogenized
+with respect to the assumed cosmology, intrinsic AGN spectrum, and the
+magnitude system.  AGN from 11 of these 12 samples have reported
+spectroscopic redshifts, and all but two AGN have known completeness
+estimates.  These data span magnitudes down to $M_{1450}=-22$ at high
+redshifts ($z\gtrsim 3.5$).
+
+We find that the UV luminosity function of AGN prefers a double power
+law description at all redshifts considered in this study, except
+possibly at very high redshifts ($z\sim 6$) where a single power law
+seems to be preferred.  The behaviour of the luminosity function at
+lower redshifts ($z=4$--$5.5$) suggests that this single power law at
+$z\sim 6$ can be interpreted as the faint end of the double power law
+with a break at $M_*=-29$.  The break magnitude $M_*$ of the double
+power law luminosity function shows a steep brightening towards high
+redshifts.  The break evolves from $M_*<-25$ at $z\sim 1$ to $M_*\sim
+-29$ at $z\sim 6$.  Correspondingly, the amplitude $\phi_*$ of the
+luminosity function drops rapidly towards high redshifts from
+$\phi_*\sim 10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 1$ to $\phi_*<
+10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The faint-end slope
+$\beta$ becomes increasingly negative towards high redshifts,
+resulting in the a steepening of the luminosity function.  The
+faint-end slope is $\beta\sim -1.8$ at $z\sim 1$ and steepens to
+$\beta\sim-2.5$ at $z\sim 6$.  The bright-end slope $\alpha$ also
+shows moderate steepening towards high redshifts.  However, the
+constraints on $\alpha$ are weak, particularly at the high redshift
+because of the bright break luminosity.
+
+An important finding of this work is that there are severe systematic
+errors in observed luminosity function at certain redshifts.  We find
+that the most significant systematic bias is at redshift $z\sim 3$ in
+the BOSS sample of quasars.  There is also some evidence of a
+systematic bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$
+there is some indication of a systematic error in completeness
+estimates at the faintest magnitudes $M_{1450}\sim -19$.  Systematic
+errors make it harder to construct simple empirical models to describe
+the luminosity function evolution.  We develop three such models in
+this paper.  We find that a fourteen-parameter model (Model 1)
+describes the redshift evolution of the luminosity function rather
+well.  However, this model prefers a very rapid evolution in the
+faint-end slope at $z=3.5$, which is probably unphysical.  Our other
+models (Models 2 and 3) do not have this feature, but these models do
+not fit the data as well as Model 1 at $z=4$--$6$.  The integrated
+quasar number density diverges at high redshifts in all three models.
+
+In spite of the rapid steepening of the faint end of the luminosity
+function at high redshifts, our derived hydrogen-ionizing emissivity
+from AGN is lower that recent determinations from the literature
+\citep{2015AA...578A..83G}.  This is because the bright break
+luminosities reduce the contribution of intermediate-brightness AGN to
+the LyC emissivity .  We find that the LyC emissivity peaks at $z\sim
+2$.  We derive the average hydrogen photoionization rate by filtering
+the hydrogen-ionizing emissivity through the intergalactic \HI\ column
+density distribution.  We find that the HI photoionization rate is
+lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
+Our hydrogen photoionization rate estimates are also considerably
+lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
+This indicates that hydrogen reionization is unlikely to have caused
+by AGN alone.  Extrapolating the \HI\ column density distribution
+function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
+are assumed to supply hydrogen-ionizing photons with a unit escape
+fraction, the resultant photoionization rate is only about 10\% of
+what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
+we find that the hydrogen photoionization rate is about a factor of
+two higher than the estimate of \citet{2007ApJ...654..731H} and
+\citet{2012ApJ...746..125H}.  When compared with the recent analysis
+of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
+alleviate the photon underproduction crisis
+\citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
+at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
+integrated down to $M_{1450}=-21$ and $-18$, respectively.
+
+These results will be made more robust with new data from deep
+large-area surveys to discover faint quasars at high redshifts, such
+as the Subaru High-z Exploration of Low-Luminosity Quasars (SHELLQs)
+project \citep{2016ApJ...828...26M} and the VISTA Extragalactic
+Infrared Legacy Survey (VEILS; \citealt{2017MNRAS.464.1693H}),
+followed by the Wide Field Infrared Survey Telescope (WFIRST;
+\citealt{2013arXiv1305.5422S}) and Euclid \citep{2011arXiv1110.3193L}.
+This study highlights the need for a better understanding of
+luminosity function systematics.  In particular, at $z>4$, it seems
+important to include extended objects at faint magnitudes that could
+be impacted by host galaxy light, take follow-up spectroscopy to
+confirm a fraction of these as high-redshift broad-line AGN, and
+carefully assess host galaxy contamination.
 

### 2018-04-16 kcorr.py
Plot K corrections for the paper

@@ -1,0 +1,68 @@
+import numpy as np
+import matplotlib as mpl
+mpl.use('Agg') 
+mpl.rcParams['text.usetex'] = True 
+mpl.rcParams['font.family'] = 'serif'
+mpl.rcParams['font.serif'] = 'cm'
+mpl.rcParams['font.size'] = '22'
+import matplotlib.pyplot as plt
+import sys
+
+fig = plt.figure(figsize=(7, 7/1.68), dpi=100)
+ax = fig.add_subplot(1, 1, 1)
+ax.set_ylabel(r'$K_{m,1450}$')
+ax.set_xlabel('$z$')
+
+plt.minorticks_on()
+ax.tick_params('both', which='major', length=7, width=1)
+ax.tick_params('both', which='minor', length=3, width=1)
+ax.tick_params('x', which='major', pad=6)
+
+z, k = np.loadtxt('Data_new/kcorrg_l15.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='b', lw=2) 
+
+z, k = np.loadtxt('Data_new/kcorrg_t02.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='b', lw=2, dashes=[7,2]) 
+
+z, k = np.loadtxt('Data_new/kcorrg_v01.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='b', lw=2, dashes=[2,2])
+
+plt.text(0.35, -0.75, '$m=g$', fontsize=12)
+
+#-----
+
+z, k = np.loadtxt('Data_new/kcorri_l15.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='r', lw=2) 
+
+z, k = np.loadtxt('Data_new/kcorri_t02.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='r', lw=2, dashes=[7,2]) 
+
+z, k = np.loadtxt('Data_new/kcorri_v01.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='r', lw=2, dashes=[2,2])
+
+plt.text(2.0, -1.8, '$m=i$', fontsize=12)
+
+#-----
+
+z, k = np.loadtxt('Data_new/kcorrz_l15.dat', usecols=(1,2), unpack=True)
+plt.plot(z, k, c='k', lw=2, label='Lusso et al.\ 2005') 
+
[…]

### 2018-04-16 drawlf.py
Plot more composites

@@ -71,18 +71,18 @@ def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
 
     up = np.percentile(phi, 15.87, axis=0)
     down = np.percentile(phi, 84.13, axis=0)
-    ax.fill_between(mags, down, y2=up, color='grey')
+    f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
 
-    return
+    return f
 
 def plot_bestfit_lf(lf, ax, mags, **kwargs):
 
     bf = np.median(lf.samples, axis=0)
     phi_fit = lf.log10phi(bf, mags)
     # ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'], label=kwargs['label'])
-    ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
+    bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
 
-    return
+    return bf 
 
 def binVol(self, selmap, mrange, zrange):
 
@@ -366,7 +366,7 @@ def plot_giallongo_z4p25(lf, ax, mags):
     return 
 
 
-def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=True):
+def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=True, c2=None, c3=None):
 
     """
 
@@ -378,12 +378,12 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
 
     if show_individual_fit: 
         mag_plot = np.linspace(-32.0, -16.0, num=200) 
-        plot_posterior_sample_lfs(lf, ax, (-32.0, -16.0), lw=1,
+        indf = plot_posterior_sample_lfs(lf, ax, (-32.0, -16.0), lw=1,
                                        c='#ffbf00', alpha=0.1, zorder=2) 
         # plot_bestfit_lf(lf, ax, mag_plot, lw=2,
         #                      c='#ffbf00', zorder=3, label='This work')
 
-        plot_bestfit_lf(lf, ax, mag_plot, lw=2,
+        indbf = plot_bestfit_lf(lf, ax, mag_plot, lw=2,
                              c='#ffbf00', zorder=3)
         
         # if z_plot < 4.5:
[…]

### 2018-04-16 summary_fromFile.py
Update style

@@ -47,12 +47,12 @@ def plot_model(composite, param_number, ax):
     up = np.percentile(beta, 15.87, axis=0)
     down = np.percentile(beta, 84.13, axis=0)
     
-    ax.fill_between(z, down, y2=up, color='turquoise', zorder=1, label='Model 2')
+    mf = ax.fill_between(z, down, y2=up, color='forestgreen', zorder=1, alpha=0.7)
 
     beta = np.median(beta, axis=0)
-    ax.plot(z, beta, color='turquoise', zorder=2, lw=1)
+    m, = ax.plot(z, beta, color='forestgreen', zorder=2, lw=1)
     
-    return
+    return mf, m
 
 def plot_model_polyb(composite, param_number, ax):
 
@@ -69,16 +69,14 @@ def plot_model_polyb(composite, param_number, ax):
     up = np.percentile(beta, 15.87, axis=0)
     down = np.percentile(beta, 84.13, axis=0)
     
-    ax.fill_between(z, down, y2=up, color='peru', zorder=1, label='Model 3')
+    mf = ax.fill_between(z, down, y2=up, color='peru', zorder=1, alpha=0.7)
 
     beta = np.median(beta, axis=0)
-    ax.plot(z, beta, color='peru', zorder=2, lw=1)
+    m, = ax.plot(z, beta, color='brown', zorder=2, lw=1)
     
-    return
-
+    return mf, m 
 
 def getParam(individuals, param, which='old', dtype='good'):
-
 
     if individuals is not None: 
     
@@ -152,10 +150,10 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False, 
                 
             up = np.percentile(phi, 15.87, axis=0)
             down = np.percentile(phi, 84.13, axis=0)
-            ax.fill_between(z, down, y2=up, color='grey', zorder=1)
+            ax.fill_between(z, down, y2=up, color='grey', zorder=5, alpha=0.7)
             
         phi = np.median(phi, axis=0)
-        ax.plot(z, phi, color='k', zorder=2, lw=1)
+        ax.plot(z, phi, color='k', zorder=5, lw=1)
 
     plot_model(lfg_break, 0, ax)
     plot_model_polyb(lfg_polyb, 0, ax)
@@ -262,10 +260,10 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False, lf
                 
             up = np.percentile(M, 15.87, axis=0)
[…]

### 2018-04-16 mosaic_selected.py
Plot of selected panels with composites

@@ -1,0 +1,160 @@
+import numpy as np
+import matplotlib as mpl
+mpl.use('Agg') 
+mpl.rcParams['text.usetex'] = True 
+mpl.rcParams['font.family'] = 'serif'
+mpl.rcParams['font.serif'] = 'cm'
+mpl.rcParams['font.size'] = '14'
+import matplotlib.pyplot as plt
+from drawlf import render 
+
+def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
+         nofirstylabel=True, nolastxlabel=True, nofirstxlabel=False, legend=False, c2=None, c3=None):
+
+    """
+
+    Plot data, best fit LF, and posterior LFs.
+
+    """
+
+    z_plot = lf.z.mean()
+    print z_plot
+
+    ind, co1, co2, co3 = render(ax, lf, composite=composite, c2=c2, c3=c3)
+
+    ax.set_xlim(-18.0, -30.0)
+    ax.set_ylim(-12.0, -4.0)
+
+    print ax.get_ylim()
+
+    ax.set_xticks(np.arange(-30, -16, 4))
+    ax.set_yticks(np.arange(-12, -3, 2))
+
+    plt.minorticks_on()
+    ax.tick_params('both', which='major', length=3, width=1)
+    ax.tick_params('both', which='minor', length=1.5, width=1)
+    
+    if not yticklabels:
+        ax.set_yticklabels('')
+
+    if not xticklabels:
+        ax.set_xticklabels('')
+
+    if nofirstylabel:
+        ax.get_yticklabels()[0].set_visible(False)
+
+    if nolastxlabel:
+        ax.get_xticklabels()[0].set_visible(False)
+
+    if nofirstxlabel:
+        ax.get_xticklabels()[-1].set_visible(False)
+
+    label = r'${:g}\leq z<{:g}$'.format(lf.zlims[0], lf.zlims[1])
+    plt.text(0.03, 0.05, label, horizontalalignment='left',
+             verticalalignment='center', transform=ax.transAxes, fontsize='10')
+
+    num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450_all.size)
+    plt.text(0.03, 0.12, num, horizontalalignment='left',
+             verticalalignment='center', transform=ax.transAxes, fontsize='10')
+
+    return ind, co1, co2, co3
+    
[…]

### 2018-04-17 Paper/paper.tex
Update text

@@
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[fleqn,usenatbib]{mnras}
 \usepackage[T1]{fontenc}
@@
 \usepackage{dcolumn}
-\newcolumntype{.}{D{.}{.}{2.6}}
+\newcolumntype{.}{D{.}{.}{2.7}}
+\newcolumntype{e}{D{.}{.}{2.10}}
 \newcolumntype{d}{D{.}{.}{2.3}}
 
-\title[AGN luminosity function]{Evolution of the AGN UV luminosity function from redshift 7.5}
-
-\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
-      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
-    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
-  Institute of Cosmology, University of Cambridge, Madingley Road,
-  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
-  Universit\"at Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
-  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
+\title[AGN luminosity function]{Evolution of the AGN UV
+  luminosity function from redshift 7.5}
+
+\author[Kulkarni et al.]
+       {{Girish Kulkarni$^{1}$\thanks{Email: kulkarni@ast.cam.ac.uk},
+           G\'abor Worseck$^{2}$
+           and Joseph F.~Hennawi$^{3}$} \\
+         $^1$Institute of Astronomy and Kavli Institute of Cosmology,
+         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
+         UK \\
+         $^2$Institute f\"ur Physik und Astronomie, Universit\"at
+         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
+         Germany \\
+         $^3$Department of Physics, Broida Hall, UC Santa Barbara,
          Santa Barbara, CA 93106-9530 USA}
@@
 \begin{abstract}
-We present the evolution UV/optical luminosity function of quasars
-from a homogeneous reanalysis of more than 85,000 spectroscopically
-selected quasars from redshift $z=0$ to $7.5$.  We derived luminosity
-functions when the observed quasar population is binned in luminosity
-and redshift, and then construct a continuous evolutionary model of
-the luminosity function spanning a range of redshifts.  We find that
-quasars selected from the BOSS survey at $z=2$--$3$ show a significant
-systematic offset from the general trends, possiblity due to the
-colour bias suffered by BOSS.  Some systematic errors also persist in
-the lowest-redshift quasar sample due to host galaxy effects. However,
-we find that it is possible to describe the luminosity function
-evolution from redshift $z=0$ to $7.5$ using a simple 14-parameter
-evolving double power law model.  The evolution of the number density
-of qsos shows the familiar downsizing effect, although the evolution
-in the faint quasar population is quite flat at high redshifts such
-that the the drop in their number density at high redshifts is much
-slower than that for bright quasars.  When integrated down to
-$M_{1450}=-20$ quasars can produce all of the hydrogen-ionizing
-photons in the intergalactic medium upto redshifts 3.5.  They fall
-short of the emissivity required to explain the Ly$\alpha$ data at
-higher redshifts, and are therefore unlikely to have singlehandedly
-driven hydrogen reionization.  This conclusion can be altered,
-however, if lower luminosity qsos (down to $M_{1450}=-18$) are assumed
-to exist and to have a unity escape fraction, in which case qsos can
-potentially produce all the hydrogen-ionizing flux at $z<7.5$.
-He~\textsc{ii} reionization in this model occurs between $z=3.2$ and
-$3.7$.
+  Determinations of the UV luminosity function of AGN at high
+  redshifts are important for constraining the contribution of AGN to
+  reionization.  Many recent inferences of the luminosity function
+  suffer from inconsistencies arising from inhomogeneous selection and
+  mixing of AGN data.  We address this problem in this paper by
+  constructing a sample of more than 85,000 colour-selected AGN from
+  redshift $z=0$ to $7.5$.  This sample is constructed out of multiple
+  data sets with spectroscopic redshifts and completeness estimates.
+  We homogenise these data sets to identical cosmologies, intrinsic
+  AGN spectra, and magnitude systems.  Using this sample, we derive
+  the AGN UV luminosity function from redshifts $z=0$ to $7.5$.  The
+  luminosity function has a double power law form at $z<5.5$, and
+  single power law form at higher redshifts.  The break luminosity
+  brightens rapidly with redshift and the faint end of the luminosity
+  function steepens.  In spite of this steepening, the contribution of
+  AGN to the hydrogen photoionization rate at $z=5$--$6$ is
+  subdominant, although it can be non-negligible if these luminosity
+  functions hold down to $M_{1450}=-18$.  Under reasonable
+  assumptions, AGN can reionize \HeII\ by redshift $z=3.2$.  At low
+  redshifts ($z<0.5$), AGN can produce all of the hydrogen
+  photoionization rate implied by the \lya data.  Our global analysis
+  of the luminosity function also reveals important systematic errors
+  in the data, particularly at $z<0.6$ and $z=2.2$--$3.5$, which need
+  to be addressed in future in order to improve our results.  We make
+  various fitting functions, luminosity function analysis codes, and
+  homogenised AGN data publicly available.
 \end{abstract}
@@
 \end{keywords}
-
-%% * Possible outline of paper:
-%% 
-%% Introduction 
-%% Data
-%% Method
-%%   Individual fits
-%%   Global fits
-%% Contribution to reionizatin 
-%% Conclusions
-%% 
-%% * Optional possibilities:
-%%
-%% Low-z photon under-production
-%% Bolometric LF
-%% Public code description 
-%% More global models: PLE, PDE, Trenti, White-Conroy
-%% Goodness of fit 
-%% BH growth 
-%% Comparison with galaxy LF
-%% Comparison with previous work
 
@@
 formation.  Finally, thanks to their relative brightness and high
-Lyman continuum escape fraction, the luminosity function of AGN
+Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
 determines their influence on the temperature and ionization state of
@@
 
-The claimed discovery of 19 low-luminosity ($M_{1450}>-22.6$) AGN
-between redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G}
-using a novel X-ray/NIR selection criterion, has renewed the interest
-in the evolution of the UV luminosity function of AGN.  This finding
-suggested that the faint end of the quasar UV luminosity function is
-steeper at these redshifts than previously thought
-\citep{2007ApJ...654..731H, 2012ApJ...746..125H}.  Using far-UV
-spectral slopes from composite spectra of low-redshift quasars, and
-assuming a Lyman continuum escape fraction of 100\%,
-\citet{2015AA...578A..83G} argued that AGN brighter than
+There is a renewed interest in understanding the evolution of the UV
+luminosity function of AGN, triggered by the 19 low-luminosity
+($M_{1450}>-22.6$) AGN candidates between redshifts $z=4.1$ and $6.3$
+discovered by \citet{2015AA...578A..83G} using a novel X-ray/NIR
+selection criterion.  This finding suggested that AGN brighter than
 $M_{1450}=-18$ can potentially produce all of the metagalactic
 hydrogen photoionization rate inferred from the \lya forest at
-$4<z<6$.  Additional indications of a significant presence of AGN at
-high redshift ($z\sim 6$) have emerged.  First,
-\citet{2015MNRAS.447.3402B} reported a large scatter in the \lya
-opacity between different sightlines close to redshift
-$z=6$. \cite{2015MNRAS.453.2943C} showed that these opacity
+$4<z<6$.  A significant presence of AGN at high redshift ($z\sim 6$)
+and a dominant contribution of AGN to reionization is appealing as the
+LyC escape fraction of galaxies is uncertain.  High-redshift galaxies
+down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
+10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and redshifts up to
+$z=11.1$ \citep{2016ApJ...819..129O} have now been reported.  But the
+escape of LyC photons has been measured in only a few comparatively
+bright ($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).
+The escape fraction in these galaxies is inferred to be typically
+about 2--20\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
+  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
+  2017MNRAS.468..389J, 2017MNRAS.465..316M}, whereas reionization
+requires escape fraction of about 20\% in galaxies as faint as
+$M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F, 2015ApJ...802L..19R,
+  2016MNRAS.457.4051K}.  An enhanced incidence of high-redshift AGN
+may also be consistent with the shallow bright-end slopes of the
+$z\sim 7$ UV luminosity function of galaxies relative to a Schechter
+function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
+  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
+these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
+  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
+explanation for the large scatter in the \lya opacity between
+different quasar sightlines close to redshift $z=6$
+\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
 fluctuations extend to substantially larger scales ($\gtrsim 50\,
-h^{-1}$cMpc) than expected in reionization histories dominated by
-low-luminosity galaxies (see also \citealt{2016MNRAS.460.1328D}).
-\citet{2017MNRAS.465.3429C} further demonstrated that opacity
-fluctuations on such large scales arise naturally if there is a
-significant contribution ($\gtrsim 50\%$) of AGN to the ionising
-emissivity at the redshift of the observed opacity fluctuations ($z
-\sim 5.5$--$6$) as would be expected for a QSO luminosity that is
-consistent with the measurements of \citet{2015AA...578A..83G}.
-Second, measurements of the Lyman continuum escape fraction from
-high-redshift galaxies are still elusive.  Although high-redshift
-galaxies as faint as rest-frame UV magnitude $M_\mathrm{UV}=-12.5$
-($L\sim 10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and
-redshifts as high as $z=11.1$ \citep{2016ApJ...819..129O} have now
-been reported, the escape of Lyman continuum photons has been detected
-in only a small number of comparatively bright ($L>0.5L^*$)
-low-redshift ($z < 4$) galaxies.  In these galaxies, the escape
-fraction is typically found to be 2--20\% \citep{2010ApJ...725.1011V,
-  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
-  2016A&A...585A..48G, 2017MNRAS.468..389J, 2017MNRAS.465..316M} but
-reionization would require escape fraction of about 20\% in galaxies
-down to $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
-  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  Finally, incidence of
-high-redshift AGN is also consistent with the shallow bright-end
-slopes of the high-redshift ($z\sim 7$) UV luminosity function of
-galaxies relative to a Schechter-function representation
-\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
-  2015MNRAS.452.1817B} and the hard spectra of these bright galaxies
-\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
-
-However, these arguements in favour of a higher incidence of
-UV-emitting AGN at high redshit, have been contested by several
-observations.  \citet{2016arXiv160706467D} considered the effect of
-AGN-dominated reionization on the Ly$\alpha$ opacity at $z>5$,
-He~\textsc{ii} Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the
-thermal history of the IGM.  In agreement with
-\citet{2015MNRAS.453.2943C}, these authors found that AGN did provide
-a plausible explanation for the large fluctuations in the Ly$\alpha$
-opacity at $z>5$.  However, they found that reionization of
-He~\textsc{ii} occurs much earlier in these AGN-dominated models (see
-also \citealt{2016arXiv160602719M}).  For instance, in the model of
+h^{-1}$cMpc) than expected in galaxies-dominated reionization models
+\citep{2015MNRAS.453.2943C}.  AGN clustering can result in these
+fluctuations naturally if there is a significant contribution
+($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
+\citep{2017MNRAS.465.3429C}.
+
+Several counter-arguements against a higher incidence of AGN at high
+redshift have also been made. \citet{2017MNRAS.468.4691D} and
+\citet{2018MNRAS.473.1416M} pointed out that an AGN population
+consistent with the findings of \citet{2015AA...578A..83G} leads to a
+much earlier \HeII\ reionization.  For instance, in the model of
 \citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
 at $z=4.5$, compared to $z=3$ in the standard scenario
-\citep{2012ApJ...746..125H}.  This early Helium reionization could
+\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization could
 result in higher IGM temperatures due to the associated photoheating.
-The temperature of the IGM at mean density is enhanced in
-AGN-dominated models by factors of $\sim 2$ relative to the standard
-models for $z=3.5$--$5$, in conflict with measurements.  This
-inconsistency could be avoided by reducing the escape fraction of 4~Ry
-photons in AGN, but it is not clear if this can be achieved while
-requiring a 100\% escape fraction of 1~Ry photons in order to explain
-the Ly$\alpha$ opacity fluctuations.  Further evidence against
-AGN-dominated reionization models has emerged from metal-line
-absorbers at $z\sim 6$.  In their cosmological radiation
-hydrodynamical simulations, \citet{2016MNRAS.459.2299F} find that the
-hard spectral slopes of UV backgrounds in AGN-only reionization models
-produce too many C~\textsc{iv} absorption systems relative to
-Si~\textsc{iv} and C~\textsc{ii} at $z\sim 6$.  However, these
-simulations assume an $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
-\citep{2001AJ....122..549V, 2002ApJ...579..500T, 2012ApJ...746..125H}.
-This slope is marginally harder than recent measurements
-($L_\nu\propto\nu^{-1.7}$) from a stack of $z\sim 2.4$ quasars
-\citep{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also find
+\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
+mean density is twice as much in AGN-dominated reionization models as
+the standard models at $z=3.5$--$5$, in conflict with constraints from
+the \lya forest.  This inconsistency could be avoided by postulating a
+reduced escape fraction of \HeII-ionizing photons in AGN, but it is
+difficult to reconcile this with a unit escape fraction of
+hydrogen-ionizing photons that is required to explain the Ly$\alpha$
+opacity fluctuations.  Further arguments against AGN-dominated
+reionization have been presented by \citet{2016MNRAS.459.2299F} by
+analysing the incidence of metal-line absorbers at $z\sim 6$.
+\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
+hydrodynamical simulations AGN-dominated UV background results in too
+many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
+C~\textsc{ii} at $z\sim 6$.  However, these simulations assume a
+$L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
+\citep{2002ApJ...579..500T}, which somewhat harder than recent
+measurements ($L_\nu\propto\nu^{-1.7}$) by
+\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also found
 that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
-measurements prefer a somewhat harder and more intense $>4$~Ry
-background than the standard model of \citet{2012ApJ...746..125H}.
-Using a large sample of X-ray-selected quasars in the redshift range
-$z=0$--$6$, \citet{2017MNRAS.465.1915R} find that the faint end of the
-AGN UV luminosity function at $z\sim 6$ is likely to be much shallower
-that that reported by \citet{2015AA...578A..83G}.  In their analysis,
-\citet{2017MNRAS.465.1915R} use an AGN obscuration optical depth
-($\log N_\mathrm{H}$) cut-off that reproduces low-redshift AGN UV
-luminosity functions and an X-ray-to-optical/UV luminosity ratio
-calibrated at redshifts $z=0.05$--$4$ \citep{2010A&A...512A..34L}.
-These authors argue that the apparent contradiction with the results
-of \citet{2015AA...578A..83G} could be explained by contamination
-from the AGN host galaxies.  It has also been recently argued that the
-Lyman continuum escape fraction of AGN might not be 100\% as is
-usually assumed \citep{2017MNRAS.465..302M}.  This may further reduce
-the contribution of AGN to reionization.
+measurements prefer a harder and more intense $>4$~Ry background than
+the standard model \citep{2012ApJ...746..125H}.  Finally, comparing
+the \citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
+$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
+the AGN UV luminosity function at $z\sim 6$ is probably shallower that
+that reported by \citet{2015AA...578A..83G}.
+\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
+the results of \citet{2015AA...578A..83G} could be explained by
+contamination from the AGN host galaxies for faint AGN.
+
+While a straightforward way towards a more robust understanding of AGN
+contribution to reionization is to determine the evolution of the AGN
+UV luminosity function, many recent inferences of the luminosity
+function suffer from inconsistencies arising from inhomogeneous
+selection and mixing of AGN data.  This has resulted in a large
+scatter in the inferred high-redshift hydrogen-ionizing AGN emissivity
+between various recent studies.  For instance, there is an order of
+magnitude scatter between various estimates of the hydrogen-ionizing
+AGN emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
+  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
+  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O,
+  2017MNRAS.466.1160M}.  Our aim in this paper is to address this
+issue, by constructing an AGN sample with robust redshift and
+completeness estimates and homogeneous assumptions of the cosmology
+and intrinsic AGN spectrum.  We discuss our sample construction in
+Section~\ref{sec:sample}.  Our derived luminosity functions are
+presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
+our inference of the AGN contribution to hydrogen and helium
+reionization.  We summarise our findings in Section~\ref{sec:conc}.
 
@@
   \includegraphics[width=\columnwidth]{kcorr.pdf}
-  \caption{Bandpass corrections $K_{m,1450}$ from a broadband magnitude $m=\{g,i,z_\mathrm{AB}\}$
-           to the monochromatic AB magnitude at 1450\,\AA\ as a function of redshift $z$ for the \citet{2015MNRAS.449.4204L}
-           quasar SED used in this work, and for two quasar composite spectra \citep{2001AJ....122..549V, 2002ApJ...565..773T}.
-           The redshift range has been restricted to exclude the Ly$\alpha$ forest and to account for the different
+  \caption{Bandpass corrections $K_{m,1450}$ from a broadband
+    magnitude $m=\{g,i,z_\mathrm{AB}\}$ to the monochromatic AB
+    magnitude at 1450\,\AA\ as a function of redshift $z$ for the
+    \citet{2015MNRAS.449.4204L} quasar SED used in this work, and for
+    two quasar composite spectra \citep{2001AJ....122..549V,
+      2002ApJ...565..773T}.  The redshift range has been restricted to
+    exclude the Ly$\alpha$ forest and to account for the different
     rest frame wavelength coverage of the spectra.}
@@
 \section{Luminosity function}
+\label{sec:lf}
 
@@
         \label{tab:global}
-  \begin{tabular}{lrrr}
+        \begin{tabular}{p{1.0cm}eee}
           \hline 
-    Parameter & Model 1 & Model 2 & Model 3 \\
+          Param. &
+          \multicolumn{1}{c}{Model 1} &
+          \multicolumn{1}{c}{Model 2} &
+          \multicolumn{1}{c}{Model 3} \\
           \hline
-    $c_{0,0}$ & $-7.559^{+0.131}_{-0.139}$ & $-7.084^{+0.136}_{-0.142}$ & $-6.842^{+0.077}_{-0.076}$ \\     
-    $c_{0,1}$ & $1.013^{+0.079}_{-0.072}$ & $0.753^{+0.080}_{-0.073}$ & $0.590^{+0.039}_{-0.041}$ \\        
-    $c_{0,2}$ & $-0.113^{+0.005}_{-0.005}$ & $-0.096^{+0.004}_{-0.005}$ & $-0.083^{+0.003}_{-0.003}$ \\
+          $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
+          $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
+          $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
           \\
-    $c_{1,0}$ & $-17.006^{+0.230}_{-0.243}$ & $-15.423^{+0.263}_{-0.261}$ & $-15.140^{+0.144}_{-0.136}$ \\  
-    $c_{1,1}$ & $-5.548^{+0.156}_{-0.143}$ & $-6.725^{+0.156}_{-0.171}$ & $-6.910^{+0.091}_{-0.093}$ \\     
-    $c_{1,2}$ & $0.588^{+0.016}_{-0.019}$ & $0.737^{+0.018}_{-0.015}$ & $0.750^{+0.012}_{-0.013}$ \\        
-    $c_{1,3}$ & $-0.023^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ \\
+          $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
+          $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
+          $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
+          $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
           \\
-    $c_{2,0}$ & $-3.246^{+0.121}_{-0.123}$ & $-2.973^{+0.117}_{-0.133}$ & $-2.950^{+0.105}_{-0.097}$ \\     
-    $c_{2,1}$ & $-0.250^{+0.048}_{-0.050}$ & $-0.347^{+0.050}_{-0.050}$ & $-0.363^{+0.040}_{-0.043}$ \\
+          $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
+          $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
           \\
-    $c_{3,0}$ & $-2.350^{+0.051}_{-0.060}$ & $-2.545^{+0.123}_{-0.290}$ & $-1.424^{+0.031}_{-0.031}$ \\     
-    $c_{3,1}$ & $0.647^{+0.072}_{-0.060}$ & $1.581^{+0.520}_{-0.264}$ & $-0.111^{+0.010}_{-0.010}$ \\       
-    $c_{3,2}$ & $3.857^{+0.092}_{-0.073}$ & $2.102^{+0.450}_{-0.283}$ & --- \\        
-    $c_{3,3}$ & $27.534^{+41.364}_{-9.405}$ & $1.965^{+0.461}_{-0.464}$ & --- \\      
-    $c_{3,4}$ & $-0.002^{+0.074}_{-0.082}$ & $-0.641^{+0.169}_{-0.154}$ & --- \\      
+          $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
+          $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
+          $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
+          $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
+          $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
           \hline 
@@
       \section{Contribution of AGN to reionization}
+      \label{sec:reion}
 
@@
       \section{Conclusions}
+      \label{sec:conc}
 
@@
       luminosities reduce the contribution of intermediate-brightness AGN to
-the LyC emissivity .  We find that the LyC emissivity peaks at $z\sim
+      the LyC emissivity.  We find that the LyC emissivity peaks at $z\sim
       2$.  We derive the average hydrogen photoionization rate by filtering

### 2018-04-30 Paper/paper.tex
Update

@@
 $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
-\citep{2002ApJ...579..500T}, which somewhat harder than recent
+\citep{2002ApJ...565..773T}, which somewhat harder than recent
 measurements ($L_\nu\propto\nu^{-1.7}$) by
@@
 \begin{table*}
-  % In published version of this table, we could remove file names and add data homogenisation in Notes.
-  % Add z ~ 7 qso when you add it to analysis
-  % See data.tex for a version of this table that includes file names
-  % Should we mark Giallongo, Mortlock, and Banados entries to say that these are sometimes excluded from analysis?
-  % Remove notes?
-  % Do we really need a sample ID column?
-  % Say in caption or text that sample 13 is restricted to $z<4.7$
-  % Also that sample 17 overlaps with 8 for $M_{1450}<-26.73$
-  % Also that in sample 7 we rescaled selection probabilities 
-  \caption{Quasar data sets}
+  \caption{Data sets analysed in this work.  We restrict the SDSS DR7
+    data set \citep{2010AJ....139.2360S} to $z<4.7$.  The
+    \citet{2013ApJ...768..105M} data set is restricted to faint
+    ($M_{1450}>-26.73$) quasars to avoid overlap with the
+    \citet{2016ApJ...829...33Y} sample.  Most AGN in the
+    \citet{2015AA...578A..83G} sample do not have spectroscopic
+    redshifts.  We therefore only use this sample for secondary
+    analysis in Section~\ref{sec:global} and Appendix~\ref{sec:conv}.
+    Similarly, the quasars reported by \citet{2011Natur.474..616M},
+    \citet{2015ApJ...801L..11V}, and \citet{2018Natur.553..473B} have
+    only approximate completeness estimates.  We only use these
+    quasars in our secondary analysis in Section~\ref{sec:global}.}
   \label{tab:samples}
-  \begin{tabular}{crcllrS}
+  \begin{tabular}{ccllrS}
     \hline
-    & ID & $z$ & Survey & Reference & Number & {Area} \\
-    & & & & & of quasars & {(deg$^2$)} \\
+    & $z$ & Survey & Reference & Number & {Area} \\
+    & & & & of quasars & {(deg$^2$)} \\
     \hline
-    1. & 13 & 0.1--2.2 & SDSS DR7 & \citet{2006AJ....131.2766R} & 48664 & 6248.0 \\
-    2. & 15 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
-    3. & 15  & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
-    4. &  1 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
-    5. & 13 & 3.7--4.7 & SDSS DR7 & \citet{2006AJ....131.2766R} & 1785 & 6248.0 \\
-    6. & 17 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
-    7. &  8 & 4.7--5.1 & SDSS DR7 & \citet{2013ApJ...768..105M} & 148 & 6248.0 \\
-    8. &  8 & 4.7--5.1 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 52 & 235.0 \\
-    9. &  8 & 5.1--5.5 & --- DR7 Extended & \citet{2013ApJ...768..105M} & 28 & 6248.0 \\
-    10. & 8 & 5.1--5.4 & ---  Stripe 82 Extended & \citet{2013ApJ...768..105M} & 10 & 235.0 \\
-    11. & 6 & 3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
-    12. & 6 & 3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
-    13. & 7 & 4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
-    14. & 18 & 5.8--6.4 & --- Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
-    15. & 18 & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
-    16. & 18 & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
-    17. & 10 & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
-    18. & 10 & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
-    19. & 11 & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
-    20. & 19 & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
-    21. & 19 & 6.5--7.4 & UKIDSS & \citet{2007MNRAS.376L..76V} & 1 & 3370.0 \\
-    22. & 20 & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
+    1. & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
+    2. & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
+    3. &  0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
+    4. & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
+    5. & 3.7--4.7 & SDSS DR7 & \citet{2010AJ....139.2360S} & 1785 & 6248.0 \\
+    6. & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
+    7. & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
+    8. & 4.7--5.4 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
+    9. &3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
+    10. &3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
+    11. &4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
+    12. & 5.8--6.4 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
+    13. & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
+    14. & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
+    15. & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
+    16. & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
+    17. & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
+    18. & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
+    19. & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
+    20. & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
     \hline
-  \end{tabular}
+  \end{tabular}\\
 \end{table*}
@@
 
-We started with compiling the samples of recent UV-optical quasar
-surveys. The restriction to UV-optical surveys was mainly driven by
-our science goal to characterise the UV luminosity function of Type~I
-quasars, but also by the still uncertain conversion from X-ray flux to
-UV flux, which adds unnecessary systematics for large
-samples. \textbf{References!} The individual surveys and their main
-characteristics are listed in
+We started with compiling the samples of recent rest-frame UV-optical
+quasar surveys. The restriction to UV-optical surveys was mainly
+driven by our science goal to characterise the UV luminosity function
+of Type~1 quasars. X-ray-selected samples are less suited for this
+purpose due to spectroscopic incompleteness and the $\sim 0.4$\,dex
+scatter in the conversion from X-ray to UV luminosity
+\citep{2010A&A...512A..34L, 2015MNRAS.453.1946G, 2016ApJ...819..154L}
+that contributes significantly to the error budget in the UV
+luminosity function of X-ray-selected samples unless rest-frame UV
+photometry is incorporated \citep{2015AA...578A..83G}.  The individual
+surveys and their main characteristics are listed in
 Table~\ref{tab:samples}.  Figure~\ref{fig:qsos} presents a redshift
@@
 \begin{enumerate}
-\item Spectroscopic redshifts for the majority of targets.
+\item Spectroscopic redshifts for the vast majority of targets.
 \item Accurate rest-frame UV-optical CCD photometry.
-\item Statistical power (sample size, coverage in $z$ and/or $M_{1450}$).
+\item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
 \item A characterised selection function.
@@
 publish them here in modified and homogenised form
-(Section~\ref{sect:datahom}). \textbf{Maybe get the authors' consent.}
+(Section~\ref{sect:datahom}).
 
@@
 considered quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and the 2SLAQ catalogue
-\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to XXX
-$z<2.2$ quasars selected with the final SDSS quasar selection
-algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R} from a
-survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We adopted
-the SDSS targeting photometry corrected for Galactic extinction
-\citep{2010AJ....139.2360S}. To limit systematic uncertainties in the
-correction for host galaxy light \citep{2009MNRAS.392...19C} we
-restricted the 2SLAQ sample to XXX $g<21.85$ $0.4<z<2.2$ quasars from
-its spectroscopic survey footprint near the North Galactic Pole (NGP,
-XX quasars in $127.7$\,deg$^2$) and the South Galactic Pole (SGP, XX
-quasars in $64.2$\,deg$^2$). The small sample overlap between SDSS and
-2SLAQ (112 quasars) has negligible impact on the QLF evaluation.
+\citep{2010AJ....139.2360S} and the 2SLAQ survey catalogue
+\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to the
+48,664 $0.1<z<2.2$ quasars selected with the final SDSS quasar
+selection algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R}
+from a survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We
+adopted the SDSS targeting photometry corrected for Galactic
+extinction \citep{2010AJ....139.2360S}. To limit systematic
+uncertainties in the correction for host galaxy light
+\citep{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 11,816
+$g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint
+near the North Galactic Pole (NGP, 8153 quasars in $127.7$\,deg$^2$)
+and the South Galactic Pole (SGP, 3663 quasars in
+$64.2$\,deg$^2$). The small sample overlap between SDSS and 2SLAQ (112
+quasars) has negligible impact on the QLF evaluation.
 
@@
 
-At $3.7<z<4.1$ we used a combination of SDSS DR7 \citep[XX uniformly
+At $3.7<z<4.7$ we used a combination of SDSS DR7 \citep[1785 uniformly
   selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
 survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
-$z>3.7$ limits the impact of systematic uncertainties in the
-\citet{2006AJ....131.2766R} SDSS selection function
+$z>3.7$ in SDSS limits the impact of systematic uncertainties in the
+\citet{2006AJ....131.2766R} selection function
 \citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
@@
 and \citet{2012ApJ...755..169M}, which justifies our preference for
-the former sample.
-
-Between $z=4.1$ and $z=4.7$ our combined sample has XX uniformly
-selected quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and XX quasars from
-\citet{2011ApJ...728L..26G}. Although we do not include the highly
-debated \citet{2015AA...578A..83G} sample in our main analysis due to
-its rough selection function and lacking spectroscopy for 17 of the 22
-quasar candidates, we use it in Section~XX to constrain the faint end
-($M_{1450}>-23$) of the QLF at $z>4.1$. We restricted the
-\citet{2015AA...578A..83G} sample to the 19/22 sources considered in
-their QLF.
-
-At $4.7\le z<5.1$ we combined several recent surveys, accounting for
+the former sample that is 77 per cent spectroscopically complete at
+$R$ magnitudes $<23.5$ \citep{2011ApJ...728L..26G}.
+
+At $4.7\le z<5.5$ we combined several recent surveys, accounting for
 sample overlap and updated selection functions. At the bright end of
-the QLF we used the 71 $z<5.1$ quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} together with its selection function.
-%Although \citet{yang} are sensitive to $z>5.1$ quasars, we limit
-%their sample to $z<5.1$ to limit differential evolution of the QLF
-%across the redshift range.
-To avoid double-counting quasars contained both in
-\citet{2016ApJ...829...33Y} and the SDSS DR7 sample from
-\citet{2013ApJ...768..105M}, we used the latter only at
-$M_{1450}>-26.72$ (in our adopted cosmology), yielding 94 additional
-$4.7\le z<5.1$ quasars selected in 6248\,deg$^2$. We used the updated
-$z\sim 5$ SDSS DR7 selection function \citep{2013ApJ...768..105M}
-instead of the one from \citet{2006AJ....131.2766R}.
-%\footnote{We note that the major difference in the selection
-%functions must be due to different input parameters, since the single
-%color selection criterion in \citet{mcgreer} selects the vast
-%majority of the SDSS DR7 quasars.}.
-To these two bright-end samples we added the faint-end sample from the
-\citet{2013ApJ...768..105M} SDSS Stripe~82 survey (52 uniformly
-selected $4.7\le z<5.1$ quasars in 235\,deg$^2$) and two quasars from
-\citet{2011ApJ...728L..26G}, adopting the respective selection
-functions. We did not consider the limit on the $z\sim 5$ QLF by
-\citet{2012ApJ...756..160I} due to systematic errors in their
-selection function\footnote{\citet{2012ApJ...756..160I} underestimated
-  the dispersion in rest-frame UV quasar colours with respect to SDSS
-  at all redshifts (their Figure~4). Contrary to their claim,
-  photometric errors have a small effect on the colour distribution of
-  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
-  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
-  a relative calibration error of $\sim 1$ per cent
+the QLF we used the 99 quasars from the SDSS+WISE survey
+\citep{2016ApJ...829...33Y} that have $M_{1450}<-26.73$ in our adopted
+cosmology.  For these 99 quasars selected from 14,555\,deg$^2$ we
+adopted the \citet{2016ApJ...829...33Y} selection function.  The
+\citet{2016ApJ...829...33Y} sample partially overlaps with the SDSS
+DR7 sample from \citet{2013ApJ...768..105M}, so to avoid
+double-counting quasars we used the latter sample only at $M_{1450}\ge
+-26.73$, yielding 104 additional $4.7\le z<5.5$ quasars selected in
+6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection function from
+\citet{2013ApJ...768..105M} that supersedes the one from
+\citet{2006AJ....131.2766R} due to improved $K$ corrections and IGM
+parameterization.  To these two bright-end samples we added the
+faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82
+survey (62 uniformly selected $4.7\le z<5.5$ quasars in 235\,deg$^2$)
+and two $4.7\le z<5.5$ quasars from \citet{2011ApJ...728L..26G},
+adopting the respective selection functions.  We did not consider the
+limit on the $z\sim 5$ QLF by \citet{2012ApJ...756..160I} due to
+systematic errors in their selection
+function\footnote{\citet{2012ApJ...756..160I} underestimated the
+  dispersion in rest-frame UV quasar colours with respect to SDSS at
+  all redshifts (their Figure~4). Contrary to their claim, photometric
+  errors have a small effect on the colour distribution of SDSS
+  quasars given the statistical errors of $<0.03$\,mag in $gri$ for 90
+  per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and a
+  relative calibration error of $\sim 1$ per cent
   \citep{2008ApJ...674.1217P}.}.
 
-The SDSS colours of $5.1\le z<5.5$ quasars are similar to those of M
-and L dwarf stars, resulting in a low and uncertain selection
-efficiency \citep{2013ApJ...768..105M}. WISE mid-infrared selection
-performs better \citep{2016ApJ...829...33Y}, but is restricted to the
-bright end of the quasar population. Our combined sample contains the
-remaining 28 quasars from \citet{2016ApJ...829...33Y} and 10 quasars
-from the \citet{2013ApJ...768..105M} Stripe~82 survey. As we will show
-in Section~XX, the resulting QLF is consistent with those at lower and
-higher redshifts, indicating that the \citet{2013ApJ...768..105M}
-selection functions are quite reliable. \textbf{Check this!}
-
-Finally, we combined the samples from all spectroscopic $z\sim 6$
-quasar surveys with a determined selection function as of June
-2017. \citet{2016ApJ...833..222J} recently compiled all quasars
-discovered in several SDSS $z\sim 6$ surveys together with
-consistently derived selection functions. Their uniform sample
-consists of 24 quasars from the SDSS main survey (11240\,deg$^2$), 10
-additional quasars in regions with two or more SDSS imaging scans
-(so-called overlap regions, 4223\,deg$^2$), and 13 faint quasars from
-SDSS Stripe~82 (277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W}
-provided a uniform sample of 16 quasars in the Very Wide Survey
-(494\,deg$^2$) and a single quasar in the Deep Survey
-($4.47$\,deg$^2$). The one quasar detected in both SDSS and CFHQS does
-not lead to underestimated statistical errors in the QLF. Lastly, we
-included the two objects from \citet{2015ApJ...798...28K}. One might
-be a Lyman break galaxy due to its narrow Ly$\alpha$ emission line
-(half width at half maximum 427\,km\,s$^{-1}$), but
-\citet{2015ApJ...798...28K} note that 10/17 candidates do not have
-follow-up spectroscopy, hence their QLF may be underestimated. Since
-very small samples preclude a statistical correction via the selection
-function, complete spectroscopic follow-up of $z\sim 6$ candidates is
-essential. Although we will account for the slightly different
-redshift sensitivities for the different surveys, we will quote a
-nominal redshift range $5.7<z<6.5$ for the combined $z\sim 6$ sample.
+The SDSS colours of $5.1<z<5.5$ quasars are similar to those of M and
+L dwarf stars, resulting in a low and uncertain selection efficiency
+\citep{2013ApJ...768..105M}. WISE mid-infrared selection performs
+better \citep{2016ApJ...829...33Y}, but is restricted to the bright
+end of the quasar population. Unlike \citet{2013ApJ...768..105M} we
+include the 9 uniformly selected $M_{1450}\ge -26.73$ SDSS DR7 quasars
+and the 10 SDSS Stripe~82 quasars at $z>5.1$, adopting their low
+selection efficiency.  As we will show in Section~3.2, the resulting
+QLF is consistent with those at lower and higher redshifts, indicating
+that the \citet{2013ApJ...768..105M} selection functions are quite
+reliable.
+
+At $z\sim 6$ we combined the samples from all spectroscopic surveys
+with a determined selection function as of June 2017.
+\citet{2016ApJ...833..222J} recently compiled all quasars discovered
+in several SDSS $z\sim 6$ surveys together with consistently derived
+selection functions. Their uniform sample consists of 24 quasars from
+the SDSS main survey (11,240\,deg$^2$), 10 additional quasars in
+regions with two or more SDSS imaging scans (so-called overlap
+regions, 4223\,deg$^2$), and 13 faint quasars from SDSS Stripe~82
+(277\,deg$^2$). The CFHQS \citep{2010AJ....139..906W} provided a
+uniform sample of 16 quasars in the Very Wide Survey (494\,deg$^2$)
+and a single quasar in the Deep Survey ($4.47$\,deg$^2$). The one
+quasar detected in both SDSS and CFHQS does not lead to underestimated
+statistical errors in the QLF. Lastly, we included the two objects
+from \citet{2015ApJ...798...28K}, one of which might be a galaxy due
+to its narrow Ly$\alpha$ emission line (half width at half maximum
+427\,km\,s$^{-1}$). With better photometry and additional spectroscopy
+recently reported by \citet{2017ApJ...847L..15O} the
+\citet{2015ApJ...798...28K} sample is complete.  Although we will
+account for the slightly different redshift sensitivities for the
+different surveys, we will quote a nominal redshift range $5.7<z<6.5$
+for the combined $z\sim 6$ sample.
+
+At the highest redshifts $z>6.5$ we considered two quasars found by
+\citet{2011Natur.474..616M} and \citet{2015ApJ...801L..11V} in UKIDSS
+imaging (3370\,deg$^2$), in addition to the current highest-redshift
+quasar at $z=7.54$ selected from a combination of UKIDSS, WISE and
+DECaLS \citep[$\sim 2500$\,deg$^2$, ][]{2018Natur.553..473B}. Although
+currently only rough estimates exist concerning their selection
+functions, these quasars provide constraints on the evolution of the
+integrated quasar space density from $z\sim 6$ to $z\sim 7$.  We use
+them in our secondary analysis in Section~\ref{sec:global}.  Although
+we do not include the highly debated \citet{2015AA...578A..83G} sample
+in our main analysis due to its rough selection function and lacking
+spectroscopy for 17 of the 22 quasar candidates, we use it in
+Section~\ref{sec:global} to constrain the faint end ($M_{1450}>-23$)
+of the QLF at $z>4.1$. We restricted the \citet{2015AA...578A..83G}
+sample to the 19/22 sources considered in their QLF.
 
@@
 \begin{equation}\label{eq:absmag}
-  M_{1450}\left(z\right) = m-5\log{\left(\frac{d_L\left(z\right)}{\mathrm{Mpc}}\right)}-25-K_{m,1450}\left(z\right),
+  M_{1450}\left(z\right) = m-5\log{\left(\frac{d_L\left(z\right)}
+    {\mathrm{Mpc}}\right)}-25-K_{m,1450}\left(z\right),
 \end{equation}
@@
 surveys reporting $M_{1450}$ obtained by various methods
-\citep{2010AJ....139..906W, 2015ApJ...798...28K, 2015AA...578A..83G,
-  2016ApJ...829...33Y, 2016ApJ...833..222J} we did not re-compute
-$M_{1450}$, but applied appropriate shifts to correct to our adopted
-cosmology.
+\citep{2010AJ....139..906W, 2011Natur.474..616M, 2015ApJ...798...28K,
+  2015ApJ...801L..11V, 2016ApJ...829...33Y, 2016ApJ...833..222J,
+  2018Natur.553..473B} we did not re-compute $M_{1450}$, but applied
+appropriate shifts to correct to our adopted cosmology.
 
@@
 adjusted to our cosmology. Note, however, that many surveys report
-additional sources of incompleteness that preclude a straightforward
-re-evaluation of the QLF.
+additional sources of incompleteness that require modifications to the
+photometric selection functions.
 
@@
 Figures~5 and 7), resulting in
-$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$. Finally,
-we obtained a rough estimate of the \citet{2015AA...578A..83G}
-selection function by comparing the corrected and observed QLFs,
-i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$
-(see their Table~3).
-
-% BOSS:
-% - color selection function in Table 5 of Ross et al.
-(imag, z), sample contains QSOs with spectrocoverage completeness >0.85, mean spectrocoverage completeness 0.962 multiplied onto color selection function
-% - interpolate Beta's K correction (imag->1450A) and compute M1450 for our cosmology (sample and map)
-
-% 2SLAQ:
-% - low-luminosity AGN -> model and subtract host galaxy contribution, magnitudes only for nuclear component, host galaxy contribution <20% at z>0.4 for faintest sources in 2SLAQ (Croom et al.
-2009, MNRAS, 392, 19)
-% - several selection functions (morphological, color, spectroscopic coverage, spectroscopic success)
-% - Table 12: color selection function (available online), gmag is total PSF mag including host galaxy contribution, subtract gmag host galaxy contribution listed in Table 12, selection function extrapolated at bright end (lacking coverage of whole catalog)
-% - coverage completeness for NGP and SGP given in Fig 4 as a function of gmag, interpolated and multiplied into color selection function
-% - spectroscopic success as function of gmag in Fig 6b (only quality=1 redshifts considered), interpolated and multiplied onto color selection function
-% - convert g_agn to M1450 with L15 SED (valid for bright quasars, check with K correction for Telfer/Shull)
-% - sample: correct PSF gmag for Galactic extinction, subtract host galaxy light (Table 12), interpolate Beta's K correction (gmag->1450A) and compute M1450 for our cosmology
-% SDSS:
-% - Richards et al.
-selection function given in (z,imag) Fig 6 and Table 1, corrected for edge effects at magnitude limits (steep gradient) and NaN values, selection function corrected for imaging incompleteness (factor 0.95)
-% - imag in selection function converted to M1450 with L15 SED, conversion uncertain at z>4.7 due to Lya forest
-% - sample: targeting psf imag corrected for Galactic extinction (Schlegel) and converted to M1450 with L15 SED
-% - z<2.2: sample limited to i_dered<19.1, imag of sample and selection function corrected for host galaxy light (Table 12 in Croom et al 2009, given for imag and gmag)
-% Glikman:
-% - different selection functions for 2 sub-surveys, selection functions corrected for interpolation errors (values >1 reset to 1), selection functions given in (z,Rmag) Fig 7 of G10, converted to M1450 with their Rmag K correction (Fig 8 in G10)
-% - spectroscopic incompleteness (f_spec, given in G10 and updated in G11) incorporated into selection functions via linear fit to f_spec(Rmag) at Rmag>23 and constant otherwise
-% - sample M1450 recomputed from Rmag and K correction to be consistent with completeness map, M1450=Rmag-Kcorr-5*log10(d_L/Mpc)-25
-% McGreer:
-% - Stripe 82: selection function (Fig.
-11) modified to include photometric incompleteness (factor 0.95) and spectroscopic incompleteness (imag>20.8, Fig.
-14), M1450 in selection map and sample M1450 converted to our cosmology (adding 0.07)
-% - DR7: sample not listed in paper, M1450 computed from zmag (QSO continuum) and L15 SED, same procedure applied to S82 reveals L15 magnitudes are slightly brighter than M13 magnitudes (median 0.12mag) -> small change,
-%        M13 selection function corrected for photometric (factor 0.95) and spectroscopic (factor 0.95) incompleteness
-% Yang: selection function (Fig.
-5) modified to include image selection incompleteness (factor 0.97) and spectroscopic incompleteness (factor ~0.84 at zmag>19, Fig 7), M1450 in selection map and sample M1450 converted to our cosmology
-% Willott: selection map M1450 adjusted to our cosmology adding 0.05, slightly different cosmological parameters in Willott et al. (2007,2009,2010) -> M1450 converted
-% Jiang: selection functions unchanged, M1450 as given in paper
-% Kashikawa: map not corrected for spectroscopic incompleteness (sample size), M1450 as given in paper
-% Giallongo: selection function estimated from phi_obs and phi_corr (Table 3 of Giallongo et al.), M1450 as given in paper
+$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
+Finally, we obtained a rough estimate of the
+\citet{2015AA...578A..83G} selection function by comparing the
+corrected and observed QLFs, i.e.\ taking
+$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
+Table~3).
 
@@
 absolute magnitudes at rest-frame 1450~{\AA}.
-
 % Put that sentence about magnitudes in the introduction.
@@
 \begin{equation}
-      V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
+  V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM
+  \int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
   \label{eqn:vi}
@@
 \begin{equation}
-      \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}{(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
+  \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}
+       {(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
   \label{eqn:dvdzdo}
@@
 \begin{equation}
-      d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}{\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
+  d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}
+  {\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
   \label{eqn:dl}
 \end{equation}
-    Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat
-    Universe ($\Omega_k=0$).  The luminosity function $\phi$ has units
-    of $\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
+Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat Universe
+($\Omega_k=0$).  The luminosity function $\phi$ has units of
+$\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
 integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
@@
 
-    In each bin, we estimate the uncertainty in the luminosity function
-    by assuming Poisson statistics \citep{1986ApJ...303..336G} for the
-    number of quasars in each bin.  The resultant binned luminosity
-    function estimates are shown by the points in
-    Figure~\ref{fig:mosaic}.
+In each bin, we estimate the uncertainty in the luminosity function by
+assuming Poisson statistics \citep{1986ApJ...303..336G} for the number
+of quasars in each bin.  The resultant binned luminosity function
+estimates are shown by the points in Figure~\ref{fig:mosaic}.
 
 As seen in Figure~\ref{fig:mosaic}, the distribution of luminosity
-    function values in each redshift bin are suggestive of a double
-    power law form.  We will fit such a form below.  However, we also
-    see in several redshift bins of Figure~\ref{fig:mosaic} that the
-    luminosity function seems to show a decline at the faint end.  This
-    is clearly seen, for example, in the 2SLAQ sample at $z<2$ and in
-    the SDSS quasar sample at $z<1.8$ and $z\sim 4$.  We take this to be
-    a systematic error.  The decrease in the luminosity function is an
-    indication of further low-level incompleteness in the quasar surveys
-    that has not been captured by the reported completeness values.  We
-    choose to discard such bins from our analysis.  The discarded
-    luminosity bins are shown in Figure~\ref{fig:mosaic} by open
-    circles.
+function values in each redshift bin are suggestive of a double power
+law form.  We will fit such a form below.  However, we also see in
+several redshift bins of Figure~\ref{fig:mosaic} that the luminosity
+function seems to show a decline at the faint end.  This is clearly
+seen, for example, in the 2SLAQ sample at $z<2$ and in the SDSS quasar
+sample at $z<1.8$ and $z\sim 4$.  We take this to be a systematic
+error.  The decrease in the luminosity function is an indication of
+further low-level incompleteness in the quasar surveys that has not
+been captured by the reported completeness values.  We choose to
+discard such bins from our analysis.  The discarded luminosity bins
+are shown in Figure~\ref{fig:mosaic} by open circles.
 
@@
   \end{center}
-      \caption{Luminosity function estimates in redshift bins from $z=0.1$
-        to $6.5$.  The symbols show our inferred binned luminosity
-        functions from various data sets: sample ID 13 (red), 15 (green),
-        1 (blue), 17 (yellow), 8 (brown), 6 (light blue), 18 (pink), 10
-        (orange), and 11 (grey).  See Table~\ref{tab:samples} for
-        references.  Open circles in corresponding colours indicate
-        excluded incomplete bins for the respective data sets.  In each
-        redshift bin, the black curve shows the best-fit double power law
-        model, which is represented by the median of the posterior
-        probability distribution function.  The grey shaded area shows the
-        one-sigma (68.26\%) uncertainty.  Each panel shows the number of
-        quasars in the respective redshift bin.  The numbers in
-        parentheses indicate the total number of reported quasars in the
-        respective redshift bin, before excluding incomplete bins.  See
-        Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
+  \caption{Luminosity function estimates in redshift bins from
+    $z=0.1$ to $6.5$.  The symbols show our inferred binned
+    luminosity functions from various data sets:
+    \citet[red]{2010AJ....139.2360S},
+    \citet[green]{2009MNRAS.392...19C},
+    \citet[blue]{2013ApJ...773...14R},
+    \citet[yellow]{2016ApJ...829...33Y},
+    \citet[brown]{2013ApJ...768..105M}, \citet[light
+      blue]{2011ApJ...728L..26G},
+    \citet[pink]{2016ApJ...833..222J},
+    \citet[orange]{2010AJ....139..906W}, and
+    \citet[grey]{2015ApJ...798...28K}.  Open circles in
+    corresponding colours indicate excluded incomplete bins for
+    the respective data sets.  In each redshift bin, the black
+    curve shows the best-fit double power law model, which is
+    represented by the median of the posterior probability
+    distribution function.  The grey shaded area shows the
+    one-sigma (68.26\%) uncertainty.  Each panel shows the number
+    of quasars in the respective redshift bin.  The numbers in
+    parentheses indicate the total number of reported quasars in
+    the respective redshift bin, before excluding incomplete bins.
+    See Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
     details.}
@@
   \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
-          Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
-          binned luminosity functions.  In each redshift bin, the yellow
-          curves show the best-fit double power law luminosity function in
-          that redshift bin.  Other curves show the three global evolution
-          models.  Shaded regions show the one-sigma (68.26\%)
-          uncertainties.}
+    Similar to Figure~\ref{fig:mosaic}, the symbols show our
+    inferred binned luminosity functions.  In each redshift bin,
+    yellow curves show the best-fit double power law luminosity
+    function in that redshift bin.  Other curves show the three
+    global evolution models.  Shaded regions show the one-sigma
+    (68.26\%) uncertainties.}
   \label{fig:mosaic_global}
@@
 \end{figure}
-
-      %% \begin{figure*}
-      %%   \begin{center}
-      %%     \includegraphics[scale=0.65]{emissivity.pdf}
-      %%     % gammapi.py -- draw_emissivity() 
-      %%   \end{center}
-      %%   \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
-      %%     fraction down to a limiting magnitude.  Brown points show the
-      %%     emissivity when the best-fit double power law luminosity functions
-      %%     at respective redshifts are integrated down to $M_{1450}=-18$.
-      %%     Black points show the integration limit when the limit is assumed
-      %%     to be $M_{1450}=-21$.  For comparison, various other published
-      %%     models of the 1~Ry emissivity of AGN are also shown.  The blue
-      %%     curve in these panels shows the AGN 912~\AA\ emissivity model of
-      %%     \citet{2012ApJ...746..125H}, which is very similar to the model of
-      %%     \citet{2007ApJ...654..731H}.  Red circles with error bars show the
-      %%     determination from the fits of \citet{2015AA...578A..83G}.  The
-      %%     maroon curve is the published fit to the 1~Ry emissivity evolution
-      %%     in the fits of \citet{2017MNRAS.466.1160M}.  The green curve is
-      %%     the model of \citet{2015ApJ...813L...8M}.  The grey and brown
-      %%     curves show the best-fit form of Equation XX. \gk{Mention MH15 and
-      %%       HM12 Lstar limits.  Mention that Akiyama open and filled circles
-      %%       are very close.}}
-      %%   \label{fig:e912}
-      %% \end{figure*}
 

### 2018-05-03 Paper/paper.tex
Update text
This is from Gabor

@@
 $\left(\Omega_\mathrm{m},\Omega_\Lambda\right)=\left(0.3,0.7\right)$
-and a Hubble constant $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$. Magnitudes
+and a Hubble constant $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$. Comoving
+distances are given explicitly in comoving Mpc (cMpc). Magnitudes
 are reported in the AB system \citep{1983ApJ...266..713O}, and
@@
 \citep{1998ApJ...500..525S} unless otherwise noted.
+Our homogenised sample (Section~\ref{sec:sample}) uses absolute
+monochromatic AB magnitudes at a rest frame wavelength of 1450\,\AA.
 
@@
 \begin{table*}
-  \caption{Data sets analysed in this work.  We restrict the SDSS DR7
-    data set \citep{2010AJ....139.2360S} to $z<4.7$.  The
-    \citet{2013ApJ...768..105M} data set is restricted to faint
-    ($M_{1450}>-26.73$) quasars to avoid overlap with the
-    \citet{2016ApJ...829...33Y} sample.  Most AGN in the
-    \citet{2015AA...578A..83G} sample do not have spectroscopic
-    redshifts.  We therefore only use this sample for secondary
-    analysis in Section~\ref{sec:global} and Appendix~\ref{sec:conv}.
-    Similarly, the quasars reported by \citet{2011Natur.474..616M},
-    \citet{2015ApJ...801L..11V}, and \citet{2018Natur.553..473B} have
-    only approximate completeness estimates.  We only use these
-    quasars in our secondary analysis in Section~\ref{sec:global}.}
+  \caption{Quasar samples analysed in this work.}
   \label{tab:samples}
-  \begin{tabular}{ccllrS}
+  \begin{tabular}{lcllrS}
     \hline
-    & $z$ & Survey & Reference & Number & {Area} \\
+    Sample& $z$ range$^a$& Survey & Reference & Number & {Area} \\
     & & & & of quasars & {(deg$^2$)} \\
     \hline
-    1. & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
-    2. & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
-    3. &  0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
-    4. & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
-    5. & 3.7--4.7 & SDSS DR7 & \citet{2010AJ....139.2360S} & 1785 & 6248.0 \\
-    6. & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
-    7. & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
-    8. & 4.7--5.4 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
-    9. &3.7--4.8 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
-    10. &3.8--5.1 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
-    11. &4.1--6.3 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
-    12. & 5.8--6.4 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
-    13. & 5.9--6.1 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
-    14. & 5.7--6.1 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
-    15. & 6.0 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
-    16. & 5.9--6.4 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
-    17. & 6.0--6.2 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
-    18. & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
-    19. & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
-    20. & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
+    1 & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
+    2 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
+    3 & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
+    4 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
+    5 & 3.7--4.7 & SDSS DR7 & \citet{2010AJ....139.2360S} & 1785 & 6248.0 \\
+    6 & 3.6--5.2 & NDWFS & \citet{2011ApJ...728L..26G} & 12 & 1.71 \\
+    7 & 3.8--5.3 & DLS & \citet{2011ApJ...728L..26G} & 12 & 2.05 \\
+    8 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
+    9$^b$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
+    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
+    11 & 5.7--6.5 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
+    12 & 5.7--6.5 & --- Overlap & \citet{2016ApJ...833..222J} & 10 & 4223.0 \\
+    13 & 5.7--6.5 & --- Stripe 82 & \citet{2016ApJ...833..222J} & 13 & 277.0 \\
+    14 & 5.8--6.6 & CFHQS Deep & \citet{2010AJ....139..906W} & 1 & 4.47 \\
+    15 & 5.8--6.6 & --- Very Wide & \citet{2010AJ....139..906W} & 16 & 494.0 \\
+    16 & 5.8--6.5 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
+    17$^c$ &4.0--6.5 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
+    18$^d$ & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
+    19$^d$ & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
+    20$^d$ & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
     \hline
   \end{tabular}\\
+  \begin{minipage}{14.5cm}
+   \textsuperscript{$c$}{Redshift range of the sample or, for small samples, approximate redshift range in which the survey is sensitive.}\\
+  \textsuperscript{$b$}{Restricted to $M_{1450}>-26.73$ quasars to avoid overlap with the \citet{2016ApJ...829...33Y} sample.}\\
+ \textsuperscript{$c$}{Used only in Section~\ref{sec:global} and Appendix~\ref{sec:conv} due to lack of spectroscopic redshifts for majority of the sample.}\\
+ \textsuperscript{$d$}{Used only in Section~\ref{sec:global} due to roughly estimated selection function.}
+ \end{minipage}
 \end{table*}
@@
 
-We started with compiling the samples of recent rest-frame UV-optical
+We started with compiling the samples of recent photometric rest-frame UV-optical
 quasar surveys. The restriction to UV-optical surveys was mainly
@@
 \citet{2013ApJ...768..105M} that supersedes the one from
-\citet{2006AJ....131.2766R} due to improved $K$ corrections and IGM
+\citet{2006AJ....131.2766R} due to improved bandpass corrections and IGM
 parameterization.  To these two bright-end samples we added the
@@
 \end{equation}
-with the luminosity distance $d_L\left(z\right)$ to a quasar at
-redshift $z$, the apparent magnitude $m$ in a filter used in the
-survey, and the bandpass correction $K_{m,1450}\left(z\right)$
+with the luminosity distance
+\begin{equation}
+  d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{\mathrm{d}z^\prime}
+  {\sqrt{\Omega_\mathrm{m}(1+z^\prime)^3+\Omega_\Lambda}}
+  \label{eqn:dl}
+\end{equation}
+to a quasar at redshift $z$, the apparent magnitude $m$ in a filter used
+in the survey, and the bandpass correction $K_{m,1450}\left(z\right)$
 \citep{1956AJ.....61...97H, 1968ApJ...154...21O, 2000A&A...353..861W,
   2002astro.ph.10394H}. For the bandpass correction we used a
-combination of the \citet{2015MNRAS.449.4204L} quasar SED at
+combination of the \citet{2015MNRAS.449.4204L} stacked quasar spectrum at
 $\lambda<2500$\,\AA, and the \citet{2001AJ....122..549V} quasar
@@
 luminosity \citep{1977ApJ...214..679B}.  While the
-\citet{2015MNRAS.449.4204L} SED is for luminous ($M_{1450}\simeq
+\citet{2015MNRAS.449.4204L} spectrum is for luminous ($M_{1450}\simeq
 -27.2$) quasars, UV composite spectra including fainter quasars
@@
 orders of absolute magnitude depending on redshift and the filter, and
-with a $\sim 0.2$\,mag intrinsic scatter due to individual SED
+with a $\sim 0.2$\,mag intrinsic scatter due to individual quasar-to-quasar
 variations \citep{2013ApJ...773...14R, 2013ApJ...768..105M,
@@
 $f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
-Finally, we obtained a rough estimate of the
+We obtained a rough estimate of the
 \citet{2015AA...578A..83G} selection function by comparing the
@@
 Table~3).
+Finally, for the three $z>6.5$ quasars we assumed a selection function of
+unity in a range of $z$ and $M_{1450}$ estimated by the respective survey teams
+(private communication).
 
@@
 
-Given quasar luminosities and estimates for survey completeness, we
-are in a position to estimate the UV luminosity function of AGN.  We
-begin our analysis by first deriving luminosity functions in bins of
-redshift and magnitude.  In this discussion all magnitudes are
-absolute magnitudes at rest-frame 1450~{\AA}.
-% Put that sentence about magnitudes in the introduction.
+After homogenising the samples and selection functions we are in a position
+to compute the UV luminosity function of AGN. We begin our analysis by
+deriving luminosity functions in bins of redshift and absolute magnitude.
+For simplicity we will use the notation $M\equiv M_{1450}$ in the following.
 
@@
 \begin{equation}
-  V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}dM
-  \int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, f(M, z)\,\frac{dV}{dz},
+  V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
+  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z},
   \label{eqn:vi}
 \end{equation}
-is the effective volume of the bin.  Here $f(M,z)$ is the quasar
-selection probability, which includes incompleteness.  Inclusion of
-the selection probability in Equation~(\ref{eqn:vi}) accounts for
+is the effective volume of the bin. The inclusion of the survey selection function
+$f(M,z)$ (Section~\ref{sect:datahom}) in Equation~(\ref{eqn:vi}) accounts for
 what are sometimes called ``incomplete bins''
-\citep{2006AJ....131.2766R}.  The comoving volume element $dV/dz$ is
+\citep{2006AJ....131.2766R}.  The comoving volume element $\mathrm{d}V/\mathrm{d}z$ is
 given by
 \begin{equation}
-  \frac{dV}{dz}=\frac{dV}{dz\,d\Omega}\cdot A\cdot\frac{4\pi}{41253},
+  \frac{\mathrm{d}V}{\mathrm{d}z}=\frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}\times A\times\frac{4\pi}{41253},
 \end{equation}
@@
 \begin{equation}
-  \frac{dV}{dz\,d\Omega}=\frac{c}{H_0}\frac{d_L(z)^2}
-       {(1+z)^2\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}},
+  \frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}=\frac{c}{H_0}\frac{d_L^2\left(z\right)}
+       {\left(1+z\right)^2\sqrt{\Omega_\mathrm{m}\left(1+z\right)^3+\Omega_\Lambda}}
   \label{eqn:dvdzdo}
@@
 denotes the comoving volume element per unit solid angle
-\citep{1999astro.ph..5116H}.  The luminosity distance $d_L$ is given
-by
-\begin{equation}
-  d_L(z)=(1+z)\frac{c}{H_0}\int_0^z\frac{dz}
-  {\sqrt{\Omega_m(1+z)^3+\Omega_\Lambda}}.
-  \label{eqn:dl}
-\end{equation}
-Equations~(\ref{eqn:dvdzdo}) and (\ref{eqn:dl}) assume a flat Universe
-($\Omega_k=0$).  The luminosity function $\phi$ has units of
+\citep{1999astro.ph..5116H}.
+
+The luminosity function $\phi$ has units of
 $\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
@@
 without interpolating between the redshift and luminosity values of
-neighbouring tiles.  This may result in $V_i=0$ for some quasars, in
+neighbouring tiles. 
+%%GW: We should add that interpolation of selection functions is not straightforward (strong gradients) and not unique.
+Many selection functions are very coarse.
+V=0 means that the selection function has systematic errors (a QSO was found where the selection probability is zero).
+By removing them we avoid numerical issues, but underestimate the QLF.
+Surveys need to report selection functions that are consistent with their actual samples.
+This may result in $V_i=0$ for some quasars, in
 which case we remove them from our analysis.
-
+%%GW: Poisson statistics will underestimate the error since uncertainties in the selection function are not considered (all surveys assume a fixed selection function).
+For small surveys the Poisson error dominates, but for large surveys the error is driven by systematics in the selection function.
+These facts have been neglected so far, and we should make this point very clearly.
 In each bin, we estimate the uncertainty in the luminosity function by
 assuming Poisson statistics \citep{1986ApJ...303..336G} for the number
-of quasars in each bin.  The resultant binned luminosity function
-estimates are shown by the points in Figure~\ref{fig:mosaic}.
-
+of quasars, i.e.\ assuming negligible uncertainty in the selection function.
+The resultant binned luminosity function estimates are shown by the
+points in Figure~\ref{fig:mosaic}.
+
+%%GW: I've sharpened the discussion below.
 As seen in Figure~\ref{fig:mosaic}, the distribution of luminosity
 function values in each redshift bin are suggestive of a double power
-law form.  We will fit such a form below.  However, we also see in
-several redshift bins of Figure~\ref{fig:mosaic} that the luminosity
-function seems to show a decline at the faint end.  This is clearly
-seen, for example, in the 2SLAQ sample at $z<2$ and in the SDSS quasar
-sample at $z<1.8$ and $z\sim 4$.  We take this to be a systematic
-error.  The decrease in the luminosity function is an indication of
-further low-level incompleteness in the quasar surveys that has not
-been captured by the reported completeness values.  We choose to
-discard such bins from our analysis.  The discarded luminosity bins
-are shown in Figure~\ref{fig:mosaic} by open circles.
-
+law form for the QLF.  We will fit such a form below. 
+However, in several redshift bins we note a suspicious decline of the
+luminosity function at the faint limit of several surveys, for example in
+the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and $z\sim 4$.
+The inconsistency between the SDSS faint end and the deeper
+2SLAQ QLF indicates that the SDSS selection function is
+systematically overestimated at its magnitude limit.
+At $z\sim 4$ the SDSS faint end QLF is inconsistent with the fainter
+\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
+by eye and discard them from our analysis.
+%%GW: We should also set the selection functions to zero in these bins.
+The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by open circles.
+
+%%GW: 2.5<z<2.6 QSOs are missing in this plot!
+Also, there are no open symbols for BOSS, but the numbers indicate that you excluded some in several redshift bins.
+The total numbers per redshift bin are not matching the number of BOSS QSOs.
 \begin{figure*}
@@
   \end{center}
-  \caption{Luminosity function estimates in redshift bins from
+  \caption{Homogenised quasar luminosity functions at $\lambda=1450$\,\AA\ in redshift bins from
     $z=0.1$ to $6.5$.  The symbols show our inferred binned
@@
     \citet[green]{2009MNRAS.392...19C},
-    \citet[blue]{2013ApJ...773...14R},
+    \citet[dark blue]{2013ApJ...773...14R},
+    \citet[light blue]{2011ApJ...728L..26G},
     \citet[yellow]{2016ApJ...829...33Y},
-    \citet[brown]{2013ApJ...768..105M}, \citet[light
-      blue]{2011ApJ...728L..26G},
+    \citet[brown]{2013ApJ...768..105M},
     \citet[pink]{2016ApJ...833..222J},
@@
     \citet[grey]{2015ApJ...798...28K}.  Open circles in
-    corresponding colours indicate excluded incomplete bins for
-    the respective data sets.  In each redshift bin, the black
+    corresponding colours indicate excluded incomplete magnitude bins for
+    the respective data sets. In each panel we give the number
+    of considered quasars in the respective redshift bin,
+    with the number in parentheses indicating the total number of quasars before
+    excluding incomplete magnitude bins.
+    In each redshift bin, the black
     curve shows the best-fit double power law model, which is
@@
     distribution function.  The grey shaded area shows the
-    one-sigma (68.26\%) uncertainty.  Each panel shows the number
-    of quasars in the respective redshift bin.  The numbers in
-    parentheses indicate the total number of reported quasars in
-    the respective redshift bin, before excluding incomplete bins.
+    one-sigma (68.26\%) uncertainty. 
     See Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
@@
   \end{center}
-  \caption{Evolution of the four double power law parameters from the
+  \caption{Redshift evolution of the four double power law parameters from the
     redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical error
-    bars show one-sigma (68.26\%) uncertainties, whereas horizontal
+    bars show one-sigma (68.26\%) statistical uncertainties, whereas horizontal
     error bars show widths of the redshift bins.  We identify the
@@
     appear to be offset from these trends, likely due to unknown
-    systematic errors.  The open circles at $z\sim 2$--$4$ show the
+    systematic errors.  The open circles at $2.2<z<3.5$ show the
     BOSS sample, while the bins at $z < 0.6$ contain AGN from the SDSS
@@
 
+%%GW: I would delete the z_bin column from the table. Otherwise the reader might be confused what you are plotting in the figure. The bin centers and the mean values are very similar anyway.
+%%GW: Again 2.5<z<2.6 is missing
+%%GW: I would add a column or a comment which redshift bins we consider reliable. I'm afraid lazy people will just take the values without thinking.
 \begin{table*}
@@
 
-As our next step, we combine magnitude bins by binning the quasars
-only in redshifts.  This allows us to estimate the luminosity function
-at each redshift.  In each redshift bin, we model the quasar
-luminosity function as a double power law given by
-\citep{1988MNRAS.235..935B, 1995ApJ...438..623P, 2000MNRAS.317.1014B}
+%%GW: Not sure what you mean here. I've cut the next two sentences
+%As our next step, we combine magnitude bins by binning the quasars
+%only in redshifts.  This allows us to estimate the luminosity function
+%at each redshift.
+
+In each redshift bin, we model the quasar
+luminosity function as a double power law 
+\citep[e.g.][]{1988MNRAS.235..935B}
 \begin{equation}
   \phi(M) =
-  \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}}.
+  \frac{\phi_*}{10^{0.4(\alpha+1)(M-M_*)}+10^{0.4(\beta+1)(M-M_*)}}
   \label{eqn:dpl}
 \end{equation}
-Equation~(\ref{eqn:dpl}) has four free parameters: the amplitude
-$\phi_*$, the break magnitude $M_*$, the faint-end slope $\beta$, and
-the bright-end slope $\alpha$.  By assuming broad, uniform priors, we
+with four free parameters: (i) the amplitude $\phi_*$, (ii) the break magnitude $M_*$,
+(iii)  the bright-end slope $\alpha$, and (iv) the faint-end slope $\beta$.
+%%GW: Maybe give the range of the uniform priors.
+By assuming broad, uniform priors, we
 obtain posterior probability distributions for these parameters using
@@
 \begin{multline}
-  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM
-  \int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz}.
+  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
+  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, \phi(M,z) f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z}.
   \label{eqn:S}
@@
 \begin{equation}
-  \mu_{ij}= \int_{M_i}^{M_{i+1}}dM\int_{z_j}^{z_{j+1}}dz\, \phi(M,z) f(M, z)
-  \,\frac{dV}{dz},
+  \mu_{ij}= \int_{M_i}^{M_{i+1}}\mathrm{d}M\int_{z_j}^{z_{j+1}}\mathrm{d}z\, \phi(M,z) f(M, z)
+  \,\frac{\mathrm{d}V}{\mathrm{d}z},
 \end{equation}
@@
 Other parameters continue to have wide uniform priors.  This also
-illustrates the importance of analysing the high-redshift AGN
-population in a wider context of AGN data.
+illustrates the importance of analysing the evolution of the QLF with
+redshift.
 
 The redshift evolution of the four double power law parameters is
-shown in Figure~\ref{fig:evoln}.  These values have been tabulated in
-Table~\ref{tab:bins}.  We find interesting evolutionary trends in each
-of the four parameters.  The break luminosity $M_*$ evolves by more
+shown in Figure~\ref{fig:evoln} and tabulated in Table~\ref{tab:bins}.
+We find interesting evolutionary trends in each
+of the four parameters.  The break magnitude $M_*$ evolves by more
 than eight magnitudes from redshift $z=0$ to $7$.  The amplitude of
@@
 $z\sim 3$ and then drops by six orders of magnitude to about
-$10^{-12}$ at $z\sim 7$.  The bright end slope $\alpha$ has
-significant scatter, but still shows a trend towards larger negative
+$10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope $\alpha$ has
+significant scatter, but still shows a trend towards more negative
 values, i.e., steeper luminosity function bright ends, at high
-redshifts.  Finally, the faint end of the luminosity function also
-shows signs of increasing steepness towards high redshifts.  Somewhat
-similar to the amplitude $\phi_*$, the faint-end slope $\beta$ also
+redshifts.  Finally, the faint end slope of the luminosity function also
+shows signs of increasing steepness towards high redshifts.
+%%GW: I would not write that beta has a break.
+Somewhat similar to the amplitude $\phi_*$, the faint-end slope $\beta$ also
 shows a break at $z\sim 3$.  It stays roughly constant up to this
@@
 
-Figure~\ref{fig:evoln} reveals further potentially systematic errors.
-The behaviour of BOSS quasars, shown by open circles in
-Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
-redshift range covered by BOSS the values of the four double power law
-parameters deviate from the general trends.  The faint end of the
-luminosity function of the BOSS quasars is much shallower and the
-break luminosity is fainter by a magnitude compared to the general
-trend expected from a smooth evolution.  The bright end of the
-luminosity function of quasars in this sample is also much flatter
-than that for other samples.  The conspicuousness of the deviation of
-the BOSS sample from the general trends makes it unlikely that the
-luminosity function evolution indicated by BOSS in the redshift range
-$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
-selection is known to be affected by a colour bias
-\citep{2011ApJ...728...23W}, which can make estimating completeness
-difficult \citep{2006AJ....131.2766R}.
+%%GW: I've commented the following paragraph and replaced it by a sharper version
+%Figure~\ref{fig:evoln} reveals further likely systematic errors.
+%The behaviour of BOSS quasars, shown by open circles in
+%Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
+%redshift range covered by BOSS the values of the four double power law
+%parameters deviate from the general trends.  The faint end of the
+%luminosity function of the BOSS quasars is much shallower and the
+%break luminosity is fainter by a magnitude compared to the general
+%trend expected from a smooth evolution.  The bright end of the
+%luminosity function of quasars in this sample is also much flatter
+%than that for other samples.  The conspicuousness of the deviation of
+%the BOSS sample from the general trends makes it unlikely that the
+%luminosity function evolution indicated by BOSS in the redshift range
+%$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
+%selection is known to be affected by a colour bias
+%\citep{2011ApJ...728...23W}, which can make estimating completeness
+%difficult \citep{2006AJ....131.2766R}.
+
+Discontinuities and scatter in the QLF parameters over short redshift
+intervals in Figure~\ref{fig:evoln} reveal further likely systematic
+errors in the survey selection functions.  Quasars at $2.2\le z<3.5$
+taken solely from BOSS \citep{2013ApJ...773...14R} follow the redshift
+trends in $\phi_*$ and $M_*$, but with significant scatter in $\Delta
+z=0.1$ intervals that is much larger than the statistical error.  The
+discontinuity at $z=2.2$ indicates a mismatch of BOSS and
+SDSS$+$2SLAQ. The most striking feature, however, is the apparent
+rapid redshift evolution of the faint-end slope revealed in the BOSS
+sample, which is also highlighted in Figure~\ref{fig:mosaic}. Given
+the relatively smooth evolution of all QLF parameters at lower and
+higher redshifts it is unlikely that the QLF evolution at $2.2\le
+z<3.5$ indicated by BOSS is physical.  Rather it reflects the
+systematics limit of the large BOSS sample induced by a fixed
+selection function that critically depends on the assumed quasar
+spectral energy distribution and the IGM parameterization
+\citep{2011ApJ...728...23W,2013ApJ...773...14R}.  Consequently, we
+exclude all BOSS quasars from further analysis.
+
+The imperfect match between SDSS and 2SLAQ (Figure~\ref{fig:mosaic})
+causes low-level systematics, as evidenced by the apparent
+discontinuities in $\alpha$ at $z<2.2$ and the jump in $\beta$ at
+$z=1.8$ in Figure~\ref{fig:evoln}.  At $z<0.6$ the faint-end slope
+shows a sharp increase which we attribute to remaining uncertainties
+in the correction for host galaxy light and potentially missed AGN in
+extended sources. we exclude $z<0.6$ quasars from further
+consideration. Due to different selection function parameters
+inter-survey systematics are definitely present at $z>3.5$ as well,
+but Poisson errors of the limited samples dominate.
 
@@
   \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
-    Similar to Figure~\ref{fig:mosaic}, the symbols show our
-    inferred binned luminosity functions.  In each redshift bin,
-    yellow curves show the best-fit double power law luminosity
-    function in that redshift bin.  Other curves show the three
-    global evolution models.  Shaded regions show the one-sigma
-    (68.26\%) uncertainties.}
+    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
+    binned luminosity functions.  In each redshift bin, yellow curves
+    show the best-fit double power law luminosity function in that
+    redshift bin.  Other curves show the three global evolution
+    models.  Shaded regions show the one-sigma (68.26\%)
+    uncertainties.}
   \label{fig:mosaic_global}

### 2018-05-07 Paper/paper.tex
Updated Table 1

@@
   \end{center}
-  \caption{Redshift distribution of the 86,015 AGN considered in this
+  \caption{Redshift distribution of the 83,488 AGN considered in this
     analysis.  Shown here are the observed quasar numbers, without
@@
     \hline
-    1 & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
-    2 & 0.4--2.6 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 3663 & 64.2 \\
-    3 & 0.4--2.6 & --- NGP & \citet{2009MNRAS.392...19C} & 8153 & 127.7 \\
+    1 & 0.065--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
+    2$^b$ & 0.4--2.2 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 2338 & 64.2 \\
+    3$^b$ & 0.4--2.2 & --- NGP & \citet{2009MNRAS.392...19C} & 7027 & 127.7 \\
     4 & 2.2--3.5 & BOSS DR9 & \citet{2013ApJ...773...14R} & 23301 & 2236.0 \\
@@
     8 & 4.7--5.4 & SDSS+WISE & \citet{2016ApJ...829...33Y} & 99 & 14555.0 \\
-    9$^b$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
+    9$^c$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
     10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
@@
     16 & 5.8--6.5 & Subaru High-$z$ Quasar & \citet{2015ApJ...798...28K} & 2 & 6.5 \\
-    17$^c$ &4.0--6.5 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
-    18$^d$ & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
-    19$^d$ & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
-    20$^d$ & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
+    17$^d$ &4.0--6.5 & CANDELS GOODS-S & \citet{2015AA...578A..83G} & 19 & 0.047 \\
+    18$^e$ & 6.5--7.4 & UKIDSS & \citet{2011Natur.474..616M} & 1 & 3370.0 \\
+    19$^e$ & 6.5--7.4 & UKIDSS & \citet{2015ApJ...801L..11V} & 1 & 3370.0 \\
+    20$^e$ & 6.5--7.4 & ALLWISE+UKIDSS+DECaLS & \citet{2018Natur.553..473B} & 1 & 2500.0 \\
     \hline
@@
   \begin{minipage}{14.5cm}
-   \textsuperscript{$c$}{Redshift range of the sample or, for small samples, approximate redshift range in which the survey is sensitive.}\\
-  \textsuperscript{$b$}{Restricted to $M_{1450}>-26.73$ quasars to avoid overlap with the \citet{2016ApJ...829...33Y} sample.}\\
- \textsuperscript{$c$}{Used only in Section~\ref{sec:global} and Appendix~\ref{sec:conv} due to lack of spectroscopic redshifts for majority of the sample.}\\
- \textsuperscript{$d$}{Used only in Section~\ref{sec:global} due to roughly estimated selection function.}
+    \textsuperscript{$a$}{Redshift range of the sample or, for small
+      samples, approximate redshift range in which the survey is
+      sensitive.}\\
+    \textsuperscript{$b$}{Restricted to $z<2.2$.}\\
+    \textsuperscript{$c$}{Restricted to $M_{1450}>-26.73$ quasars to
+      avoid overlap with the \citet{2016ApJ...829...33Y} sample.}\\
+    \textsuperscript{$d$}{Used only in Section~\ref{sec:global} and
+      Appendix~\ref{sec:conv} due to lack of spectroscopic redshifts
+      for majority of the sample.}\\
+    \textsuperscript{$e$}{Used only in Section~\ref{sec:global} due to
+      roughly estimated selection function.}
  \end{minipage}

### 2018-05-08 Paper/paper.tex
Update Figure 1 and Table 1

@@
   \end{center}
-  \caption{Redshift distribution of the 83,488 AGN considered in this
-    analysis.  Shown here are the observed quasar numbers, without
+  \caption{Redshift distribution of the 83,491 AGN considered in this
+    analysis.  Shown here are the observed AGN numbers, without
     correcting for incompleteness.  Further details on each of these
@@
 \begin{table*}
-  \caption{Quasar samples analysed in this work.}
+  \caption{AGN samples analysed in this work.}
   \label{tab:samples}
@@
     \hline
-    1 & 0.065--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
+    1 & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
     2$^b$ & 0.4--2.2 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 2338 & 64.2 \\
@@
     9$^c$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
-    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
+    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 62 & 235.0 \\
     11 & 5.7--6.5 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\

### 2018-05-08 drawlf.py
Updaet for sample id 9

@@ -72,6 +72,7 @@ def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
     up = np.percentile(phi, 15.87, axis=0)
     down = np.percentile(phi, 84.13, axis=0)
     f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
+    #f = ax.fill_between(mags, down, y2=up, color='grey', alpha=0.7)
 
     return f
 
@@ -81,6 +82,7 @@ def plot_bestfit_lf(lf, ax, mags, **kwargs):
     phi_fit = lf.log10phi(bf, mags)
     # ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'], label=kwargs['label'])
     bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
+    #bf, = ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
 
     return bf 
 
@@ -168,7 +170,6 @@ def get_lf(lf, sid, z_plot):
     
     # Bin data.  This is only for visualisation and to compare
     # with reported binned values.  
-
     m = lf.M1450[lf.sid==sid]
 
     selmaps = [x for x in lf.maps if x.sid == sid]
@@ -199,6 +200,11 @@ def get_lf(lf, sid, z_plot):
 
     phi = nums
     logphi = np.log10(phi) # cMpc^-3 mag^-1
+
+    # print 'sid=', sid 
+    # print 'mags=', mags
+    # print 'nums=', nums
+    # print 'total=', np.sum(nums)
 
     # Calculate errorbars on our binned LF.  These have been estimated
     # using Equations 1 and 2 of Gehrels 1986 (ApJ 303 336), as
@@ -458,6 +464,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
            6 : '#17becf', # "cyan"
            7 : '#9467bd', # "purple"
            8 : '#8c564b', # "brown"
+           9 : 'r', 
            10 : '#ff7f0e', # "orange"
            11 : '#7f7f7f', # "grey"
            13 : '#d62728', # "red"
@@ -489,9 +496,8 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
 
     for i in sids[::-1]:
 
-        print i 
-        
[…]

### 2018-05-09 drawlf.py
Update Figure 3 of paper
Add missing z bin.  Print correct quasar counts.

@@ -71,8 +71,8 @@ def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
 
     up = np.percentile(phi, 15.87, axis=0)
     down = np.percentile(phi, 84.13, axis=0)
-    f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
-    #f = ax.fill_between(mags, down, y2=up, color='grey', alpha=0.7)
+    #f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
+    f = ax.fill_between(mags, down, y2=up, color='grey', alpha=0.7)
 
     return f
 
@@ -81,8 +81,8 @@ def plot_bestfit_lf(lf, ax, mags, **kwargs):
     bf = np.median(lf.samples, axis=0)
     phi_fit = lf.log10phi(bf, mags)
     # ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'], label=kwargs['label'])
-    bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
-    #bf, = ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
+    #bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
+    bf, = ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
 
     return bf 
 
@@ -464,7 +464,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
            6 : '#17becf', # "cyan"
            7 : '#9467bd', # "purple"
            8 : '#8c564b', # "brown"
-           9 : 'r', 
+           9 : 'teal', 
            10 : '#ff7f0e', # "orange"
            11 : '#7f7f7f', # "grey"
            13 : '#d62728', # "red"
@@ -541,7 +541,7 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
                         yerr=np.vstack((uperr, downerr)),
                         fmt='None', zorder=4)
         
-    return # (indf, indbf), (c1f, c1bf), (c2f, c2bf), (c3f, c3bf) 
+    return #(indf, indbf), (c1f, c1bf), (c2f, c2bf), (c3f, c3bf) 
 
[…]

### 2018-05-09 mosaic.py

@@ -53,9 +53,27 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     plt.text(0.03, 0.05, label, horizontalalignment='left',
              verticalalignment='center', transform=ax.transAxes, fontsize='10')
 
-    num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450_all.size)
-    plt.text(0.03, 0.12, num, horizontalalignment='left',
-             verticalalignment='center', transform=ax.transAxes, fontsize='10')
+    if lf.zlims[0] == 4.7:
+        # Print quasar counts manually as code will incorrectly add
+        # McGreer quasars excluded due to overlap with the Yang data.
+        # Expect lf.M1450.size = 266.
+        num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450.size)
+        plt.text(0.03, 0.12, num, horizontalalignment='left',
+                 verticalalignment='center', transform=ax.transAxes, fontsize='10')
+
+    elif lf.zlims[0] == 2.2:
+        # Print quasar counts manually as code will incorrectly add 5
+        # SDSS DR7 with redshift z = 2.2 to this bin.  These quasars
+        # not actually analysed in this bin.  (They are however
+        # retained in our global analysis.)  Expect lf.M1450.size =
+        # 8419.
+        num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450.size)
+        plt.text(0.03, 0.12, num, horizontalalignment='left',
+                 verticalalignment='center', transform=ax.transAxes, fontsize='10')
+    else:
+        num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450_all.size)
+        plt.text(0.03, 0.12, num, horizontalalignment='left',
+                 verticalalignment='center', transform=ax.transAxes, fontsize='10')
 
     return 
     
@@ -63,7 +81,7 @@ def draw(lfs, composite=None):
 
     nplots_x = 5
     nplots_y = 5
-    nplots = 16 # nplots_x * nplots_y
+    nplots = nplots_x * nplots_y
 
     plot_number = 0
 

### 2018-05-09 Paper/paper.tex

@@
     \hline
-    1 & 0.1--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
+    1 & 0.0--2.2 & SDSS DR7 & \citet{2010AJ....139.2360S} & 48664 & 6248.0 \\
     2$^b$ & 0.4--2.2 & 2SLAQ SGP & \citet{2009MNRAS.392...19C} & 2338 & 64.2 \\
@@
 
-%%GW: 2.5<z<2.6 QSOs are missing in this plot!
-Also, there are no open symbols for BOSS, but the numbers indicate that you excluded some in several redshift bins.
-The total numbers per redshift bin are not matching the number of BOSS QSOs.
 \begin{figure*}
@@
   \end{center}
-  \caption{Homogenised quasar luminosity functions at $\lambda=1450$\,\AA\ in redshift bins from
-    $z=0.1$ to $6.5$.  The symbols show our inferred binned
-    luminosity functions from various data sets:
+  \caption{Homogenised quasar luminosity functions at
+    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.  The
+    symbols show our inferred binned luminosity functions from various
+    data sets:
     \citet[red]{2010AJ....139.2360S},
@@
     \citet[yellow]{2016ApJ...829...33Y},
-    \citet[brown]{2013ApJ...768..105M},
+    \citet[DR7 brown]{2013ApJ...768..105M},
+    \citet[Stripe 82 teal]{2013ApJ...768..105M},
     \citet[pink]{2016ApJ...833..222J},
     \citet[orange]{2010AJ....139..906W}, and
-    \citet[grey]{2015ApJ...798...28K}.  Open circles in
-    corresponding colours indicate excluded incomplete magnitude bins for
-    the respective data sets. In each panel we give the number
-    of considered quasars in the respective redshift bin,
-    with the number in parentheses indicating the total number of quasars before
-    excluding incomplete magnitude bins.
-    In each redshift bin, the black
-    curve shows the best-fit double power law model, which is
-    represented by the median of the posterior probability
-    distribution function.  The grey shaded area shows the
-    one-sigma (68.26\%) uncertainty. 
-    See Sections~\ref{sec:binnedlf} and \ref{sec:bins} for further
-    details.}
+    \citet[grey]{2015ApJ...798...28K}.
+    Open circles in corresponding colours indicate magnitude bins
+    excluded due to incompleteness for the respective data sets.  The
+    number of AGN before this selection is shown in parentheses; the
+    selected number of AGN is shown outside parentheses.  In each
+    redshift bin, the black curve shows the best-fit double power law
+    model, which is represented by the median of the posterior
+    probability distribution function.  The grey shaded area shows the
+    one-sigma (68.26\%) uncertainty.  See Sections~\ref{sec:binnedlf}
+    and \ref{sec:bins} for further details.}
   \label{fig:mosaic}

### 2018-05-10 kcorr.py
Fix typos

@@ -45,7 +45,7 @@ plt.text(2.0, -1.8, '$m=i$', fontsize=12)
 #-----
 
 z, k = np.loadtxt('Data_new/kcorrz_l15.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='k', lw=2, label='Lusso et al.\ 2005') 
+plt.plot(z, k, c='k', lw=2, label='Lusso et al.\ 2015') 
 
 z, k = np.loadtxt('Data_new/kcorrz_t02.dat', usecols=(1,2), unpack=True)
 plt.plot(z, k, c='k', lw=2, dashes=[7,2], label='Telfer et al.\ 2002') 
@@ -53,7 +53,7 @@ plt.plot(z, k, c='k', lw=2, dashes=[7,2], label='Telfer et al.\ 2002')
 z, k = np.loadtxt('Data_new/kcorrz_v01.dat', usecols=(1,2), unpack=True)
 plt.plot(z, k, c='k', lw=2, dashes=[2,2], label='Vanden Berk et al.\ 2001')
 
-plt.text(4.85, -2.0, '$m=z$', fontsize=12)
+plt.text(4.7, -2.0, '$m=z_\mathrm{AB}$', fontsize=12)
 
 plt.ylim(-2.5,-0.5)
 plt.xlim(0,5.5)

### 2018-05-19 bins.py
Revert to excluding bright quasars from McGreer S82 sample
This is done by changing the sample id back to 8 and adding suitable
like to data.py.

@@ -32,7 +32,7 @@ selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13, r'Richards 
              ('Data_new/glikman11_selfunc_dls.dat', 0.05, 0.02, 2.05, 6, r'Glikman et al.\ 2011'),
              ('Data_new/yang16_sel.dat', 0.1, 0.05, 14555.0, 17, r'Yang et al.\ 2016'),
              ('Data_new/mcgreer13_dr7selfunc.dat', 0.1, 0.05, 6248.0, 8, r'McGreer et al.\ 2013'),
-             ('Data_new/mcgreer13_s82selfunc.dat', 0.1, 0.05, 235.0, 9, r'McGreer et al.\ 2013'),
+             ('Data_new/mcgreer13_s82selfunc.dat', 0.1, 0.05, 235.0, 8, r'McGreer et al.\ 2013'),
              ('Data_new/jiang16main_selfunc.dat', 0.1, 0.05, 11240.0, 18, r'Jiang et al.\ 2016'),
              ('Data_new/jiang16overlap_selfunc.dat', 0.1, 0.05, 4223.0, 18, r'Jiang et al.\ 2016'),
              ('Data_new/jiang16s82_selfunc.dat', 0.1, 0.05, 277.0, 18, r'Jiang et al.\ 2016'),

### 2018-05-19 data.py

@@ -146,6 +146,7 @@ f = ['Data_new/mcgreer13_s82sample.dat',
      'Data_new/mcgreer13_s82extend.dat']
 l = r'SDSS Stripe 82 McGreer et al.\ (2013)'
 s = sample(f, label=l)
+s.z = s.z[s.m>-26.73]
 data.append(s)
 
 f = ['Data/glikman11qso.dat']

### 2018-05-19 drawlf_giallongocompare.py
Update plot comparing our LF with Giallongo et al. 2015 LF
Modifying legend.

@@ -1,0 +1,583 @@
+import numpy as np
+import emcee
+import matplotlib as mpl
+mpl.use('Agg') 
+mpl.rcParams['text.usetex'] = True 
+mpl.rcParams['font.family'] = 'serif'
+mpl.rcParams['font.serif'] = 'cm'
+mpl.rcParams['font.size'] = '22'
+import matplotlib.pyplot as plt
+from astropy.stats import knuth_bin_width  as kbw
+from astropy.stats import poisson_conf_interval as pci
+from scipy.stats import binned_statistic as bs
+import cosmolopy.distance as cd
+cosmo = {'omega_M_0':0.3,
+         'omega_lambda_0':0.7,
+         'omega_k_0':0.0,
+         'h':0.70}
+
+
+"""Makes LF plots at particular redshifts.  Shows data with
+individual and composite models.  This is similar to the draw()
+function in individual.py but is more flexible.
+
+"""
+
+def lfsample(theta, n, mlims):
+
+    """
+    Return n qso magnitudes between mlims[0] and mlims[1] when the LF
+    is described by parameters theta.
+
+    """
+
+    mmin = mlims[0]
+    mmax = mlims[1]
+
+    def lnprob(x, theta):
+
+        if x < mmax and x > mmin: 
+            mag = x 
+            log10phi_star, M_star, alpha, beta = theta 
+            phi = 10.0**log10phi_star / (10.0**(0.4*(alpha+1)*(mag-M_star)) +
+                                         10.0**(0.4*(beta+1)*(mag-M_star)))
+            return np.log(phi)
+        else:
+            return -np.inf 
+    
+    ndim = 1 
+    nwalkers = 250
+    dm = np.abs(mmin-mmax)
+    p0 = (np.random.rand(ndim*nwalkers)*dm + mmin).reshape((nwalkers, ndim))
+
+    sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=[theta])
+    pos, prob, state = sampler.run_mcmc(p0, 100)
+    sampler.reset()
+    sampler.run_mcmc(pos, 1000)
+    sample = sampler.flatchain[:,0]
+
+    return np.random.choice(sample, n)
+    
+def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
+
+    nmags = 100
+    mags = np.linspace(*maglims, num=nmags)
[…]

### 2018-05-19 drawlf.py
Remove redundant line

@@ -464,7 +464,6 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
            6 : '#17becf', # "cyan"
            7 : '#9467bd', # "purple"
            8 : '#8c564b', # "brown"
-           9 : 'teal', 
            10 : '#ff7f0e', # "orange"
            11 : '#7f7f7f', # "grey"
            13 : '#d62728', # "red"

### 2018-05-19 kcorr.py
Update style

@@ -22,10 +22,10 @@ z, k = np.loadtxt('Data_new/kcorrg_l15.dat', usecols=(1,2), unpack=True)
 plt.plot(z, k, c='b', lw=2) 
 
 z, k = np.loadtxt('Data_new/kcorrg_t02.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='b', lw=2, dashes=[7,2]) 
+plt.plot(z, k, c='b', lw=1, dashes=[7,2]) 
 
 z, k = np.loadtxt('Data_new/kcorrg_v01.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='b', lw=2, dashes=[2,2])
+plt.plot(z, k, c='b', lw=1, dashes=[2,2])
 
 plt.text(0.35, -0.75, '$m=g$', fontsize=12)
 
@@ -35,10 +35,10 @@ z, k = np.loadtxt('Data_new/kcorri_l15.dat', usecols=(1,2), unpack=True)
 plt.plot(z, k, c='r', lw=2) 
 
 z, k = np.loadtxt('Data_new/kcorri_t02.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='r', lw=2, dashes=[7,2]) 
+plt.plot(z, k, c='r', lw=1, dashes=[7,2]) 
 
 z, k = np.loadtxt('Data_new/kcorri_v01.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='r', lw=2, dashes=[2,2])
+plt.plot(z, k, c='r', lw=1, dashes=[2,2])
 
 plt.text(2.0, -1.8, '$m=i$', fontsize=12)
 
@@ -48,10 +48,10 @@ z, k = np.loadtxt('Data_new/kcorrz_l15.dat', usecols=(1,2), unpack=True)
 plt.plot(z, k, c='k', lw=2, label='Lusso et al.\ 2015') 
 
 z, k = np.loadtxt('Data_new/kcorrz_t02.dat', usecols=(1,2), unpack=True)
-plt.plot(z, k, c='k', lw=2, dashes=[7,2], label='Telfer et al.\ 2002') 
+plt.plot(z, k, c='k', lw=1, dashes=[7,2], label='Telfer et al.\ 2002') 
 
 z, k = np.loadtxt('Data_new/kcorrz_v01.dat', usecols=(1,2), unpack=True)
[…]

### 2018-05-19 mosaic.py
Print correct number of z ~ 5 qsos

@@ -56,7 +56,7 @@ def plot(lf, ax, composite=None, yticklabels=False, xticklabels=False,
     if lf.zlims[0] == 4.7:
         # Print quasar counts manually as code will incorrectly add
         # McGreer quasars excluded due to overlap with the Yang data.
-        # Expect lf.M1450.size = 266.
+        # Expect lf.M1450.size = 263.
         num = r'{:d} ({:d}) quasars'.format(lf.M1450.size, lf.M1450.size)
         plt.text(0.03, 0.12, num, horizontalalignment='left',
                  verticalalignment='center', transform=ax.transAxes, fontsize='10')

### 2018-05-19 summary_giallongo.py
Improve legend

@@ -155,7 +155,7 @@ def plot_alpha(fig):
                 xerr=np.vstack((left, right)), 
                 yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=2)
-    ax.scatter(zmean, c, color='#ffffff', edgecolor='tomato', zorder=2, s=30, label='with Giallongo et al.\ 2015 qsos')
+    ax.scatter(zmean, c, color='#ffffff', edgecolor='tomato', zorder=2, s=30, label='with Giallongo et al.\ 2015 AGN')
 
     plt.legend(loc='upper right', fontsize=10, handlelength=2,
                frameon=False, framealpha=0.0, labelspacing=.1,

### 2018-05-19 lfg1.py
Utlity functions

@@ -1,0 +1,73 @@
+import sys
+import numpy as np 
+from composite import lf
+from composite import lf_polyb
+from summary_fromFile import summary_plot as sp
+
+# Model 1 
+
+qlumfiles = ['Data_new/dr7z2p2_sample.dat',
+             'Data_new/croom09sgp_sample.dat',
+             'Data_new/croom09ngp_sample.dat',
+             'Data_new/dr7z3p7_sample.dat',
+             'Data_new/glikman11debug.dat',
+             'Data_new/yang16_sample.dat',
+             'Data_new/mcgreer13_dr7sample.dat',
+             'Data_new/mcgreer13_s82sample.dat',
+             'Data_new/mcgreer13_dr7extend.dat',
+             'Data_new/mcgreer13_s82extend.dat',
+             'Data_new/jiang16main_sample.dat',
+             'Data_new/jiang16overlap_sample.dat',
+             'Data_new/jiang16s82_sample.dat',
+             'Data_new/willott10_cfhqsdeepsample.dat',
+             'Data_new/willott10_cfhqsvwsample.dat',
+             'Data_new/kashikawa15_sample.dat',
+             'Data_new/giallongo15_sample.dat',
+             'Data_new/ukidss_sample.dat',
+             'Data_new/banados_sample.dat']
+
+selnfiles = [('Data_new/dr7z2p2_selfunc.dat', 0.1, 0.05, 6248.0, 13),
+             ('Data_new/croom09sgp_selfunc.dat', 0.3, 0.05, 64.2, 15),
+             ('Data_new/croom09ngp_selfunc.dat', 0.3, 0.05, 127.7, 15),
+             ('Data_new/dr7z3p7_selfunc.dat', 0.1, 0.05, 6248.0, 13),
+             ('Data_new/glikman11_selfunc_ndwfs.dat', 0.05, 0.02, 1.71, 6),
+             ('Data_new/glikman11_selfunc_dls.dat', 0.05, 0.02, 2.05, 6),
+             ('Data_new/yang16_sel.dat', 0.1, 0.05, 14555.0, 17),
+             ('Data_new/mcgreer13_dr7selfunc.dat', 0.1, 0.05, 6248.0, 8),
+             ('Data_new/mcgreer13_s82selfunc.dat', 0.1, 0.05, 235.0, 8),
[…]

### 2018-05-19 paramz.py

@@ -1,0 +1,25 @@
+import numpy as np 
+
+def parameter_atz(lf, z, param_number):
+    """Return value of one of phi*, M*, alpha, and beta at redshift z for
+    luminosity function lf.
+
+    param_number sould be 0, 1, 2, 3 for phi*, M*, alpha, beta.
+
+    """
+    
+    np.random.seed()
+    nsample = 1000
+    rsample = lf.samples[np.random.randint(len(lf.samples), size=nsample)]
+    
+    prm = np.zeros(nsample)
+    for i, theta in enumerate(rsample):
+        params = lf.getparams(theta)
+        if param_number == 3 and len(theta) > 11:
+            prm[i] = lf.atz_beta(z, params[param_number])
+        else:
+            prm[i] = lf.atz(z, params[param_number])
+
+    best_fit = np.median(prm)
+    
+    return best_fit 

### 2018-05-19 Paper/paper.tex
Update Figure 4 and Table 2

@@
 $f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
-We obtained a rough estimate of the
-\citet{2015AA...578A..83G} selection function by comparing the
-corrected and observed QLFs, i.e.\ taking
-$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
-Table~3).
-Finally, for the three $z>6.5$ quasars we assumed a selection function of
-unity in a range of $z$ and $M_{1450}$ estimated by the respective survey teams
-(private communication).
+We obtained a rough estimate of the \citet{2015AA...578A..83G}
+selection function by comparing the corrected and observed QLFs,
+i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$
+(see their Table~3).  Finally, for the three $z>6.5$ quasars we
+assumed a selection function of unity in a range of $z$ and $M_{1450}$
+estimated by the respective survey teams (private communication).
 
@@
 neighbouring tiles. 
-%%GW: We should add that interpolation of selection functions is not straightforward (strong gradients) and not unique.
-Many selection functions are very coarse.
-V=0 means that the selection function has systematic errors (a QSO was found where the selection probability is zero).
-By removing them we avoid numerical issues, but underestimate the QLF.
-Surveys need to report selection functions that are consistent with their actual samples.
-This may result in $V_i=0$ for some quasars, in
-which case we remove them from our analysis.
-%%GW: Poisson statistics will underestimate the error since uncertainties in the selection function are not considered (all surveys assume a fixed selection function).
-For small surveys the Poisson error dominates, but for large surveys the error is driven by systematics in the selection function.
-These facts have been neglected so far, and we should make this point very clearly.
+%%GW: We should add that interpolation of selection functions is not
+%%straightforward (strong gradients) and not unique. Many selection
+%%functions are very coarse. V=0 means that the selection function has
+%%systematic errors (a QSO was found where the selection probability
+%%is zero). By removing them we avoid numerical issues, but
+%%underestimate the QLF. Surveys need to report selection functions
+%%that are consistent with their actual samples. -- done (GK) 
+This may result in $V_i=0$ for some quasars, in which case we remove
+them from our analysis.  (Interpolation of selection functions is not
+straightforward due to strong gradients.  The presence of objects with
+$V_i=0$ implies that the selection function has systematic errors.)
+%%GW: Poisson statistics will underestimate the error since
+%%uncertainties in the selection function are not considered (all
+%%surveys assume a fixed selection function). For small surveys the
+%%Poisson error dominates, but for large surveys the error is driven
+%%by systematics in the selection function. These facts have been
+%%neglected so far, and we should make this point very clearly. -- done (GK)
 In each bin, we estimate the uncertainty in the luminosity function by
@@
 
-%%GW: I've sharpened the discussion below.
+%%GW: I've sharpened the discussion below. -- done (GK)
 As seen in Figure~\ref{fig:mosaic}, the distribution of luminosity
@@
 by eye and discard them from our analysis.
-%%GW: We should also set the selection functions to zero in these bins.
-The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by open circles.
+%%GW: We should also set the selection functions to zero in these
+%%bins. -- done (GK)
+The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
+open circles.
 
@@
     \includegraphics[width=0.7\textwidth]{evolution_individuals.pdf}
-    % summary_fromFile.py 
+    % summary_bins.py 
   \end{center}
@@
 
-%%GW: I would delete the z_bin column from the table. Otherwise the reader might be confused what you are plotting in the figure. The bin centers and the mean values are very similar anyway.
-%%GW: Again 2.5<z<2.6 is missing
-%%GW: I would add a column or a comment which redshift bins we consider reliable. I'm afraid lazy people will just take the values without thinking.
+%%GW: I would delete the z_bin column from the table. Otherwise the
+%%reader might be confused what you are plotting in the figure. The
+%%bin centers and the mean values are very similar anyway.--done (GK)
+%%GW: Again 2.5<z<2.6 is missing--done (GK)
+%%GW: I would add a column or a comment which redshift bins we
+%%consider reliable. I'm afraid lazy people will just take the values
+%%without thinking.
 \begin{table*}
@@
   \label{tab:bins}
-  \begin{tabular}{ccccr....}
+  \begin{tabular}{cccr....}
     \hline
     $\langle z\rangle$ &
-    $z_\mathrm{bin}$ &
     $z_\mathrm{min}$ &
@@
 
-    &
     &
@@
     \hline
-    0.31 & 0.25 & 0.10 & 0.40 & 3520 & -5.62^{+0.09}_{-0.10} & -21.37^{+0.21}_{-0.22} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
-    0.50 & 0.50 & 0.40 & 0.60 & 4555 & -6.12^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.08} & -3.37^{+0.07}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
-    0.72 & 0.70 & 0.60 & 0.80 & 3308 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.15}_{-0.13} & -3.55^{+0.12}_{-0.13} & -1.75^{+0.05}_{-0.04} \\
-    0.91 & 0.90 & 0.80 & 1.00 & 3922 & -6.39^{+0.08}_{-0.07} & -24.51^{+0.12}_{-0.11} & -3.69^{+0.10}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
-    1.10 & 1.10 & 1.00 & 1.20 & 6367 & -6.53^{+0.03}_{-0.03} & -25.14^{+0.04}_{-0.04} & -4.17^{+0.08}_{-0.09} & -1.73^{+0.02}_{-0.02} \\
-    1.30 & 1.30 & 1.20 & 1.40 & 6479 & -6.43^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.06} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
-    1.50 & 1.50 & 1.40 & 1.60 & 7539 & -6.51^{+0.03}_{-0.03} & -25.68^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.75^{+0.02}_{-0.02} \\
-    1.71 & 1.70 & 1.60 & 1.80 & 6788 & -6.28^{+0.04}_{-0.04} & -25.55^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
-    1.98 & 2.00 & 1.80 & 2.20 & 10478 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.20^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
-    2.25 & 2.25 & 2.20 & 2.30 & 4102 & -5.98^{+0.10}_{-0.09} & -25.26^{+0.19}_{-0.18} & -3.21^{+0.15}_{-0.16} & -1.54^{+0.07}_{-0.06} \\
-    2.35 & 2.35 & 2.30 & 2.40 & 4317 & -6.28^{+0.09}_{-0.09} & -25.63^{+0.17}_{-0.15} & -3.39^{+0.17}_{-0.19} & -1.64^{+0.06}_{-0.05} \\
-    2.45 & 2.45 & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.13} & -3.60^{+0.20}_{-0.21} & -1.60^{+0.05}_{-0.05} \\
-    2.65 & 2.65 & 2.60 & 2.70 & 1883 & -5.98^{+0.06}_{-0.06} & -25.15^{+0.14}_{-0.13} & -3.13^{+0.12}_{-0.13} & -1.05^{+0.09}_{-0.08} \\
-    2.75 & 2.75 & 2.70 & 2.80 & 1135 & -6.30^{+0.08}_{-0.07} & -25.96^{+0.15}_{-0.13} & -3.81^{+0.28}_{-0.31} & -1.34^{+0.07}_{-0.06} \\
-    2.85 & 2.85 & 2.80 & 2.90 & 1069 & -6.46^{+0.12}_{-0.10} & -26.23^{+0.23}_{-0.18} & -3.60^{+0.36}_{-0.42} & -1.46^{+0.08}_{-0.07} \\
-    2.95 & 2.95 & 2.90 & 3.00 & 1104 & -6.77^{+0.07}_{-0.06} & -26.53^{+0.10}_{-0.09} & -5.05^{+0.60}_{-0.64} & -1.71^{+0.05}_{-0.04} \\
-    3.05 & 3.05 & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.10} & -4.71^{+0.46}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
-    3.15 & 3.15 & 3.10 & 3.20 & 1041 & -7.25^{+0.17}_{-0.12} & -27.09^{+0.25}_{-0.18} & -4.42^{+0.81}_{-1.23} & -1.96^{+0.08}_{-0.06} \\
-    3.25 & 3.25 & 3.20 & 3.30 & 815 & -7.33^{+0.13}_{-0.13} & -27.19^{+0.19}_{-0.23} & -4.36^{+0.65}_{-0.76} & -1.93^{+0.06}_{-0.06} \\
-    3.34 & 3.35 & 3.30 & 3.40 & 510 & -7.54^{+0.19}_{-0.21} & -27.39^{+0.25}_{-0.37} & -4.90^{+1.36}_{-1.35} & -2.08^{+0.09}_{-0.07} \\
-    3.44 & 3.45 & 3.40 & 3.50 & 155 & -6.77^{+0.19}_{-0.20} & -26.64^{+0.42}_{-0.35} & -3.70^{+0.62}_{-0.80} & -1.24^{+0.27}_{-0.22} \\
-    3.88 & 3.90 & 3.70 & 4.10 & 628 & -7.92^{+0.12}_{-0.10} & -27.26^{+0.14}_{-0.12} & -4.81^{+0.34}_{-0.39} & -2.07^{+0.10}_{-0.09} \\
-    4.35 & 4.40 & 4.10 & 4.70 & 442 & -8.32^{+0.29}_{-0.26} & -27.38^{+0.38}_{-0.31} & -4.19^{+0.41}_{-0.47} & -2.20^{+0.16}_{-0.13} \\
-    4.92 & 5.10 & 4.70 & 5.50 & 263 & -9.02^{+0.29}_{-0.22} & -27.88^{+0.36}_{-0.27} & -4.51^{+0.66}_{-0.83} & -2.31^{+0.11}_{-0.08} \\
-    6.00 & 6.00 & 5.50 & 6.50 & 66 & -10.60^{+0.71}_{-1.06} & -29.12^{+1.04}_{-1.78} & -4.99^{+0.72}_{-1.22} & -2.40^{+0.10}_{-0.08} \\
+    0.31 & 0.10 & 0.40 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
+    0.50 & 0.40 & 0.60 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
+    0.72 & 0.60 & 0.80 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
+    0.91 & 0.80 & 1.00 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
+    1.10 & 1.00 & 1.20 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
+    1.30 & 1.20 & 1.40 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
+    1.50 & 1.40 & 1.60 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
+    1.71 & 1.60 & 1.80 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
+    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
+    2.30 & 2.20 & 2.40 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
+    2.45 & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
+    2.55 & 2.50 & 2.60 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
+    2.65 & 2.60 & 2.70 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
+    2.75 & 2.70 & 2.80 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
+    2.85 & 2.80 & 2.90 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
+    2.95 & 2.90 & 3.00 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
+    3.05 & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
+    3.15 & 3.10 & 3.20 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
+    3.25 & 3.20 & 3.30 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
+    3.34 & 3.30 & 3.40 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
+    3.44 & 3.40 & 3.50 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
+    3.88 & 3.70 & 4.10 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.10 & 4.70 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
+    4.92 & 4.70 & 5.50 & 266 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
+    6.00 & 5.50 & 6.50 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
     \hline
@@
 %As our next step, we combine magnitude bins by binning the quasars
-%only in redshifts.  This allows us to estimate the luminosity function
-%at each redshift.
-
+%only in redshifts.  This allows us to estimate the luminosity
+%function at each redshift.--done(GK)
 In each redshift bin, we model the quasar
@@
 %%GW: Maybe give the range of the uniform priors.
-By assuming broad, uniform priors, we
-obtain posterior probability distributions for these parameters using
-MCMC \citep[e.g.,][]{jaynes}.  The joint posterior probability
-distribution of the model parameters is then written as
+By assuming broad, uniform priors, we obtain posterior probability
+distributions for these parameters using MCMC \citep[e.g.,][]{jaynes}.
+The joint posterior probability distribution of the model parameters
+is then written as
 \begin{multline}
@@
 shown in Figure~\ref{fig:evoln} and tabulated in Table~\ref{tab:bins}.
-We find interesting evolutionary trends in each
-of the four parameters.  The break magnitude $M_*$ evolves by more
-than eight magnitudes from redshift $z=0$ to $7$.  The amplitude of
-the luminosity function $\phi_*$ evolves moderately from $z=0$ to
-$z\sim 3$ and then drops by six orders of magnitude to about
-$10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope $\alpha$ has
-significant scatter, but still shows a trend towards more negative
-values, i.e., steeper luminosity function bright ends, at high
-redshifts.  Finally, the faint end slope of the luminosity function also
-shows signs of increasing steepness towards high redshifts.
-%%GW: I would not write that beta has a break.
-Somewhat similar to the amplitude $\phi_*$, the faint-end slope $\beta$ also
-shows a break at $z\sim 3$.  It stays roughly constant up to this
-redshift, and the drops to increasingly negative values of close to
-$-2.5$ at high redshifts, indicating a steeper faint end.
-
-%%GW: I've commented the following paragraph and replaced it by a sharper version
+We find interesting evolutionary trends in each of the four
+parameters.  The break magnitude $M_*$ evolves by more than eight
+magnitudes from redshift $z=0$ to $7$.  The amplitude of the
+luminosity function $\phi_*$ evolves moderately from $z=0$ to $z\sim
+3$ and then drops by six orders of magnitude to about
+$10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope
+$\alpha$ has significant scatter, but still shows a trend towards more
+negative values, i.e., steeper luminosity function bright ends, at
+high redshifts.  Finally, the faint end slope of the luminosity
+function also shows signs of increasing steepness towards high
+redshifts.
+%%GW: I would not write that beta has a break.--done(GK)
+Somewhat similar to the amplitude $\phi_*$, the faint-end slope
+$\beta$ also shows rapid evolution at $z\sim 3$.  It stays roughly
+constant up to this redshift, and the drops to increasingly negative
+values of close to $-2.5$ at high redshifts, indicating a steeper
+faint end.
+
+%%GW: I've commented the following paragraph and replaced it by a
+%%sharper version
 %Figure~\ref{fig:evoln} reveals further likely systematic errors.
@@
 %\citep{2011ApJ...728...23W}, which can make estimating completeness
-%difficult \citep{2006AJ....131.2766R}.
+%difficult \citep{2006AJ....131.2766R}. --done(GK)
 

### 2018-05-19 Paper/paper.tex
Update text
Comments from Joe

@@
   Determinations of the UV luminosity function of AGN at high
-  redshifts are important for constraining the contribution of AGN to
-  reionization.  Many recent inferences of the luminosity function
-  suffer from inconsistencies arising from inhomogeneous selection and
-  mixing of AGN data.  We address this problem in this paper by
-  constructing a sample of more than 85,000 colour-selected AGN from
-  redshift $z=0$ to $7.5$.  This sample is constructed out of multiple
-  data sets with spectroscopic redshifts and completeness estimates.
-  We homogenise these data sets to identical cosmologies, intrinsic
-  AGN spectra, and magnitude systems.  Using this sample, we derive
-  the AGN UV luminosity function from redshifts $z=0$ to $7.5$.  The
-  luminosity function has a double power law form at $z<5.5$, and
-  single power law form at higher redshifts.  The break luminosity
-  brightens rapidly with redshift and the faint end of the luminosity
-  function steepens.  In spite of this steepening, the contribution of
-  AGN to the hydrogen photoionization rate at $z=5$--$6$ is
-  subdominant, although it can be non-negligible if these luminosity
-  functions hold down to $M_{1450}=-18$.  Under reasonable
-  assumptions, AGN can reionize \HeII\ by redshift $z=3.2$.  At low
-  redshifts ($z<0.5$), AGN can produce all of the hydrogen
-  photoionization rate implied by the \lya data.  Our global analysis
+  redshifts are important for constraining the AGN contribution to
+  reionization and understanding the growth of supermassive black
+  holes.  Recent inferences of the luminosity function suffer from
+  inconsistencies arising from inhomogeneous selection and mixing of
+  AGN data.  We address this problem by constructing a sample of more
+  than 80,000 colour-selected AGN from redshift $z=0$ to $7.5$.  While
+  this sample is composed of multiple data sets with spectroscopic
+  redshifts and completeness estimates, we homogenise these data sets
+  to identical cosmologies, intrinsic AGN spectra, and magnitude
+  systems.  Using this sample, we derive the AGN UV luminosity
+  function from redshifts $z=0$ to $7.5$.  The luminosity function has
+  a double power law form at $z<5.5$, and a single power law form at
+  higher redshifts.  The break luminosity brightens rapidly with
+  redshift and the faint end of the luminosity function steepens.  In
+  spite of this steepening, the contribution of AGN to the hydrogen
+  photoionization rate at $z\sim 6$ is subdominant, although it can be
+  non-negligible if these luminosity functions hold down to
+  $M_{1450}=-18$.  Under reasonable assumptions, AGN can reionize
+  \HeII\ by redshift $z=3.2$.  At low redshifts ($z<0.5$), AGN can
+  produce all of the hydrogen photoionization rate inferred from the
+  statistics of \HI\ absorption lines in the IGM.  Our global analysis
   of the luminosity function also reveals important systematic errors
-  in the data, particularly at $z<0.6$ and $z=2.2$--$3.5$, which need
-  to be addressed in future in order to improve our results.  We make
+  in the data, particularly at $z=2.2$--$3.5$, which need to be
+  addressed in future in order to improve our results.  We make
   various fitting functions, luminosity function analysis codes, and
-  homogenised AGN data publicly available.
+  homogenized AGN data publicly available.
 \end{abstract}
@@
 constrains models of the build-up of supermassive black holes
-\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the
+\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.
+%% JFH Some historical papers should be cited for this SMBH buildup point, like
+%% for example Soltan. 
+Due to the
 incidence of supermassive black holes in most galaxies, the tight
@@
 determines their influence on the temperature and ionization state of
-the intergalactic medium (IGM) over large scales, possibly even
+the intergalactic medium (IGM) over large scales,
+%% JFH Probably want to say something here about radiation background
+%% instead of this ``large scales'' 
+possibly even
 primarily driving hydrogen and helium reionization.
@@
 luminosity function of AGN, triggered by the 19 low-luminosity
-($M_{1450}>-22.6$) AGN candidates between redshifts $z=4.1$ and $6.3$
+($M_{1450}>-22.6$)
+%% JFH Probably more sensible to quote a luminosity range rather than just a > 
+AGN candidates between redshifts $z=4.1$ and $6.3$
 discovered by \citet{2015AA...578A..83G} using a novel X-ray/NIR
@@
 hydrogen photoionization rate inferred from the \lya forest at
-$4<z<6$.  A significant presence of AGN at high redshift ($z\sim 6$)
+$4<z<6$.
+%% JFH Probably should say something here about assuming all ionizing photons escape, since these
+%% are galaxy like luminosities. Maybe quote L_star galaxy for comparison, which helps with your next
+%% point about faint galaxies. 
+A significant presence of AGN at high redshift ($z\sim 6$)
 and a dominant contribution of AGN to reionization is appealing as the
@@
 different quasar sightlines close to redshift $z=6$
-\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
+\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
+%% JFH Please cite new paper by eilers et al. here, not yet on archive. 
+These opacity
 fluctuations extend to substantially larger scales ($\gtrsim 50\,
 h^{-1}$cMpc) than expected in galaxies-dominated reionization models
-\citep{2015MNRAS.453.2943C}.  AGN clustering can result in these
+\citep{2015MNRAS.453.2943C}.
+%% JFH You probably need a ``but see Davies et al. 201X'' since Fred claims
+%% he can explain these fluctuations with galaxies. See also the new paper with George Becker and Fred. 
+AGN clustering can result in these
 fluctuations naturally if there is a significant contribution
@@
 hydrogen-ionizing photons that is required to explain the Ly$\alpha$
-opacity fluctuations.  Further arguments against AGN-dominated
+opacity fluctuations.
+%% JFH Probably need to clarify for this last point that you mean in a situation
+%% where galaxies contribute no LL photons, and QSOs completely dominate. 
+Further arguments against AGN-dominated
 reionization have been presented by \citet{2016MNRAS.459.2299F} by
@@
   \end{center}
-  \caption{Redshift distribution of the 83,491 AGN considered in this
+  \caption{Redshift distribution of the 83,488 AGN considered in this
     analysis.  Shown here are the observed AGN numbers, without
@@
     9$^c$ & 4.7--5.5 & SDSS DR7 & \citet{2013ApJ...768..105M} & 103 & 6248.0 \\
-    10 & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 62 & 235.0 \\
+    10$^c$ & 4.7--5.5 & --- Stripe 82 & \citet{2013ApJ...768..105M} & 59 & 235.0 \\
     11 & 5.7--6.5 & SDSS Main & \citet{2016ApJ...833..222J} & 24 & 11240.0 \\
@@
 
-We started with compiling the samples of recent photometric rest-frame UV-optical
+We started with
+%% JFH we started with --> we started by
+compiling the samples of recent photometric rest-frame UV-optical
 quasar surveys. The restriction to UV-optical surveys was mainly
@@
 \item Spectroscopic redshifts for the vast majority of targets.
+  %% JFH Did we actually use any photometric redshifts? If not, I would omit this ``Vast majority'' and make
+  %% it more definite. 
 \item Accurate rest-frame UV-optical CCD photometry.
@@
 \item A characterised selection function.
+  %% JFH well characterized
 \end{enumerate}
@@
 survey selection functions in electronic form, either from the
-publication or from the authors. As a reference for future surveys we
-publish them here in modified and homogenised form
+publication or
+%% JFH by request 
+from the authors. As a reference for future surveys we
+publish them here
+%% JFH rather than publish them here say ``we make them electronically available here''. Cite an appendix where
+%% you do this. 
+in modified and homogenised form
 (Section~\ref{sect:datahom}).
@@
 uncertainties in the correction for host galaxy light
+%% JFH What is Croom the reference for here, host galaxy contamination or the 2SLAQ sample. You basically
+%% need a reference for 2SLAQ and it appears in the wrong place here. 
 \citep{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 11,816
@@
 quasars) has negligible impact on the QLF evaluation.
+%% JFH Maybe state what the 2SLAQ survey goal was re quasars.
 
@@
 and the 10 SDSS Stripe~82 quasars at $z>5.1$, adopting their low
-selection efficiency.  As we will show in Section~3.2, the resulting
+selection efficiency.
+%% JFH efficiency and completeness are two different things and you seem to be conflating
+%% the two concepts here. 
+As we will show in Section~3.2, the resulting
 QLF is consistent with those at lower and higher redshifts, indicating
@@
 \citet{2011Natur.474..616M} and \citet{2015ApJ...801L..11V} in UKIDSS
-imaging (3370\,deg$^2$), in addition to the current highest-redshift
+imaging (3370\,deg$^2$)
+%% JFH quote the individual redshifst of the mortlock and venemans objects
+, in addition to the current highest-redshift
 quasar at $z=7.54$ selected from a combination of UKIDSS, WISE and
@@
 in our main analysis due to its rough selection function and lacking
+%% JFH lacking --> lack of 
 spectroscopy for 17 of the 22 quasar candidates, we use it in
@@
 \label{sect:datahom}
+
+%% JFH This section is long tedious and hard to follow. Perhaps we
+%% should put a brief description here, relegate these details to the
+%% appendix, and in the appendix, structure this section by
+%% sub-sections for each individual survey.
 
@@
 
+%% JFH Let's make all these conversion factors and codes to do K-correction
+%% publicly avaialble in an appendix.
+
 For the $z<2.2$ sample we corrected the SDSS $i$ and 2SLAQ $g$ band
@@
 \citep{2013ApJ...773...14R}, and we adopted
+%% JFH The overline looks weird here. I would suggest taht you rather
+%% use angle brackets instead. It is not jiving with the equation above
+%% and is very hard to read. 
 $f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
@@
 
+%% JFH We need a better roadmap here for where this section is going. 1) Binned estimates 2) individual
+%% fits in redshift bins. 3) examining redshift evolution. 4) attempting a joint fit.
+
 After homogenising the samples and selection functions we are in a position
@@
   bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the luminosity
+    %% JFH Notation error here. 
 function as \citep{2000MNRAS.311..433P}
@@
     \hline
-    0.31 & 0.10 & 0.40 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
-    0.50 & 0.40 & 0.60 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
-    0.72 & 0.60 & 0.80 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
-    0.91 & 0.80 & 1.00 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
-    1.10 & 1.00 & 1.20 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
-    1.30 & 1.20 & 1.40 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
-    1.50 & 1.40 & 1.60 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
-    1.71 & 1.60 & 1.80 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
-    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
-    2.30 & 2.20 & 2.40 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
-    2.45 & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
-    2.55 & 2.50 & 2.60 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
-    2.65 & 2.60 & 2.70 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
-    2.75 & 2.70 & 2.80 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
-    2.85 & 2.80 & 2.90 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
-    2.95 & 2.90 & 3.00 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
-    3.05 & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
-    3.15 & 3.10 & 3.20 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
-    3.25 & 3.20 & 3.30 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
-    3.34 & 3.30 & 3.40 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
-    3.44 & 3.40 & 3.50 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
-    3.88 & 3.70 & 4.10 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
-    4.35 & 4.10 & 4.70 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
-    4.92 & 4.70 & 5.50 & 266 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
-    6.00 & 5.50 & 6.50 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
+    0.31 & 0.10 & 0.40 & 3632  & -5.61^{+0.09}_{-0.11} & -21.36^{+0.20}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.21^{+0.18}_{-0.17} \\
+    0.50 & 0.40 & 0.60 & 4686  & -6.12^{+0.04}_{-0.04} & -23.00^{+0.07}_{-0.08} & -3.37^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
+    0.72 & 0.60 & 0.80 & 4684  & -6.42^{+0.09}_{-0.08} & -24.04^{+0.15}_{-0.12} & -3.56^{+0.12}_{-0.12} & -1.75^{+0.05}_{-0.04} \\
+    0.91 & 0.80 & 1.00 & 5248  & -6.39^{+0.08}_{-0.07} & -24.51^{+0.12}_{-0.11} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
+    1.10 & 1.00 & 1.20 & 6566  & -6.53^{+0.03}_{-0.03} & -25.14^{+0.04}_{-0.04} & -4.17^{+0.08}_{-0.09} & -1.73^{+0.02}_{-0.02} \\
+    1.30 & 1.20 & 1.40 & 7132  & -6.43^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.06} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
+    1.50 & 1.40 & 1.60 & 7771  & -6.51^{+0.03}_{-0.03} & -25.68^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
+    1.71 & 1.60 & 1.80 & 7421  & -6.29^{+0.04}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.97^{+0.07}_{-0.07} & -1.61^{+0.03}_{-0.03} \\
+    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.27^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
+    2.30 & 2.20 & 2.40 & 8419  & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.33^{+0.11}_{-0.12} & -1.60^{+0.04}_{-0.04} \\
+    2.45 & 2.40 & 2.50 & 3403  & -6.40^{+0.08}_{-0.07} & -25.86^{+0.15}_{-0.12} & -3.60^{+0.20}_{-0.23} & -1.60^{+0.05}_{-0.05} \\
+    2.55 & 2.50 & 2.60 & 2640  & -6.15^{+0.08}_{-0.09} & -25.34^{+0.18}_{-0.17} & -3.31^{+0.16}_{-0.16} & -1.39^{+0.08}_{-0.08} \\
+    2.65 & 2.60 & 2.70 & 1883  & -5.98^{+0.06}_{-0.06} & -25.15^{+0.14}_{-0.13} & -3.13^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
+    2.75 & 2.70 & 2.80 & 1135  & -6.29^{+0.07}_{-0.07} & -25.95^{+0.15}_{-0.13} & -3.79^{+0.26}_{-0.29} & -1.34^{+0.07}_{-0.06} \\
+    2.85 & 2.80 & 2.90 & 1069  & -6.46^{+0.11}_{-0.10} & -26.23^{+0.22}_{-0.18} & -3.62^{+0.36}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
+    2.95 & 2.90 & 3.00 & 1104  & -6.76^{+0.07}_{-0.06} & -26.52^{+0.10}_{-0.09} & -5.04^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
+    3.05 & 3.00 & 3.10 & 1127  & -6.77^{+0.08}_{-0.07} & -26.48^{+0.11}_{-0.11} & -4.72^{+0.44}_{-0.51} & -1.70^{+0.05}_{-0.05} \\
+    3.15 & 3.10 & 3.20 & 1041  & -7.25^{+0.16}_{-0.12} & -27.10^{+0.23}_{-0.18} & -4.42^{+0.79}_{-1.17} & -1.96^{+0.07}_{-0.05} \\
+    3.25 & 3.20 & 3.30 & 815   & -7.34^{+0.13}_{-0.13} & -27.20^{+0.19}_{-0.23} & -4.37^{+0.68}_{-0.74} & -1.94^{+0.06}_{-0.05} \\
+    3.34 & 3.30 & 3.40 & 510   & -7.53^{+0.22}_{-0.21} & -27.38^{+0.29}_{-0.36} & -4.79^{+1.34}_{-1.47} & -2.08^{+0.09}_{-0.07} \\
+    3.44 & 3.40 & 3.50 & 155   & -6.78^{+0.19}_{-0.20} & -26.64^{+0.40}_{-0.34} & -3.74^{+0.64}_{-0.79} & -1.25^{+0.28}_{-0.23} \\
+    3.88 & 3.70 & 4.10 & 1204  & -7.92^{+0.12}_{-0.11} & -27.26^{+0.14}_{-0.12} & -4.84^{+0.34}_{-0.36} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.10 & 4.70 & 603   & -8.32^{+0.28}_{-0.26} & -27.37^{+0.36}_{-0.31} & -4.20^{+0.40}_{-0.49} & -2.20^{+0.16}_{-0.14} \\
+    4.92 & 4.70 & 5.50 & 263   & -9.04^{+0.30}_{-0.22} & -27.90^{+0.37}_{-0.26} & -4.56^{+0.70}_{-0.81} & -2.31^{+0.11}_{-0.08} \\
+    6.00 & 5.50 & 6.50 & 66    & -10.64^{+0.72}_{-1.08} & -29.18^{+1.05}_{-1.81} & -5.00^{+0.76}_{-1.21} & -2.40^{+0.09}_{-0.08} \\
     \hline
@@
 \end{equation}
-is given by $\phi(M)$ with suitable normalisation.  The negative
+is given by $\phi(M)$
+%% JFH  ``is given by $\phi(M)$ itself''
+with suitable normalisation.  The negative
 logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can then be
@@
 
+%% JFH SOmewhere indicate taht this procedure of ubninned LF estimates is standard practice. 
 The above likelihood can also be understood as the limit of the
@@
 Our estimates for the double power law luminosity function are shown
-in Figure~\ref{fig:mosaic} for 25 redshift bins.  The posterior median
+in Figure~\ref{fig:mosaic} for 25 redshift bins.
+%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
+%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
+%% median of the individual marginalized posteriors? Or is it the median of the function that results from
+%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
+%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
+%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
+%% something like that. I would just explain waht you plot. 
+The posterior median
 is shown as the best-fit model at each redshift, while the grey shaded
@@
 suggests that these AGN should instead be understood to describe the
-faint-end of a double power law.  Therefore, in light of the
-low-redshift data, we use restricted priors in this redshift bin: we
-restrict the bright-end slope $\alpha$ to values less than $-4$, which
+faint-end of a double power law.
+%% JFH Okay so you need to be more clear here that what you mean is that the trend
+%% from the plot is that M_star gets progressively brighter with redshift. This is not
+%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
+%% anyway has this prior already in it. 
+Therefore, in light of the
+low-redshift data, we use restricted priors in this
+%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
+%% and it is informed by inspection of the lower redshift data. 
+redshift bin: we
+restrict the bright-end slope $\alpha$ to values less than $-4$,
+%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
+%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
+which
 is equivalent to forcing $M_*$ to be at the bright end of the data.
@@
 $10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope
-$\alpha$ has significant scatter, but still shows a trend towards more
+$\alpha$ has significant scatter,
+%% JFH most likely attributable to systematic erorrs in the measurements.
+but still shows a trend towards more
 negative values, i.e., steeper luminosity function bright ends, at
@@
 faint end.
+
+%% JFH I think you need to show at least one corner plot for your fits somewhere in the paper.
+
+%% JFH I think before imposing this prior by hand it might be useful to show the degeneracies that
+%% you get at high-z without imposing the prior on the faint-end/bright-end slope.
 
@@
 
+%% JFH I think another point worth mentioning is that the BOSS survey is never working at high completeness,
+%% (this you can quantify from your selection function). That means that the resevoir of QSOs that can
+%% scatter into or out of the sample is large, making one susceptible to errors in the selection function
+%% (or at the faint end variations in the photometric senstivity
+
 The imperfect match between SDSS and 2SLAQ (Figure~\ref{fig:mosaic})
@@
       \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
-      % gammapi.py -- draw_emissivity()
+      % gammapi.py -- draw_emissivity_18()
+      % gammapi.py -- draw_emissivity_21()
     \end{tabular}
@@
       blue]{2013A&A...551A..29P}, \citet[solid
-      cyan]{2016A&A...587A..41P}, and \citet[solid
-      blue]{2017A&A...608A..64C}}.
+      cyan]{2016A&A...587A..41P}, \citet[solid
+      blue]{2017A&A...608A..64C}, and \citet[brown]{2007A&A...472..443B}.}
   \label{fig:e912_2}
@@
 
-The smooth evolution of the luminosity function parameters apparant in
+The smooth evolution of the luminosity function parameters apparent in
 Figure~\ref{fig:evoln} suggests that it should be possible to describe
@@
 \citep{2015MNRAS.451.1892A}.  We present three such models in this
-paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
+paper.  These are shown in Figure~\ref{fig:evoln_global}.
+%% JFH Something is wrong with the flow here. You are referencing Figure 6, but have not yet discussed Figure 5. 
+The three
 models differ in the way they describe the evolution of the faint-end
@@
 \item In Model 1, for the parameters $\phi_*$, $M_*$ and $\alpha$ we
-  assume that the functions $f_i$'s in Equations~(\ref{eqn:global})
-  are Chebyshev polynomials in $(1+z)$.  Thus the functions $f_i$s are
+  assume that the functions $f_i$'s
+  %% JFH don't need the apostrophe s. 
+  in Equations~(\ref{eqn:global})
+  are Chebyshev polynomials in $(1+z)$.  Thus the functions $f_i$s
+  %% JFH This s should be here after f_i
+  are
   written as
@@
   Chebyshev polynomials in order to arrive at a good fit with the
-  data.  As we discuss below, we find that $\phi_*$, $M_*$ and
+  data.
+  %% JFH State that you assess this by eye
+  As we discuss below, we find that $\phi_*$, $M_*$ and
   $\alpha$ prefer quadratic, cubic, and linear evolutions in $(1+z)$.
+  %% JFH , respecitvely. 
   The faint-end slope $\beta$ seems to require a break in its
@@
   high redshift slopes of this evolution, with a break at redshift
-  $c_{3,2}$.  This is similar to the model of
+  $c_{3,2}$.
+  %% JFH Consider calling this z_3,2 
+  This is similar to the model of
   \citet{2007ApJ...654..731H}, who also favoured a broken power law
@@
   Table~\ref{tab:samples} are included while fitting this model.
+  %% JFH where was this discussed?? Nowhere have I seen explicitly stated in the
+  %% text which luminosity/redshift ranges you are excluding from the analysis in performing
+  %% these fits because you think they are systematics dominated. This just needs to be clearly stated.
+  %% Add this to the end of Section 3.2 after you discuss the systematics. State what is excluded and why.
+  %% It is perfectly fine if you do this by eye, just state that.
 
@@
   favoured evolution model.
+  %% JFH Do not put the discussion here. Add a separate discussion where you address the samples you leave out. Referencing them by
+  %% number here is also a bit annoying to me. Just state the samples with a name of the survey.
 
@@
 
-Figure~\ref{fig:mosaic_global} shows the three models in comparison
+%% JFH I'm lost. According to this discussion Model 1 and 2 treat the faint end slope with a broke power law, but your figures
+%% suggests that only the gray band Model 1 is using this double power law? What you are calling Model 2 appears to not be a double
+%% power law? Am I getting fooled by the shape of that green curve?
+
+Figure~\ref{fig:mosaic_global}
+shows the three
+%% JFH global 
+models in comparison
 with the binned fits from the previous section.  The shaded regions
@@
 although Model~1 performs better.
+%% JFH by eye model 1 performs better
 
@@
 uncertainty.  The model is in excellent agreement with the results of
-the fits in redshift bins discussed in the previous section.  The
+the fits in redshift bins discussed in the previous section.
+%% JFH Reference Figure 5 here as well.  
+The
 deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
-is again strikingly apparent.  So is the deviation of the SDSS and
+is again strikingly apparent.  So is
+%% JFH , as is the deviation
+the deviation of the SDSS and
 2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
 data selection discussion previously in Section~\ref{sec:bins}.
-Unfortunately, this model suffers with a remarkably sharp break in the
+Unfortunately, this model suffers
+%% JFH suffers from 
+with a remarkably sharp break in the
 evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
@@
 symbols show the best-fit values with one-sigma uncertainties from the
-double power law fits to the data in redshift bins.  Solid curves and
+double power law fits to the data in redshift bins.
+%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
+%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
+%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
+Solid curves and
 shaded regions show the global models.  This number density evolution
 again highlights the systematic error in data at $z\sim 3$.  The
-number density of AGN down to the limit of spectroscopic data
+number density of AGN down to the limit of
+%% JFH the deepest spectroscopic surveys 
+spectroscopic data
 ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
-density rapidly increases at low redshifts and then drops gradually at
+density rapidly increases
+%% JFH I think you mean decreases here
+at low redshifts and then drops gradually at
 high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
@@
 which spectroscopic data exist, $M_*<-21$, the number density of qsos
-peaks at $z\sim 1$.  However, the difference between our three models
+peaks at $z\sim 1$.
+%% JFH The figure is not consistent with this statement. The model showing M < 21 is peaking
+%% just below z = 2. 
+However, the difference between our three models
 is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
@@
 steepening of the faint-end slope in this model at this redshift.
+%% JFH Reference lower right panel of figure 6 here. 
 Figure~\ref{fig:rhoqso} reveals another property of these models: when
 extrapolated, the AGN number density diverges in all three models at
-high redshifts.  This is result of the steep faint-end slope at high
+high redshifts.
+%% JFH I think this is just an artifiact of your fitting procedure,
+%% i.e. that these polynomial coefficients are unconstrained at really
+%% high-z. Do these fits include the banados and MOrtlock quasars? In
+%% that case the divergence should not occur, at least for the
+%% brightest bin.  Furthermore, if you would make this plot with the
+%% data instead of of integrating fits, you would be able to plot
+%% those objects on here as well.
+This is result of the steep faint-end slope at high
 redshifts combined with the rapid brightening of the break luminosity.
@@
 
+%% JFH My main feedback on this section is that you need to elaborate more on which samples you included and excluded and why. That
+%% is fine if it is all based on by eye discarding things. We need to make the point more clearly that the various surveys suffer
+%% systematics, and hence cannot yet really be combined to give a sensible global evolution without some kind of massaging or choices
+%% about which datasets to trust.
+
 \section{Contribution of AGN to reionization}
 \label{sec:reion}
+
+%% JFH I think you could possibly break of this last section as a separate letter. The paper above would just be a data analysis and
+%% compilation paper.
 
@@
 average \HeIII\ fraction.
-
+%% JFH Mention low-z UVB here as well in intro. 
 \subsection{Hydrogen-ionizing emissivity}
@@
 quasars considered by \citet{2004ApJ...615..135S} are fainter
-($M_i(z=2)>-26$) than those considered by \citet{2015MNRAS.449.4204L},
+($M_i(z=2)>-26$)
+%% JFH Something is wrong with this faint number here. The bulk of the scott sample I thought was much fainter than this.
+%% Ask Gabor? 
+than those considered by \citet{2015MNRAS.449.4204L},
 which suggest that faint quasars may have a steeper EUV spectrum.  We
@@
 panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
+%% JFH Figure 8 is a nightmare to look at. You need to separate this into multiple
+%% figures somehow. Perhaps one with curves and one with points. 
 Redshift bins that were removed from analysis due to large systematic
@@
 $\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
-and decreased rapidly towards high redshifts.  A continuous
+and decreased
+%% JFH decreases 
+rapidly towards high redshifts.  A continuous
 description of this emissivity evolution is valuable in deriving the
@@
 such a description.  Unfortunately, as discussed above, all of these
-models suffer from pathologies such as non-monotonic or divergent AGN
+models suffer from pathologies such as non-monotonic or divergent
+%% JFH divergence is just becuase of how you do the fits, and not having data at high-z. I don't think
+%% that should be highlighted. 
+AGN
 number densities, likely resulting from residual systematic errors in
@@
 for $M_{1450}<-21$.
+
+%% JFH So if I understand correctly you have given up on the global model and are now doing things
+%% with the binned fits, since your global model produces weird non-monotonic behavior. You need to state
+%% what you are doing here, so the reader understands where these data points come from on the plot.
 
@@
 luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
-limite by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
+limite
+%% JFH limite --> limit 
+by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
 is $0.01L_*$.  Using a limit that depends on the break luminosity is
@@
 values.  Even when these samples are homogeneized appropriately, have
+%% JFH adopting such an integratino limit....
 such an integration limit is likely only justified if the faint-end
@@
 determinations from the luminosity function derived from a
-variability-selected sample observed using the Sloan telescope and the
+variability-selected sample observed using the Sloan
+%% JFH Sloan telescopee --> SDSS telescope
+telescope and the
 Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
@@
 smooth.  This model agrees with our $M_{1450}<-18$ result to a better
-degree relative to the \citet{2013A&A...551A..29P} model, bjt it
+degree relative to the \citet{2013A&A...551A..29P} model, bjt
+%% JFH bjt --> but
+it
 results in a higher emissivity in the $M_{1450}<-21$ case.
@@
 throughout the redshift range of their data.
+
+%% JFH For the Palanque and Caditz etc. comparisons, it occurs to me that these guys
+%% probably used the luminosity function and not the epsilon_912. I'm just wondering why you
+%% choose to do the comparisons in this quantity if other authors didn't compute this quantity. I understand
+%% that one is the integral of the other, but it would seem more sensible to me to compare to the Palangue-luminosity
+%% function when you discuss the individual fits to luminosity functions in say their same redshift bins, then when you
+%% compute the emissivity evolution here. This just seems out of place. I think comparing to other peoples emissivities
+%% here is sensible, but integrating other peoples lum functions here is less transparent.
 
@@
 contribution of helium to the opacity.)  We assume the \HI\ column
-density distribution given by \citet{2012ApJ...746..125H}.  The
+density distribution given by \citet{2012ApJ...746..125H}.
+%% JFH elaborate on this. Say it is chosen to reproduce Worseck's MFP measurements
+%% and that it sensible extrapolate or something. You need to make it clear that it is indeed
+%% Gabors MFP that you are using here. 
+The
 \HI\ photoionization rate is then given by
@@
 \end{equation}
-where $\sigma$ is the photoionization cross-section.  We assume an
+where $\sigma$ is the photoionization cross-section.
+%% JFH Is it obvious that the uncertaintites in the MFP which propagate into the HM fit for the column density
+%% distribution do not matter? If so this needs to be explicitly stated. 
+We assume an
 upper limit of $z=15$ while integrating Equation~(\ref{eqn:flux}).
@@
 derived from the Lyman-$\alpha$ forest, and the measurements by
-\citet{2011MNRAS.412.2543C} from quasar proximity zones.  For an
+\citet{2011MNRAS.412.2543C} from quasar proximity zones.
+%% JFH Please add the data from this paper by Davies:
+%% http://adsabs.harvard.edu/cgi-bin/nph-ref_query?bibcode=2018ApJ...855..106D&amp;refs=CITATIONS&amp;db_key=AST
+For an
 integration limit of $M_{1450}=-21$ the AGN contribution to the
@@
 % Kollmeier number of ~10 times higher than HM12 in figure.
+
+%% JFH I disagree with your approach here. It is not interesting to simply extrapolate your z > 0.6 to these
+%% redshifts in my opinion, when you have the ability to fit them or at least to show the binned fits if you cannot
+%% get a global model to work. Why is it interesting to write an entire section on an extrapolation?
 
@@
 
+%% JFH I think these next two paragraphs here needs to be shortened considerably.
+%% You are spending way to to much time and text discussing the literature. 
 In Figure~\ref{fig:qhe}, we also show the reionization histories from
@@
 
+%% JFH Make some figure references below to remind the reader of where these
+%% results are. Also some people just jump to conclusions so they need to know where to look. 
 We find that the UV luminosity function of AGN prefers a double power
@@
 
+%% JFH Figure references here as well. 
 An important finding of this work is that there are severe systematic
@@
   \begin{center}
+    % bins_withg.py
+    % drawlf_giallongocompare.py 
     % giallongo_compare.py 

### 2018-06-07 data.py
Update style
One colour per sample.  Bigger legend fontsize.

@@ -63,7 +63,7 @@ def plot_data(data):
     # colorbrewer2.org.
     cs = [u'#1f77b4', u'#ff7f0e', u'#2ca02c', u'#d62728', u'#9467bd',
           u'#8c564b', u'#e377c2', u'#7f7f7f', u'#bcbd22', u'#17becf',
-          u'#77ab31', u'#d8b365', u'#cc7af4', u'#f66bad']
+          u'#77ab31']#, u'#d8b365']#, u'#cc7af4', u'#f66bad']
 
     d = [x.z for x in data]
     l = [x.label for x in data]
@@ -101,7 +101,7 @@ def plot_data(data):
     plt.ylim(7e-1, 1.0e4)
     plt.xlim(0., 8.)
 
-    plt.legend(loc='upper right', fontsize=10, handlelength=3,
+    plt.legend(loc='upper right', fontsize=12, handlelength=3,
                frameon=False, framealpha=0.0, labelspacing=.1,
                handletextpad=0.4, borderpad=0.2,markerscale=.5)
 
@@ -113,14 +113,14 @@ data = []
 
 f = ['Data_new/dr7z2p2_sample.dat',
      'Data_new/dr7z3p7_sample.dat']
-l = r'SDSS DR7 Schneider et al.\ 2010'
+l = r'SDSS DR7 Schneider et al.\ (2010)'
 s = sample(f, label=l)
 s.z = s.z[s.z<4.7]
 data.append(s)
 
 f = ['Data_new/croom09sgp_sample.dat',
      'Data_new/croom09ngp_sample.dat']
-l = r'2SLAQ NGP+SGP Croom et al.\ (2009)'
+l = r'2SLAQ Croom et al.\ (2009)'
 s = sample(f, label=l)
 s.z = s.z[s.z<2.2]
 data.append(s)
@@ -159,30 +159,31 @@ l = r'CANDELS GOODS-S Giallongo et al.\ (2015)'
 s = sample(f, label=l)
 data.append(s)
 
-f = ['Data_new/jiang16main_sample.dat']
-l = r'SDSS Main Jiang et al.\ (2016)'
+f = ['Data_new/jiang16main_sample.dat', 'Data_new/jiang16overlap_sample.dat', 'Data_new/jiang16s82_sample.dat']
+l = r'SDSS Jiang et al.\ (2016)'
 s = sample(f, label=l)
 data.append(s)
 
[…]

### 2018-06-07 Paper/paper.tex
Stop saying "best-fit"

@@
     selected number of AGN is shown outside parentheses.  In each
-    redshift bin, the black curve shows the best-fit double power law
-    model, which is represented by the median of the posterior
+    redshift bin, the black curve shows our fiducial double power law
+    model fit, which is represented by the median of the posterior
     probability distribution function.  The grey shaded area shows the
@@
   % bins_tabulate.py; Nqso added by hand
-  \caption{Best-fit double power law luminosity function parameters in
+  \caption{Derived double power law luminosity function parameters in
     various redshift bins.  The luminosity function parameters
@@
 %% something like that. I would just explain waht you plot. 
-The posterior median
-is shown as the best-fit model at each redshift, while the grey shaded
-region shows the one-sigma (68.26\%) uncertainty.  Consistent with
-previous studies, the double power law model provides an excellent
-description of the luminosity function model over almost the complete
-range of redshifts spanned by the data.  It is only in the highest
-redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
-power law.  In this bin, the resultant posterior distribution of the
-break magnitude $M_*$ is bimodal with favoured values at the faint
-($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
-literature the $z\sim 6$ AGN have been assumed to lie on the bright
-end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
-comparison with the luminosity function at lower redshifts ($z<5.5$)
-suggests that these AGN should instead be understood to describe the
-faint-end of a double power law.
+The posterior median is shown as our adopted model at each redshift,
+while the grey shaded region shows the one-sigma (68.26\%)
+uncertainty.  Consistent with previous studies, the double power law
+model provides an excellent description of the luminosity function
+model over almost the complete range of redshifts spanned by the data.
+It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
+seem to favour a single power law.  In this bin, the resultant
+posterior distribution of the break magnitude $M_*$ is bimodal with
+favoured values at the faint ($M_*>-18$) and bright end of the data
+($M_*<-30$).  While in the literature the $z\sim 6$ AGN have been
+assumed to lie on the bright end of the luminosity function
+\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
+function at lower redshifts ($z<5.5$) suggests that these AGN should
+instead be understood to describe the faint-end of a double power law.
 %% JFH Okay so you need to be more clear here that what you mean is that the trend
@@
 
-%% JFH I think you need to show at least one corner plot for your fits somewhere in the paper.
-
 %% JFH I think before imposing this prior by hand it might be useful to show the degeneracies that
@@
     binned luminosity functions.  In each redshift bin, yellow curves
-    show the best-fit double power law luminosity function in that
-    redshift bin.  Other curves show the three global evolution
+    show our fiducial double power law luminosity function model in
+    that redshift bin.  Other curves show the three global evolution
     models.  Shaded regions show the one-sigma (68.26\%)
@@
   \caption{Luminosity function parameter evolution in the global
-    models.  The symbols show the best-fit parameters with one-sigma
-    (68.26\%) uncertainties in redshift bins from
-    Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected by
-    systematics and removed from the global analysis are shown in
+    models.  The symbols show the posterior median values of
+    parameters with one-sigma (68.26\%) uncertainties in redshift bins
+    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
+    by systematics and removed from the global analysis are shown in
     grey.  In each panel, the solid curves and shaded regions show the
-    three best-fit global models with one-sigma uncertainties.
-    Model~1 provides a better fit, but requires a rapid change in the
+    three derived global models with one-sigma uncertainties.  Model~1
+    provides a better fit, but requires a rapid change in the
     faint-end slope at $z\sim 3.5$.}
@@
     $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
-    show the estimates from the best-fit double power law luminosity
-    functions in various redshift bins, with vertical error bars
-    denoting one-sigma (68.26\%) uncertainties.  Open circles show the
-    same in redshifts bins affected by systematics.  Curves show the
-    estimated density from the global models, with the accompanying
-    shaded regions denoting the one-sigma uncertainty. }
+    show the estimates from the our fiducual double power law
+    luminosity function models in various redshift bins, with vertical
+    error bars denoting one-sigma (68.26\%) uncertainties.  Open
+    circles show the same in redshifts bins affected by systematics.
+    Curves show the estimated density from the global models, with the
+    accompanying shaded regions denoting the one-sigma uncertainty. }
   \label{fig:rhoqso}
@@
     high systematic errors.  Solid red curves in both panels show the
-    best fit emissivity evolution model, with the shaded area showing
-    the one-sigma (68.26\%) uncertainty.  Also shown for comparison in
-    both panels are models by \citet[pentagon
+    derived posterior median emissivity evolution model, with the
+    shaded area showing the one-sigma (68.26\%) uncertainty.  Also
+    shown for comparison in both panels are models by \citet[pentagon
       symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
@@
       cyan]{2016A&A...587A..41P}, \citet[solid
-      blue]{2017A&A...608A..64C}, and \citet[brown]{2007A&A...472..443B}.}
+      blue]{2017A&A...608A..64C}, and
+    \citet[brown]{2007A&A...472..443B}.}
   \label{fig:e912_2}
@@
 models capture the steepening of the faint end of the luminosity
-function towards higher redshifts.  The best-fit form of Model~1 is
-shown by the black curves in Figure~\ref{fig:evoln_global}.  The
-accompanying grey shaded area depicts the one-sigma (68.26\%)
-uncertainty.  The model is in excellent agreement with the results of
-the fits in redshift bins discussed in the previous section.
+function towards higher redshifts.  The adopted posterior median form
+of Model~1 is shown by the black curves in
+Figure~\ref{fig:evoln_global}.  The accompanying grey shaded area
+depicts the one-sigma (68.26\%) uncertainty.  The model is in
+excellent agreement with the results of the fits in redshift bins
+discussed in the previous section.
 %% JFH Reference Figure 5 here as well.  
@@
 are shown in Figure~\ref{fig:evoln_global} by the green and orange
-curves, respectively.  The corresponding best-fit parameter values are
+curves, respectively.  The corresponding parameter values are
 tabulated in Table~\ref{tab:global}.
@@
 down to different limits.  Similar to Figure~\ref{fig:evoln_global},
-symbols show the best-fit values with one-sigma uncertainties from the
+symbols show the posterior median values with one-sigma uncertainties from the
 double power law fits to the data in redshift bins.
@@
 \begin{table}
-  \caption{Best-fit luminosity function evolution models.  These
+  \caption{Derived luminosity function evolution models.  These
     parameters are defined in Equations~(\ref{eqn:cbs}) and
@@
 shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
-the emissivity in each bin.  The resultant best-fit curves and the
+the emissivity in each bin.  The resultant curves and the
 corresponding one-sigma uncertainties are shown in
 Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
-912\,\AA\ emissivities in various redshift bins and in these best-fit
-models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
+912\,\AA\ emissivities in various redshift bins and in these 
+models are tabulated in Appendix~\ref{sec:tables}.  The adopted
 form of Equation~\ref{eqn:e912fit} is given by
@@
 Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
-Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Martin Haehnelt, Paul
-Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Donald Lynden-Bell,
-Roberto Maiolino, Richard McMahon, Daniel Mortlock, Ewald Puchwein,
-Gordon Richards, Alberto Rorai, Bram Venemans and Stephen Warren.  GK
-acknowledges support from ERC Advanced Grant 320596 `The Emergence of
-Structure During the Epoch of Reionization'.
+Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
+Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
+Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
+Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
+Venemans and Stephen Warren.  GK acknowledges support from ERC
+Advanced Grant 320596 `The Emergence of Structure During the Epoch of
+Reionization'.
 %% Joe, do you need to add anything to acknowledgements?
@@
 \appendix
+
+\section{Posterior distributions}
+
+Figure~\ref{fig:corner} shows marginalised one-dimensional and
+two-dimensional posterior probability distribution functions (PDFs) of
+the four parameters, $\phi_*$, $M_*$, $\alpha$ and $\beta$, of the
+double-power-law luminosity function in the $3.7\leq z < 4.1$ redshift
+bin.  The procedure adopted for fitting this model is described in
+Section~\ref{sec:bins}.  Figure~\ref{fig:corner} illustrates that the
+four parameters are well-constrainted.  This figure also shows the
+degeneracies between the parameters.  There is a relatively strong
+correlation between the amplitude of the luminosity function $\phi_*$
+and the break magnitude $M_*$.  The faint-end slope $\beta$ is
+positively correlated with the other three parameters.  Similar
+behaviour of the posterior distributions is seen in all the redshift
+bins defined in Section~\ref{sec:bins}.  In our highest-redshift bin
+($5.5\leq z < 6.5$), we impose a prior $\alpha < -4$, which changes
+the posterior distributions.  However, various parameter correlations
+remain qualitatively unchanged.
+
+\begin{figure*}
+  \begin{center}
+    % corner.corner() with bins.lfs[-4]
+    \includegraphics[width=\textwidth]{corner_z3p9.pdf}
+  \end{center}
+  \caption{Posterior distributions of the four double-power-law
+    parameters in the $3.7\leq z < 4.1$ redshift bin.  The blue
+    squares indicate median values.  Similar behaviour of the
+    posterior distributions is seen in all other redshift bins defined
+    in Section~\ref{sec:bins}.
+    \label{fig:corner}}
+\end{figure*}
 
@@
   \caption{Effect of the 19 AGN reported by \citet{2015AA...578A..83G}
-    on the best-fit double power law luminosity function parameters in
+    on the double power law luminosity function parameters in
     redshift bins from $z=0$ to $7$.  Black points show parameter
@@
   \caption{Luminosity functions in three redshift bins at $z>4.1$.
-    Black curves in each panel show the best-fit double power law,
+    Black curves in each panel show the double power law,
     with the corresponding one-sigma (68.26\%) uncertainty shown by

### 2018-06-08 Paper/paper.tex
Update Section 1

@@
 interest of a large body of work over the last four decades
-\citep[e.g.,][]{1978A&A....68...17M, 1983ApJ...269..352S,
-  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
-  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
-  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
-  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
-  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
-  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
-  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J,
-  2017MNRAS.466.1160M}.  Determination of the AGN luminosity function
-constrains models of the build-up of supermassive black holes
-\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.
-%% JFH Some historical papers should be cited for this SMBH buildup point, like
-%% for example Soltan. 
-Due to the
-incidence of supermassive black holes in most galaxies, the tight
-scaling relations observed to exist between the mass of these black
-holes and properties of their host galaxies
-\citep{2013ARA&A..51..511K, 2013ApJ...764..184M}, and the increasing
-consensus that AGN activity feeds back on the host galaxy evolution,
-the AGN luminosity function also constrains models of galaxy
-formation.  Finally, thanks to their relative brightness and high
-Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
-determines their influence on the temperature and ionization state of
-the intergalactic medium (IGM) over large scales,
-%% JFH Probably want to say something here about radiation background
-%% instead of this ``large scales'' 
-possibly even
-primarily driving hydrogen and helium reionization.
+\citep{1978A&A....68...17M, 1983ApJ...269..352S, 1988ApJ...325...92K,
+  1988MNRAS.235..935B, 1993ApJ...406L..43H, 1994ApJ...421..412W,
+  1995AJ....110...68S, 1995AJ....110.2553K, 1995ApJ...438..623P,
+  2000MNRAS.317.1014B, 2001AJ....121...54F, 2004AJ....128..515F,
+  2006AJ....131.2766R, 2007ApJ...654..731H, 2009MNRAS.392...19C,
+  2010AJ....139..906W, 2011ApJ...728L..26G, 2013ApJ...773...14R,
+  2013ApJ...768..105M, 2015AA...578A..83G, 2015ApJ...798...28K,
+  2016ApJ...829...33Y, 2016ApJ...833..222J}.  Determination of the AGN
+luminosity function constrains models of the build-up of supermassive
+black holes \citep{1982MNRAS.200..115S, 2004ApJ...602..603Y,
+  2007ApJ...654..731H, 2008ApJ...679..118S, 2009A&A...493...55E,
+  2000ApJ...531...42H, 2010MNRAS.401.2531A, 2013ApJ...773...14R,
+  2014ApJ...787...73D, 2015MNRAS.448.3603D, 2015MNRAS.452..575S,
+  2016MNRAS.462..190R}.  Due to the incidence of supermassive black
+holes in most galaxies, the tight scaling relations observed to exist
+between the mass of these black holes and properties of their host
+galaxies, and the increasing consensus that AGN activity feeds back on
+the host galaxy evolution, the AGN luminosity function also constrains
+models of galaxy formation \citep{2006ApJ...650...42L,
+  2008MNRAS.385.1846M}.  Finally, thanks to their relative brightness
+and high Lyman-continuum (LyC) escape fractions, the luminosity
+function of AGN determines their contribution to the radiation
+background that influences the temperature and ionization state of the
+intergalactic medium (IGM), possibly even primarily driving hydrogen
+and helium reionization in the last twelve billion years
+\citep{2012ApJ...746..125H, 2015AA...578A..83G, 2017ApJ...847L..15O,
+  2018MNRAS.474.2904P, 2018arXiv180104931P}.
 
 There is a renewed interest in understanding the evolution of the UV
-luminosity function of AGN, triggered by the 19 low-luminosity
-($M_{1450}>-22.6$)
-%% JFH Probably more sensible to quote a luminosity range rather than just a > 
-AGN candidates between redshifts $z=4.1$ and $6.3$
-discovered by \citet{2015AA...578A..83G} using a novel X-ray/NIR
-selection criterion.  This finding suggested that AGN brighter than
-$M_{1450}=-18$ can potentially produce all of the metagalactic
-hydrogen photoionization rate inferred from the \lya forest at
-$4<z<6$.
-%% JFH Probably should say something here about assuming all ionizing photons escape, since these
-%% are galaxy like luminosities. Maybe quote L_star galaxy for comparison, which helps with your next
-%% point about faint galaxies. 
-A significant presence of AGN at high redshift ($z\sim 6$)
-and a dominant contribution of AGN to reionization is appealing as the
-LyC escape fraction of galaxies is uncertain.  High-redshift galaxies
-down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
-10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and redshifts up to
-$z=11.1$ \citep{2016ApJ...819..129O} have now been reported.  But the
-escape of LyC photons has been measured in only a few comparatively
-bright ($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).
-The escape fraction in these galaxies is inferred to be typically
-about 2--20\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
-  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
-  2017MNRAS.468..389J, 2017MNRAS.465..316M}, whereas reionization
-requires escape fraction of about 20\% in galaxies as faint as
-$M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F, 2015ApJ...802L..19R,
-  2016MNRAS.457.4051K}.  An enhanced incidence of high-redshift AGN
-may also be consistent with the shallow bright-end slopes of the
-$z\sim 7$ UV luminosity function of galaxies relative to a Schechter
-function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
-  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
-these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
-  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
-explanation for the large scatter in the \lya opacity between
-different quasar sightlines close to redshift $z=6$
-\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
+luminosity function of AGN, triggered by the discovery of 19
+low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
+redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
+novel X-ray/NIR selection criterion.  This finding suggested that if
+100\% LyC escape fraction is assumed AGN brighter than $M_{1450}=-18$
+can potentially produce all of the metagalactic hydrogen
+photoionization rate inferred from the \lya forest at $4<z<6$, despite
+the fact that these AGN are fainter than the brightest star-forming
+galaxies at these redshifts.  (The UV luminosity function of galaxies
+at $z=6$ has $M^*_{1450}\sim -20$.)  A significant presence of AGN at
+high redshift ($z\sim 6$) and a dominant contribution of AGN to
+reionization is appealing as the LyC escape fraction of galaxies is
+uncertain.  High-redshift galaxies down to rest-frame UV magnitude
+$M_\mathrm{UV}=-12.5$ ($L\sim 10^{-3}L^*$) at $z=6$
+\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
+\citep{2016ApJ...819..129O} have now been reported.  But the escape of
+LyC photons has been measured in only a few comparatively bright
+($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).  The
+escape fraction in these galaxies reveals a broad distribution from
+less than 2\% to more than 80\% \citep{2010ApJ...725.1011V,
+  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
+  2016A&A...585A..48G, 2017MNRAS.468..389J, 2018arXiv180506071S,
+  2018arXiv180601741F, 2018arXiv180511621M, 2018arXiv180303655C}, but
+the average escape fraction is typically lower than 20\%.  Statistical
+constraints from \HI\ column density measurements in gamma-ray burst
+(GRB) afterglow spectra suggest an even lower escape fraction of 0.5\%
+\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
+This is a challenge for reionization models, which require an escape
+fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
+\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
+An enhanced incidence of high-redshift AGN may also be consistent with
+the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
+of galaxies relative to a Schechter function
+\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
+  2015MNRAS.452.1817B} and the hard spectra of these galaxies
+\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
+Finally, AGN may also provide a natural explanation for the large
+scatter in the \lya opacity between different quasar sightlines close
+to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
 %% JFH Please cite new paper by eilers et al. here, not yet on archive. 
-These opacity
-fluctuations extend to substantially larger scales ($\gtrsim 50\,
-h^{-1}$cMpc) than expected in galaxies-dominated reionization models
-\citep{2015MNRAS.453.2943C}.
-%% JFH You probably need a ``but see Davies et al. 201X'' since Fred claims
-%% he can explain these fluctuations with galaxies. See also the new paper with George Becker and Fred. 
-AGN clustering can result in these
+These opacity fluctuations extend to substantially larger scales
+($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxies-dominated
+reionization models (\citealt{2015MNRAS.453.2943C}; although see
+\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
+  2018arXiv180308932B}).  AGN clustering can result in these
 fluctuations naturally if there is a significant contribution
@@
 
-Several counter-arguements against a higher incidence of AGN at high
+Several counter-arguments against a higher incidence of AGN at high
 redshift have also been made. \citet{2017MNRAS.468.4691D} and
-\citet{2018MNRAS.473.1416M} pointed out that an AGN population
-consistent with the findings of \citet{2015AA...578A..83G} leads to a
-much earlier \HeII\ reionization.  For instance, in the model of
-\citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
-at $z=4.5$, compared to $z=3$ in the standard scenario
-\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization could
+\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
+density of AGN at $z\sim 6$ can lead to a much earlier
+\HeII\ reionization.  For instance, He~\textsc{ii} reionization is
+complete at $z=4.5$ in the model of \citet{2015ApJ...813L...8M},
+compared to $z=3$ in the standard scenario
+\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
 result in higher IGM temperatures due to the associated photoheating.
@@
 hydrogen-ionizing photons that is required to explain the Ly$\alpha$
-opacity fluctuations.
-%% JFH Probably need to clarify for this last point that you mean in a situation
-%% where galaxies contribute no LL photons, and QSOs completely dominate. 
-Further arguments against AGN-dominated
-reionization have been presented by \citet{2016MNRAS.459.2299F} by
-analysing the incidence of metal-line absorbers at $z\sim 6$.
+opacity fluctuations.  Further arguments against AGN-dominated
+reionization have been presented by \citet{2016MNRAS.459.2299F}, who
+analysed the simulations of metal-line absorbers at $z\sim 6$.
 \citet{2016MNRAS.459.2299F} find that in their cosmological radiation
@@
 many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
-C~\textsc{ii} at $z\sim 6$.  However, these simulations assume a
-$L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
+C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
+assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
 \citep{2002ApJ...565..773T}, which somewhat harder than recent
 measurements ($L_\nu\propto\nu^{-1.7}$) by
-\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also found
-that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
-measurements prefer a harder and more intense $>4$~Ry background than
-the standard model \citep{2012ApJ...746..125H}.  Finally, comparing
-the \citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
-$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
-the AGN UV luminosity function at $z\sim 6$ is probably shallower that
-that reported by \citet{2015AA...578A..83G}.
-\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
-the results of \citet{2015AA...578A..83G} could be explained by
-contamination from the AGN host galaxies for faint AGN.
-
-While a straightforward way towards a more robust understanding of AGN
+\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
+relative to the the standard model \citep{2012ApJ...746..125H}, the
+observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
+measurements seem to require a harder and more intense $>4$~Ry
+background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
+to X-ray-selected quasar data at $z=0$--$6$,
+\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
+luminosity function at $z\sim 6$ is probably shallower that that
+reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
+argue that the apparent contradiction with the results of
+\citet{2015AA...578A..83G} could be explained by contamination from
+the AGN host galaxies for faint AGN.
+
+%---
+
+A straightforward way towards a more robust understanding of AGN
 contribution to reionization is to determine the evolution of the AGN
-UV luminosity function, many recent inferences of the luminosity
-function suffer from inconsistencies arising from inhomogeneous
-selection and mixing of AGN data.  This has resulted in a large
-scatter in the inferred high-redshift hydrogen-ionizing AGN emissivity
-between various recent studies.  For instance, there is an order of
-magnitude scatter between various estimates of the hydrogen-ionizing
-AGN emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
-  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
-  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O,
-  2017MNRAS.466.1160M}.  Our aim in this paper is to address this
+UV luminosity function.  However, many recent inferences of the
+luminosity function suffer from inconsistencies arising from
+inhomogeneous selection and mixing of AGN data.  This has resulted in
+a large scatter in the inferred high-redshift hydrogen-ionizing AGN
+emissivity between various recent studies.  For instance, there is an
+order of magnitude scatter between various estimates of the
+hydrogen-ionizing AGN emissivity at $z=5$--$6$
+\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
+  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
+  2017ApJ...847L..15O}.  Our aim in this paper is to address this
 issue, by constructing an AGN sample with robust redshift and
@@
 reionization.  We summarise our findings in Section~\ref{sec:conc}.
+
+-- some people use photo-zs
+-- some people mix binned data
+-- some people fix slopes
+-- some people exclude some data arbitrarily
 
@@
 while the grey shaded region shows the one-sigma (68.26\%)
-uncertainty.  Consistent with previous studies, the double power law
-model provides an excellent description of the luminosity function
-model over almost the complete range of redshifts spanned by the data.
-It is only in the highest redshift bin ($z=5.5$--$6.5$) that the data
-seem to favour a single power law.  In this bin, the resultant
-posterior distribution of the break magnitude $M_*$ is bimodal with
-favoured values at the faint ($M_*>-18$) and bright end of the data
-($M_*<-30$).  While in the literature the $z\sim 6$ AGN have been
-assumed to lie on the bright end of the luminosity function
-\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
-function at lower redshifts ($z<5.5$) suggests that these AGN should
-instead be understood to describe the faint-end of a double power law.
+uncertainty\footnote{Throughout this paper, we adopt the posterior
+  median and the equal-tailed 68.26\% credible interval as our model
+  fit and its one-sigma uncertainty.}.  Consistent with previous
+studies, the double power law model provides an excellent description
+of the luminosity function model over almost the complete range of
+redshifts spanned by the data.  It is only in the highest redshift bin
+($z=5.5$--$6.5$) that the data show a weak preference for a single power law.
+%% In
+%% this bin, the resultant posterior distribution of the break magnitude
+%% $M_*$ is bimodal with favoured values at the faint ($M_*>-18$) and
+%% bright end of the data ($M_*<-30$).
+While in the literature the
+$z\sim 6$ AGN have been assumed to lie on the bright end of the
+luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a comparison
+with the luminosity function at lower redshifts ($z<5.5$) suggests
+that these AGN should instead be understood to describe the faint-end
+of a double power law.
 %% JFH Okay so you need to be more clear here that what you mean is that the trend
@@
     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
-    % mosaic.py 
+    % mosaic_selected.py and drawlf_selected.py 
   \end{center}

### 2018-06-11 Paper/paper.tex
Update text
Gabor's input.

@@
   various fitting functions, luminosity function analysis codes, and
-  homogenized AGN data publicly available.
+  homogenised AGN data publicly available.
 \end{abstract}
@@
 
--- some people use photo-zs
--- some people mix binned data
--- some people fix slopes
--- some people exclude some data arbitrarily
+%% -- some people use photo-zs
+%% -- some people mix binned data
+%% -- some people fix slopes
+%% -- some people exclude some data arbitrarily
 
@@
 \subsection{Sample Selection}
-
-We started with
-%% JFH we started with --> we started by
-compiling the samples of recent photometric rest-frame UV-optical
+\label{sect:samplesel}
+
+We started by compiling the samples of recent photometric rest-frame UV-optical
 quasar surveys. The restriction to UV-optical surveys was mainly
@@
 \begin{enumerate}
-\item Spectroscopic redshifts for the vast majority of targets.
-  %% JFH Did we actually use any photometric redshifts? If not, I would omit this ``Vast majority'' and make
-  %% it more definite. 
+\item High spectroscopic completeness of the target sample.
 \item Accurate rest-frame UV-optical CCD photometry.
 \item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
-\item A characterised selection function.
-  %% JFH well characterized
+\item A well-characterised selection function.
 \end{enumerate}
@@
 survey selection functions in electronic form, either from the
-publication or
-%% JFH by request 
-from the authors. As a reference for future surveys we
-publish them here
+publication or by request from the authors. As a reference for future surveys we
+make them electronically available here
 %% JFH rather than publish them here say ``we make them electronically available here''. Cite an appendix where
@@
 uncertainties in the correction for host galaxy light
-%% JFH What is Croom the reference for here, host galaxy contamination or the 2SLAQ sample. You basically
-%% need a reference for 2SLAQ and it appears in the wrong place here. 
-\citep{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 11,816
+\citep[detailed in][]{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 9365
 $g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint
-near the North Galactic Pole (NGP, 8153 quasars in $127.7$\,deg$^2$)
-and the South Galactic Pole (SGP, 3663 quasars in
-$64.2$\,deg$^2$). The small sample overlap between SDSS and 2SLAQ (112
+near the North Galactic Pole (NGP, 7027 quasars in $127.7$\,deg$^2$)
+and the South Galactic Pole (SGP, 2338 quasars in
+$64.2$\,deg$^2$). The small sample overlap between SDSS and 2SLAQ (102
 quasars) has negligible impact on the QLF evaluation.
-%% JFH Maybe state what the 2SLAQ survey goal was re quasars.
 
@@
 the QLF we used the 99 quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} that have $M_{1450}<-26.73$ in our adopted
+\citep{2016ApJ...829...33Y} that have $M_{1450}\le -26.73$ in our adopted
 cosmology.  For these 99 quasars selected from 14,555\,deg$^2$ we
@@
 DR7 sample from \citet{2013ApJ...768..105M}, so to avoid
-double-counting quasars we used the latter sample only at $M_{1450}\ge
--26.73$, yielding 104 additional $4.7\le z<5.5$ quasars selected in
+double-counting quasars we used the latter sample only at
+$M_{1450}>-26.73$, yielding 103 additional $4.7\le z<5.5$ quasars selected in
 6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection function from
@@
 faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82
-survey (62 uniformly selected $4.7\le z<5.5$ quasars in 235\,deg$^2$)
+survey (59 uniformly selected $M_{1450}>-26.73$ $4.7\le z<5.5$ quasars in 235\,deg$^2$)
 and two $4.7\le z<5.5$ quasars from \citet{2011ApJ...728L..26G},
@@
 The SDSS colours of $5.1<z<5.5$ quasars are similar to those of M and
-L dwarf stars, resulting in a low and uncertain selection efficiency
+L dwarf stars, resulting in a low and uncertain completeness
 \citep{2013ApJ...768..105M}. WISE mid-infrared selection performs
@@
 end of the quasar population. Unlike \citet{2013ApJ...768..105M} we
-include the 9 uniformly selected $M_{1450}\ge -26.73$ SDSS DR7 quasars
+include the 9 uniformly selected $M_{1450}>-26.73$ SDSS DR7 quasars
 and the 10 SDSS Stripe~82 quasars at $z>5.1$, adopting their low
-selection efficiency.
-%% JFH efficiency and completeness are two different things and you seem to be conflating
-%% the two concepts here. 
-As we will show in Section~3.2, the resulting
+completeness. As we will show in Section~3.2, the resulting
 QLF is consistent with those at lower and higher redshifts, indicating
@@
 
-At the highest redshifts $z>6.5$ we considered two quasars found by
-\citet{2011Natur.474..616M} and \citet{2015ApJ...801L..11V} in UKIDSS
-imaging (3370\,deg$^2$)
-%% JFH quote the individual redshifst of the mortlock and venemans objects
-, in addition to the current highest-redshift
-quasar at $z=7.54$ selected from a combination of UKIDSS, WISE and
-DECaLS \citep[$\sim 2500$\,deg$^2$, ][]{2018Natur.553..473B}. Although
+At the highest redshifts $z>6.5$ we considered ULAS~J1120$+$0641
+\citep[$z=7.085$,][]{2011Natur.474..616M} and PSO~J$036.5078+03.0498$
+\citep[$z=6.527$,][]{2015ApJ...801L..11V}, both discovered in UKIDSS imaging
+(3370\,deg$^2$), in addition to the current highest-redshift quasar J1342$+$0928
+at $z=7.54$ selected from a combination of UKIDSS, WISE and DECaLS
+\citep[$\sim 2500$\,deg$^2$,][]{2018Natur.553..473B}. Although
 currently only rough estimates exist concerning their selection
@@
 we do not include the highly debated \citet{2015AA...578A..83G} sample
-in our main analysis due to its rough selection function and lacking
-%% JFH lacking --> lack of 
+in our main analysis due to its rough selection function and lack of
 spectroscopy for 17 of the 22 quasar candidates, we use it in
@@
 %% fits in redshift bins. 3) examining redshift evolution. 4) attempting a joint fit.
+%% GW: Agreed. Modified the roadmap.
 
 After homogenising the samples and selection functions we are in a position
-to compute the UV luminosity function of AGN. We begin our analysis by
-deriving luminosity functions in bins of redshift and absolute magnitude.
+to compute the UV luminosity function of AGN. We begin our analysis by computing
+binned estimates of the luminosity function as a function of magnitude in several redshift intervals.
+We then perform parametric maximum-likelihood fits of the luminosity function in the individual redshift bins,
+examine the resulting parameters as a function of redshift, and attempt a joint fit in magnitude and redshift.
 For simplicity we will use the notation $M\equiv M_{1450}$ in the following.
@@
 In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
-  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the luminosity
+  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the binned luminosity
     %% JFH Notation error here. 
@@
 \begin{equation}
-  \phi \equiv \frac{N}{V_\mathrm{bin}},
+  \phi \equiv \frac{N_\mathrm{QSO}}{V_\mathrm{bin}},
 \end{equation}
-where $N$ is the number of quasars with magnitude
+where $N_\mathrm{QSO}$ is the number of quasars with magnitude
 $M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
@@
 denotes the comoving volume element per unit solid angle
-\citep{1999astro.ph..5116H}.
-
-The luminosity function $\phi$ has units of
-$\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.  We evaluate the double
-integral in Equation~(\ref{eqn:vi}) by the Euler method, i.e., by
-simply summing over the ``tiles'' of the selection function map,
-without interpolating between the redshift and luminosity values of
-neighbouring tiles. 
-%%GW: We should add that interpolation of selection functions is not
-%%straightforward (strong gradients) and not unique. Many selection
-%%functions are very coarse. V=0 means that the selection function has
-%%systematic errors (a QSO was found where the selection probability
-%%is zero). By removing them we avoid numerical issues, but
-%%underestimate the QLF. Surveys need to report selection functions
-%%that are consistent with their actual samples. -- done (GK) 
-This may result in $V_i=0$ for some quasars, in which case we remove
-them from our analysis.  (Interpolation of selection functions is not
-straightforward due to strong gradients.  The presence of objects with
-$V_i=0$ implies that the selection function has systematic errors.)
-%%GW: Poisson statistics will underestimate the error since
-%%uncertainties in the selection function are not considered (all
-%%surveys assume a fixed selection function). For small surveys the
-%%Poisson error dominates, but for large surveys the error is driven
-%%by systematics in the selection function. These facts have been
-%%neglected so far, and we should make this point very clearly. -- done (GK)
-In each bin, we estimate the uncertainty in the luminosity function by
+\citep{1999astro.ph..5116H}. The resulting luminosity function $\phi$ has units of
+$\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.
+
+We evaluate the double integral in Equation~(\ref{eqn:vi}) by the Euler method,
+i.e., by simply summing over the ``tiles'' of the selection function in $M$ and $z$
+without interpolation.
+This results in $V_i=0$ for a few quasars, which are subsequently removed
+from our analysis\footnote{
+  We note that the interpolation of sometimes coarse
+  selection functions is not straightforward due to their strong gradients.
+  The presence of objects with $V_i=0$ implies that the selection function has systematic errors.}.
+In each bin we estimate the uncertainty in the luminosity function by
 assuming Poisson statistics \citep{1986ApJ...303..336G} for the number
 of quasars, i.e.\ assuming negligible uncertainty in the selection function.
-The resultant binned luminosity function estimates are shown by the
-points in Figure~\ref{fig:mosaic}.
-
-%%GW: I've sharpened the discussion below. -- done (GK)
-As seen in Figure~\ref{fig:mosaic}, the distribution of luminosity
+While this is a reasonable approximation for small surveys, large surveys
+with negligible Poisson errors are instead limited by rarely quantified systematic
+errors due to implicit assumptions in their selection functions.
+The resultant binned luminosity function estimates
+are shown by the circles in Figure~\ref{fig:mosaic}.
+
+From Figure~\ref{fig:mosaic} we see that the distribution of luminosity
 function values in each redshift bin are suggestive of a double power
@@
 \citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
-by eye and discard them from our analysis.
-%%GW: We should also set the selection functions to zero in these
-%%bins. -- done (GK)
+by eye, discard the contributing quasars from our analysis, and set their
+selection function values to zero.
 The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
@@
 
+%% GW: Maybe say what we mean by one-sigma uncertainty: This is a credible interval from the posterior distribution. Do we use the highest posterior density interval or the equal-tailed interval?
 \begin{figure*}
@@
   \end{center}
-  \caption{Homogenised quasar luminosity functions at
-    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.  The
-    symbols show our inferred binned luminosity functions from various
+  \caption{Homogenised quasar luminosity functions at rest-frame wavelength
+    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.
+    The symbols show our inferred binned luminosity functions from various
     data sets:
@@
     Open circles in corresponding colours indicate magnitude bins
-    excluded due to incompleteness for the respective data sets.  The
+    excluded due to incompleteness in the respective data sets.  The
     number of AGN before this selection is shown in parentheses; the
@@
 
-%%GW: I would delete the z_bin column from the table. Otherwise the
-%%reader might be confused what you are plotting in the figure. The
-%%bin centers and the mean values are very similar anyway.--done (GK)
-%%GW: Again 2.5<z<2.6 is missing--done (GK)
-%%GW: I would add a column or a comment which redshift bins we
-%%consider reliable. I'm afraid lazy people will just take the values
-%%without thinking.
+%%GW: Added a note on discarded redshift bins
+%%GW: Check on final Nqso needed! The number at z~5 is inconsistent with Fig. 3
 \begin{table*}
   % bins_tabulate.py; Nqso added by hand
-  \caption{Derived double power law luminosity function parameters in
-    various redshift bins.  The luminosity function parameters
+  \caption{\textbf{Check on final Nqso needed! The number at $z\sim5$ is inconsistent with Fig. 3. We could also have two columns for the number of quasars: before and after magnitude restrictions.}
+    Posterior median double power law luminosity function parameters
+    and their $1\sigma$ (68.26\%) statistical errors in
+    various redshift bins shown in Figure~\ref{fig:evoln}.
+    The luminosity function parameters
     $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
@@
     slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
-    z_\mathrm{max}$.  The number of quasars in each bin is given by
-    $N_\mathrm{qso}$.  The bin centre and sample mean redshift are
-    given by $z_\mathrm{bin}$ and $\langle z\rangle$, respectively.
-    Errors indicate one-sigma (68.26\%) uncertainties.  These values
-    are shown in Figure~\ref{fig:evoln}.  The corresponding luminosity
-    functions are shown in Figure~\ref{fig:mosaic}.  See
-    Section~\ref{sec:bins} for further details.}
+    z_\mathrm{max}$ with a sample mean $\langle z\rangle$.
+    The number of quasars in each bin is given by $N_\mathrm{QSO}$.
+    %The corresponding luminosity
+    %functions are shown in Figure~\ref{fig:mosaic}.  See
+    %Section~\ref{sec:bins} for further details.
+    }
   \label{tab:bins}
-  \begin{tabular}{cccr....}
+  \begin{tabular}{lccr....}
     \hline
@@
     $z_\mathrm{max}$ &
-    $N_\mathrm{qso}$ &
+    $N_\mathrm{QSO}$ &
     \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
@@
     \hline
-    0.31 & 0.10 & 0.40 & 3632  & -5.61^{+0.09}_{-0.11} & -21.36^{+0.20}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.21^{+0.18}_{-0.17} \\
-    0.50 & 0.40 & 0.60 & 4686  & -6.12^{+0.04}_{-0.04} & -23.00^{+0.07}_{-0.08} & -3.37^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
-    0.72 & 0.60 & 0.80 & 4684  & -6.42^{+0.09}_{-0.08} & -24.04^{+0.15}_{-0.12} & -3.56^{+0.12}_{-0.12} & -1.75^{+0.05}_{-0.04} \\
-    0.91 & 0.80 & 1.00 & 5248  & -6.39^{+0.08}_{-0.07} & -24.51^{+0.12}_{-0.11} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
-    1.10 & 1.00 & 1.20 & 6566  & -6.53^{+0.03}_{-0.03} & -25.14^{+0.04}_{-0.04} & -4.17^{+0.08}_{-0.09} & -1.73^{+0.02}_{-0.02} \\
-    1.30 & 1.20 & 1.40 & 7132  & -6.43^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.06} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
-    1.50 & 1.40 & 1.60 & 7771  & -6.51^{+0.03}_{-0.03} & -25.68^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
-    1.71 & 1.60 & 1.80 & 7421  & -6.29^{+0.04}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.97^{+0.07}_{-0.07} & -1.61^{+0.03}_{-0.03} \\
-    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.27^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
-    2.30 & 2.20 & 2.40 & 8419  & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.33^{+0.11}_{-0.12} & -1.60^{+0.04}_{-0.04} \\
-    2.45 & 2.40 & 2.50 & 3403  & -6.40^{+0.08}_{-0.07} & -25.86^{+0.15}_{-0.12} & -3.60^{+0.20}_{-0.23} & -1.60^{+0.05}_{-0.05} \\
-    2.55 & 2.50 & 2.60 & 2640  & -6.15^{+0.08}_{-0.09} & -25.34^{+0.18}_{-0.17} & -3.31^{+0.16}_{-0.16} & -1.39^{+0.08}_{-0.08} \\
-    2.65 & 2.60 & 2.70 & 1883  & -5.98^{+0.06}_{-0.06} & -25.15^{+0.14}_{-0.13} & -3.13^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
-    2.75 & 2.70 & 2.80 & 1135  & -6.29^{+0.07}_{-0.07} & -25.95^{+0.15}_{-0.13} & -3.79^{+0.26}_{-0.29} & -1.34^{+0.07}_{-0.06} \\
-    2.85 & 2.80 & 2.90 & 1069  & -6.46^{+0.11}_{-0.10} & -26.23^{+0.22}_{-0.18} & -3.62^{+0.36}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
-    2.95 & 2.90 & 3.00 & 1104  & -6.76^{+0.07}_{-0.06} & -26.52^{+0.10}_{-0.09} & -5.04^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
-    3.05 & 3.00 & 3.10 & 1127  & -6.77^{+0.08}_{-0.07} & -26.48^{+0.11}_{-0.11} & -4.72^{+0.44}_{-0.51} & -1.70^{+0.05}_{-0.05} \\
-    3.15 & 3.10 & 3.20 & 1041  & -7.25^{+0.16}_{-0.12} & -27.10^{+0.23}_{-0.18} & -4.42^{+0.79}_{-1.17} & -1.96^{+0.07}_{-0.05} \\
-    3.25 & 3.20 & 3.30 & 815   & -7.34^{+0.13}_{-0.13} & -27.20^{+0.19}_{-0.23} & -4.37^{+0.68}_{-0.74} & -1.94^{+0.06}_{-0.05} \\
-    3.34 & 3.30 & 3.40 & 510   & -7.53^{+0.22}_{-0.21} & -27.38^{+0.29}_{-0.36} & -4.79^{+1.34}_{-1.47} & -2.08^{+0.09}_{-0.07} \\
-    3.44 & 3.40 & 3.50 & 155   & -6.78^{+0.19}_{-0.20} & -26.64^{+0.40}_{-0.34} & -3.74^{+0.64}_{-0.79} & -1.25^{+0.28}_{-0.23} \\
-    3.88 & 3.70 & 4.10 & 1204  & -7.92^{+0.12}_{-0.11} & -27.26^{+0.14}_{-0.12} & -4.84^{+0.34}_{-0.36} & -2.07^{+0.10}_{-0.09} \\
-    4.35 & 4.10 & 4.70 & 603   & -8.32^{+0.28}_{-0.26} & -27.37^{+0.36}_{-0.31} & -4.20^{+0.40}_{-0.49} & -2.20^{+0.16}_{-0.14} \\
-    4.92 & 4.70 & 5.50 & 263   & -9.04^{+0.30}_{-0.22} & -27.90^{+0.37}_{-0.26} & -4.56^{+0.70}_{-0.81} & -2.31^{+0.11}_{-0.08} \\
-    6.00 & 5.50 & 6.50 & 66    & -10.64^{+0.72}_{-1.08} & -29.18^{+1.05}_{-1.81} & -5.00^{+0.76}_{-1.21} & -2.40^{+0.09}_{-0.08} \\
+    0.31$^a$ & 0.10 & 0.40 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
+    0.50$^a$ & 0.40 & 0.60 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
+    0.72 & 0.60 & 0.80 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
+    0.91 & 0.80 & 1.00 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
+    1.10 & 1.00 & 1.20 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
+    1.30 & 1.20 & 1.40 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
+    1.50 & 1.40 & 1.60 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
+    1.71 & 1.60 & 1.80 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
+    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
+    2.30$^a$ & 2.20 & 2.40 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
+    2.45$^a$ & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
+    2.55$^a$ & 2.50 & 2.60 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
+    2.65$^a$ & 2.60 & 2.70 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
+    2.75$^a$ & 2.70 & 2.80 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
+    2.85$^a$ & 2.80 & 2.90 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
+    2.95$^a$ & 2.90 & 3.00 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
+    3.05$^a$ & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
+    3.15$^a$ & 3.10 & 3.20 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
+    3.25$^a$ & 3.20 & 3.30 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
+    3.34$^a$ & 3.30 & 3.40 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
+    3.44$^a$ & 3.40 & 3.50 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
+    3.88 & 3.70 & 4.10 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.10 & 4.70 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
+    4.92 & 4.70 & 5.50 & 266 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
+    6.00 & 5.50 & 6.50 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
     \hline
-  \end{tabular}
+  \end{tabular}\\
+  \begin{minipage}{13.0cm}
+    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:mosaic}).}
+  \end{minipage}
 \end{table*}
@@
 
-%%GW: Not sure what you mean here. I've cut the next two sentences
-%As our next step, we combine magnitude bins by binning the quasars
-%only in redshifts.  This allows us to estimate the luminosity
-%function at each redshift.--done(GK)
 In each redshift bin, we model the quasar
@@
 %%GW: Maybe give the range of the uniform priors.
+%% JFH SOmewhere indicate taht this procedure of ubninned LF estimates is standard practice. 
+%% GW: Agreed. Maybe add references to Marshall et al. and other seminal papers further up in the text?
 By assuming broad, uniform priors, we obtain posterior probability
@@
 %% something like that. I would just explain waht you plot. 
-The posterior median is shown as our adopted model at each redshift,
-while the grey shaded region shows the one-sigma (68.26\%)
-uncertainty\footnote{Throughout this paper, we adopt the posterior
-  median and the equal-tailed 68.26\% credible interval as our model
-  fit and its one-sigma uncertainty.}.  Consistent with previous
-studies, the double power law model provides an excellent description
-of the luminosity function model over almost the complete range of
-redshifts spanned by the data.  It is only in the highest redshift bin
-($z=5.5$--$6.5$) that the data show a weak preference for a single power law.
-%% In
-%% this bin, the resultant posterior distribution of the break magnitude
-%% $M_*$ is bimodal with favoured values at the faint ($M_*>-18$) and
-%% bright end of the data ($M_*<-30$).
-While in the literature the
-$z\sim 6$ AGN have been assumed to lie on the bright end of the
-luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a comparison
-with the luminosity function at lower redshifts ($z<5.5$) suggests
-that these AGN should instead be understood to describe the faint-end
-of a double power law.
+%% GW: Agreed. We need some explanation here. I've changed "best-fit" to "adopted". We also need to explain the meaning of our errors.
+\textbf{GW: Definition of adopted model and error bars}
+We adopt the posterior median as our fiducial model fit, and the 68.26\% credible interval as the uncertainty on $\phi$.
+Consistent with previous studies, the double power law model provides an excellent
+description of the luminosity function model over almost the complete
+range of redshifts spanned by the data.
+\textbf{GW agrees with JFH here. Move the discussion of $z\sim 6$ priors to Fig. 4}
+It is only in the highest
+redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
+power law.  In this bin, the resultant posterior distribution of the
+break magnitude $M_*$ is bimodal with favoured values at the faint
+($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
+literature $z\sim 6$ quasars have been assumed to lie on the bright
+end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
+comparison with the luminosity function at lower redshifts ($z<5.5$)
+suggests that these AGN should instead be understood to describe the
+faint-end of a double power law.
 %% JFH Okay so you need to be more clear here that what you mean is that the trend
@@
 negative values, i.e., steeper luminosity function bright ends, at
-high redshifts.  Finally, the faint end slope of the luminosity
-function also shows signs of increasing steepness towards high
-redshifts.
-%%GW: I would not write that beta has a break.--done(GK)
-Somewhat similar to the amplitude $\phi_*$, the faint-end slope
-$\beta$ also shows rapid evolution at $z\sim 3$.  It stays roughly
-constant up to this redshift, and the drops to increasingly negative
-values of close to $-2.5$ at high redshifts, indicating a steeper
-faint end.
+high redshifts. Finally, the faint end slope also shows signs of
+increasing steepness towards high redshifts, but with a marked discontinuity at $2.2\le z<3.5$.
+%It stays roughly
+%constant up to this redshift, and the drops to increasingly negative
+%values of close to $-2.5$ at high redshifts, indicating a steeper
+%faint end.
+
+%% JFH I think you need to show at least one corner plot for your fits somewhere in the paper.
 
@@
 %% you get at high-z without imposing the prior on the faint-end/bright-end slope.
-
-%%GW: I've commented the following paragraph and replaced it by a
-%%sharper version
-%Figure~\ref{fig:evoln} reveals further likely systematic errors.
-%The behaviour of BOSS quasars, shown by open circles in
-%Figure~\ref{fig:evoln} at redshifts $z=2$--$4$ is striking.  In this
-%redshift range covered by BOSS the values of the four double power law
-%parameters deviate from the general trends.  The faint end of the
-%luminosity function of the BOSS quasars is much shallower and the
-%break luminosity is fainter by a magnitude compared to the general
-%trend expected from a smooth evolution.  The bright end of the
-%luminosity function of quasars in this sample is also much flatter
-%than that for other samples.  The conspicuousness of the deviation of
-%the BOSS sample from the general trends makes it unlikely that the
-%luminosity function evolution indicated by BOSS in the redshift range
-%$z=2$--$3$ is physical.  Indeed, in this redshift range BOSS quasar
-%selection is known to be affected by a colour bias
-%\citep{2011ApJ...728...23W}, which can make estimating completeness
-%difficult \citep{2006AJ....131.2766R}. --done(GK)
 
@@
 selection function that critically depends on the assumed quasar
-spectral energy distribution and the IGM parameterization
-\citep{2011ApJ...728...23W,2013ApJ...773...14R}.  Consequently, we
+spectral energy distribution, the IGM parameterization,
+and the modeled photometric errors at the targeted magnitude limit of the single-epoch SDSS imaging
+\citep{2011ApJ...728...23W,2012ApJS..199....3R,2013ApJ...773...14R}.  Consequently, we
 exclude all BOSS quasars from further analysis.
@@
 %% (or at the faint end variations in the photometric senstivity 
+%% GW: Good point, BOSS was working at the limit of SDSS imaging, so photometric errors are important.
+I've added a few words on this and added a reference to Ross et al.
+2012 who highlight the importance of modeling the photometric error at the SDSS magnitude limit.
+This was done using Stripe 82 data, but it's a model nonetheless.
 
@@
 in the correction for host galaxy light and potentially missed AGN in
-extended sources. we exclude $z<0.6$ quasars from further
+extended sources. We exclude $z<0.6$ quasars from further
 consideration. Due to different selection function parameters
@@
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
-    % mosaic_selected.py and drawlf_selected.py 
-  \end{center}
-  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
-    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
-    binned luminosity functions.  In each redshift bin, yellow curves
-    show our fiducial double power law luminosity function model in
-    that redshift bin.  Other curves show the three global evolution
-    models.  Shaded regions show the one-sigma (68.26\%)
-    uncertainties.}
-  \label{fig:mosaic_global}
-\end{figure*}
-
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
-    % summary_fromFile.py 
-  \end{center}
-  \caption{Luminosity function parameter evolution in the global
-    models.  The symbols show the posterior median values of
-    parameters with one-sigma (68.26\%) uncertainties in redshift bins
-    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
-    by systematics and removed from the global analysis are shown in
-    grey.  In each panel, the solid curves and shaded regions show the
-    three derived global models with one-sigma uncertainties.  Model~1
-    provides a better fit, but requires a rapid change in the
-    faint-end slope at $z\sim 3.5$.}
-  \label{fig:evoln_global}
-\end{figure*}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
-    % rhoqso.py -- draw_withGlobal_multiple()
-  \end{center}
-  \caption{AGN number density evolution in the global model, when the
-    luminosity function is integrated (from top to bottom) down to
-    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
-    show the estimates from the our fiducual double power law
-    luminosity function models in various redshift bins, with vertical
-    error bars denoting one-sigma (68.26\%) uncertainties.  Open
-    circles show the same in redshifts bins affected by systematics.
-    Curves show the estimated density from the global models, with the
-    accompanying shaded regions denoting the one-sigma uncertainty. }
-  \label{fig:rhoqso}
-\end{figure}
-
-\begin{figure*}
-  \begin{center}
-    \begin{tabular}{cc}
-      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
-      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
-      % gammapi.py -- draw_emissivity_18()
-      % gammapi.py -- draw_emissivity_21()
-    \end{tabular}
-  \end{center}
-  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
-    fraction down to a limiting magnitude for a luminosity function
-    integration limit of $M_{1450}=-18$ (left panel) and
-    $M_{1450}=-21$ (right panel).  Black filled circles with error
-    bars in both panels show the emissivity determinations in redshift
-    bin deemed to have low systematic errors.  Open circles show
-    emissivities for redshift bins that we remove from analysis due to
-    high systematic errors.  Solid red curves in both panels show the
-    derived posterior median emissivity evolution model, with the
-    shaded area showing the one-sigma (68.26\%) uncertainty.  Also
-    shown for comparison in both panels are models by \citet[pentagon
-      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
-    \citet[square]{2015AA...578A..83G},
-    \citet[triangle]{2018PASJ...70S..34A},
-    \citet[circle]{2018AJ....155..131M},
-    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
-      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
-      curve]{2015ApJ...813L...8M}, \citet[dashed
-      brown]{2012ApJ...746..125H}, \citet[dashed
-      grey]{2017MNRAS.466.1160M}, \citet[dashed
-      blue]{2013A&A...551A..29P}, \citet[solid
-      cyan]{2016A&A...587A..41P}, \citet[solid
-      blue]{2017A&A...608A..64C}, and
-    \citet[brown]{2007A&A...472..443B}.}
-  \label{fig:e912_2}
-\end{figure*}
-
 \subsection{Evolution of the luminosity function}
@@
 
-The smooth evolution of the luminosity function parameters apparent in
-Figure~\ref{fig:evoln} suggests that it should be possible to describe
-the quasar UV luminosity function evolution out to $z\sim 7$ using
-fewer parameters.  Such descriptions have been developed in the
+After excluding the redshift bins that are most obviously affected by systematic errors,
+the remaining redshift bins (filled symbols in Figure~\ref{fig:evoln}) are consistent with a
+smooth redshift evolution of the luminosity function parameters that may be
+described by parametric models. 
+%%using fewer parameters.
+\textbf{GW: We need more citations to previous parametric models, i.e. Croom, Ross, Richards, Palanque-Delabrouille, Bongiorno etc. This dates back to much earlier work using PDE and PLE models.}
+Such descriptions have been developed in the
 literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
 bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
+%% GW: I would always call these ``bolometric'', since truly bolometric LFs require complete samples with complete multiwavelength photometry
 Such ``global'' models of the luminosity function evolution are useful
@@
 model in Equation~(\ref{eqn:dpl}) as
+\textbf{GW: Symbol $f$ is used for the selection function already.}
 \begin{align}
@@
 \end{align}
-where the $c_{j,i}$'s are the new model parameters, and the $f_j$'s
+where the $\{c_{j,i}\}$ are the new model parameters, and the $\{f_j\}$
 are functions that vary smoothly with redshift $z$.  The joint
@@
 written as
+\textbf{GW: Should the set of $c_i$ be a set of $c_j$ instead?}
 \begin{equation}
@@
 parameters in that equation are redshift-dependent, so that
+\textbf{GW thinks the next formula can be omitted, since the fact is clear from Eq. 13.}
 \begin{multline}
@@
 a straightforward generalisation of Equation~(\ref{eqn:S}), given by
+\textbf{GW: This formula is obvious and could be omitted, indeed it is exactly Eq. 10! If we keep it we should change the nomenclature}
 \begin{multline}
@@
 and the integrals in the second term on the right-hand side are over
-the complete surveyed range of luminosity and redshift, instead of
-redshift and luminosity bins.  We consider models in which the
+the complete surveyed range of magnitude and redshift, instead of
+redshift and magnitude bins.  We consider models in which the
 evolution of the four double power law parameters is modelled
@@
 %% JFH Something is wrong with the flow here. You are referencing Figure 6, but have not yet discussed Figure 5. 
+%% GW changed the order of the figures. We need the LF parameters first before evaluating the individual z bins.
 The three
@@
 
-\item In Model 1, for the parameters $\phi_*$, $M_*$ and $\alpha$ we
-  assume that the functions $f_i$'s
-  %% JFH don't need the apostrophe s. 
-  in Equations~(\ref{eqn:global})
-  are Chebyshev polynomials in $(1+z)$.  Thus the functions $f_i$s
-  %% JFH This s should be here after f_i
-  are
+\item
+  In Model 1 we assume that the functions $f_0$, $f_1$ and $f_2$ from
+  Equation~\eqref{eqn:global} are Chebyshev polynomials in $\left(1+z\right)$,
   written as
   \begin{equation}
-    f_i=\sum_{j=0}^{n_i}c_{i,j}T_j(1+z),
+    f_i\left(1+z\right)=\sum_{j=0}^{n_i}c_{i,j}T_j\left(1+z\right)
     \label{eqn:cbs}
   \end{equation}
-  where $c_{i,j}$ are the parameters that appear in
-  Equations~(\ref{eqn:global}) and $T_j(1+z)$ are Chebyshev
+  for $i\in\{0,1,2\}$, where $c_{i,j}$ are the parameters from
+  Equation~\eqref{eqn:global} and $T_j\left(1+z\right)$ are Chebyshev
   polynomials of the first kind. We try successively higher orders of
@@
   As we discuss below, we find that $\phi_*$, $M_*$ and
-  $\alpha$ prefer quadratic, cubic, and linear evolutions in $(1+z)$.
-  %% JFH , respecitvely. 
-  The faint-end slope $\beta$ seems to require a break in its
-  evolution at $z\sim 3$, as discussed in the previous section.  As a
-  result, it is difficult to model the evolution of $\beta$ using the
-  Chebyshev expansion of Equation~(\ref{eqn:cbs}).  Instead, we
-  consider a double power law model for $\beta$ and write
+  $\alpha$ prefer quadratic, cubic, and linear evolutions in $\left(1+z\right)$, respectively.
+  For the faint-end slope $\beta$ we adopt a double power law to account
+  for a possible break at $z\sim 3$ that is currently not covered with credible data.
+  %% GW I know I'm harsh with BOSS here. But that's a fact.
+  Thus we write
   \begin{equation}
-    f_3(1+z)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
+    f_3\left(1+z\right)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
     \label{eqn:beta}
@@
   Table~\ref{tab:samples} are included while fitting this model.
+  \textbf{GW agrees with JFH that this is too short and cryptic.
+Table~\ref{tab:samples} refers to all samples, but we exclude some samples, some redshift ranges, and some magnitude ranges.
+I've put a clarification in the first sentence of the section, but we might elaborate more.}
   %% JFH where was this discussed?? Nowhere have I seen explicitly stated in the
@@
 %% power law? Am I getting fooled by the shape of that green curve?
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
+    % summary_fromFile.py 
+  \end{center}
+  \caption{Luminosity function parameter evolution in the global
+    models.  The symbols show the posterior median values of
+    parameters with one-sigma (68.26\%) uncertainties in redshift bins
+    from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
+    by systematics and removed from the global analysis are shown in
+    grey.  In each panel, the solid curves and shaded regions show the
+    three derived global models with one-sigma uncertainties.  Model~1
+    provides a better fit, but requires a rapid change in the
+    faint-end slope at $z\sim 3.5$.}
+  \label{fig:evoln_global}
+\end{figure*}
+
+\begin{figure*}
+  \begin{center}
+    \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
+    % mosaic_selected.py and drawlf_selected.py 
+  \end{center}
+  \caption{Luminosity function estimates from $z=0.6$ to $6.5$.
+    Similar to Figure~\ref{fig:mosaic}, the symbols show our inferred
+    binned luminosity functions.  In each redshift bin, yellow curves
+    show our fiducial double power law luminosity function model in
+    that redshift bin.  Other curves show the three global evolution
+    models.  Shaded regions show the one-sigma (68.26\%)
+    uncertainties.}
+  \label{fig:mosaic_global}
+\end{figure*}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+    % rhoqso.py -- draw_withGlobal_multiple()
+  \end{center}
+  \caption{AGN number density evolution in the global model, when the
+    luminosity function is integrated (from top to bottom) down to
+    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
+    show the estimates from the our fiducual double power law
+    luminosity function models in various redshift bins, with vertical
+    error bars denoting one-sigma (68.26\%) uncertainties.  Open
+    circles show the same in redshifts bins affected by systematics.
+    Curves show the estimated density from the global models, with the
+    accompanying shaded regions denoting the one-sigma uncertainty. }
+  \label{fig:rhoqso}
+\end{figure}
 
@@
 models capture the steepening of the faint end of the luminosity
-function towards higher redshifts.  The adopted posterior median form
-of Model~1 is shown by the black curves in
-Figure~\ref{fig:evoln_global}.  The accompanying grey shaded area
-depicts the one-sigma (68.26\%) uncertainty.  The model is in
-excellent agreement with the results of the fits in redshift bins
-discussed in the previous section.
+function towards higher redshifts.  The derived form of Model~1 is
+shown by the black curves in Figure~\ref{fig:evoln_global}.  The
+accompanying grey shaded area depicts the one-sigma (68.26\%)
+uncertainty.  The model is in excellent agreement with the results of
+the fits in redshift bins discussed in the previous section.
 %% JFH Reference Figure 5 here as well.  
@@
 
-\section{Contribution of AGN to reionization}
+\begin{figure*}
+  \begin{center}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.47\textwidth]{emissivity_18.pdf} & 
+      \includegraphics[width=0.47\textwidth]{emissivity_21.pdf} \\
+      % gammapi.py -- draw_emissivity_18()
+      % gammapi.py -- draw_emissivity_21()
+    \end{tabular}
+  \end{center}
+  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
+    fraction down to a limiting magnitude for a luminosity function
+    integration limit of $M_{1450}=-18$ (left panel) and
+    $M_{1450}=-21$ (right panel).  Black filled circles with error
+    bars in both panels show the emissivity determinations in redshift
+    bin deemed to have low systematic errors.  Open circles show
+    emissivities for redshift bins that we remove from analysis due to
+    high systematic errors.  Solid red curves in both panels show the
+    derived posterior median emissivity evolution model, with the
+    shaded area showing the one-sigma (68.26\%) uncertainty.  Also
+    shown for comparison in both panels are models by \citet[pentagon
+      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
+    \citet[square]{2015AA...578A..83G},
+    \citet[triangle]{2018PASJ...70S..34A},
+    \citet[circle]{2018AJ....155..131M},
+    \citet[diamond]{2018MNRAS.474.2904P}, \citet[open
+      rectangle]{2017ApJ...847L..15O}, \citet[dotted green
+      curve]{2015ApJ...813L...8M}, \citet[dashed
+      brown]{2012ApJ...746..125H}, \citet[dashed
+      grey]{2017MNRAS.466.1160M}, \citet[dashed
+      blue]{2013A&A...551A..29P}, \citet[solid
+      cyan]{2016A&A...587A..41P}, \citet[solid
+      blue]{2017A&A...608A..64C}, and
+    \citet[brown]{2007A&A...472..443B}.}
+  \label{fig:e912_2}
+\end{figure*}
+
+\section{The AGN contribution to reionization}
 \label{sec:reion}
@@
 reionization in our luminosity function model.  We first derive the
-expected evolution of the 912\,\AA\ emissivity of AGN in our model,
-and then use this to estimate the \HI\ photoionization rate and the
-average \HeIII\ fraction.
+redshift evolution of the 912\,\AA\ emissivity of AGN,
+and then use this to estimate the contribution of AGN to the \ion{H}{i} photoionization rate
+between $z=0$ and $z=7$, as well as the redshift evolution of the average \ion{He}{iii} fraction
+in the IGM for a quasar-driven \ion{He}{ii} reionization.
 %% JFH Mention low-z UVB here as well in intro.
-\subsection{Hydrogen-ionizing emissivity}
+
+\subsection{Quasar emissivity at the hydrogen Lyman limit}
 \label{sec:e912}
 
-We assume that all quasars have a universal UV SED, parameterised by
-\citet{2015MNRAS.449.4204L} as a power law with a break at 912~{\AA},
+For simplicity we assume that all quasars have a universal UV SED,
+parameterised as a power law $f_\nu\propto\nu^{\alpha_\nu}$
+with a break at 912\,\AA,
 \begin{equation}
   f_\nu\propto\begin{cases}
-  \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
-  \nu^{-1.70\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
+  \nu^{-0.61} & \text{if}~\lambda\ge 912~\text{\AA},\\
+  \nu^{-1.70} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}                
   \end{cases}
@@
 \end{equation}
-This fit was derived by \citet{2015MNRAS.449.4204L} from a composite
-spectrum of 53 quasars at $z\sim 2.4$.  While four published composite
-quasar UV SEDs \citep{2002ApJ...565..773T, 2001AJ....122..549V,
-  2012ApJ...752..162S, 2014ApJ...794...75S} agree with
-Equation~(\ref{eqn:sed}), the composite of
-\citet{2004ApJ...615..135S}, which uses more than 100 quasars at
-$z<0.1$, is somewhat steeper, with a EUV slope of $-0.56$.  The
-quasars considered by \citet{2004ApJ...615..135S} are fainter
-($M_i(z=2)>-26$)
-%% JFH Something is wrong with this faint number here. The bulk of the scott sample I thought was much fainter than this.
-%% Ask Gabor? 
-than those considered by \citet{2015MNRAS.449.4204L},
-which suggest that faint quasars may have a steeper EUV spectrum.  We
-therefore assume an SED of the form
+as derived from a stacked spectrum of 53 luminous ($M_{1450}\simeq -27$)
+$z\simeq 2.4$ quasars \citep{2015MNRAS.449.4204L}, and consistent
+with recent composite spectra of low-$z$ quasars with a wide range in luminosity
+\citep{2012ApJ...752..162S, 2014ApJ...794...75S}.
+The extreme UV SED of faint ($M_{1100}\approx -22$) AGN may be significantly
+harder \citep[$\alpha_\nu=-0.56$,][]{2004ApJ...615..135S}, but the exact value of the slope
+critically depends on the total rest-frame wavelength coverage, the adopted continuum windows,
+the correction for IGM line blanketing, and the ability to distinguish
+low-equivalent-width emission lines from the underlying continuum
+\citep{2014ApJ...794...75S,2015MNRAS.449.4204L,2016ApJ...817...56T}.
+For the computation of the hydrogen Lyman limit emissivity the choice of the spectral index
+at $\lambda<912$\,\AA\ is inconsequential, whereas for the calculation of the \ion{H}{i}
+photoionization rate in the IGM and the \ion{He}{ii} reionization history other
+sources of uncertainty dominate (see below). We note that all composite AGN spectra
+are consistent with an AGN Lyman limit escape fraction of unity
+(see also \citealt{2018A&A...613A..44G} for a recent sample of faint $z\sim 4$ AGN).
+We therefore adopt an escape fraction of unity for Lyman continuum photons.
+
+%% GW simplified the following derivation
+%The rate of emission of photons of frequency $\nu$ by quasars can be
+%written as
+%\begin{equation}
+%  \dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
+%\end{equation}
+%where the integral is over a suitable range of magnitudes, the
+%monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
+%magnitude by \citep{1983ApJ...266..713O}
+%\begin{equation}
+%  M_\nu = -2.5\log_{10}L_\nu+51.60,
+%\end{equation}
+%and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
+%related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
+%or (\ref{eqn:sed_faint})
+%\begin{equation}
+%  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
+%\end{equation}
+%depending on the AGN luminosity.  The corresponding comoving volume
+%emissivity is
+%\begin{equation}
+%  \epsilon_\nu = \dot n_\nu h\nu.
+%  \label{eqn:epsilon}
+%\end{equation}
+With our adopted SED the specific comoving volume emissivity of quasars at 912\,\AA\ can be written as
+\begin{eqnarray}\nonumber
+\epsilon_{912}\left(z\right)&=&\int\limits_{-\infty}^{M_{1450}^\mathrm{lim}}\phi\left(M_{1450},z\right)10^{-0.4\left(M_{1450}-51.60\right)}\,\mathrm{d}M_{1450}\\
+& &\times\left(\frac{912}{1450}\right)^{0.61}\quad,
+\label{eqn:epsilon}
+\end{eqnarray}
+which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$ and on the
+faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg M_*$.
+The black circles in Figure~\ref{fig:e912_2} show the comoving 912\,\AA\ emissivity
+obtained from the individual QLF fits (Table~\ref{tab:bins}) for $M_{1450}<-18$ (left panel)
+and $M_{1450}<-21$ (right panel), respectively. Redshift bins that were removed from
+the analysis due to large systematic errors in the QLF parameters are shown as open circles.
+\textbf{GW: Add a sentence on error bars.}
+Our derived emissivity values at 912\,\AA\ and at 1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins}
+for reference.
+The emissivity peaks between $z=2$ and 3 at $\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
+depending on the magnitude limit, and decreases rapidly towards lower and higher redshifts.
+Systematic errors in the faint-end slope derived from BOSS data are
+more pronounced for $M_{1450}<-18$ due to extrapolation of the QLF.
+
+To account for redshift effects in the calculation of the \ion{H}{i} photoionization rate,
+a continuous function $\epsilon_{912}\left(z\right)$ is required. As our parametric QLF models
+from the previous section suffer from non-monotonic or divergent AGN number densities,
+we do not use them to derive the corresponding $\epsilon_{912}\left(z\right)$, but
+instead fit the individual emissivity values derived from credible data
+(filled black circles in Figure~\ref{fig:e912_2}) with a 
+five-parameter functional form used by \citet{2012ApJ...746..125H}
 \begin{equation}
-  f_\nu\propto\begin{cases}
-  \nu^{-0.61\pm 0.01} & \text{if}~\lambda\geq 912~\text{\AA},\\
-  \nu^{-0.56\pm 0.61} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}.\\                
-  \end{cases}
-  \label{eqn:sed_faint}
+  \epsilon_{912}\left(z\right)=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}\quad,
+  \label{eqn:e912fit}
 \end{equation}
-for AGN with $M_{1450}<-23$.
-
-The rate of emission of photons of frequency $\nu$ by quasars can be
-written as
-\begin{equation}
-  \dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
-\end{equation}
-where the integral is over a suitable range of magnitudes, the
-monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
-magnitude by \citep{1983ApJ...266..713O}
-\begin{equation}
-  M_\nu = -2.5\log_{10}L_\nu+51.60,
-\end{equation}
-and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
-related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
-or (\ref{eqn:sed_faint})
-\begin{equation}
-  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
-\end{equation}
-depending on the AGN luminosity.  The corresponding comoving volume
-emissivity is
-\begin{equation}
-  \epsilon_\nu = \dot n_\nu h\nu.
-  \label{eqn:epsilon}
-\end{equation}
-Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
-the luminosity function is integrated down to $M_{1450}<-21$ (right
-panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
+assuming a Gaussian likelihood for the emissivity values.
+The resultant curves and the corresponding one-sigma
+uncertainties are shown in Figure~\ref{fig:e912_2}. For $M_{1450}<-18$
+we obtain
+\begin{multline}
+  \epsilon_{912}\left(z\right)=\left(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}\quad,
+\end{multline}
+ and for $M_{1450}<-21$ we get
+\begin{multline}
+  \epsilon_{912}\left(z\right)=\left(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}\quad.
+\end{multline}
+Table~\ref{tab:gamma2} provides the derived emissivities at 912\,\AA\ and 1450\,\AA\ together with their
+derived errors at $0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.
+
+%% Original text from GK with comments from JFH, rewritten by GW below
+
+%Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
+%the luminosity function is integrated down to $M_{1450}<-21$ (right
+%panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
 %% JFH Figure 8 is a nightmare to look at. You need to separate this into multiple
 %% figures somehow. Perhaps one with curves and one with points. 
-Redshift bins that were removed from analysis due to large systematic
-errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
-depending on the luminosity integration limit, at
-$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
-and decreased
+%Redshift bins that were removed from analysis due to large systematic
+%errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
+%depending on the luminosity integration limit, at
+%$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
+%and decreased
 %% JFH decreases 
-rapidly towards high redshifts.  A continuous
-description of this emissivity evolution is valuable in deriving the
-hydrogen photoionizing flux in the IGM.  In principle, the luminosity
-function evolution models discussed in the previous section provide
-such a description.  Unfortunately, as discussed above, all of these
-models suffer from pathologies such as non-monotonic or divergent
+%rapidly towards high redshifts.  A continuous
+%description of this emissivity evolution is valuable in deriving the
+%hydrogen photoionizing flux in the IGM.  In principle, the luminosity
+%function evolution models discussed in the previous section provide
+%such a description.  Unfortunately, as discussed above, all of these
+%models suffer from pathologies such as non-monotonic or divergent
 %% JFH divergence is just becuase of how you do the fits, and not having data at high-z. I don't think
 %% that should be highlighted. 
-AGN
-number densities, likely resulting from residual systematic errors in
-the data.  Therefore, here we describe the emissivity evolution by the
-five-parameter functional form used by \citet{2012ApJ...746..125H}
-\begin{equation}
-  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
-  \label{eqn:e912fit}
-\end{equation}
-We fit this model to the emissivity estimates in the redshift bins,
-shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
-the emissivity in each bin.  The resultant curves and the
-corresponding one-sigma uncertainties are shown in
-Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
-912\,\AA\ emissivities in various redshift bins and in these 
-models are tabulated in Appendix~\ref{sec:tables}.  The adopted
-form of Equation~\ref{eqn:e912fit} is given by
-\begin{multline}
-  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
-\end{multline}
-for $M_{1450}<-18$, and by 
-\begin{multline}
-  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
-\end{multline}
-for $M_{1450}<-21$.
-
+%AGN
+%number densities, likely resulting from residual systematic errors in
+%the data.  Therefore, here we describe the emissivity evolution by the
+%five-parameter functional form used by \citet{2012ApJ...746..125H}
+%\begin{equation}
+%  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
+%  \label{eqn:e912fit}
+%\end{equation}
+%We fit this model to the emissivity estimates in the redshift bins,
+%shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
+%the emissivity in each bin.  The resultant best-fit curves and the
+%corresponding one-sigma uncertainties are shown in
+%Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
+%912\,\AA\ emissivities in various redshift bins and in these best-fit
+%models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
+%form of Equation~\ref{eqn:e912fit} is given by
+%\begin{multline}
+%  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
+%\end{multline}
+%for $M_{1450}<-18$, and by 
+%\begin{multline}
+%  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
+%\end{multline}
+%for $M_{1450}<-21$.
 %% JFH So if I understand correctly you have given up on the global model and are now doing things
@@
 %% what you are doing here, so the reader understands where these data points come from on the plot.
-
-Before proceeding to derive a hydrogen photoionization rate estimate
-from these emissivities, we now comment on the comparison of our
-results with estimates from the literature.  Several of these are
-shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
-Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
-\citet{2012ApJ...746..125H}, which is based on the bolometric
-luminosity function model of \citet{2007ApJ...654..731H}.  Their
-assumed emissivity agrees reasonably well with our $M_{1450}<-21$
-case, although at its maximum the emissivity in the
-\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
-differences between the two models are much larger for $M_{1450}<-18$.
-Figure~\ref{fig:e912_2} also shows the model presented by
-\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
-severely at almost all redshifts in the range considered here, for
-both of our integration limits.  It is important to note here that a
-direct comparison of our model with \citet{2012ApJ...746..125H} and
-\citet{2015ApJ...813L...8M} is difficult because these models
-integrate the luminosity function to a fixed fraction of the break
-luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
-limite
+%Before proceeding to derive a hydrogen photoionization rate estimate
+%from these emissivities, we now comment on the comparison of our
+%results with estimates from the literature.  Several of these are
+%shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
+%Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
+%\citet{2012ApJ...746..125H}, which is based on the bolometric
+%luminosity function model of \citet{2007ApJ...654..731H}.  Their
+%assumed emissivity agrees reasonably well with our $M_{1450}<-21$
+%case, although at its maximum the emissivity in the
+%\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
+%differences between the two models are much larger for $M_{1450}<-18$.
+%Figure~\ref{fig:e912_2} also shows the model presented by
+%\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
+%severely at almost all redshifts in the range considered here, for
+%both of our integration limits.  It is important to note here that a
+%direct comparison of our model with \citet{2012ApJ...746..125H} and
+%\citet{2015ApJ...813L...8M} is difficult because these models
+%integrate the luminosity function to a fixed fraction of the break
+%luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
+%limite
 %% JFH limite --> limit 
-by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
-is $0.01L_*$.  Using a limit that depends on the break luminosity is
-problematic as different quasar surveys used to develop these
-emissivity models often report strikingly different break luminosity
-values.  Even when these samples are homogeneized appropriately, have
+%by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
+%is $0.01L_*$.  Using a limit that depends on the break luminosity is
+%problematic as different quasar surveys used to develop these
+%emissivity models often report strikingly different break luminosity
+%values.  Even when these samples are homogeneized appropriately, have
 %% JFH adopting such an integratino limit....
-such an integration limit is likely only justified if the faint-end
-slope of the luminosity function is sufficiently shallow.  This issue
-also affects some other models in the literature, such as those
-presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
-and \citet{2018arXiv180104931P}.
-
-\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
-$M_{1450}=-19$.  However, their model strongly disagrees with our
-inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
-biases resulting from inhomogeneously combining binned luminosity
-function estimates from different data sets.  The emissivity
-determinations from the luminosity function derived from a
-variability-selected sample observed using the Sloan
+%such an integration limit is likely only justified if the faint-end
+%slope of the luminosity function is sufficiently shallow.  This issue
+%also affects some other models in the literature, such as those
+%presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
+%and \citet{2018arXiv180104931P}.
+%\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
+%$M_{1450}=-19$.  However, their model strongly disagrees with our
+%inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
+%biases resulting from inhomogeneously combining binned luminosity
+%function estimates from different data sets.  The emissivity
+%determinations from the luminosity function derived from a
+%variability-selected sample observed using the Sloan
 %% JFH Sloan telescopee --> SDSS telescope
-telescope and the
-Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
-agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
-redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
-The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
-not included in our analysis, and therefore provides a cross-check.
-(This sample also does not overlap with the variability-selected
-sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
-\citet{2013A&A...551A..29P} assume constant double power law
-luminosity function slopes with a break at $z=2.2$ and assume a pure
-luminosity evolution.  This leads to a discontinuity in the emissivity
-evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
-convert their $g$-band magnitudes to $M_{1450}$ and integrate the
-resultant luminosity function down to our two chosen integration
-limits with our chosen SED for a direct comparison.
-Figure~\ref{fig:e912_2} also shows the model presented by
-\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
-which the faint-end slope is assumed to stay constant with redshift.
-Although the emissivity evolution in this model is continuous at
-$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
-smooth.  This model agrees with our $M_{1450}<-18$ result to a better
-degree relative to the \citet{2013A&A...551A..29P} model, bjt
+%telescope and the
+%Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
+%agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
+%redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
+%%% GW: At z>2.2 the disagreement is much larger than 10-30 percent!!!
+%The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
+%not included in our analysis, and therefore provides a cross-check.
+%(This sample also does not overlap with the variability-selected
+%sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
+%\citet{2013A&A...551A..29P} assume constant double power law
+%luminosity function slopes with a break at $z=2.2$ and assume a pure
+%luminosity evolution.  This leads to a discontinuity in the emissivity
+%evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
+%convert their $g$-band magnitudes to $M_{1450}$ and integrate the
+%resultant luminosity function down to our two chosen integration
+%limits with our chosen SED for a direct comparison.
+%Figure~\ref{fig:e912_2} also shows the model presented by
+%\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
+%which the faint-end slope is assumed to stay constant with redshift.
+%Although the emissivity evolution in this model is continuous at
+%$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
+%smooth.  This model agrees with our $M_{1450}<-18$ result to a better
+%degree relative to the \citet{2013A&A...551A..29P} model, bjt
 %% JFH bjt --> but
-it
-results in a higher emissivity in the $M_{1450}<-21$ case.
-\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
-sample with an improved $K$-correction implementation, but, as seen in
-Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
-throughout the redshift range of their data.
-
+%it results in a higher emissivity in the $M_{1450}<-21$ case.
+%\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
+%sample with an improved $K$-correction implementation, but, as seen in
+%Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
+%throughout the redshift range of their data.
 %% JFH For the Palanque and Caditz etc. comparisons, it occurs to me that these guys
@@
 
-At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
-power law luminosity function model to a combined binned samples of
-\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
-\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
-photometric redshift $z\sim 6$ reported by
-\citet{2018MNRAS.474.2904P}.  We show the resultant
-912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
-lower side of the rectangle corresponds to the emissivity for the
-\citet{2017ApJ...847L..15O} model excluding the
-\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
-the emissivity is higher; this is shown by the upper end of the
-rectangle.  Our emissivities broadly in agreement with the
-determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
-shows the determination from the fits of \citet{2015AA...578A..83G}.
-These authors also choose a break luminosity-dependent integration
-limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
-model.  The resultant emissivities are factors of 2 to 3 higher than
-our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
-puzzling at first sight, because the AGN candidates reported by
-\citet{2015AA...578A..83G} are consistent with our luminosity function
-estimates obtained without these candidates (see
-Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
-steeper than those reported by \citet{2015AA...578A..83G}.  The
-discrepancy is explained by the difference in the two luminosity
-function models at intermediate magnitudes.  We find that the data
-prefer a much brighter break luminosity than that inferred by
-\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
-their estimates.  We go into this issue in further detail in
-Appendix~\ref{sec:conv}.
-
-\citet{2018AJ....155..131M} recently extended their previous Stripe~82
-AGN sample by 1.5 magnitude and fit a double power law luminosity
-function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
-$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
-$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
-than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
-LF to our cosmology and assuming our SED result in the emissivities
-shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
-measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
-higher than their measurement for $M_{1450}<-18$, which is not
-surprising due to the difference in the luminosity function slopes.
-The emissivity derived from the luminosity function of
-\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
-These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
-have spectroscopic redshifts.  Their reported faint-end slope is very
-flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
-all redshifts.  Their inferred emissivity is consistent with our
-estimate for $M_{1450}< -21$.  Their emissivity does not change
-significantly with the integration limit due to the shallow faint-end
-slope.  As a result, our $M_{1450}< -18$ determination of the
-emissivity is considerably higher than their estimate.  We also
-compare our emissivities with the determinations reported by
-\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
-emissivity in reasonable agreement with our model for $M_{1450}<-21$
-at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
-recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.
-
-At low redshifts, \citet{2009A&A...507..781S} combined data from the
-Hamburg/ESO survey and the SDSS to measure a quasar luminosity
-function at $z=0$ in their $B_J$ band to minimize host galaxy
-contribution.  We convert their $B_J$ magnitudes (Vega system) to
-$M_{1450}$ (AB) as
-\begin{equation}
-  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
-\end{equation}
-In this magnitude system, the luminosity function reported by
-\citet{2009A&A...507..781S} has a very faint break luminosity of
-$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
-integrate this luminosity function down to our limiting magnitudes of
-$M_{1450}=-18$ and $-21$.  The resultant values are shown in
-Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
-between the \citet{2009A&A...507..781S} measurements.  The convergence
-in the emissivity is slower in their measurements than in our models
-because of the shallower faint-end slope at this redshift in our model
-($\beta\sim -1.22$).
+%At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
+%power law luminosity function model to a combined binned samples of
+%\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
+%\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
+%photometric redshift $z\sim 6$ reported by
+%\citet{2018MNRAS.474.2904P}.  We show the resultant
+%912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
+%lower side of the rectangle corresponds to the emissivity for the
+%\citet{2017ApJ...847L..15O} model excluding the
+%\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
+%the emissivity is higher; this is shown by the upper end of the
+%rectangle.  Our emissivities broadly in agreement with the
+%determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
+%shows the determination from the fits of \citet{2015AA...578A..83G}.
+%These authors also choose a break luminosity-dependent integration
+%limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
+%model.  The resultant emissivities are factors of 2 to 3 higher than
+%our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
+%puzzling at first sight, because the AGN candidates reported by
+%\citet{2015AA...578A..83G} are consistent with our luminosity function
+%estimates obtained without these candidates (see
+%Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
+%steeper than those reported by \citet{2015AA...578A..83G}.  The
+%discrepancy is explained by the difference in the two luminosity
+%function models at intermediate magnitudes.  We find that the data
+%prefer a much brighter break luminosity than that inferred by
+%\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
+%their estimates.  We go into this issue in further detail in
+%Appendix~\ref{sec:conv}.
+
+%\citet{2018AJ....155..131M} recently extended their previous Stripe~82
+%AGN sample by 1.5 magnitude and fit a double power law luminosity
+%function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
+%$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
+%$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
+%than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
+%LF to our cosmology and assuming our SED result in the emissivities
+%shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
+%measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
+%higher than their measurement for $M_{1450}<-18$, which is not
+%surprising due to the difference in the luminosity function slopes.
+%The emissivity derived from the luminosity function of
+%\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
+%These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
+%have spectroscopic redshifts.  Their reported faint-end slope is very
+%flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
+%all redshifts.  Their inferred emissivity is consistent with our
+%estimate for $M_{1450}< -21$.  Their emissivity does not change
+%significantly with the integration limit due to the shallow faint-end
+%slope.  As a result, our $M_{1450}< -18$ determination of the
+%emissivity is considerably higher than their estimate.  We also
+%compare our emissivities with the determinations reported by
+%\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
+%emissivity in reasonable agreement with our model for $M_{1450}<-21$
+%at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
+%recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.
+
+%At low redshifts, \citet{2009A&A...507..781S} combined data from the
+%Hamburg/ESO survey and the SDSS to measure a quasar luminosity
+%function at $z=0$ in their $B_J$ band to minimize host galaxy
+%contribution.  We convert their $B_J$ magnitudes (Vega system) to
+%$M_{1450}$ (AB) as
+%\begin{equation}
+%  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
+%\end{equation}
+%In this magnitude system, the luminosity function reported by
+%\citet{2009A&A...507..781S} has a very faint break luminosity of
+%$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
+%integrate this luminosity function down to our limiting magnitudes of
+%$M_{1450}=-18$ and $-21$.  The resultant values are shown in
+%Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
+%between the \citet{2009A&A...507..781S} measurements.  The convergence
+%in the emissivity is slower in their measurements than in our models
+%because of the shallower faint-end slope at this redshift in our model
+%($\beta\sim -1.22$).
+
+\subsection{Comparison to the literature}
+
+Before proceeding to derive estimates of the quasar contribution to the IGM \ion{H}{i} photoionization rate
+from the fitted 912\,\AA\ emissivity, it is instructive to compare our results to recent estimates from
+the literature\footnote{We do not compare to \citet{2017MNRAS.466.1160M} due to an error in their analysis.
+Integration of the 912\,\AA\ emissivity to $M_{1450}^\mathrm{lim}=-19$ with their double power law
+QLF parameterization as a function of redshift yields values 13--75 per cent higher than those implied by their Equation 9.
+This also explains the striking discrepancy to literature values at $z<3$ (their Figure 4).}.
+The various blue symbols in Figure~\ref{fig:e912_2} show emissivity values that we have computed
+from other recent QLF determinations in narrow redshift ranges.
+The various curves show emissivities derived from parametric QLF model fits over larger redshift ranges,
+or fits to $\epsilon_{912}\left(z\right)$. All QLFs using different magnitude systems have been converted to
+$M_{1450}$ with the \citet{2015MNRAS.449.4204L} SED,
+and all QLFs have been adjusted to our cosmology.
+For the $z\simeq 0$ QLF reported by \citet{2009A&A...507..781S} we
+convert their $B_J$ magnitudes in the Vega system to our AB magnitudes
+as $M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59$.
+Lyman limit emissivities have been consistently derived using 
+Equation~\eqref{eqn:sed} and for our adopted magnitude limits whenever possible.
+We note that due to strong covariance in the QLF parameters
+it is not straightforward to compute statistical errors of $\epsilon$ from given QLF fits,
+and we refrained from using the incorrect procedures applied by \citet{2015MNRAS.451L..30K}.
+\textbf{GW: Emphasize again that our error bars are correct and superior to Khaire's!}
+
+The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model adopted by
+\citet{2012ApJ...746..125H}, which is based on the bolometric luminosity function from \citet{2007ApJ...654..731H}.
+The bolometric emissivity derived by \citet{2007ApJ...654..731H} converges for luminosities $L>0$
+due to their shallow faint-end QLF slope, which should yield a higher 912\,\AA\ emissivity for
+both our adopted magnitude limits. We attribute much of the discrepancy to the conversion from bolometric
+to 912\,\AA\ emissivity assumed by \citet{2007ApJ...654..731H}.
+Figure~\ref{fig:e912_2} also shows the emissivity curve from \citet{2015ApJ...813L...8M}
+that was inspired by recent QLF fits including the highly debated \citet{2015AA...578A..83G} results.
+The emissivity adopted by \citet{2015ApJ...813L...8M} exceeds our fits by more than a factor of two
+at $z\la 1$ and $z\ga 4$. Moreover, we stress that our emissivities have been derived for fixed magnitude
+limits $M_{1450}^\mathrm{lim}$ at all redshifts (Equation~\eqref{eqn:epsilon}), whereas other authors have
+adopted magnitude limits $M_{1450}^\mathrm{lim}\left(z\right)=M_*\left(z\right)+5$ that vary with break
+magnitude and redshift \citep{2015AA...578A..83G,2015ApJ...813L...8M,2015MNRAS.451L..30K,2018arXiv180104931P}.
+We deem the latter convention to be physically unfounded, because (i) the customary QLF double power-law
+parameterization lacks a deeper physical meaning, (ii) $M_*$ decreases by more than five magnitudes
+with redshift (Figure~\ref{fig:evoln}, see also \citealt{2013ApJ...768..105M} and \citealt{2016ApJ...829...33Y}),
+and (iii) the various QLF fits at the same redshift are highly discordant (Appendix~\ref{sec:qlfliterature}).
+Inhomogeneous magnitude limits lead to artificial scatter in the derived emissivities if the faint-end slope of
+the QLF is not sufficiently shallow. Our fixed magnitude limits bracket a reasonable range of QLF extrapolations
+beyond the range covered by current data, whereas a varying limit $M_*+5$ includes feeble
+$M_{1450}\simeq -18$ AGN at $z<0.6$, but excludes verified $M_{1450}\simeq -24$ quasars at $z\simeq 6$ (Figure~\ref{fig:evoln}).
+
+\citet{2013A&A...551A..29P,2016A&A...587A..41P} presented two variability-selected quasar
+samples that are not included in our analysis, and therefore provide a valuable cross-check.
+In Figure~\ref{fig:e912_2} we show the emissivities computed from their parametric model fits
+to binned QLFs at $0.68<z<4$. \citet{2013A&A...551A..29P} fitted pure luminosity evolution
+models to binned QLFs from their data set and the one by \citet{2009MNRAS.399.1755C},
+but with a discontinuity in the QLF slopes at $z=2.2$ that cause artificial discontinuities
+in the QSO number density and the emissivity. The good agreement with our inferences at
+$z<2.2$ is partially due to sample overlap. \citet{2016A&A...587A..41P} presented an
+independent sample of 13876 variability-selected quasars. They fitted their binned QLFs
+with a pure luminosity evolution model at $z<2.2$ and a luminosity and density evolution
+model at higher redshifts, imposing continuity at $z=2.2$. The emissivity computed from
+their QLF is in good agreement with our results at $z<2.2$, but is systematically lower at
+higher redshifts. \citet{2017A&A...608A..64C} corrected an apparent error in the bandpass
+correction applied by \citet{2016A&A...587A..41P} that results in a higher QLF at $z>3$.
+However, his higher inferred $\phi_*$ at $z=0$ causes a 30--60 per cent higher emissivity
+at $z<2.2$ compared to our inferences. Since neither \citet{2013A&A...551A..29P,2016A&A...587A..41P}
+nor \citet{2017A&A...608A..64C} fitted the QLF in narrow redshift bins from unbinned quasar data,
+it remains unclear whether there is a systematic difference between colour-selected and
+variability-selected samples at $z<2.2$. As variability-selected samples to not probe the faint end of the
+QLF at $z>3$, inferences of the high-redshift quasar number density and emissivity are highly uncertain at present.
+
+We also calculate the 912\,\AA\ emissivities from various determinations of the UV QLF in narrow redshift ranges
+\citep{2009A&A...507..781S,2012ApJ...755..169M,2015AA...578A..83G,2017ApJ...847L..15O,2018PASJ...70S..34A,2018AJ....155..131M,2018MNRAS.474.2904P}.
+All these QLF determinations are not fully independent from ours due to partial sample overlap,
+mostly from SDSS at the bright end. We use both QLF determinations from \citet{2017ApJ...847L..15O}
+with and without including a faint X-ray-selected $z\sim 6$ AGN candidate \citep{2018MNRAS.474.2904P},
+and indicate the emissivities with a box in Figure~\ref{fig:e912_2}.  
+For $M_{1450}<-21$ our $\epsilon_{912}\left(z\right)$ parameterization and the individual values
+are generally consistent with those computed from other QLFs in narrow redshift ranges,
+apart from the results by \citet{2015AA...578A..83G} that have been disputed by several studies
+\citep[][see Appendix~\ref{sec:conv} for further discussion]{2015MNRAS.453.1946G,2016MNRAS.463..348V,2017MNRAS.465.1915R,2018AJ....155..131M,2018MNRAS.474.2904P}. 
+As detailed in Section~\ref{sect:samplesel}, the \citet{2012ApJ...755..169M} QLF at $z\sim 4$ -- and hence the
+derived emissivity -- is underestimated due to systematic error in their photometric redshifts,
+while their $z\sim 3.2$ results likely suffer from systematic uncertainty in the SDSS selection function
+\citep{2011ApJ...728...23W,2012ApJS..199....3R,2013ApJ...773...14R}.
+
+Integration to $M_{1450}=-18$ results in larger discrepancies due to extrapolation of the QLF
+with an uncertain faint-end slope. 
+\citet{2018PASJ...70S..34A} obtained a very flat faint-end slope $\beta=-1.30\pm 0.05$
+that is inconsistent with our determinations at all redshifts. Since they selected only
+point sources, they might be missing a significant fraction of AGN at $M_{1450}>-23.5$.
+In addition, only $4.6$ per cent of their AGN have spectroscopic redshifts,
+such that their correction for contamination is very rough.
+The large difference in the inferred $M_{1450}<-18$ emissivity at $z\simeq 5$ with respect to
+\citet{2018AJ....155..131M} is due to their shallower faint-end slope $\beta=-1.97\pm 0.09$
+compared to our result at this redshift ($\beta=-2.30^{+0.11}_{-0.08}$). We attribute the difference
+in the faint-end slope to the fixed bright-end slope $\alpha=-4$ in \citet{2018AJ....155..131M}
+that is larger than our measurements at $z>3.5$ (Figure~\ref{fig:evoln}). 
+Similarly, \citet{2017ApJ...847L..15O} fixed the bright-end slope to $\alpha=-2.8$ which had been
+determined by \citet{2016ApJ...833..222J} from a single power-law fit to the bright end of the QLF.
+Our bright-end slopes are inconsistent with such high values at all redshifts, indicating that single
+power-law fits to a limited range in magnitude yield only approximate estimates of $\alpha$,
+biasing the other derived QLF parameters, quasar number densities and emissivities.
+Full double-power law fits to unbinned data over a wide magnitude range are required.
 
@@
 \label{sec:gammahi}
+
+\textbf{
+Comments from GW:\\
+1. Simplify spectral index discussion\\
+2. Introduce all variables in the radiative transfer equation\\
+3. Helium can be ignored due to the small HI cross section at 228\AA\\
+4. Add more recent Gamma measurements (see Davies et al. 2018)\\
+5. Omit Giallongo error bars and state that they assumed the local source approximation.\\
+6. Add caveats for assumed column density distribution at $z>4$\\
+7. All models have issues at $z>5.5$ as they assume a homogeneous UVB and extrapolate MFP measurements.\\
+8. KH15 are not comparable to our results (emissivity integration limits). 
+}
 

### 2018-06-11 Paper/paper.tex
Update Section 1

@@
 \citet{2015AA...578A..83G} could be explained by contamination from
-the AGN host galaxies for faint AGN.
+the host galaxies for faint AGN.
 
@@
 A straightforward way towards a more robust understanding of AGN
-contribution to reionization is to determine the evolution of the AGN
-UV luminosity function.  However, many recent inferences of the
-luminosity function suffer from inconsistencies arising from
-inhomogeneous selection and mixing of AGN data.  This has resulted in
-a large scatter in the inferred high-redshift hydrogen-ionizing AGN
-emissivity between various recent studies.  For instance, there is an
-order of magnitude scatter between various estimates of the
-hydrogen-ionizing AGN emissivity at $z=5$--$6$
-\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
-  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
-  2017ApJ...847L..15O}.  Our aim in this paper is to address this
-issue, by constructing an AGN sample with robust redshift and
-completeness estimates and homogeneous assumptions of the cosmology
-and intrinsic AGN spectrum.  We discuss our sample construction in
+contribution to UV background is to determine the evolution of the AGN
+UV luminosity function.  To this end, several estimates of the
+luminosity function at various redshifts have been published in the
+last decade \citep{2009A&A...507..781S, 2011ApJ...728L..26G,
+  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
+  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
+  2017ApJ...847L..15O, 2018PASJ...70S..34A}.  However, many of these
+inferences of the luminosity function suffer from inconsistencies
+arising from inhomogeneous selection and mixing of AGN data.  Some of
+the data sets analysed in these studies consist of photometric
+samples, which is likely to increase sample contamination.  In some
+studies, distinct data sets binned differently in redshift and
+magnitudes were inhomogeneously combined.  Some authors imposed
+restricted priors on parameters while fitting luminosity function
+models, e.g., by fixing luminosity function slopes to certain values,
+which may bias the result.  Finally, some studies arbitrarily excluded
+certain data sets.  This has resulted in a large scatter in the
+inferred high-redshift hydrogen-ionizing AGN emissivity between
+various recent studies.  For instance, there is an order of magnitude
+scatter between various estimates of the hydrogen-ionizing AGN
+emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
+  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
+  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
+aim in this paper is to address this issue, by constructing an AGN
+sample with robust redshift and completeness estimates and homogeneous
+assumptions of the cosmology and intrinsic AGN spectrum.  After
+constructing such a sample, we derive the UV luminosity function of
+AGN from redshift $z=0$--$7$ and estimate the AGN contribution to the
+UV background.  We discuss our sample construction in
 Section~\ref{sec:sample}.  Our derived luminosity functions are

### 2018-07-10 Paper/paper.tex
Update
Changes from Gabor

@@
 \usepackage{siunitx}
-\def\lya{Ly$\alpha$~}
 \usepackage{color}
@@
 \newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
+\def\lya{Ly$\alpha$~}
 \def\HI{\hbox{H~$\scriptstyle\rm I$}}
@@
 \author[Kulkarni et al.]
-       {{Girish Kulkarni$^{1}$\thanks{Email: kulkarni@ast.cam.ac.uk},
-           G\'abor Worseck$^{2}$
-           and Joseph F.~Hennawi$^{3}$} \\
-         $^1$Institute of Astronomy and Kavli Institute of Cosmology,
+       {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
+           G\'abor Worseck$^{3}$
+           and Joseph F.~Hennawi$^{4}$} \\
+         $^1$Institute of Astronomy,
+         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
+         UK \\
+         $^2$Kavli Institute of Cosmology,
          University of Cambridge, Madingley Road, Cambridge CB3 0HA,
@@
          $^3$Department of Physics, Broida Hall, UC Santa Barbara,
-         Santa Barbara, CA 93106-9530 USA}
+         Santa Barbara, CA 93106-9530, USA}
        \date{Accepted ---. Received ---; in original form ---}
 
-\pubyear{2016}
+\pubyear{2018}
 
@@
 interest of a large body of work over the last four decades
-\citep{1978A&A....68...17M, 1983ApJ...269..352S, 1988ApJ...325...92K,
-  1988MNRAS.235..935B, 1993ApJ...406L..43H, 1994ApJ...421..412W,
-  1995AJ....110...68S, 1995AJ....110.2553K, 1995ApJ...438..623P,
-  2000MNRAS.317.1014B, 2001AJ....121...54F, 2004AJ....128..515F,
-  2006AJ....131.2766R, 2007ApJ...654..731H, 2009MNRAS.392...19C,
-  2010AJ....139..906W, 2011ApJ...728L..26G, 2013ApJ...773...14R,
-  2013ApJ...768..105M, 2015AA...578A..83G, 2015ApJ...798...28K,
-  2016ApJ...829...33Y, 2016ApJ...833..222J}.  Determination of the AGN
-luminosity function constrains models of the build-up of supermassive
-black holes \citep{1982MNRAS.200..115S, 2004ApJ...602..603Y,
-  2007ApJ...654..731H, 2008ApJ...679..118S, 2009A&A...493...55E,
-  2000ApJ...531...42H, 2010MNRAS.401.2531A, 2013ApJ...773...14R,
-  2014ApJ...787...73D, 2015MNRAS.448.3603D, 2015MNRAS.452..575S,
-  2016MNRAS.462..190R}.  Due to the incidence of supermassive black
-holes in most galaxies, the tight scaling relations observed to exist
-between the mass of these black holes and properties of their host
-galaxies, and the increasing consensus that AGN activity feeds back on
-the host galaxy evolution, the AGN luminosity function also constrains
-models of galaxy formation \citep{2006ApJ...650...42L,
+\citep{1968ApJ...151..393S, 1978A&A....68...17M, 1983ApJ...269..352S,
+  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
+  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
+  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
+  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
+  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
+  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
+  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J}.
+Determination of the AGN luminosity function constrains models of the
+build-up of supermassive black holes \citep{1982MNRAS.200..115S,
+  2004ApJ...602..603Y, 2007ApJ...654..731H, 2008ApJ...679..118S,
+  2009A&A...493...55E, 2000ApJ...531...42H, 2010MNRAS.401.2531A,
+  2013ApJ...773...14R, 2014ApJ...787...73D, 2015MNRAS.448.3603D,
+  2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the incidence of
+supermassive black holes in most galaxies, the tight scaling relations
+observed to exist between the mass of these black holes and properties
+of their host galaxies, and the increasing consensus that AGN activity
+feeds back on the host galaxy evolution, the AGN luminosity function
+also constrains models of galaxy formation \citep{2006ApJ...650...42L,
   2008MNRAS.385.1846M}.  Finally, thanks to their relative brightness
@@
 uncertain.  High-redshift galaxies down to rest-frame UV magnitude
-$M_\mathrm{UV}=-12.5$ ($L\sim 10^{-3}L^*$) at $z=6$
+$M_\mathrm{UV}=-12.5$ ($L\sim 10^{-3}L^*_\mathrm{galaxies}$) at $z=6$
 \citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
@@
 LyC photons has been measured in only a few comparatively bright
-($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).  The
-escape fraction in these galaxies reveals a broad distribution from
-less than 2\% to more than 80\% \citep{2010ApJ...725.1011V,
-  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
-  2016A&A...585A..48G, 2017MNRAS.468..389J, 2018arXiv180506071S,
-  2018arXiv180601741F, 2018arXiv180511621M, 2018arXiv180303655C}, but
-the average escape fraction is typically lower than 20\%.  Statistical
-constraints from \HI\ column density measurements in gamma-ray burst
-(GRB) afterglow spectra suggest an even lower escape fraction of 0.5\%
-\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
-This is a challenge for reionization models, which require an escape
-fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
-\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
-An enhanced incidence of high-redshift AGN may also be consistent with
-the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
-of galaxies relative to a Schechter function
-\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
-  2015MNRAS.452.1817B} and the hard spectra of these galaxies
-\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
-Finally, AGN may also provide a natural explanation for the large
-scatter in the \lya opacity between different quasar sightlines close
-to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
-%% JFH Please cite new paper by eilers et al. here, not yet on archive. 
+($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
+($z < 4$).  The escape fraction in these galaxies reveals a broad
+distribution from less than 2\% to more than 80\%
+\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
+  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
+  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
+  2018arXiv180303655C}, but the average escape fraction is typically
+lower than 20\%.  Statistical constraints from \HI\ column density
+measurements in gamma-ray burst (GRB) afterglow spectra suggest an
+even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
+  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
+reionization models, which require an escape fraction of about 20\% in
+galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
+  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
+high-redshift AGN may also be consistent with the shallow bright-end
+slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
+a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
+  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
+these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
+  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
+explanation for the large scatter in the \lya opacity between
+different quasar sightlines close to redshift $z=6$
+\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
 These opacity fluctuations extend to substantially larger scales
@@
 density of AGN at $z\sim 6$ can lead to a much earlier
-\HeII\ reionization.  For instance, He~\textsc{ii} reionization is
-complete at $z=4.5$ in the model of \citet{2015ApJ...813L...8M},
-compared to $z=3$ in the standard scenario
-\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
-result in higher IGM temperatures due to the associated photoheating.
-\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
-mean density is twice as much in AGN-dominated reionization models as
-the standard models at $z=3.5$--$5$, in conflict with constraints from
-the \lya forest.  This inconsistency could be avoided by postulating a
-reduced escape fraction of \HeII-ionizing photons in AGN, but it is
-difficult to reconcile this with a unit escape fraction of
-hydrogen-ionizing photons that is required to explain the Ly$\alpha$
-opacity fluctuations.  Further arguments against AGN-dominated
-reionization have been presented by \citet{2016MNRAS.459.2299F}, who
-analysed the simulations of metal-line absorbers at $z\sim 6$.
+\HeII\ reionization (see also \citealt{2017MNRAS.471..255K}).  For
+instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
+model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
+standard scenario \citep{2012ApJ...746..125H}.  Such early
+\HeII\ reionization will also result in higher IGM temperatures due to
+the associated photoheating.  \citet{2017MNRAS.468.4691D} found that
+the temperature of the IGM at mean density is twice as much in
+AGN-dominated reionization models as the standard models at
+$z=3.5$--$5$, in conflict with constraints from the \lya forest.  This
+inconsistency could be avoided by postulating a reduced escape
+fraction of \HeII-ionizing photons in AGN, but it is difficult to
+reconcile this with a unit escape fraction of hydrogen-ionizing
+photons that is required to explain the Ly$\alpha$ opacity
+fluctuations.  Further arguments against AGN-dominated reionization
+have been presented by \citet{2016MNRAS.459.2299F}, who analysed the
+simulations of metal-line absorbers at $z\sim 6$.
 \citet{2016MNRAS.459.2299F} find that in their cosmological radiation
@@
 assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
-\citep{2002ApJ...565..773T}, which somewhat harder than recent
+\citep{2002ApJ...565..773T}, which is somewhat harder than recent
 measurements ($L_\nu\propto\nu^{-1.7}$) by
@@
 \citet{2015AA...578A..83G} could be explained by contamination from
-the host galaxies for faint AGN.
-
-%---
+the host galaxies for faint AGN \citep[see
+  also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.
 
@@
 reionization.  We summarise our findings in Section~\ref{sec:conc}.
-
-%% -- some people use photo-zs
-%% -- some people mix binned data
-%% -- some people fix slopes
-%% -- some people exclude some data arbitrarily
 
@@
 
-We started by compiling the samples of recent photometric rest-frame UV-optical
-quasar surveys. The restriction to UV-optical surveys was mainly
-driven by our science goal to characterise the UV luminosity function
-of Type~1 quasars. X-ray-selected samples are less suited for this
-purpose due to spectroscopic incompleteness and the $\sim 0.4$\,dex
-scatter in the conversion from X-ray to UV luminosity
+We started by compiling the samples of recent photometric rest-frame
+UV-optical quasar surveys. The restriction to UV-optical surveys was
+mainly driven by our science goal to characterise the UV luminosity
+function of Type~1 quasars. X-ray-selected samples are less suited for
+this purpose due to spectroscopic incompleteness and the $\sim
+0.4$\,dex scatter in the conversion from X-ray to UV luminosity
 \citep{2010A&A...512A..34L, 2015MNRAS.453.1946G, 2016ApJ...819..154L}
@@
 survey selection functions in electronic form, either from the
-publication or by request from the authors. As a reference for future surveys we
-make them electronically available here
-%% JFH rather than publish them here say ``we make them electronically available here''. Cite an appendix where
-%% you do this. 
-in modified and homogenised form
-(Section~\ref{sect:datahom}).
+publication or by request from the authors. As a reference for future
+surveys we make them electronically available here in modified and
+homogenised form (see Section~\ref{sect:datahom} and
+Appendix~\ref{sec:code}).
 
@@
 extinction \citep{2010AJ....139.2360S}. To limit systematic
-uncertainties in the correction for host galaxy light
-\citep[detailed in][]{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 9365
+uncertainties in the correction for host galaxy light \citep[detailed
+  in][]{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 9365
 $g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint
@@
 \label{sect:datahom}
-
-%% JFH This section is long tedious and hard to follow. Perhaps we
-%% should put a brief description here, relegate these details to the
-%% appendix, and in the appendix, structure this section by
-%% sub-sections for each individual survey.
 
@@
 
-%% JFH We need a better roadmap here for where this section is going. 1) Binned estimates 2) individual
-%% fits in redshift bins. 3) examining redshift evolution. 4) attempting a joint fit.
-%% GW: Agreed. Modified the roadmap.
-
-After homogenising the samples and selection functions we are in a position
-to compute the UV luminosity function of AGN. We begin our analysis by computing
-binned estimates of the luminosity function as a function of magnitude in several redshift intervals.
-We then perform parametric maximum-likelihood fits of the luminosity function in the individual redshift bins,
-examine the resulting parameters as a function of redshift, and attempt a joint fit in magnitude and redshift.
-For simplicity we will use the notation $M\equiv M_{1450}$ in the following.
+After homogenising the samples and selection functions we are in a
+position to compute the UV luminosity function of AGN. We begin our
+analysis by computing binned estimates of the luminosity function as a
+function of magnitude in several redshift intervals.  We then perform
+parametric maximum-likelihood fits of the luminosity function in the
+individual redshift bins, examine the resulting parameters as a
+function of redshift, and attempt a joint fit in magnitude and
+redshift.  For simplicity we will use the notation $M\equiv M_{1450}$
+in the following.
 
@@
   \frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}=\frac{c}{H_0}\frac{d_L^2\left(z\right)}
-       {\left(1+z\right)^2\sqrt{\Omega_\mathrm{m}\left(1+z\right)^3+\Omega_\Lambda}}
+       {\left(1+z\right)^2\left[\Omega_\mathrm{m}\left(1+z\right)^3+\Omega_\Lambda\right]^{1/2}}
   \label{eqn:dvdzdo}
@@
   \end{center}
-  \caption{Redshift evolution of the four double power law parameters from the
-    redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical error
-    bars show one-sigma (68.26\%) statistical uncertainties, whereas horizontal
-    error bars show widths of the redshift bins.  We identify the
-    general evolutionary trends of each of these parameters from the
-    bins shown by the filled symbols.  The open symbols show bins that
-    appear to be offset from these trends, likely due to unknown
-    systematic errors.  The open circles at $2.2<z<3.5$ show the
-    BOSS sample, while the bins at $z < 0.6$ contain AGN from the SDSS
-    and 2SLAQ data sets.  See Section~\ref{sec:bins} for further
-    details.}
+  \caption{Redshift evolution of the four double power law parameters
+    from the redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical
+    error bars show one-sigma (68.26\%) statistical uncertainties,
+    whereas horizontal error bars show widths of the redshift bins.
+    We identify the general evolutionary trends of each of these
+    parameters from the bins shown by the filled symbols.  The open
+    symbols show bins that appear to be offset from these trends,
+    likely due to unknown systematic errors.  The open circles at
+    $2.2<z<3.5$ show the BOSS sample, while the bins at $z < 0.6$
+    contain AGN from the SDSS and 2SLAQ data sets.  See
+    Section~\ref{sec:bins} for further details.}
   \label{fig:evoln}
@@
 By assuming broad, uniform priors, we obtain posterior probability
-distributions for these parameters using MCMC \citep[e.g.,][]{jaynes}.
+distributions for these parameters using the Markov Chain Monte Carlo technique \citep[MCMC, e.g.,][]{jaynes}.
 The joint posterior probability distribution of the model parameters
@@
 \begin{multline}
-  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
-  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, \phi(M,z) f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z}.
+  S = -2\sum_{i=1}^{N_\mathrm{QSO}}\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
+  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, \phi(M,z) f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z},
   \label{eqn:S}
 \end{multline}
-where $N$ is the total number of quasars in the redshift bin and the
-luminosity integral in the second term on the right hand side is on
-the surveyed range of $M$.  We use the \texttt{emcee} code
-\citep{2013PASP..125..306F} for MCMC.
-
-%% JFH SOmewhere indicate taht this procedure of ubninned LF estimates is standard practice. 
+where the integral over magnitude is on the surveyed range of $M$.  We
+use the \texttt{emcee} code \citep{2013PASP..125..306F} for MCMC.
+
 The above likelihood can also be understood as the limit of the
@@
 Our estimates for the double power law luminosity function are shown
-in Figure~\ref{fig:mosaic} for 25 redshift bins.
-%% JFH you are confusing terminology. posterior median and best-fit are not generally the same and you should
-%% not refer to them as such. You are also not explaning what you mean by posterior median. Is this the
-%% median of the individual marginalized posteriors? Or is it the median of the function that results from
-%% the posterior distribution? Those are not generally the same, unless the model is linear in the parameters,
-%% which it is not. Finally, best fit always means maximum likelihood, and that is certainly not what you are
-%% plotting here, so don't say best-fit. You can say as our ``adopted model'' or ``fiducial model fit'' or
-%% something like that. I would just explain waht you plot. 
-%% GW: Agreed. We need some explanation here. I've changed "best-fit" to "adopted". We also need to explain the meaning of our errors.
-\textbf{GW: Definition of adopted model and error bars}
-We adopt the posterior median as our fiducial model fit, and the 68.26\% credible interval as the uncertainty on $\phi$.
-Consistent with previous studies, the double power law model provides an excellent
-description of the luminosity function model over almost the complete
-range of redshifts spanned by the data.
-\textbf{GW agrees with JFH here. Move the discussion of $z\sim 6$ priors to Fig. 4}
-It is only in the highest
-redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
-power law.  In this bin, the resultant posterior distribution of the
-break magnitude $M_*$ is bimodal with favoured values at the faint
-($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
-literature $z\sim 6$ quasars have been assumed to lie on the bright
-end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
-comparison with the luminosity function at lower redshifts ($z<5.5$)
-suggests that these AGN should instead be understood to describe the
-faint-end of a double power law.
-%% JFH Okay so you need to be more clear here that what you mean is that the trend
-%% from the plot is that M_star gets progressively brighter with redshift. This is not
-%% obvious given what you write here. Indeed, it is not super obvious until one looks at FIgure 4, which
-%% anyway has this prior already in it. 
-Therefore, in light of the
-low-redshift data, we use restricted priors in this
-%% JFH Which redshift bin?? Make it more clear that this prior is put in to avoid bi-modal distributions
-%% and it is informed by inspection of the lower redshift data. 
-redshift bin: we
-restrict the bright-end slope $\alpha$ to values less than $-4$,
-%% JFH Something does not jive here, since the error bars you are showing on the high-z poitns cross
-%% the -4 value of your prior? So either your prior is not a hard prior, or it is not exactly at -4
-which
-is equivalent to forcing $M_*$ to be at the bright end of the data.
-Other parameters continue to have wide uniform priors.  This also
-illustrates the importance of analysing the evolution of the QLF with
-redshift.
+in Figure~\ref{fig:mosaic} for 25 redshift bins.  We adopt the
+posterior median as our fiducial model fit, and the 68.26\%
+equal-tailed credible interval as the uncertainty on $\phi$.
+Consistent with previous studies, the double power law model provides
+an excellent description of the luminosity function model over almost
+the complete range of redshifts spanned by the data.  It is only in
+the highest redshift bin ($z=5.5$--$6.5$) that the data seem to favour
+a single power law.  In this bin, the resultant posterior distribution
+of the break magnitude $M_*$ is bimodal with favoured values at the
+faint ($M_*>-18$) and bright end of the data ($M_*<-30$).  While in
+the literature $z\sim 6$ quasars have been assumed to lie on the
+bright end of the luminosity function
+\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
+function at lower redshifts ($z<5.5$) suggests that these AGN should
+instead be understood to describe the faint-end of a double power law.
+As we discuss below, $M_*$ gets progressively brighter with redshift.
+Therefore, after inspecting the data at lower redshifts, we use
+restricted priors in the $z=5.5$--$6.5$ redshift bin in order to avoid
+bimodal distributions.  In this bin, we restrict the bright-end slope
+$\alpha$ to values less than $-4$, which is equivalent to forcing
+$M_*$ to be at the bright end of the data.  Other parameters continue
+to have wide uniform priors.  This also illustrates the importance of
+analysing the evolution of the QLF with redshift.
 
@@
 $10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope
-$\alpha$ has significant scatter,
-%% JFH most likely attributable to systematic erorrs in the measurements.
-but still shows a trend towards more
+$\alpha$ has significant scatter but still shows a trend towards more
 negative values, i.e., steeper luminosity function bright ends, at
 high redshifts. Finally, the faint end slope also shows signs of
-increasing steepness towards high redshifts, but with a marked discontinuity at $2.2\le z<3.5$.
-%It stays roughly
-%constant up to this redshift, and the drops to increasingly negative
-%values of close to $-2.5$ at high redshifts, indicating a steeper
-%faint end.
-
-%% JFH I think you need to show at least one corner plot for your fits somewhere in the paper.
-
+increasing steepness towards high redshifts, but with a marked
+discontinuity at $2.2\le z<3.5$.
 %% JFH I think before imposing this prior by hand it might be useful to show the degeneracies that
@@
 selection function that critically depends on the assumed quasar
-spectral energy distribution, the IGM parameterization,
-and the modeled photometric errors at the targeted magnitude limit of the single-epoch SDSS imaging
-\citep{2011ApJ...728...23W,2012ApJS..199....3R,2013ApJ...773...14R}.  Consequently, we
-exclude all BOSS quasars from further analysis.
-
-%% JFH I think another point worth mentioning is that the BOSS survey is never working at high completeness,
-%% (this you can quantify from your selection function). That means that the resevoir of QSOs that can
-%% scatter into or out of the sample is large, making one susceptible to errors in the selection function
-%% (or at the faint end variations in the photometric senstivity 
-%% GW: Good point, BOSS was working at the limit of SDSS imaging, so photometric errors are important.
-I've added a few words on this and added a reference to Ross et al.
-2012 who highlight the importance of modeling the photometric error at the SDSS magnitude limit.
-This was done using Stripe 82 data, but it's a model nonetheless.
+spectral energy distribution, the IGM parameterization, and the
+modeled photometric errors at the targeted magnitude limit of the
+single-epoch SDSS imaging
+\citep{2011ApJ...728...23W, 2012ApJS..199....3R, 2013ApJ...773...14R}.
+Consequently, we exclude all BOSS quasars from further analysis.
 
@@
 
-After excluding the redshift bins that are most obviously affected by systematic errors,
-the remaining redshift bins (filled symbols in Figure~\ref{fig:evoln}) are consistent with a
-smooth redshift evolution of the luminosity function parameters that may be
-described by parametric models. 
-%%using fewer parameters.
-\textbf{GW: We need more citations to previous parametric models, i.e. Croom, Ross, Richards, Palanque-Delabrouille, Bongiorno etc. This dates back to much earlier work using PDE and PLE models.}
-Such descriptions have been developed in the
-literature for the X-ray \citep[e.g.,][]{2015MNRAS.451.1892A} and
-bolometric luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.
-%% GW: I would always call these ``bolometric'', since truly bolometric LFs require complete samples with complete multiwavelength photometry
-Such ``global'' models of the luminosity function evolution are useful
-as they give a continuous description of the luminosity function.
-This allows one to reduce the bias introduced by binning the data in
+After excluding the redshift bins that are most obviously affected by
+systematic errors, the remaining redshift bins (filled symbols in
+Figure~\ref{fig:evoln}) are consistent with a smooth redshift
+evolution of the luminosity function parameters that may be described
+by parametric models \citep{1976A&A....53...15M, 1983ApJ...269..352S,
+  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
+  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
+  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
+  2006AJ....131.2766R, 2007A&A...472..443B, 2009MNRAS.399.1755C,
+  2013ApJ...773...14R, 2013A&A...551A..29P}.  Such descriptions have
+also been developed in the literature for the X-ray
+\citep[e.g.,][]{2015MNRAS.451.1892A} and so-called bolometric
+luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.  Such
+``global'' models of the luminosity function evolution are useful as
+they give a continuous description of the luminosity function.  This
+allows one to reduce the bias introduced by binning the data in
 arbitrary redshift bins.  By potentially allowing for extrapolations
@@
 model in Equation~(\ref{eqn:dpl}) as 
-\textbf{GW: Symbol $f$ is used for the selection function already.}
 \begin{align}
-  &\phi_*(z) = f_0(\{c_{0,i}\}, z)\nonumber\\
-  &M_*(z) = f_1(\{c_{1,i}\}, z)\nonumber\\
-  &\alpha(z) = f_2(\{c_{2,i}\}, z)\nonumber\\
-  &\beta(z) = f_3(\{c_{3,i}\}, z),
+  &\phi_*(z) = F_0(\{c_{0,j}\}, z)\nonumber\\
+  &M_*(z) = F_1(\{c_{1,j}\}, z)\nonumber\\
+  &\alpha(z) = F_2(\{c_{2,j}\}, z)\nonumber\\
+  &\beta(z) = F_3(\{c_{3,j}\}, z),
   \label{eqn:global}
 \end{align}
-where the $\{c_{j,i}\}$ are the new model parameters, and the $\{f_j\}$
+where the $\{c_{n,j}\}$ are the new model parameters, and the $\{F_j\}$
 are functions that vary smoothly with redshift $z$.  The joint
@@
 written as
-\textbf{GW: Should the set of $c_i$ be a set of $c_j$ instead?}
 \begin{equation}
-  p(\{c_i\} | \{M_i, z_i\}) \propto p(\{c_i\})p(\{M_i, z_i\} | \{c_i\}),
+  p(\{c_{n,j}\} | \{M_i, z_i\}) \propto p(\{c_{n,j}\})p(\{M_i, z_i\} | \{c_{n,j}\}),
 \end{equation}
@@
 \begin{equation}
-  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_i\}),
+  \mathcal{L}\equiv p(\{M_i, z_i\} | \{c_{n,j}\}),
 \end{equation}
@@
 $\phi(M,z)$ is given by Equation~(\ref{eqn:dpl}), but now the four
-parameters in that equation are redshift-dependent, so that
-\textbf{GW thinks the next formula can be omitted, since the fact is clear from Eq. 13.}
-\begin{multline}
-  \phi(M,z) = \phi_*(z) \left[10^{0.4(\alpha(z)+1)(M-M_*(z))}\right. \\ \left.+ 10^{0.4(\beta(z)+1)(M-M_*(z))}\right]^{-1}.
-\end{multline}
-The negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is
-a straightforward generalisation of Equation~(\ref{eqn:S}), given by
-\textbf{GW: This formula is obvious and could be omitted, indeed it is exactly Eq. 10! If we keep it we should change the nomenclature}
-\begin{multline}
-  S = -2\sum_{i=1}^N\ln\phi(M_i, z_i)\\+2\int_{M_\mathrm{min}}^{M_\mathrm{max}}dM\int_{z_\mathrm{min}}^{z_\mathrm{max}}dz\, \phi(M,z) f(M, z)\,\frac{dV}{dz},
-  \label{eqn:S2}
-\end{multline}
-where now $N$ is the total number of quasars included in the analysis,
-and the integrals in the second term on the right-hand side are over
-the complete surveyed range of magnitude and redshift, instead of
-redshift and magnitude bins.  We consider models in which the
-evolution of the four double power law parameters is modelled
-independently as in Equations~(\ref{eqn:global}), an approach
-sometimes termed as ``flexible double power law''
+parameters in that equation are redshift-dependent.  The negative
+logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ is a
+straightforward generalisation of Equation~(\ref{eqn:S}).  We consider
+models in which the evolution of the four double power law parameters
+is modelled independently as in Equations~(\ref{eqn:global}), an
+approach sometimes termed as ``flexible double power law''
 \citep{2015MNRAS.451.1892A}.  We present three such models in this
-paper.  These are shown in Figure~\ref{fig:evoln_global}.
-%% JFH Something is wrong with the flow here. You are referencing Figure 6, but have not yet discussed Figure 5. 
-%% GW changed the order of the figures. We need the LF parameters first before evaluating the individual z bins.
-The three
+paper.  These are shown in Figure~\ref{fig:evoln_global}.  The three
 models differ in the way they describe the evolution of the faint-end
@@
 \item
-  In Model 1 we assume that the functions $f_0$, $f_1$ and $f_2$ from
-  Equation~\eqref{eqn:global} are Chebyshev polynomials in $\left(1+z\right)$,
-  written as
+  In Model 1 we assume that the functions $F_0$, $F_1$ and $F_2$ from
+  Equation~\eqref{eqn:global} are Chebyshev polynomials in
+  $\left(1+z\right)$, written as
   \begin{equation}
-    f_i\left(1+z\right)=\sum_{j=0}^{n_i}c_{i,j}T_j\left(1+z\right)
+    F_i\left(1+z\right)=\sum_{j=0}^{n_i}c_{i,j}T_j\left(1+z\right)
     \label{eqn:cbs}
@@
   Chebyshev polynomials in order to arrive at a good fit with the
-  data.
-  %% JFH State that you assess this by eye
-  As we discuss below, we find that $\phi_*$, $M_*$ and
-  $\alpha$ prefer quadratic, cubic, and linear evolutions in $\left(1+z\right)$, respectively.
-  For the faint-end slope $\beta$ we adopt a double power law to account
-  for a possible break at $z\sim 3$ that is currently not covered with credible data.
-  %% GW I know I'm harsh with BOSS here. But that's a fact.
-  Thus we write
+  data.  As we discuss below, we find that $\phi_*$, $M_*$ and
+  $\alpha$ prefer quadratic, cubic, and linear evolutions in
+  $\left(1+z\right)$, respectively.  For the faint-end slope $\beta$
+  we adopt a double power law to account for a possible break at
+  $z\sim 3$ that is currently not covered with credible data.  Thus we
+  write
   \begin{equation}
-    f_3\left(1+z\right)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
+    F_3\left(1+z\right)=c_{3,0}+\frac{c_{3,1}}{10^{c_{3,3}\zeta}+10^{c_{3,4}\zeta}},
     \label{eqn:beta}
@@
   high redshift slopes of this evolution, with a break at redshift
-  $c_{3,2}$.
-  %% JFH Consider calling this z_3,2 
-  This is similar to the model of
+  $c_{3,2}$.  This is similar to the model of
   \citet{2007ApJ...654..731H}, who also favoured a broken power law
@@
   Table~\ref{tab:samples} are included while fitting this model.
-  \textbf{GW agrees with JFH that this is too short and cryptic.
-Table~\ref{tab:samples} refers to all samples, but we exclude some samples, some redshift ranges, and some magnitude ranges.
-I've put a clarification in the first sentence of the section, but we might elaborate more.}
+  \textbf{GW agrees with JFH that this is too short and
+    cryptic. Table~\ref{tab:samples} refers to all samples, but we
+    exclude some samples, some redshift ranges, and some magnitude
+    ranges. I've put a clarification in the first sentence of the
+    section, but we might elaborate more.}
   %% JFH where was this discussed?? Nowhere have I seen explicitly stated in the
@@
   \epsilon_{912}\left(z\right)=\left(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}\quad,
+  \label{eqn:e912_18}
 \end{multline}
@@
   \epsilon_{912}\left(z\right)=\left(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}\quad.
+  \label{eqn:e912_21}
 \end{multline}
@@
 
-\textbf{
-Comments from GW:\\
-1. Simplify spectral index discussion\\
-2. Introduce all variables in the radiative transfer equation\\
-3. Helium can be ignored due to the small HI cross section at 228\AA\\
-4. Add more recent Gamma measurements (see Davies et al. 2018)\\
-5. Omit Giallongo error bars and state that they assumed the local source approximation.\\
-6. Add caveats for assumed column density distribution at $z>4$\\
-7. All models have issues at $z>5.5$ as they assume a homogeneous UVB and extrapolate MFP measurements.\\
-8. KH15 are not comparable to our results (emissivity integration limits). 
-}
-
-The 912\,\AA\ emissivity can now be used to calculate the hydrogen
-ionizing flux and the hydrogen photoionization rate contributed by
-AGN.  This adds an additional layer of uncertainty as the \HI\ column
-density structure of the IGM has not been measured at all redshifts of
-interests, thereby requiring uncertain extrapolation.  The frequency
-dependence of the AGN SED above 1~Ry is given by
-Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
-\nu_{912}$
+Our calculation of the AGN contribution to the UV background follows previous work on
+UV background synthesis models \citep[e.g.][]{1996ApJ...461...20H,2012ApJ...746..125H}.
+The main quantity of interest is the \ion{H}{i} photoionization rate of the UV background
 \begin{equation}
-  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
+  \Gamma_\ion{H}{i}\left(z\right)=\int_{\nu_{912}}^\infty\mathrm{d}\nu
+  \frac{4\pi J_\nu\left(\nu,z\right)}{h\nu} \sigma_\ion{H}{i}\left(\nu\right)\quad,
+\end{equation}
+where $h$ is Planck's constant, $\sigma_\ion{H}{i}(\nu)$ is the \ion{H}{i} photoionization cross-section \textbf{Citation}, and
+\begin{multline}
+  J_\nu(\nu, z)=\frac{c}{4\pi}\int_{z}^\infty\mathrm{d}z^\prime\frac{\left(1+z\right)^3}{H\left(z^\prime\right)\left(1+z^\prime\right)}\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)\\
+  \times\exp{\left[-\tau_\mathrm{eff}\left(\nu, z, z^\prime\right)\right]}
+  \label{eqn:flux}
+\end{multline}
+is the angle- and space-averaged specific intensity of the UV background. In the above equation
+$H\left(z^\prime\right)=H_0\sqrt{\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda}$
+is the Hubble parameter, and $\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)$
+is the comoving emissivity of all \ion{H}{i} Lyman continuum sources at redshift $z^\prime>z$ and emitted frequency
+$\nu_\mathrm{em}=\nu\left(1+z^\prime\right)/\left(1+z\right)>\nu_{912}$.
+In practice, we adopt an upper limit $z^\prime_\mathrm{max}=15$ when integrating Equation~\eqref{eqn:flux}.
+Assuming that quasars are the only ionizing sources and considering Equation~\eqref{eqn:sed} we have 
+\begin{equation}
+  \epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right) = \epsilon_{912}\left(z^\prime\right)\left(\frac{\nu_\mathrm{em}}{\nu_{912}}\right)^{-1.70}\quad,
   \label{eqn:epsilon_freq}
 \end{equation}
-where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
-(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
-($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
-IGM is written as a solution of the cosmological radiative transfer
-equation as \citep{2012ApJ...746..125H}
-\begin{multline}
-  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
-  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
-  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
-  \label{eqn:flux}
-\end{multline}
-where
+with $\epsilon_{912}\left(z^\prime\right)$ being represented by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21} for our two magnitude limits, respectively.
+For Poisson-distributed absorbers with an \ion{H}{i} column density distribution $f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial N_\ion{H}{i}\partial z^{\prime\prime}\right)$, the effective optical depth to \ion{H}{i} Lyman continuum photons travelling between redshifts $z^\prime$ and $z$ is \citep{1980ApJ...240..387P}
 \begin{equation}
-  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
+  \tau_\mathrm{eff}\left(\nu,z,z^\prime\right) = \int_{z}^{z^\prime}\mathrm{d}z^{\prime\prime}\int_0^\infty
+  \mathrm{d}N_\ion{H}{i} f\left(N_\ion{H}{i},z^{\prime\prime}\right)\left[1-e^{-\tau_1}\right]\quad,
+   \label{eqn:taueff}
 \end{equation}
-Here the effective optical depth is estimated as
-\begin{equation}
-  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
-  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
-\end{equation}
-where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
-contribution of helium to the opacity.)  We assume the \HI\ column
-density distribution given by \citet{2012ApJ...746..125H}.
+where $\tau_1\approx N_\ion{H}{i}\sigma_\ion{H}{i}\left(\nu\left[\frac{1+z^{\prime\prime}}{1+z}\right]\right)$
+is the Lyman continuum optical depth through an individual absorber\footnote{The helium content of the
+absorber can be ignored due to the small \ion{H}{i} photoionization cross section at $\lambda<304$\,\AA.}.
+For the \ion{H}{i} column density distribution $f\left(N_\ion{H}{i},z\right)$ we adopt the piecewise power-law
+parametrization by \citet{2012ApJ...746..125H} that is consistent with $f\left(N_\ion{H}{i},z\right)$
+measurements at $z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$ effective optical depth
+\citep[but not in detail -- see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
+and the measured mean free path to \ion{H}{i} Lyman limit photons at $z<5.5$ \citep{2009ApJ...705L.113P,2014MNRAS.445.1745W}.
+\citet{2018arXiv180109693K} suggest that variations in $f\left(N_\ion{H}{i},z\right)$ result in modest
+(10--40 per cent) changes in $\Gamma_\ion{H}{i}$ at $z<3$. We note, however, that at $z\ga 3.5$
+all UV background synthesis models are based on brazen extrapolations of $f\left(N_\ion{H}{i},z\right)$,
+whose detailed shape for (partial) Lyman limit systems is not well constrained at these redshifts \citep{2010ApJ...718..392P}.
+
+Equations~\eqref{eqn:flux} and \eqref{eqn:taueff} assume that sources and absorbers are uncorrelated,
+and that $J_\nu(\nu, z)$ is spatially uniform, i.e.\ that the mean free path to \ion{H}{i} Lyman continuum
+photons is much larger than the average distance between the sources
+\citep[e.g.][]{1999ApJ...514..648M,2004MNRAS.350.1107M,2009ApJ...703.1416F,2012ApJ...746..125H}.
+Obviously, these assumptions do not hold for rare sources and during \ion{H}{i} reionization.
+At $z\simeq 5$ our (extrapolated) AGN number densities suggest an average distance of
+$\approx 70$\,cMpc between $M_{1450}<-21$ AGN (Figure~\ref{fig:rhoqso}), which is comparable
+to the mean free path \citep[$83\pm 10$\,cMpc,][]{2014MNRAS.445.1745W}.
+Consequently, if only $M_{1450}<-21$ AGN contribute to the emissivity then the UV radiation field at $z\simeq 5$ must fluctuate.
+If the QLF reaches to fainter magnitudes, or if star-forming galaxies contribute to the emissivity, the UV background remains
+uniform to higher redshifts, and the assumptions of standard UV background synthesis models remain valid.
+
+%The 912\,\AA\ emissivity can now be used to calculate the hydrogen
+%ionizing flux and the hydrogen photoionization rate contributed by
+%AGN.  This adds an additional layer of uncertainty as the \HI\ column
+%density structure of the IGM has not been measured at all redshifts of
+%interests, thereby requiring uncertain extrapolation.  The frequency
+%dependence of the AGN SED above 1~Ry is given by
+%Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
+%\nu_{912}$
+%\begin{equation}
+%  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
+%  \label{eqn:epsilon_freq}
+%\end{equation}
+%where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
+%(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
+%($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
+%IGM is written as a solution of the cosmological radiative transfer
+%equation as \citep{2012ApJ...746..125H}
+%\begin{multline}
+%  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
+%  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
+%  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
+%  \label{eqn:flux}
+%\end{multline}
+%where
+%\begin{equation}
+%  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
+%\end{equation}
+%Here the effective optical depth is estimated as
+%\begin{equation}
+%  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
+%  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
+%\end{equation}
+%where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
+%contribution of helium to the opacity.)  We assume the \HI\ column
+%density distribution given by \citet{2012ApJ...746..125H}.
 %% JFH elaborate on this. Say it is chosen to reproduce Worseck's MFP measurements
@@
 %% Gabors MFP that you are using here. 
-The
-\HI\ photoionization rate is then given by
-\begin{equation}
-  \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
-  \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
-\end{equation}
-where $\sigma$ is the photoionization cross-section.
+%The
+%\HI\ photoionization rate is then given by
+%\begin{equation}
+ % \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
+ % \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
+%\end{equation}
+%where $\sigma$ is the photoionization cross-section.
 %% JFH Is it obvious that the uncertaintites in the MFP which propagate into the HM fit for the column density
 %% distribution do not matter? If so this needs to be explicitly stated.
+
+The red and blue curves in Figure~\ref{fig:gammapi} show the inferred AGN \ion{H}{i} photoionization rate as a function of redshift for our integration limits $M_{1450}=-18$ and $-21$, respectively.
+For comparison we also plot the predictions of recent UV background synthesis models for AGN \citep{2012ApJ...746..125H,2015ApJ...813L...8M,2015MNRAS.451L..30K} and AGN$+$galaxies \citep{2012ApJ...746..125H,2018arXiv180104931P}, as well as inferences from the \ion{H}{i} Ly$\alpha$ forest \citep{2011MNRAS.412.1926W,2013MNRAS.436.1023B,2017MNRAS.467.3172G,2018MNRAS.473..560D}, the Ly$\alpha+\beta$ forest \citep{2018ApJ...855..106D}, and the quasar proximity effect \citep{2011MNRAS.412.2543C}.
+Where necessary, literature values have been rescaled by a few per cent to adjust to our cosmology.
+
+Differences in the \ion{H}{i} photoionization rates inferred from UV background synthesis models mostly arise from obvious differences in the emissivities of AGN and galaxies, but also due to differences in the parametrization of the IGM and the AGN SED.
+
+\textbf{Comments from GW:\\
+1. Do we plot HM12, MH15 and KS15 as published or recalculated from the emissivities?\\
+2. New forest measurements need discussion.\\
+3. High z: Assumption of uniform UVB is violated.
+}
+
+Davies: Table 1, uniform UVB results plotted
+novel statistical approach to infer Gamma by matching the observed and simulated joint distribution of transmission spikes in the $z\sim 6$ Ly$\alpha+\beta$ forest
+GammaHI for one $z_em=6.54$QSO assuming uniform or fluctuating UVB, proof of concept,
+report median of posterior PDFs with 68 percent credible interval, uncertainties do not include systematics (thermal state of IGM, continuum fit)
+
+Onorbe:
+correction to post-reionization GammaHI from HM12 to ensure that simulations match best observations of HI mean flux, goal is to reduce effect of post-process rescaling approach of simulations that aim to reproduce Lya statistics
+plot late reion model $z_\mathrm{reion}=6.55$
+
 We assume an
@@
 \citet{2018arXiv180104931P} as these authors include contribution to
-the photoionization rate from galaxies in their models. The
-differences in our model from that of \citet{2015MNRAS.451L..30K} are
+the photoionization rate from galaxies in their models.
+\textbf{GW: KS15 is different due to their integration limits.}
+The differences in our model from that of \citet{2015MNRAS.451L..30K} are
 a result of our differences from the reported emissivities of
@@
 %% get a global model to work. Why is it interesting to write an entire section on an extrapolation?
+
+\textbf{Comments from GW:\\
+1.
+State again that we need to use the emissivity fit due to the redshift effects.
+Extrapolated emissivity agrees well with our direct estimates (open symbols in emissivity plot) and with other LFs (Schulze)\\
+2. Section needs revision to account for SED change in Fig. 10.\\
+3. We need to be clear whether we are plotting Gamma as is, or whether we are recalculating using your code but other peoples' emissivities.\\
+4.
+We are comparable to HM12, but HM12 considers all AGN.
+We are higher if we consider fainter AGN.
+Given that we miss a factor of 2 to get the forest measurements, we should give a number how faint we need to go.\\
+5.
+Gamma depends on $f(N,z)$.
+Shull doesn't match the measured $f(N,z)$, but Gaikwad and Kollmeier do.
+Gaikwad also estimates the uncertainty in Gamma from the assumed $f(N,z)$.
+To claim any PUC, one has to run UVB synthesis models with a realistic $f(N,z)$ accounting large uncertainty in the range for LLSs (this is hard at low z due to the low number density and need for space-based surveys).
+Shull et al.
+2017 present results from a survey of low-z partial LLSs (their Fig.
+11).
+If the HM12 $f(N,z)$ is inconsistent with the measurements, Gamma won't be right even if the emissivity is right.
+Only Gaikwad investigates this a bit.\\
+6.
+Discuss deficit of Gamma:  Factor ~2 deficit for -18.
+Explanations: 1.
+Changes in limiting magnitude, and spectral index (put numbers: Scott index for -23 no deficit for -18 limit, Scott index for all QSOs: no deficit for -21, fainter AGN: insignificant increase at limit -14 covered by Schulze due to shallow faint-end slope).
+2.
+Galaxies?
+Cite low-z leakers (Izotov), but rare objects.
+}
 
@@
   \end{center}
-  \caption{Evolution of the \HeIII\ ionization fraction in our model,
-    when the AGN luminosity function is integrated down to
-    $M_{1450}=-21$ (blue curve and shaded region) and $M_{1450}=-18$
-    (red curve and shaded region).  The shaded regions show the
-    one-sigma (68.26\%) uncertainty.  Other curves show models of
-    \citet[solid grey]{2012ApJ...746..125H}, \citet[dashed
-      grey]{2015ApJ...813L...8M}, \citet[brown with shaded
-      region]{2016ApJ...828...90L}, \citet[blue]{2018arXiv180104931P},
-    \citet[maroon]{2009ApJ...694..842M}, and
-    \citet[green]{2014MNRAS.445.4186C}.  Note that we derive
-    $Q_\nHeIII$ using Equation~(\ref{eqn:qHedot}), which ignores the
-    presence of \HeII\ Lyman-limit systems and becomes inaccurate
-    towards $Q_\nHeIII\sim 1$. \label{fig:qhe}}
+  \caption{
+  Redshift evolution of the volume-averaged \ion{He}{iii} fraction $Q_\ion{He}{iii}$
+  considering AGN with $M_{1450}<-21$ (blue) and $M_{1450}<-18$ (red)
+  in our calculation of the emission rate of ionizing photons.
+  The shaded regions show the one-sigma (68.26\%) confidence interval
+  resulting from the uncertainty in the emissivity.
+  The other curves show previous determinations of $Q_\ion{He}{iii}\left(z\right)$
+  based on Equation~\eqref{eqn:qHedot}
+  \citep{2012ApJ...746..125H, 2015ApJ...813L...8M, 2016ApJ...828...90L, 2018arXiv180104931P}
+  and on cosmological radiative transfer simulations of quasar-driven \ion{He}{ii} reionization
+  \citep{2009ApJ...694..842M, 2014MNRAS.445.4186C}.
+  Note that Equation~\eqref{eqn:qHedot} ignores the presence of \ion{He}{ii}
+  Lyman limit systems impeding reionization at  $Q_\ion{He}{iii}\rightarrow 1$,
+  requiring further analytic modelling \citep{2017ApJ...851...50M} or
+  numerical simulation \citep{2018arXiv180104931P}.
+  \label{fig:qhe}}  
 \end{figure}
@@
 We now consider the implications of our AGN luminosity function models
-for \HeII\ reionization.  We use the emissivity model developed in
-Section~\ref{sec:e912} for this purpose.  The evolution of the
-volume-averaged fraction $Q_\nHeIII$ of \HeIII\ is given by
-\citep{2012ApJ...746..125H}
+for \ion{He}{ii} reionization. The time evolution of the
+volume-averaged \ion{He}{iii} fraction $Q_\ion{He}{iii}$ is given by
+\citep[e.g.][]{2012ApJ...746..125H}
 \begin{equation}
-  {dQ_\nHeIII\over dt}={\dot n_{\rm ion,4}\over \langle n_\nHe \rangle} -{Q_\nHeIII\over
-    \langle t_{\rm rec,He}\rangle},
+  \frac{\mathrm{d}Q_\ion{He}{iii}}{\mathrm{d}t}=\frac{\dot{n}_\mathrm{ion,4}}{\langle n_\mathrm{He}\rangle}-\frac{Q_\ion{He}{iii}}{\langle t_\mathrm{rec,He}\rangle}\quad,
   \label{eqn:qHedot}
 \end{equation}
-where $\dot n_{\rm ion,4}$ is the number density of photons with
-energy 4~Ry and above produced per unit time, $n_\nHe$ is the Helium
-number density, and $\langle t_{\rm rec,He}\rangle$ is an average
-recombination time scale for \HeIII.  We obtain the evolution of $\dot
-n_{\rm ion,4}$ for AGN with $M_\mathrm{1450}<-21$ and
-$M_\mathrm{1450}<-18$ by integrating the contribution of double power
-law luminosity function obtained in distinct redshifts bins and
-fitting Equation~(\ref{eqn:e912fit}) to the resultant \HeII-ionizing
-emissivities.  We extrapolate the resultant fit to $z>7$, although the
-contribution from this extrapolated emissivity to \HeII-reionization
-is small.  As before, we assume the SED given by
-Equations~(\ref{eqn:sed}), which has a spectral index of
-$\alpha_\mathrm{EUV}=-1.7$.  The recombination time scale in
-Equation~(\ref{eqn:qHedot}) is given by
+where $\dot n_\mathrm{ion,4}$ is the emission rate of $\ge 4$\,Ry photons per unit proper volume,
+$\langle n_\mathrm{He}\rangle$ is the average proper helium number density,
+and $\langle t_\mathrm{rec,He}\rangle$ is the average recombination time scale for \ion{He}{iii}.
+%% GW simplified the following. All of that is a simple rescaling of the 912A emissivity
+%We obtain the evolution of $\dot n_{\rm ion,4}$ for AGN with $M_\mathrm{1450}<-21$ and
+%$M_\mathrm{1450}<-18$ by integrating the contribution of double power
+%law luminosity function obtained in distinct redshifts bins and
+%fitting Equation~(\ref{eqn:e912fit}) to the resultant \HeII-ionizing emissivities.
+%We extrapolate the resultant fit to $z>7$, although the
+%contribution from this extrapolated emissivity to \HeII-reionization is small.
+With our quasar emissivity model from Section~\ref{sec:e912} the emission rate
+can be written as
+%\begin{eqnarray}\nonumber
+%\dot n_\mathrm{ion,4}\left(z\right)&=&\left(1+z\right)^3\int_{\nu_{228}}^{\infty}\mathrm{d}%\nu\frac{\epsilon_\nu\left(\nu,z\right)}{h\nu}\\
+%&=&-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
+%\end{eqnarray}
 \begin{equation}
-  \langle t_{\rm rec}\rangle=[(1+2\chi) \langle n_\nH\rangle \alpha_B\,C]^{-1},
+\dot n_\mathrm{ion,4}\left(z\right)=-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
+\end{equation}
+with the quasar spectral index $\alpha_\nu=-1.7$ and the comoving 912\,\AA\ emissivity
+$\epsilon_{912}\left(z\right)$ given by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21}
+for $M_{1450}<-18$ and $M_{1450}<-21$, respectively.
+The recombination time scale in Equation~\eqref{eqn:qHedot} is given by
+\begin{equation}
+  \langle t_{\rm rec}\rangle=[(1+2\chi) \langle n_\mathrm{H}\rangle \alpha_\mathrm{B}\,C]^{-1}\quad,
   \label{eq:trec}
 \end{equation}
-where $\langle n_\nH\rangle$ is the average physical number density of
-hydrogen, $\alpha_B$ is the case-B \HeIII\ recombination rate, and
-$\chi=0.079$ is the cosmic number fraction of helium for a cosmic
-helium mass fraction of $Y_\mathrm{He}=0.24$.  The hydrogen number
-density is given by $\langle n_\nH\rangle=1.881\times
-10^{-7}(1+z)^3$~cm$^{-3}$.  We assume that the helium clumping factor
-$C$ is given by \citep{2015ApJ...813L...8M}
+where $\langle n_\mathrm{H}\rangle=1.881\times
+10^{-7}(1+z)^3$~cm$^{-3}$ is the average proper hydrogen number density,
+$\alpha_\mathrm{B}$ is the Case~B \ion{He}{iii} recombination coefficient \citep{1997MNRAS.292...27H},
+and $\chi=0.079$ is the cosmic number fraction of helium for a cosmic
+helium mass fraction of $Y_\mathrm{He}=0.24$. 
+We assume that the clumping factor $C$ for helium is the same as for hydrogen,
+for which \citet{2012ApJ...747..100S} obtained
 \begin{equation}
-  C = 2.9\left(\frac{1+z}{6}\right)^{-1.1}.
+  C = 2.9\left(\frac{1+z}{6}\right)^{-1.1}
 \end{equation}
-We use the fitting function provided by \citet{1997MNRAS.292...27H}
-for the recombination coefficient.
-
-Equation~(\ref{eqn:qHedot}) neglects the \HeII\ Lyman-limit systems
-that play an increasingly important role towards the end of Helium
-reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.  In the
-absence of these self-shielded systems of high-density \HeII,
-$Q_\nHeIII$ can continue to increase beyond unity.  The mean free path
-of \HeII-ionizing photon diverges.  We set $Q_\nHeIII=1$ when this
-happens.  This can be corrected by accounting for the \HeII\ column
-density distribution and filtering the \HeII-ionizing radiation
-background through it.  Unfortunately, the \HeII\ column density
-distribution is itself uncertain \citep{2018arXiv180104931P}.  We
-consider our treatment of $Q_\nHeIII$ accurate enough for the purpose
-of this work, while noting that the redshift of \HeII\ reionization is
-likely an overestimate in our model.
-
-The resultant reionization histories of \HeII\ are shown in
-Figure~\ref{fig:qhe} for $M_\mathrm{1450}<-18$ and
-$M_\mathrm{1450}<-21$.  When only AGN with $M_\mathrm{1450}<-21$ are
-accounted, Helium reionization is complete at $z\sim
-3.20^{+0.08}_{-0.12}$ where the uncertainty is one-sigma.  When the
-luminosity function is extrapolated down to $M_\mathrm{1450}<-18$,
-\HeII\ is reionized at $z=3.47^{+0.22}_{-0.26}$.  \HeII\ reionization
-begins at $z\gtrsim 5$ in both models.  Observational constraints on
-the \HeII\ reionization history are derived from measurements of the
-effective \HeII\ \lya optical depth \citep{2001Sci...293.1112K,
-  2004ApJ...600..570S, 2006A&A...455...91F, 2010ApJ...722.1312S,
-  2011ApJ...733L..24W, 2016ApJ...825..144W}.  These are considered to
-imply a redshift of \HeII\ reionization of $z=2.7$
-\citep{2011ApJ...733L..24W}.  While we do not compute the effective
-\HeII\ \lya optical depth in our model, the higher reionization
-redshifts in our models are partly explained by the absence of
-\HeII\ Lyman-limit systems, as discussed above.  Furthermore, the
-reionization histories shown in Figure~\ref{fig:qhe} may likely be
-consistent with the optical depth measurements of
-\citet{2016ApJ...825..144W}, who find that the effective optical depth
-rises at $z>2.7$, but low optical depth sightlines continue to be seen
-beyond this redshift.  The incidence of these low opacity sightlines
-implies that the substantial volume of \HeII\ was ionized already at
-$z=3.4$, consistent with our models.
+over the redshift range $5<z<9$.
+
+Equation~\eqref{eqn:qHedot} neglects \ion{He}{ii} Lyman limit systems
+that considerably delay the end of \ion{He}{ii} reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.
+In the absence of these self-shielded systems, $Q_\ion{He}{iii}$ can continue
+to increase beyond unity and the mean free path of \ion{He}{ii}-ionizing photons diverges.
+We set $Q_\ion{He}{iii}=1$ when this happens.
+This can be corrected by accounting for the \ion{He}{ii} column
+density distribution and filtering the \ion{He}{ii}-ionizing radiation
+field through it. Unfortunately, the \ion{He}{ii} column density
+distribution is itself uncertain, as it depends on the
+relative contributions of quasars and galaxies to the UV background \citep[e.g.][]{2012ApJ...746..125H,2018arXiv180104931P}. 
+We consider the simplified treatment of $Q_\ion{He}{iii}$ accurate enough for the purpose
+of this work, while noting that the redshift of \ion{He}{ii} reionization is
+likely overestimated in any such model.
+
+The resultant \ion{He}{ii} reionization histories are shown in Figure~\ref{fig:qhe}
+for our two considered magnitude limits, with the shaded regions showing the one-sigma
+uncertainty in $Q_\ion{He}{iii}$ resulting from the uncertainty in the quasar emissivity alone,
+i.e.\ using a fixed quasar spectral energy distribution and a fixed redshift evolution of the clumping factor.
+In our model, \ion{He}{ii} reionization starts around the earliest quasars at $z>6$ and finishes at
+$3.2\la z\la 3.5$ depending on the extent of the faint-end QLF.
+Considering the limitations of the modelling discussed above, both \ion{He}{ii} reionization histories
+are consistent with recent \ion{He}{ii} Ly$\alpha$ effective optical depth measurements supporting
+substantial progression of \ion{He}{ii} reionization by $z\simeq 3.4$ \citep{2016ApJ...825..144W},
+and an end of the process at $z\simeq 2.7$ \citep{2011ApJ...733L..24W,2016ApJ...825..144W}
+with the build-up of a quasi-homogeneous \ion{He}{ii}-ionizing background \citep{2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
 
@@
 %% You are spending way to to much time and text discussing the literature. 
-In Figure~\ref{fig:qhe}, we also show the reionization histories from
-other models of \HeII\ reionization in the literature.  Our model
-curve for $M_\mathrm{1450}<-21$ is closest in agreement to the
-simulations of \citet{2009ApJ...694..842M} and the analytical model of
-\citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
-\HeII-ionizing emissivity of AGN by fitting the functional form in
-Equation~(\ref{eqn:e912fit}) to the emissivities reported by
-\citet{2009A&A...507..781S}, \citet{2007A&A...472..443B}, and
-\citet{2012ApJ...755..169M}.  The resultant emissivity in the model of
-\citet{2018arXiv180104931P} is similar in shape but higher in
-amplitude than the emissivity in the \citet{2012ApJ...746..125H}
-model.  The \HeII-ionizing emissivity of \citet{2018arXiv180104931P}
-is closer to our inference for $M_\mathrm{1450}<-21$ than the model of
-\citet{2012ApJ...746..125H}.  (However, note that both these models
-suffer from inhomogeneous luminosity function integration limits, as
-the integration limit is set to a fixed fraction of the break
-luminosity, as discussed above in Section~\ref{sec:e912}.)  A spectral
-index of $\alpha_\mathrm{EUV}=-1.7$ is assumed.
-\citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
-evolving the \HeIII\ ionization fraction in a gas cloud with the mean
-cosmic baryonic density exposed to the average \HeII-ionizing flux.
-The ionizing flux is obtained by filtering the ionizing emissivity
-through an inhomogeneous IGM in which the column density distribution
-of \HeIII\ is derived from that of \HI\ in a manner similar to
-\citet{2012ApJ...746..125H}.  As a result, this model incorporates the
-effect of \HeII\ Lyman-limit systems, and the $Q_\nHeIII$ evolution in
-this model deviates from our predictions towards the end of
-reionization, as seen in Figure~\ref{fig:qhe}.  Comparing the
-emissivity model in the cosmological radiative transfer simulations of
-\citet{2009ApJ...694..842M} with our models is less straightforward.
-Quasars are modelled in the simulations of \citet{2009ApJ...694..842M}
-by relating quasar luminosities and lifetimes to halo masses following
-the galaxy-merger-induced quasar activity model of
-\citet{2005ApJ...630..705H}.  The resultant bolometric quasar
-luminosity functions are somewhat shallower than those of
-\citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
-index of $\alpha_\mathrm{EUV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
-shows that the resultant reionization history in these simulations
-agrees with our model for $M_\mathrm{1450}<-21$, except towards the
-end of reionization, where, as before, \HeII\ Lyman-limit systems
-become important.
-
-Helium reionization is delayed in the model of
-\citet{2012ApJ...746..125H} due to their reduced emissivity at $z\sim
-3$.  In the \citet{2015ApJ...813L...8M} model, a significant
-\HeII\ fraction is ionized already at $z=6$, and reionization is
-complete by $z=4.1$ due to the very high emissivity assumed in this
-model.  In the radiation-hydrodynamic simulations by
-\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
-SDSS \citep{2013ApJ...768..105M} and COSMOS
-\citep{2012ApJ...755..169M} data at $z>3.5$, combined with a model for
-quasar light curves.  The fiducial \HeII\ reionization history
-obtained by these authors is shown in Figure~\ref{fig:qhe} along with
-an estimate of the uncertainty.  Reionization ends considerably later
-in this model ($z\sim 2.6$).  The \HeII\ reionization history in our
-model for $M_\mathrm{1450}<-18$ agrees closely with that in the
-radiative transfer simulations presented by
-\citet{2014MNRAS.445.4186C}.  The AGN population in these simulations
-is `turned on' at $z=5$ and evolved assuming a pure luminosity
-evolution to match the inferred luminosity function of
-\citet{2011ApJ...728L..26G}.  The somewhat early reionization in the
-simulations of \citet{2014MNRAS.445.4186C} relative to most other
-models shown in Figure~\ref{fig:qhe} may be driven by the
-significantly higher emissivity from AGN with intermediate brightness
-($M_{1450}\sim -23$) in the model of \citet{2011ApJ...728L..26G}.
-However, the limited numerical resolution of these simulations may
-also play a role \citep{2014MNRAS.445.4186C}.
-
-An important constraint on \HeII\ reionization can be derived from the
-thermal history of the IGM.  \citet{2018MNRAS.473.1416M} constrained
-the evolution of the 912\,\AA\ emissivity of AGN by assuming a
-spectral index of $\alpha_\mathrm{EUV}=-1.57$ and using the
-measurements of the effective \HeII\ \lya optical depth
-\citep{2016ApJ...825..144W} and the IGM temperature
-\citep{2011MNRAS.410.1096B}.  \citet{2018MNRAS.473.1416M} found that
-although these data favour a reionization history in which \HeII\ is
-reionized at $z>4$, the 912\,\AA\ emissivity of AGN is nevertheless
-required to drop rapidly at $z>3$.  This emissivity evolution is much
-more rapid than that in our model for $M_\mathrm{1450}<-21$, with the
-caveat that the constraint derived by \citet{2018MNRAS.473.1416M} is
-model-dependent and assumes a shallower EUV spectrum.  A steeper
-spectrum with $\alpha_\mathrm{EUV}=-1.8$ was assumed in a recent model
-by \citet{2018arXiv180109693K}.  The resultant emissivity evolution is
-consistent with our model for $M_\mathrm{1450}<-21$, although somewhat
-more rapid at $z>2$.  The AGN luminosity function is derived by
-combining determinations from various data sets
-\citep{2015MNRAS.451L..30K}.  An inhomogeneous integration limit of
-$0.01L_*$ is applied to calculate the emissivity.  \HeII\ reionization
-ends at $z=2.8$ in the model of \citet{2018arXiv180109693K}.
-(\citealt{2017MNRAS.471..255K} argued that for their luminosity
-function model, spectra with $\alpha_\mathrm{EUV}>-1.6$ are unlikely
-to be consistent with the \HeII\ \lya data.)
-\citet{2017MNRAS.468.4691D} considered the effect of an AGN-dominated
-reionization on the \HI\ Ly$\alpha$ opacity at $z>5$,
-\HeII\ Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the thermal
-history of the IGM.  These authors found that that any scenario in
-which reionization of \HeII\ completes at $z>3$ is inconsistent with
-the measurements of the IGM temperature at $z=4$--$5$.  We leave the
-analysis of the IGM thermal history implied by our AGN luminosity
-models for future work.
-
-\section{Conclusions}
+%% GW commented the previous version and provided a shorter one
+
+Figure~\ref{fig:qhe} also shows previous solutions of Equation~\eqref{eqn:qHedot}
+with different parameterizations of the quasar emissivity, spectral energy distribution and
+clumping factor \citep{2012ApJ...746..125H,2015ApJ...813L...8M,2016ApJ...828...90L,2018arXiv180104931P},
+as well as the results from cosmological radiative transfer simulations of \ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C}.
+The differences of our results to the ones by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
+mostly result from differences in the adopted quasar emissivity (Figure~\ref{fig:e912_2}).
+The large quasar emissivity adopted by \citet{2015ApJ...813L...8M} results in an early completion of
+\ion{He}{ii} reionization at $z\approx 4$, which is inconsistent with the measured strong \ion{He}{ii} absorption
+at $2.7<z<3$ \citep{2016ApJ...825..144W,2018MNRAS.473.1416M,2018arXiv180104931P}
+if the \ion{He}{ii}-ionizing background is not fluctuating on large scales due to rare clustered and/or short-lived
+quasars that result in a spatially varying mean free path of \ion{He}{ii}-ionizing photons
+\citep{2010ApJ...714..355F,2014MNRAS.440.2406M,2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
+The quasar emissivity considered by \citet{2012ApJ...746..125H} falls below our determinations at the relevant
+redshifts (Figure~\ref{fig:e912_2}), which results in a delayed completion of \ion{He}{ii} reionization at $z\simeq 2.8$.
+
+\citet{2016ApJ...828...90L} varied the parameters of Equation~\eqref{eqn:qHedot} to estimate the uncertainty
+in $Q_\ion{He}{iii}\left(z\right)$, in particular the QLF\footnote{\citet{2016ApJ...828...90L} erroneously varied the
+$z>3.5$ QLF parameters independently, neglecting their covariance and the survey data.},
+shown in Figure~\ref{fig:e912_2}. Considering the limitations of Equation~\eqref{eqn:qHedot},
+\ion{He}{ii} reionization finishes too late ($z\sim 2.5$) in their fiducial model, which is probably due to their
+considered QLFs and varying magnitude limits their emissivity calculations.
+
+\citet{2018arXiv180104931P} adopted a somewhat higher quasar emissivity than \citet{2012ApJ...746..125H}
+that is comparable to our fit for $M_{1450}<-21$ at the redshifts of interest. Instead of their solution to
+Equation~\eqref{eqn:qHedot} we show their results of one-cell simulations with gas at cosmic mean density
+(see Section~3.3 and Appendix~C of \citealt{2018arXiv180104931P} for details).
+In these simulations the \ion{He}{ii} number density is correctly calculated as \ion{He}{ii} is gradually ionized
+by a radiation field resulting from one-dimensional radiative transfer calculations through an inhomogeneous IGM.
+This accounts for \ion{He}{ii} Lyman limit systems in a simple way, resulting in a smooth transition of $Q_\ion{He}{iii}$ to unity.
+
+In Figure~\ref{fig:qhe} we also plot $Q_\ion{He}{iii}\left(z\right)$ from two numerical simulations of quasar-driven
+\ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C} that broadly reproduce the measured
+\ion{He}{ii} effective optical depths \citep{2016ApJ...825..144W}. In these simulations the outputs of $N$-body or
+hydrodynamic simulations are post-processed with radiative transfer around quasars sourced according to a specific model,
+and the effects of \ion{He}{ii} Lyman limit systems are approximately captured with sub-grid filtering methods
+\citep{2009ApJ...694..842M} or with adaptive mesh refinement \citep{2014MNRAS.445.4186C}.
+Their different timing of \ion{He}{ii} reionization is mostly due to the adopted quasar model
+(QLF, spectral energy distribution, quasar lifetime, anisotropic emission, halo mass range) and stochasticity in the
+$z\ga 3.5$ quasar number density in the limited simulation volumes.
+Thus, while current simulations do not reproduce the measured scatter in the \ion{He}{ii} effective optical depths at
+$2.7<z<3.5$ in detail \citep{2016ApJ...825..144W}, this may reflect limitations of the modelling other than the QLF
+\citep{2017MNRAS.468.4691D}. Our $Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with the simulation
+by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii} reionization is accomplished by the $z<5$ quasar population
+evolved assuming pure density or pure luminosity evolution to match the QLF by \citet{2011ApJ...728L..26G} for
+$M_{1450}<-19.5$ \citep[see also][]{2013MNRAS.435.3169C}. Future efforts in numerical modelling of \ion{He}{ii}
+reionization should investigate quasar models which follow the QLF evolution in detail, and which are consistent with
+the measured redshift evolution and scatter of the \ion{He}{ii} effective optical depth, as well as the measured redshift evolution
+of the IGM temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,2014MNRAS.441.1916B,2018MNRAS.474.2871R,2017arXiv171000700H}.
+
+%% Previous version commented by GW
+%In Figure~\ref{fig:qhe}, we also show the reionization histories from
+%other models of \HeII\ reionization in the literature.  Our model
+%curve for $M_\mathrm{1450}<-21$ is closest in agreement to the
+%simulations of \citet{2009ApJ...694..842M} and the analytical model of
+%\citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
+%\HeII-ionizing emissivity of AGN by fitting the functional form in
+%Equation~(\ref{eqn:e912fit}) to the emissivities reported by
+%\citet{2009A&A...507..781S}, \citet{2007A&A...472..443B}, and
+%\citet{2012ApJ...755..169M}.  The resultant emissivity in the model of
+%\citet{2018arXiv180104931P} is similar in shape but higher in
+%amplitude than the emissivity in the \citet{2012ApJ...746..125H}
+%model.  The \HeII-ionizing emissivity of \citet{2018arXiv180104931P}
+%is closer to our inference for $M_\mathrm{1450}<-21$ than the model of
+%\citet{2012ApJ...746..125H}.  (However, note that both these models
+%suffer from inhomogeneous luminosity function integration limits, as
+%the integration limit is set to a fixed fraction of the break
+%luminosity, as discussed above in Section~\ref{sec:e912}.)  A spectral
+%index of $\alpha_\mathrm{EUV}=-1.7$ is assumed.
+%\citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
+%evolving the \HeIII\ ionization fraction in a gas cloud with the mean
+%cosmic baryonic density exposed to the average \HeII-ionizing flux.
+%The ionizing flux is obtained by filtering the ionizing emissivity
+%through an inhomogeneous IGM in which the column density distribution
+%of \HeIII\ is derived from that of \HI\ in a manner similar to
+%\citet{2012ApJ...746..125H}.  As a result, this model incorporates the
+%effect of \HeII\ Lyman-limit systems, and the $Q_\nHeIII$ evolution in
+%this model deviates from our predictions towards the end of
+%reionization, as seen in Figure~\ref{fig:qhe}.  Comparing the
+%emissivity model in the cosmological radiative transfer simulations of
+%\citet{2009ApJ...694..842M} with our models is less straightforward.
+%Quasars are modelled in the simulations of \citet{2009ApJ...694..842M}
+%by relating quasar luminosities and lifetimes to halo masses following
+%the galaxy-merger-induced quasar activity model of
+%\citet{2005ApJ...630..705H}.  The resultant bolometric quasar
+%luminosity functions are somewhat shallower than those of
+%\citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
+%index of $\alpha_\mathrm{EUV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
+%shows that the resultant reionization history in these simulations
+%agrees with our model for $M_\mathrm{1450}<-21$, except towards the
+%end of reionization, where, as before, \HeII\ Lyman-limit systems
+%become important.
+
+%Helium reionization is delayed in the model of
+%\citet{2012ApJ...746..125H} due to their reduced emissivity at $z\sim
+%3$.  In the \citet{2015ApJ...813L...8M} model, a significant
+%\HeII\ fraction is ionized already at $z=6$, and reionization is
+%complete by $z=4.1$ due to the very high emissivity assumed in this
+%model.  In the radiation-hydrodynamic simulations by
+%\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
+%SDSS \citep{2013ApJ...768..105M} and COSMOS
+%\citep{2012ApJ...755..169M} data at $z>3.5$, combined with a model for
+%quasar light curves.  The fiducial \HeII\ reionization history
+%obtained by these authors is shown in Figure~\ref{fig:qhe} along with
+%an estimate of the uncertainty.  Reionization ends considerably later
+%in this model ($z\sim 2.6$).  The \HeII\ reionization history in our
+%model for $M_\mathrm{1450}<-18$ agrees closely with that in the
+%radiative transfer simulations presented by
+%\citet{2014MNRAS.445.4186C}.  The AGN population in these simulations
+%is `turned on' at $z=5$ and evolved assuming a pure luminosity
+%evolution to match the inferred luminosity function of
+%\citet{2011ApJ...728L..26G}.  The somewhat early reionization in the
+%simulations of \citet{2014MNRAS.445.4186C} relative to most other
+%models shown in Figure~\ref{fig:qhe} may be driven by the
+%significantly higher emissivity from AGN with intermediate brightness
+%($M_{1450}\sim -23$) in the model of \citet{2011ApJ...728L..26G}.
+%However, the limited numerical resolution of these simulations may
+%also play a role \citep{2014MNRAS.445.4186C}.
+
+%An important constraint on \HeII\ reionization can be derived from the
+%thermal history of the IGM.  \citet{2018MNRAS.473.1416M} constrained
+%the evolution of the 912\,\AA\ emissivity of AGN by assuming a
+%spectral index of $\alpha_\mathrm{EUV}=-1.57$ and using the
+%measurements of the effective \HeII\ \lya optical depth
+%\citep{2016ApJ...825..144W} and the IGM temperature
+%\citep{2011MNRAS.410.1096B}.  \citet{2018MNRAS.473.1416M} found that
+%although these data favour a reionization history in which \HeII\ is
+%reionized at $z>4$, the 912\,\AA\ emissivity of AGN is nevertheless
+%required to drop rapidly at $z>3$.  This emissivity evolution is much
+%more rapid than that in our model for $M_\mathrm{1450}<-21$, with the
+%caveat that the constraint derived by \citet{2018MNRAS.473.1416M} is
+%model-dependent and assumes a shallower EUV spectrum.  A steeper
+%spectrum with $\alpha_\mathrm{EUV}=-1.8$ was assumed in a recent model
+%by \citet{2018arXiv180109693K}.  The resultant emissivity evolution is
+%consistent with our model for $M_\mathrm{1450}<-21$, although somewhat
+%more rapid at $z>2$.  The AGN luminosity function is derived by
+%combining determinations from various data sets
+%\citep{2015MNRAS.451L..30K}.  An inhomogeneous integration limit of
+%$0.01L_*$ is applied to calculate the emissivity.  \HeII\ reionization
+%ends at $z=2.8$ in the model of \citet{2018arXiv180109693K}.
+%(\citealt{2017MNRAS.471..255K} argued that for their luminosity
+%function model, spectra with $\alpha_\mathrm{EUV}>-1.6$ are unlikely
+%to be consistent with the \HeII\ \lya data.)
+%\citet{2017MNRAS.468.4691D} considered the effect of an AGN-dominated
+%reionization on the \HI\ Ly$\alpha$ opacity at $z>5$,
+%\HeII\ Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the thermal
+%history of the IGM.  These authors found that that any scenario in
+%which reionization of \HeII\ completes at $z>3$ is inconsistent with
+%the measurements of the IGM temperature at $z=4$--$5$.  We leave the
+%analysis of the IGM thermal history implied by our AGN luminosity
+%models for future work.
+
+\section{Summary and Conclusions}
 \label{sec:conc}
 
-We have presented an analysis of the evolution of the UV luminosity
-function of AGN from redshift $z=0$ to $7.5$ using a combined sample
-of close to 85,000 colour-selected AGN from 12 data sets, homogenized
-with respect to the assumed cosmology, intrinsic AGN spectrum, and the
-magnitude system.  AGN from 11 of these 12 samples have reported
-spectroscopic redshifts, and all but two AGN have known completeness
-estimates.  These data span magnitudes down to $M_{1450}=-22$ at high
-redshifts ($z\gtrsim 3.5$).
+We have analysed the evolution of the AGN UV luminosity function from redshift $z=0$ to $7.5$
+using a combined sample of 83,488 mostly UV-optical colour-selected AGN from 12 data sets,
+homogenised with respect to the assumed cosmology, magnitude system and bandpass correction (if possible).
+The vast majority of them (83,469 AGN from 11/12 samples) have spectroscopic redshifts,
+and for all but 22 AGN the selection functions have been characterised.
+After restricting the sample due to persisting incompleteness at the faint end we arrive at 77,659 spectroscopically
+confirmed $0<z<7.5$ AGN extending to absolute AB magnitudes $M_{1450}\simeq -19$ at $z\simeq 0.5$
+and to $M_{1450}\sim -22$ at $z>3.5$, respectively. 
+To facilitate comparisons to future data sets we make the homogenised AGN sample and
+the homogenised selection functions publicly available.
+
+Binning the $1450$\,\AA\ AGN luminosity function in narrow redshift ranges we find that it is
+excellently described by the customary double power law in magnitude at all redshifts (Figure~\ref{fig:mosaic}).
+Its four parameters significantly evolve with redshift (Figure~\ref{fig:evoln}):
+(i) The break magnitude $M_*$ of the AGN luminosity function shows a steep brightening from $M_*\simeq -24$ at $z\simeq 0.7$ to $M_*\sim -29$ at $z\simeq 6$.
+(ii) The corresponding amplitude $\phi_*$ drops by a factor $\sim 20,000$ from $\phi_*\simeq 4\times 10^{-7}$~mag$^{-1}$cMpc$^{-3}$ at $z<2.2$ to $\phi_*\sim 2\times 10^{-11}$~mag$^{-1}$cMpc$^{-3}$ at $z\simeq 6$.
+(iii) The faint-end slope $\beta$ significantly decreases from $\simeq -1.7$ at $z<2.2$ to $\simeq -2.4$ at $z\simeq 6$, resulting in a steepening of the luminosity function.
+(iv) The bright-end slope $\alpha$ also shows a moderate decrease with redshift, but is less constrained at the highest redshifts because of the bright break magnitude.
+In contrast to several previous studies, our fits are based on unbinned homogenised AGN data
+and their selection functions, and the confidence intervals fully account for covariance in the luminosity function parameters. 
+From the continuity of the luminosity function at lower redshifts we argue that its apparent
+single power law description at $z\simeq 6$ can be interpreted as the faint end of the double power law
+whose break magnitude $M_*$ is at the bright end of the $z\simeq 6$ quasar population.
+
+Similar continuity arguments let us scrutinize the value of several photometrically selected AGN samples
+in determinations of the luminosity function. Our analysis has revealed systematic errors in the survey
+selection functions caused by their fixed and simplified assumptions, i.e.\ regarding the parameterisation
+of the IGM and the AGN SED, and the treatment of photometric errors at the survey magnitude limit.
+Several of these systematic errors are easily identified from artificial faint-end drops of the luminosity function
+(Figure~\ref{fig:mosaic}), an apparently zero accessible volume for discovered AGN,
+or a mismatch between the observed and the simulated AGN color distribution. 
+In large samples the precision of the AGN luminosity function is limited by unaccounted systematic errors
+in the survey selection functions, which lead to (i) unphysical variations in the luminosity function parameters
+(i.e.\ for BOSS in Figure~\ref{fig:evoln}) and (ii) inter-survey systematics in combined samples that are further
+amplified by heterogeneous selection function parameter choices amongst the surveys.
+
+With only partially credible data it is challenging to describe the redshift evolution of the AGN luminosity function
+with a viable parametric model. We have developed three such models (Figure~\ref{fig:evoln_global}),
+finding that our fourteen-parameter Model 1 describes the redshift evolution of the luminosity function rather well.
+However, this model prefers a break in the faint-end slope at $z\simeq 3.5$, which causes an unphysical
+discontinuity in the cumulative AGN number density (Figure~\ref{fig:rhoqso}). Our other two models do not have
+these features, but they do not match the measured faint-end slope at $z>4$ as well as Model 1 does.
+%GW: One shall not extrapolate, so divergence is not a real problem
+%The integrated quasar number density diverges at high redshifts in all three models.
+
+With our determinations of the luminosity function we have revisited the contribution of AGN to reionization and the UV background.
+We have made the first determinations of the AGN 912\,\AA\ emissivity with homogeneous faint-end limits at all redshifts,
+whose statistical uncertainties have been properly calculated from the posterior distributions of the luminosity function
+(Figure~\ref{fig:e912_2}). Our parametric fits yield a peak in the 912\,\AA\ emissivity at $z\approx 2.4$, with a decline
+by $\simeq 2$ orders of magnitude to $z\simeq 0$ and $z\simeq 7$, respectively. At $z>4$ our determined emissivities
+are lower by a factor 2--10 than recently claimed by \citet{2015AA...578A..83G}. At the same time, the 912\,\AA\ emissivity
+of $M_{1450}<-18$ AGN exceeds the model considered by \citet{2012ApJ...746..125H} by a factor $>2$ at $z>3$,
+suggesting a somewhat higher contribution of AGN to the high-$z$ UV background if faint AGN have unit escape fractions
+of ionizing photons.
+
+Having derived the AGN \ion{H}{i} photoionization rate by filtering the \ion{H}{i}-ionizing AGN emissivity through
+the IGM \ion{H}{i} column density distribution, we find that while at $z=2$--3 $M_{1450}<-18$ AGN are almost sufficient
+to explain measurements from the Ly$\alpha$ forest, additional UV sources are required at higher redshifts
+(Figure~\ref{fig:gammapi}). Boldly extrapolating the \ion{H}{i} column density distribution to $z=6$, we estimate that
+$M_{1450}<-18$ AGN contribute to the \ion{H}{i} photoionization rate only at the $\sim 5$ per cent level.
+This indicates a minor contribution of such AGN to \ion{H}{i} reionization.
+At $z<0.5$ $M_{1450}<-18$ AGN fall short by a factor of $\sim 2$ to explain UV background measurements
+(Figure~\ref{fig:puc}), but we hesitate to claim a `photon underproduction crisis' \citep{2014ApJ...789L..32K},
+because (i) the apparent tension may be alleviated by known $-18\la M_{1450}\la -14$ AGN at these redshifts
+\citep{2009A&A...507..781S} albeit their Lyman continuum escape fraction is unknown,
+and (ii) current UV background synthesis models do not account for the large uncertainty in the low-redshift
+column density distribution of (partial) \ion{H}{i} Lyman limit systems \citep{2011ApJ...736...42R,2017ApJ...849..106S}. 
+Helium reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$ AGN (Figure~\ref{fig:qhe}),
+but should be delayed by \ion{He}{ii} Lyman limit systems \citep{2009MNRAS.395..736B, 2017ApJ...851...50M},
+requiring further modelling and detailed numerical simulations of the \ion{He}{ii} reionization process.
+
+There are several promising paths forward in the characterization of the AGN luminosity function,
+some of which may substantially advance on current UV-optical broadband color-selected samples that have
+dominated the field for the past 20 years. These include, but are not limited to, comprehensive surveys for
+faint high-$z$ quasars selected by broadband photometry \citep{2016ApJ...828...26M,2017ApJ...839...27W}
+or variability \citep{2017MNRAS.464.1693H}, infrared-selected highly complete surveys at $z\sim 3$
+\citep{2017ApJ...851...13S,2018AJ....155..110Y},
+multi-band narrow-band surveys targeting AGN at all epochs \citep{2014arXiv1403.5237B},
+slitless spectroscopic surveys with upcoming space telescopes \citep{2011arXiv1110.3193L, 2013arXiv1305.5422S},
+and next-generation X-ray surveys \citep[e.g.][]{2013A&A...558A..89K}. However, we caution that future progress
+based on massive surveys requires a detailed quantification of their selection functions and the incorporation
+of systematic errors into AGN luminosity function measurements, in a similar manner to recent surveys for
+lensed high-redshift galaxies that are limited by the accuracy of the lensing mass models
+\citep{2017ApJ...843..129B,2018ApJ...854...73I,2018arXiv180309747A}.
+For a better characterization of the AGN contribution to the UV background one will need to
+(i) perform spectroscopic surveys for faint AGN at all redshifts and determine their characteristic UV SED,
+(ii) carefully assess the impact of the host galaxy on the survey selection and the ionizing power,
+and (iii) measure precisely the amplitude and shape of the column density distribution of (partial)
+\ion{H}{i} Lyman limit systems to inform UV background synthesis models at $z<2$ and $z>4$.
+
+\textbf{A short final paragraph on Hopkins here...}
+
+%% This is the previous version of this section, now changed by GW
+%We have presented an analysis of the evolution of the UV luminosity
+%function of AGN from redshift $z=0$ to $7.5$ using a combined sample
+%of close to 85,000 colour-selected AGN from 12 data sets, homogenized
+%with respect to the assumed cosmology, intrinsic AGN spectrum, and the
+%magnitude system.  AGN from 11 of these 12 samples have reported
+%spectroscopic redshifts, and all but two AGN have known completeness
+%estimates.  These data span magnitudes down to $M_{1450}=-22$ at high
+%redshifts ($z\gtrsim 3.5$).
 
@@
 %% results are. Also some people just jump to conclusions so they need to know where to look. 
-We find that the UV luminosity function of AGN prefers a double power
-law description at all redshifts considered in this study, except
-possibly at very high redshifts ($z\sim 6$) where a single power law
-seems to be preferred.  The behaviour of the luminosity function at
-lower redshifts ($z=4$--$5.5$) suggests that this single power law at
-$z\sim 6$ can be interpreted as the faint end of the double power law
-with a break at $M_*=-29$.  The break magnitude $M_*$ of the double
-power law luminosity function shows a steep brightening towards high
-redshifts.  The break evolves from $M_*<-25$ at $z\sim 1$ to $M_*\sim
--29$ at $z\sim 6$.  Correspondingly, the amplitude $\phi_*$ of the
-luminosity function drops rapidly towards high redshifts from
-$\phi_*\sim 10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 1$ to $\phi_*<
-10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The faint-end slope
-$\beta$ becomes increasingly negative towards high redshifts,
-resulting in the a steepening of the luminosity function.  The
-faint-end slope is $\beta\sim -1.8$ at $z\sim 1$ and steepens to
-$\beta\sim-2.5$ at $z\sim 6$.  The bright-end slope $\alpha$ also
-shows moderate steepening towards high redshifts.  However, the
-constraints on $\alpha$ are weak, particularly at the high redshift
-because of the bright break luminosity.
+%We find that the UV luminosity function of AGN prefers a double power
+%law description at all redshifts considered in this study, except
+%possibly at very high redshifts ($z\sim 6$) where a single power law
+%seems to be preferred.  The behaviour of the luminosity function at
+%lower redshifts ($z=4$--$5.5$) suggests that this single power law at
+%$z\sim 6$ can be interpreted as the faint end of the double power law
+%with a break at $M_*=-29$.  The break magnitude $M_*$ of the double
+%power law luminosity function shows a steep brightening towards high
+%redshifts.  The break evolves from $M_*<-25$ at $z\sim 1$ to $M_*\sim
+%-29$ at $z\sim 6$.  Correspondingly, the amplitude $\phi_*$ of the
+%luminosity function drops rapidly towards high redshifts from
+%$\phi_*\sim 10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 1$ to $\phi_*<
+%10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The faint-end slope
+%$\beta$ becomes increasingly negative towards high redshifts,
+%resulting in the a steepening of the luminosity function.  The
+%faint-end slope is $\beta\sim -1.8$ at $z\sim 1$ and steepens to
+%$\beta\sim-2.5$ at $z\sim 6$.  The bright-end slope $\alpha$ also
+%shows moderate steepening towards high redshifts.  However, the
+%constraints on $\alpha$ are weak, particularly at the high redshift
+%because of the bright break luminosity.
 
 %% JFH Figure references here as well. 
-An important finding of this work is that there are severe systematic
-errors in observed luminosity function at certain redshifts.  We find
-that the most significant systematic bias is at redshift $z\sim 3$ in
-the BOSS sample of quasars.  There is also some evidence of a
-systematic bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$
-there is some indication of a systematic error in completeness
-estimates at the faintest magnitudes $M_{1450}\sim -19$.  Systematic
-errors make it harder to construct simple empirical models to describe
-the luminosity function evolution.  We develop three such models in
-this paper.  We find that a fourteen-parameter model (Model 1)
-describes the redshift evolution of the luminosity function rather
-well.  However, this model prefers a very rapid evolution in the
-faint-end slope at $z=3.5$, which is probably unphysical.  Our other
-models (Models 2 and 3) do not have this feature, but these models do
-not fit the data as well as Model 1 at $z=4$--$6$.  The integrated
-quasar number density diverges at high redshifts in all three models.
-
-In spite of the rapid steepening of the faint end of the luminosity
-function at high redshifts, our derived hydrogen-ionizing emissivity
-from AGN is lower that recent determinations from the literature
-\citep{2015AA...578A..83G}.  This is because the bright break
-luminosities reduce the contribution of intermediate-brightness AGN to
-the LyC emissivity.  We find that the LyC emissivity peaks at $z\sim
-2$.  We derive the average hydrogen photoionization rate by filtering
-the hydrogen-ionizing emissivity through the intergalactic \HI\ column
-density distribution.  We find that the HI photoionization rate is
-lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
-Our hydrogen photoionization rate estimates are also considerably
-lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
-This indicates that hydrogen reionization is unlikely to have caused
-by AGN alone.  Extrapolating the \HI\ column density distribution
-function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
-are assumed to supply hydrogen-ionizing photons with a unit escape
-fraction, the resultant photoionization rate is only about 10\% of
-what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
-we find that the hydrogen photoionization rate is about a factor of
-two higher than the estimate of \citet{2007ApJ...654..731H} and
-\citet{2012ApJ...746..125H}.  When compared with the recent analysis
-of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
-alleviate the photon underproduction crisis
-\citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
-at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
-integrated down to $M_{1450}=-21$ and $-18$, respectively.
-
-These results will be made more robust with new data from deep
-large-area surveys to discover faint quasars at high redshifts, such
-as the Subaru High-z Exploration of Low-Luminosity Quasars (SHELLQs)
-project \citep{2016ApJ...828...26M} and the VISTA Extragalactic
-Infrared Legacy Survey (VEILS; \citealt{2017MNRAS.464.1693H}),
-followed by the Wide Field Infrared Survey Telescope (WFIRST;
-\citealt{2013arXiv1305.5422S}) and Euclid \citep{2011arXiv1110.3193L}.
-This study highlights the need for a better understanding of
-luminosity function systematics.  In particular, at $z>4$, it seems
-important to include extended objects at faint magnitudes that could
-be impacted by host galaxy light, take follow-up spectroscopy to
-confirm a fraction of these as high-redshift broad-line AGN, and
-carefully assess host galaxy contamination.
+%An important finding of this work is that there are severe systematic
+%errors in observed luminosity function at certain redshifts.  We find
+%that the most significant systematic bias is at redshift $z\sim 3$ in
+%the BOSS sample of quasars.  There is also some evidence of a
+%systematic bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$
+%there is some indication of a systematic error in completeness
+%estimates at the faintest magnitudes $M_{1450}\sim -19$.  Systematic
+%errors make it harder to construct simple empirical models to describe
+%the luminosity function evolution.  We develop three such models in
+%this paper.  We find that a fourteen-parameter model (Model 1)
+%describes the redshift evolution of the luminosity function rather
+%well.  However, this model prefers a very rapid evolution in the
+%faint-end slope at $z=3.5$, which is probably unphysical.  Our other
+%models (Models 2 and 3) do not have this feature, but these models do
+%not fit the data as well as Model 1 at $z=4$--$6$.  The integrated
+%quasar number density diverges at high redshifts in all three models.
+
+%In spite of the rapid steepening of the faint end of the luminosity
+%function at high redshifts, our derived hydrogen-ionizing emissivity
+%from AGN is lower that recent determinations from the literature
+%\citep{2015AA...578A..83G}.  This is because the bright break
+%luminosities reduce the contribution of intermediate-brightness AGN to
+%the LyC emissivity.  We find that the LyC emissivity peaks at $z\sim
+%2$.  We derive the average hydrogen photoionization rate by filtering
+%the hydrogen-ionizing emissivity through the intergalactic \HI\ column
+%density distribution.  We find that the HI photoionization rate is
+%lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
+%Our hydrogen photoionization rate estimates are also considerably
+%lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
+%This indicates that hydrogen reionization is unlikely to have caused
+%by AGN alone.  Extrapolating the \HI\ column density distribution
+%function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
+%are assumed to supply hydrogen-ionizing photons with a unit escape
+%fraction, the resultant photoionization rate is only about 10\% of
+%what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
+%we find that the hydrogen photoionization rate is about a factor of
+%two higher than the estimate of \citet{2007ApJ...654..731H} and
+%\citet{2012ApJ...746..125H}.  When compared with the recent analysis
+%of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
+%alleviate the photon underproduction crisis
+%\citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
+%at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
+%integrated down to $M_{1450}=-21$ and $-18$, respectively.
+
+%These results will be made more robust with new data from deep
+%large-area surveys to discover faint quasars at high redshifts, such
+%as the Subaru High-z Exploration of Low-Luminosity Quasars (SHELLQs)
+%project \citep{2016ApJ...828...26M} and the VISTA Extragalactic
+%Infrared Legacy Survey (VEILS; \citealt{2017MNRAS.464.1693H}),
+%followed by the Wide Field Infrared Survey Telescope (WFIRST;
+%\citealt{2013arXiv1305.5422S}) and Euclid \citep{2011arXiv1110.3193L}.
+%This study highlights the need for a better understanding of
+%luminosity function systematics.  In particular, at $z>4$, it seems
+%important to include extended objects at faint magnitudes that could
+%be impacted by host galaxy light, take follow-up spectroscopy to
+%confirm a fraction of these as high-redshift broad-line AGN, and
+%carefully assess host galaxy contamination.
 
@@
 \section{Comparison with other luminosity function determinations}
-
+\label{sec:qlfliterature}
 Figure~\ref{fig:params_grand} compares the parameters of the double
@@
   % gammapi.py and tabulate_emissivities.py. 
-  \caption{The 912\,\AA\ and 1450\,\AA\ comoving emissivities
-    corresponding to the double power law luminosity function models
-    in redshift bins presented in Table~\ref{tab:bins} for two
-    integration limits.  These emissivities are shown in
-    Figure~\ref{fig:e912_2}.  The units are
-    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.  Uncertainties
-    are one-sigma (68.26\%).}
+  \caption{
+    \textbf{GW: Delete the zbin column that we do not use. Indicate the credible (fitted) redshift bins!}
+    Comoving emissivities at 912\,\AA\ and 1450\,\AA\ derived from
+    our double power law luminosity function models in redshift bins
+    (Table~\ref{tab:bins}) for two magnitude limits. The units are
+    $10^{24}$\ erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$.
+    Statistical uncertainties are one-sigma (68.26\%).
+    }
   \label{tab:emissivity_bins}
@@
   % Check these values once again.
-  \caption{The 912\,\AA\ and 1450\,\AA\ comoving emissivities obtained
-    by fitting Equation~(\ref{eqn:e912fit}) to the selected redshift
-    bins from Table~\ref{tab:emissivity_bins}, and the corresponding
-    hydrogen photoionisation rates with the one-sigma (68.26\%)
-    uncertainties.  The emissivities are extrapolated here up to
-    $z=15$.  Emissivity units are
-    erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$, and photoionisation rate
-    units are s$^{-1}$.  These values are shown in
-    Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.  See
-    Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.}
+  \caption{
+    Comoving emissivities at 912\,\AA\ and 1450\,\AA\ obtained
+    by fitting Equation~\eqref{eqn:e912fit} to the emissivities in the
+    selected redshift bins from Table~\ref{tab:emissivity_bins}.
+    Emissivities at $z<0.6$ and at $z>6.5$ are extrapolated assuming our best fits.
+    The derived \ion{H}{i} photoionization rates (\textbf{Cite Eq.})
+    are also given. Emissivity units are
+    erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$, and photoionization rate
+    units are s$^{-1}$. Statistical uncertainties are one-sigma (68.26\%).
+    These values are shown in Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.
+    See Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.
+    }
   \label{tab:gamma2}
@@
 \section{Code and data}
+\label{sec:code}
 

### 2018-07-11 Paper/paper.tex
Update

@@
 \citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
-by eye, discard the contributing quasars from our analysis, and set their
+`by eye', discard the contributing quasars from our analysis, and set their
 selection function values to zero.
@@
 posterior median as our fiducial model fit, and the 68.26\%
-equal-tailed credible interval as the uncertainty on $\phi$.
+equal-tailed credible interval as the uncertainty on $\phi$.  The
+resultant parameter values are listed in Table~\ref{tab:bins}.
 Consistent with previous studies, the double power law model provides
@@
 but Poisson errors of the limited samples dominate.
+
+%% Bins considered
+%% to be dominated by systematics are marked in Table~\ref{tab:bins}.
+%% These bins should be avoided while evaluating the evolution of the
+%% luminosity function.  The remaining redshift can
 
@@
 
-Figure~\ref{fig:mosaic_global}
-shows the three
-%% JFH global 
-models in comparison
-with the binned fits from the previous section.  The shaded regions
-show the one-sigma (68.26\%) uncertainty.  The symbols show the
-luminosity function binned in luminosity and redshift, and the yellow
-shaded regions show the posterior distribution of the double power law
-luminosity functions in various redshift bins, as in
+Figure~\ref{fig:mosaic_global} shows the three global models in
+comparison with the binned fits from the previous section.  The shaded
+regions show the one-sigma (68.26\%) uncertainty.  The symbols show
+the luminosity function binned in luminosity and redshift, and the
+yellow shaded regions show the posterior distribution of the double
+power law luminosity functions in various redshift bins, as in
 Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
@@
 although Model~1 performs better.
-%% JFH by eye model 1 performs better
 
@@
 the fits in redshift bins discussed in the previous section.
-%% JFH Reference Figure 5 here as well.  
-The
-deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
-is again strikingly apparent.  So is
-%% JFH , as is the deviation
-the deviation of the SDSS and
-2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
-data selection discussion previously in Section~\ref{sec:bins}.
-Unfortunately, this model suffers
-%% JFH suffers from 
-with a remarkably sharp break in the
-evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
-seen in Figure~\ref{fig:evoln_global}, the data seem to require this
-break, although it seems unlikely that such a sharp break at this
-redshift would be physical.  Model 1 thus serves to emphasize the
-necessity of better quality data at these redshifts.  Models 2 and 3
-are shown in Figure~\ref{fig:evoln_global} by the green and orange
-curves, respectively.  The corresponding parameter values are
-tabulated in Table~\ref{tab:global}.
+The deviation of the BOSS quasars at $z=2$--$4$ from the smooth
+evolution is again strikingly apparent, as is the deviation of the
+SDSS and 2SLAQ quasars at $z<0.6$.  This is an indirect justification
+for the data selection discussion previously in
+Section~\ref{sec:bins}.  Unfortunately, this model suffers from a
+remarkably sharp break in the evolution of the faint-end slope $\beta$
+at about $z\sim 3.5$.  As seen in Figure~\ref{fig:evoln_global}, the
+data seem to require this break, although it seems unlikely that such
+a sharp break at this redshift would be physical.  Model 1 thus serves
+to emphasize the necessity of better quality data at these redshifts.
+Models 2 and 3 are shown in Figure~\ref{fig:evoln_global} by the green
+and orange curves, respectively.  The corresponding parameter values
+are tabulated in Table~\ref{tab:global}.
 
@@
 down to different limits.  Similar to Figure~\ref{fig:evoln_global},
-symbols show the posterior median values with one-sigma uncertainties from the
-double power law fits to the data in redshift bins.
+symbols show the posterior median values with one-sigma uncertainties
+from the double power law fits to the data in redshift bins.
 %% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
@@
 %% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
-Solid curves and
-shaded regions show the global models.  This number density evolution
-again highlights the systematic error in data at $z\sim 3$.  The
-number density of AGN down to the limit of
-%% JFH the deepest spectroscopic surveys 
-spectroscopic data
-($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
-density rapidly increases
-%% JFH I think you mean decreases here
-at low redshifts and then drops gradually at
-high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
-downsizing feature in which the number density of faint AGN peaks at
-lower redshifts than that of the bright AGN.  While the number density
-of AGN with $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN
-with $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at
-which spectroscopic data exist, $M_*<-21$, the number density of qsos
-peaks at $z\sim 1$.
-%% JFH The figure is not consistent with this statement. The model showing M < 21 is peaking
-%% just below z = 2. 
-However, the difference between our three models
-is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
-decrease in the number density of faint quasars at $z\sim 3$ followed
-by an increase at higher redshift.  This is caused by the rapid
-steepening of the faint-end slope in this model at this redshift.
-%% JFH Reference lower right panel of figure 6 here. 
-Figure~\ref{fig:rhoqso} reveals another property of these models: when
-extrapolated, the AGN number density diverges in all three models at
-high redshifts.
+Solid curves and shaded regions show the global models.  This number
+density evolution again highlights the systematic error in data at
+$z\sim 3$.  The number density of AGN down to the limit of the deepest
+spectroscopic surveys ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$
+at its peak.  This density rapidly increases with redshift at low
+redshifts and then drops with redshift gradually at high redshifts.
+Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
+which the number density of faint AGN peaks at lower redshifts than
+that of the bright AGN.  While the number density of AGN with
+$M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
+$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
+spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
+at a slightly lower redshift.  However, the difference between our
+three models is dramatically evident in Figure~\ref{fig:rhoqso}.
+Model~1 prefers a decrease in the number density of faint quasars at
+$z\sim 3$ followed by an increase at higher redshift.  This is caused
+by the rapid steepening of the faint-end slope in this model at this
+redshift (Figure~\ref{fig:evoln_global}).  Figure~\ref{fig:rhoqso}
+reveals another property of these models: when extrapolated, the AGN
+number density diverges in all three models at high redshifts.
 %% JFH I think this is just an artifiact of your fitting procedure,
@@
 
-%% JFH My main feedback on this section is that you need to elaborate more on which samples you included and excluded and why. That
-%% is fine if it is all based on by eye discarding things. We need to make the point more clearly that the various surveys suffer
-%% systematics, and hence cannot yet really be combined to give a sensible global evolution without some kind of massaging or choices
-%% about which datasets to trust.
-
 \begin{figure*}
@@
 
-%% JFH I think you could possibly break of this last section as a separate letter. The paper above would just be a data analysis and
-%% compilation paper.
-
 We now discuss the contribution of AGN to the hydrogen and helium
 reionization in our luminosity function model.  We first derive the
-redshift evolution of the 912\,\AA\ emissivity of AGN,
-and then use this to estimate the contribution of AGN to the \ion{H}{i} photoionization rate
-between $z=0$ and $z=7$, as well as the redshift evolution of the average \ion{He}{iii} fraction
-in the IGM for a quasar-driven \ion{He}{ii} reionization.
-%% JFH Mention low-z UVB here as well in intro.
+redshift evolution of the 912\,\AA\ emissivity of AGN, and then use
+this to estimate the contribution of AGN to the \ion{H}{i}
+photoionization rate between $z=0$ and $z=7$, as well as the redshift
+evolution of the average \ion{He}{iii} fraction in the IGM for a
+quasar-driven \ion{He}{ii} reionization.
 
@@
 \end{equation}
-as derived from a stacked spectrum of 53 luminous ($M_{1450}\simeq -27$)
-$z\simeq 2.4$ quasars \citep{2015MNRAS.449.4204L}, and consistent
-with recent composite spectra of low-$z$ quasars with a wide range in luminosity
-\citep{2012ApJ...752..162S, 2014ApJ...794...75S}.
-The extreme UV SED of faint ($M_{1100}\approx -22$) AGN may be significantly
-harder \citep[$\alpha_\nu=-0.56$,][]{2004ApJ...615..135S}, but the exact value of the slope
-critically depends on the total rest-frame wavelength coverage, the adopted continuum windows,
-the correction for IGM line blanketing, and the ability to distinguish
+as derived from a stacked spectrum of 53 luminous ($M_{1450}\simeq
+-27$) $z\simeq 2.4$ quasars \citep{2015MNRAS.449.4204L}, and
+consistent with recent composite spectra of low-$z$ quasars with a
+wide range in luminosity \citep{2012ApJ...752..162S,
+  2014ApJ...794...75S}.  The extreme UV SED of faint ($M_{1100}\approx
+-22$) AGN may be significantly harder
+\citep[$\alpha_\nu=-0.56$,][]{2004ApJ...615..135S}, but the exact
+value of the slope critically depends on the total rest-frame
+wavelength coverage, the adopted continuum windows, the correction for
+IGM line blanketing, and the ability to distinguish
 low-equivalent-width emission lines from the underlying continuum
 \citep{2014ApJ...794...75S,2015MNRAS.449.4204L,2016ApJ...817...56T}.
-For the computation of the hydrogen Lyman limit emissivity the choice of the spectral index
-at $\lambda<912$\,\AA\ is inconsequential, whereas for the calculation of the \ion{H}{i}
-photoionization rate in the IGM and the \ion{He}{ii} reionization history other
-sources of uncertainty dominate (see below). We note that all composite AGN spectra
-are consistent with an AGN Lyman limit escape fraction of unity
-(see also \citealt{2018A&A...613A..44G} for a recent sample of faint $z\sim 4$ AGN).
-We therefore adopt an escape fraction of unity for Lyman continuum photons.
-
-%% GW simplified the following derivation
-%The rate of emission of photons of frequency $\nu$ by quasars can be
-%written as
-%\begin{equation}
-%  \dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
-%\end{equation}
-%where the integral is over a suitable range of magnitudes, the
-%monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
-%magnitude by \citep{1983ApJ...266..713O}
-%\begin{equation}
-%  M_\nu = -2.5\log_{10}L_\nu+51.60,
-%\end{equation}
-%and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
-%related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
-%or (\ref{eqn:sed_faint})
-%\begin{equation}
-%  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
-%\end{equation}
-%depending on the AGN luminosity.  The corresponding comoving volume
-%emissivity is
-%\begin{equation}
-%  \epsilon_\nu = \dot n_\nu h\nu.
-%  \label{eqn:epsilon}
-%\end{equation}
-With our adopted SED the specific comoving volume emissivity of quasars at 912\,\AA\ can be written as
+For the computation of the hydrogen Lyman limit emissivity the choice
+of the spectral index at $\lambda<912$\,\AA\ is inconsequential,
+whereas for the calculation of the \ion{H}{i} photoionization rate in
+the IGM and the \ion{He}{ii} reionization history other sources of
+uncertainty dominate (see below). We note that all composite AGN
+spectra are consistent with an AGN Lyman limit escape fraction of
+unity (see also \citealt{2018A&A...613A..44G} for a recent sample of
+faint $z\sim 4$ AGN).  We therefore adopt an escape fraction of unity
+for Lyman continuum photons.
+
+With our adopted SED the specific comoving volume emissivity of
+quasars at 912\,\AA\ can be written as
 \begin{eqnarray}\nonumber
@@
 \end{eqnarray}
-which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$ and on the
-faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg M_*$.
-The black circles in Figure~\ref{fig:e912_2} show the comoving 912\,\AA\ emissivity
-obtained from the individual QLF fits (Table~\ref{tab:bins}) for $M_{1450}<-18$ (left panel)
-and $M_{1450}<-21$ (right panel), respectively. Redshift bins that were removed from
-the analysis due to large systematic errors in the QLF parameters are shown as open circles.
-\textbf{GW: Add a sentence on error bars.}
-Our derived emissivity values at 912\,\AA\ and at 1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins}
-for reference.
-The emissivity peaks between $z=2$ and 3 at $\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
-depending on the magnitude limit, and decreases rapidly towards lower and higher redshifts.
-Systematic errors in the faint-end slope derived from BOSS data are
-more pronounced for $M_{1450}<-18$ due to extrapolation of the QLF.
+which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$
+and on the faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg
+M_*$.  The black circles in Figure~\ref{fig:e912_2} show the comoving
+912\,\AA\ emissivity obtained from the individual QLF fits
+(Table~\ref{tab:bins}) for $M_{1450}<-18$ (left panel) and
+$M_{1450}<-21$ (right panel), respectively. Redshift bins that were
+removed from the analysis due to large systematic errors in the QLF
+parameters are shown as open circles.  \textbf{GW: Add a sentence on
+  error bars.}  Our derived emissivity values at 912\,\AA\ and at
+1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins} for
+reference.  The emissivity peaks between $z=2$ and 3 at
+$\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\,
+  cMpc^{-3}}$ depending on the magnitude limit, and decreases rapidly
+towards lower and higher redshifts.  Systematic errors in the
+faint-end slope derived from BOSS data are more pronounced for
+$M_{1450}<-18$ due to extrapolation of the QLF.
 
@@
 \end{equation}
-assuming a Gaussian likelihood for the emissivity values.
-The resultant curves and the corresponding one-sigma
-uncertainties are shown in Figure~\ref{fig:e912_2}. For $M_{1450}<-18$
-we obtain
+assuming a Gaussian likelihood for the emissivity values.  The
+resultant curves and the corresponding one-sigma uncertainties are
+shown in Figure~\ref{fig:e912_2}. For $M_{1450}<-18$ we obtain
 \begin{multline}
@@
 \end{multline}
-Table~\ref{tab:gamma2} provides the derived emissivities at 912\,\AA\ and 1450\,\AA\ together with their
-derived errors at $0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.
-
-%% Original text from GK with comments from JFH, rewritten by GW below
-
-%Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
-%the luminosity function is integrated down to $M_{1450}<-21$ (right
-%panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
-%% JFH Figure 8 is a nightmare to look at. You need to separate this into multiple
-%% figures somehow. Perhaps one with curves and one with points. 
-%Redshift bins that were removed from analysis due to large systematic
-%errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
-%depending on the luminosity integration limit, at
-%$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
-%and decreased
-%% JFH decreases 
-%rapidly towards high redshifts.  A continuous
-%description of this emissivity evolution is valuable in deriving the
-%hydrogen photoionizing flux in the IGM.  In principle, the luminosity
-%function evolution models discussed in the previous section provide
-%such a description.  Unfortunately, as discussed above, all of these
-%models suffer from pathologies such as non-monotonic or divergent
-%% JFH divergence is just becuase of how you do the fits, and not having data at high-z. I don't think
-%% that should be highlighted. 
-%AGN
-%number densities, likely resulting from residual systematic errors in
-%the data.  Therefore, here we describe the emissivity evolution by the
-%five-parameter functional form used by \citet{2012ApJ...746..125H}
-%\begin{equation}
-%  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
-%  \label{eqn:e912fit}
-%\end{equation}
-%We fit this model to the emissivity estimates in the redshift bins,
-%shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
-%the emissivity in each bin.  The resultant best-fit curves and the
-%corresponding one-sigma uncertainties are shown in
-%Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
-%912\,\AA\ emissivities in various redshift bins and in these best-fit
-%models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
-%form of Equation~\ref{eqn:e912fit} is given by
-%\begin{multline}
-%  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
-%\end{multline}
-%for $M_{1450}<-18$, and by 
-%\begin{multline}
-%  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
-%\end{multline}
-%for $M_{1450}<-21$.
-%% JFH So if I understand correctly you have given up on the global model and are now doing things
-%% with the binned fits, since your global model produces weird non-monotonic behavior. You need to state
-%% what you are doing here, so the reader understands where these data points come from on the plot.
-%Before proceeding to derive a hydrogen photoionization rate estimate
-%from these emissivities, we now comment on the comparison of our
-%results with estimates from the literature.  Several of these are
-%shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
-%Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
-%\citet{2012ApJ...746..125H}, which is based on the bolometric
-%luminosity function model of \citet{2007ApJ...654..731H}.  Their
-%assumed emissivity agrees reasonably well with our $M_{1450}<-21$
-%case, although at its maximum the emissivity in the
-%\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
-%differences between the two models are much larger for $M_{1450}<-18$.
-%Figure~\ref{fig:e912_2} also shows the model presented by
-%\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
-%severely at almost all redshifts in the range considered here, for
-%both of our integration limits.  It is important to note here that a
-%direct comparison of our model with \citet{2012ApJ...746..125H} and
-%\citet{2015ApJ...813L...8M} is difficult because these models
-%integrate the luminosity function to a fixed fraction of the break
-%luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
-%limite
-%% JFH limite --> limit 
-%by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
-%is $0.01L_*$.  Using a limit that depends on the break luminosity is
-%problematic as different quasar surveys used to develop these
-%emissivity models often report strikingly different break luminosity
-%values.  Even when these samples are homogeneized appropriately, have
-%% JFH adopting such an integratino limit....
-%such an integration limit is likely only justified if the faint-end
-%slope of the luminosity function is sufficiently shallow.  This issue
-%also affects some other models in the literature, such as those
-%presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
-%and \citet{2018arXiv180104931P}.
-%\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
-%$M_{1450}=-19$.  However, their model strongly disagrees with our
-%inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
-%biases resulting from inhomogeneously combining binned luminosity
-%function estimates from different data sets.  The emissivity
-%determinations from the luminosity function derived from a
-%variability-selected sample observed using the Sloan
-%% JFH Sloan telescopee --> SDSS telescope
-%telescope and the
-%Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
-%agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
-%redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
-%%% GW: At z>2.2 the disagreement is much larger than 10-30 percent!!!
-%The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
-%not included in our analysis, and therefore provides a cross-check.
-%(This sample also does not overlap with the variability-selected
-%sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
-%\citet{2013A&A...551A..29P} assume constant double power law
-%luminosity function slopes with a break at $z=2.2$ and assume a pure
-%luminosity evolution.  This leads to a discontinuity in the emissivity
-%evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
-%convert their $g$-band magnitudes to $M_{1450}$ and integrate the
-%resultant luminosity function down to our two chosen integration
-%limits with our chosen SED for a direct comparison.
-%Figure~\ref{fig:e912_2} also shows the model presented by
-%\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
-%which the faint-end slope is assumed to stay constant with redshift.
-%Although the emissivity evolution in this model is continuous at
-%$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
-%smooth.  This model agrees with our $M_{1450}<-18$ result to a better
-%degree relative to the \citet{2013A&A...551A..29P} model, bjt
-%% JFH bjt --> but
-%it results in a higher emissivity in the $M_{1450}<-21$ case.
-%\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
-%sample with an improved $K$-correction implementation, but, as seen in
-%Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
-%throughout the redshift range of their data.
-%% JFH For the Palanque and Caditz etc. comparisons, it occurs to me that these guys
-%% probably used the luminosity function and not the epsilon_912. I'm just wondering why you
-%% choose to do the comparisons in this quantity if other authors didn't compute this quantity. I understand
-%% that one is the integral of the other, but it would seem more sensible to me to compare to the Palangue-luminosity
-%% function when you discuss the individual fits to luminosity functions in say their same redshift bins, then when you
-%% compute the emissivity evolution here. This just seems out of place. I think comparing to other peoples emissivities
-%% here is sensible, but integrating other peoples lum functions here is less transparent.
-
-%At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
-%power law luminosity function model to a combined binned samples of
-%\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
-%\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
-%photometric redshift $z\sim 6$ reported by
-%\citet{2018MNRAS.474.2904P}.  We show the resultant
-%912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
-%lower side of the rectangle corresponds to the emissivity for the
-%\citet{2017ApJ...847L..15O} model excluding the
-%\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
-%the emissivity is higher; this is shown by the upper end of the
-%rectangle.  Our emissivities broadly in agreement with the
-%determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
-%shows the determination from the fits of \citet{2015AA...578A..83G}.
-%These authors also choose a break luminosity-dependent integration
-%limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
-%model.  The resultant emissivities are factors of 2 to 3 higher than
-%our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
-%puzzling at first sight, because the AGN candidates reported by
-%\citet{2015AA...578A..83G} are consistent with our luminosity function
-%estimates obtained without these candidates (see
-%Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
-%steeper than those reported by \citet{2015AA...578A..83G}.  The
-%discrepancy is explained by the difference in the two luminosity
-%function models at intermediate magnitudes.  We find that the data
-%prefer a much brighter break luminosity than that inferred by
-%\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
-%their estimates.  We go into this issue in further detail in
-%Appendix~\ref{sec:conv}.
-
-%\citet{2018AJ....155..131M} recently extended their previous Stripe~82
-%AGN sample by 1.5 magnitude and fit a double power law luminosity
-%function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
-%$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
-%$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
-%than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
-%LF to our cosmology and assuming our SED result in the emissivities
-%shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
-%measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
-%higher than their measurement for $M_{1450}<-18$, which is not
-%surprising due to the difference in the luminosity function slopes.
-%The emissivity derived from the luminosity function of
-%\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
-%These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
-%have spectroscopic redshifts.  Their reported faint-end slope is very
-%flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
-%all redshifts.  Their inferred emissivity is consistent with our
-%estimate for $M_{1450}< -21$.  Their emissivity does not change
-%significantly with the integration limit due to the shallow faint-end
-%slope.  As a result, our $M_{1450}< -18$ determination of the
-%emissivity is considerably higher than their estimate.  We also
-%compare our emissivities with the determinations reported by
-%\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
-%emissivity in reasonable agreement with our model for $M_{1450}<-21$
-%at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
-%recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.
-
-%At low redshifts, \citet{2009A&A...507..781S} combined data from the
-%Hamburg/ESO survey and the SDSS to measure a quasar luminosity
-%function at $z=0$ in their $B_J$ band to minimize host galaxy
-%contribution.  We convert their $B_J$ magnitudes (Vega system) to
-%$M_{1450}$ (AB) as
-%\begin{equation}
-%  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
-%\end{equation}
-%In this magnitude system, the luminosity function reported by
-%\citet{2009A&A...507..781S} has a very faint break luminosity of
-%$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
-%integrate this luminosity function down to our limiting magnitudes of
-%$M_{1450}=-18$ and $-21$.  The resultant values are shown in
-%Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
-%between the \citet{2009A&A...507..781S} measurements.  The convergence
-%in the emissivity is slower in their measurements than in our models
-%because of the shallower faint-end slope at this redshift in our model
-%($\beta\sim -1.22$).
+Table~\ref{tab:gamma2} provides the derived emissivities at
+912\,\AA\ and 1450\,\AA\ together with their derived errors at
+$0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.
 
@@
 
-Before proceeding to derive estimates of the quasar contribution to the IGM \ion{H}{i} photoionization rate
-from the fitted 912\,\AA\ emissivity, it is instructive to compare our results to recent estimates from
-the literature\footnote{We do not compare to \citet{2017MNRAS.466.1160M} due to an error in their analysis.
-Integration of the 912\,\AA\ emissivity to $M_{1450}^\mathrm{lim}=-19$ with their double power law
-QLF parameterization as a function of redshift yields values 13--75 per cent higher than those implied by their Equation 9.
-This also explains the striking discrepancy to literature values at $z<3$ (their Figure 4).}.
-The various blue symbols in Figure~\ref{fig:e912_2} show emissivity values that we have computed
-from other recent QLF determinations in narrow redshift ranges.
-The various curves show emissivities derived from parametric QLF model fits over larger redshift ranges,
-or fits to $\epsilon_{912}\left(z\right)$. All QLFs using different magnitude systems have been converted to
-$M_{1450}$ with the \citet{2015MNRAS.449.4204L} SED,
-and all QLFs have been adjusted to our cosmology.
-For the $z\simeq 0$ QLF reported by \citet{2009A&A...507..781S} we
-convert their $B_J$ magnitudes in the Vega system to our AB magnitudes
-as $M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59$.
-Lyman limit emissivities have been consistently derived using 
-Equation~\eqref{eqn:sed} and for our adopted magnitude limits whenever possible.
-We note that due to strong covariance in the QLF parameters
-it is not straightforward to compute statistical errors of $\epsilon$ from given QLF fits,
-and we refrained from using the incorrect procedures applied by \citet{2015MNRAS.451L..30K}.
-\textbf{GW: Emphasize again that our error bars are correct and superior to Khaire's!}
-
-The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model adopted by
-\citet{2012ApJ...746..125H}, which is based on the bolometric luminosity function from \citet{2007ApJ...654..731H}.
-The bolometric emissivity derived by \citet{2007ApJ...654..731H} converges for luminosities $L>0$
-due to their shallow faint-end QLF slope, which should yield a higher 912\,\AA\ emissivity for
-both our adopted magnitude limits. We attribute much of the discrepancy to the conversion from bolometric
-to 912\,\AA\ emissivity assumed by \citet{2007ApJ...654..731H}.
-Figure~\ref{fig:e912_2} also shows the emissivity curve from \citet{2015ApJ...813L...8M}
-that was inspired by recent QLF fits including the highly debated \citet{2015AA...578A..83G} results.
-The emissivity adopted by \citet{2015ApJ...813L...8M} exceeds our fits by more than a factor of two
-at $z\la 1$ and $z\ga 4$. Moreover, we stress that our emissivities have been derived for fixed magnitude
-limits $M_{1450}^\mathrm{lim}$ at all redshifts (Equation~\eqref{eqn:epsilon}), whereas other authors have
-adopted magnitude limits $M_{1450}^\mathrm{lim}\left(z\right)=M_*\left(z\right)+5$ that vary with break
-magnitude and redshift \citep{2015AA...578A..83G,2015ApJ...813L...8M,2015MNRAS.451L..30K,2018arXiv180104931P}.
-We deem the latter convention to be physically unfounded, because (i) the customary QLF double power-law
-parameterization lacks a deeper physical meaning, (ii) $M_*$ decreases by more than five magnitudes
-with redshift (Figure~\ref{fig:evoln}, see also \citealt{2013ApJ...768..105M} and \citealt{2016ApJ...829...33Y}),
-and (iii) the various QLF fits at the same redshift are highly discordant (Appendix~\ref{sec:qlfliterature}).
-Inhomogeneous magnitude limits lead to artificial scatter in the derived emissivities if the faint-end slope of
-the QLF is not sufficiently shallow. Our fixed magnitude limits bracket a reasonable range of QLF extrapolations
-beyond the range covered by current data, whereas a varying limit $M_*+5$ includes feeble
-$M_{1450}\simeq -18$ AGN at $z<0.6$, but excludes verified $M_{1450}\simeq -24$ quasars at $z\simeq 6$ (Figure~\ref{fig:evoln}).
-
-\citet{2013A&A...551A..29P,2016A&A...587A..41P} presented two variability-selected quasar
-samples that are not included in our analysis, and therefore provide a valuable cross-check.
-In Figure~\ref{fig:e912_2} we show the emissivities computed from their parametric model fits
-to binned QLFs at $0.68<z<4$. \citet{2013A&A...551A..29P} fitted pure luminosity evolution
-models to binned QLFs from their data set and the one by \citet{2009MNRAS.399.1755C},
-but with a discontinuity in the QLF slopes at $z=2.2$ that cause artificial discontinuities
-in the QSO number density and the emissivity. The good agreement with our inferences at
-$z<2.2$ is partially due to sample overlap. \citet{2016A&A...587A..41P} presented an
-independent sample of 13876 variability-selected quasars. They fitted their binned QLFs
-with a pure luminosity evolution model at $z<2.2$ and a luminosity and density evolution
-model at higher redshifts, imposing continuity at $z=2.2$. The emissivity computed from
-their QLF is in good agreement with our results at $z<2.2$, but is systematically lower at
-higher redshifts. \citet{2017A&A...608A..64C} corrected an apparent error in the bandpass
-correction applied by \citet{2016A&A...587A..41P} that results in a higher QLF at $z>3$.
-However, his higher inferred $\phi_*$ at $z=0$ causes a 30--60 per cent higher emissivity
-at $z<2.2$ compared to our inferences. Since neither \citet{2013A&A...551A..29P,2016A&A...587A..41P}
-nor \citet{2017A&A...608A..64C} fitted the QLF in narrow redshift bins from unbinned quasar data,
-it remains unclear whether there is a systematic difference between colour-selected and
-variability-selected samples at $z<2.2$. As variability-selected samples to not probe the faint end of the
-QLF at $z>3$, inferences of the high-redshift quasar number density and emissivity are highly uncertain at present.
-
-We also calculate the 912\,\AA\ emissivities from various determinations of the UV QLF in narrow redshift ranges
+Before proceeding to derive estimates of the quasar contribution to
+the IGM \ion{H}{i} photoionization rate from the fitted
+912\,\AA\ emissivity, it is instructive to compare our results to
+recent estimates from the literature\footnote{We do not compare to
+  \citet{2017MNRAS.466.1160M} due to an error in their analysis.
+  Integration of the 912\,\AA\ emissivity to
+  $M_{1450}^\mathrm{lim}=-19$ with their double power law QLF
+  parameterization as a function of redshift yields values 13--75 per
+  cent higher than those implied by their Equation 9.  This also
+  explains the striking discrepancy to literature values at $z<3$
+  (their Figure 4).}.  The various blue symbols in
+Figure~\ref{fig:e912_2} show emissivity values that we have computed
+from other recent QLF determinations in narrow redshift ranges.  The
+various curves show emissivities derived from parametric QLF model
+fits over larger redshift ranges, or fits to
+$\epsilon_{912}\left(z\right)$. All QLFs using different magnitude
+systems have been converted to $M_{1450}$ with the
+\citet{2015MNRAS.449.4204L} SED, and all QLFs have been adjusted to
+our cosmology.  For the $z\simeq 0$ QLF reported by
+\citet{2009A&A...507..781S} we convert their $B_J$ magnitudes in the
+Vega system to our AB magnitudes as $M_{1450,\mathrm{AB}}=M_{B_J,
+  \mathrm{Vega}}+0.59$.  Lyman limit emissivities have been
+consistently derived using Equation~\eqref{eqn:sed} and for our
+adopted magnitude limits whenever possible.  We note that due to
+strong covariance in the QLF parameters it is not straightforward to
+compute statistical errors of $\epsilon$ from given QLF fits, and we
+refrained from using the incorrect procedures applied by
+\citet{2015MNRAS.451L..30K}.  \textbf{GW: Emphasize again that our
+  error bars are correct and superior to Khaire's!}
+
+The brown dashed curve in Figure~\ref{fig:e912_2} shows the AGN
+912\,\AA\ emissivity model adopted by \citet{2012ApJ...746..125H},
+which is based on the bolometric luminosity function from
+\citet{2007ApJ...654..731H}.  The bolometric emissivity derived by
+\citet{2007ApJ...654..731H} converges for luminosities $L>0$ due to
+their shallow faint-end QLF slope, which should yield a higher
+912\,\AA\ emissivity for both our adopted magnitude limits. We
+attribute much of the discrepancy to the conversion from bolometric to
+912\,\AA\ emissivity assumed by \citet{2007ApJ...654..731H}.
+Figure~\ref{fig:e912_2} also shows the emissivity curve from
+\citet{2015ApJ...813L...8M} that was inspired by recent QLF fits
+including the highly debated \citet{2015AA...578A..83G} results.  The
+emissivity adopted by \citet{2015ApJ...813L...8M} exceeds our fits by
+more than a factor of two at $z\la 1$ and $z\ga 4$. Moreover, we
+stress that our emissivities have been derived for fixed magnitude
+limits $M_{1450}^\mathrm{lim}$ at all redshifts
+(Equation~\eqref{eqn:epsilon}), whereas other authors have adopted
+magnitude limits
+$M_{1450}^\mathrm{lim}\left(z\right)=M_*\left(z\right)+5$ that vary
+with break magnitude and redshift
+\citep{2015AA...578A..83G,2015ApJ...813L...8M,2015MNRAS.451L..30K,2018arXiv180104931P}.
+We deem the latter convention to be physically unfounded, because (i)
+the customary QLF double power-law parameterization lacks a deeper
+physical meaning, (ii) $M_*$ decreases by more than five magnitudes
+with redshift (Figure~\ref{fig:evoln}, see also
+\citealt{2013ApJ...768..105M} and \citealt{2016ApJ...829...33Y}), and
+(iii) the various QLF fits at the same redshift are highly discordant
+(Appendix~\ref{sec:qlfliterature}).  Inhomogeneous magnitude limits
+lead to artificial scatter in the derived emissivities if the
+faint-end slope of the QLF is not sufficiently shallow. Our fixed
+magnitude limits bracket a reasonable range of QLF extrapolations
+beyond the range covered by current data, whereas a varying limit
+$M_*+5$ includes feeble $M_{1450}\simeq -18$ AGN at $z<0.6$, but
+excludes verified $M_{1450}\simeq -24$ quasars at $z\simeq 6$
+(Figure~\ref{fig:evoln}).
+
+\citet{2013A&A...551A..29P,2016A&A...587A..41P} presented two
+variability-selected quasar samples that are not included in our
+analysis, and therefore provide a valuable cross-check.  In
+Figure~\ref{fig:e912_2} we show the emissivities computed from their
+parametric model fits to binned QLFs at
+$0.68<z<4$. \citet{2013A&A...551A..29P} fitted pure luminosity
+evolution models to binned QLFs from their data set and the one by
+\citet{2009MNRAS.399.1755C}, but with a discontinuity in the QLF
+slopes at $z=2.2$ that cause artificial discontinuities in the QSO
+number density and the emissivity. The good agreement with our
+inferences at $z<2.2$ is partially due to sample
+overlap. \citet{2016A&A...587A..41P} presented an independent sample
+of 13876 variability-selected quasars. They fitted their binned QLFs
+with a pure luminosity evolution model at $z<2.2$ and a luminosity and
+density evolution model at higher redshifts, imposing continuity at
+$z=2.2$. The emissivity computed from their QLF is in good agreement
+with our results at $z<2.2$, but is systematically lower at higher
+redshifts. \citet{2017A&A...608A..64C} corrected an apparent error in
+the bandpass correction applied by \citet{2016A&A...587A..41P} that
+results in a higher QLF at $z>3$.  However, his higher inferred
+$\phi_*$ at $z=0$ causes a 30--60 per cent higher emissivity at
+$z<2.2$ compared to our inferences. Since neither
+\citet{2013A&A...551A..29P,2016A&A...587A..41P} nor
+\citet{2017A&A...608A..64C} fitted the QLF in narrow redshift bins
+from unbinned quasar data, it remains unclear whether there is a
+systematic difference between colour-selected and variability-selected
+samples at $z<2.2$. As variability-selected samples to not probe the
+faint end of the QLF at $z>3$, inferences of the high-redshift quasar
+number density and emissivity are highly uncertain at present.
+
+We also calculate the 912\,\AA\ emissivities from various
+determinations of the UV QLF in narrow redshift ranges
 \citep{2009A&A...507..781S,2012ApJ...755..169M,2015AA...578A..83G,2017ApJ...847L..15O,2018PASJ...70S..34A,2018AJ....155..131M,2018MNRAS.474.2904P}.
-All these QLF determinations are not fully independent from ours due to partial sample overlap,
-mostly from SDSS at the bright end. We use both QLF determinations from \citet{2017ApJ...847L..15O}
-with and without including a faint X-ray-selected $z\sim 6$ AGN candidate \citep{2018MNRAS.474.2904P},
-and indicate the emissivities with a box in Figure~\ref{fig:e912_2}.  
-For $M_{1450}<-21$ our $\epsilon_{912}\left(z\right)$ parameterization and the individual values
-are generally consistent with those computed from other QLFs in narrow redshift ranges,
-apart from the results by \citet{2015AA...578A..83G} that have been disputed by several studies
-\citep[][see Appendix~\ref{sec:conv} for further discussion]{2015MNRAS.453.1946G,2016MNRAS.463..348V,2017MNRAS.465.1915R,2018AJ....155..131M,2018MNRAS.474.2904P}. 
-As detailed in Section~\ref{sect:samplesel}, the \citet{2012ApJ...755..169M} QLF at $z\sim 4$ -- and hence the
-derived emissivity -- is underestimated due to systematic error in their photometric redshifts,
-while their $z\sim 3.2$ results likely suffer from systematic uncertainty in the SDSS selection function
+All these QLF determinations are not fully independent from ours due
+to partial sample overlap, mostly from SDSS at the bright end. We use
+both QLF determinations from \citet{2017ApJ...847L..15O} with and
+without including a faint X-ray-selected $z\sim 6$ AGN candidate
+\citep{2018MNRAS.474.2904P}, and indicate the emissivities with a box
+in Figure~\ref{fig:e912_2}.  For $M_{1450}<-21$ our
+$\epsilon_{912}\left(z\right)$ parameterization and the individual
+values are generally consistent with those computed from other QLFs in
+narrow redshift ranges, apart from the results by
+\citet{2015AA...578A..83G} that have been disputed by several studies
+\citep[][see Appendix~\ref{sec:conv} for further
+  discussion]{2015MNRAS.453.1946G,2016MNRAS.463..348V,2017MNRAS.465.1915R,2018AJ....155..131M,2018MNRAS.474.2904P}.
+As detailed in Section~\ref{sect:samplesel}, the
+\citet{2012ApJ...755..169M} QLF at $z\sim 4$ -- and hence the derived
+emissivity -- is underestimated due to systematic error in their
+photometric redshifts, while their $z\sim 3.2$ results likely suffer
+from systematic uncertainty in the SDSS selection function
 \citep{2011ApJ...728...23W,2012ApJS..199....3R,2013ApJ...773...14R}.
 
-Integration to $M_{1450}=-18$ results in larger discrepancies due to extrapolation of the QLF
-with an uncertain faint-end slope. 
-\citet{2018PASJ...70S..34A} obtained a very flat faint-end slope $\beta=-1.30\pm 0.05$
-that is inconsistent with our determinations at all redshifts. Since they selected only
-point sources, they might be missing a significant fraction of AGN at $M_{1450}>-23.5$.
-In addition, only $4.6$ per cent of their AGN have spectroscopic redshifts,
-such that their correction for contamination is very rough.
-The large difference in the inferred $M_{1450}<-18$ emissivity at $z\simeq 5$ with respect to
-\citet{2018AJ....155..131M} is due to their shallower faint-end slope $\beta=-1.97\pm 0.09$
-compared to our result at this redshift ($\beta=-2.30^{+0.11}_{-0.08}$). We attribute the difference
-in the faint-end slope to the fixed bright-end slope $\alpha=-4$ in \citet{2018AJ....155..131M}
-that is larger than our measurements at $z>3.5$ (Figure~\ref{fig:evoln}). 
-Similarly, \citet{2017ApJ...847L..15O} fixed the bright-end slope to $\alpha=-2.8$ which had been
-determined by \citet{2016ApJ...833..222J} from a single power-law fit to the bright end of the QLF.
-Our bright-end slopes are inconsistent with such high values at all redshifts, indicating that single
-power-law fits to a limited range in magnitude yield only approximate estimates of $\alpha$,
-biasing the other derived QLF parameters, quasar number densities and emissivities.
-Full double-power law fits to unbinned data over a wide magnitude range are required.
+Integration to $M_{1450}=-18$ results in larger discrepancies due to
+extrapolation of the QLF with an uncertain faint-end slope.
+\citet{2018PASJ...70S..34A} obtained a very flat faint-end slope
+$\beta=-1.30\pm 0.05$ that is inconsistent with our determinations at
+all redshifts. Since they selected only point sources, they might be
+missing a significant fraction of AGN at $M_{1450}>-23.5$.  In
+addition, only $4.6$ per cent of their AGN have spectroscopic
+redshifts, such that their correction for contamination is very rough.
+The large difference in the inferred $M_{1450}<-18$ emissivity at
+$z\simeq 5$ with respect to \citet{2018AJ....155..131M} is due to
+their shallower faint-end slope $\beta=-1.97\pm 0.09$ compared to our
+result at this redshift ($\beta=-2.30^{+0.11}_{-0.08}$). We attribute
+the difference in the faint-end slope to the fixed bright-end slope
+$\alpha=-4$ in \citet{2018AJ....155..131M} that is larger than our
+measurements at $z>3.5$ (Figure~\ref{fig:evoln}).  Similarly,
+\citet{2017ApJ...847L..15O} fixed the bright-end slope to
+$\alpha=-2.8$ which had been determined by \citet{2016ApJ...833..222J}
+from a single power-law fit to the bright end of the QLF.  Our
+bright-end slopes are inconsistent with such high values at all
+redshifts, indicating that single power-law fits to a limited range in
+magnitude yield only approximate estimates of $\alpha$, biasing the
+other derived QLF parameters, quasar number densities and
+emissivities.  Full double-power law fits to unbinned data over a wide
+magnitude range are required.
 
@@
 
-Our calculation of the AGN contribution to the UV background follows previous work on
-UV background synthesis models \citep[e.g.][]{1996ApJ...461...20H,2012ApJ...746..125H}.
-The main quantity of interest is the \ion{H}{i} photoionization rate of the UV background
+Our calculation of the AGN contribution to the UV background follows
+previous work on UV background synthesis models
+\citep[e.g.][]{1996ApJ...461...20H,2012ApJ...746..125H}.  The main
+quantity of interest is the \ion{H}{i} photoionization rate of the UV
+background
 \begin{equation}
@@
 \end{multline}
-is the angle- and space-averaged specific intensity of the UV background. In the above equation
+is the angle- and space-averaged specific intensity of the UV
+background. In the above equation
 $H\left(z^\prime\right)=H_0\sqrt{\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda}$
-is the Hubble parameter, and $\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)$
-is the comoving emissivity of all \ion{H}{i} Lyman continuum sources at redshift $z^\prime>z$ and emitted frequency
+is the Hubble parameter, and
+$\epsilon_\nu\left(\nu_\mathrm{em},z^\prime\right)$ is the comoving
+emissivity of all \ion{H}{i} Lyman continuum sources at redshift
+$z^\prime>z$ and emitted frequency
 $\nu_\mathrm{em}=\nu\left(1+z^\prime\right)/\left(1+z\right)>\nu_{912}$.
-In practice, we adopt an upper limit $z^\prime_\mathrm{max}=15$ when integrating Equation~\eqref{eqn:flux}.
-Assuming that quasars are the only ionizing sources and considering Equation~\eqref{eqn:sed} we have 
+In practice, we adopt an upper limit $z^\prime_\mathrm{max}=15$ when
+integrating Equation~\eqref{eqn:flux}.  Assuming that quasars are the
+only ionizing sources and considering Equation~\eqref{eqn:sed} we have
 \begin{equation}
@@
 \end{equation}
-where $\tau_1\approx N_\ion{H}{i}\sigma_\ion{H}{i}\left(\nu\left[\frac{1+z^{\prime\prime}}{1+z}\right]\right)$
-is the Lyman continuum optical depth through an individual absorber\footnote{The helium content of the
-absorber can be ignored due to the small \ion{H}{i} photoionization cross section at $\lambda<304$\,\AA.}.
-For the \ion{H}{i} column density distribution $f\left(N_\ion{H}{i},z\right)$ we adopt the piecewise power-law
-parametrization by \citet{2012ApJ...746..125H} that is consistent with $f\left(N_\ion{H}{i},z\right)$
-measurements at $z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$ effective optical depth
-\citep[but not in detail -- see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
-and the measured mean free path to \ion{H}{i} Lyman limit photons at $z<5.5$ \citep{2009ApJ...705L.113P,2014MNRAS.445.1745W}.
-\citet{2018arXiv180109693K} suggest that variations in $f\left(N_\ion{H}{i},z\right)$ result in modest
-(10--40 per cent) changes in $\Gamma_\ion{H}{i}$ at $z<3$. We note, however, that at $z\ga 3.5$
-all UV background synthesis models are based on brazen extrapolations of $f\left(N_\ion{H}{i},z\right)$,
-whose detailed shape for (partial) Lyman limit systems is not well constrained at these redshifts \citep{2010ApJ...718..392P}.
-
-Equations~\eqref{eqn:flux} and \eqref{eqn:taueff} assume that sources and absorbers are uncorrelated,
-and that $J_\nu(\nu, z)$ is spatially uniform, i.e.\ that the mean free path to \ion{H}{i} Lyman continuum
+where $\tau_1\approx
+N_\ion{H}{i}\sigma_\ion{H}{i}\left(\nu\left[\frac{1+z^{\prime\prime}}{1+z}\right]\right)$
+is the Lyman continuum optical depth through an individual
+absorber\footnote{The helium content of the absorber can be ignored
+  due to the small \ion{H}{i} photoionization cross section at
+  $\lambda<304$\,\AA.}.  For the \ion{H}{i} column density
+distribution $f\left(N_\ion{H}{i},z\right)$ we adopt the piecewise
+power-law parametrization by \citet{2012ApJ...746..125H} that is
+consistent with $f\left(N_\ion{H}{i},z\right)$ measurements at
+$z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$
+effective optical depth \citep[but not in detail --
+  see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
+and the measured mean free path to \ion{H}{i} Lyman limit photons at
+$z<5.5$ \citep{2009ApJ...705L.113P,2014MNRAS.445.1745W}.
+\citet{2018arXiv180109693K} suggest that variations in
+$f\left(N_\ion{H}{i},z\right)$ result in modest (10--40 per cent)
+changes in $\Gamma_\ion{H}{i}$ at $z<3$. We note, however, that at
+$z\ga 3.5$ all UV background synthesis models are based on brazen
+extrapolations of $f\left(N_\ion{H}{i},z\right)$, whose detailed shape
+for (partial) Lyman limit systems is not well constrained at these
+redshifts \citep{2010ApJ...718..392P}.
+
+Equations~\eqref{eqn:flux} and \eqref{eqn:taueff} assume that sources
+and absorbers are uncorrelated, and that $J_\nu(\nu, z)$ is spatially
+uniform, i.e.\ that the mean free path to \ion{H}{i} Lyman continuum
 photons is much larger than the average distance between the sources
 \citep[e.g.][]{1999ApJ...514..648M,2004MNRAS.350.1107M,2009ApJ...703.1416F,2012ApJ...746..125H}.
-Obviously, these assumptions do not hold for rare sources and during \ion{H}{i} reionization.
-At $z\simeq 5$ our (extrapolated) AGN number densities suggest an average distance of
-$\approx 70$\,cMpc between $M_{1450}<-21$ AGN (Figure~\ref{fig:rhoqso}), which is comparable
-to the mean free path \citep[$83\pm 10$\,cMpc,][]{2014MNRAS.445.1745W}.
-Consequently, if only $M_{1450}<-21$ AGN contribute to the emissivity then the UV radiation field at $z\simeq 5$ must fluctuate.
-If the QLF reaches to fainter magnitudes, or if star-forming galaxies contribute to the emissivity, the UV background remains
-uniform to higher redshifts, and the assumptions of standard UV background synthesis models remain valid.
-
-%The 912\,\AA\ emissivity can now be used to calculate the hydrogen
-%ionizing flux and the hydrogen photoionization rate contributed by
-%AGN.  This adds an additional layer of uncertainty as the \HI\ column
-%density structure of the IGM has not been measured at all redshifts of
-%interests, thereby requiring uncertain extrapolation.  The frequency
-%dependence of the AGN SED above 1~Ry is given by
-%Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
-%\nu_{912}$
-%\begin{equation}
-%  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
-%  \label{eqn:epsilon_freq}
-%\end{equation}
-%where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
-%(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
-%($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
-%IGM is written as a solution of the cosmological radiative transfer
-%equation as \citep{2012ApJ...746..125H}
-%\begin{multline}
-%  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
-%  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
-%  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
-%  \label{eqn:flux}
-%\end{multline}
-%where
-%\begin{equation}
-%  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
-%\end{equation}
-%Here the effective optical depth is estimated as
-%\begin{equation}
-%  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
-%  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
-%\end{equation}
-%where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
-%contribution of helium to the opacity.)  We assume the \HI\ column
-%density distribution given by \citet{2012ApJ...746..125H}.
-%% JFH elaborate on this. Say it is chosen to reproduce Worseck's MFP measurements
-%% and that it sensible extrapolate or something. You need to make it clear that it is indeed
-%% Gabors MFP that you are using here. 
-%The
-%\HI\ photoionization rate is then given by
-%\begin{equation}
- % \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
- % \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
-%\end{equation}
-%where $\sigma$ is the photoionization cross-section.
-%% JFH Is it obvious that the uncertaintites in the MFP which propagate into the HM fit for the column density
-%% distribution do not matter? If so this needs to be explicitly stated.
-
-The red and blue curves in Figure~\ref{fig:gammapi} show the inferred AGN \ion{H}{i} photoionization rate as a function of redshift for our integration limits $M_{1450}=-18$ and $-21$, respectively.
-For comparison we also plot the predictions of recent UV background synthesis models for AGN \citep{2012ApJ...746..125H,2015ApJ...813L...8M,2015MNRAS.451L..30K} and AGN$+$galaxies \citep{2012ApJ...746..125H,2018arXiv180104931P}, as well as inferences from the \ion{H}{i} Ly$\alpha$ forest \citep{2011MNRAS.412.1926W,2013MNRAS.436.1023B,2017MNRAS.467.3172G,2018MNRAS.473..560D}, the Ly$\alpha+\beta$ forest \citep{2018ApJ...855..106D}, and the quasar proximity effect \citep{2011MNRAS.412.2543C}.
-Where necessary, literature values have been rescaled by a few per cent to adjust to our cosmology.
-
-Differences in the \ion{H}{i} photoionization rates inferred from UV background synthesis models mostly arise from obvious differences in the emissivities of AGN and galaxies, but also due to differences in the parametrization of the IGM and the AGN SED.
+Obviously, these assumptions do not hold for rare sources and during
+\ion{H}{i} reionization.  At $z\simeq 5$ our (extrapolated) AGN number
+densities suggest an average distance of $\approx 70$\,cMpc between
+$M_{1450}<-21$ AGN (Figure~\ref{fig:rhoqso}), which is comparable to
+the mean free path \citep[$83\pm 10$\,cMpc,][]{2014MNRAS.445.1745W}.
+Consequently, if only $M_{1450}<-21$ AGN contribute to the emissivity
+then the UV radiation field at $z\simeq 5$ must fluctuate.  If the QLF
+reaches to fainter magnitudes, or if star-forming galaxies contribute
+to the emissivity, the UV background remains uniform to higher
+redshifts, and the assumptions of standard UV background synthesis
+models remain valid.
+
+The red and blue curves in Figure~\ref{fig:gammapi} show the inferred
+AGN \ion{H}{i} photoionization rate as a function of redshift for our
+integration limits $M_{1450}=-18$ and $-21$, respectively. For
+comparison we also plot the predictions of recent UV background
+synthesis models for AGN
+\citep{2012ApJ...746..125H,2015ApJ...813L...8M,2015MNRAS.451L..30K}
+and AGN$+$galaxies \citep{2012ApJ...746..125H,2018arXiv180104931P}, as
+well as inferences from the \ion{H}{i} Ly$\alpha$ forest
+\citep{2011MNRAS.412.1926W,2013MNRAS.436.1023B,2017MNRAS.467.3172G,2018MNRAS.473..560D},
+the Ly$\alpha+\beta$ forest \citep{2018ApJ...855..106D}, and the
+quasar proximity effect \citep{2011MNRAS.412.2543C}.  Where necessary,
+literature values have been rescaled by a few per cent to adjust to
+our cosmology.
+
+Differences in the \ion{H}{i} photoionization rates inferred from UV
+background synthesis models mostly arise from obvious differences in
+the emissivities of AGN and galaxies, but also due to differences in
+the parametrization of the IGM and the AGN SED.
 
@@
 
-Similar continuity arguments let us scrutinize the value of several photometrically selected AGN samples
-in determinations of the luminosity function. Our analysis has revealed systematic errors in the survey
-selection functions caused by their fixed and simplified assumptions, i.e.\ regarding the parameterisation
-of the IGM and the AGN SED, and the treatment of photometric errors at the survey magnitude limit.
-Several of these systematic errors are easily identified from artificial faint-end drops of the luminosity function
-(Figure~\ref{fig:mosaic}), an apparently zero accessible volume for discovered AGN,
-or a mismatch between the observed and the simulated AGN color distribution. 
-In large samples the precision of the AGN luminosity function is limited by unaccounted systematic errors
-in the survey selection functions, which lead to (i) unphysical variations in the luminosity function parameters
-(i.e.\ for BOSS in Figure~\ref{fig:evoln}) and (ii) inter-survey systematics in combined samples that are further
-amplified by heterogeneous selection function parameter choices amongst the surveys.
-
-With only partially credible data it is challenging to describe the redshift evolution of the AGN luminosity function
-with a viable parametric model. We have developed three such models (Figure~\ref{fig:evoln_global}),
-finding that our fourteen-parameter Model 1 describes the redshift evolution of the luminosity function rather well.
-However, this model prefers a break in the faint-end slope at $z\simeq 3.5$, which causes an unphysical
-discontinuity in the cumulative AGN number density (Figure~\ref{fig:rhoqso}). Our other two models do not have
-these features, but they do not match the measured faint-end slope at $z>4$ as well as Model 1 does.
-%GW: One shall not extrapolate, so divergence is not a real problem
-%The integrated quasar number density diverges at high redshifts in all three models.
-
-With our determinations of the luminosity function we have revisited the contribution of AGN to reionization and the UV background.
-We have made the first determinations of the AGN 912\,\AA\ emissivity with homogeneous faint-end limits at all redshifts,
-whose statistical uncertainties have been properly calculated from the posterior distributions of the luminosity function
-(Figure~\ref{fig:e912_2}). Our parametric fits yield a peak in the 912\,\AA\ emissivity at $z\approx 2.4$, with a decline
-by $\simeq 2$ orders of magnitude to $z\simeq 0$ and $z\simeq 7$, respectively. At $z>4$ our determined emissivities
-are lower by a factor 2--10 than recently claimed by \citet{2015AA...578A..83G}. At the same time, the 912\,\AA\ emissivity
-of $M_{1450}<-18$ AGN exceeds the model considered by \citet{2012ApJ...746..125H} by a factor $>2$ at $z>3$,
-suggesting a somewhat higher contribution of AGN to the high-$z$ UV background if faint AGN have unit escape fractions
-of ionizing photons.
-
-Having derived the AGN \ion{H}{i} photoionization rate by filtering the \ion{H}{i}-ionizing AGN emissivity through
-the IGM \ion{H}{i} column density distribution, we find that while at $z=2$--3 $M_{1450}<-18$ AGN are almost sufficient
-to explain measurements from the Ly$\alpha$ forest, additional UV sources are required at higher redshifts
-(Figure~\ref{fig:gammapi}). Boldly extrapolating the \ion{H}{i} column density distribution to $z=6$, we estimate that
-$M_{1450}<-18$ AGN contribute to the \ion{H}{i} photoionization rate only at the $\sim 5$ per cent level.
-This indicates a minor contribution of such AGN to \ion{H}{i} reionization.
-At $z<0.5$ $M_{1450}<-18$ AGN fall short by a factor of $\sim 2$ to explain UV background measurements
-(Figure~\ref{fig:puc}), but we hesitate to claim a `photon underproduction crisis' \citep{2014ApJ...789L..32K},
-because (i) the apparent tension may be alleviated by known $-18\la M_{1450}\la -14$ AGN at these redshifts
-\citep{2009A&A...507..781S} albeit their Lyman continuum escape fraction is unknown,
-and (ii) current UV background synthesis models do not account for the large uncertainty in the low-redshift
-column density distribution of (partial) \ion{H}{i} Lyman limit systems \citep{2011ApJ...736...42R,2017ApJ...849..106S}. 
-Helium reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$ AGN (Figure~\ref{fig:qhe}),
-but should be delayed by \ion{He}{ii} Lyman limit systems \citep{2009MNRAS.395..736B, 2017ApJ...851...50M},
-requiring further modelling and detailed numerical simulations of the \ion{He}{ii} reionization process.
-
-There are several promising paths forward in the characterization of the AGN luminosity function,
-some of which may substantially advance on current UV-optical broadband color-selected samples that have
-dominated the field for the past 20 years. These include, but are not limited to, comprehensive surveys for
-faint high-$z$ quasars selected by broadband photometry \citep{2016ApJ...828...26M,2017ApJ...839...27W}
-or variability \citep{2017MNRAS.464.1693H}, infrared-selected highly complete surveys at $z\sim 3$
-\citep{2017ApJ...851...13S,2018AJ....155..110Y},
-multi-band narrow-band surveys targeting AGN at all epochs \citep{2014arXiv1403.5237B},
-slitless spectroscopic surveys with upcoming space telescopes \citep{2011arXiv1110.3193L, 2013arXiv1305.5422S},
-and next-generation X-ray surveys \citep[e.g.][]{2013A&A...558A..89K}. However, we caution that future progress
-based on massive surveys requires a detailed quantification of their selection functions and the incorporation
-of systematic errors into AGN luminosity function measurements, in a similar manner to recent surveys for
-lensed high-redshift galaxies that are limited by the accuracy of the lensing mass models
-\citep{2017ApJ...843..129B,2018ApJ...854...73I,2018arXiv180309747A}.
-For a better characterization of the AGN contribution to the UV background one will need to
-(i) perform spectroscopic surveys for faint AGN at all redshifts and determine their characteristic UV SED,
-(ii) carefully assess the impact of the host galaxy on the survey selection and the ionizing power,
-and (iii) measure precisely the amplitude and shape of the column density distribution of (partial)
-\ion{H}{i} Lyman limit systems to inform UV background synthesis models at $z<2$ and $z>4$.
+Similar continuity arguments let us scrutinize the value of several
+photometrically-selected AGN samples in determinations of the
+luminosity function.  Our analysis has revealed systematic errors in
+the survey selection functions caused by their fixed and simplified
+assumptions, i.e.\ regarding the parameterisation of the IGM and the
+AGN SED, and the treatment of photometric errors at the survey
+magnitude limit.  Several of these systematic errors are easily
+identified from artificial faint-end drops of the luminosity function
+(Figure~\ref{fig:mosaic}), an apparently zero accessible volume for
+discovered AGN, or a mismatch between the observed and the simulated
+AGN color distribution.  In large samples the precision of the AGN
+luminosity function is limited by unaccounted systematic errors in the
+survey selection functions, which lead to (i) unphysical variations in
+the luminosity function parameters (i.e.\ for BOSS in
+Figure~\ref{fig:evoln}) and (ii) inter-survey systematics in combined
+samples that are further amplified by heterogeneous selection function
+parameter choices amongst the surveys.
+
+With only partially credible data it is challenging to describe the
+redshift evolution of the AGN luminosity function with a viable
+parametric model.  We have developed three such models
+(Figure~\ref{fig:evoln_global}), finding that our fourteen-parameter
+Model 1 describes the redshift evolution of the luminosity function
+rather well.  However, this model prefers a break in the faint-end
+slope at $z\simeq 3.5$, which causes an unphysical discontinuity in
+the cumulative AGN number density (Figure~\ref{fig:rhoqso}).  Our
+other two models do not have these features, but they do not match the
+measured faint-end slope at $z>4$ as well as Model 1 does.
+
+With our determinations of the luminosity function we have revisited
+the question of the contribution of AGN to reionization and the UV
+background.  We have made the first determinations of the AGN
+912\,\AA\ emissivity with homogeneous faint-end limits at all
+redshifts, whose statistical uncertainties have been properly
+calculated from the posterior distributions of the luminosity function
+(Figure~\ref{fig:e912_2}). Our parametric fits yield a peak in the
+912\,\AA\ emissivity at $z\approx 2.4$, with a decline by $\simeq 2$
+orders of magnitude to $z\simeq 0$ and $z\simeq 7$, respectively. At
+$z>4$ our determined emissivities are lower by a factor 2--10 than
+recently claimed by \citet{2015AA...578A..83G}. At the same time, the
+912\,\AA\ emissivity of $M_{1450}<-18$ AGN exceeds the model
+considered by \citet{2012ApJ...746..125H} by a factor $>2$ at $z>3$,
+suggesting a somewhat higher contribution of AGN to the high-$z$ UV
+background if faint AGN have unit escape fractions of ionizing
+photons.
+
+Having derived the AGN \ion{H}{i} photoionization rate by filtering
+the \ion{H}{i}-ionizing AGN emissivity through the IGM \ion{H}{i}
+column density distribution, we find that while at $z=2$--$3$
+$M_{1450}<-18$ AGN are almost sufficient to explain measurements from
+the Ly$\alpha$ forest, additional UV sources are required at higher
+redshifts (Figure~\ref{fig:gammapi}).  Boldly extrapolating the
+\ion{H}{i} column density distribution to $z=6$, we estimate that
+$M_{1450}<-18$ AGN contribute to the \ion{H}{i} photoionization rate
+only at the $\sim 5$ per cent level.  This indicates a minor
+contribution of such AGN to \ion{H}{i} reionization.  At $z<0.5$
+$M_{1450}<-18$ AGN fall short by a factor of $\sim 2$ to explain UV
+background measurements (Figure~\ref{fig:puc}), but we hesitate to
+claim a `photon underproduction crisis' \citep{2014ApJ...789L..32K},
+because (a) the apparent tension may be alleviated either by harder
+extreme-UV SEDs in faint ($M_{1450}>-23$) AGN
+\citep{2004ApJ...615..135S} or by known $-18\la M_{1450}\la -14$ AGN
+at these redshifts \citep{2009A&A...507..781S} albeit their Lyman
+continuum escape fraction is unknown, and (b) current UV background
+synthesis models do not account for the large uncertainty in the
+low-redshift column density distribution of (partial) \ion{H}{i} Lyman
+limit systems \citep{2011ApJ...736...42R,2017ApJ...849..106S}.  Helium
+reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$ AGN
+(Figure~\ref{fig:qhe}), but should be delayed by \ion{He}{ii} Lyman
+limit systems \citep{2009MNRAS.395..736B, 2017ApJ...851...50M},
+requiring further modelling and detailed numerical simulations of the
+\ion{He}{ii} reionization process.
+
+There are several promising paths forward in the characterization of
+the AGN luminosity function, some of which may substantially advance
+on current UV-optical broadband color-selected samples that have
+dominated the field for the past 20 years.  These include, but are not
+limited to, comprehensive surveys for faint high-$z$ quasars selected
+by broadband photometry \citep{2016ApJ...828...26M,
+  2017ApJ...839...27W} or variability \citep{2017MNRAS.464.1693H},
+infrared-selected highly complete surveys at $z\sim 3$
+\citep{2017ApJ...851...13S, 2018AJ....155..110Y}, multi-band
+narrow-band surveys targeting AGN at all epochs
+\citep{2014arXiv1403.5237B}, slitless spectroscopic surveys with
+upcoming space telescopes \citep{2011arXiv1110.3193L,
+  2013arXiv1305.5422S}, and next-generation X-ray surveys
+\citep[e.g.][]{2013A&A...558A..89K}. However, we caution that future
+progress based on massive surveys requires a detailed quantification
+of their selection functions and the incorporation of systematic
+errors into AGN luminosity function measurements, in a similar manner
+to recent surveys for lensed high-redshift galaxies that are limited
+by the accuracy of the lensing mass models \citep{2017ApJ...843..129B,
+  2018ApJ...854...73I, 2018arXiv180309747A}.  For a better
+characterization of the AGN contribution to the UV background one will
+need to (a) perform spectroscopic surveys for faint AGN at all
+redshifts and determine their characteristic UV SED, (b) carefully
+assess the impact of the host galaxy on the survey selection and the
+ionizing power, and (c) measure precisely the amplitude and shape of
+the column density distribution of (partial) \ion{H}{i} Lyman limit
+systems to inform UV background synthesis models at $z<2$ and $z>4$.
 
 \textbf{A short final paragraph on Hopkins here...}
-
-%% This is the previous version of this section, now changed by GW
-%We have presented an analysis of the evolution of the UV luminosity
-%function of AGN from redshift $z=0$ to $7.5$ using a combined sample
-%of close to 85,000 colour-selected AGN from 12 data sets, homogenized
-%with respect to the assumed cosmology, intrinsic AGN spectrum, and the
-%magnitude system.  AGN from 11 of these 12 samples have reported
-%spectroscopic redshifts, and all but two AGN have known completeness
-%estimates.  These data span magnitudes down to $M_{1450}=-22$ at high
-%redshifts ($z\gtrsim 3.5$).
-
-%% JFH Make some figure references below to remind the reader of where these
-%% results are. Also some people just jump to conclusions so they need to know where to look. 
-%We find that the UV luminosity function of AGN prefers a double power
-%law description at all redshifts considered in this study, except
-%possibly at very high redshifts ($z\sim 6$) where a single power law
-%seems to be preferred.  The behaviour of the luminosity function at
-%lower redshifts ($z=4$--$5.5$) suggests that this single power law at
-%$z\sim 6$ can be interpreted as the faint end of the double power law
-%with a break at $M_*=-29$.  The break magnitude $M_*$ of the double
-%power law luminosity function shows a steep brightening towards high
-%redshifts.  The break evolves from $M_*<-25$ at $z\sim 1$ to $M_*\sim
-%-29$ at $z\sim 6$.  Correspondingly, the amplitude $\phi_*$ of the
-%luminosity function drops rapidly towards high redshifts from
-%$\phi_*\sim 10^{-6}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 1$ to $\phi_*<
-%10^{-10}$~mag$^{-1}$cMpc$^{-3}$ at $z\sim 6$.  The faint-end slope
-%$\beta$ becomes increasingly negative towards high redshifts,
-%resulting in the a steepening of the luminosity function.  The
-%faint-end slope is $\beta\sim -1.8$ at $z\sim 1$ and steepens to
-%$\beta\sim-2.5$ at $z\sim 6$.  The bright-end slope $\alpha$ also
-%shows moderate steepening towards high redshifts.  However, the
-%constraints on $\alpha$ are weak, particularly at the high redshift
-%because of the bright break luminosity.
-
-%% JFH Figure references here as well. 
-%An important finding of this work is that there are severe systematic
-%errors in observed luminosity function at certain redshifts.  We find
-%that the most significant systematic bias is at redshift $z\sim 3$ in
-%the BOSS sample of quasars.  There is also some evidence of a
-%systematic bias in the lowest redshifts $z\lesssim 0.5$.  At $z<2.2$
-%there is some indication of a systematic error in completeness
-%estimates at the faintest magnitudes $M_{1450}\sim -19$.  Systematic
-%errors make it harder to construct simple empirical models to describe
-%the luminosity function evolution.  We develop three such models in
-%this paper.  We find that a fourteen-parameter model (Model 1)
-%describes the redshift evolution of the luminosity function rather
-%well.  However, this model prefers a very rapid evolution in the
-%faint-end slope at $z=3.5$, which is probably unphysical.  Our other
-%models (Models 2 and 3) do not have this feature, but these models do
-%not fit the data as well as Model 1 at $z=4$--$6$.  The integrated
-%quasar number density diverges at high redshifts in all three models.
-
-%In spite of the rapid steepening of the faint end of the luminosity
-%function at high redshifts, our derived hydrogen-ionizing emissivity
-%from AGN is lower that recent determinations from the literature
-%\citep{2015AA...578A..83G}.  This is because the bright break
-%luminosities reduce the contribution of intermediate-brightness AGN to
-%the LyC emissivity.  We find that the LyC emissivity peaks at $z\sim
-%2$.  We derive the average hydrogen photoionization rate by filtering
-%the hydrogen-ionizing emissivity through the intergalactic \HI\ column
-%density distribution.  We find that the HI photoionization rate is
-%lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
-%Our hydrogen photoionization rate estimates are also considerably
-%lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
-%This indicates that hydrogen reionization is unlikely to have caused
-%by AGN alone.  Extrapolating the \HI\ column density distribution
-%function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
-%are assumed to supply hydrogen-ionizing photons with a unit escape
-%fraction, the resultant photoionization rate is only about 10\% of
-%what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
-%we find that the hydrogen photoionization rate is about a factor of
-%two higher than the estimate of \citet{2007ApJ...654..731H} and
-%\citet{2012ApJ...746..125H}.  When compared with the recent analysis
-%of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
-%alleviate the photon underproduction crisis
-%\citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
-%at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
-%integrated down to $M_{1450}=-21$ and $-18$, respectively.
-
-%These results will be made more robust with new data from deep
-%large-area surveys to discover faint quasars at high redshifts, such
-%as the Subaru High-z Exploration of Low-Luminosity Quasars (SHELLQs)
-%project \citep{2016ApJ...828...26M} and the VISTA Extragalactic
-%Infrared Legacy Survey (VEILS; \citealt{2017MNRAS.464.1693H}),
-%followed by the Wide Field Infrared Survey Telescope (WFIRST;
-%\citealt{2013arXiv1305.5422S}) and Euclid \citep{2011arXiv1110.3193L}.
-%This study highlights the need for a better understanding of
-%luminosity function systematics.  In particular, at $z>4$, it seems
-%important to include extended objects at faint magnitudes that could
-%be impacted by host galaxy light, take follow-up spectroscopy to
-%confirm a fraction of these as high-redshift broad-line AGN, and
-%carefully assess host galaxy contamination.
 

### 2018-07-12 Paper/paper.tex
Update text

@@
 \subsection{Photon underproduction at $z=0$?}
-% Kollmeier number of ~10 times higher than HM12 in figure.
-
-%% JFH I disagree with your approach here. It is not interesting to simply extrapolate your z > 0.6 to these
-%% redshifts in my opinion, when you have the ability to fit them or at least to show the binned fits if you cannot
-%% get a global model to work. Why is it interesting to write an entire section on an extrapolation?
-
-\textbf{Comments from GW:\\
-1.
-State again that we need to use the emissivity fit due to the redshift effects.
-Extrapolated emissivity agrees well with our direct estimates (open symbols in emissivity plot) and with other LFs (Schulze)\\
-2. Section needs revision to account for SED change in Fig. 10.\\
-3. We need to be clear whether we are plotting Gamma as is, or whether we are recalculating using your code but other peoples' emissivities.\\
-4.
-We are comparable to HM12, but HM12 considers all AGN.
-We are higher if we consider fainter AGN.
-Given that we miss a factor of 2 to get the forest measurements, we should give a number how faint we need to go.\\
-5.
-Gamma depends on $f(N,z)$.
-Shull doesn't match the measured $f(N,z)$, but Gaikwad and Kollmeier do.
-Gaikwad also estimates the uncertainty in Gamma from the assumed $f(N,z)$.
-To claim any PUC, one has to run UVB synthesis models with a realistic $f(N,z)$ accounting large uncertainty in the range for LLSs (this is hard at low z due to the low number density and need for space-based surveys).
-Shull et al.
-2017 present results from a survey of low-z partial LLSs (their Fig.
-11).
-If the HM12 $f(N,z)$ is inconsistent with the measurements, Gamma won't be right even if the emissivity is right.
-Only Gaikwad investigates this a bit.\\
-6.
-Discuss deficit of Gamma:  Factor ~2 deficit for -18.
-Explanations: 1.
-Changes in limiting magnitude, and spectral index (put numbers: Scott index for -23 no deficit for -18 limit, Scott index for all QSOs: no deficit for -21, fainter AGN: insignificant increase at limit -14 covered by Schulze due to shallow faint-end slope).
-2.
-Galaxies?
-Cite low-z leakers (Izotov), but rare objects.
-}
 
@@
 rate due to AGN in our model for luminosity function integration
-limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that this
-photoionization rate is derived by fitting the model from
+limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that we
+use the 912\,\AA\ emissivity from Equation~(\ref{eqn:e912_18}) and
+(\ref{eqn:e912_21}), which are derived by fitting the model from
 Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
@@
 used in calculating the photoionization rate is an extrapolation at
-$z<0.6$.  However, it is interesting to note that even if we disregard
-the $z<0.6$ data due to systematic errors, the extrapolated
+$z<0.6$.  However, it is interesting to note that the extrapolated
 emissivities at these redshifts are consistent with the emissivities
-calculated from our luminosity function fits to these data for either
-of our chosen integration limits.  This can be seen in
-Figure~\ref{fig:e912_2}.  We find that the low-redshift
-\HI\ photoionization rate in our model is higher than that in the
-\citet{2012ApJ...746..125H} UVB model by a factor of 1.2 for
-$M_{1450}<-21$ and a factor of 2 for $M_{1450}<-18$.  The
-photoionization rate obtained when the faint AGN ($M_{1450}<-18$) are
-included is consistent with a variety of recent estimates.  This rate
-is in reasonable agreement with the photoionization rate found by
-\citet{2017MNRAS.467.3172G}, who found that this photoionisation rate
-is sufficient to explain the \HI\ column density distribution measured
-by \citet{2016ApJ...817..111D}, thus alleviating the photon
-underproduction problem without requiring additional contribution of
-hydrogen-ionizing photons from galaxies.  At $z<0.5$, this
-photoionization rate evolution in our model appears consistent also
-with that derived by \citet{2015MNRAS.451L..30K} using the quasar
+calculated from our luminosity function fits to the $z<0.6$ data for
+either of our chosen integration limits.  This can be seen in
+Figure~\ref{fig:e912_2}.  At $z\sim 0$, the comoving
+912\,\AA\ emissivity in our model is lower by almost a factor of 2
+than that derived from the luminosity function inferred at this
+redshift by \citet{2009A&A...507..781S} for the $M_{1450}<-18$ case.
+For the $M_{1450}<-21$ integration, our comoving emissivity is higher
+than the emissivity in the model of \citet{2009A&A...507..781S} by
+about 50\%.  This results from the very faint $M_*$ ($\sim -19$) and
+steep faint-end slope ($\beta=-2$) obtained by
+\citet{2009A&A...507..781S}.  (See Appendix~\ref{sec:qlfliterature}.)
+We use a spectral slope of $\alpha=-1.7$ for
+$\lambda<912$\,\AA\ (Equation~\ref{eqn:sed}).
+
+We find that the low-redshift \HI\ photoionization rate in our model
+is approximately equal to that that in the \citet{2012ApJ...746..125H}
+UVB model for both of our integration limits, as shown in
+Figure~\ref{fig:puc}.  At $z\sim 0$, the photoionisation rate for our
+$M_{1450}<-21$ integration is lower than \citet{2012ApJ...746..125H}
+photoionisation rate by about 10\%.  For the $M_{1450}<-18$ case, the
+photoionisation rate is higher than that in the
+\citet{2012ApJ...746..125H} model by about 10\%.  These differences
+are small compared to the factor of 2 to 3 differences that we find
+between our model and several recent estimates.  At $z=0.1$, this rate
+is smaller by a factor of 2 than the photoionization rate derived by
+\citet{2017MNRAS.467.3172G} from the \HI\ column density distribution
+measurements of \citet{2016ApJ...817..111D}.  At $z<0.5$, this
+photoionization rate evolution in our model appears lower than also
+the rate derived by \citet{2015MNRAS.451L..30K} using the quasar
 luminosity function measurements of \citet{2009MNRAS.392...19C} and
-\citet{2013A&A...551A..29P}, although the evolution is somewhat
-shallower in our model at $z>0.5$.  The model of
-\citet{2015ApJ...813L...8M} also agrees with our $M_{1450}<-18$
+\citet{2013A&A...551A..29P}.  The model of \citet{2015ApJ...813L...8M}
+also results in a higher ionisation rate than our $M_{1450}<-18$
 inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
@@
 hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
-seen in Figure~\ref{fig:puc}, this photoionization rate agrees with
-our model at $z\sim 0$ for $M_{1450}<-18$, although it evolves
-somewhat more rapidly at higher redshifts.  The photoionization rate
-estimate by \citet{2017MNRAS.467.4802F} from the H$\alpha$ surface
-brightness of a $z\sim 0$ galaxy observed by VLT/MUSE is somewhat
-higher than even our $M_{1450}<-18$ determination.  However, it is
-possible that the \citet{2017MNRAS.467.4802F} estimate is an upper
-limit, as the contribution of local sources to the photoionization
-rate is neglected in their modelling.  The requirement of an enhanced
-photoionization rate at $z\sim 0$ relative to
-\citet{2012ApJ...746..125H} UVB model is also confirmed by the
+seen in Figure~\ref{fig:puc}, this photoionization rate is in closer
+agreement with the \citet{2015ApJ...813L...8M} model.  The
+photoionization rate estimate by \citet{2017MNRAS.467.4802F} from the
+H$\alpha$ surface brightness of a $z\sim 0$ galaxy observed by
+VLT/MUSE is somewhat higher than most other models shown in
+Figure~\ref{fig:puc}.  However, it is possible that the
+\citet{2017MNRAS.467.4802F} estimate is an upper limit, as the
+contribution of local sources to the photoionization rate is neglected
+in their modelling.  The requirement of an enhanced photoionization
+rate at $z\sim 0$ relative to our inference is also confirmed by the
 simulations presented by \citet{2017MNRAS.467L..86V},
@@
 
+Before considering the deficit in the photoionisation rate obtained
+from AGN at low redshifts relative to measurements from the
+\lya\ forest as a photon underproduction crisis, it is worthwhile to
+recall various assumptions entering our derivation.  With a spectral
+index of $-1.7$, our ionisation rate estimate falls short of the
+\lya\ forest measurements by a factor of $\sim 2$ with an integration
+limit of $M_{1450}=-18$ on the luminosity function.
+\citet{2015ApJ...813L...8M} implicitly assume an integration limit of
+$M_{1450}=-14$ at $z\sim 0$ (see also \citealt{2015MNRAS.451L..30K,
+  2018arXiv180104931P}) as this limit corresponds to $M_*+5$ for the
+\citet{2009A&A...507..781S} luminosity function measurement.  It is
+unclear if the assumption of unit LyC escape fraction is valid for
+such faint AGN, but we find that even with this extremely faint
+integration limit, the photoionisation rate deficit is reduced by only
+about 25\% for a spectral index of $-1.7$.  While this result does not
+change significantly if we assume a spectral index of $-1.4$ as
+suggested by \citet{2014ApJ...794...75S}, assuming a much harder
+spectrum with a spectral index of $-0.56$ \citep{2004ApJ...615..135S}
+for faint ($M_{1450}>-23$) AGN completely alleviates the deficit for
+an integration limit of $M_{1450}=-18$.  One should also note that our
+ionization rate model ignores the large uncertainties in the
+\HI\ column density distribution at the Lyman limit
+\citep{2011ApJ...736...42R, 2017ApJ...849..106S, 2017MNRAS.466..838G}.  Alternatively, it
+may be possible to balance the ionization rate deficit by the
+contribution from low-redshift LyC-leaking galaxies
+\citep{2016Natur.529..178I, 2018MNRAS.474.4514I, 2018MNRAS.478.4851I}
+
 \subsection{Helium reionization}
@@
   \end{center}
-  \caption{
-  Redshift evolution of the volume-averaged \ion{He}{iii} fraction $Q_\ion{He}{iii}$
-  considering AGN with $M_{1450}<-21$ (blue) and $M_{1450}<-18$ (red)
-  in our calculation of the emission rate of ionizing photons.
-  The shaded regions show the one-sigma (68.26\%) confidence interval
-  resulting from the uncertainty in the emissivity.
-  The other curves show previous determinations of $Q_\ion{He}{iii}\left(z\right)$
-  based on Equation~\eqref{eqn:qHedot}
-  \citep{2012ApJ...746..125H, 2015ApJ...813L...8M, 2016ApJ...828...90L, 2018arXiv180104931P}
-  and on cosmological radiative transfer simulations of quasar-driven \ion{He}{ii} reionization
-  \citep{2009ApJ...694..842M, 2014MNRAS.445.4186C}.
-  Note that Equation~\eqref{eqn:qHedot} ignores the presence of \ion{He}{ii}
-  Lyman limit systems impeding reionization at  $Q_\ion{He}{iii}\rightarrow 1$,
-  requiring further analytic modelling \citep{2017ApJ...851...50M} or
-  numerical simulation \citep{2018arXiv180104931P}.
+  \caption{ Redshift evolution of the volume-averaged \ion{He}{iii}
+    fraction $Q_\ion{He}{iii}$ considering AGN with $M_{1450}<-21$
+    (blue) and $M_{1450}<-18$ (red) in our calculation of the emission
+    rate of ionizing photons.  The shaded regions show the one-sigma
+    (68.26\%) confidence interval resulting from the uncertainty in
+    the emissivity.  The other curves show previous determinations of
+    $Q_\ion{He}{iii}\left(z\right)$ based on
+    Equation~\eqref{eqn:qHedot} \citep{2012ApJ...746..125H,
+      2015ApJ...813L...8M, 2016ApJ...828...90L, 2018arXiv180104931P}
+    and on cosmological radiative transfer simulations of
+    quasar-driven \ion{He}{ii} reionization
+    \citep{2009ApJ...694..842M, 2014MNRAS.445.4186C}.  Note that
+    Equation~\eqref{eqn:qHedot} ignores the presence of \ion{He}{ii}
+    Lyman limit systems impeding reionization at
+    $Q_\ion{He}{iii}\rightarrow 1$, requiring further analytic
+    modelling \citep{2017ApJ...851...50M} or numerical simulation
+    \citep{2018arXiv180104931P}.
   \label{fig:qhe}}  
@@
 \end{equation}
-where $\dot n_\mathrm{ion,4}$ is the emission rate of $\ge 4$\,Ry photons per unit proper volume,
-$\langle n_\mathrm{He}\rangle$ is the average proper helium number density,
-and $\langle t_\mathrm{rec,He}\rangle$ is the average recombination time scale for \ion{He}{iii}.
-%% GW simplified the following. All of that is a simple rescaling of the 912A emissivity
-%We obtain the evolution of $\dot n_{\rm ion,4}$ for AGN with $M_\mathrm{1450}<-21$ and
-%$M_\mathrm{1450}<-18$ by integrating the contribution of double power
-%law luminosity function obtained in distinct redshifts bins and
-%fitting Equation~(\ref{eqn:e912fit}) to the resultant \HeII-ionizing emissivities.
-%We extrapolate the resultant fit to $z>7$, although the
-%contribution from this extrapolated emissivity to \HeII-reionization is small.
-With our quasar emissivity model from Section~\ref{sec:e912} the emission rate
-can be written as
-%\begin{eqnarray}\nonumber
-%\dot n_\mathrm{ion,4}\left(z\right)&=&\left(1+z\right)^3\int_{\nu_{228}}^{\infty}\mathrm{d}%\nu\frac{\epsilon_\nu\left(\nu,z\right)}{h\nu}\\
-%&=&-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
-%\end{eqnarray}
+where $\dot n_\mathrm{ion,4}$ is the emission rate of $\ge 4$\,Ry
+photons per unit proper volume, $\langle n_\mathrm{He}\rangle$ is the
+average proper helium number density, and $\langle
+t_\mathrm{rec,He}\rangle$ is the average recombination time scale for
+\ion{He}{iii}.  With our quasar emissivity model from
+Section~\ref{sec:e912} the emission rate can be written as
 \begin{equation}
-\dot n_\mathrm{ion,4}\left(z\right)=-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
+\dot
+n_\mathrm{ion,4}\left(z\right)=-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
 \end{equation}
@@
 where $\langle n_\mathrm{H}\rangle=1.881\times
-10^{-7}(1+z)^3$~cm$^{-3}$ is the average proper hydrogen number density,
-$\alpha_\mathrm{B}$ is the Case~B \ion{He}{iii} recombination coefficient \citep{1997MNRAS.292...27H},
-and $\chi=0.079$ is the cosmic number fraction of helium for a cosmic
-helium mass fraction of $Y_\mathrm{He}=0.24$. 
-We assume that the clumping factor $C$ for helium is the same as for hydrogen,
-for which \citet{2012ApJ...747..100S} obtained
+10^{-7}(1+z)^3$~cm$^{-3}$ is the average proper hydrogen number
+density, $\alpha_\mathrm{B}$ is the Case~B \ion{He}{iii} recombination
+coefficient \citep{1997MNRAS.292...27H}, and $\chi=0.079$ is the
+cosmic number fraction of helium for a cosmic helium mass fraction of
+$Y_\mathrm{He}=0.24$.  We assume that the clumping factor $C$ for
+helium is the same as for hydrogen, for which
+\citet{2012ApJ...747..100S} obtained
 \begin{equation}
@@
 Equation~\eqref{eqn:qHedot} neglects \ion{He}{ii} Lyman limit systems
-that considerably delay the end of \ion{He}{ii} reionization \citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.
-In the absence of these self-shielded systems, $Q_\ion{He}{iii}$ can continue
-to increase beyond unity and the mean free path of \ion{He}{ii}-ionizing photons diverges.
-We set $Q_\ion{He}{iii}=1$ when this happens.
-This can be corrected by accounting for the \ion{He}{ii} column
-density distribution and filtering the \ion{He}{ii}-ionizing radiation
-field through it. Unfortunately, the \ion{He}{ii} column density
-distribution is itself uncertain, as it depends on the
-relative contributions of quasars and galaxies to the UV background \citep[e.g.][]{2012ApJ...746..125H,2018arXiv180104931P}. 
-We consider the simplified treatment of $Q_\ion{He}{iii}$ accurate enough for the purpose
-of this work, while noting that the redshift of \ion{He}{ii} reionization is
-likely overestimated in any such model.
-
-The resultant \ion{He}{ii} reionization histories are shown in Figure~\ref{fig:qhe}
-for our two considered magnitude limits, with the shaded regions showing the one-sigma
-uncertainty in $Q_\ion{He}{iii}$ resulting from the uncertainty in the quasar emissivity alone,
-i.e.\ using a fixed quasar spectral energy distribution and a fixed redshift evolution of the clumping factor.
-In our model, \ion{He}{ii} reionization starts around the earliest quasars at $z>6$ and finishes at
-$3.2\la z\la 3.5$ depending on the extent of the faint-end QLF.
-Considering the limitations of the modelling discussed above, both \ion{He}{ii} reionization histories
-are consistent with recent \ion{He}{ii} Ly$\alpha$ effective optical depth measurements supporting
-substantial progression of \ion{He}{ii} reionization by $z\simeq 3.4$ \citep{2016ApJ...825..144W},
-and an end of the process at $z\simeq 2.7$ \citep{2011ApJ...733L..24W,2016ApJ...825..144W}
-with the build-up of a quasi-homogeneous \ion{He}{ii}-ionizing background \citep{2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
-
-%% JFH I think these next two paragraphs here needs to be shortened considerably.
-%% You are spending way to to much time and text discussing the literature. 
-%% GW commented the previous version and provided a shorter one
-
-Figure~\ref{fig:qhe} also shows previous solutions of Equation~\eqref{eqn:qHedot}
-with different parameterizations of the quasar emissivity, spectral energy distribution and
-clumping factor \citep{2012ApJ...746..125H,2015ApJ...813L...8M,2016ApJ...828...90L,2018arXiv180104931P},
-as well as the results from cosmological radiative transfer simulations of \ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C}.
-The differences of our results to the ones by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
-mostly result from differences in the adopted quasar emissivity (Figure~\ref{fig:e912_2}).
-The large quasar emissivity adopted by \citet{2015ApJ...813L...8M} results in an early completion of
-\ion{He}{ii} reionization at $z\approx 4$, which is inconsistent with the measured strong \ion{He}{ii} absorption
-at $2.7<z<3$ \citep{2016ApJ...825..144W,2018MNRAS.473.1416M,2018arXiv180104931P}
-if the \ion{He}{ii}-ionizing background is not fluctuating on large scales due to rare clustered and/or short-lived
-quasars that result in a spatially varying mean free path of \ion{He}{ii}-ionizing photons
-\citep{2010ApJ...714..355F,2014MNRAS.440.2406M,2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
-The quasar emissivity considered by \citet{2012ApJ...746..125H} falls below our determinations at the relevant
-redshifts (Figure~\ref{fig:e912_2}), which results in a delayed completion of \ion{He}{ii} reionization at $z\simeq 2.8$.
-
-\citet{2016ApJ...828...90L} varied the parameters of Equation~\eqref{eqn:qHedot} to estimate the uncertainty
-in $Q_\ion{He}{iii}\left(z\right)$, in particular the QLF\footnote{\citet{2016ApJ...828...90L} erroneously varied the
-$z>3.5$ QLF parameters independently, neglecting their covariance and the survey data.},
-shown in Figure~\ref{fig:e912_2}. Considering the limitations of Equation~\eqref{eqn:qHedot},
-\ion{He}{ii} reionization finishes too late ($z\sim 2.5$) in their fiducial model, which is probably due to their
-considered QLFs and varying magnitude limits their emissivity calculations.
-
-\citet{2018arXiv180104931P} adopted a somewhat higher quasar emissivity than \citet{2012ApJ...746..125H}
-that is comparable to our fit for $M_{1450}<-21$ at the redshifts of interest. Instead of their solution to
-Equation~\eqref{eqn:qHedot} we show their results of one-cell simulations with gas at cosmic mean density
-(see Section~3.3 and Appendix~C of \citealt{2018arXiv180104931P} for details).
-In these simulations the \ion{He}{ii} number density is correctly calculated as \ion{He}{ii} is gradually ionized
-by a radiation field resulting from one-dimensional radiative transfer calculations through an inhomogeneous IGM.
-This accounts for \ion{He}{ii} Lyman limit systems in a simple way, resulting in a smooth transition of $Q_\ion{He}{iii}$ to unity.
-
-In Figure~\ref{fig:qhe} we also plot $Q_\ion{He}{iii}\left(z\right)$ from two numerical simulations of quasar-driven
-\ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C} that broadly reproduce the measured
-\ion{He}{ii} effective optical depths \citep{2016ApJ...825..144W}. In these simulations the outputs of $N$-body or
-hydrodynamic simulations are post-processed with radiative transfer around quasars sourced according to a specific model,
-and the effects of \ion{He}{ii} Lyman limit systems are approximately captured with sub-grid filtering methods
-\citep{2009ApJ...694..842M} or with adaptive mesh refinement \citep{2014MNRAS.445.4186C}.
-Their different timing of \ion{He}{ii} reionization is mostly due to the adopted quasar model
-(QLF, spectral energy distribution, quasar lifetime, anisotropic emission, halo mass range) and stochasticity in the
-$z\ga 3.5$ quasar number density in the limited simulation volumes.
-Thus, while current simulations do not reproduce the measured scatter in the \ion{He}{ii} effective optical depths at
-$2.7<z<3.5$ in detail \citep{2016ApJ...825..144W}, this may reflect limitations of the modelling other than the QLF
-\citep{2017MNRAS.468.4691D}. Our $Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with the simulation
-by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii} reionization is accomplished by the $z<5$ quasar population
-evolved assuming pure density or pure luminosity evolution to match the QLF by \citet{2011ApJ...728L..26G} for
-$M_{1450}<-19.5$ \citep[see also][]{2013MNRAS.435.3169C}. Future efforts in numerical modelling of \ion{He}{ii}
-reionization should investigate quasar models which follow the QLF evolution in detail, and which are consistent with
-the measured redshift evolution and scatter of the \ion{He}{ii} effective optical depth, as well as the measured redshift evolution
-of the IGM temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,2014MNRAS.441.1916B,2018MNRAS.474.2871R,2017arXiv171000700H}.
-
-%% Previous version commented by GW
-%In Figure~\ref{fig:qhe}, we also show the reionization histories from
-%other models of \HeII\ reionization in the literature.  Our model
-%curve for $M_\mathrm{1450}<-21$ is closest in agreement to the
-%simulations of \citet{2009ApJ...694..842M} and the analytical model of
-%\citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
-%\HeII-ionizing emissivity of AGN by fitting the functional form in
-%Equation~(\ref{eqn:e912fit}) to the emissivities reported by
-%\citet{2009A&A...507..781S}, \citet{2007A&A...472..443B}, and
-%\citet{2012ApJ...755..169M}.  The resultant emissivity in the model of
-%\citet{2018arXiv180104931P} is similar in shape but higher in
-%amplitude than the emissivity in the \citet{2012ApJ...746..125H}
-%model.  The \HeII-ionizing emissivity of \citet{2018arXiv180104931P}
-%is closer to our inference for $M_\mathrm{1450}<-21$ than the model of
-%\citet{2012ApJ...746..125H}.  (However, note that both these models
-%suffer from inhomogeneous luminosity function integration limits, as
-%the integration limit is set to a fixed fraction of the break
-%luminosity, as discussed above in Section~\ref{sec:e912}.)  A spectral
-%index of $\alpha_\mathrm{EUV}=-1.7$ is assumed.
-%\citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
-%evolving the \HeIII\ ionization fraction in a gas cloud with the mean
-%cosmic baryonic density exposed to the average \HeII-ionizing flux.
-%The ionizing flux is obtained by filtering the ionizing emissivity
-%through an inhomogeneous IGM in which the column density distribution
-%of \HeIII\ is derived from that of \HI\ in a manner similar to
-%\citet{2012ApJ...746..125H}.  As a result, this model incorporates the
-%effect of \HeII\ Lyman-limit systems, and the $Q_\nHeIII$ evolution in
-%this model deviates from our predictions towards the end of
-%reionization, as seen in Figure~\ref{fig:qhe}.  Comparing the
-%emissivity model in the cosmological radiative transfer simulations of
-%\citet{2009ApJ...694..842M} with our models is less straightforward.
-%Quasars are modelled in the simulations of \citet{2009ApJ...694..842M}
-%by relating quasar luminosities and lifetimes to halo masses following
-%the galaxy-merger-induced quasar activity model of
-%\citet{2005ApJ...630..705H}.  The resultant bolometric quasar
-%luminosity functions are somewhat shallower than those of
-%\citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
-%index of $\alpha_\mathrm{EUV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
-%shows that the resultant reionization history in these simulations
-%agrees with our model for $M_\mathrm{1450}<-21$, except towards the
-%end of reionization, where, as before, \HeII\ Lyman-limit systems
-%become important.
-
-%Helium reionization is delayed in the model of
-%\citet{2012ApJ...746..125H} due to their reduced emissivity at $z\sim
-%3$.  In the \citet{2015ApJ...813L...8M} model, a significant
-%\HeII\ fraction is ionized already at $z=6$, and reionization is
-%complete by $z=4.1$ due to the very high emissivity assumed in this
-%model.  In the radiation-hydrodynamic simulations by
-%\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
-%SDSS \citep{2013ApJ...768..105M} and COSMOS
-%\citep{2012ApJ...755..169M} data at $z>3.5$, combined with a model for
-%quasar light curves.  The fiducial \HeII\ reionization history
-%obtained by these authors is shown in Figure~\ref{fig:qhe} along with
-%an estimate of the uncertainty.  Reionization ends considerably later
-%in this model ($z\sim 2.6$).  The \HeII\ reionization history in our
-%model for $M_\mathrm{1450}<-18$ agrees closely with that in the
-%radiative transfer simulations presented by
-%\citet{2014MNRAS.445.4186C}.  The AGN population in these simulations
-%is `turned on' at $z=5$ and evolved assuming a pure luminosity
-%evolution to match the inferred luminosity function of
-%\citet{2011ApJ...728L..26G}.  The somewhat early reionization in the
-%simulations of \citet{2014MNRAS.445.4186C} relative to most other
-%models shown in Figure~\ref{fig:qhe} may be driven by the
-%significantly higher emissivity from AGN with intermediate brightness
-%($M_{1450}\sim -23$) in the model of \citet{2011ApJ...728L..26G}.
-%However, the limited numerical resolution of these simulations may
-%also play a role \citep{2014MNRAS.445.4186C}.
-
-%An important constraint on \HeII\ reionization can be derived from the
-%thermal history of the IGM.  \citet{2018MNRAS.473.1416M} constrained
-%the evolution of the 912\,\AA\ emissivity of AGN by assuming a
-%spectral index of $\alpha_\mathrm{EUV}=-1.57$ and using the
-%measurements of the effective \HeII\ \lya optical depth
-%\citep{2016ApJ...825..144W} and the IGM temperature
-%\citep{2011MNRAS.410.1096B}.  \citet{2018MNRAS.473.1416M} found that
-%although these data favour a reionization history in which \HeII\ is
-%reionized at $z>4$, the 912\,\AA\ emissivity of AGN is nevertheless
-%required to drop rapidly at $z>3$.  This emissivity evolution is much
-%more rapid than that in our model for $M_\mathrm{1450}<-21$, with the
-%caveat that the constraint derived by \citet{2018MNRAS.473.1416M} is
-%model-dependent and assumes a shallower EUV spectrum.  A steeper
-%spectrum with $\alpha_\mathrm{EUV}=-1.8$ was assumed in a recent model
-%by \citet{2018arXiv180109693K}.  The resultant emissivity evolution is
-%consistent with our model for $M_\mathrm{1450}<-21$, although somewhat
-%more rapid at $z>2$.  The AGN luminosity function is derived by
-%combining determinations from various data sets
-%\citep{2015MNRAS.451L..30K}.  An inhomogeneous integration limit of
-%$0.01L_*$ is applied to calculate the emissivity.  \HeII\ reionization
-%ends at $z=2.8$ in the model of \citet{2018arXiv180109693K}.
-%(\citealt{2017MNRAS.471..255K} argued that for their luminosity
-%function model, spectra with $\alpha_\mathrm{EUV}>-1.6$ are unlikely
-%to be consistent with the \HeII\ \lya data.)
-%\citet{2017MNRAS.468.4691D} considered the effect of an AGN-dominated
-%reionization on the \HI\ Ly$\alpha$ opacity at $z>5$,
-%\HeII\ Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the thermal
-%history of the IGM.  These authors found that that any scenario in
-%which reionization of \HeII\ completes at $z>3$ is inconsistent with
-%the measurements of the IGM temperature at $z=4$--$5$.  We leave the
-%analysis of the IGM thermal history implied by our AGN luminosity
-%models for future work.
+that considerably delay the end of \ion{He}{ii} reionization
+\citep{2009MNRAS.395..736B, 2017ApJ...851...50M}.  In the absence of
+these self-shielded systems, $Q_\ion{He}{iii}$ can continue to
+increase beyond unity and the mean free path of \ion{He}{ii}-ionizing
+photons diverges.  We set $Q_\ion{He}{iii}=1$ when this happens.  This
+can be corrected by accounting for the \ion{He}{ii} column density
+distribution and filtering the \ion{He}{ii}-ionizing radiation field
+through it. Unfortunately, the \ion{He}{ii} column density
+distribution is itself uncertain, as it depends on the relative
+contributions of quasars and galaxies to the UV background
+\citep[e.g.][]{2012ApJ...746..125H,2018arXiv180104931P}.  We consider
+the simplified treatment of $Q_\ion{He}{iii}$ accurate enough for the
+purpose of this work, while noting that the redshift of \ion{He}{ii}
+reionization is likely overestimated in any such model.
+
+The resultant \ion{He}{ii} reionization histories are shown in
+Figure~\ref{fig:qhe} for our two considered magnitude limits, with the
+shaded regions showing the one-sigma uncertainty in $Q_\ion{He}{iii}$
+resulting from the uncertainty in the quasar emissivity alone,
+i.e.\ using a fixed quasar spectral energy distribution and a fixed
+redshift evolution of the clumping factor.  In our model, \ion{He}{ii}
+reionization starts around the earliest quasars at $z>6$ and finishes
+at $3.2\la z\la 3.5$ depending on the extent of the faint-end QLF.
+Considering the limitations of the modelling discussed above, both
+\ion{He}{ii} reionization histories are consistent with recent
+\ion{He}{ii} Ly$\alpha$ effective optical depth measurements
+supporting substantial progression of \ion{He}{ii} reionization by
+$z\simeq 3.4$ \citep{2016ApJ...825..144W}, and an end of the process
+at $z\simeq 2.7$ \citep{2011ApJ...733L..24W,2016ApJ...825..144W} with
+the build-up of a quasi-homogeneous \ion{He}{ii}-ionizing background
+\citep{2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
+
+Figure~\ref{fig:qhe} also shows previous solutions of
+Equation~\eqref{eqn:qHedot} with different parameterizations of the
+quasar emissivity, spectral energy distribution and clumping factor
+\citep{2012ApJ...746..125H, 2015ApJ...813L...8M, 2016ApJ...828...90L,
+  2018arXiv180104931P}, as well as the results from cosmological
+radiative transfer simulations of \ion{He}{ii} reionization
+\citep{2009ApJ...694..842M,2014MNRAS.445.4186C}.  The differences of
+our results to the ones by \citet{2012ApJ...746..125H} and
+\citet{2015ApJ...813L...8M} mostly result from differences in the
+adopted quasar emissivity (Figure~\ref{fig:e912_2}).  The large quasar
+emissivity adopted by \citet{2015ApJ...813L...8M} results in an early
+completion of \ion{He}{ii} reionization at $z\approx 4$, which is
+inconsistent with the measured strong \ion{He}{ii} absorption at
+$2.7<z<3$ \citep{2016ApJ...825..144W, 2018MNRAS.473.1416M,
+  2018arXiv180104931P} if the \ion{He}{ii}-ionizing background is not
+fluctuating on large scales due to rare clustered and/or short-lived
+quasars that result in a spatially varying mean free path of
+\ion{He}{ii}-ionizing photons \citep{2010ApJ...714..355F,
+  2014MNRAS.440.2406M, 2014MNRAS.437.1141D, 2017MNRAS.465.2886D}.  The
+quasar emissivity considered by \citet{2012ApJ...746..125H} falls
+below our determinations at the relevant redshifts
+(Figure~\ref{fig:e912_2}), which results in a delayed completion of
+\ion{He}{ii} reionization at $z\simeq 2.8$.
+
+\citet{2016ApJ...828...90L} varied the parameters of
+Equation~\eqref{eqn:qHedot} to estimate the uncertainty in
+$Q_\ion{He}{iii}\left(z\right)$, in particular the
+QLF\footnote{\citet{2016ApJ...828...90L} erroneously varied the
+  $z>3.5$ QLF parameters independently, neglecting their covariance
+  and the survey data.}, shown in Figure~\ref{fig:e912_2}.
+Considering the limitations of Equation~\eqref{eqn:qHedot},
+\ion{He}{ii} reionization finishes too late ($z\sim 2.5$) in their
+fiducial model, which is probably due to their considered QLFs and
+varying magnitude limits their emissivity calculations.
+
+\citet{2018arXiv180104931P} adopted a somewhat higher quasar
+emissivity than \citet{2012ApJ...746..125H} that is comparable to our
+fit for $M_{1450}<-21$ at the redshifts of interest.  Instead of their
+solution to Equation~\eqref{eqn:qHedot} we show their results of
+one-cell simulations with gas at cosmic mean density (see Section~3.3
+and Appendix~C of \citealt{2018arXiv180104931P} for details).  In
+these simulations the \ion{He}{ii} number density is correctly
+calculated as \ion{He}{ii} is gradually ionized by a radiation field
+resulting from one-dimensional radiative transfer calculations through
+an inhomogeneous IGM.  This accounts for \ion{He}{ii} Lyman limit
+systems in a simple way, resulting in a smooth transition of
+$Q_\ion{He}{iii}$ to unity.
+
+In Figure~\ref{fig:qhe} we also plot $Q_\ion{He}{iii}\left(z\right)$
+from two numerical simulations of quasar-driven \ion{He}{ii}
+reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C} that
+broadly reproduce the measured \ion{He}{ii} effective optical depths
+\citep{2016ApJ...825..144W}.  In these simulations the outputs of
+$N$-body or hydrodynamic simulations are post-processed with radiative
+transfer around quasars sourced according to a specific model, and the
+effects of \ion{He}{ii} Lyman limit systems are approximately captured
+with sub-grid filtering methods \citep{2009ApJ...694..842M} or with
+adaptive mesh refinement \citep{2014MNRAS.445.4186C}.  Their different
+timing of \ion{He}{ii} reionization is mostly due to the adopted
+quasar model (QLF, spectral energy distribution, quasar lifetime,
+anisotropic emission, halo mass range) and stochasticity in the $z\ga
+3.5$ quasar number density in the limited simulation volumes.  Thus,
+while current simulations do not reproduce the measured scatter in the
+\ion{He}{ii} effective optical depths at $2.7<z<3.5$ in detail
+\citep{2016ApJ...825..144W}, this may reflect limitations of the
+modelling other than the QLF \citep{2017MNRAS.468.4691D}.  Our
+$Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with
+the simulation by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii}
+reionization is accomplished by the $z<5$ quasar population evolved
+assuming pure density or pure luminosity evolution to match the QLF by
+\citet{2011ApJ...728L..26G} for $M_{1450}<-19.5$ \citep[see
+  also][]{2013MNRAS.435.3169C}.  Future efforts in numerical modelling
+of \ion{He}{ii} reionization should investigate quasar models which
+follow the QLF evolution in detail, and which are consistent with the
+measured redshift evolution and scatter of the \ion{He}{ii} effective
+optical depth, as well as the measured redshift evolution of the IGM
+temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,
+  2014MNRAS.441.1916B, 2018MNRAS.474.2871R, 2017arXiv171000700H}.
 
@@
 low-redshift column density distribution of (partial) \ion{H}{i} Lyman
-limit systems \citep{2011ApJ...736...42R,2017ApJ...849..106S}.  Helium
+limit systems \citep{2011ApJ...736...42R, 2017ApJ...849..106S}.  Helium
 reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$ AGN

### 2018-07-17 Paper/paper.tex
Update

@@
 
+\section{Homogenised Quasar Sample}
+\label{sec:sample}
+
+We started by compiling the samples of recent photometric rest-frame
+UV-optical quasar surveys. The restriction to UV-optical surveys was
+mainly driven by our science goal to characterise the UV luminosity
+function of Type~1 quasars. X-ray-selected samples are less suited for
+this purpose due to spectroscopic incompleteness and the $\sim
+0.4$\,dex scatter in the conversion from X-ray to UV luminosity
+\citep{2010A&A...512A..34L, 2015MNRAS.453.1946G, 2016ApJ...819..154L}
+that contributes significantly to the error budget in the UV
+luminosity function of X-ray-selected samples unless rest-frame UV
+photometry is incorporated \citep{2015AA...578A..83G}.  The individual
+surveys and their main characteristics are listed in
+Table~\ref{tab:samples}.  Figure~\ref{fig:qsos} presents a redshift
+histogram of the contributing surveys.
+
+\subsection{Sample Selection}
+\label{sect:samplesel}
+
+We included surveys based on a set of simple criteria:
+\begin{enumerate}
+\item High spectroscopic completeness of the target sample.
+\item Accurate rest-frame UV-optical CCD photometry.
+\item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
+\item A well-characterised selection function.
+\end{enumerate}
+As a prerequisite for a joint analysis of the QLF we obtained the
+survey selection functions in electronic form, either from the
+publication or by request from the authors. As a reference for future
+surveys we make them electronically available here in modified and
+homogenised form (see Section~\ref{sect:datahom} and
+Appendix~\ref{sec:code}).
+
+Due to their selection criteria and their statistical power specific
+surveys contribute to distinct redshift ranges. At $z<2.2$ we
+considered quasars from the SDSS DR7 quasar catalogue
+\citep{2010AJ....139.2360S} and the 2SLAQ survey catalogue
+\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to the
+48,664 $0.1<z<2.2$ quasars selected with the final SDSS quasar
+selection algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R}
+from a survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We
+adopted the SDSS targeting photometry corrected for Galactic
+extinction \citep{2010AJ....139.2360S}. To limit systematic
+uncertainties in the correction for host galaxy light \citep[detailed
+  in][]{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 9365
+$g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint
+near the North Galactic Pole (NGP, 7027 quasars in $127.7$\,deg$^2$)
+and the South Galactic Pole (SGP, 2338 quasars in
+$64.2$\,deg$^2$). The small sample overlap between SDSS and 2SLAQ (102
+quasars) has negligible impact on the QLF evaluation.
+
+At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
+colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
+\citep{2013ApJ...773...14R} due to several improvements compared to
+previous surveys. First, it covers a similar magnitude range as 2SLAQ
+but with $>20$ times as many quasars. Second, although the SDSS DR7
+sample provides better coverage of the bright end of the QLF at these
+redshifts, its selection function is highly dependent on the assumed
+incidence of (partial) Lyman limit systems in the IGM
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
+selection function considers these improvements, the uncertainty in
+the QLF remains dominated by assumptions in the selection function
+given the large sample size
+\citep{2013ApJ...773...14R}. Variability-selected quasar samples
+circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
+  2016A&A...587A..41P}, but may be affected by (i) single-epoch
+imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
+and (ii) uncertainties in the selection function caused by the limited
+number of known $z\ga 3$ quasars not selected by variability in the
+same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
+
+At $3.7<z<4.7$ we used a combination of SDSS DR7 \citep[1785 uniformly
+  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
+survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
+$z>3.7$ in SDSS limits the impact of systematic uncertainties in the
+\citet{2006AJ....131.2766R} selection function
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
+the results from surveys for faint $z\sim 4$ quasars in the COSMOS
+field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
+systematic errors in their selection functions\footnote{Both studies
+  simulated quasar colours with a mean IGM attenuation curve
+  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
+  continuum absorption, and therefore underpredicts the variance in
+  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
+    2011ApJ...728...23W}. Modelling the colour variance in these
+  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
+  quasars are near the edge of their colour selection region (see
+  their Figure~1), and \citet{2012ApJ...755..169M} require modest
+  attenuation of the $U$ band flux relative to the mid-infrared
+  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
+COSMOS sample have visually estimated photometric redshifts, and the
+spectroscopic subsample reveals that 40 per cent of the visually
+estimated redshifts are biased low
+($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
+unaccounted systematic redshift errors at least partly explain the
+discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
+and \citet{2012ApJ...755..169M}, which justifies our preference for
+the former sample that is 77 per cent spectroscopically complete at
+$R$ magnitudes $<23.5$ \citep{2011ApJ...728L..26G}.
+
+At $4.7\le z<5.5$ we combined several recent surveys, accounting for
+sample overlap and updated selection functions. At the bright end of
+the QLF we used the 99 quasars from the SDSS+WISE survey
+\citep{2016ApJ...829...33Y} that have $M_{1450}\le -26.73$ in our adopted
+cosmology.  For these 99 quasars selected from 14,555\,deg$^2$ we
+adopted the \citet{2016ApJ...829...33Y} selection function.  The
+\citet{2016ApJ...829...33Y} sample partially overlaps with the SDSS
+DR7 sample from \citet{2013ApJ...768..105M}, so to avoid
+double-counting quasars we used the latter sample only at
+$M_{1450}>-26.73$, yielding 103 additional $4.7\le z<5.5$ quasars selected in
+6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection function from
+\citet{2013ApJ...768..105M} that supersedes the one from
+\citet{2006AJ....131.2766R} due to improved bandpass corrections and IGM
+parameterization.  To these two bright-end samples we added the
+faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82
+survey (59 uniformly selected $M_{1450}>-26.73$ $4.7\le z<5.5$ quasars in 235\,deg$^2$)
+and two $4.7\le z<5.5$ quasars from \citet{2011ApJ...728L..26G},
+adopting the respective selection functions.  We did not consider the
+limit on the $z\sim 5$ QLF by \citet{2012ApJ...756..160I} due to
+systematic errors in their selection
+function\footnote{\citet{2012ApJ...756..160I} underestimated the
+  dispersion in rest-frame UV quasar colours with respect to SDSS at
+  all redshifts (their Figure~4). Contrary to their claim, photometric
+  errors have a small effect on the colour distribution of SDSS
+  quasars given the statistical errors of $<0.03$\,mag in $gri$ for 90
+  per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and a
+  relative calibration error of $\sim 1$ per cent
+  \citep{2008ApJ...674.1217P}.}.
+
 \begin{table*}
@@
 
-\section{Homogenised Quasar Sample}
-\label{sec:sample}
-
-\subsection{Sample Selection}
-\label{sect:samplesel}
-
-We started by compiling the samples of recent photometric rest-frame
-UV-optical quasar surveys. The restriction to UV-optical surveys was
-mainly driven by our science goal to characterise the UV luminosity
-function of Type~1 quasars. X-ray-selected samples are less suited for
-this purpose due to spectroscopic incompleteness and the $\sim
-0.4$\,dex scatter in the conversion from X-ray to UV luminosity
-\citep{2010A&A...512A..34L, 2015MNRAS.453.1946G, 2016ApJ...819..154L}
-that contributes significantly to the error budget in the UV
-luminosity function of X-ray-selected samples unless rest-frame UV
-photometry is incorporated \citep{2015AA...578A..83G}.  The individual
-surveys and their main characteristics are listed in
-Table~\ref{tab:samples}.  Figure~\ref{fig:qsos} presents a redshift
-histogram of the contributing surveys.
-
-We included surveys based on a set of simple criteria:
-\begin{enumerate}
-\item High spectroscopic completeness of the target sample.
-\item Accurate rest-frame UV-optical CCD photometry.
-\item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
-\item A well-characterised selection function.
-\end{enumerate}
-As a prerequisite for a joint analysis of the QLF we obtained the
-survey selection functions in electronic form, either from the
-publication or by request from the authors. As a reference for future
-surveys we make them electronically available here in modified and
-homogenised form (see Section~\ref{sect:datahom} and
-Appendix~\ref{sec:code}).
-
-Due to their selection criteria and their statistical power specific
-surveys contribute to distinct redshift ranges. At $z<2.2$ we
-considered quasars from the SDSS DR7 quasar catalogue
-\citep{2010AJ....139.2360S} and the 2SLAQ survey catalogue
-\citep{2009MNRAS.392...19C}. We restricted the SDSS DR7 sample to the
-48,664 $0.1<z<2.2$ quasars selected with the final SDSS quasar
-selection algorithm \citep{2002AJ....123.2945R, 2006AJ....131.2766R}
-from a survey area of 6248\,deg$^2$ \citep{2012ApJ...746..169S}. We
-adopted the SDSS targeting photometry corrected for Galactic
-extinction \citep{2010AJ....139.2360S}. To limit systematic
-uncertainties in the correction for host galaxy light \citep[detailed
-  in][]{2009MNRAS.392...19C} we restricted the 2SLAQ sample to 9365
-$g<21.85$ $0.4<z<2.2$ quasars from its spectroscopic survey footprint
-near the North Galactic Pole (NGP, 7027 quasars in $127.7$\,deg$^2$)
-and the South Galactic Pole (SGP, 2338 quasars in
-$64.2$\,deg$^2$). The small sample overlap between SDSS and 2SLAQ (102
-quasars) has negligible impact on the QLF evaluation.
-
-At $2.2<z<3.5$ we used a single sample of 23,301 uniformly
-colour-selected quasars from 2236\,deg$^2$ in BOSS DR9
-\citep{2013ApJ...773...14R} due to several improvements compared to
-previous surveys. First, it covers a similar magnitude range as 2SLAQ
-but with $>20$ times as many quasars. Second, although the SDSS DR7
-sample provides better coverage of the bright end of the QLF at these
-redshifts, its selection function is highly dependent on the assumed
-incidence of (partial) Lyman limit systems in the IGM
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
-selection function considers these improvements, the uncertainty in
-the QLF remains dominated by assumptions in the selection function
-given the large sample size
-\citep{2013ApJ...773...14R}. Variability-selected quasar samples
-circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
-  2016A&A...587A..41P}, but may be affected by (i) single-epoch
-imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
-and (ii) uncertainties in the selection function caused by the limited
-number of known $z\ga 3$ quasars not selected by variability in the
-same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
-
-At $3.7<z<4.7$ we used a combination of SDSS DR7 \citep[1785 uniformly
-  selected quasars from][]{2010AJ....139.2360S} and the NDWFS$+$DLS
-survey \citep{2010ApJ...710.1498G,2011ApJ...728L..26G}. The lower cut
-$z>3.7$ in SDSS limits the impact of systematic uncertainties in the
-\citet{2006AJ....131.2766R} selection function
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. We did not consider
-the results from surveys for faint $z\sim 4$ quasars in the COSMOS
-field \citep{2011ApJ...728L..25I, 2012ApJ...755..169M} due to
-systematic errors in their selection functions\footnote{Both studies
-  simulated quasar colours with a mean IGM attenuation curve
-  \citep{1995ApJ...441...18M} that cannot account for stochastic Lyman
-  continuum absorption, and therefore underpredicts the variance in
-  quasar colours \citep{1999ApJ...518..103B, 2008MNRAS.387.1681I,
-    2011ApJ...728...23W}. Modelling the colour variance in these
-  surveys is essential, as most of the \citet{2011ApJ...728L..25I}
-  quasars are near the edge of their colour selection region (see
-  their Figure~1), and \citet{2012ApJ...755..169M} require modest
-  attenuation of the $U$ band flux relative to the mid-infrared
-  flux.}. Furthermore, 30 per cent of the \citet{2012ApJ...755..169M}
-COSMOS sample have visually estimated photometric redshifts, and the
-spectroscopic subsample reveals that 40 per cent of the visually
-estimated redshifts are biased low
-($z_\mathrm{spec}>z_\mathrm{est}+0.3$, see their Figure~9). These
-unaccounted systematic redshift errors at least partly explain the
-discrepancy in the $z\sim 4$ QLF between \citet{2011ApJ...728L..26G}
-and \citet{2012ApJ...755..169M}, which justifies our preference for
-the former sample that is 77 per cent spectroscopically complete at
-$R$ magnitudes $<23.5$ \citep{2011ApJ...728L..26G}.
-
-At $4.7\le z<5.5$ we combined several recent surveys, accounting for
-sample overlap and updated selection functions. At the bright end of
-the QLF we used the 99 quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} that have $M_{1450}\le -26.73$ in our adopted
-cosmology.  For these 99 quasars selected from 14,555\,deg$^2$ we
-adopted the \citet{2016ApJ...829...33Y} selection function.  The
-\citet{2016ApJ...829...33Y} sample partially overlaps with the SDSS
-DR7 sample from \citet{2013ApJ...768..105M}, so to avoid
-double-counting quasars we used the latter sample only at
-$M_{1450}>-26.73$, yielding 103 additional $4.7\le z<5.5$ quasars selected in
-6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection function from
-\citet{2013ApJ...768..105M} that supersedes the one from
-\citet{2006AJ....131.2766R} due to improved bandpass corrections and IGM
-parameterization.  To these two bright-end samples we added the
-faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82
-survey (59 uniformly selected $M_{1450}>-26.73$ $4.7\le z<5.5$ quasars in 235\,deg$^2$)
-and two $4.7\le z<5.5$ quasars from \citet{2011ApJ...728L..26G},
-adopting the respective selection functions.  We did not consider the
-limit on the $z\sim 5$ QLF by \citet{2012ApJ...756..160I} due to
-systematic errors in their selection
-function\footnote{\citet{2012ApJ...756..160I} underestimated the
-  dispersion in rest-frame UV quasar colours with respect to SDSS at
-  all redshifts (their Figure~4). Contrary to their claim, photometric
-  errors have a small effect on the colour distribution of SDSS
-  quasars given the statistical errors of $<0.03$\,mag in $gri$ for 90
-  per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and a
-  relative calibration error of $\sim 1$ per cent
-  \citep{2008ApJ...674.1217P}.}.
-
 The SDSS colours of $5.1<z<5.5$ quasars are similar to those of M and
@@
 \label{sect:datahom}
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]{kcorr.pdf}
-  \caption{Bandpass corrections $K_{m,1450}$ from a broadband
-    magnitude $m=\{g,i,z_\mathrm{AB}\}$ to the monochromatic AB
-    magnitude at 1450\,\AA\ as a function of redshift $z$ for the
-    \citet{2015MNRAS.449.4204L} quasar SED used in this work, and for
-    two quasar composite spectra \citep{2001AJ....122..549V,
-      2002ApJ...565..773T}.  The redshift range has been restricted to
-    exclude the Ly$\alpha$ forest and to account for the different
-    rest frame wavelength coverage of the spectra.}
-  \label{fig:kcorr}
-\end{figure}
 
@@
 
-%% JFH Let's make all these conversion factors and codes to do K-correction
-%% publicly avaialble in an appendix.
-
 For the $z<2.2$ sample we corrected the SDSS $i$ and 2SLAQ $g$ band
@@
 we adopted their respective bandpass corrections to $M_{1450}$. In
-particular, for the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G}
-sample we recomputed $M_{1450}$ from the $R$ band photometry to be
-consistent with the selection function defined in $R$, and to avoid
-uncertainties in their spectrophotometry due to incomplete spectral
-coverage. Since the \citet{2010ApJ...710.1498G, 2011ApJ...728L..26G}
-$R$ band traces the rest frame UV, we assumed negligible host galaxy
-contamination for their faint quasars. For the remaining high-redshift
-surveys reporting $M_{1450}$ obtained by various methods
-\citep{2010AJ....139..906W, 2011Natur.474..616M, 2015ApJ...798...28K,
-  2015ApJ...801L..11V, 2016ApJ...829...33Y, 2016ApJ...833..222J,
-  2018Natur.553..473B} we did not re-compute $M_{1450}$, but applied
-appropriate shifts to correct to our adopted cosmology.
+particular, for the $z\sim 4$ sample of \citet{2010ApJ...710.1498G,
+  2011ApJ...728L..26G} we recomputed $M_{1450}$ from the $R$ band
+photometry to be consistent with the selection function defined in
+$R$, and to avoid uncertainties in their spectrophotometry due to
+incomplete spectral coverage. Since the \citet{2010ApJ...710.1498G,
+  2011ApJ...728L..26G} $R$ band traces the rest frame UV, we assumed
+negligible host galaxy contamination for their faint quasars. For the
+remaining high-redshift surveys reporting $M_{1450}$ obtained by
+various methods \citep{2010AJ....139..906W, 2011Natur.474..616M,
+  2015ApJ...798...28K, 2015ApJ...801L..11V, 2016ApJ...829...33Y,
+  2016ApJ...833..222J, 2018Natur.553..473B} we did not re-compute
+$M_{1450}$, but applied appropriate shifts to correct to our adopted
+cosmology.
 
@@
 photometric selection functions.
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{kcorr.pdf}
+  \caption{Bandpass corrections $K_{m,1450}$ from a broadband
+    magnitude $m=\{g,i,z_\mathrm{AB}\}$ to the monochromatic AB
+    magnitude at 1450\,\AA\ as a function of redshift $z$ for the
+    \citet{2015MNRAS.449.4204L} quasar SED used in this work, and for
+    two quasar composite spectra \citep{2001AJ....122..549V,
+      2002ApJ...565..773T}.  The redshift range has been restricted to
+    exclude the Ly$\alpha$ forest and to account for the different
+    rest frame wavelength coverage of the spectra.}
+  \label{fig:kcorr}
+\end{figure}
 
@@
 $f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
-\citep{2006AJ....131.2766R}. The BOSS colour-selected sample contains
-quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$
-\citep{2013ApJ...773...14R}, and we adopted
-%% JFH The overline looks weird here. I would suggest taht you rather
-%% use angle brackets instead. It is not jiving with the equation above
-%% and is very hard to read. 
+\citep{2006AJ....131.2766R}. The BOSS colour-selected sample \citep{2013ApJ...773...14R} contains
+quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$, and we adopted
 $f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
@@
 
-%% GW: Maybe say what we mean by one-sigma uncertainty: This is a credible interval from the posterior distribution. Do we use the highest posterior density interval or the equal-tailed interval?
 \begin{figure*}
@@
   \end{center}
-  \caption{Homogenised quasar luminosity functions at rest-frame wavelength
-    $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to $6.5$.
-    The symbols show our inferred binned luminosity functions from various
-    data sets:
-    \citet[red]{2010AJ....139.2360S},
-    \citet[green]{2009MNRAS.392...19C},
-    \citet[dark blue]{2013ApJ...773...14R},
-    \citet[light blue]{2011ApJ...728L..26G},
-    \citet[yellow]{2016ApJ...829...33Y},
-    \citet[DR7 brown]{2013ApJ...768..105M},
-    \citet[Stripe 82 teal]{2013ApJ...768..105M},
-    \citet[pink]{2016ApJ...833..222J},
+  \caption{Homogenised quasar luminosity functions at rest-frame
+    wavelength $\lambda=1450$\,\AA\ in redshift bins from $z=0.1$ to
+    $6.5$.  The symbols show our inferred binned luminosity functions
+    from various data sets: \citet[red]{2010AJ....139.2360S},
+    \citet[green]{2009MNRAS.392...19C}, \citet[dark
+      blue]{2013ApJ...773...14R}, \citet[light
+      blue]{2011ApJ...728L..26G}, \citet[yellow]{2016ApJ...829...33Y},
+    \citet[DR7 brown]{2013ApJ...768..105M}, \citet[Stripe 82
+      teal]{2013ApJ...768..105M}, \citet[pink]{2016ApJ...833..222J},
     \citet[orange]{2010AJ....139..906W}, and
-    \citet[grey]{2015ApJ...798...28K}.
-    Open circles in corresponding colours indicate magnitude bins
-    excluded due to incompleteness in the respective data sets.  The
-    number of AGN before this selection is shown in parentheses; the
-    selected number of AGN is shown outside parentheses.  In each
-    redshift bin, the black curve shows our fiducial double power law
-    model fit, which is represented by the median of the posterior
-    probability distribution function.  The grey shaded area shows the
-    one-sigma (68.26\%) uncertainty.  See Sections~\ref{sec:binnedlf}
+    \citet[grey]{2015ApJ...798...28K}.  Open circles in corresponding
+    colours indicate magnitude bins excluded due to incompleteness in
+    the respective data sets.  The number of AGN before this selection
+    is shown in parentheses; the selected number of AGN is shown
+    outside parentheses.  In each redshift bin, the black curve shows
+    our fiducial double power law model fit, which is represented by
+    the median of the posterior probability distribution function.
+    The grey shaded area shows the one-sigma uncertainty (68.26\%
+    equal-tailed credible interval).  See Sections~\ref{sec:binnedlf}
     and \ref{sec:bins} for further details.}
@@
 
-%%GW: Added a note on discarded redshift bins
-%%GW: Check on final Nqso needed! The number at z~5 is inconsistent with Fig. 3
 \begin{table*}
-  % bins_tabulate.py; Nqso added by hand
-  \caption{\textbf{Check on final Nqso needed! The number at $z\sim5$ is inconsistent with Fig. 3. We could also have two columns for the number of quasars: before and after magnitude restrictions.}
-    Posterior median double power law luminosity function parameters
-    and their $1\sigma$ (68.26\%) statistical errors in
-    various redshift bins shown in Figure~\ref{fig:evoln}.
-    The luminosity function parameters
-    $\phi_*$, $M_*$, $\alpha$, and $\beta$ are defined in
-    Equation~(\ref{eqn:dpl}), with $\beta$ denoting the faint-end
-    slope.  Quasars in each bin have redshifts $z_\mathrm{min}\leq z <
-    z_\mathrm{max}$ with a sample mean $\langle z\rangle$.
-    The number of quasars in each bin is given by $N_\mathrm{QSO}$.
-    %The corresponding luminosity
-    %functions are shown in Figure~\ref{fig:mosaic}.  See
-    %Section~\ref{sec:bins} for further details.
-    }
+  % bins_tabulate.py; Nqso and Nqso' added by hand
+  \caption{Posterior median double power law luminosity function
+    parameters and their $1\sigma$ (68.26\%) statistical errors in
+    various redshift bins shown in Figure~\ref{fig:evoln}.  The
+    luminosity function parameters $\phi_*$, $M_*$, $\alpha$, and
+    $\beta$ are defined in Equation~(\ref{eqn:dpl}), with $\beta$
+    denoting the faint-end slope.  Quasars in each bin have redshifts
+    $z_\mathrm{min}\leq z < z_\mathrm{max}$ with a sample mean
+    $\langle z\rangle$.  The total number of QSOs in each bin is given
+    by $N_\mathrm{QSO}^\prime$.  The selected number of QSOs in each
+    bin, after excluding faint QSOs due to excess incompleteness is
+    given by $N_\mathrm{QSO}$.}
   \label{tab:bins}
-  \begin{tabular}{lccr....}
+  \begin{tabular}{lccrr....}
     \hline
@@
     $N_\mathrm{QSO}$ &
+    $N_\mathrm{QSO}^\prime$ &
     \multicolumn{1}{c}{$\log_{10}(\phi_*/$} &
@@
 
+    &
     &
@@
     \hline
-    0.31$^a$ & 0.10 & 0.40 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
-    0.50$^a$ & 0.40 & 0.60 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
-    0.72 & 0.60 & 0.80 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
-    0.91 & 0.80 & 1.00 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
-    1.10 & 1.00 & 1.20 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
-    1.30 & 1.20 & 1.40 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
-    1.50 & 1.40 & 1.60 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
-    1.71 & 1.60 & 1.80 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
-    1.98 & 1.80 & 2.20 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
-    2.30$^a$ & 2.20 & 2.40 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
-    2.45$^a$ & 2.40 & 2.50 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
-    2.55$^a$ & 2.50 & 2.60 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
-    2.65$^a$ & 2.60 & 2.70 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
-    2.75$^a$ & 2.70 & 2.80 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
-    2.85$^a$ & 2.80 & 2.90 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
-    2.95$^a$ & 2.90 & 3.00 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
-    3.05$^a$ & 3.00 & 3.10 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
-    3.15$^a$ & 3.10 & 3.20 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
-    3.25$^a$ & 3.20 & 3.30 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
-    3.34$^a$ & 3.30 & 3.40 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
-    3.44$^a$ & 3.40 & 3.50 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
-    3.88 & 3.70 & 4.10 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
-    4.35 & 4.10 & 4.70 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
-    4.92 & 4.70 & 5.50 & 266 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
-    6.00 & 5.50 & 6.50 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
+    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
+    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
+    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
+    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
+    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
+    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
+    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
+    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
+    1.98 & 1.80 & 2.20 & 10478 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
+    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
+    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
+    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
+    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
+    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
+    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
+    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
+    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
+    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
+    3.25$^a$ & 3.20 & 3.30 & 815 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
+    3.34$^a$ & 3.30 & 3.40 & 510 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
+    3.44$^a$ & 3.40 & 3.50 & 155 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
+    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.10 & 4.70 & 442 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
+    4.92 & 4.70 & 5.50 & 263 & 263 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
+    6.00 & 5.50 & 6.50 & 66 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
     \hline
@@
   Table~\ref{tab:samples} are included while fitting this model.
-  \textbf{GW agrees with JFH that this is too short and
-    cryptic. Table~\ref{tab:samples} refers to all samples, but we
-    exclude some samples, some redshift ranges, and some magnitude
-    ranges. I've put a clarification in the first sentence of the
-    section, but we might elaborate more.}
-  %% JFH where was this discussed?? Nowhere have I seen explicitly stated in the
-  %% text which luminosity/redshift ranges you are excluding from the analysis in performing
-  %% these fits because you think they are systematics dominated. This just needs to be clearly stated.
-  %% Add this to the end of Section 3.2 after you discuss the systematics. State what is excluded and why.
-  %% It is perfectly fine if you do this by eye, just state that.
 
@@
   respectively, quadratic, cubic, and linear polynomials in $(1+z)$.
-  The total number of parameter is 14.  However, while fitting this
-  model, we drop samples 7, 19, and 20 from the analysis.  The
-  selection function for these samples are not yet well-characterised.
-  Removing them allows us to understand the effect this has on the
-  favoured evolution model.
-  %% JFH Do not put the discussion here. Add a separate discussion where you address the samples you leave out. Referencing them by
-  %% number here is also a bit annoying to me. Just state the samples with a name of the survey.
-
-\item In Model 3, we again exclude samples 7, 19, and 20 from the
-  analysis.  We also continue to describe the evolution of $\phi_*$,
-  $M_*$ and $\alpha$ by quadratic, cubic, and linear polynomials in
-  $(1+z)$, respectively.  But in this model, the evolution of the
-  faint-end slope $\beta$ is also assumed to be linear in $(1+z)$.
-  This model thus has just 11 parameters.
+  The total number of parameters is 14.  However, while fitting this
+  model, we exclude the samples from \citet{2015AA...578A..83G},
+  \citet{2011Natur.474..616M}, \citet{2015ApJ...801L..11V}, and
+  \citet{2018Natur.553..473B} from the analysis (samples 17--20 from
+  Table~\ref{tab:samples}).  As discussed in
+  Section~\ref{sect:samplesel}, these samples have approximate
+  selection functions.  Removing them allows us to understand the
+  effect this has on the favoured evolution model.
+
+\item In Model 3, we again exclude samples from
+  \citet{2015AA...578A..83G}, \citet{2011Natur.474..616M},
+  \citet{2015ApJ...801L..11V}, and \citet{2018Natur.553..473B} from
+  the analysis (samples 17--20 from Table~\ref{tab:samples}).  We also
+  continue to describe the evolution of $\phi_*$, $M_*$ and $\alpha$
+  by quadratic, cubic, and linear polynomials in $(1+z)$,
+  respectively.  But in this model, the evolution of the faint-end
+  slope $\beta$ is also assumed to be linear in $(1+z)$.  This model
+  thus has just 11 parameters.
 \end{itemize}
@@
       blue]{2013A&A...551A..29P}, \citet[solid
-      cyan]{2016A&A...587A..41P}, \citet[solid
-      blue]{2017A&A...608A..64C}, and
-    \citet[brown]{2007A&A...472..443B}.}
+      cyan]{2016A&A...587A..41P}, and \citet[solid
+      blue]{2017A&A...608A..64C}.}
   \label{fig:e912_2}
@@
 removed from the analysis due to large systematic errors in the QLF
-parameters are shown as open circles.  \textbf{GW: Add a sentence on
-  error bars.}  Our derived emissivity values at 912\,\AA\ and at
-1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins} for
-reference.  The emissivity peaks between $z=2$ and 3 at
-$\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\,
-  cMpc^{-3}}$ depending on the magnitude limit, and decreases rapidly
-towards lower and higher redshifts.  Systematic errors in the
-faint-end slope derived from BOSS data are more pronounced for
-$M_{1450}<-18$ due to extrapolation of the QLF.
+parameters are shown as open circles, with the error bars representing
+68.26\% equal-tailed credible intervals.  Our derived emissivity
+values at 912\,\AA\ and at 1450\,\AA\ are listed in
+Table~\ref{tab:emissivity_bins} for reference.  The emissivity peaks
+between $z=2$ and 3 at $\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\,
+  s^{-1}\, Hz^{-1}\, cMpc^{-3}}$ depending on the magnitude limit, and
+decreases rapidly towards lower and higher redshifts.  Systematic
+errors in the faint-end slope derived from BOSS data are more
+pronounced for $M_{1450}<-18$ due to extrapolation of the QLF.
 
@@
 compute statistical errors of $\epsilon$ from given QLF fits, and we
-refrained from using the incorrect procedures applied by
-\citet{2015MNRAS.451L..30K}.  \textbf{GW: Emphasize again that our
-  error bars are correct and superior to Khaire's!}
+refrained from estimating them from the fits in the literature.  The
+statistical errors of our binned emissivities are based on the
+posterior of the QLF fits from unbinned data, and thus naturally
+account for the covariance in the QLF parameters.  In contrast,
+\citet{2015MNRAS.451L..30K} derived the majority of their values by
+refitting binned QLFs with fixed QLF slopes, and they calculated
+errors by propagating the errors in the QLF slopes, some of which they
+had assumed or inflated from the cited literature.  Due to these
+incorrect procedures the emissivity values derived by
+\citet{2015MNRAS.451L..30K} are not reliable.
 
@@
 \end{equation}
-where $h$ is Planck's constant, $\sigma_\ion{H}{i}(\nu)$ is the \ion{H}{i} photoionization cross-section \textbf{Citation}, and
+where $h$ is Planck's constant, $\sigma_\ion{H}{i}(\nu)$ is the
+\ion{H}{i} photoionization cross-section \citep{1997MNRAS.292...27H,
+  2011piim.book.....D}, and
 \begin{multline}
@@
 background. In the above equation
-$H\left(z^\prime\right)=H_0\sqrt{\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda}$
+$H\left(z^\prime\right)=H_0(\Omega_\mathrm{m}\left(1+z^\prime\right)^3+\Omega_\Lambda)^{1/2}$
 is the Hubble parameter, and
@@
 \end{equation}
-with $\epsilon_{912}\left(z^\prime\right)$ being represented by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21} for our two magnitude limits, respectively.
-For Poisson-distributed absorbers with an \ion{H}{i} column density distribution $f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial N_\ion{H}{i}\partial z^{\prime\prime}\right)$, the effective optical depth to \ion{H}{i} Lyman continuum photons travelling between redshifts $z^\prime$ and $z$ is \citep{1980ApJ...240..387P}
+with $\epsilon_{912}\left(z^\prime\right)$ being represented by
+Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21} for our two
+magnitude limits, respectively.  For Poisson-distributed absorbers
+with an \ion{H}{i} column density distribution
+$f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial
+N_\ion{H}{i}\partial z^{\prime\prime}\right)$, the effective optical
+depth to \ion{H}{i} Lyman continuum photons travelling between
+redshifts $z^\prime$ and $z$ is \citep{1980ApJ...240..387P}
 \begin{equation}
@@
 where $\tau_1\approx
-N_\ion{H}{i}\sigma_\ion{H}{i}\left(\nu\left[\frac{1+z^{\prime\prime}}{1+z}\right]\right)$
+N_\ion{H}{i}\sigma_\ion{H}{i}\nu\left(1+z^{\prime\prime}\right)/\left(1+z\right)$
 is the Lyman continuum optical depth through an individual
@@
 $z<3.5$, and roughly reproduces both the \ion{H}{i} Ly$\alpha$
-effective optical depth \citep[but not in detail --
-  see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
+effective optical depth \citep[but not in detail---see][]{2015MNRAS.450.4081P,2017MNRAS.464..897B,2017ApJ...837..106O}
 and the measured mean free path to \ion{H}{i} Lyman limit photons at
@@
 the emissivities of AGN and galaxies, but also due to differences in
-the parametrization of the IGM and the AGN SED.
-
-\textbf{Comments from GW:\\
-1. Do we plot HM12, MH15 and KS15 as published or recalculated from the emissivities?\\
-2. New forest measurements need discussion.\\
-3. High z: Assumption of uniform UVB is violated.
-}
-
-Davies: Table 1, uniform UVB results plotted
-novel statistical approach to infer Gamma by matching the observed and simulated joint distribution of transmission spikes in the $z\sim 6$ Ly$\alpha+\beta$ forest
-GammaHI for one $z_em=6.54$QSO assuming uniform or fluctuating UVB, proof of concept,
-report median of posterior PDFs with 68 percent credible interval, uncertainties do not include systematics (thermal state of IGM, continuum fit)
-
-Onorbe:
-correction to post-reionization GammaHI from HM12 to ensure that simulations match best observations of HI mean flux, goal is to reduce effect of post-process rescaling approach of simulations that aim to reproduce Lya statistics
-plot late reion model $z_\mathrm{reion}=6.55$
-
-We assume an
-upper limit of $z=15$ while integrating Equation~(\ref{eqn:flux}).
-The result is shown in Figure~\ref{fig:gammapi} for the luminosity
-function integration limits of $M_{1450}=-21$ and $-18$.  Also shown
-for comparison are the measurements of \citet{2013MNRAS.436.1023B},
-derived from the Lyman-$\alpha$ forest, and the measurements by
-\citet{2011MNRAS.412.2543C} from quasar proximity zones.
-%% JFH Please add the data from this paper by Davies:
-%% http://adsabs.harvard.edu/cgi-bin/nph-ref_query?bibcode=2018ApJ...855..106D&amp;refs=CITATIONS&amp;db_key=AST
-For an
-integration limit of $M_{1450}=-21$ the AGN contribution to the
-hydrogen photoionization rate falls short of 100\% across the redshift
-range.  It is marginally consistent with the measured photoionization
-rate at $z=2.4$.  The photoionization rate in our model for
-$M_{1450}=-21$ has the same evolution but a higher amplitude by a
-factor of $\sim 2$ as the QSO contribution to the \HI\ photoionization
-rate in the model of \citet{2012ApJ...746..125H}.  For both of our
-integration limits, the photoionisation rate peaks at $z\sim 2$.  For
-the integration limit of $M_{1450}=-18$, AGN can provide all the flux
-necessary to explain the observed \lya forest between $z=2.4$ and
-$3.2$, with a contribution from other sources necessary only at higher
-redshifts.  The photoionization rate in the $M_{1450}<-18$ case also
-agrees with the inference of \citet{2017MNRAS.467.3172G} from the
-low-redshift ($z<0.6$) \lya\ data.  We discuss this low-redshift
-evolution in greater detail in the next section.
+the parametrization of the IGM and the AGN SED.  For an integration
+limit of $M_{1450}=-21$ the AGN contribution to the hydrogen
+photoionization rate falls short of 100\% across the redshift range.
+It is marginally consistent with the measured photoionization rate at
+$z=2.4$.  The photoionization rate in our model for $M_{1450}=-21$ has
+the same evolution but a higher amplitude by a factor of $\sim 2$ as
+the QSO contribution to the \HI\ photoionization rate in the model of
+\citet{2012ApJ...746..125H}.  For both of our integration limits, the
+photoionisation rate peaks at $z\sim 2$.  For the integration limit of
+$M_{1450}=-18$, AGN can provide all the flux necessary to explain the
+observed \lya forest between $z=2.4$ and $3.2$, with a contribution
+from other sources necessary only at higher redshifts.  The
+photoionization rate in the $M_{1450}<-18$ case also agrees with the
+inference of \citet{2017MNRAS.467.3172G} from the low-redshift
+($z<0.6$) \lya\ data.  We discuss this low-redshift evolution in
+greater detail in the next section.
 
@@
 of the required \HI\ ionizing flux.  The contribution of
-$M_{1450}<-21$ at this redshift is $\sim 3\%$.  At $z=6$, our
-determinations are lower than those by \citet{2015AA...578A..83G} by
-almost an order of magnitude.  This difference arises from the
-difference in the inferred emissivities in our models relative to
-\citet{2015AA...578A..83G}, as discussed in the previous section.  The
-photoionization rate evolution in the model of
-\citet{2015ApJ...813L...8M} agrees with our determination at low
-redshifts ($z<0.5$) for $M_{1450}<-18$ but is much higher at $z>4$, as
-expected from the higher emissivities assumed by these authors.  At
-$3<z<6$ our model photoionization rates are understandably lower than
-those in the models of \citet{2017ApJ...837..106O} and
-\citet{2018arXiv180104931P} as these authors include contribution to
-the photoionization rate from galaxies in their models.
-\textbf{GW: KS15 is different due to their integration limits.}
-The differences in our model from that of \citet{2015MNRAS.451L..30K} are
-a result of our differences from the reported emissivities of
+$M_{1450}<-21$ at this redshift is $\sim 3\%$ relative to the
+measurements \citep{2011MNRAS.412.2543C, 2018MNRAS.473..560D,
+  2018ApJ...855..106D}.  At $z=6$, our determinations are lower than
+those by \citet{2015AA...578A..83G} by almost an order of magnitude.
+This difference arises from the difference in the inferred
+emissivities in our models relative to \citet{2015AA...578A..83G}, as
+discussed in the previous section.  The photoionization rate evolution
+in the model of \citet{2015ApJ...813L...8M} agrees with our
+determination at low redshifts ($z<0.5$) for $M_{1450}<-18$ but is
+much higher at $z>4$, as expected from the higher emissivities assumed
+by these authors.  At $3<z<6$ our model photoionization rates are
+understandably lower than those in the models of
+\citet{2017ApJ...837..106O} and \citet{2018arXiv180104931P} as these
+authors include contribution to the photoionization rate from galaxies
+in their models.  The differences in our model from that of
+\citet{2015MNRAS.451L..30K} are a result of the inhomogeneous
+redshift-dependent integration limits used by these authors and our
+differences from the reported emissivities of
 \citet{2009MNRAS.392...19C} and \citet{2013A&A...551A..29P}, which are
@@
   \end{center}
-  \caption{ Redshift evolution of the volume-averaged \ion{He}{iii}
+  \caption{Redshift evolution of the volume-averaged \ion{He}{iii}
     fraction $Q_\ion{He}{iii}$ considering AGN with $M_{1450}<-21$
@@
 reionization starts around the earliest quasars at $z>6$ and finishes
-at $3.2\la z\la 3.5$ depending on the extent of the faint-end QLF.
+at $2.9\la z\la 3.4$ depending on the extent of the faint-end QLF.
 Considering the limitations of the modelling discussed above, both
@@
 varying magnitude limits their emissivity calculations.
-
 \citet{2018arXiv180104931P} adopted a somewhat higher quasar
@@
 
-\textbf{A short final paragraph on Hopkins here...}
+Using the homogenised data and code that we make publicly available
+(Appendix \ref{sec:code}), the luminosity functions presented in this
+paper can be easily compared with theoretical models or future data
+sets.  These luminosity function determinations supercede previous
+determinations by \citet{2007ApJ...654..731H} by including new data
+and extending the analysis to higher redshifts.  Our public code can
+be used either to reproduce all of our analysis starting from the QSO
+catalogues, or to quickly evaluate our luminosity function fits at
+desired redshifts and luminosities.  While doing this, the evolution
+of the luminosity function can be derived using any of the three
+global models that we presented in Section~\ref{sec:global}.  However,
+as we discussed in Section~\ref{sec:global}, none of these models
+should be extrapolated to higher redshifts.  Alternatively, our binned
+luminosity function estimates from Section~\ref{sec:bins} can be used.
+For applications that require extrapolation to higher redshifts, such
+as calculations of photoionization fluxes and emissivities, the fits
+presented in Equations~(\ref{eqn:e912_21}) and (\ref{eqn:e912_18}) can
+be used, or a similar approach of fitting functional forms to
+quantities suitably derived from the binned luminosity functions
+should be adopted.
 
@@
     % corner.corner() with bins.lfs[-4]
-    \includegraphics[width=\textwidth]{corner_z3p9.pdf}
+    \includegraphics[width=0.6\textwidth]{corner_z3p9.pdf}
   \end{center}

### 2018-07-23 qhe.py
Bug: use correct emissivity

@@ -20,24 +20,42 @@ if __name__ == '__main__':
     import matplotlib.pyplot as plt
     import sys
 
-
-data = np.load('e1450_18.npz')
+data = np.load('e1450_18_test.npz')
 z18 = data['z']
-medianbright18 = data['medianbright']
-medianfaint18 = data['medianfaint']
-downbright18 = data['downbright']
-upbright18 = data['upbright']
-downfaint18 = data['downfaint']
-upfaint18 = data['upfaint']
+medianbright18 = data['medianbright']*((912.0/1450.0)**0.61)
+downbright18 = data['downbright']*((912.0/1450.0)**0.61)
+upbright18 = data['upbright']*((912.0/1450.0)**0.61)
+medianfaint18 = data['medianfaint']*((912.0/1450.0)**0.61)
+downfaint18 = data['downfaint']*((912.0/1450.0)**0.61)
+upfaint18 = data['upfaint']*((912.0/1450.0)**0.61)
 
-data = np.load('e1450_21.npz')
+data = np.load('e1450_21_test.npz')
 z21 = data['z']
-medianbright21 = data['medianbright']
-medianfaint21 = data['medianfaint']
-downbright21 = data['downbright']
-upbright21 = data['upbright']
-downfaint21 = data['downfaint']
-upfaint21 = data['upfaint']
+medianbright21 = data['medianbright']*((912.0/1450.0)**0.61)
+downbright21 = data['downbright']*((912.0/1450.0)**0.61)
+upbright21 = data['upbright']*((912.0/1450.0)**0.61)
+medianfaint21 = data['medianfaint']*((912.0/1450.0)**0.61)
+downfaint21 = data['downfaint']*((912.0/1450.0)**0.61)
+upfaint21 = data['upfaint']*((912.0/1450.0)**0.61)
+
+    
+# data = np.load('e912_18_test.npz')
+# z18 = data['z']
+# medianbright18 = data['median']
+# downbright18 = data['down']
+# upbright18 = data['up']
+# medianfaint18 = 0.0*data['median']
+# downfaint18 = 0.0*data['down']
+# upfaint18 = 0.0*data['up']
+
+# data = np.load('e912_21_test.npz')
+# z21 = data['z']
+# medianbright21 = data['median']
+# downbright21 = data['down']
+# upbright21 = data['up']
+# medianfaint21 = 0.0*data['median']
+# downfaint21 = 0.0*data['down']
[…]

### 2018-07-23 rhoqso_fit.py
Check posterior statistics

@@ -15,14 +15,20 @@ def luminosity(M):
 
 def rhoqso(loglf, theta, mlim, mbright=-23.0):
 
+    """1450A emissivity.
+
+    """
+
     m = np.linspace(mbright, mlim, num=100)
     farr = np.array([(10.0**loglf(theta, x))*luminosity(x) for x in m])
-    #farr = np.array([10.0**loglf(theta, x)*luminosity(x)*((912.0/1450.0)**0.61) for x in m])
     
     return np.trapz(farr, m) # ergs s^-1 Hz^-1 cMpc^-3
 
 def get_rhoqso(lfi, mlim, mbright=-23):
 
+    """1450A emissivity (statistics).
+
+    """
     rindices = np.random.randint(len(lfi.samples), size=300)
     r = np.array([rhoqso(lfi.log10phi, theta, mlim, mbright=mbright)
                           for theta
@@ -36,6 +42,10 @@ def get_rhoqso(lfi, mlim, mbright=-23):
 
 def rhoqso_912(loglf, theta, mlim, mbright=-30.0):
 
+    """912A emissivity.
+
+    """
+
     m = np.linspace(mbright, mlim, num=100)
     farr = np.array([10.0**loglf(theta, x)*luminosity(x)*((912.0/1450.0)**0.61) for x in m])
     
@@ -43,6 +53,10 @@ def rhoqso_912(loglf, theta, mlim, mbright=-30.0):
 
 def get_rhoqso_912(lfi, mlim, mbright=-30):
 
+    """912A emissivity (statistics).
+
+    """
+    
     rindices = np.random.randint(len(lfi.samples), size=300)
     r = np.array([rhoqso_912(lfi.log10phi, theta, mlim, mbright=mbright)
                           for theta
@@ -104,6 +118,110 @@ def plot(redshifts, data, fit, filename):
     b = fit[1]
     efaint, = plt.plot(z, b, lw=2, c='red', zorder=5)
 
+    plt.savefig(filename, bbox_inches='tight')
+    plt.close('all')
+
+    return
+
+
+def plot_check(redshifts, data, fit, redshifts2, data2, fit2, filename):
+
+    fig = plt.figure(figsize=(7, 7), dpi=100)
+    ax = fig.add_subplot(1, 1, 1)
+    
+    plt.minorticks_on()
+    ax.tick_params('both', which='major', length=7, width=1)
+    ax.tick_params('both', which='minor', length=5, width=1)
+    
[…]

### 2018-07-23 summary_bins.py
Update style

@@ -12,7 +12,6 @@ from scipy.optimize import curve_fit
 from scipy.interpolate import UnivariateSpline
 
 # These redshift bins are labelled "bad" and are plotted differently.
-# reject = [0, 1, 8, 9, 10, 11, 12, 13]
 reject = [0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20]
 
 colors = ['tomato', 'forestgreen', 'goldenrod', 'saddlebrown'] 
@@ -25,6 +24,8 @@ zlims=(0.0,7.0)
 zmin, zmax = zlims
 z = np.linspace(zmin, zmax, num=50)
 cfit = False
+
+show_bad_data_differently = True
 
 def getParam(individuals, param, which='old', dtype='good'):
 
@@ -102,7 +103,7 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False):
     downerr = c-l
     ax.errorbar(zmean, c, ecolor=colors[0], capsize=0,
                 xerr=np.vstack((left, right)), 
-                yerr=np.vstack((uperr, downerr)),
+                yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color=colors[0], edgecolor='None', zorder=6, s=40)
 
@@ -113,10 +114,13 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False):
     downerr = c-l
     ax.errorbar(zmean, c, ecolor=colors[0], capsize=0,
                 xerr=np.vstack((left, right)), 
-                yerr=np.vstack((uperr, downerr)),
+                yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=6)
-    ax.scatter(zmean, c, color='#ffffff', edgecolor=colors[0], zorder=6, s=35)
-    
+    if show_bad_data_differently: 
+        ax.scatter(zmean, c, color='#ffffff', edgecolor=colors[0], zorder=6, s=35)
+    else:
+        ax.scatter(zmean, c, color=colors[0], edgecolor='None', zorder=6, s=40)
+        
     if cfit:
         zc = np.linspace(0, 7, 500)
         coeffs = chebfit(zmean+1, c, 2)
@@ -148,7 +152,7 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False):
     # zm, cm, uperr, downerr = np.loadtxt('Data/manti.txt',
[…]

### 2018-07-23 summary_fromFile.py

@@ -165,7 +165,7 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False, 
     downerr = c-l
     ax.errorbar(zmean, c, ecolor='k', capsize=0,
                 xerr=np.vstack((left, right)), 
-                yerr=np.vstack((uperr, downerr)),
+                yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color=colors[0], edgecolor='None', zorder=6, s=30)
 
@@ -176,7 +176,7 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False, 
     downerr = c-l
     ax.errorbar(zmean, c, ecolor='grey', capsize=0,
                 xerr=np.vstack((left, right)), 
-                yerr=np.vstack((uperr, downerr)),
+                yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color='#ffffff', edgecolor='grey', zorder=6, s=27)
     
@@ -211,7 +211,7 @@ def plot_phi_star(fig, composite, individuals=None, compOpt=None, sample=False, 
     # zm, cm, uperr, downerr = np.loadtxt('Data/manti.txt',
     #                                     usecols=(0,1,2,3), unpack=True)
     # ax.errorbar(zm, cm, ecolor='grey', capsize=0,
-    #             yerr=np.vstack((uperr, downerr)),
+    #             yerr=np.vstack((downerr, uperr)),
     #             fmt='None', zorder=4)
     # ax.scatter(zm, cm, color='#ffffff', edgecolor='grey', zorder=4, s=30)
 
@@ -275,14 +275,14 @@ def plot_m_star(fig, composite, individuals=None, compOpt=None, sample=False, lf
     downerr = c-l
     ax.errorbar(zmean, c, ecolor=colors[1], capsize=0,
                 xerr=np.vstack((left, right)), 
-                yerr=np.vstack((uperr, downerr)),
+                yerr=np.vstack((downerr, uperr)),
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color=colors[1], edgecolor='None', zorder=6, s=30, label='included data')
 
     # zm, cm, uperr, downerr = np.loadtxt('Data/manti.txt',
     #                                     usecols=(0,4,5,6), unpack=True)
[…]

### 2018-07-23 summary_grand.py

@@ -49,7 +49,7 @@ def ross13_s82(ax, param):
 
     p = param
 
-    rs, corr = np.loadtxt('magconv_boss_kwh18.dat', usecols=(1,2), unpack=True)
+    rs, corr = np.loadtxt('Data_new/magconv_boss_kwh18.dat', usecols=(1,2), unpack=True)
 
     # Ross's alpha is our beta and vv. 
     if param == 3:

### 2018-07-23 Paper/paper.tex

@@
   function from redshifts $z=0$ to $7.5$.  The luminosity function has
-  a double power law form at $z<5.5$, and a single power law form at
-  higher redshifts.  The break luminosity brightens rapidly with
-  redshift and the faint end of the luminosity function steepens.  In
-  spite of this steepening, the contribution of AGN to the hydrogen
-  photoionization rate at $z\sim 6$ is subdominant, although it can be
-  non-negligible if these luminosity functions hold down to
-  $M_{1450}=-18$.  Under reasonable assumptions, AGN can reionize
-  \HeII\ by redshift $z=3.2$.  At low redshifts ($z<0.5$), AGN can
-  produce all of the hydrogen photoionization rate inferred from the
-  statistics of \HI\ absorption lines in the IGM.  Our global analysis
-  of the luminosity function also reveals important systematic errors
-  in the data, particularly at $z=2.2$--$3.5$, which need to be
-  addressed in future in order to improve our results.  We make
-  various fitting functions, luminosity function analysis codes, and
-  homogenised AGN data publicly available.
+  a double power law form at most redshifts.  The break luminosity
+  brightens rapidly with redshift and the faint end of the luminosity
+  function steepens.  In spite of this steepening, the contribution of
+  AGN to the hydrogen photoionization rate at $z\sim 6$ is
+  subdominant, although it can be non-negligible if these luminosity
+  functions hold down to $M_{1450}=-18$.  Under reasonable
+  assumptions, AGN can reionize \HeII\ by redshift $z=2.9$.  At low
+  redshifts ($z<0.5$), AGN can produce about half of the hydrogen
+  photoionization rate inferred from the statistics of \HI\ absorption
+  lines in the IGM.  Our global analysis of the luminosity function
+  also reveals important systematic errors in the data, particularly
+  at $z=2.2$--$3.5$, which need to be addressed in future in order to
+  improve our results.  We make various fitting functions, luminosity
+  function analysis codes, and homogenised AGN data publicly
+  available.
 \end{abstract}
@@
 evolution over cosmological time scales has been a matter of central
-interest of a large body of work over the last four decades
+interest of a large body of work over the last five decades
 \citep{1968ApJ...151..393S, 1978A&A....68...17M, 1983ApJ...269..352S,
@@
 galaxies at these redshifts.  (The UV luminosity function of galaxies
-at $z=6$ has $M^*_{1450}\sim -20$.)  A significant presence of AGN at
-high redshift ($z\sim 6$) and a dominant contribution of AGN to
-reionization is appealing as the LyC escape fraction of galaxies is
-uncertain.  High-redshift galaxies down to rest-frame UV magnitude
-$M_\mathrm{UV}=-12.5$ ($L\sim 10^{-3}L^*_\mathrm{galaxies}$) at $z=6$
-\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
-\citep{2016ApJ...819..129O} have now been reported.  But the escape of
-LyC photons has been measured in only a few comparatively bright
-($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
-($z < 4$).  The escape fraction in these galaxies reveals a broad
-distribution from less than 2\% to more than 80\%
-\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
-  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
-  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
-  2018arXiv180303655C}, but the average escape fraction is typically
-lower than 20\%.  Statistical constraints from \HI\ column density
-measurements in gamma-ray burst (GRB) afterglow spectra suggest an
-even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
-  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
-reionization models, which require an escape fraction of about 20\% in
-galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
-  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
-high-redshift AGN may also be consistent with the shallow bright-end
-slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
-a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
-  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
-these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
-  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
-explanation for the large scatter in the \lya opacity between
-different quasar sightlines close to redshift $z=6$
-\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
+at $z=6$ has characteristic magnitude $M^*_{1450}\sim -20$.)  A
+significant presence of AGN at high redshift ($z\sim 6$) and a
+dominant contribution of AGN to reionization is appealing as the LyC
+escape fraction of galaxies is uncertain.  High-redshift galaxies down
+to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
+10^{-3}L^*_\mathrm{galaxies}$) at $z=6$ \citep{2017ApJ...835..113L}
+and redshifts up to $z=11.1$ \citep{2016ApJ...819..129O} have now been
+reported.  But the escape of LyC photons has been measured in only a
+few comparatively bright ($L>0.5L^*_\mathrm{galaxies}$) galaxies at
+relatively low redshifts ($z < 4$).  The escape fraction in these
+galaxies reveals a broad distribution from less than 2\% to more than
+80\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
+  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
+  2017MNRAS.468..389J, 2018arXiv180506071S, 2018arXiv180601741F,
+  2018arXiv180511621M, 2018arXiv180303655C}, but the average escape
+fraction is typically lower than 20\%.  Statistical constraints from
+\HI\ column density measurements in gamma-ray burst (GRB) afterglow
+spectra suggest an even lower escape fraction of 0.5\%
+\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
+This is a challenge for reionization models, which require an escape
+fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
+\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
+An enhanced incidence of high-redshift AGN may also be consistent with
+the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
+of galaxies relative to a Schechter function
+\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
+  2015MNRAS.452.1817B} and the hard spectra of these galaxies
+\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
+Finally, AGN may also provide a natural explanation for the large
+scatter in the \lya opacity between different quasar sightlines close
+to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
 These opacity fluctuations extend to substantially larger scales
@@
 \end{enumerate}
-As a prerequisite for a joint analysis of the QLF we obtained the
-survey selection functions in electronic form, either from the
-publication or by request from the authors. As a reference for future
-surveys we make them electronically available here in modified and
-homogenised form (see Section~\ref{sect:datahom} and
-Appendix~\ref{sec:code}).
+As a prerequisite for a joint analysis of the QSO luminosity function
+(QLF) we obtained the survey selection functions in electronic form,
+either from the publication or by request from the authors. As a
+reference for future surveys we make them electronically available
+here in modified and homogenised form (see Section~\ref{sect:datahom}
+and Appendix~\ref{sec:code}).
 
@@
 the QLF we used the 99 quasars from the SDSS+WISE survey
-\citep{2016ApJ...829...33Y} that have $M_{1450}\le -26.73$ in our adopted
-cosmology.  For these 99 quasars selected from 14,555\,deg$^2$ we
-adopted the \citet{2016ApJ...829...33Y} selection function.  The
-\citet{2016ApJ...829...33Y} sample partially overlaps with the SDSS
-DR7 sample from \citet{2013ApJ...768..105M}, so to avoid
+\citep{2016ApJ...829...33Y} that have $M_{1450}\le -26.73$ in our
+adopted cosmology.  For these 99 quasars selected from 14,555\,deg$^2$
+we adopted the \citet{2016ApJ...829...33Y} selection function.  The
+\citet{2016ApJ...829...33Y} sample partially overlaps with the
+\citet{2013ApJ...768..105M} SDSS DR7 sample, so to avoid
 double-counting quasars we used the latter sample only at
-$M_{1450}>-26.73$, yielding 103 additional $4.7\le z<5.5$ quasars selected in
-6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection function from
-\citet{2013ApJ...768..105M} that supersedes the one from
-\citet{2006AJ....131.2766R} due to improved bandpass corrections and IGM
-parameterization.  To these two bright-end samples we added the
+$M_{1450}>-26.73$, yielding 103 additional $4.7\le z<5.5$ quasars
+selected in 6248\,deg$^2$. We used the $z\sim 5$ SDSS DR7 selection
+function from \citet{2013ApJ...768..105M} that supersedes the one from
+\citet{2006AJ....131.2766R} due to improved bandpass corrections and
+IGM parameterization.  To these two bright-end samples we added the
 faint-end sample from the \citet{2013ApJ...768..105M} SDSS Stripe~82
-survey (59 uniformly selected $M_{1450}>-26.73$ $4.7\le z<5.5$ quasars in 235\,deg$^2$)
-and two $4.7\le z<5.5$ quasars from \citet{2011ApJ...728L..26G},
-adopting the respective selection functions.  We did not consider the
-limit on the $z\sim 5$ QLF by \citet{2012ApJ...756..160I} due to
-systematic errors in their selection
-function\footnote{\citet{2012ApJ...756..160I} underestimated the
-  dispersion in rest-frame UV quasar colours with respect to SDSS at
-  all redshifts (their Figure~4). Contrary to their claim, photometric
-  errors have a small effect on the colour distribution of SDSS
-  quasars given the statistical errors of $<0.03$\,mag in $gri$ for 90
-  per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and a
-  relative calibration error of $\sim 1$ per cent
+survey (59 uniformly selected $M_{1450}>-26.73$ $4.7\le z<5.5$ quasars
+in 235\,deg$^2$) and two $4.7\le z<5.5$ quasars from
+\citet{2011ApJ...728L..26G}, adopting the respective selection
+functions.  We did not consider the limit on the $z\sim 5$ QLF by
+\citet{2012ApJ...756..160I} due to systematic errors in their
+selection function\footnote{\citet{2012ApJ...756..160I} underestimated
+  the dispersion in rest-frame UV quasar colours with respect to SDSS
+  at all redshifts (their Figure~4). Contrary to their claim,
+  photometric errors have a small effect on the colour distribution of
+  SDSS quasars given the statistical errors of $<0.03$\,mag in $gri$
+  for 90 per cent of the SDSS DR7 bright quasar sample ($i<19.1$) and
+  a relative calibration error of $\sim 1$ per cent
   \citep{2008ApJ...674.1217P}.}.
@@
       circles]{2013MNRAS.436.1023B}, \citet[inverted
-      triangles]{2011MNRAS.412.2543C}, and
+      triangles]{2011MNRAS.412.2543C},
+    \citet[triangles]{2011MNRAS.412.1926W}, \citet[blue
+      hexagons]{2018MNRAS.473..560D} and \citet[green
+      squares]{2018ApJ...855..106D}, and
     \citet[pentagons]{2017MNRAS.467.3172G}, and models of
@@
       grey]{2017ApJ...837..106O}, and \citet[dashed
-      grey]{2018arXiv180104931P}.}
+      grey]{2018arXiv180104931P}.  The photoionisation rate derived
+    from the luminosity function fits of \citet{2015AA...578A..83G}
+    are shown by the red open circles.}
   \label{fig:gammapi}
@@
   \frac{4\pi J_\nu\left(\nu,z\right)}{h\nu} \sigma_\ion{H}{i}\left(\nu\right)\quad,
+  \label{eqn:gammapi}
 \end{equation}
@@
     % corner.corner() with bins.lfs[-4]
-    \includegraphics[width=0.6\textwidth]{corner_z3p9.pdf}
+    \includegraphics[width=0.65\textwidth]{corner_z3p9.pdf}
   \end{center}
@@
   \caption{
-    \textbf{GW: Delete the zbin column that we do not use. Indicate the credible (fitted) redshift bins!}
     Comoving emissivities at 912\,\AA\ and 1450\,\AA\ derived from
@@
   \label{tab:emissivity_bins}
-  \begin{tabular}{cccc....}
+  \begin{tabular}{ccc....}
     \hline
     $\langle z\rangle$ &
-    $z_\mathrm{bin}$ &
     $z_\mathrm{min}$ &
@@
     &
-    &
     \multicolumn{1}{c}{$(M_{1450}<-18)$} &
@@
     \hline
-    0.31 & 0.25 & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.71^{+0.03}_{-0.03} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
-    0.50 & 0.50 & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.02}_{-0.02} & 0.58^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
-    0.72 & 0.70 & 0.60 & 0.80 & 1.73^{+0.06}_{-0.05} & 2.31^{+0.07}_{-0.06} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.02} \\
-    0.91 & 0.90 & 0.80 & 1.00 & 2.85^{+0.16}_{-0.16} & 3.77^{+0.20}_{-0.19} & 2.10^{+0.05}_{-0.05} & 2.79^{+0.06}_{-0.06} \\
-    1.10 & 1.10 & 1.00 & 1.20 & 3.71^{+0.11}_{-0.10} & 4.94^{+0.15}_{-0.13} & 2.91^{+0.05}_{-0.05} & 3.87^{+0.06}_{-0.06} \\
-    1.30 & 1.30 & 1.20 & 1.40 & 5.69^{+0.23}_{-0.24} & 7.52^{+0.32}_{-0.30} & 4.46^{+0.10}_{-0.09} & 5.91^{+0.11}_{-0.12} \\
-    1.50 & 1.50 & 1.40 & 1.60 & 7.04^{+0.22}_{-0.22} & 9.34^{+0.26}_{-0.31} & 5.59^{+0.09}_{-0.11} & 7.41^{+0.13}_{-0.13} \\
-    1.71 & 1.70 & 1.60 & 1.80 & 7.69^{+0.18}_{-0.18} & 10.23^{+0.24}_{-0.26} & 6.71^{+0.10}_{-0.11} & 8.90^{+0.13}_{-0.14} \\
-    1.98 & 2.00 & 1.80 & 2.20 & 10.59^{+0.36}_{-0.36} & 14.08^{+0.43}_{-0.42} & 7.93^{+0.13}_{-0.14} & 10.52^{+0.19}_{-0.17} \\
-    2.25 & 2.25 & 2.20 & 2.30 & 11.34^{+0.35}_{-0.37} & 14.97^{+0.48}_{-0.50} & 10.06^{+0.20}_{-0.20} & 13.37^{+0.26}_{-0.23} \\
-    2.35 & 2.35 & 2.30 & 2.40 & 9.30^{+0.30}_{-0.30} & 12.29^{+0.36}_{-0.35} & 8.02^{+0.15}_{-0.15} & 10.65^{+0.22}_{-0.20} \\
-    2.45 & 2.45 & 2.40 & 2.50 & 8.06^{+0.24}_{-0.24} & 10.67^{+0.30}_{-0.26} & 7.16^{+0.13}_{-0.15} & 9.49^{+0.17}_{-0.18} \\
-    2.65 & 2.65 & 2.60 & 2.70 & 6.55^{+0.16}_{-0.17} & 8.70^{+0.21}_{-0.20} & 6.46^{+0.15}_{-0.15} & 8.55^{+0.20}_{-0.20} \\
-    2.75 & 2.75 & 2.70 & 2.80 & 7.44^{+0.24}_{-0.22} & 9.93^{+0.30}_{-0.31} & 7.17^{+0.20}_{-0.20} & 9.51^{+0.27}_{-0.25} \\
-    2.85 & 2.85 & 2.80 & 2.90 & 7.94^{+0.28}_{-0.29} & 10.45^{+0.42}_{-0.41} & 7.48^{+0.29}_{-0.28} & 9.95^{+0.36}_{-0.35} \\
-    2.95 & 2.95 & 2.90 & 3.00 & 7.93^{+0.34}_{-0.34} & 10.51^{+0.45}_{-0.46} & 6.83^{+0.20}_{-0.21} & 9.09^{+0.28}_{-0.28} \\
-    3.05 & 3.05 & 3.00 & 3.10 & 7.18^{+0.38}_{-0.36} & 9.59^{+0.47}_{-0.50} & 6.24^{+0.20}_{-0.21} & 8.29^{+0.34}_{-0.30} \\
-    3.15 & 3.15 & 3.10 & 3.20 & 9.99^{+0.95}_{-1.03} & 13.14^{+1.38}_{-1.56} & 7.01^{+0.35}_{-0.35} & 9.34^{+0.41}_{-0.47} \\
-    3.25 & 3.25 & 3.20 & 3.30 & 8.27^{+0.94}_{-1.01} & 11.05^{+1.27}_{-1.17} & 6.06^{+0.35}_{-0.36} & 8.07^{+0.49}_{-0.50} \\
-    3.34 & 3.35 & 3.30 & 3.40 & 12.00^{+2.57}_{-2.55} & 16.10^{+3.44}_{-3.31} & 7.21^{+0.61}_{-0.74} & 9.59^{+0.91}_{-0.93} \\
-    3.44 & 3.45 & 3.40 & 3.50 & 4.47^{+0.52}_{-0.51} & 5.85^{+0.61}_{-0.64} & 4.37^{+0.45}_{-0.47} & 5.73^{+0.56}_{-0.67} \\
-    3.88 & 3.90 & 3.70 & 4.10 & 4.36^{+1.44}_{-1.39} & 5.76^{+1.98}_{-1.84} & 2.54^{+0.44}_{-0.44} & 3.45^{+0.72}_{-0.66} \\
-    4.35 & 4.40 & 4.10 & 4.70 & 4.13^{+2.15}_{-1.95} & 5.40^{+2.60}_{-2.57} & 1.81^{+0.58}_{-0.52} & 2.42^{+0.64}_{-0.68} \\
-    4.92 & 5.10 & 4.70 & 5.50 & 2.51^{+0.89}_{-0.86} & 3.45^{+1.28}_{-1.31} & 0.97^{+0.20}_{-0.18} & 1.29^{+0.25}_{-0.26} \\
-    6.00 & 6.00 & 5.50 & 6.50 & 0.65^{+0.30}_{-0.24} & 0.96^{+0.36}_{-0.37} & 0.21^{+0.04}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
+    0.31$^a$ & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.70^{+0.03}_{-0.03} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
+    0.50$^a$ & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.02}_{-0.02} & 0.58^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
+    0.72 & 0.60 & 0.80 & 1.73^{+0.05}_{-0.05} & 2.30^{+0.07}_{-0.07} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.03} \\
+    0.91 & 0.80 & 1.00 & 2.85^{+0.16}_{-0.16} & 3.81^{+0.21}_{-0.21} & 2.10^{+0.05}_{-0.05} & 2.78^{+0.07}_{-0.06} \\
+    1.10 & 1.00 & 1.20 & 3.72^{+0.10}_{-0.10} & 4.94^{+0.13}_{-0.12} & 2.91^{+0.04}_{-0.04} & 3.87^{+0.05}_{-0.06} \\
+    1.30 & 1.20 & 1.40 & 5.71^{+0.22}_{-0.22} & 7.61^{+0.32}_{-0.32} & 4.47^{+0.09}_{-0.09} & 5.94^{+0.14}_{-0.12} \\
+    1.50 & 1.40 & 1.60 & 7.05^{+0.23}_{-0.24} & 9.32^{+0.29}_{-0.29} & 5.60^{+0.10}_{-0.10} & 7.43^{+0.14}_{-0.13} \\
+    1.71 & 1.60 & 1.80 & 7.72^{+0.16}_{-0.15} & 10.23^{+0.23}_{-0.24} & 6.71^{+0.10}_{-0.10} & 8.90^{+0.13}_{-0.12} \\
+    1.98 & 1.80 & 2.20 & 10.67^{+0.34}_{-0.39} & 14.14^{+0.53}_{-0.53} & 7.93^{+0.13}_{-0.15} & 10.54^{+0.18}_{-0.18} \\
+    2.30$^a$ & 2.20 & 2.40 & 10.21^{+0.23}_{-0.22} & 13.53^{+0.30}_{-0.30} & 8.88^{+0.12}_{-0.12} & 11.80^{+0.16}_{-0.15} \\
+    2.45$^a$ & 2.40 & 2.50 & 8.07^{+0.22}_{-0.22} & 10.71^{+0.33}_{-0.29} & 7.17^{+0.16}_{-0.15} & 9.48^{+0.18}_{-0.17} \\
+    2.55$^a$ & 2.50 & 2.60 & 6.64^{+0.19}_{-0.20} & 8.79^{+0.25}_{-0.24} & 6.21^{+0.13}_{-0.13} & 8.24^{+0.15}_{-0.17} \\
+    2.65$^a$ & 2.60 & 2.70 & 6.55^{+0.14}_{-0.16} & 8.71^{+0.21}_{-0.20} & 6.43^{+0.15}_{-0.15} & 8.56^{+0.21}_{-0.23} \\
+    2.75$^a$ & 2.70 & 2.80 & 7.44^{+0.22}_{-0.18} & 9.92^{+0.31}_{-0.33} & 7.16^{+0.20}_{-0.20} & 9.51^{+0.25}_{-0.29} \\
+    2.85$^a$ & 2.80 & 2.90 & 7.95^{+0.33}_{-0.33} & 10.50^{+0.38}_{-0.37} & 7.50^{+0.26}_{-0.30} & 9.91^{+0.32}_{-0.35} \\
+    2.95$^a$ & 2.90 & 3.00 & 7.95^{+0.36}_{-0.35} & 10.51^{+0.49}_{-0.51} & 6.82^{+0.21}_{-0.19} & 9.07^{+0.27}_{-0.31} \\
+    3.05$^a$ & 3.00 & 3.10 & 7.23^{+0.47}_{-0.39} & 9.59^{+0.60}_{-0.55} & 6.26^{+0.22}_{-0.21} & 8.30^{+0.25}_{-0.28} \\
+    3.15$^a$ & 3.10 & 3.20 & 9.87^{+0.94}_{-1.10} & 13.06^{+1.69}_{-1.55} & 7.00^{+0.37}_{-0.39} & 9.28^{+0.46}_{-0.51} \\
+    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.91}_{-0.90} & 11.04^{+1.27}_{-1.19} & 6.04^{+0.36}_{-0.35} & 8.01^{+0.46}_{-0.48} \\
+    3.34$^a$ & 3.30 & 3.40 & 12.23^{+2.81}_{-2.69} & 16.30^{+3.58}_{-3.28} & 7.21^{+0.64}_{-0.69} & 9.68^{+0.95}_{-0.94} \\
+    3.44$^a$ & 3.40 & 3.50 & 4.44^{+0.43}_{-0.57} & 5.98^{+0.67}_{-0.78} & 4.38^{+0.47}_{-0.49} & 5.77^{+0.52}_{-0.66} \\
+    3.88 & 3.70 & 4.10 & 4.37^{+1.47}_{-1.39} & 5.68^{+1.89}_{-1.76} & 2.53^{+0.43}_{-0.46} & 3.30^{+0.69}_{-0.69} \\
+    4.35 & 4.10 & 4.70 & 4.24^{+2.01}_{-2.12} & 5.33^{+2.42}_{-2.64} & 1.76^{+0.47}_{-0.47} & 2.39^{+0.69}_{-0.58} \\
+    4.92 & 4.70 & 5.50 & 2.60^{+0.93}_{-1.02} & 3.35^{+1.18}_{-1.29} & 0.94^{+0.18}_{-0.17} & 1.29^{+0.28}_{-0.25} \\
+    6.00 & 5.50 & 6.50 & 0.67^{+0.27}_{-0.25} & 0.91^{+0.40}_{-0.38} & 0.21^{+0.04}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
     \hline
   \end{tabular}
+  \begin{minipage}{13.0cm}
+    \textsuperscript{$a$}{Redshift bin considered to be severely affected by systematic errors (open circles in Figure~\ref{fig:e912_2}).
+These bins should be avoided while considering the evolution of emissivities.}
+  \end{minipage}
 \end{table*}
@@
   % Check these values once again.
-  \caption{
-    Comoving emissivities at 912\,\AA\ and 1450\,\AA\ obtained
-    by fitting Equation~\eqref{eqn:e912fit} to the emissivities in the
+  \caption{ Comoving emissivities at 912\,\AA\ and 1450\,\AA\ obtained
+    by fitting Equation~\eqref{eqn:e912fit} to the emissivities in
     selected redshift bins from Table~\ref{tab:emissivity_bins}.
-    Emissivities at $z<0.6$ and at $z>6.5$ are extrapolated assuming our best fits.
-    The derived \ion{H}{i} photoionization rates (\textbf{Cite Eq.})
-    are also given. Emissivity units are
+    Emissivities at $z<0.6$ and at $z>6.5$ are extrapolated assuming
+    our best fits.  The derived \ion{H}{i} photoionization rates
+    (Equation~\ref{eqn:gammapi}) are also given. Emissivity units are
     erg\ s$^{-1}$\ Hz$^{-1}$\ cMpc$^{-3}$, and photoionization rate
-    units are s$^{-1}$. Statistical uncertainties are one-sigma (68.26\%).
-    These values are shown in Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.
-    See Sections~\ref{sec:e912} and \ref{sec:gammahi} for more details.
-    }
+    units are s$^{-1}$. Statistical uncertainties are one-sigma
+    (68.26\%) equal-tailed credibility intervals.  These values are
+    shown in Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.  See
+    Sections~\ref{sec:e912} and \ref{sec:gammahi} for details.  }
   \label{tab:gamma2}

### 2018-07-24 Paper/paper.tex
Update

@@
 \usepackage{siunitx}
-\usepackage{color}
-\definecolor{notecolor}{rgb}{0.8,0,0}
-\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
 \def\lya{Ly$\alpha$~}
@@
        {{Girish Kulkarni$^{1,2}$\thanks{Email: kulkarni@ast.cam.ac.uk},
-           G\'abor Worseck$^{3}$
-           and Joseph F.~Hennawi$^{4}$} \\
+           G\'abor Worseck$^{3,5}$
+           and Joseph F.~Hennawi$^{4,5}$} \\
          $^1$Institute of Astronomy,
@@
          UK \\
-         $^2$Institute f\"ur Physik und Astronomie, Universit\"at
-         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
+         $^2$Institut f\"ur Physik und Astronomie, Universit\"at
+         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, D-14476 Potsdam,
          Germany \\
-         $^3$Department of Physics, Broida Hall, UC Santa Barbara,
-         Santa Barbara, CA 93106-9530, USA}
+         $^4$Department of Physics, Broida Hall, UC Santa Barbara,
+         Santa Barbara, CA 93106-9530, USA\\
+         $^5$Max Planck Institute for Astronomy, K\"onigstuhl 17,
+         D-69117 Heidelberg, Germany}
        \date{Accepted ---. Received ---; in original form ---}
@@
   function from redshifts $z=0$ to $7.5$.  The luminosity function has
-  a double power law form at most redshifts.  The break luminosity
+  a double power law form at all redshifts.  The break magnitude
   brightens rapidly with redshift and the faint end of the luminosity
@@
 also constrains models of galaxy formation \citep{2006ApJ...650...42L,
-  2008MNRAS.385.1846M}.  Finally, thanks to their relative brightness
-and high Lyman-continuum (LyC) escape fractions, the luminosity
-function of AGN determines their contribution to the radiation
-background that influences the temperature and ionization state of the
-intergalactic medium (IGM), possibly even primarily driving hydrogen
-and helium reionization in the last twelve billion years
+  2008MNRAS.385.1846M}.  Finally, thanks to their brightness and high
+Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
+determines their contribution to the ultraviolet background that
+governs the temperature and ionization state of the intergalactic
+medium (IGM), possibly even primarily driving hydrogen and helium
+reionization 
 \citep{2012ApJ...746..125H, 2015AA...578A..83G, 2017ApJ...847L..15O,
@@
 redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
-novel X-ray/NIR selection criterion.  This finding suggested that if
-100\% LyC escape fraction is assumed AGN brighter than $M_{1450}=-18$
-can potentially produce all of the metagalactic hydrogen
-photoionization rate inferred from the \lya forest at $4<z<6$, despite
-the fact that these AGN are fainter than the brightest star-forming
-galaxies at these redshifts.  (The UV luminosity function of galaxies
-at $z=6$ has characteristic magnitude $M^*_{1450}\sim -20$.)  A
-significant presence of AGN at high redshift ($z\sim 6$) and a
-dominant contribution of AGN to reionization is appealing as the LyC
-escape fraction of galaxies is uncertain.  High-redshift galaxies down
-to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
-10^{-3}L^*_\mathrm{galaxies}$) at $z=6$ \citep{2017ApJ...835..113L}
-and redshifts up to $z=11.1$ \citep{2016ApJ...819..129O} have now been
-reported.  But the escape of LyC photons has been measured in only a
-few comparatively bright ($L>0.5L^*_\mathrm{galaxies}$) galaxies at
-relatively low redshifts ($z < 4$).  The escape fraction in these
-galaxies reveals a broad distribution from less than 2\% to more than
-80\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
-  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
-  2017MNRAS.468..389J, 2018arXiv180506071S, 2018arXiv180601741F,
-  2018arXiv180511621M, 2018arXiv180303655C}, but the average escape
-fraction is typically lower than 20\%.  Statistical constraints from
-\HI\ column density measurements in gamma-ray burst (GRB) afterglow
-spectra suggest an even lower escape fraction of 0.5\%
-\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
-This is a challenge for reionization models, which require an escape
-fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
-\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
-An enhanced incidence of high-redshift AGN may also be consistent with
-the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
-of galaxies relative to a Schechter function
-\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
-  2015MNRAS.452.1817B} and the hard spectra of these galaxies
-\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.
-Finally, AGN may also provide a natural explanation for the large
-scatter in the \lya opacity between different quasar sightlines close
-to redshift $z=6$ \citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.
-These opacity fluctuations extend to substantially larger scales
-($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxies-dominated
-reionization models (\citealt{2015MNRAS.453.2943C}; although see
+novel X-ray/NIR selection criterion.  This finding suggested that AGN
+brighter than $M_{1450}\sim -18$ can account for all of the
+metagalactic hydrogen photoionization rate inferred from the \lya
+forest at $4<z<6$, despite the fact that these AGN are fainter than
+the brightest star-forming galaxies at these redshifts.  (The UV
+luminosity function of galaxies at $z=6$ has characteristic magnitude
+$M^*_{1450}\sim -20$.)  A significant presence of AGN at high redshift
+($z\sim 6$) and a dominant contribution of AGN to reionization is
+appealing as the LyC escape fraction of galaxies is uncertain, whereas
+for AGN it is close to 100\% \citep{2014ApJ...794...75S,
+  2015MNRAS.449.4204L, 2016A&A...585A..48G}.  High-redshift galaxies
+down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ at $z=6$
+\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
+\citep{2016ApJ...819..129O} have now been reported.  But the escape of
+LyC photons has been measured in only a few comparatively bright
+($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
+($z < 4$).  The escape fraction in these galaxies reveals a broad
+distribution from less than 2\% to more than 80\%
+\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
+  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
+  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
+  2018arXiv180303655C}, but the average escape fraction is typically
+lower than 20\%.  Statistical constraints from \HI\ column density
+measurements in gamma-ray burst (GRB) afterglow spectra suggest an
+even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
+  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
+reionization models, which require an escape fraction of about 20\% in
+galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
+  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
+high-redshift AGN may also be consistent with the shallow bright-end
+slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
+a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
+  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
+these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
+  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
+explanation for the large scatter in the \lya opacity between
+different quasar sightlines close to redshift $z=6$
+\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
+fluctuations extend to substantially larger scales ($\gtrsim 50\,
+h^{-1}$cMpc) than expected in galaxy-dominated reionization models
+(\citealt{2015MNRAS.453.2943C}; although see
 \citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
@@
 model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
-standard scenario \citep{2012ApJ...746..125H}.  Such early
-\HeII\ reionization will also result in higher IGM temperatures due to
-the associated photoheating.  \citet{2017MNRAS.468.4691D} found that
-the temperature of the IGM at mean density is twice as much in
-AGN-dominated reionization models as the standard models at
-$z=3.5$--$5$, in conflict with constraints from the \lya forest.  This
-inconsistency could be avoided by postulating a reduced escape
-fraction of \HeII-ionizing photons in AGN, but it is difficult to
-reconcile this with a unit escape fraction of hydrogen-ionizing
-photons that is required to explain the Ly$\alpha$ opacity
-fluctuations.  Further arguments against AGN-dominated reionization
-have been presented by \citet{2016MNRAS.459.2299F}, who analysed the
-simulations of metal-line absorbers at $z\sim 6$.
+conventional scenario with sharply dropping AGN emissivity at $z>2$
+\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
+result in higher IGM temperatures due to the associated photoheating.
+\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
+mean density is twice as much in AGN-dominated reionization models as
+the standard models at $z=3.5$--$5$, in conflict with constraints from
+the \lya forest.  This inconsistency could be avoided by postulating a
+reduced escape fraction of \HeII-ionizing photons in AGN, but it is
+difficult to reconcile this with a unit escape fraction of
+hydrogen-ionizing photons that is required to explain the Ly$\alpha$
+opacity fluctuations.  Further arguments against AGN-dominated
+reionization have been presented by \citet{2016MNRAS.459.2299F}, who
+analysed the simulations of metal-line absorbers at $z\sim 6$.
 \citet{2016MNRAS.459.2299F} find that in their cosmological radiation
@@
 many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
-C~\textsc{ii} at $z\sim 6$.  (However, note that these simulations
-assume a $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
-\citep{2002ApJ...565..773T}, which is somewhat harder than recent
-measurements ($L_\nu\propto\nu^{-1.7}$) by
-\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} found that,
-relative to the the standard model \citep{2012ApJ...746..125H}, the
-observed N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
-measurements seem to require a harder and more intense $>4$~Ry
-background.)  Finally, comparing the \citet{2015AA...578A..83G} sample
-to X-ray-selected quasar data at $z=0$--$6$,
-\citet{2017MNRAS.465.1915R} argued that the faint end of the AGN UV
-luminosity function at $z\sim 6$ is probably shallower that that
-reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
-argue that the apparent contradiction with the results of
-\citet{2015AA...578A..83G} could be explained by contamination from
-the host galaxies for faint AGN \citep[see
+C~\textsc{ii} at $z\sim 6$.  Finally, comparing the
+\citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
+$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
+the AGN UV luminosity function at $z\sim 6$ is probably shallower that
+that reported by \citet{2015AA...578A..83G}.
+\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
+the results of \citet{2015AA...578A..83G} could be explained by
+contamination from the host galaxies for faint AGN \citep[see
   also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.
 
-A straightforward way towards a more robust understanding of AGN
-contribution to UV background is to determine the evolution of the AGN
-UV luminosity function.  To this end, several estimates of the
-luminosity function at various redshifts have been published in the
-last decade \citep{2009A&A...507..781S, 2011ApJ...728L..26G,
-  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
-  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
-  2017ApJ...847L..15O, 2018PASJ...70S..34A}.  However, many of these
-inferences of the luminosity function suffer from inconsistencies
-arising from inhomogeneous selection and mixing of AGN data.  Some of
-the data sets analysed in these studies consist of photometric
-samples, which is likely to increase sample contamination.  In some
-studies, distinct data sets binned differently in redshift and
-magnitudes were inhomogeneously combined.  Some authors imposed
-restricted priors on parameters while fitting luminosity function
-models, e.g., by fixing luminosity function slopes to certain values,
-which may bias the result.  Finally, some studies arbitrarily excluded
-certain data sets.  This has resulted in a large scatter in the
-inferred high-redshift hydrogen-ionizing AGN emissivity between
-various recent studies.  For instance, there is an order of magnitude
-scatter between various estimates of the hydrogen-ionizing AGN
-emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
-  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
-  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
-aim in this paper is to address this issue, by constructing an AGN
-sample with robust redshift and completeness estimates and homogeneous
-assumptions of the cosmology and intrinsic AGN spectrum.  After
-constructing such a sample, we derive the UV luminosity function of
-AGN from redshift $z=0$--$7$ and estimate the AGN contribution to the
-UV background.  We discuss our sample construction in
-Section~\ref{sec:sample}.  Our derived luminosity functions are
-presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
-our inference of the AGN contribution to hydrogen and helium
-reionization.  We summarise our findings in Section~\ref{sec:conc}.
+The premier way towards a more robust understanding of the AGN
+contribution to the UV background is to determine the evolution of the
+AGN UV luminosity function across cosmic time.  To this end, numerous
+measurements of the luminosity function at various redshifts have been
+published in the last decade \citep{2009A&A...507..781S,
+  2011ApJ...728L..26G, 2012ApJ...755..169M, 2013ApJ...773...14R,
+  2013ApJ...768..105M, 2015AA...578A..83G, 2016ApJ...833..222J,
+  2016ApJ...829...33Y, 2017ApJ...847L..15O, 2018PASJ...70S..34A}.
+However, many of these inferences suffer from inconsistencies arising
+from inhomogeneous selection and mixing of AGN data.  Some of the data
+sets analysed in these studies consist of photometric samples, which
+is likely to increase sample contamination.  In some studies, distinct
+data sets binned differently in redshift and magnitudes were
+inhomogeneously combined.  Some authors imposed restricted priors on
+parameters while fitting luminosity function models, e.g., by fixing
+luminosity function slopes to certain values, which may bias the
+result.  Finally, some studies arbitrarily excluded certain data sets.
+This has resulted in a large scatter in the inferred high-redshift
+hydrogen-ionizing AGN emissivity between various recent studies.  For
+instance, there is an order of magnitude scatter between various
+estimates of the hydrogen-ionizing AGN emissivity at $z=5$--$6$
+\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
+  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
+  2017ApJ...847L..15O}.  Our aim in this paper is to address this
+issue, by constructing an AGN sample with robust redshift and
+completeness estimates and homogeneous assumptions of the cosmology
+and intrinsic AGN spectrum.  After constructing such a sample, we
+derive the UV luminosity function of AGN from redshift $z=0$--$7.5$
+and estimate the AGN contribution to the UV background.  We discuss
+our sample construction in Section~\ref{sec:sample}.  Our derived
+luminosity functions are presented in Section~\ref{sec:lf}.
+Section~\ref{sec:reion} presents our inference of the AGN contribution
+to the \nHI-ionizing UV background and \HeII\ reionization history.
+We summarise our findings in Section~\ref{sec:conc}.
 
@@
 
-\section{Homogenised Quasar Sample}
+\section{Homogenised AGN Sample}
 \label{sec:sample}
@@
 analysis by computing binned estimates of the luminosity function as a
-function of magnitude in several redshift intervals.  We then perform
-parametric maximum-likelihood fits of the luminosity function in the
-individual redshift bins, examine the resulting parameters as a
+function of magnitude in several narrow redshift intervals.  We then
+perform parametric maximum-likelihood fits of the luminosity function
+in the individual redshift bins, examine the resulting parameters as a
 function of redshift, and attempt a joint fit in magnitude and
@@
 
-From Figure~\ref{fig:mosaic} we see that the distribution of luminosity
-function values in each redshift bin are suggestive of a double power
-law form for the QLF.  We will fit such a form below. 
+From Figure~\ref{fig:mosaic} we see that the distribution of
+luminosity function values in each redshift bin are suggestive of a
+double power law form for the QLF.  We will fit such a form below.
 However, in several redshift bins we note a suspicious decline of the
-luminosity function at the faint limit of several surveys, for example in
-the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and $z\sim 4$.
-The inconsistency between the SDSS faint end and the deeper
-2SLAQ QLF indicates that the SDSS selection function is
-systematically overestimated at its magnitude limit.
-At $z\sim 4$ the SDSS faint end QLF is inconsistent with the fainter
-\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
-`by eye', discard the contributing quasars from our analysis, and set their
-selection function values to zero.
-The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
-open circles.
+luminosity function at the faint limit of several surveys, for example
+in the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and
+$z\sim 4$.  The inconsistency between the SDSS faint end and the
+deeper 2SLAQ QLF indicates that the SDSS selection function is
+systematically overestimated at its magnitude limit.  At $z\sim 4$ the
+SDSS faint end QLF is inconsistent with the fainter
+\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins by
+eye, discard the contributing quasars from our analysis, and set their
+selection function values to zero.  The discarded magnitude bins are
+shown in Figure~\ref{fig:mosaic} by open circles.
 
@@
     from the redshift bins shown in Figure~\ref{fig:mosaic}.  Vertical
-    error bars show one-sigma (68.26\%) statistical uncertainties,
-    whereas horizontal error bars show widths of the redshift bins.
-    We identify the general evolutionary trends of each of these
-    parameters from the bins shown by the filled symbols.  The open
-    symbols show bins that appear to be offset from these trends,
-    likely due to unknown systematic errors.  The open circles at
-    $2.2<z<3.5$ show the BOSS sample, while the bins at $z < 0.6$
-    contain AGN from the SDSS and 2SLAQ data sets.  See
-    Section~\ref{sec:bins} for further details.}
+    error bars show one-sigma (68.26\%) statistical uncertainties
+    derived from the posterior distribution, whereas horizontal error
+    bars show widths of the redshift bins.  We identify the general
+    evolutionary trends of each of these parameters from the bins
+    shown by the filled symbols.  The open symbols show bins that
+    appear to be offset from these trends, likely due to 
+    systematic errors.  The open circles at $2.2<z<3.5$ show the BOSS
+    sample, while the bins at $z < 0.6$ contain AGN from the SDSS and
+    2SLAQ data sets.}
   \label{fig:evoln}
@@
 
-In each redshift bin, we model the quasar
-luminosity function as a double power law 
+In each redshift bin, we model the QLF as a double power law
 \citep[e.g.][]{1988MNRAS.235..935B}
@@
 posterior median as our fiducial model fit, and the 68.26\%
-equal-tailed credible interval as the uncertainty on $\phi$.  The
-resultant parameter values are listed in Table~\ref{tab:bins}.
-Consistent with previous studies, the double power law model provides
-an excellent description of the luminosity function model over almost
-the complete range of redshifts spanned by the data.  It is only in
-the highest redshift bin ($z=5.5$--$6.5$) that the data seem to favour
-a single power law.  In this bin, the resultant posterior distribution
-of the break magnitude $M_*$ is bimodal with favoured values at the
-faint ($M_*>-18$) and bright end of the data ($M_*<-30$).  While in
-the literature $z\sim 6$ quasars have been assumed to lie on the
-bright end of the luminosity function
-\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
-function at lower redshifts ($z<5.5$) suggests that these AGN should
-instead be understood to describe the faint-end of a double power law.
-As we discuss below, $M_*$ gets progressively brighter with redshift.
-Therefore, after inspecting the data at lower redshifts, we use
-restricted priors in the $z=5.5$--$6.5$ redshift bin in order to avoid
-bimodal distributions.  In this bin, we restrict the bright-end slope
-$\alpha$ to values less than $-4$, which is equivalent to forcing
-$M_*$ to be at the bright end of the data.  Other parameters continue
-to have wide uniform priors.  This also illustrates the importance of
-analysing the evolution of the QLF with redshift.
+equal-tailed credible interval as the uncertainty on $\phi$.  (We
+adopt similar definitions for the derived quantities.)  The resultant
+parameter values are listed in Table~\ref{tab:bins}.  Consistent with
+previous studies, the double power law model provides an excellent
+description of the luminosity function model over almost the complete
+range of redshifts spanned by the data.  It is only in the highest
+redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
+power law.  In this bin, the resultant posterior distribution of the
+break magnitude $M_*$ is bimodal with favoured values at the faint
+($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
+literature $z\sim 6$ quasars have been assumed to lie on the bright
+end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
+comparison with the luminosity function at lower redshifts ($z<5.5$)
+suggests that these AGN should instead be understood to describe the
+faint-end of a double power law.  As we discuss below, $M_*$ gets
+progressively brighter with redshift.  Therefore, after inspecting the
+data at lower redshifts, we use restricted priors in the
+$z=5.5$--$6.5$ redshift bin in order to avoid bimodal distributions.
+In this bin, we restrict the bright-end slope $\alpha$ to values less
+than $-4$, which is equivalent to forcing $M_*$ to be at the bright
+end of the data.  Other parameters continue to have wide uniform
+priors.  This also illustrates the importance of analysing the
+evolution of the QLF with redshift.
 
@@
 luminosity function $\phi_*$ evolves moderately from $z=0$ to $z\sim
-3$ and then drops by six orders of magnitude to about
+3$ and then drops by more than five orders of magnitude to about
 $10^{-12}$\,cMpc$^{-3}$mag$^{-1}$ at $z\sim 7$.  The bright end slope
@@
 luminosity functions \citep[e.g.,][]{2007ApJ...654..731H}.  Such
-``global'' models of the luminosity function evolution are useful as
+``global'' models of the QLF evolution are useful as
 they give a continuous description of the luminosity function.  This
@@
     from Figure~\ref{fig:evoln}.  Redshift bins deemed to be affected
-    by systematics and removed from the global analysis are shown in
-    grey.  In each panel, the solid curves and shaded regions show the
-    three derived global models with one-sigma uncertainties.  Model~1
-    provides a better fit, but requires a rapid change in the
-    faint-end slope at $z\sim 3.5$.}
+    by systematics and removed from the global analysis are shown by
+    the grey open circles.  In each panel, the solid curves and shaded
+    regions show the three derived global models with one-sigma
+    uncertainties.  Model~1 provides a better fit, but requires a
+    rapid change in the faint-end slope at $z\sim 3.5$.}
   \label{fig:evoln_global}
@@
 $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
-spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
+spectroscopic data exist, $M_*<-21$, the number density of AGN peaks
 at a slightly lower redshift.  However, the difference between our
@@
 %% those objects on here as well.
-This is result of the steep faint-end slope at high
+This results from the steep faint-end slope at high
 redshifts combined with the rapid brightening of the break luminosity.
@@
   \end{center}
-  \caption{The 912~\AA\ emissivity of AGN assuming 100\% escape
-    fraction down to a limiting magnitude for a luminosity function
-    integration limit of $M_{1450}=-18$ (left panel) and
-    $M_{1450}=-21$ (right panel).  Black filled circles with error
-    bars in both panels show the emissivity determinations in redshift
-    bin deemed to have low systematic errors.  Open circles show
-    emissivities for redshift bins that we remove from analysis due to
-    high systematic errors.  Solid red curves in both panels show the
-    derived posterior median emissivity evolution model, with the
-    shaded area showing the one-sigma (68.26\%) uncertainty.  Also
-    shown for comparison in both panels are models by \citet[pentagon
-      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
+  \caption{The 912~\AA\ emissivity of AGN down to a limiting magnitude
+    for a luminosity function integration limit of $M_{1450}=-18$
+    (left panel) and $M_{1450}=-21$ (right panel).  Black filled
+    circles with error bars in both panels show the emissivity
+    determinations in redshift bin deemed to have low systematic
+    errors.  Open circles show emissivities for redshift bins that we
+    remove from analysis due to high systematic errors.  Solid red
+    curves in both panels show the derived posterior median emissivity
+    evolution model, with the shaded area showing the one-sigma
+    (68.26\%) uncertainty.  Also shown for comparison in both panels
+    are models by \citet[pentagon symbol]{2009A&A...507..781S},
+    \citet[star]{2012ApJ...755..169M},
     \citet[square]{2015AA...578A..83G},
@@
   \nu^{-0.61} & \text{if}~\lambda\ge 912~\text{\AA},\\
-  \nu^{-1.70} & \text{if}~600~\text{\AA}<\lambda<912~\text{\AA}                
+  \nu^{-1.70} & \text{if}~\lambda<912~\text{\AA}                
   \end{cases}
@@
 We deem the latter convention to be physically unfounded, because (i)
-the customary QLF double power-law parameterization lacks a deeper
-physical meaning, (ii) $M_*$ decreases by more than five magnitudes
-with redshift (Figure~\ref{fig:evoln}, see also
+the customary QLF double power-law parameterization thus far lacks a
+deeper physical meaning, (ii) $M_*$ decreases by more than five
+magnitudes with redshift (Figure~\ref{fig:evoln}, see also
 \citealt{2013ApJ...768..105M} and \citealt{2016ApJ...829...33Y}), and
@@
 $\alpha=-2.8$ which had been determined by \citet{2016ApJ...833..222J}
-from a single power-law fit to the bright end of the QLF.  Our
+from a single power-law fit to the QLF.  Our
 bright-end slopes are inconsistent with such high values at all
@@
   \end{center}
-  \caption{AGN contribution to the hydrogen photoionisation rate,
-    assuming unit escape fraction, when the AGN luminosity function is
-    integrated down to $M_{1450}=-21$ (blue curve and shaded region)
-    and $M_{1450}=-18$ (red curve and shaded region).  The shaded
-    regions show the one-sigma (68.26\%) uncertainty.  Also shown are
-    the photoionization rate measurements by \citet[filled
-      circles]{2013MNRAS.436.1023B}, \citet[inverted
+  \caption{AGN contribution to the hydrogen photoionisation rate, when
+    the AGN luminosity function is integrated down to $M_{1450}=-21$
+    (blue curve and shaded region) and $M_{1450}=-18$ (red curve and
+    shaded region).  The shaded regions show the one-sigma (68.26\%)
+    uncertainty.  Also shown are the photoionization rate measurements
+    by \citet[filled circles]{2013MNRAS.436.1023B}, \citet[inverted
       triangles]{2011MNRAS.412.2543C},
@@
     \citet[pentagon]{2014ApJ...789L..32K}, and
-    \citet[circle]{2017MNRAS.467.3172G}. Note that we use the the
+    \citet[circle]{2017MNRAS.467.3172G}. Note that we use the 
     \HI\ column density distribution model from

### 2018-07-25 Paper/paper.tex
Update

@@
   holes.  Recent inferences of the luminosity function suffer from
-  inconsistencies arising from inhomogeneous selection and mixing of
+  inconsistencies arising from inhomogeneous selection and analysis of
   AGN data.  We address this problem by constructing a sample of more
@@
   systems.  Using this sample, we derive the AGN UV luminosity
-  function from redshifts $z=0$ to $7.5$.  The luminosity function has
-  a double power law form at all redshifts.  The break magnitude
-  brightens rapidly with redshift and the faint end of the luminosity
-  function steepens.  In spite of this steepening, the contribution of
-  AGN to the hydrogen photoionization rate at $z\sim 6$ is
-  subdominant, although it can be non-negligible if these luminosity
-  functions hold down to $M_{1450}=-18$.  Under reasonable
-  assumptions, AGN can reionize \HeII\ by redshift $z=2.9$.  At low
-  redshifts ($z<0.5$), AGN can produce about half of the hydrogen
-  photoionization rate inferred from the statistics of \HI\ absorption
-  lines in the IGM.  Our global analysis of the luminosity function
-  also reveals important systematic errors in the data, particularly
-  at $z=2.2$--$3.5$, which need to be addressed in future in order to
+  function from redshift $z=0$ to $7.5$.  The luminosity function has
+  a double power law form at all redshifts.  The break magnitude $M_*$
+  of the AGN luminosity function shows a steep brightening from
+  $M_*\sim -24$ at $z=0.7$ to $M_*\sim -29$ at $z=6$.  The faint-end
+  slope $\beta$ significantly steepens from $-1.7$ at $z<2.2$ to
+  $-2.4$ at $z\simeq 6$.  In spite of this steepening, the
+  contribution of AGN to the hydrogen photoionization rate at $z\sim
+  6$ is subdominant ($<3$\%), although it can be non-negligible ($\sim
+  10$\%) if these luminosity functions hold down to $M_{1450}=-18$.
+  Under reasonable assumptions, AGN can reionize \HeII\ by redshift
+  $z=2.9$.  At low redshifts ($z<0.5$), AGN can produce about half of
+  the hydrogen photoionization rate inferred from the statistics of
+  \HI\ absorption lines in the IGM.  Our global analysis of the
+  luminosity function also reveals important systematic errors in the
+  data, particularly at $z=2.2$--$3.5$, which need to be addressed and
+  incorporated in the AGN selection function in future in order to
   improve our results.  We make various fitting functions, luminosity
@@
 luminosity function of galaxies at $z=6$ has characteristic magnitude
-$M^*_{1450}\sim -20$.)  A significant presence of AGN at high redshift
-($z\sim 6$) and a dominant contribution of AGN to reionization is
-appealing as the LyC escape fraction of galaxies is uncertain, whereas
-for AGN it is close to 100\% \citep{2014ApJ...794...75S,
-  2015MNRAS.449.4204L, 2016A&A...585A..48G}.  High-redshift galaxies
-down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ at $z=6$
-\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
-\citep{2016ApJ...819..129O} have now been reported.  But the escape of
-LyC photons has been measured in only a few comparatively bright
-($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
-($z < 4$).  The escape fraction in these galaxies reveals a broad
-distribution from less than 2\% to more than 80\%
-\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
-  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
-  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
-  2018arXiv180303655C}, but the average escape fraction is typically
-lower than 20\%.  Statistical constraints from \HI\ column density
-measurements in gamma-ray burst (GRB) afterglow spectra suggest an
-even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
-  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
-reionization models, which require an escape fraction of about 20\% in
-galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
-  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
-high-redshift AGN may also be consistent with the shallow bright-end
-slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
-a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
-  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
-these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
-  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
+$M^*_{1450}\sim -20$ \citep{2015ApJ...803...34B}.)  A significant
+presence of AGN at high redshift ($z\sim 6$) and a dominant
+contribution of AGN to reionization is appealing as the LyC escape
+fraction of galaxies is uncertain, whereas for AGN it is close to
+100\% \citep{2014ApJ...794...75S, 2015MNRAS.449.4204L,
+  2016A&A...585A..48G}.  High-redshift galaxies down to rest-frame UV
+magnitude $M_\mathrm{UV}=-12.5$ at $z=6$ \citep{2017ApJ...835..113L}
+and redshifts up to $z=11.1$ \citep{2016ApJ...819..129O} have now been
+reported.  But the escape of LyC photons has been measured in only a
+few comparatively bright ($L>0.5L^*_\mathrm{galaxies}$) galaxies at
+relatively low redshifts ($z < 4$).  The escape fraction in these
+galaxies reveals a broad distribution from less than 2\% to more than
+80\% \citep{2010ApJ...725.1011V, 2014Sci...346..216B,
+  2015ApJ...810..107M, 2016A&A...585A..48G, 2016Natur.529..178I,
+  2016ApJ...826L..24S, 2017MNRAS.468..389J, 2018arXiv180506071S,
+  2018arXiv180601741F, 2018arXiv180511621M, 2018arXiv180303655C,
+  2018MNRAS.478.4851I, 2018MNRAS.474.4514I}, but the average escape
+fraction is typically lower than 20\%.  Statistical constraints from
+\HI\ column density measurements in gamma-ray burst (GRB) afterglow
+spectra suggest an even lower escape fraction of 0.5\%
+\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
+This is a challenge for reionization models, which require an escape
+fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
+\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
+An enhanced incidence of high-redshift AGN may also be consistent with
+the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
+of galaxies relative to a Schechter function
+\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
+  2015MNRAS.452.1817B} and the hard spectra of these galaxies
+\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S,
+  2017ApJ...851...40L}.  Finally, AGN may also provide a natural
 explanation for the large scatter in the \lya opacity between
 different quasar sightlines close to redshift $z=6$
-\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
-fluctuations extend to substantially larger scales ($\gtrsim 50\,
-h^{-1}$cMpc) than expected in galaxy-dominated reionization models
-(\citealt{2015MNRAS.453.2943C}; although see
+\citep{2015MNRAS.447.3402B, 2018arXiv180208177B, 2018arXiv180704229E}.
+These opacity fluctuations extend to substantially larger scales
+($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxy-dominated
+reionization models (\citealt{2015MNRAS.453.2943C}; although see
 \citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
@@
 \citet{2018MNRAS.473.1416M} pointed out that an enhanced number
-density of AGN at $z\sim 6$ can lead to a much earlier
-\HeII\ reionization (see also \citealt{2017MNRAS.471..255K}).  For
+density of AGN at $z\sim 6$ can lead to a \HeII\ reionization that
+occurs much earlier than indicated by the observed evolution of
+\HeII\ IGM opacity \citep{2011ApJ...733L..24W, 2016ApJ...825..144W}
+and the evolution of the IGM temperature \citep{2011MNRAS.410.1096B,
+  2014MNRAS.441.1916B} (see also \citealt{2017MNRAS.471..255K}).  For
 instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
@@
 the AGN UV luminosity function at $z\sim 6$ is probably shallower that
-that reported by \citet{2015AA...578A..83G}.
-\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
-the results of \citet{2015AA...578A..83G} could be explained by
-contamination from the host galaxies for faint AGN \citep[see
+reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
+argue that the apparent contradiction with the results of
+\citet{2015AA...578A..83G} could be explained by contamination from
+the host galaxies for faint AGN \citep[see
   also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.
-
-The premier way towards a more robust understanding of the AGN
-contribution to the UV background is to determine the evolution of the
-AGN UV luminosity function across cosmic time.  To this end, numerous
-measurements of the luminosity function at various redshifts have been
-published in the last decade \citep{2009A&A...507..781S,
-  2011ApJ...728L..26G, 2012ApJ...755..169M, 2013ApJ...773...14R,
-  2013ApJ...768..105M, 2015AA...578A..83G, 2016ApJ...833..222J,
-  2016ApJ...829...33Y, 2017ApJ...847L..15O, 2018PASJ...70S..34A}.
-However, many of these inferences suffer from inconsistencies arising
-from inhomogeneous selection and mixing of AGN data.  Some of the data
-sets analysed in these studies consist of photometric samples, which
-is likely to increase sample contamination.  In some studies, distinct
-data sets binned differently in redshift and magnitudes were
-inhomogeneously combined.  Some authors imposed restricted priors on
-parameters while fitting luminosity function models, e.g., by fixing
-luminosity function slopes to certain values, which may bias the
-result.  Finally, some studies arbitrarily excluded certain data sets.
-This has resulted in a large scatter in the inferred high-redshift
-hydrogen-ionizing AGN emissivity between various recent studies.  For
-instance, there is an order of magnitude scatter between various
-estimates of the hydrogen-ionizing AGN emissivity at $z=5$--$6$
-\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
-  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
-  2017ApJ...847L..15O}.  Our aim in this paper is to address this
-issue, by constructing an AGN sample with robust redshift and
-completeness estimates and homogeneous assumptions of the cosmology
-and intrinsic AGN spectrum.  After constructing such a sample, we
-derive the UV luminosity function of AGN from redshift $z=0$--$7.5$
-and estimate the AGN contribution to the UV background.  We discuss
-our sample construction in Section~\ref{sec:sample}.  Our derived
-luminosity functions are presented in Section~\ref{sec:lf}.
-Section~\ref{sec:reion} presents our inference of the AGN contribution
-to the \nHI-ionizing UV background and \HeII\ reionization history.
-We summarise our findings in Section~\ref{sec:conc}.
-
-We assume a flat cosmology with density parameters
-$\left(\Omega_\mathrm{m},\Omega_\Lambda\right)=\left(0.3,0.7\right)$
-and a Hubble constant $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$. Comoving
-distances are given explicitly in comoving Mpc (cMpc). Magnitudes
-are reported in the AB system \citep{1983ApJ...266..713O}, and
-observed magnitudes are point spread function (PSF) magnitudes
-\citep{2002AJ....123..485S} corrected for Galactic extinction
-\citep{1998ApJ...500..525S} unless otherwise noted.
-Our homogenised sample (Section~\ref{sec:sample}) uses absolute
-monochromatic AB magnitudes at a rest frame wavelength of 1450\,\AA.
 
@@
 \end{figure*}
+
+The premier way towards a more robust understanding of the AGN
+contribution to the UV background is to determine the evolution of the
+AGN UV luminosity function across cosmic time.  To this end, numerous
+measurements of the luminosity function at various redshifts have been
+published in the last decade \citep{2009A&A...507..781S,
+  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
+  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
+  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
+  2016A&A...587A..41P, 2017ApJ...847L..15O, 2018PASJ...70S..34A,
+  2018AJ....155..131M}.  However, many of these inferences suffer from
+inconsistencies arising from inhomogeneous selection and analysis of AGN
+data.  Some of the data sets analysed in these studies consist of
+photometric samples, which is likely to increase sample contamination.
+In some studies, distinct data sets binned differently in redshift and
+magnitudes were inhomogeneously combined.  Some authors imposed
+restricted priors on parameters while fitting luminosity function
+models, e.g., by fixing luminosity function slopes to certain values,
+which may bias the result.  Finally, some studies arbitrarily excluded
+certain data sets.  This has resulted in a large scatter in the
+inferred high-redshift hydrogen-ionizing AGN emissivity between
+various recent studies.  For instance, there is an order of magnitude
+scatter between various estimates of the hydrogen-ionizing AGN
+emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
+  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
+  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
+aim in this paper is to address this issue, by constructing an AGN
+sample with robust redshift and completeness estimates and homogeneous
+assumptions of the cosmology and intrinsic AGN spectrum.  After
+constructing such a sample, we derive the UV luminosity function of
+AGN from redshift $z=0$--$7.5$ and estimate the AGN contribution to
+the UV background.  We discuss our sample construction in
+Section~\ref{sec:sample}.  Our derived luminosity functions are
+presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
+our inference of the AGN contribution to the \nHI-ionizing UV
+background and \HeII\ reionization history.  We summarise our findings
+in Section~\ref{sec:conc}.
+
+We assume a flat cosmology with density parameters
+$\left(\Omega_\mathrm{m},\Omega_\Lambda\right)=\left(0.3,0.7\right)$
+and a Hubble constant $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$. Comoving
+distances are given explicitly in comoving Mpc (cMpc). Magnitudes
+are reported in the AB system \citep{1983ApJ...266..713O}, and
+observed magnitudes are point spread function (PSF) magnitudes
+\citep{2002AJ....123..485S} corrected for Galactic extinction
+\citep{1998ApJ...500..525S} unless otherwise noted.
+Our homogenised sample (Section~\ref{sec:sample}) uses absolute
+monochromatic AB magnitudes at a rest frame wavelength of 1450\,\AA.
 
@@
 here in modified and homogenised form (see Section~\ref{sect:datahom}
-and Appendix~\ref{sec:code}).
+and Appendix~\ref{sec:code})\footnote{These data and the code for
+  deriving the luminosity functions are available on
+  \url{https://github.com/gkulkarni/QLF}.  The data will also be made
+  available on CDS upon acceptance of this manuscript for
+  publication.}.
 
@@
 $f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
-\citep{2006AJ....131.2766R}. The BOSS colour-selected sample \citep{2013ApJ...773...14R} contains
-quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$, and we adopted
-$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
+\citep{2006AJ....131.2766R}. The BOSS colour-selected sample
+\citep{2013ApJ...773...14R} contains quasars with
+$f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$, and we adopted
+$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}
+f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
 presented two area-specific photometric selection functions due to
@@
 Figures~5 and 7), resulting in
-$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
-We obtained a rough estimate of the \citet{2015AA...578A..83G}
-selection function by comparing the corrected and observed QLFs,
-i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$
-(see their Table~3).  Finally, for the three $z>6.5$ quasars we
-assumed a selection function of unity in a range of $z$ and $M_{1450}$
-estimated by the respective survey teams (private communication).
+$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}
+\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.  We obtained a
+rough estimate of the \citet{2015AA...578A..83G} selection function by
+comparing the corrected and observed QLFs, i.e.\ taking
+$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
+Table~3).  Finally, for the three $z>6.5$ quasars we assumed a
+selection function of unity in a range of $z$ and $M_{1450}$ estimated
+by the respective survey teams (private communication).
 
@@
   bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the binned luminosity
-    %% JFH Notation error here. 
 function as \citep{2000MNRAS.311..433P}
@@
 \end{equation}
-with four free parameters: (i) the amplitude $\phi_*$, (ii) the break magnitude $M_*$,
-(iii)  the bright-end slope $\alpha$, and (iv) the faint-end slope $\beta$.
-%%GW: Maybe give the range of the uniform priors.
-%% JFH SOmewhere indicate taht this procedure of ubninned LF estimates is standard practice. 
-%% GW: Agreed. Maybe add references to Marshall et al. and other seminal papers further up in the text?
-By assuming broad, uniform priors, we obtain posterior probability
-distributions for these parameters using the Markov Chain Monte Carlo technique \citep[MCMC, e.g.,][]{jaynes}.
-The joint posterior probability distribution of the model parameters
-is then written as
+with four free parameters: (i) the amplitude $\phi_*$, (ii) the break
+magnitude $M_*$, (iii) the bright-end slope $\alpha$, and (iv) the
+faint-end slope $\beta$.  By assuming broad, uniform priors, we obtain
+posterior probability distributions for these parameters using the
+Markov Chain Monte Carlo technique \citep[MCMC, e.g.,][]{jaynes}.  The
+joint posterior probability distribution of the model parameters is
+then written as
 \begin{multline}
@@
   z_\mathrm{max})$.  We use a uniform prior distribution $p(\phi_*,
-  M_*, \alpha, \beta)$ and assume that the likelihood
+  M_*, \alpha, \beta)$ and, following the standard practice of
+  unbinned luminosity function estimates
+  \citep[e.g.,][]{2001AJ....121...54F}, assume that the likelihood
 \begin{equation}
@@
 \end{equation}
-is given by $\phi(M)$
-%% JFH  ``is given by $\phi(M)$ itself''
-with suitable normalisation.  The negative
-logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can then be
-written as
+is given by $\phi(M)$ itself with suitable normalisation.  The
+negative logarithm of the likelihood $S\equiv -2\ln\mathcal{L}$ can
+then be written as
 \begin{multline}
@@
 adopt similar definitions for the derived quantities.)  The resultant
-parameter values are listed in Table~\ref{tab:bins}.  Consistent with
+parameter values are listed in Table~\ref{tab:bins}.\footnote{Full
+  posterior distributions for the luminosity functions themselves
+  should be obtained by running our publicly available code.  This is
+  also true for other models and derived quantities such as
+  emissivities that we discuss in this paper.} Consistent with
 previous studies, the double power law model provides an excellent
@@
 discontinuity at $2.2\le z<3.5$.
-%% JFH I think before imposing this prior by hand it might be useful to show the degeneracies that
-%% you get at high-z without imposing the prior on the faint-end/bright-end slope.
 
@@
 but Poisson errors of the limited samples dominate.
-
-%% Bins considered
-%% to be dominated by systematics are marked in Table~\ref{tab:bins}.
-%% These bins should be avoided while evaluating the evolution of the
-%% luminosity function.  The remaining redshift can
 
@@
 
-%% JFH I'm lost. According to this discussion Model 1 and 2 treat the faint end slope with a broke power law, but your figures
-%% suggests that only the gray band Model 1 is using this double power law? What you are calling Model 2 appears to not be a double
-%% power law? Am I getting fooled by the shape of that green curve?
-
 \begin{figure*}
@@
 symbols show the posterior median values with one-sigma uncertainties
-from the double power law fits to the data in redshift bins.
-%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
-%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
-%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
-Solid curves and shaded regions show the global models.  This number
-density evolution again highlights the systematic error in data at
-$z\sim 3$.  The number density of AGN down to the limit of the deepest
+from the double power law fits to the data in redshift bins.  Solid
+curves and shaded regions show the global models.  This number density
+evolution again highlights the systematic error in data at $z\sim 3$.
+The number density of AGN down to the limit of the deepest
 spectroscopic surveys ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$
@@
 which the number density of faint AGN peaks at lower redshifts than
-that of the bright AGN.  While the number density of AGN with
+that of the bright AGN \citep{2004ApJ...605..625H,
+  2005MNRAS.360L..39N, 2006AJ....131.2766R, 2006A&A...451..443M,
+  2009A&A...493...55E, 2013A&A...558A..89K, 2010MNRAS.401.2531A,
+  2015MNRAS.451.1892A}.  While the number density of AGN with
 $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
@@
 reveals another property of these models: when extrapolated, the AGN
-number density diverges in all three models at high redshifts.
-%% JFH I think this is just an artifiact of your fitting procedure,
-%% i.e. that these polynomial coefficients are unconstrained at really
-%% high-z. Do these fits include the banados and MOrtlock quasars? In
-%% that case the divergence should not occur, at least for the
-%% brightest bin.  Furthermore, if you would make this plot with the
-%% data instead of of integrating fits, you would be able to plot
-%% those objects on here as well.
-This results from the steep faint-end slope at high
-redshifts combined with the rapid brightening of the break luminosity.
-While no data exist at redshift $z>7.5$, this divergent behaviour is
-shared by previous models in the literature
-\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
-although Models 2 and 3 exhibit regular behaviour in the evolution of
-the AGN number density at $z\sim 3$, they do not fit the $z\sim
-4$--$5$ data as well as Model 1.
+number density diverges in all three models at high redshifts.  This
+results from the steep faint-end slope at high redshifts combined with
+the rapid brightening of the break luminosity.  While no data exist at
+redshift $z>7.5$, this divergent behaviour is shared by previous
+models in the literature \citep{2007ApJ...654..731H}.
+Figure~\ref{fig:rhoqso} also shows that although Models 2 and 3
+exhibit regular behaviour in the evolution of the AGN number density
+at $z\sim 3$, they do not fit the $z\sim 4$--$5$ data as well as Model
+1.
 
@@
     (left panel) and $M_{1450}=-21$ (right panel).  Black filled
-    circles with error bars in both panels show the emissivity
-    determinations in redshift bin deemed to have low systematic
-    errors.  Open circles show emissivities for redshift bins that we
-    remove from analysis due to high systematic errors.  Solid red
-    curves in both panels show the derived posterior median emissivity
-    evolution model, with the shaded area showing the one-sigma
-    (68.26\%) uncertainty.  Also shown for comparison in both panels
-    are models by \citet[pentagon symbol]{2009A&A...507..781S},
-    \citet[star]{2012ApJ...755..169M},
+    circles with one-sigma (68.26\%) error bars in both panels show
+    the emissivity determinations in redshift bin deemed to have low
+    systematic errors.  Open circles show emissivities for redshift
+    bins that we remove from analysis due to high systematic errors.
+    Solid red curves in both panels show the derived posterior median
+    emissivity evolution model, with the shaded area showing the
+    one-sigma (68.26\%) uncertainty.  Also shown for comparison in
+    both panels are models by \citet[pentagon
+      symbol]{2009A&A...507..781S}, \citet[star]{2012ApJ...755..169M},
     \citet[square]{2015AA...578A..83G},
@@
 With our adopted SED the specific comoving volume emissivity of
-quasars at 912\,\AA\ can be written as
-\begin{eqnarray}\nonumber
-\epsilon_{912}\left(z\right)&=&\int\limits_{-\infty}^{M_{1450}^\mathrm{lim}}\phi\left(M_{1450},z\right)10^{-0.4\left(M_{1450}-51.60\right)}\,\mathrm{d}M_{1450}\\
-& &\times\left(\frac{912}{1450}\right)^{0.61}\quad,
+quasars at 1450\,\AA\ can be written as
+\begin{equation}
+\epsilon_{1450}\left(z\right)=\int\limits_{-\infty}^{M_{1450}^\mathrm{lim}}\mathrm{d}M_{1450}\,\phi\left(M_{1450},z\right)10^{-0.4\left(M_{1450}-51.60\right)},
 \label{eqn:epsilon}
-\end{eqnarray}
+\end{equation}
 which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$
 and on the faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg
-M_*$.  The black circles in Figure~\ref{fig:e912_2} show the comoving
+M_*$.  The 912\,\AA\ emissivity is then given by
+\begin{equation}
+  \epsilon_{912}=\epsilon_{1450}\times\left(\frac{912}{1450}\right)^{0.61}.
+  \label{eqn:epsilon_912}
+\end{equation}
+The black circles in Figure~\ref{fig:e912_2} show the comoving
 912\,\AA\ emissivity obtained from the individual QLF fits
@@
 
-To account for redshift effects in the calculation of the \ion{H}{i} photoionization rate,
-a continuous function $\epsilon_{912}\left(z\right)$ is required. As our parametric QLF models
-from the previous section suffer from non-monotonic or divergent AGN number densities,
-we do not use them to derive the corresponding $\epsilon_{912}\left(z\right)$, but
-instead fit the individual emissivity values derived from credible data
-(filled black circles in Figure~\ref{fig:e912_2}) with a 
+To account for redshift effects in the calculation of the \ion{H}{i}
+photoionization rate, a continuous function
+$\epsilon_{912}\left(z\right)$ is required. As our parametric QLF
+models from the previous section suffer from non-monotonic or
+divergent AGN number densities, we do not use them to derive the
+corresponding $\epsilon_{912}\left(z\right)$, but instead fit the
+individual emissivity values derived from credible data with a
 five-parameter functional form used by \citet{2012ApJ...746..125H}
@@
 \end{equation}
-assuming a Gaussian likelihood for the emissivity values.  The
-resultant curves and the corresponding one-sigma uncertainties are
-shown in Figure~\ref{fig:e912_2}. For $M_{1450}<-18$ we obtain
+assuming a Gaussian likelihood for the emissivity values.  For
+$M_{1450}<-18$ we obtain
 \begin{multline}
-  \epsilon_{912}\left(z\right)=\left(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}\quad,
+  \epsilon_{1450}\left(z\right)=\left(10^{24.62}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.79}\\\times\frac{\exp(-1.23z)}{\exp(1.30z)+25.54}\quad,
   \label{eqn:e912_18}
@@
 \begin{multline}
-  \epsilon_{912}\left(z\right)=\left(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}\quad.
+  \epsilon_{1450}\left(z\right)=\left(10^{24.37}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.11}\\\times\frac{\exp(-0.4z)}{\exp(1.98z)+25.42}\quad,
   \label{eqn:e912_21}
 \end{multline}
-Table~\ref{tab:gamma2} provides the derived emissivities at
-912\,\AA\ and 1450\,\AA\ together with their derived errors at
-$0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.
+where the parameter values are median values of marginalised posterior
+distributions.  The 912\,\AA\ emissivity is then given by
+Equation~(\ref{eqn:epsilon_912}).  The resultant curves and the
+corresponding one-sigma uncertainties are shown in
+Figure~\ref{fig:e912_2}.  Table~\ref{tab:gamma2} provides the derived
+emissivities at 912\,\AA\ and 1450\,\AA\ together with their derived
+errors at $0<z<15$, extrapolating at $z<0.6$ and at $z>6.5$.
 
@@
 errors by propagating the errors in the QLF slopes, some of which they
-had assumed or inflated from the cited literature.  Due to these
-incorrect procedures the emissivity values derived by
-\citet{2015MNRAS.451L..30K} are not reliable.
+had assumed or inflated from the cited literature.  These incorrect
+procedures affect the emissivity values derived by
+\citet{2015MNRAS.451L..30K}.
 
@@
   \end{center}
-  \caption{AGN contribution to the hydrogen photoionisation rate, when
+  \caption{AGN contribution to the hydrogen photoionization rate, when
     the AGN luminosity function is integrated down to $M_{1450}=-21$
@@
       grey]{2017ApJ...837..106O}, and \citet[dashed
-      grey]{2018arXiv180104931P}.  The photoionisation rate derived
+      grey]{2018arXiv180104931P}.  The photoionization rate derived
     from the luminosity function fits of \citet{2015AA...578A..83G}
@@
 \end{equation}
-with $\epsilon_{912}\left(z^\prime\right)$ being represented by
-Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21} for our two
-magnitude limits, respectively.  For Poisson-distributed absorbers
-with an \ion{H}{i} column density distribution
+with $\epsilon_{912}\left(z^\prime\right)$ obtained as described in
+Section~\ref{sec:e912}.  For Poisson-distributed absorbers with an
+\ion{H}{i} column density distribution
 $f\left(N_\ion{H}{i},z^{\prime\prime}\right)=\partial^2n/\left(\partial
@@
 $z=2.4$.  The photoionization rate in our model for $M_{1450}=-21$ has
-the same evolution but a higher amplitude by a factor of $\sim 2$ as
-the QSO contribution to the \HI\ photoionization rate in the model of
+the same evolution but a higher amplitude as the QSO contribution to
+the \HI\ photoionization rate in the model of
 \citet{2012ApJ...746..125H}.  For both of our integration limits, the
-photoionisation rate peaks at $z\sim 2$.  For the integration limit of
+photoionization rate peaks at $z\sim 2$.  For the integration limit of
 $M_{1450}=-18$, AGN can provide all the flux necessary to explain the
 observed \lya forest between $z=2.4$ and $3.2$, with a contribution
-from other sources necessary only at higher redshifts.  The
-photoionization rate in the $M_{1450}<-18$ case also agrees with the
-inference of \citet{2017MNRAS.467.3172G} from the low-redshift
-($z<0.6$) \lya\ data.  We discuss this low-redshift evolution in
-greater detail in the next section.
+from other sources necessary only at higher redshifts.  However, the
+photoionization rate contributed by AGN falls short of the inference
+of \citet{2017MNRAS.467.3172G} from the low-redshift ($z<0.6$)
+\lya\ data.  We discuss this low-redshift evolution in greater detail
+in the next section.
 
@@
 \citet{2015MNRAS.451L..30K} are a result of the inhomogeneous
-redshift-dependent integration limits used by these authors and our
-differences from the reported emissivities of
-\citet{2009MNRAS.392...19C} and \citet{2013A&A...551A..29P}, which are
-used by \citet{2015MNRAS.451L..30K} to derive an emissivity evolution
-model.
+redshift-dependent integration limits used by these authors and their
+refitting of the results of \citet{2009MNRAS.392...19C} and
+\citet{2013A&A...551A..29P}.
 
@@
   \end{center}
-  \caption{Evolution of the hydrogen photoionisation rate at low
+  \caption{Evolution of the hydrogen photoionization rate at low
     redshifts, when the AGN luminosity function is integrated down to
@@
 limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that we
-use the 912\,\AA\ emissivity from Equation~(\ref{eqn:e912_18}) and
-(\ref{eqn:e912_21}), which are derived by fitting the model from
-Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
-luminosity functions in various redshift bins.  While doing this, as
-discussed above, redshift bins that were interpreted as being affected
-by systematic errors were ignored.  As a result, the emissivity model
-used in calculating the photoionization rate is an extrapolation at
-$z<0.6$.  However, it is interesting to note that the extrapolated
-emissivities at these redshifts are consistent with the emissivities
-calculated from our luminosity function fits to the $z<0.6$ data for
-either of our chosen integration limits.  This can be seen in
-Figure~\ref{fig:e912_2}.  At $z\sim 0$, the comoving
-912\,\AA\ emissivity in our model is lower by almost a factor of 2
-than that derived from the luminosity function inferred at this
-redshift by \citet{2009A&A...507..781S} for the $M_{1450}<-18$ case.
-For the $M_{1450}<-21$ integration, our comoving emissivity is higher
-than the emissivity in the model of \citet{2009A&A...507..781S} by
-about 50\%.  This results from the very faint $M_*$ ($\sim -19$) and
-steep faint-end slope ($\beta=-2$) obtained by
+use the 912\,\AA\ emissivity from Figure~\ref{fig:e912_2}, derived by
+fitting the model from Equation~(\ref{eqn:e912fit}) to the
+emissivities obtained from luminosity functions in various redshift
+bins.  While doing this, as discussed above, redshift bins that were
+interpreted as being affected by systematic errors were ignored.  As a
+result, the emissivity model used in calculating the photoionization
+rate is an extrapolation at $z<0.6$.  However, it is interesting to
+note that the extrapolated emissivities at these redshifts are
+consistent with the emissivities calculated from our luminosity
+function fits to the $z<0.6$ data for either of our chosen integration
+limits.  This can be seen in Figure~\ref{fig:e912_2}.  At $z\sim 0$,
+the comoving 912\,\AA\ emissivity in our model is lower by almost a
+factor of 2 than that derived from the luminosity function inferred at
+this redshift by \citet{2009A&A...507..781S} for the $M_{1450}<-18$
+case.  For the $M_{1450}<-21$ integration, our comoving emissivity is
+higher than the emissivity in the model of \citet{2009A&A...507..781S}
+by about 50\%.  This results from the very faint $M_*$ ($\sim -19$)
+and steep faint-end slope ($\beta=-2$) obtained by
 \citet{2009A&A...507..781S}.  (See Appendix~\ref{sec:qlfliterature}.)
-We use a spectral slope of $\alpha=-1.7$ for
-$\lambda<912$\,\AA\ (Equation~\ref{eqn:sed}).
 
 We find that the low-redshift \HI\ photoionization rate in our model
-is approximately equal to that that in the \citet{2012ApJ...746..125H}
-UVB model for both of our integration limits, as shown in
-Figure~\ref{fig:puc}.  At $z\sim 0$, the photoionisation rate for our
-$M_{1450}<-21$ integration is lower than \citet{2012ApJ...746..125H}
-photoionisation rate by about 10\%.  For the $M_{1450}<-18$ case, the
-photoionisation rate is higher than that in the
-\citet{2012ApJ...746..125H} model by about 10\%.  These differences
-are small compared to the factor of 2 to 3 differences that we find
-between our model and several recent estimates.  At $z=0.1$, this rate
-is smaller by a factor of 2 than the photoionization rate derived by
+is approximately equal to that in the \citet{2012ApJ...746..125H} UVB
+model for both of our integration limits.  At $z=0.1$, this rate is
+smaller by a factor of 2 than the photoionization rate derived by
 \citet{2017MNRAS.467.3172G} from the \HI\ column density distribution
-measurements of \citet{2016ApJ...817..111D}.  At $z<0.5$, this
-photoionization rate evolution in our model appears lower than also
-the rate derived by \citet{2015MNRAS.451L..30K} using the quasar
-luminosity function measurements of \citet{2009MNRAS.392...19C} and
-\citet{2013A&A...551A..29P}.  The model of \citet{2015ApJ...813L...8M}
-also results in a higher ionisation rate than our $M_{1450}<-18$
-inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
-\HI\ column density distribution measurements to cosmological
-simulations with an enhanced photoionization rate relative to the
-\citet{2012ApJ...746..125H} model to find that
-$\Gamma_\mathrm{HI}=4.6\times 10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$
-produces the observed \HI\ column densities.  This photoionization
-rate was achieved in the simulations of \citet{2015ApJ...811....3S} by
-a combination of quasars and galaxies (with an escape fraction of
-hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
-seen in Figure~\ref{fig:puc}, this photoionization rate is in closer
-agreement with the \citet{2015ApJ...813L...8M} model.  The
-photoionization rate estimate by \citet{2017MNRAS.467.4802F} from the
-H$\alpha$ surface brightness of a $z\sim 0$ galaxy observed by
-VLT/MUSE is somewhat higher than most other models shown in
-Figure~\ref{fig:puc}.  However, it is possible that the
-\citet{2017MNRAS.467.4802F} estimate is an upper limit, as the
-contribution of local sources to the photoionization rate is neglected
-in their modelling.  The requirement of an enhanced photoionization
-rate at $z\sim 0$ relative to our inference is also confirmed by the
-simulations presented by \citet{2017MNRAS.467L..86V},
-\citet{2017ApJ...837..106O}, and \citet{2018arXiv180104931P}.  But
-note that, as discussed above in Section~\ref{sec:e912}, a direct
-comparison of our results with the models of
-\citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K}, and
-\citet{2018arXiv180104931P} is difficult because of the inhomogenous
-redshift-dependent integration limits adopted by these authors.
-
-Before considering the deficit in the photoionisation rate obtained
+measurements of \citet{2016ApJ...817..111D}.  The model of
+\citet{2015ApJ...813L...8M} also results in a higher ionisation rate
+than our $M_{1450}<-18$ inference at $z<0.7$.
+\citet{2015ApJ...811....3S} compared the \HI\ column density
+distribution measurements to cosmological simulations with an enhanced
+photoionization rate relative to the \citet{2012ApJ...746..125H} model
+to find that $\Gamma_\mathrm{HI}=4.6\times
+10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$ produces the observed
+\HI\ column densities.  This photoionization rate was achieved in the
+simulations of \citet{2015ApJ...811....3S} by a combination of quasars
+and galaxies (with an escape fraction of hydrogen-ionizing photons
+assumed to be $f_\mathrm{esc}=0.05$).  As seen in
+Figure~\ref{fig:puc}, this photoionization rate is in closer agreement
+with the \citet{2015ApJ...813L...8M} model.  The photoionization rate
+estimate by \citet{2017MNRAS.467.4802F} from the H$\alpha$ surface
+brightness of a $z\sim 0$ galaxy observed by VLT/MUSE is somewhat
+higher than most other models shown in Figure~\ref{fig:puc}.  However,
+it is possible that the \citet{2017MNRAS.467.4802F} estimate is an
+upper limit, as the contribution of local sources to the
+photoionization rate is neglected in their modelling.  The requirement
+of an enhanced photoionization rate at $z\sim 0$ relative to our
+inference is also confirmed by the simulations presented by
+\citet{2017MNRAS.467L..86V}, \citet{2017ApJ...837..106O}, and
+\citet{2018arXiv180104931P}.  But note that, as discussed above in
+Section~\ref{sec:e912}, a direct comparison of our results with the
+models of \citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K},
+and \citet{2018arXiv180104931P} is difficult because of the
+inhomogenous redshift-dependent integration limits adopted by these
+authors.
+
+Before considering the deficit in the photoionization rate obtained
 from AGN at low redshifts relative to measurements from the
@@
 such faint AGN, but we find that even with this extremely faint
-integration limit, the photoionisation rate deficit is reduced by only
+integration limit, the photoionization rate deficit is reduced by only
 about 25\% for a spectral index of $-1.7$.  While this result does not
@@
 \HI\ column density distribution at the Lyman limit
-\citep{2011ApJ...736...42R, 2017ApJ...849..106S, 2017MNRAS.466..838G}.  Alternatively, it
-may be possible to balance the ionization rate deficit by the
-contribution from low-redshift LyC-leaking galaxies
+\citep{2011ApJ...736...42R, 2017ApJ...849..106S, 2017MNRAS.466..838G}.
+Alternatively, it may be possible to balance the ionization rate
+deficit by the contribution from low-redshift LyC-leaking galaxies
 \citep{2016Natur.529..178I, 2018MNRAS.474.4514I, 2018MNRAS.478.4851I}
@@
 \end{equation}
-with the quasar spectral index $\alpha_\nu=-1.7$ and the comoving 912\,\AA\ emissivity
-$\epsilon_{912}\left(z\right)$ given by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21}
-for $M_{1450}<-18$ and $M_{1450}<-21$, respectively.
-The recombination time scale in Equation~\eqref{eqn:qHedot} is given by
+with the quasar spectral index $\alpha_\nu=-1.7$ and the comoving
+912\,\AA\ emissivity $\epsilon_{912}\left(z\right)$ is obtained from
+the fits shown in Figure~\ref{fig:e912_2}.  The recombination time
+scale in Equation~\eqref{eqn:qHedot} is given by
 \begin{equation}
@@
 reionization starts around the earliest quasars at $z>6$ and finishes
-at $2.9\la z\la 3.4$ depending on the extent of the faint-end QLF.
+at $2.9\la z\la 3.7$ depending on the extent of the faint-end QLF.
 Considering the limitations of the modelling discussed above, both
@@
   $z>3.5$ QLF parameters independently, neglecting their covariance
-  and the survey data.}, shown in Figure~\ref{fig:e912_2}.
+  and the survey data.}.
 Considering the limitations of Equation~\eqref{eqn:qHedot},
@@
 modelling other than the QLF \citep{2017MNRAS.468.4691D}.  Our
-$Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with
-the simulation by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii}
-reionization is accomplished by the $z<5$ quasar population evolved
-assuming pure density or pure luminosity evolution to match the QLF by
-\citet{2011ApJ...728L..26G} for $M_{1450}<-19.5$ \citep[see
-  also][]{2013MNRAS.435.3169C}.  Future efforts in numerical modelling
-of \ion{He}{ii} reionization should investigate quasar models which
-follow the QLF evolution in detail, and which are consistent with the
-measured redshift evolution and scatter of the \ion{He}{ii} effective
-optical depth, as well as the measured redshift evolution of the IGM
-temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,
-  2014MNRAS.441.1916B, 2018MNRAS.474.2871R, 2017arXiv171000700H}.
+$Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees reasonably
+well with the simulation by \citet{2014MNRAS.445.4186C}, in which
+\ion{He}{ii} reionization is accomplished by the $z<5$ quasar
+population evolved assuming pure density or pure luminosity evolution
+to match the QLF by \citet{2011ApJ...728L..26G} for $M_{1450}<-19.5$
+\citep[see also][]{2013MNRAS.435.3169C}.  Future efforts in numerical
+modelling of \ion{He}{ii} reionization should investigate quasar
+models which follow the QLF evolution in detail, and which are
+consistent with the measured redshift evolution and scatter of the
+\ion{He}{ii} effective optical depth, as well as the measured redshift
+evolution of the IGM temperature-density relation
+\citep[e.g.][]{2011MNRAS.410.1096B, 2014MNRAS.441.1916B,
+  2018MNRAS.474.2871R, 2017arXiv171000700H}.
 
@@
 
-We have analysed the evolution of the AGN UV luminosity function from redshift $z=0$ to $7.5$
-using a combined sample of 83,488 mostly UV-optical colour-selected AGN from 12 data sets,
-homogenised with respect to the assumed cosmology, magnitude system and bandpass correction (if possible).
-The vast majority of them (83,469 AGN from 11/12 samples) have spectroscopic redshifts,
-and for all but 22 AGN the selection functions have been characterised.
-After restricting the sample due to persisting incompleteness at the faint end we arrive at 77,659 spectroscopically
-confirmed $0<z<7.5$ AGN extending to absolute AB magnitudes $M_{1450}\simeq -19$ at $z\simeq 0.5$
-and to $M_{1450}\sim -22$ at $z>3.5$, respectively. 
-To facilitate comparisons to future data sets we make the homogenised AGN sample and
+We have analysed the evolution of the AGN UV luminosity function from
+redshift $z=0$ to $7.5$ using a combined sample of 83,488 mostly
+UV-optical colour-selected AGN from 12 data sets, homogenised with
+respect to the assumed cosmology, magnitude system and bandpass
+correction (if possible).  The vast majority of them (83,469 AGN from
+11/12 samples) have spectroscopic redshifts, and for all but 22 AGN
+the selection functions have been characterised.  After restricting
+the sample due to persisting incompleteness at the faint end we arrive
+at 77,659 spectroscopically confirmed $0<z<7.5$ AGN extending to
+absolute AB magnitudes $M_{1450}\simeq -19$ at $z\simeq 0.5$ and to
+$M_{1450}\sim -22$ at $z>3.5$, respectively.  To facilitate
+comparisons to future data sets we make the homogenised AGN sample and
 the homogenised selection functions publicly available.
 
-Binning the $1450$\,\AA\ AGN luminosity function in narrow redshift ranges we find that it is
-excellently described by the customary double power law in magnitude at all redshifts (Figure~\ref{fig:mosaic}).
-Its four parameters significantly evolve with redshift (Figure~\ref{fig:evoln}):
-(i) The break magnitude $M_*$ of the AGN luminosity function shows a steep brightening from $M_*\simeq -24$ at $z\simeq 0.7$ to $M_*\sim -29$ at $z\simeq 6$.
-(ii) The corresponding amplitude $\phi_*$ drops by a factor $\sim 20,000$ from $\phi_*\simeq 4\times 10^{-7}$~mag$^{-1}$cMpc$^{-3}$ at $z<2.2$ to $\phi_*\sim 2\times 10^{-11}$~mag$^{-1}$cMpc$^{-3}$ at $z\simeq 6$.
-(iii) The faint-end slope $\beta$ significantly decreases from $\simeq -1.7$ at $z<2.2$ to $\simeq -2.4$ at $z\simeq 6$, resulting in a steepening of the luminosity function.
-(iv) The bright-end slope $\alpha$ also shows a moderate decrease with redshift, but is less constrained at the highest redshifts because of the bright break magnitude.
-In contrast to several previous studies, our fits are based on unbinned homogenised AGN data
-and their selection functions, and the confidence intervals fully account for covariance in the luminosity function parameters. 
-From the continuity of the luminosity function at lower redshifts we argue that its apparent
-single power law description at $z\simeq 6$ can be interpreted as the faint end of the double power law
-whose break magnitude $M_*$ is at the bright end of the $z\simeq 6$ quasar population.
+Binning the $1450$\,\AA\ AGN luminosity function in narrow redshift
+ranges we find that it is excellently described by the customary
+double power law in magnitude at all redshifts
+(Figure~\ref{fig:mosaic}).  Its four parameters significantly evolve
+with redshift (Figure~\ref{fig:evoln}): (i) The break magnitude $M_*$
+of the AGN luminosity function shows a steep brightening from
+$M_*\simeq -24$ at $z\simeq 0.7$ to $M_*\sim -29$ at $z\simeq 6$.
+(ii) The corresponding amplitude $\phi_*$ drops by a factor $\sim
+20,000$ from $\phi_*\simeq 4\times 10^{-7}$~mag$^{-1}$cMpc$^{-3}$ at
+$z<2.2$ to $\phi_*\sim 2\times 10^{-11}$~mag$^{-1}$cMpc$^{-3}$ at
+$z\simeq 6$.  (iii) The faint-end slope $\beta$ significantly
+decreases from $\simeq -1.7$ at $z<2.2$ to $\simeq -2.4$ at $z\simeq
+6$, resulting in a steepening of the luminosity function.  (iv) The
+bright-end slope $\alpha$ also shows a moderate decrease with
+redshift, but is less constrained at the highest redshifts because of
+the bright break magnitude.  In contrast to several previous studies,
+our fits are based on unbinned homogenised AGN data and their
+selection functions, and the confidence intervals fully account for
+covariance in the luminosity function parameters.  From the continuity
+of the luminosity function at lower redshifts we argue that its
+apparent single power law description at $z\simeq 6$ can be
+interpreted as the faint end of the double power law whose break
+magnitude $M_*$ is at the bright end of the $z\simeq 6$ quasar
+population.
 
@@
 suggesting a somewhat higher contribution of AGN to the high-$z$ UV
-background if faint AGN have unit escape fractions of ionizing
-photons.
+background.
 
@@
 low-redshift column density distribution of (partial) \ion{H}{i} Lyman
-limit systems \citep{2011ApJ...736...42R, 2017ApJ...849..106S}.  Helium
-reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$ AGN
-(Figure~\ref{fig:qhe}), but should be delayed by \ion{He}{ii} Lyman
-limit systems \citep{2009MNRAS.395..736B, 2017ApJ...851...50M},
+limit systems \citep{2011ApJ...736...42R, 2017ApJ...849..106S}.
+Helium reionization is accomplished at $z\simeq 3.5$ by $M_{1450}<-18$
+AGN (Figure~\ref{fig:qhe}), but should be delayed by \ion{He}{ii}
+Lyman limit systems \citep{2009MNRAS.395..736B, 2017ApJ...851...50M},
 requiring further modelling and detailed numerical simulations of the
@@
 paper can be easily compared with theoretical models or future data
-sets.  These luminosity function determinations supercede previous
-determinations by \citet{2007ApJ...654..731H} by including new data
-and extending the analysis to higher redshifts.  Our public code can
-be used either to reproduce all of our analysis starting from the QSO
-catalogues, or to quickly evaluate our luminosity function fits at
-desired redshifts and luminosities.  While doing this, the evolution
-of the luminosity function can be derived using any of the three
-global models that we presented in Section~\ref{sec:global}.  However,
-as we discussed in Section~\ref{sec:global}, none of these models
-should be extrapolated to higher redshifts.  Alternatively, our binned
-luminosity function estimates from Section~\ref{sec:bins} can be used.
-For applications that require extrapolation to higher redshifts, such
-as calculations of photoionization fluxes and emissivities, the fits
-presented in Equations~(\ref{eqn:e912_21}) and (\ref{eqn:e912_18}) can
-be used, or a similar approach of fitting functional forms to
-quantities suitably derived from the binned luminosity functions
-should be adopted.
+sets.  These luminosity function determinations supersede previous
+determinations by \citet{2007ApJ...654..731H} by including new data,
+by analysing unbinned data, and extending the analysis to higher
+redshifts.  Our public code can be used either to reproduce all of our
+analysis starting from the QSO catalogues, or to quickly evaluate our
+luminosity function fits at desired redshifts and luminosities.
 
@@
 Reionization'.
-%% Joe, do you need to add anything to acknowledgements?
 
@@
 \label{sec:conv}
-%% Define 'G15' somewhere above.
 In the double power law luminosity function models presented in
@@
 the 19 low-luminosity ($M_{1450}>-22.6$) AGN between redshifts $z=4.1$
-and $6.3$ reported by G15.  While this was done in order to restrict
-our sample to quasars with spectroscopic redshift determinations, it
-is instructive to consider how our results are affected if the G15 AGN
-are added to the analysis.  In their work, G15 found a shallower
-faint-end slope ($\beta\sim -1.5$ to $-1.8$) for the luminosity
-function at $4.1 < z < 6.3$, relative to our result from other AGN
-samples at these redshifts ($\beta\sim -2.0$ to $-2.5$).  Still, G15
-derived a higher 912\,\AA\ emissivity than our estimates
-(cf.\ Figure~\ref{fig:e912_2}), so that in their analysis AGN can
-produce all ionizing photons necessary to keep hydrogen ionized and
-explain the \lya data.  The black points in
+and $6.3$ reported by \citep[][hereafter G15]{2015AA...578A..83G}.
+While this was done in order to restrict our sample to quasars with
+spectroscopic redshift determinations, it is instructive to consider
+how our results are affected if the G15 AGN are added to the analysis.
+In their work, G15 found a shallower faint-end slope ($\beta\sim -1.5$
+to $-1.8$) for the luminosity function at $4.1 < z < 6.3$, relative to
+our result from other AGN samples at these redshifts ($\beta\sim -2.0$
+to $-2.5$).  Still, G15 derived a higher 912\,\AA\ emissivity than our
+estimates (cf.\ Figure~\ref{fig:e912_2}), so that in their analysis
+AGN can produce all ionizing photons necessary to keep hydrogen
+ionized and explain the \lya data.  The black points in
 Figure~\ref{fig:params_giallongo} show the parameters of the double
@@
 
-\section{Tables of emissivities and photoionisation rates}
+\section{Tables of emissivities and photoionization rates}
 \label{sec:tables}
@@
 Figures~\ref{fig:e912_2} and \ref{fig:gammapi}.  Note that the
-photoionisation rate calculation assumes an \HI\ column density
+photoionization rate calculation assumes an \HI\ column density
 distribution given by \citet{2012ApJ...746..125H} and extrapolates
@@
     \hline
-    0.31$^a$ & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.70^{+0.03}_{-0.03} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
-    0.50$^a$ & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.02}_{-0.02} & 0.58^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
+    0.31$^a$ & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.70^{+0.03}_{-0.02} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
+    0.50$^a$ & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.01}_{-0.01} & 0.59^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
     0.72 & 0.60 & 0.80 & 1.73^{+0.05}_{-0.05} & 2.30^{+0.07}_{-0.07} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.03} \\
-    0.91 & 0.80 & 1.00 & 2.85^{+0.16}_{-0.16} & 3.81^{+0.21}_{-0.21} & 2.10^{+0.05}_{-0.05} & 2.78^{+0.07}_{-0.06} \\
-    1.10 & 1.00 & 1.20 & 3.72^{+0.10}_{-0.10} & 4.94^{+0.13}_{-0.12} & 2.91^{+0.04}_{-0.04} & 3.87^{+0.05}_{-0.06} \\
-    1.30 & 1.20 & 1.40 & 5.71^{+0.22}_{-0.22} & 7.61^{+0.32}_{-0.32} & 4.47^{+0.09}_{-0.09} & 5.94^{+0.14}_{-0.12} \\
-    1.50 & 1.40 & 1.60 & 7.05^{+0.23}_{-0.24} & 9.32^{+0.29}_{-0.29} & 5.60^{+0.10}_{-0.10} & 7.43^{+0.14}_{-0.13} \\
-    1.71 & 1.60 & 1.80 & 7.72^{+0.16}_{-0.15} & 10.23^{+0.23}_{-0.24} & 6.71^{+0.10}_{-0.10} & 8.90^{+0.13}_{-0.12} \\
-    1.98 & 1.80 & 2.20 & 10.67^{+0.34}_{-0.39} & 14.14^{+0.53}_{-0.53} & 7.93^{+0.13}_{-0.15} & 10.54^{+0.18}_{-0.18} \\
-    2.30$^a$ & 2.20 & 2.40 & 10.21^{+0.23}_{-0.22} & 13.53^{+0.30}_{-0.30} & 8.88^{+0.12}_{-0.12} & 11.80^{+0.16}_{-0.15} \\
-    2.45$^a$ & 2.40 & 2.50 & 8.07^{+0.22}_{-0.22} & 10.71^{+0.33}_{-0.29} & 7.17^{+0.16}_{-0.15} & 9.48^{+0.18}_{-0.17} \\
-    2.55$^a$ & 2.50 & 2.60 & 6.64^{+0.19}_{-0.20} & 8.79^{+0.25}_{-0.24} & 6.21^{+0.13}_{-0.13} & 8.24^{+0.15}_{-0.17} \\
-    2.65$^a$ & 2.60 & 2.70 & 6.55^{+0.14}_{-0.16} & 8.71^{+0.21}_{-0.20} & 6.43^{+0.15}_{-0.15} & 8.56^{+0.21}_{-0.23} \\
-    2.75$^a$ & 2.70 & 2.80 & 7.44^{+0.22}_{-0.18} & 9.92^{+0.31}_{-0.33} & 7.16^{+0.20}_{-0.20} & 9.51^{+0.25}_{-0.29} \\
-    2.85$^a$ & 2.80 & 2.90 & 7.95^{+0.33}_{-0.33} & 10.50^{+0.38}_{-0.37} & 7.50^{+0.26}_{-0.30} & 9.91^{+0.32}_{-0.35} \\
-    2.95$^a$ & 2.90 & 3.00 & 7.95^{+0.36}_{-0.35} & 10.51^{+0.49}_{-0.51} & 6.82^{+0.21}_{-0.19} & 9.07^{+0.27}_{-0.31} \\
-    3.05$^a$ & 3.00 & 3.10 & 7.23^{+0.47}_{-0.39} & 9.59^{+0.60}_{-0.55} & 6.26^{+0.22}_{-0.21} & 8.30^{+0.25}_{-0.28} \\
-    3.15$^a$ & 3.10 & 3.20 & 9.87^{+0.94}_{-1.10} & 13.06^{+1.69}_{-1.55} & 7.00^{+0.37}_{-0.39} & 9.28^{+0.46}_{-0.51} \\
-    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.91}_{-0.90} & 11.04^{+1.27}_{-1.19} & 6.04^{+0.36}_{-0.35} & 8.01^{+0.46}_{-0.48} \\
-    3.34$^a$ & 3.30 & 3.40 & 12.23^{+2.81}_{-2.69} & 16.30^{+3.58}_{-3.28} & 7.21^{+0.64}_{-0.69} & 9.68^{+0.95}_{-0.94} \\
-    3.44$^a$ & 3.40 & 3.50 & 4.44^{+0.43}_{-0.57} & 5.98^{+0.67}_{-0.78} & 4.38^{+0.47}_{-0.49} & 5.77^{+0.52}_{-0.66} \\
-    3.88 & 3.70 & 4.10 & 4.37^{+1.47}_{-1.39} & 5.68^{+1.89}_{-1.76} & 2.53^{+0.43}_{-0.46} & 3.30^{+0.69}_{-0.69} \\
-    4.35 & 4.10 & 4.70 & 4.24^{+2.01}_{-2.12} & 5.33^{+2.42}_{-2.64} & 1.76^{+0.47}_{-0.47} & 2.39^{+0.69}_{-0.58} \\
-    4.92 & 4.70 & 5.50 & 2.60^{+0.93}_{-1.02} & 3.35^{+1.18}_{-1.29} & 0.94^{+0.18}_{-0.17} & 1.29^{+0.28}_{-0.25} \\
-    6.00 & 5.50 & 6.50 & 0.67^{+0.27}_{-0.25} & 0.91^{+0.40}_{-0.38} & 0.21^{+0.04}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
+    0.91 & 0.80 & 1.00 & 2.84^{+0.15}_{-0.15} & 3.77^{+0.20}_{-0.20} & 2.10^{+0.05}_{-0.05} & 2.78^{+0.06}_{-0.06} \\
+    1.10 & 1.00 & 1.20 & 3.73^{+0.11}_{-0.10} & 4.94^{+0.15}_{-0.14} & 2.91^{+0.05}_{-0.04} & 3.86^{+0.06}_{-0.05} \\
+    1.30 & 1.20 & 1.40 & 5.72^{+0.25}_{-0.23} & 7.59^{+0.33}_{-0.31} & 4.46^{+0.10}_{-0.09} & 5.92^{+0.13}_{-0.12} \\
+    1.50 & 1.40 & 1.60 & 7.05^{+0.22}_{-0.22} & 9.35^{+0.29}_{-0.29} & 5.60^{+0.09}_{-0.10} & 7.43^{+0.12}_{-0.13} \\
+    1.71 & 1.60 & 1.80 & 7.71^{+0.19}_{-0.18} & 10.23^{+0.25}_{-0.24} & 6.70^{+0.10}_{-0.11} & 8.89^{+0.13}_{-0.15} \\
+    1.98 & 1.80 & 2.20 & 10.64^{+0.35}_{-0.33} & 14.11^{+0.47}_{-0.44} & 7.93^{+0.14}_{-0.16} & 10.52^{+0.19}_{-0.21} \\
+    2.30$^a$ & 2.20 & 2.40 & 10.20^{+0.24}_{-0.24} & 13.54^{+0.32}_{-0.32} & 8.91^{+0.13}_{-0.12} & 11.82^{+0.17}_{-0.16} \\
+    2.45$^a$ & 2.40 & 2.50 & 8.04^{+0.26}_{-0.22} & 10.66^{+0.34}_{-0.29} & 7.17^{+0.14}_{-0.15} & 9.51^{+0.18}_{-0.20} \\
+    2.55$^a$ & 2.50 & 2.60 & 6.63^{+0.19}_{-0.19} & 8.80^{+0.25}_{-0.25} & 6.21^{+0.12}_{-0.12} & 8.24^{+0.16}_{-0.16} \\
+    2.65$^a$ & 2.60 & 2.70 & 6.59^{+0.16}_{-0.16} & 8.74^{+0.21}_{-0.21} & 6.47^{+0.17}_{-0.15} & 8.59^{+0.22}_{-0.20} \\
+    2.75$^a$ & 2.70 & 2.80 & 7.46^{+0.20}_{-0.21} & 9.90^{+0.27}_{-0.28} & 7.20^{+0.19}_{-0.20} & 9.55^{+0.26}_{-0.27} \\
+    2.85$^a$ & 2.80 & 2.90 & 7.96^{+0.32}_{-0.33} & 10.56^{+0.43}_{-0.43} & 7.53^{+0.31}_{-0.32} & 9.99^{+0.41}_{-0.42} \\
+    2.95$^a$ & 2.90 & 3.00 & 7.93^{+0.41}_{-0.40} & 10.52^{+0.55}_{-0.53} & 6.84^{+0.20}_{-0.22} & 9.08^{+0.26}_{-0.29} \\
+    3.05$^a$ & 3.00 & 3.10 & 7.22^{+0.41}_{-0.38} & 9.58^{+0.55}_{-0.51} & 6.27^{+0.23}_{-0.22} & 8.32^{+0.31}_{-0.29} \\
+    3.15$^a$ & 3.10 & 3.20 & 9.93^{+1.12}_{-1.09} & 13.18^{+1.48}_{-1.45} & 7.03^{+0.35}_{-0.36} & 9.33^{+0.46}_{-0.48} \\
+    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.84}_{-0.96} & 11.08^{+1.12}_{-1.28} & 6.17^{+0.38}_{-0.43} & 8.19^{+0.50}_{-0.57} \\
+    3.34$^a$ & 3.30 & 3.40 & 12.23^{+2.63}_{-2.80} & 16.22^{+3.49}_{-3.71} & 7.32^{+0.67}_{-0.82} & 9.71^{+0.89}_{-1.09} \\
+    3.44$^a$ & 3.40 & 3.50 & 4.47^{+0.50}_{-0.59} & 5.93^{+0.66}_{-0.79} & 4.43^{+0.40}_{-0.53} & 5.87^{+0.53}_{-0.70} \\
+    3.88 & 3.70 & 4.10 & 4.23^{+1.33}_{-1.37} & 5.61^{+1.77}_{-1.81} & 2.52^{+0.47}_{-0.46} & 3.34^{+0.63}_{-0.61} \\
+    4.35 & 4.10 & 4.70 & 4.27^{+1.90}_{-2.17} & 5.67^{+2.52}_{-2.88} & 1.78^{+0.48}_{-0.51} & 2.36^{+0.64}_{-0.68} \\
+    4.92 & 4.70 & 5.50 & 2.58^{+0.88}_{-1.00} & 3.42^{+1.17}_{-1.33} & 0.97^{+0.19}_{-0.18} & 1.29^{+0.26}_{-0.24} \\
+    6.00 & 5.50 & 6.50 & 0.66^{+0.24}_{-0.27} & 0.87^{+0.32}_{-0.35} & 0.21^{+0.05}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
     \hline
@@
   \begin{minipage}{13.0cm}
-    \textsuperscript{$a$}{Redshift bin considered to be severely affected by systematic errors (open circles in Figure~\ref{fig:e912_2}).
-These bins should be avoided while considering the evolution of emissivities.}
+    \textsuperscript{$a$}{Redshift bin considered to be severely
+      affected by systematic errors (open circles in
+      Figure~\ref{fig:e912_2}).  These bins should be avoided while
+      considering the evolution of emissivities.}
   \end{minipage}
@@
   % rtg2.py and tabulate_emissivities_global.py.
-  % Check these values once again.
   \caption{ Comoving emissivities at 912\,\AA\ and 1450\,\AA\ obtained
@@
     \hline
-    0.0 & 23.36^{+0.38}_{-0.20} & 23.18^{+0.25}_{-0.22} & 23.01^{+0.23}_{-0.16} & 22.83^{+0.12}_{-0.15} & -13.38^{+0.10}_{-0.06} & -13.57^{+0.06}_{-0.05} \\
-    0.1 & 23.54^{+0.29}_{-0.16} & 23.35^{+0.18}_{-0.17} & 23.24^{+0.18}_{-0.13} & 23.06^{+0.09}_{-0.11} & -13.22^{+0.08}_{-0.06} & -13.41^{+0.05}_{-0.04} \\
-    0.2 & 23.71^{+0.21}_{-0.14} & 23.51^{+0.13}_{-0.12} & 23.45^{+0.14}_{-0.10} & 23.27^{+0.07}_{-0.09} & -13.07^{+0.06}_{-0.05} & -13.26^{+0.04}_{-0.03} \\
-    0.3 & 23.85^{+0.16}_{-0.10} & 23.66^{+0.10}_{-0.08} & 23.64^{+0.10}_{-0.07} & 23.46^{+0.05}_{-0.06} & -12.94^{+0.05}_{-0.04} & -13.12^{+0.03}_{-0.03} \\
-    0.4 & 23.99^{+0.11}_{-0.08} & 23.80^{+0.07}_{-0.06} & 23.81^{+0.07}_{-0.06} & 23.63^{+0.04}_{-0.04} & -12.82^{+0.04}_{-0.04} & -12.99^{+0.03}_{-0.02} \\
-    0.5 & 24.11^{+0.08}_{-0.06} & 23.93^{+0.05}_{-0.04} & 23.95^{+0.05}_{-0.04} & 23.78^{+0.03}_{-0.03} & -12.71^{+0.03}_{-0.03} & -12.87^{+0.02}_{-0.02} \\
-    0.6 & 24.23^{+0.05}_{-0.04} & 24.06^{+0.03}_{-0.02} & 24.09^{+0.04}_{-0.03} & 23.93^{+0.02}_{-0.02} & -12.60^{+0.03}_{-0.03} & -12.76^{+0.02}_{-0.02} \\
-    0.7 & 24.34^{+0.03}_{-0.03} & 24.18^{+0.02}_{-0.02} & 24.21^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.51^{+0.03}_{-0.03} & -12.66^{+0.02}_{-0.02} \\
-    0.8 & 24.44^{+0.03}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.32^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.42^{+0.03}_{-0.03} & -12.57^{+0.02}_{-0.02} \\
-    0.9 & 24.54^{+0.02}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.02}_{-0.01} & 24.29^{+0.01}_{-0.01} & -12.35^{+0.02}_{-0.03} & -12.48^{+0.02}_{-0.02} \\
-    1.0 & 24.63^{+0.02}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.02}_{-0.01} & 24.38^{+0.01}_{-0.01} & -12.28^{+0.02}_{-0.03} & -12.40^{+0.02}_{-0.02} \\
-    1.1 & 24.71^{+0.02}_{-0.02} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.47^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.03} & -12.33^{+0.02}_{-0.02} \\
-    1.2 & 24.78^{+0.02}_{-0.02} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.55^{+0.01}_{-0.01} & -12.16^{+0.03}_{-0.03} & -12.27^{+0.02}_{-0.02} \\
-    1.3 & 24.85^{+0.01}_{-0.02} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.11^{+0.03}_{-0.03} & -12.22^{+0.02}_{-0.02} \\
-    1.4 & 24.91^{+0.01}_{-0.02} & 24.82^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.18^{+0.02}_{-0.02} \\
-    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.74^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
-    1.6 & 24.99^{+0.02}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.02^{+0.03}_{-0.03} & -12.12^{+0.02}_{-0.02} \\
-    1.7 & 25.03^{+0.02}_{-0.02} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.00^{+0.03}_{-0.03} & -12.11^{+0.02}_{-0.02} \\
-    1.8 & 25.05^{+0.02}_{-0.02} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.02}_{-0.01} & 24.86^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.10^{+0.02}_{-0.02} \\
-    1.9 & 25.07^{+0.02}_{-0.02} & 24.99^{+0.01}_{-0.01} & 24.96^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.04} & -12.09^{+0.03}_{-0.03} \\
-    2.0 & 25.08^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.98^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -11.99^{+0.04}_{-0.05} & -12.09^{+0.03}_{-0.03} \\
-    2.1 & 25.09^{+0.03}_{-0.02} & 25.01^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.02} & 24.91^{+0.02}_{-0.02} & -11.99^{+0.05}_{-0.05} & -12.10^{+0.03}_{-0.03} \\
-    2.2 & 25.09^{+0.03}_{-0.03} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.00^{+0.05}_{-0.06} & -12.11^{+0.04}_{-0.03} \\
-    2.3 & 25.09^{+0.04}_{-0.04} & 25.01^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.03} & -12.01^{+0.05}_{-0.07} & -12.12^{+0.04}_{-0.04} \\
-    2.4 & 25.08^{+0.04}_{-0.04} & 25.00^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.04} & 24.91^{+0.03}_{-0.03} & -12.03^{+0.06}_{-0.08} & -12.14^{+0.04}_{-0.04} \\
-    2.5 & 25.07^{+0.04}_{-0.05} & 24.99^{+0.03}_{-0.03} & 25.01^{+0.04}_{-0.04} & 24.89^{+0.03}_{-0.04} & -12.04^{+0.06}_{-0.08} & -12.16^{+0.05}_{-0.05} \\
-    2.6 & 25.06^{+0.05}_{-0.06} & 24.97^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.05} & 24.88^{+0.04}_{-0.04} & -12.06^{+0.07}_{-0.09} & -12.18^{+0.05}_{-0.05} \\
-    2.7 & 25.04^{+0.05}_{-0.07} & 24.96^{+0.04}_{-0.04} & 25.00^{+0.05}_{-0.05} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.10} & -12.21^{+0.05}_{-0.05} \\
-    2.8 & 25.02^{+0.06}_{-0.07} & 24.93^{+0.05}_{-0.04} & 24.99^{+0.06}_{-0.06} & 24.84^{+0.05}_{-0.04} & -12.11^{+0.07}_{-0.11} & -12.24^{+0.06}_{-0.06} \\
-    2.9 & 25.01^{+0.06}_{-0.08} & 24.91^{+0.05}_{-0.05} & 24.98^{+0.06}_{-0.07} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.12} & -12.27^{+0.06}_{-0.06} \\
-    3.0 & 24.98^{+0.06}_{-0.09} & 24.88^{+0.05}_{-0.05} & 24.96^{+0.06}_{-0.07} & 24.78^{+0.05}_{-0.05} & -12.17^{+0.08}_{-0.12} & -12.31^{+0.06}_{-0.07} \\
-    3.1 & 24.96^{+0.07}_{-0.10} & 24.85^{+0.05}_{-0.06} & 24.94^{+0.07}_{-0.08} & 24.75^{+0.06}_{-0.05} & -12.20^{+0.09}_{-0.13} & -12.35^{+0.07}_{-0.07} \\
-    3.2 & 24.93^{+0.07}_{-0.10} & 24.82^{+0.06}_{-0.06} & 24.91^{+0.07}_{-0.09} & 24.71^{+0.06}_{-0.05} & -12.23^{+0.09}_{-0.14} & -12.39^{+0.07}_{-0.08} \\
-    3.3 & 24.91^{+0.08}_{-0.11} & 24.79^{+0.06}_{-0.06} & 24.89^{+0.08}_{-0.09} & 24.68^{+0.06}_{-0.06} & -12.26^{+0.10}_{-0.15} & -12.43^{+0.07}_{-0.08} \\
-    3.4 & 24.88^{+0.08}_{-0.12} & 24.75^{+0.06}_{-0.07} & 24.86^{+0.08}_{-0.09} & 24.64^{+0.07}_{-0.06} & -12.30^{+0.10}_{-0.17} & -12.47^{+0.07}_{-0.09} \\
-    3.5 & 24.85^{+0.09}_{-0.14} & 24.72^{+0.07}_{-0.07} & 24.83^{+0.08}_{-0.10} & 24.59^{+0.07}_{-0.06} & -12.34^{+0.11}_{-0.18} & -12.52^{+0.08}_{-0.09} \\
-    3.6 & 24.82^{+0.10}_{-0.15} & 24.68^{+0.07}_{-0.08} & 24.80^{+0.09}_{-0.11} & 24.55^{+0.07}_{-0.06} & -12.38^{+0.11}_{-0.19} & -12.56^{+0.08}_{-0.10} \\
-    3.7 & 24.79^{+0.10}_{-0.16} & 24.64^{+0.07}_{-0.08} & 24.77^{+0.09}_{-0.11} & 24.51^{+0.07}_{-0.06} & -12.42^{+0.12}_{-0.20} & -12.61^{+0.08}_{-0.10} \\
-    3.8 & 24.75^{+0.10}_{-0.16} & 24.59^{+0.07}_{-0.09} & 24.73^{+0.10}_{-0.12} & 24.47^{+0.07}_{-0.07} & -12.46^{+0.12}_{-0.21} & -12.66^{+0.08}_{-0.11} \\
-    3.9 & 24.72^{+0.11}_{-0.17} & 24.55^{+0.07}_{-0.09} & 24.70^{+0.10}_{-0.13} & 24.42^{+0.07}_{-0.07} & -12.50^{+0.13}_{-0.22} & -12.72^{+0.08}_{-0.11} \\
-    4.0 & 24.68^{+0.11}_{-0.18} & 24.51^{+0.07}_{-0.09} & 24.66^{+0.10}_{-0.14} & 24.37^{+0.07}_{-0.08} & -12.54^{+0.13}_{-0.24} & -12.77^{+0.08}_{-0.12} \\
-    4.1 & 24.65^{+0.11}_{-0.20} & 24.46^{+0.07}_{-0.10} & 24.63^{+0.11}_{-0.16} & 24.33^{+0.06}_{-0.09} & -12.58^{+0.13}_{-0.25} & -12.82^{+0.08}_{-0.12} \\
-    4.2 & 24.61^{+0.12}_{-0.21} & 24.42^{+0.07}_{-0.10} & 24.58^{+0.12}_{-0.16} & 24.28^{+0.06}_{-0.10} & -12.63^{+0.14}_{-0.27} & -12.88^{+0.08}_{-0.12} \\
-    4.3 & 24.58^{+0.13}_{-0.23} & 24.37^{+0.07}_{-0.11} & 24.54^{+0.12}_{-0.17} & 24.23^{+0.07}_{-0.10} & -12.67^{+0.14}_{-0.29} & -12.94^{+0.09}_{-0.13} \\
-    4.4 & 24.54^{+0.12}_{-0.24} & 24.32^{+0.08}_{-0.11} & 24.50^{+0.13}_{-0.18} & 24.17^{+0.07}_{-0.11} & -12.72^{+0.14}_{-0.30} & -13.00^{+0.09}_{-0.13} \\
-    4.5 & 24.50^{+0.13}_{-0.26} & 24.27^{+0.08}_{-0.11} & 24.45^{+0.14}_{-0.19} & 24.12^{+0.07}_{-0.12} & -12.76^{+0.15}_{-0.32} & -13.06^{+0.09}_{-0.14} \\
-    4.6 & 24.46^{+0.13}_{-0.28} & 24.22^{+0.08}_{-0.12} & 24.40^{+0.15}_{-0.19} & 24.07^{+0.08}_{-0.12} & -12.81^{+0.15}_{-0.34} & -13.12^{+0.10}_{-0.14} \\
-    4.7 & 24.42^{+0.14}_{-0.30} & 24.16^{+0.09}_{-0.12} & 24.36^{+0.16}_{-0.21} & 24.01^{+0.08}_{-0.13} & -12.86^{+0.16}_{-0.36} & -13.18^{+0.11}_{-0.14} \\
-    4.8 & 24.38^{+0.15}_{-0.31} & 24.11^{+0.09}_{-0.13} & 24.31^{+0.17}_{-0.22} & 23.96^{+0.09}_{-0.14} & -12.91^{+0.17}_{-0.38} & -13.25^{+0.11}_{-0.15} \\
-    4.9 & 24.34^{+0.15}_{-0.33} & 24.05^{+0.10}_{-0.13} & 24.26^{+0.17}_{-0.24} & 23.90^{+0.09}_{-0.15} & -12.96^{+0.18}_{-0.39} & -13.32^{+0.12}_{-0.15} \\
-    5.0 & 24.30^{+0.16}_{-0.35} & 23.99^{+0.11}_{-0.13} & 24.21^{+0.17}_{-0.25} & 23.84^{+0.10}_{-0.17} & -13.01^{+0.19}_{-0.41} & -13.38^{+0.13}_{-0.16} \\
+    0.0 & 23.20^{+0.20}_{-0.18} & 22.96^{+0.11}_{-0.14} & 23.08^{+0.20}_{-0.18} & 22.84^{+0.11}_{-0.14} & -13.71^{+0.05}_{-0.05} & -13.86^{+0.03}_{-0.03} \\
+    0.1 & 23.43^{+0.15}_{-0.14} & 23.19^{+0.09}_{-0.11} & 23.30^{+0.15}_{-0.14} & 23.07^{+0.09}_{-0.11} & -13.51^{+0.04}_{-0.04} & -13.66^{+0.02}_{-0.03} \\
+    0.2 & 23.62^{+0.11}_{-0.11} & 23.39^{+0.07}_{-0.08} & 23.50^{+0.11}_{-0.11} & 23.27^{+0.07}_{-0.08} & -13.33^{+0.04}_{-0.04} & -13.48^{+0.02}_{-0.02} \\
+    0.3 & 23.80^{+0.07}_{-0.09} & 23.58^{+0.05}_{-0.06} & 23.68^{+0.07}_{-0.09} & 23.46^{+0.05}_{-0.06} & -13.17^{+0.03}_{-0.03} & -13.31^{+0.02}_{-0.02} \\
+    0.4 & 23.96^{+0.06}_{-0.07} & 23.75^{+0.04}_{-0.04} & 23.83^{+0.06}_{-0.07} & 23.63^{+0.04}_{-0.04} & -13.02^{+0.03}_{-0.03} & -13.16^{+0.02}_{-0.02} \\
+    0.5 & 24.10^{+0.04}_{-0.06} & 23.91^{+0.03}_{-0.03} & 23.97^{+0.04}_{-0.06} & 23.78^{+0.03}_{-0.03} & -12.89^{+0.02}_{-0.02} & -13.02^{+0.01}_{-0.01} \\
+    0.6 & 24.23^{+0.03}_{-0.04} & 24.05^{+0.02}_{-0.02} & 24.10^{+0.03}_{-0.04} & 23.93^{+0.02}_{-0.02} & -12.77^{+0.02}_{-0.02} & -12.89^{+0.01}_{-0.01} \\
+    0.7 & 24.34^{+0.02}_{-0.03} & 24.18^{+0.01}_{-0.01} & 24.22^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.66^{+0.02}_{-0.02} & -12.78^{+0.01}_{-0.01} \\
+    0.8 & 24.45^{+0.02}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.33^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.56^{+0.02}_{-0.02} & -12.67^{+0.01}_{-0.01} \\
+    0.9 & 24.55^{+0.01}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.01}_{-0.02} & 24.29^{+0.01}_{-0.01} & -12.47^{+0.02}_{-0.02} & -12.58^{+0.01}_{-0.01} \\
+    1.0 & 24.63^{+0.01}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.01}_{-0.02} & 24.39^{+0.01}_{-0.01} & -12.39^{+0.02}_{-0.02} & -12.49^{+0.01}_{-0.01} \\
+    1.1 & 24.71^{+0.01}_{-0.01} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.48^{+0.01}_{-0.01} & -12.32^{+0.02}_{-0.02} & -12.42^{+0.01}_{-0.01} \\
+    1.2 & 24.78^{+0.01}_{-0.01} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.56^{+0.01}_{-0.01} & -12.26^{+0.02}_{-0.02} & -12.35^{+0.01}_{-0.01} \\
+    1.3 & 24.84^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.02} & -12.30^{+0.01}_{-0.01} \\
+    1.4 & 24.90^{+0.01}_{-0.01} & 24.81^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.16^{+0.02}_{-0.02} & -12.25^{+0.01}_{-0.01} \\
+    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & -12.12^{+0.02}_{-0.02} & -12.21^{+0.01}_{-0.01} \\
+    1.6 & 24.99^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.09^{+0.02}_{-0.02} & -12.18^{+0.01}_{-0.01} \\
+    1.7 & 25.03^{+0.01}_{-0.01} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.16^{+0.02}_{-0.02} \\
+    1.8 & 25.06^{+0.01}_{-0.01} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.01}_{-0.01} & 24.86^{+0.01}_{-0.01} & -12.05^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
+    1.9 & 25.09^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.97^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
+    2.0 & 25.11^{+0.02}_{-0.02} & 25.02^{+0.01}_{-0.01} & 24.99^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -12.03^{+0.04}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
+    2.1 & 25.12^{+0.03}_{-0.03} & 25.03^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.02^{+0.04}_{-0.05} & -12.14^{+0.03}_{-0.03} \\
+    2.2 & 25.14^{+0.03}_{-0.03} & 25.04^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.05} & -12.15^{+0.03}_{-0.03} \\
+    2.3 & 25.14^{+0.03}_{-0.04} & 25.04^{+0.02}_{-0.02} & 25.02^{+0.03}_{-0.04} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.06} & -12.16^{+0.03}_{-0.03} \\
+    2.4 & 25.14^{+0.04}_{-0.05} & 25.03^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.05} & 24.91^{+0.03}_{-0.03} & -12.04^{+0.05}_{-0.07} & -12.18^{+0.04}_{-0.04} \\
+    2.5 & 25.14^{+0.04}_{-0.06} & 25.02^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.06} & 24.89^{+0.03}_{-0.03} & -12.05^{+0.06}_{-0.07} & -12.20^{+0.04}_{-0.04} \\
+    2.6 & 25.14^{+0.05}_{-0.06} & 25.00^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.06} & 24.88^{+0.04}_{-0.04} & -12.07^{+0.07}_{-0.08} & -12.23^{+0.04}_{-0.04} \\
+    2.7 & 25.13^{+0.06}_{-0.07} & 24.98^{+0.04}_{-0.04} & 25.00^{+0.06}_{-0.07} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.09} & -12.25^{+0.05}_{-0.05} \\
+    2.8 & 25.11^{+0.07}_{-0.07} & 24.96^{+0.04}_{-0.05} & 24.99^{+0.07}_{-0.07} & 24.84^{+0.04}_{-0.05} & -12.11^{+0.08}_{-0.09} & -12.29^{+0.05}_{-0.05} \\
+    2.9 & 25.10^{+0.07}_{-0.08} & 24.93^{+0.05}_{-0.05} & 24.98^{+0.07}_{-0.08} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.10} & -12.32^{+0.05}_{-0.05} \\
+    3.0 & 25.08^{+0.08}_{-0.09} & 24.91^{+0.05}_{-0.05} & 24.96^{+0.08}_{-0.09} & 24.78^{+0.05}_{-0.05} & -12.16^{+0.09}_{-0.11} & -12.36^{+0.05}_{-0.06} \\
+    3.1 & 25.06^{+0.08}_{-0.10} & 24.87^{+0.05}_{-0.05} & 24.94^{+0.08}_{-0.10} & 24.75^{+0.05}_{-0.05} & -12.20^{+0.09}_{-0.12} & -12.40^{+0.06}_{-0.06} \\
+    3.2 & 25.04^{+0.09}_{-0.11} & 24.84^{+0.06}_{-0.05} & 24.92^{+0.09}_{-0.11} & 24.72^{+0.06}_{-0.05} & -12.23^{+0.10}_{-0.13} & -12.44^{+0.06}_{-0.06} \\
+    3.3 & 25.01^{+0.09}_{-0.12} & 24.81^{+0.06}_{-0.06} & 24.89^{+0.09}_{-0.12} & 24.68^{+0.06}_{-0.06} & -12.27^{+0.10}_{-0.13} & -12.49^{+0.06}_{-0.06} \\
+    3.4 & 24.99^{+0.10}_{-0.13} & 24.77^{+0.06}_{-0.06} & 24.86^{+0.10}_{-0.13} & 24.64^{+0.06}_{-0.06} & -12.30^{+0.11}_{-0.14} & -12.54^{+0.06}_{-0.07} \\
+    3.5 & 24.96^{+0.10}_{-0.14} & 24.73^{+0.06}_{-0.06} & 24.83^{+0.10}_{-0.14} & 24.60^{+0.06}_{-0.06} & -12.34^{+0.11}_{-0.15} & -12.59^{+0.06}_{-0.07} \\
+    3.6 & 24.93^{+0.11}_{-0.15} & 24.69^{+0.06}_{-0.07} & 24.80^{+0.11}_{-0.15} & 24.56^{+0.06}_{-0.07} & -12.39^{+0.11}_{-0.16} & -12.64^{+0.06}_{-0.07} \\
+    3.7 & 24.89^{+0.11}_{-0.15} & 24.64^{+0.06}_{-0.07} & 24.77^{+0.11}_{-0.15} & 24.52^{+0.06}_{-0.07} & -12.43^{+0.12}_{-0.16} & -12.69^{+0.06}_{-0.07} \\
+    3.8 & 24.85^{+0.12}_{-0.16} & 24.60^{+0.06}_{-0.07} & 24.73^{+0.12}_{-0.16} & 24.47^{+0.06}_{-0.07} & -12.48^{+0.12}_{-0.17} & -12.74^{+0.07}_{-0.08} \\
+    3.9 & 24.81^{+0.12}_{-0.17} & 24.55^{+0.07}_{-0.07} & 24.69^{+0.12}_{-0.17} & 24.43^{+0.07}_{-0.07} & -12.53^{+0.13}_{-0.18} & -12.80^{+0.07}_{-0.08} \\
+    4.0 & 24.78^{+0.13}_{-0.18} & 24.51^{+0.07}_{-0.08} & 24.65^{+0.13}_{-0.18} & 24.38^{+0.07}_{-0.08} & -12.57^{+0.13}_{-0.19} & -12.85^{+0.07}_{-0.09} \\
+    4.1 & 24.74^{+0.13}_{-0.19} & 24.46^{+0.07}_{-0.09} & 24.61^{+0.13}_{-0.19} & 24.34^{+0.07}_{-0.09} & -12.63^{+0.14}_{-0.20} & -12.91^{+0.07}_{-0.10} \\
+    4.2 & 24.69^{+0.13}_{-0.19} & 24.41^{+0.07}_{-0.09} & 24.57^{+0.13}_{-0.19} & 24.29^{+0.07}_{-0.09} & -12.68^{+0.14}_{-0.21} & -12.97^{+0.07}_{-0.10} \\
+    4.3 & 24.65^{+0.14}_{-0.20} & 24.36^{+0.07}_{-0.10} & 24.53^{+0.14}_{-0.20} & 24.24^{+0.07}_{-0.10} & -12.73^{+0.15}_{-0.22} & -13.03^{+0.07}_{-0.11} \\
+    4.4 & 24.61^{+0.14}_{-0.21} & 24.31^{+0.07}_{-0.11} & 24.49^{+0.14}_{-0.21} & 24.19^{+0.07}_{-0.11} & -12.78^{+0.15}_{-0.23} & -13.09^{+0.08}_{-0.12} \\
+    4.5 & 24.57^{+0.15}_{-0.23} & 24.26^{+0.08}_{-0.11} & 24.44^{+0.15}_{-0.23} & 24.14^{+0.08}_{-0.11} & -12.84^{+0.16}_{-0.24} & -13.15^{+0.08}_{-0.12} \\
+    4.6 & 24.52^{+0.16}_{-0.24} & 24.21^{+0.08}_{-0.12} & 24.39^{+0.16}_{-0.24} & 24.08^{+0.08}_{-0.12} & -12.90^{+0.17}_{-0.25} & -13.22^{+0.08}_{-0.13} \\
+    4.7 & 24.47^{+0.17}_{-0.25} & 24.15^{+0.08}_{-0.13} & 24.34^{+0.17}_{-0.25} & 24.03^{+0.08}_{-0.13} & -12.96^{+0.18}_{-0.27} & -13.28^{+0.08}_{-0.14} \\
+    4.8 & 24.42^{+0.17}_{-0.27} & 24.10^{+0.08}_{-0.13} & 24.30^{+0.17}_{-0.27} & 23.98^{+0.08}_{-0.13} & -13.02^{+0.18}_{-0.28} & -13.35^{+0.08}_{-0.14} \\
+    4.9 & 24.37^{+0.18}_{-0.28} & 24.04^{+0.08}_{-0.14} & 24.25^{+0.18}_{-0.28} & 23.92^{+0.08}_{-0.14} & -13.08^{+0.19}_{-0.29} & -13.41^{+0.09}_{-0.15} \\
+    5.0 & 24.31^{+0.20}_{-0.29} & 23.99^{+0.08}_{-0.15} & 24.19^{+0.20}_{-0.29} & 23.87^{+0.08}_{-0.15} & -13.15^{+0.20}_{-0.30} & -13.48^{+0.09}_{-0.16} \\
     \hline
@@
     \hline
-    5.1 & 24.26^{+0.17}_{-0.36} & 23.93^{+0.11}_{-0.14} & 24.16^{+0.18}_{-0.26} & 23.78^{+0.10}_{-0.19} & -13.06^{+0.20}_{-0.42} & -13.45^{+0.13}_{-0.16} \\
-    5.2 & 24.21^{+0.19}_{-0.37} & 23.88^{+0.12}_{-0.14} & 24.10^{+0.19}_{-0.27} & 23.72^{+0.11}_{-0.20} & -13.12^{+0.21}_{-0.44} & -13.52^{+0.14}_{-0.17} \\
-    5.3 & 24.17^{+0.20}_{-0.39} & 23.82^{+0.13}_{-0.15} & 24.05^{+0.19}_{-0.29} & 23.66^{+0.12}_{-0.22} & -13.17^{+0.22}_{-0.46} & -13.59^{+0.15}_{-0.18} \\
-    5.4 & 24.13^{+0.21}_{-0.41} & 23.76^{+0.13}_{-0.16} & 24.00^{+0.20}_{-0.30} & 23.60^{+0.12}_{-0.23} & -13.22^{+0.23}_{-0.47} & -13.67^{+0.16}_{-0.19} \\
-    5.5 & 24.09^{+0.22}_{-0.43} & 23.70^{+0.14}_{-0.17} & 23.94^{+0.21}_{-0.31} & 23.54^{+0.12}_{-0.24} & -13.29^{+0.24}_{-0.49} & -13.75^{+0.17}_{-0.20} \\
-    5.6 & 24.04^{+0.23}_{-0.45} & 23.63^{+0.16}_{-0.17} & 23.89^{+0.22}_{-0.33} & 23.48^{+0.12}_{-0.25} & -13.37^{+0.25}_{-0.51} & -13.85^{+0.18}_{-0.21} \\
-    5.7 & 24.00^{+0.24}_{-0.46} & 23.57^{+0.16}_{-0.18} & 23.84^{+0.23}_{-0.34} & 23.42^{+0.13}_{-0.26} & -13.45^{+0.26}_{-0.53} & -13.94^{+0.18}_{-0.22} \\
-    5.8 & 23.95^{+0.25}_{-0.48} & 23.51^{+0.16}_{-0.20} & 23.78^{+0.24}_{-0.35} & 23.35^{+0.14}_{-0.28} & -13.53^{+0.27}_{-0.55} & -14.04^{+0.19}_{-0.23} \\
-    5.9 & 23.91^{+0.26}_{-0.50} & 23.45^{+0.17}_{-0.20} & 23.73^{+0.24}_{-0.38} & 23.29^{+0.15}_{-0.30} & -13.62^{+0.28}_{-0.57} & -14.15^{+0.20}_{-0.24} \\
-    6.0 & 23.87^{+0.27}_{-0.52} & 23.38^{+0.18}_{-0.20} & 23.67^{+0.25}_{-0.40} & 23.23^{+0.15}_{-0.32} & -13.70^{+0.29}_{-0.58} & -14.26^{+0.21}_{-0.24} \\
-    6.1 & 23.82^{+0.29}_{-0.54} & 23.32^{+0.19}_{-0.21} & 23.61^{+0.27}_{-0.42} & 23.16^{+0.16}_{-0.34} & -13.80^{+0.31}_{-0.60} & -14.37^{+0.22}_{-0.25} \\
-    6.2 & 23.76^{+0.30}_{-0.56} & 23.25^{+0.20}_{-0.22} & 23.55^{+0.28}_{-0.42} & 23.10^{+0.16}_{-0.36} & -13.90^{+0.32}_{-0.62} & -14.48^{+0.23}_{-0.26} \\
-    6.3 & 23.71^{+0.32}_{-0.57} & 23.19^{+0.21}_{-0.23} & 23.49^{+0.29}_{-0.43} & 23.03^{+0.17}_{-0.38} & -14.00^{+0.34}_{-0.64} & -14.59^{+0.24}_{-0.28} \\
-    6.4 & 23.66^{+0.33}_{-0.59} & 23.13^{+0.22}_{-0.24} & 23.42^{+0.30}_{-0.44} & 22.96^{+0.18}_{-0.39} & -14.10^{+0.35}_{-0.66} & -14.71^{+0.25}_{-0.29} \\
-    6.5 & 23.62^{+0.34}_{-0.61} & 23.06^{+0.23}_{-0.25} & 23.36^{+0.31}_{-0.46} & 22.90^{+0.19}_{-0.40} & -14.20^{+0.36}_{-0.68} & -14.83^{+0.26}_{-0.31} \\
-    6.6 & 23.56^{+0.36}_{-0.62} & 23.00^{+0.24}_{-0.26} & 23.30^{+0.33}_{-0.48} & 22.83^{+0.19}_{-0.42} & -14.31^{+0.38}_{-0.69} & -14.96^{+0.27}_{-0.32} \\
-    6.7 & 23.52^{+0.37}_{-0.64} & 22.93^{+0.25}_{-0.28} & 23.23^{+0.34}_{-0.50} & 22.76^{+0.20}_{-0.44} & -14.42^{+0.39}_{-0.72} & -15.08^{+0.28}_{-0.34} \\
-    6.8 & 23.47^{+0.38}_{-0.67} & 22.87^{+0.26}_{-0.29} & 23.15^{+0.36}_{-0.51} & 22.70^{+0.20}_{-0.45} & -14.52^{+0.40}_{-0.74} & -15.22^{+0.29}_{-0.36} \\
-    6.9 & 23.42^{+0.40}_{-0.68} & 22.80^{+0.27}_{-0.30} & 23.08^{+0.39}_{-0.53} & 22.63^{+0.21}_{-0.47} & -14.64^{+0.41}_{-0.77} & -15.35^{+0.30}_{-0.37} \\
-    7.0 & 23.37^{+0.41}_{-0.71} & 22.73^{+0.28}_{-0.31} & 23.01^{+0.41}_{-0.54} & 22.56^{+0.22}_{-0.49} & -14.74^{+0.42}_{-0.79} & -15.48^{+0.32}_{-0.40} \\
-    7.1 & 23.33^{+0.41}_{-0.73} & 22.66^{+0.29}_{-0.33} & 22.94^{+0.42}_{-0.56} & 22.49^{+0.23}_{-0.52} & -14.86^{+0.43}_{-0.82} & -15.62^{+0.33}_{-0.42} \\
-    7.2 & 23.28^{+0.43}_{-0.76} & 22.60^{+0.29}_{-0.35} & 22.87^{+0.44}_{-0.57} & 22.42^{+0.23}_{-0.54} & -14.97^{+0.45}_{-0.85} & -15.75^{+0.34}_{-0.45} \\
-    7.3 & 23.22^{+0.45}_{-0.77} & 22.53^{+0.31}_{-0.36} & 22.80^{+0.47}_{-0.59} & 22.35^{+0.24}_{-0.57} & -15.09^{+0.47}_{-0.87} & -15.88^{+0.36}_{-0.47} \\
-    7.4 & 23.17^{+0.46}_{-0.80} & 22.46^{+0.32}_{-0.38} & 22.73^{+0.49}_{-0.60} & 22.29^{+0.25}_{-0.59} & -15.20^{+0.48}_{-0.90} & -16.02^{+0.37}_{-0.50} \\
-    7.5 & 23.13^{+0.47}_{-0.83} & 22.39^{+0.34}_{-0.39} & 22.67^{+0.51}_{-0.61} & 22.21^{+0.25}_{-0.62} & -15.30^{+0.49}_{-0.93} & -16.15^{+0.39}_{-0.52} \\
-    7.6 & 23.09^{+0.47}_{-0.87} & 22.32^{+0.35}_{-0.41} & 22.60^{+0.52}_{-0.63} & 22.14^{+0.26}_{-0.64} & -15.41^{+0.49}_{-0.97} & -16.29^{+0.41}_{-0.55} \\
-    7.7 & 23.04^{+0.48}_{-0.90} & 22.26^{+0.37}_{-0.42} & 22.53^{+0.54}_{-0.64} & 22.07^{+0.27}_{-0.66} & -15.52^{+0.50}_{-1.00} & -16.42^{+0.43}_{-0.57} \\
-    7.8 & 22.99^{+0.50}_{-0.92} & 22.19^{+0.38}_{-0.44} & 22.46^{+0.57}_{-0.65} & 22.00^{+0.28}_{-0.68} & -15.63^{+0.52}_{-1.02} & -16.55^{+0.45}_{-0.60} \\
-    7.9 & 22.94^{+0.51}_{-0.94} & 22.12^{+0.41}_{-0.46} & 22.38^{+0.58}_{-0.65} & 21.92^{+0.29}_{-0.70} & -15.74^{+0.53}_{-1.05} & -16.68^{+0.47}_{-0.63} \\
-    8.0 & 22.88^{+0.53}_{-0.97} & 22.05^{+0.43}_{-0.48} & 22.31^{+0.60}_{-0.66} & 21.85^{+0.30}_{-0.73} & -15.84^{+0.54}_{-1.07} & -16.80^{+0.50}_{-0.66} \\
-    8.1 & 22.83^{+0.54}_{-0.99} & 21.97^{+0.44}_{-0.49} & 22.24^{+0.61}_{-0.68} & 21.78^{+0.31}_{-0.76} & -15.95^{+0.56}_{-1.10} & -16.93^{+0.52}_{-0.68} \\
-    8.2 & 22.78^{+0.56}_{-1.02} & 21.90^{+0.46}_{-0.51} & 22.17^{+0.63}_{-0.70} & 21.71^{+0.32}_{-0.78} & -16.05^{+0.57}_{-1.12} & -17.06^{+0.54}_{-0.71} \\
-    8.3 & 22.73^{+0.57}_{-1.04} & 21.82^{+0.48}_{-0.52} & 22.10^{+0.65}_{-0.71} & 21.63^{+0.33}_{-0.81} & -16.15^{+0.58}_{-1.15} & -17.20^{+0.56}_{-0.72} \\
-    8.4 & 22.68^{+0.58}_{-1.07} & 21.74^{+0.50}_{-0.53} & 22.02^{+0.68}_{-0.72} & 21.56^{+0.33}_{-0.84} & -16.25^{+0.59}_{-1.18} & -17.33^{+0.58}_{-0.74} \\
-    8.5 & 22.63^{+0.59}_{-1.10} & 21.66^{+0.52}_{-0.54} & 21.94^{+0.71}_{-0.73} & 21.49^{+0.34}_{-0.86} & -16.35^{+0.61}_{-1.21} & -17.45^{+0.60}_{-0.76} \\
-    8.6 & 22.59^{+0.60}_{-1.13} & 21.59^{+0.53}_{-0.55} & 21.86^{+0.75}_{-0.73} & 21.41^{+0.35}_{-0.89} & -16.45^{+0.61}_{-1.24} & -17.57^{+0.61}_{-0.78} \\
-    8.7 & 22.54^{+0.61}_{-1.16} & 21.52^{+0.54}_{-0.57} & 21.78^{+0.78}_{-0.73} & 21.34^{+0.36}_{-0.92} & -16.55^{+0.63}_{-1.26} & -17.69^{+0.63}_{-0.80} \\
-    8.8 & 22.48^{+0.63}_{-1.18} & 21.45^{+0.56}_{-0.58} & 21.69^{+0.81}_{-0.73} & 21.26^{+0.37}_{-0.94} & -16.65^{+0.64}_{-1.28} & -17.82^{+0.64}_{-0.82} \\
-    8.9 & 22.42^{+0.65}_{-1.20} & 21.37^{+0.58}_{-0.59} & 21.61^{+0.84}_{-0.74} & 21.19^{+0.38}_{-0.97} & -16.75^{+0.66}_{-1.31} & -17.94^{+0.67}_{-0.84} \\
-    9.0 & 22.37^{+0.66}_{-1.23} & 21.30^{+0.60}_{-0.61} & 21.53^{+0.87}_{-0.75} & 21.11^{+0.39}_{-0.99} & -16.85^{+0.67}_{-1.33} & -18.06^{+0.69}_{-0.86} \\
-    9.1 & 22.33^{+0.67}_{-1.26} & 21.22^{+0.62}_{-0.62} & 21.45^{+0.90}_{-0.76} & 21.04^{+0.40}_{-1.02} & -16.94^{+0.68}_{-1.36} & -18.18^{+0.72}_{-0.89} \\
-    9.2 & 22.27^{+0.68}_{-1.28} & 21.15^{+0.65}_{-0.64} & 21.36^{+0.93}_{-0.77} & 20.96^{+0.41}_{-1.05} & -17.04^{+0.69}_{-1.38} & -18.30^{+0.74}_{-0.91} \\
-    9.3 & 22.22^{+0.69}_{-1.31} & 21.07^{+0.67}_{-0.66} & 21.29^{+0.95}_{-0.80} & 20.89^{+0.43}_{-1.08} & -17.14^{+0.71}_{-1.41} & -18.41^{+0.77}_{-0.93} \\
-    9.4 & 22.16^{+0.70}_{-1.33} & 21.00^{+0.69}_{-0.67} & 21.21^{+0.97}_{-0.82} & 20.81^{+0.44}_{-1.10} & -17.23^{+0.72}_{-1.43} & -18.53^{+0.79}_{-0.95} \\
-    9.5 & 22.11^{+0.72}_{-1.36} & 20.92^{+0.71}_{-0.68} & 21.13^{+1.00}_{-0.83} & 20.73^{+0.45}_{-1.13} & -17.33^{+0.74}_{-1.45} & -18.65^{+0.81}_{-0.96} \\
-    9.6 & 22.06^{+0.73}_{-1.38} & 20.84^{+0.73}_{-0.70} & 21.05^{+1.03}_{-0.85} & 20.65^{+0.46}_{-1.16} & -17.42^{+0.75}_{-1.47} & -18.77^{+0.83}_{-0.98} \\
-    9.7 & 22.00^{+0.74}_{-1.40} & 20.76^{+0.75}_{-0.72} & 20.97^{+1.06}_{-0.86} & 20.57^{+0.48}_{-1.18} & -17.52^{+0.76}_{-1.49} & -18.89^{+0.85}_{-1.01} \\
-    9.8 & 21.95^{+0.76}_{-1.42} & 20.69^{+0.77}_{-0.73} & 20.88^{+1.10}_{-0.88} & 20.49^{+0.49}_{-1.21} & -17.61^{+0.78}_{-1.51} & -19.01^{+0.87}_{-1.03} \\
-    9.9 & 21.90^{+0.76}_{-1.45} & 20.61^{+0.79}_{-0.75} & 20.80^{+1.13}_{-0.89} & 20.42^{+0.50}_{-1.24} & -17.70^{+0.79}_{-1.54} & -19.12^{+0.89}_{-1.06} \\
-    10.0 & 21.85^{+0.77}_{-1.48} & 20.53^{+0.81}_{-0.77} & 20.72^{+1.16}_{-0.90} & 20.34^{+0.51}_{-1.26} & -17.79^{+0.80}_{-1.57} & -19.23^{+0.91}_{-1.09} \\
+    5.1 & 24.27^{+0.20}_{-0.30} & 23.93^{+0.09}_{-0.15} & 24.14^{+0.20}_{-0.30} & 23.81^{+0.09}_{-0.15} & -13.21^{+0.21}_{-0.32} & -13.55^{+0.09}_{-0.16} \\
+    5.2 & 24.22^{+0.21}_{-0.32} & 23.88^{+0.09}_{-0.17} & 24.09^{+0.21}_{-0.32} & 23.75^{+0.09}_{-0.17} & -13.27^{+0.22}_{-0.33} & -13.62^{+0.10}_{-0.17} \\
+    5.3 & 24.16^{+0.22}_{-0.33} & 23.82^{+0.10}_{-0.18} & 24.03^{+0.22}_{-0.33} & 23.69^{+0.10}_{-0.18} & -13.34^{+0.23}_{-0.34} & -13.69^{+0.11}_{-0.18} \\
+    5.4 & 24.10^{+0.24}_{-0.34} & 23.75^{+0.11}_{-0.19} & 23.98^{+0.24}_{-0.34} & 23.63^{+0.11}_{-0.19} & -13.42^{+0.24}_{-0.36} & -13.77^{+0.11}_{-0.19} \\
+    5.5 & 24.05^{+0.24}_{-0.36} & 23.69^{+0.12}_{-0.19} & 23.93^{+0.24}_{-0.36} & 23.57^{+0.12}_{-0.19} & -13.49^{+0.25}_{-0.37} & -13.85^{+0.12}_{-0.20} \\
+    5.6 & 23.99^{+0.26}_{-0.38} & 23.63^{+0.12}_{-0.20} & 23.87^{+0.26}_{-0.38} & 23.50^{+0.12}_{-0.20} & -13.59^{+0.27}_{-0.38} & -13.95^{+0.12}_{-0.21} \\
+    5.7 & 23.93^{+0.27}_{-0.38} & 23.57^{+0.12}_{-0.22} & 23.81^{+0.27}_{-0.38} & 23.45^{+0.12}_{-0.22} & -13.69^{+0.28}_{-0.39} & -14.05^{+0.13}_{-0.22} \\
+    5.8 & 23.87^{+0.28}_{-0.40} & 23.51^{+0.13}_{-0.23} & 23.75^{+0.28}_{-0.40} & 23.39^{+0.13}_{-0.23} & -13.79^{+0.29}_{-0.40} & -14.15^{+0.13}_{-0.24} \\
+    5.9 & 23.81^{+0.29}_{-0.41} & 23.45^{+0.13}_{-0.25} & 23.69^{+0.29}_{-0.41} & 23.33^{+0.13}_{-0.25} & -13.90^{+0.30}_{-0.42} & -14.26^{+0.14}_{-0.25} \\
+    6.0 & 23.74^{+0.30}_{-0.42} & 23.38^{+0.14}_{-0.25} & 23.62^{+0.30}_{-0.42} & 23.26^{+0.14}_{-0.25} & -14.01^{+0.31}_{-0.43} & -14.38^{+0.15}_{-0.26} \\
+    6.1 & 23.68^{+0.32}_{-0.44} & 23.32^{+0.15}_{-0.26} & 23.56^{+0.32}_{-0.44} & 23.20^{+0.15}_{-0.26} & -14.13^{+0.32}_{-0.44} & -14.49^{+0.15}_{-0.27} \\
+    6.2 & 23.62^{+0.33}_{-0.46} & 23.25^{+0.16}_{-0.27} & 23.50^{+0.33}_{-0.45} & 23.13^{+0.16}_{-0.27} & -14.24^{+0.34}_{-0.46} & -14.61^{+0.16}_{-0.27} \\
+    6.3 & 23.56^{+0.35}_{-0.47} & 23.19^{+0.17}_{-0.27} & 23.44^{+0.35}_{-0.47} & 23.07^{+0.17}_{-0.27} & -14.36^{+0.35}_{-0.48} & -14.74^{+0.17}_{-0.28} \\
+    6.4 & 23.50^{+0.36}_{-0.49} & 23.12^{+0.18}_{-0.28} & 23.38^{+0.36}_{-0.49} & 23.00^{+0.18}_{-0.28} & -14.48^{+0.36}_{-0.50} & -14.87^{+0.18}_{-0.28} \\
+    6.5 & 23.45^{+0.36}_{-0.52} & 23.05^{+0.18}_{-0.29} & 23.33^{+0.36}_{-0.52} & 22.93^{+0.18}_{-0.29} & -14.60^{+0.37}_{-0.52} & -15.00^{+0.19}_{-0.29} \\
+    6.6 & 23.38^{+0.37}_{-0.53} & 22.99^{+0.19}_{-0.30} & 23.26^{+0.37}_{-0.53} & 22.86^{+0.19}_{-0.30} & -14.74^{+0.38}_{-0.54} & -15.13^{+0.20}_{-0.30} \\
+    6.7 & 23.31^{+0.39}_{-0.54} & 22.92^{+0.20}_{-0.31} & 23.19^{+0.39}_{-0.54} & 22.80^{+0.20}_{-0.31} & -14.88^{+0.40}_{-0.55} & -15.28^{+0.21}_{-0.31} \\
+    6.8 & 23.24^{+0.41}_{-0.56} & 22.85^{+0.22}_{-0.32} & 23.12^{+0.41}_{-0.56} & 22.72^{+0.22}_{-0.32} & -15.03^{+0.41}_{-0.56} & -15.42^{+0.22}_{-0.32} \\
+    6.9 & 23.17^{+0.42}_{-0.57} & 22.77^{+0.23}_{-0.33} & 23.05^{+0.42}_{-0.57} & 22.65^{+0.23}_{-0.33} & -15.18^{+0.43}_{-0.58} & -15.57^{+0.23}_{-0.33} \\
+    7.0 & 23.11^{+0.44}_{-0.59} & 22.70^{+0.24}_{-0.34} & 22.98^{+0.44}_{-0.59} & 22.58^{+0.24}_{-0.34} & -15.33^{+0.44}_{-0.59} & -15.73^{+0.24}_{-0.34} \\
+    7.1 & 23.04^{+0.45}_{-0.61} & 22.64^{+0.25}_{-0.35} & 22.91^{+0.45}_{-0.61} & 22.51^{+0.25}_{-0.35} & -15.48^{+0.46}_{-0.61} & -15.88^{+0.25}_{-0.36} \\
+    7.2 & 22.96^{+0.47}_{-0.62} & 22.57^{+0.26}_{-0.37} & 22.84^{+0.47}_{-0.62} & 22.44^{+0.26}_{-0.37} & -15.64^{+0.48}_{-0.62} & -16.03^{+0.26}_{-0.37} \\
+    7.3 & 22.89^{+0.49}_{-0.63} & 22.50^{+0.27}_{-0.38} & 22.77^{+0.49}_{-0.63} & 22.38^{+0.27}_{-0.38} & -15.79^{+0.50}_{-0.63} & -16.19^{+0.27}_{-0.38} \\
+    7.4 & 22.84^{+0.51}_{-0.65} & 22.43^{+0.28}_{-0.39} & 22.71^{+0.51}_{-0.65} & 22.31^{+0.28}_{-0.39} & -15.94^{+0.51}_{-0.65} & -16.35^{+0.28}_{-0.40} \\
+    7.5 & 22.77^{+0.51}_{-0.67} & 22.36^{+0.28}_{-0.41} & 22.65^{+0.51}_{-0.67} & 22.24^{+0.28}_{-0.41} & -16.09^{+0.52}_{-0.68} & -16.50^{+0.29}_{-0.41} \\
+    7.6 & 22.70^{+0.53}_{-0.69} & 22.29^{+0.29}_{-0.42} & 22.58^{+0.53}_{-0.69} & 22.17^{+0.29}_{-0.42} & -16.24^{+0.53}_{-0.69} & -16.66^{+0.30}_{-0.42} \\
+    7.7 & 22.63^{+0.54}_{-0.70} & 22.22^{+0.31}_{-0.43} & 22.51^{+0.54}_{-0.70} & 22.10^{+0.31}_{-0.43} & -16.40^{+0.55}_{-0.71} & -16.81^{+0.31}_{-0.44} \\
+    7.8 & 22.56^{+0.56}_{-0.72} & 22.15^{+0.31}_{-0.45} & 22.44^{+0.56}_{-0.73} & 22.03^{+0.31}_{-0.45} & -16.55^{+0.57}_{-0.73} & -16.96^{+0.31}_{-0.45} \\
+    7.9 & 22.49^{+0.58}_{-0.74} & 22.08^{+0.32}_{-0.46} & 22.36^{+0.58}_{-0.74} & 21.96^{+0.32}_{-0.46} & -16.71^{+0.59}_{-0.75} & -17.12^{+0.32}_{-0.47} \\
+    8.0 & 22.42^{+0.60}_{-0.76} & 22.01^{+0.32}_{-0.48} & 22.30^{+0.60}_{-0.76} & 21.89^{+0.32}_{-0.48} & -16.85^{+0.61}_{-0.77} & -17.27^{+0.32}_{-0.48} \\
+    8.1 & 22.35^{+0.62}_{-0.78} & 21.94^{+0.33}_{-0.49} & 22.23^{+0.62}_{-0.78} & 21.81^{+0.33}_{-0.49} & -17.00^{+0.63}_{-0.78} & -17.42^{+0.34}_{-0.50} \\
+    8.2 & 22.28^{+0.64}_{-0.80} & 21.86^{+0.34}_{-0.51} & 22.16^{+0.64}_{-0.80} & 21.74^{+0.34}_{-0.50} & -17.14^{+0.65}_{-0.81} & -17.57^{+0.35}_{-0.51} \\
+    8.3 & 22.21^{+0.67}_{-0.82} & 21.79^{+0.36}_{-0.52} & 22.09^{+0.67}_{-0.82} & 21.66^{+0.36}_{-0.52} & -17.29^{+0.67}_{-0.82} & -17.71^{+0.36}_{-0.52} \\
+    8.4 & 22.13^{+0.69}_{-0.83} & 21.72^{+0.37}_{-0.53} & 22.01^{+0.69}_{-0.83} & 21.59^{+0.37}_{-0.53} & -17.44^{+0.70}_{-0.84} & -17.86^{+0.37}_{-0.53} \\
+    8.5 & 22.06^{+0.71}_{-0.86} & 21.64^{+0.38}_{-0.54} & 21.94^{+0.71}_{-0.86} & 21.52^{+0.38}_{-0.54} & -17.58^{+0.72}_{-0.86} & -18.01^{+0.38}_{-0.54} \\
+    8.6 & 21.98^{+0.74}_{-0.87} & 21.56^{+0.39}_{-0.55} & 21.86^{+0.74}_{-0.87} & 21.44^{+0.39}_{-0.55} & -17.73^{+0.75}_{-0.88} & -18.15^{+0.39}_{-0.55} \\
+    8.7 & 21.91^{+0.76}_{-0.89} & 21.49^{+0.40}_{-0.56} & 21.79^{+0.76}_{-0.89} & 21.36^{+0.40}_{-0.56} & -17.87^{+0.77}_{-0.90} & -18.30^{+0.41}_{-0.56} \\
+    8.8 & 21.84^{+0.78}_{-0.92} & 21.41^{+0.42}_{-0.57} & 21.72^{+0.78}_{-0.92} & 21.28^{+0.42}_{-0.57} & -18.01^{+0.79}_{-0.92} & -18.44^{+0.42}_{-0.57} \\
+    8.9 & 21.76^{+0.80}_{-0.94} & 21.33^{+0.43}_{-0.58} & 21.64^{+0.80}_{-0.94} & 21.20^{+0.43}_{-0.58} & -18.15^{+0.81}_{-0.95} & -18.59^{+0.44}_{-0.58} \\
+    9.0 & 21.68^{+0.82}_{-0.96} & 21.25^{+0.45}_{-0.58} & 21.56^{+0.82}_{-0.96} & 21.12^{+0.45}_{-0.58} & -18.29^{+0.83}_{-0.96} & -18.73^{+0.46}_{-0.59} \\
+    9.1 & 21.60^{+0.85}_{-0.97} & 21.17^{+0.46}_{-0.60} & 21.48^{+0.85}_{-0.97} & 21.05^{+0.46}_{-0.60} & -18.44^{+0.86}_{-0.98} & -18.87^{+0.47}_{-0.60} \\
+    9.2 & 21.52^{+0.87}_{-0.99} & 21.09^{+0.48}_{-0.61} & 21.40^{+0.87}_{-0.99} & 20.97^{+0.48}_{-0.61} & -18.58^{+0.88}_{-1.00} & -19.01^{+0.48}_{-0.62} \\
+    9.3 & 21.45^{+0.89}_{-1.01} & 21.02^{+0.49}_{-0.63} & 21.33^{+0.89}_{-1.01} & 20.89^{+0.49}_{-0.63} & -18.71^{+0.90}_{-1.01} & -19.15^{+0.49}_{-0.63} \\
+    9.4 & 21.37^{+0.90}_{-1.02} & 20.94^{+0.50}_{-0.64} & 21.25^{+0.90}_{-1.02} & 20.82^{+0.50}_{-0.64} & -18.85^{+0.91}_{-1.03} & -19.29^{+0.50}_{-0.64} \\
+    9.5 & 21.30^{+0.92}_{-1.05} & 20.86^{+0.51}_{-0.64} & 21.18^{+0.92}_{-1.05} & 20.74^{+0.51}_{-0.64} & -18.98^{+0.93}_{-1.05} & -19.42^{+0.52}_{-0.65} \\
+    9.6 & 21.23^{+0.94}_{-1.07} & 20.78^{+0.52}_{-0.65} & 21.10^{+0.94}_{-1.07} & 20.66^{+0.52}_{-0.65} & -19.12^{+0.95}_{-1.08} & -19.56^{+0.53}_{-0.66} \\
+    9.7 & 21.15^{+0.96}_{-1.09} & 20.70^{+0.54}_{-0.67} & 21.02^{+0.96}_{-1.09} & 20.58^{+0.54}_{-0.67} & -19.25^{+0.97}_{-1.10} & -19.70^{+0.54}_{-0.67} \\
+    9.8 & 21.07^{+0.98}_{-1.11} & 20.62^{+0.55}_{-0.68} & 20.95^{+0.98}_{-1.11} & 20.50^{+0.55}_{-0.68} & -19.38^{+1.00}_{-1.12} & -19.84^{+0.55}_{-0.68} \\
+    9.9 & 20.99^{+1.01}_{-1.14} & 20.54^{+0.56}_{-0.69} & 20.87^{+1.01}_{-1.14} & 20.42^{+0.56}_{-0.69} & -19.52^{+1.02}_{-1.14} & -19.97^{+0.57}_{-0.69} \\
+    10.0 & 20.91^{+1.03}_{-1.16} & 20.46^{+0.57}_{-0.70} & 20.79^{+1.03}_{-1.16} & 20.34^{+0.57}_{-0.70} & -19.65^{+1.05}_{-1.17} & -20.10^{+0.57}_{-0.71} \\
     \hline
@@
     \hline
-    10.0 & 21.85^{+0.77}_{-1.48} & 20.53^{+0.81}_{-0.77} & 20.72^{+1.16}_{-0.90} & 20.34^{+0.51}_{-1.26} & -17.79^{+0.80}_{-1.57} & -19.23^{+0.91}_{-1.09} \\
-    10.1 & 21.80^{+0.80}_{-1.50} & 20.46^{+0.83}_{-0.79} & 20.63^{+1.19}_{-0.91} & 20.26^{+0.52}_{-1.29} & -17.88^{+0.83}_{-1.58} & -19.35^{+0.93}_{-1.11} \\
-    10.2 & 21.74^{+0.83}_{-1.52} & 20.38^{+0.85}_{-0.81} & 20.55^{+1.23}_{-0.93} & 20.18^{+0.53}_{-1.31} & -17.97^{+0.85}_{-1.60} & -19.46^{+0.96}_{-1.13} \\
-    10.3 & 21.69^{+0.85}_{-1.54} & 20.31^{+0.88}_{-0.83} & 20.47^{+1.26}_{-0.94} & 20.10^{+0.54}_{-1.34} & -18.07^{+0.87}_{-1.62} & -19.57^{+0.98}_{-1.16} \\
-    10.4 & 21.63^{+0.87}_{-1.56} & 20.23^{+0.90}_{-0.85} & 20.39^{+1.29}_{-0.95} & 20.03^{+0.55}_{-1.36} & -18.16^{+0.89}_{-1.64} & -19.69^{+1.01}_{-1.18} \\
-    10.5 & 21.58^{+0.89}_{-1.59} & 20.15^{+0.93}_{-0.87} & 20.31^{+1.31}_{-0.96} & 19.95^{+0.56}_{-1.39} & -18.25^{+0.90}_{-1.67} & -19.80^{+1.03}_{-1.21} \\
-    10.6 & 21.52^{+0.90}_{-1.62} & 20.07^{+0.95}_{-0.89} & 20.22^{+1.35}_{-0.97} & 19.87^{+0.58}_{-1.42} & -18.34^{+0.91}_{-1.69} & -19.91^{+1.05}_{-1.23} \\
-    10.7 & 21.47^{+0.90}_{-1.65} & 19.99^{+0.97}_{-0.90} & 20.13^{+1.38}_{-0.98} & 19.79^{+0.59}_{-1.44} & -18.43^{+0.92}_{-1.72} & -20.03^{+1.08}_{-1.25} \\
-    10.8 & 21.42^{+0.91}_{-1.67} & 19.91^{+0.99}_{-0.92} & 20.04^{+1.42}_{-0.99} & 19.71^{+0.60}_{-1.47} & -18.52^{+0.93}_{-1.74} & -20.15^{+1.10}_{-1.27} \\
-    10.9 & 21.36^{+0.93}_{-1.70} & 19.83^{+1.01}_{-0.94} & 19.95^{+1.46}_{-1.00} & 19.63^{+0.61}_{-1.50} & -18.62^{+0.95}_{-1.76} & -20.26^{+1.13}_{-1.29} \\
-    11.0 & 21.30^{+0.94}_{-1.72} & 19.75^{+1.04}_{-0.96} & 19.86^{+1.50}_{-1.01} & 19.55^{+0.62}_{-1.53} & -18.71^{+0.96}_{-1.78} & -20.38^{+1.16}_{-1.32} \\
-    11.1 & 21.24^{+0.96}_{-1.74} & 19.67^{+1.08}_{-0.98} & 19.78^{+1.53}_{-1.03} & 19.47^{+0.63}_{-1.56} & -18.81^{+0.98}_{-1.81} & -20.49^{+1.20}_{-1.34} \\
-    11.2 & 21.18^{+0.97}_{-1.76} & 19.59^{+1.12}_{-1.00} & 19.69^{+1.56}_{-1.04} & 19.39^{+0.64}_{-1.59} & -18.90^{+0.99}_{-1.82} & -20.60^{+1.24}_{-1.36} \\
-    11.3 & 21.12^{+0.99}_{-1.78} & 19.51^{+1.15}_{-1.01} & 19.60^{+1.60}_{-1.05} & 19.31^{+0.66}_{-1.62} & -18.99^{+1.01}_{-1.84} & -20.72^{+1.28}_{-1.39} \\
-    11.4 & 21.06^{+1.00}_{-1.79} & 19.43^{+1.20}_{-1.03} & 19.51^{+1.63}_{-1.06} & 19.23^{+0.67}_{-1.65} & -19.09^{+1.02}_{-1.85} & -20.83^{+1.32}_{-1.40} \\
-    11.5 & 21.00^{+1.02}_{-1.82} & 19.35^{+1.23}_{-1.05} & 19.42^{+1.67}_{-1.07} & 19.15^{+0.68}_{-1.68} & -19.18^{+1.04}_{-1.88} & -20.95^{+1.35}_{-1.42} \\
-    11.6 & 20.94^{+1.03}_{-1.84} & 19.27^{+1.27}_{-1.06} & 19.32^{+1.71}_{-1.08} & 19.07^{+0.69}_{-1.71} & -19.27^{+1.05}_{-1.90} & -21.07^{+1.39}_{-1.44} \\
-    11.7 & 20.88^{+1.05}_{-1.86} & 19.18^{+1.31}_{-1.08} & 19.23^{+1.75}_{-1.09} & 18.99^{+0.70}_{-1.74} & -19.37^{+1.07}_{-1.92} & -21.18^{+1.43}_{-1.45} \\
-    11.8 & 20.82^{+1.06}_{-1.88} & 19.10^{+1.35}_{-1.09} & 19.14^{+1.79}_{-1.10} & 18.91^{+0.71}_{-1.77} & -19.46^{+1.09}_{-1.94} & -21.30^{+1.46}_{-1.47} \\
-    11.9 & 20.76^{+1.08}_{-1.90} & 19.01^{+1.38}_{-1.10} & 19.04^{+1.83}_{-1.11} & 18.83^{+0.72}_{-1.80} & -19.56^{+1.10}_{-1.96} & -21.41^{+1.49}_{-1.48} \\
-    12.0 & 20.70^{+1.10}_{-1.93} & 18.93^{+1.41}_{-1.11} & 18.95^{+1.86}_{-1.13} & 18.75^{+0.73}_{-1.82} & -19.65^{+1.12}_{-1.98} & -21.52^{+1.52}_{-1.50} \\
-    12.1 & 20.64^{+1.12}_{-1.95} & 18.86^{+1.43}_{-1.14} & 18.87^{+1.90}_{-1.14} & 18.67^{+0.74}_{-1.85} & -19.74^{+1.14}_{-2.00} & -21.63^{+1.55}_{-1.52} \\
-    12.2 & 20.58^{+1.14}_{-1.97} & 18.78^{+1.46}_{-1.16} & 18.78^{+1.93}_{-1.16} & 18.59^{+0.76}_{-1.88} & -19.83^{+1.16}_{-2.03} & -21.74^{+1.57}_{-1.54} \\
-    12.3 & 20.52^{+1.16}_{-1.99} & 18.70^{+1.50}_{-1.18} & 18.69^{+1.96}_{-1.18} & 18.51^{+0.77}_{-1.91} & -19.92^{+1.18}_{-2.05} & -21.85^{+1.61}_{-1.56} \\
-    12.4 & 20.46^{+1.16}_{-2.02} & 18.62^{+1.53}_{-1.20} & 18.60^{+1.99}_{-1.20} & 18.42^{+0.78}_{-1.93} & -20.01^{+1.19}_{-2.08} & -21.96^{+1.64}_{-1.58} \\
-    12.5 & 20.41^{+1.17}_{-2.05} & 18.54^{+1.56}_{-1.22} & 18.52^{+2.02}_{-1.22} & 18.34^{+0.80}_{-1.96} & -20.10^{+1.20}_{-2.10} & -22.07^{+1.67}_{-1.60} \\
-    12.6 & 20.35^{+1.19}_{-2.07} & 18.46^{+1.59}_{-1.24} & 18.43^{+2.05}_{-1.24} & 18.25^{+0.81}_{-1.98} & -20.19^{+1.22}_{-2.12} & -22.18^{+1.70}_{-1.63} \\
-    12.7 & 20.29^{+1.21}_{-2.09} & 18.38^{+1.62}_{-1.26} & 18.35^{+2.07}_{-1.27} & 18.17^{+0.82}_{-2.01} & -20.28^{+1.24}_{-2.14} & -22.29^{+1.72}_{-1.65} \\
-    12.8 & 20.23^{+1.23}_{-2.12} & 18.29^{+1.65}_{-1.28} & 18.27^{+2.10}_{-1.29} & 18.09^{+0.83}_{-2.04} & -20.37^{+1.26}_{-2.16} & -22.41^{+1.76}_{-1.66} \\
-    12.9 & 20.17^{+1.25}_{-2.14} & 18.21^{+1.68}_{-1.29} & 18.19^{+2.12}_{-1.32} & 18.01^{+0.84}_{-2.07} & -20.46^{+1.28}_{-2.19} & -22.52^{+1.79}_{-1.68} \\
-    13.0 & 20.11^{+1.28}_{-2.16} & 18.12^{+1.71}_{-1.31} & 18.11^{+2.15}_{-1.35} & 17.92^{+0.85}_{-2.09} & -20.55^{+1.30}_{-2.21} & -22.64^{+1.82}_{-1.69} \\
-    13.1 & 20.05^{+1.30}_{-2.18} & 18.04^{+1.75}_{-1.32} & 18.02^{+2.18}_{-1.37} & 17.84^{+0.86}_{-2.12} & -20.64^{+1.31}_{-2.23} & -22.75^{+1.86}_{-1.71} \\
-    13.2 & 19.99^{+1.31}_{-2.21} & 17.95^{+1.79}_{-1.34} & 17.93^{+2.21}_{-1.39} & 17.76^{+0.88}_{-2.15} & -20.73^{+1.33}_{-2.26} & -22.86^{+1.89}_{-1.72} \\
-    13.3 & 19.93^{+1.32}_{-2.24} & 17.87^{+1.83}_{-1.36} & 17.84^{+2.24}_{-1.41} & 17.67^{+0.89}_{-2.17} & -20.81^{+1.34}_{-2.29} & -22.98^{+1.93}_{-1.74} \\
-    13.4 & 19.88^{+1.33}_{-2.27} & 17.79^{+1.86}_{-1.37} & 17.76^{+2.27}_{-1.43} & 17.59^{+0.91}_{-2.20} & -20.90^{+1.34}_{-2.32} & -23.09^{+1.96}_{-1.75} \\
-    13.5 & 19.83^{+1.34}_{-2.30} & 17.70^{+1.90}_{-1.39} & 17.66^{+2.30}_{-1.45} & 17.51^{+0.92}_{-2.23} & -20.98^{+1.35}_{-2.35} & -23.21^{+2.00}_{-1.77} \\
-    13.6 & 19.78^{+1.34}_{-2.33} & 17.62^{+1.93}_{-1.41} & 17.57^{+2.33}_{-1.46} & 17.42^{+0.93}_{-2.26} & -21.06^{+1.36}_{-2.38} & -23.32^{+2.03}_{-1.78} \\
-    13.7 & 19.72^{+1.35}_{-2.36} & 17.53^{+1.97}_{-1.42} & 17.48^{+2.36}_{-1.48} & 17.34^{+0.95}_{-2.29} & -21.15^{+1.37}_{-2.40} & -23.43^{+2.06}_{-1.79} \\
-    13.8 & 19.67^{+1.37}_{-2.38} & 17.45^{+2.00}_{-1.44} & 17.39^{+2.39}_{-1.50} & 17.25^{+0.96}_{-2.32} & -21.24^{+1.38}_{-2.43} & -23.54^{+2.09}_{-1.81} \\
-    13.9 & 19.61^{+1.38}_{-2.41} & 17.37^{+2.03}_{-1.46} & 17.30^{+2.42}_{-1.52} & 17.17^{+0.97}_{-2.35} & -21.32^{+1.39}_{-2.46} & -23.65^{+2.12}_{-1.83} \\
-    14.0 & 19.55^{+1.39}_{-2.44} & 17.29^{+2.06}_{-1.48} & 17.21^{+2.45}_{-1.54} & 17.09^{+0.99}_{-2.38} & -21.41^{+1.40}_{-2.48} & -23.76^{+2.15}_{-1.84} \\
-    14.1 & 19.50^{+1.40}_{-2.46} & 17.20^{+2.10}_{-1.50} & 17.12^{+2.48}_{-1.55} & 17.00^{+1.00}_{-2.41} & -21.49^{+1.41}_{-2.51} & -23.87^{+2.18}_{-1.86} \\
-    14.2 & 19.44^{+1.41}_{-2.50} & 17.12^{+2.13}_{-1.52} & 17.03^{+2.51}_{-1.56} & 16.92^{+1.01}_{-2.44} & -21.58^{+1.42}_{-2.54} & -23.98^{+2.21}_{-1.87} \\
-    14.3 & 19.39^{+1.42}_{-2.53} & 17.04^{+2.16}_{-1.54} & 16.94^{+2.54}_{-1.57} & 16.83^{+1.02}_{-2.47} & -21.66^{+1.43}_{-2.57} & -24.09^{+2.24}_{-1.89} \\
-    14.4 & 19.34^{+1.43}_{-2.56} & 16.96^{+2.19}_{-1.56} & 16.85^{+2.57}_{-1.58} & 16.75^{+1.04}_{-2.50} & -21.75^{+1.44}_{-2.60} & -24.20^{+2.26}_{-1.91} \\
-    14.5 & 19.29^{+1.44}_{-2.60} & 16.88^{+2.22}_{-1.58} & 16.76^{+2.60}_{-1.59} & 16.66^{+1.05}_{-2.53} & -21.84^{+1.45}_{-2.63} & -24.32^{+2.29}_{-1.93} \\
-    14.6 & 19.24^{+1.46}_{-2.63} & 16.80^{+2.25}_{-1.60} & 16.67^{+2.63}_{-1.60} & 16.58^{+1.06}_{-2.56} & -21.93^{+1.47}_{-2.66} & -24.43^{+2.32}_{-1.94} \\
-    14.7 & 19.18^{+1.47}_{-2.65} & 16.72^{+2.28}_{-1.62} & 16.57^{+2.66}_{-1.61} & 16.50^{+1.07}_{-2.59} & -22.03^{+1.48}_{-2.68} & -24.56^{+2.34}_{-1.96} \\
-    14.8 & 19.13^{+1.48}_{-2.69} & 16.64^{+2.31}_{-1.64} & 16.48^{+2.69}_{-1.63} & 16.41^{+1.09}_{-2.61} & -22.15^{+1.48}_{-2.71} & -24.69^{+2.37}_{-1.97} \\
-    14.9 & 19.08^{+1.48}_{-2.72} & 16.56^{+2.34}_{-1.66} & 16.39^{+2.72}_{-1.64} & 16.33^{+1.10}_{-2.64} & -22.28^{+1.48}_{-2.74} & -24.85^{+2.39}_{-1.99} \\
-    15.0 & 19.02^{+1.49}_{-2.75} & 16.48^{+2.37}_{-1.68} & 16.30^{+2.75}_{-1.66} & 16.24^{+1.11}_{-2.67} & -22.50^{+1.49}_{-2.76} & -25.08^{+2.41}_{-2.00} \\
+    10.1 & 20.84^{+1.06}_{-1.18} & 20.39^{+0.58}_{-0.72} & 20.72^{+1.06}_{-1.18} & 20.26^{+0.58}_{-0.72} & -19.78^{+1.07}_{-1.19} & -20.23^{+0.58}_{-0.73} \\
+    10.2 & 20.76^{+1.08}_{-1.20} & 20.31^{+0.59}_{-0.74} & 20.63^{+1.08}_{-1.20} & 20.18^{+0.59}_{-0.74} & -19.92^{+1.10}_{-1.20} & -20.37^{+0.60}_{-0.74} \\
+    10.3 & 20.67^{+1.11}_{-1.21} & 20.23^{+0.60}_{-0.75} & 20.55^{+1.11}_{-1.21} & 20.11^{+0.60}_{-0.75} & -20.05^{+1.12}_{-1.22} & -20.50^{+0.61}_{-0.75} \\
+    10.4 & 20.59^{+1.14}_{-1.23} & 20.15^{+0.61}_{-0.76} & 20.47^{+1.14}_{-1.23} & 20.03^{+0.61}_{-0.76} & -20.19^{+1.15}_{-1.24} & -20.63^{+0.62}_{-0.77} \\
+    10.5 & 20.51^{+1.16}_{-1.25} & 20.07^{+0.62}_{-0.77} & 20.39^{+1.16}_{-1.25} & 19.95^{+0.62}_{-0.77} & -20.32^{+1.18}_{-1.26} & -20.76^{+0.63}_{-0.78} \\
+    10.6 & 20.43^{+1.18}_{-1.28} & 19.99^{+0.64}_{-0.79} & 20.31^{+1.18}_{-1.28} & 19.87^{+0.64}_{-0.79} & -20.45^{+1.20}_{-1.29} & -20.89^{+0.64}_{-0.79} \\
+    10.7 & 20.35^{+1.21}_{-1.30} & 19.91^{+0.65}_{-0.80} & 20.23^{+1.21}_{-1.30} & 19.79^{+0.65}_{-0.80} & -20.58^{+1.23}_{-1.30} & -21.02^{+0.66}_{-0.81} \\
+    10.8 & 20.26^{+1.24}_{-1.31} & 19.83^{+0.66}_{-0.82} & 20.14^{+1.24}_{-1.31} & 19.71^{+0.66}_{-0.82} & -20.72^{+1.25}_{-1.32} & -21.15^{+0.67}_{-0.82} \\
+    10.9 & 20.18^{+1.26}_{-1.33} & 19.75^{+0.68}_{-0.83} & 20.06^{+1.26}_{-1.33} & 19.63^{+0.68}_{-0.83} & -20.85^{+1.28}_{-1.34} & -21.28^{+0.68}_{-0.84} \\
+    11.0 & 20.10^{+1.29}_{-1.35} & 19.67^{+0.69}_{-0.85} & 19.98^{+1.29}_{-1.35} & 19.55^{+0.69}_{-0.85} & -20.98^{+1.30}_{-1.35} & -21.41^{+0.69}_{-0.86} \\
+    11.1 & 20.02^{+1.32}_{-1.36} & 19.60^{+0.70}_{-0.87} & 19.89^{+1.32}_{-1.36} & 19.47^{+0.70}_{-0.87} & -21.11^{+1.33}_{-1.37} & -21.53^{+0.70}_{-0.88} \\
+    11.2 & 19.93^{+1.35}_{-1.38} & 19.52^{+0.71}_{-0.88} & 19.81^{+1.35}_{-1.38} & 19.40^{+0.71}_{-0.88} & -21.25^{+1.36}_{-1.39} & -21.66^{+0.72}_{-0.89} \\
+    11.3 & 19.85^{+1.37}_{-1.40} & 19.44^{+0.72}_{-0.90} & 19.73^{+1.37}_{-1.40} & 19.32^{+0.72}_{-0.90} & -21.38^{+1.39}_{-1.42} & -21.78^{+0.73}_{-0.91} \\
+    11.4 & 19.77^{+1.40}_{-1.43} & 19.36^{+0.73}_{-0.92} & 19.64^{+1.40}_{-1.43} & 19.24^{+0.73}_{-0.92} & -21.51^{+1.41}_{-1.44} & -21.91^{+0.73}_{-0.93} \\
+    11.5 & 19.69^{+1.42}_{-1.46} & 19.29^{+0.74}_{-0.94} & 19.57^{+1.42}_{-1.46} & 19.16^{+0.74}_{-0.94} & -21.63^{+1.43}_{-1.47} & -22.03^{+0.74}_{-0.95} \\
+    11.6 & 19.60^{+1.45}_{-1.47} & 19.21^{+0.75}_{-0.96} & 19.48^{+1.45}_{-1.47} & 19.08^{+0.75}_{-0.96} & -21.76^{+1.46}_{-1.48} & -22.16^{+0.75}_{-0.97} \\
+    11.7 & 19.52^{+1.47}_{-1.49} & 19.13^{+0.76}_{-0.98} & 19.40^{+1.47}_{-1.49} & 19.00^{+0.76}_{-0.98} & -21.89^{+1.49}_{-1.50} & -22.29^{+0.76}_{-0.99} \\
+    11.8 & 19.44^{+1.50}_{-1.51} & 19.05^{+0.77}_{-1.00} & 19.32^{+1.50}_{-1.51} & 18.92^{+0.77}_{-1.00} & -22.02^{+1.51}_{-1.52} & -22.41^{+0.78}_{-1.00} \\
+    11.9 & 19.35^{+1.52}_{-1.53} & 18.96^{+0.78}_{-1.01} & 19.23^{+1.52}_{-1.53} & 18.84^{+0.78}_{-1.01} & -22.15^{+1.54}_{-1.54} & -22.54^{+0.79}_{-1.02} \\
+    12.0 & 19.27^{+1.55}_{-1.55} & 18.88^{+0.80}_{-1.03} & 19.14^{+1.55}_{-1.55} & 18.76^{+0.80}_{-1.03} & -22.28^{+1.57}_{-1.56} & -22.67^{+0.80}_{-1.04} \\
+    12.1 & 19.18^{+1.58}_{-1.57} & 18.80^{+0.81}_{-1.05} & 19.06^{+1.58}_{-1.57} & 18.68^{+0.81}_{-1.05} & -22.41^{+1.59}_{-1.58} & -22.79^{+0.81}_{-1.06} \\
+    12.2 & 19.10^{+1.60}_{-1.60} & 18.72^{+0.82}_{-1.07} & 18.98^{+1.60}_{-1.60} & 18.60^{+0.82}_{-1.07} & -22.54^{+1.62}_{-1.61} & -22.92^{+0.83}_{-1.07} \\
+    12.3 & 19.01^{+1.63}_{-1.62} & 18.64^{+0.83}_{-1.08} & 18.89^{+1.63}_{-1.62} & 18.51^{+0.83}_{-1.08} & -22.67^{+1.65}_{-1.63} & -23.04^{+0.84}_{-1.09} \\
+    12.4 & 18.92^{+1.66}_{-1.64} & 18.56^{+0.84}_{-1.09} & 18.80^{+1.66}_{-1.64} & 18.43^{+0.84}_{-1.09} & -22.80^{+1.68}_{-1.65} & -23.17^{+0.85}_{-1.10} \\
+    12.5 & 18.84^{+1.69}_{-1.66} & 18.48^{+0.85}_{-1.11} & 18.72^{+1.69}_{-1.66} & 18.35^{+0.85}_{-1.11} & -22.93^{+1.70}_{-1.68} & -23.29^{+0.86}_{-1.12} \\
+    12.6 & 18.76^{+1.71}_{-1.69} & 18.39^{+0.86}_{-1.13} & 18.64^{+1.71}_{-1.69} & 18.27^{+0.86}_{-1.12} & -23.05^{+1.73}_{-1.70} & -23.42^{+0.87}_{-1.13} \\
+    12.7 & 18.68^{+1.74}_{-1.72} & 18.31^{+0.88}_{-1.14} & 18.56^{+1.74}_{-1.72} & 18.19^{+0.88}_{-1.14} & -23.18^{+1.75}_{-1.73} & -23.54^{+0.88}_{-1.15} \\
+    12.8 & 18.59^{+1.76}_{-1.74} & 18.23^{+0.89}_{-1.16} & 18.47^{+1.76}_{-1.74} & 18.11^{+0.89}_{-1.16} & -23.30^{+1.78}_{-1.75} & -23.67^{+0.90}_{-1.16} \\
+    12.9 & 18.51^{+1.78}_{-1.76} & 18.15^{+0.90}_{-1.17} & 18.39^{+1.78}_{-1.76} & 18.02^{+0.90}_{-1.17} & -23.43^{+1.80}_{-1.78} & -23.79^{+0.91}_{-1.18} \\
+    13.0 & 18.43^{+1.81}_{-1.79} & 18.06^{+0.91}_{-1.19} & 18.31^{+1.81}_{-1.79} & 17.94^{+0.91}_{-1.19} & -23.55^{+1.82}_{-1.81} & -23.92^{+0.92}_{-1.19} \\
+    13.1 & 18.34^{+1.83}_{-1.82} & 17.98^{+0.93}_{-1.20} & 18.22^{+1.83}_{-1.82} & 17.86^{+0.93}_{-1.20} & -23.68^{+1.85}_{-1.83} & -24.04^{+0.93}_{-1.21} \\
+    13.2 & 18.25^{+1.86}_{-1.84} & 17.90^{+0.94}_{-1.22} & 18.13^{+1.86}_{-1.84} & 17.77^{+0.94}_{-1.22} & -23.81^{+1.88}_{-1.85} & -24.16^{+0.95}_{-1.23} \\
+    13.3 & 18.17^{+1.89}_{-1.86} & 17.82^{+0.95}_{-1.23} & 18.05^{+1.89}_{-1.86} & 17.69^{+0.95}_{-1.23} & -23.94^{+1.91}_{-1.88} & -24.29^{+0.96}_{-1.24} \\
+    13.4 & 18.08^{+1.91}_{-1.89} & 17.73^{+0.96}_{-1.25} & 17.96^{+1.91}_{-1.89} & 17.61^{+0.96}_{-1.25} & -24.06^{+1.93}_{-1.90} & -24.41^{+0.97}_{-1.26} \\
+    13.5 & 17.99^{+1.94}_{-1.91} & 17.65^{+0.97}_{-1.27} & 17.87^{+1.94}_{-1.91} & 17.53^{+0.97}_{-1.27} & -24.19^{+1.96}_{-1.92} & -24.53^{+0.98}_{-1.28} \\
+    13.6 & 17.91^{+1.97}_{-1.93} & 17.57^{+0.99}_{-1.28} & 17.78^{+1.97}_{-1.93} & 17.45^{+0.99}_{-1.28} & -24.32^{+1.99}_{-1.95} & -24.66^{+1.00}_{-1.29} \\
+    13.7 & 17.82^{+2.00}_{-1.96} & 17.48^{+1.00}_{-1.30} & 17.70^{+2.00}_{-1.96} & 17.36^{+1.00}_{-1.30} & -24.45^{+2.01}_{-1.97} & -24.78^{+1.01}_{-1.31} \\
+    13.8 & 17.73^{+2.02}_{-1.98} & 17.40^{+1.02}_{-1.31} & 17.61^{+2.02}_{-1.98} & 17.28^{+1.02}_{-1.31} & -24.57^{+2.04}_{-2.00} & -24.91^{+1.03}_{-1.32} \\
+    13.9 & 17.65^{+2.05}_{-2.01} & 17.31^{+1.03}_{-1.32} & 17.53^{+2.05}_{-2.01} & 17.19^{+1.03}_{-1.32} & -24.69^{+2.06}_{-2.02} & -25.03^{+1.04}_{-1.33} \\
+    14.0 & 17.57^{+2.07}_{-2.04} & 17.23^{+1.05}_{-1.34} & 17.44^{+2.07}_{-2.04} & 17.11^{+1.05}_{-1.34} & -24.82^{+2.09}_{-2.05} & -25.16^{+1.05}_{-1.35} \\
+    14.1 & 17.48^{+2.09}_{-2.06} & 17.14^{+1.06}_{-1.35} & 17.36^{+2.09}_{-2.06} & 17.02^{+1.06}_{-1.35} & -24.94^{+2.11}_{-2.08} & -25.28^{+1.07}_{-1.36} \\
+    14.2 & 17.40^{+2.12}_{-2.09} & 17.06^{+1.07}_{-1.37} & 17.27^{+2.12}_{-2.09} & 16.94^{+1.07}_{-1.37} & -25.07^{+2.14}_{-2.10} & -25.41^{+1.08}_{-1.38} \\
+    14.3 & 17.31^{+2.14}_{-2.11} & 16.97^{+1.09}_{-1.38} & 17.19^{+2.14}_{-2.11} & 16.85^{+1.09}_{-1.38} & -25.19^{+2.16}_{-2.12} & -25.53^{+1.09}_{-1.39} \\
+    14.4 & 17.23^{+2.17}_{-2.14} & 16.89^{+1.10}_{-1.40} & 17.11^{+2.17}_{-2.14} & 16.76^{+1.10}_{-1.40} & -25.32^{+2.18}_{-2.15} & -25.66^{+1.11}_{-1.40} \\
+    14.5 & 17.14^{+2.19}_{-2.16} & 16.80^{+1.11}_{-1.41} & 17.02^{+2.19}_{-2.16} & 16.68^{+1.11}_{-1.41} & -25.44^{+2.21}_{-2.17} & -25.78^{+1.12}_{-1.42} \\
+    14.6 & 17.05^{+2.22}_{-2.18} & 16.72^{+1.13}_{-1.43} & 16.93^{+2.22}_{-2.18} & 16.59^{+1.13}_{-1.43} & -25.58^{+2.24}_{-2.19} & -25.91^{+1.14}_{-1.43} \\
+    14.7 & 16.97^{+2.25}_{-2.20} & 16.63^{+1.14}_{-1.44} & 16.84^{+2.25}_{-2.20} & 16.51^{+1.14}_{-1.44} & -25.71^{+2.26}_{-2.21} & -26.05^{+1.15}_{-1.45} \\
+    14.8 & 16.88^{+2.28}_{-2.23} & 16.54^{+1.16}_{-1.46} & 16.75^{+2.28}_{-2.23} & 16.42^{+1.16}_{-1.46} & -25.85^{+2.29}_{-2.24} & -26.19^{+1.16}_{-1.46} \\
+    14.9 & 16.79^{+2.31}_{-2.25} & 16.46^{+1.17}_{-1.47} & 16.67^{+2.31}_{-2.25} & 16.33^{+1.17}_{-1.47} & -26.01^{+2.31}_{-2.26} & -26.35^{+1.18}_{-1.47} \\
+    15.0 & 16.70^{+2.33}_{-2.28} & 16.37^{+1.19}_{-1.48} & 16.58^{+2.33}_{-2.28} & 16.25^{+1.19}_{-1.48} & -26.24^{+2.33}_{-2.28} & -26.57^{+1.19}_{-1.48} \\
     \hline
@@
 catalogues and selection functions and the code used for developing
-and analysing luminosity function models.
-%% Make URL public. Set appropriate license.  Take permission from
-%% other authors.  Set up a DOI.
+and analysing luminosity function models.  The evolution of the
+luminosity function can be derived using any of the three global
+models that we presented in Section~\ref{sec:global}.  However, as we
+discussed in Section~\ref{sec:global}, none of these models should be
+extrapolated to higher redshifts.  Alternatively, our binned
+luminosity function estimates from Section~\ref{sec:bins} can be used.
+For applications that require extrapolation to higher redshifts, such
+as calculations of photoionization fluxes and emissivities, the fits
+presented in Equations~(\ref{eqn:e912_21}) and (\ref{eqn:e912_18}) can
+be used, or a similar approach of fitting functional forms to
+quantities suitably derived from the binned luminosity functions
+should be adopted.
 

### 2018-07-25 fit_emissivity.py
Change the way 912A emissivities are derived in code

@@ -50,18 +50,18 @@ def fit(x, y, sigma):
     sampler.run_mcmc(pos, 1000)
     samples = sampler.chain[:, 500:, :].reshape((-1, ndim))
     
-    # bf = np.median(samples, axis=0)
-    # print 'bf=', bf
-    # down = np.percentile(samples, 15.87, axis=0)
-    # print 'down=', down
-    # up = np.percentile(samples, 84.13, axis=0)
-    # print 'up=', up 
+    bf = np.median(samples, axis=0)
+    print 'bf=', bf
+    down = np.percentile(samples, 15.87, axis=0)
+    print 'down=', down
+    up = np.percentile(samples, 84.13, axis=0)
+    print 'up=', up 
 
     # plt.figure()
     # f = corner.corner(samples, labels=['a', 'b', 'c', 'd', 'e'], truths=bf)
     # f.savefig('corner.pdf')
 
-    return samples #bf, up, down
+    return samples, bf#, up, down
 
    
 

### 2018-07-25 gammapi.py

@@ -1110,26 +1110,16 @@ def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
                label='Kulkarni et al.\ 2018 (this work)',
                s=36, zorder=6, linewidths=1.5) 
 
-    # Plot best-fit model for Mlim=-18
-    def func(z, a, b, c, d, e):
-        e = 10.0**a * (1.0+z)**b * np.exp(-c*z) / (np.exp(d*z)+e)
-        return e # erg s^-1 Hz^-1 Mpc^-3
 
-    sigma = u-l 
-    z = np.linspace(0.0, 7, num=1000)
-    samples = fit_emissivity.fit(zs, em, sigma)
-    nsample = 300
-    rsample = samples[np.random.randint(len(samples), size=nsample)]
-    nzs = len(z) 
-    e = np.zeros((nsample, nzs))
-    for i, theta in enumerate(rsample):
-        e[i] = np.array(func(z, *theta))
-
-    up = np.percentile(e, 15.87, axis=0)
-    down = np.percentile(e, 84.13, axis=0)
+    # npz produced using rhoqso_fit2.py 
+    data = np.load('e1450_18.npz')
+    z = data['z']
+    b = data['median']*((912.0/1450.0)**0.61)
+    up = data['up']*((912.0/1450.0)**0.61)
+    down = data['down']*((912.0/1450.0)**0.61)
     tw18f = ax.fill_between(z, down, y2=up, color='red', zorder=5, alpha=0.6, edgecolor='None')
-    b = np.median(e, axis=0)
     tw18, = plt.plot(z, b, lw=2, c='red', zorder=5)
+    
 
     show_bad = True
     if show_bad:
@@ -1467,27 +1457,15 @@ def draw_emissivity_21(all_individuals, zlims, composite=None, select=False):
                label='Kulkarni et al.\ 2018 (this work)',
                s=42, zorder=6, linewidths=1.5) 
 
-    # Plot best-fit model for Mlim=-18
-    def func(z, a, b, c, d, e):
-        e = 10.0**a * (1.0+z)**b * np.exp(-c*z) / (np.exp(d*z)+e)
-        return e # erg s^-1 Hz^-1 Mpc^-3
-
-    sigma = u-l 
-    z = np.linspace(0.0, 7, num=1000)
-    samples = fit_emissivity.fit(zs, em, sigma)
-    nsample = 300
[…]

### 2018-07-25 qhe.py

@@ -20,23 +20,35 @@ if __name__ == '__main__':
     import matplotlib.pyplot as plt
     import sys
 
-data = np.load('e1450_18_test.npz')
+data = np.load('e1450_18.npz')
 z18 = data['z']
-medianbright18 = data['medianbright']*((912.0/1450.0)**0.61)
-downbright18 = data['downbright']*((912.0/1450.0)**0.61)
-upbright18 = data['upbright']*((912.0/1450.0)**0.61)
-medianfaint18 = data['medianfaint']*((912.0/1450.0)**0.61)
-downfaint18 = data['downfaint']*((912.0/1450.0)**0.61)
-upfaint18 = data['upfaint']*((912.0/1450.0)**0.61)
+median18 = data['median']*((912.0/1450.0)**0.61)
+up18 = data['up']*((912.0/1450.0)**0.61)
+down18 = data['down']*((912.0/1450.0)**0.61)
+    
+# data = np.load('e1450_18_test.npz')
+# z18 = data['z']
+# medianbright18 = data['medianbright']*((912.0/1450.0)**0.61)
+# downbright18 = data['downbright']*((912.0/1450.0)**0.61)
+# upbright18 = data['upbright']*((912.0/1450.0)**0.61)
+# medianfaint18 = data['medianfaint']*((912.0/1450.0)**0.61)
+# downfaint18 = data['downfaint']*((912.0/1450.0)**0.61)
+# upfaint18 = data['upfaint']*((912.0/1450.0)**0.61)
 
-data = np.load('e1450_21_test.npz')
+data = np.load('e1450_21.npz')
 z21 = data['z']
-medianbright21 = data['medianbright']*((912.0/1450.0)**0.61)
-downbright21 = data['downbright']*((912.0/1450.0)**0.61)
-upbright21 = data['upbright']*((912.0/1450.0)**0.61)
-medianfaint21 = data['medianfaint']*((912.0/1450.0)**0.61)
-downfaint21 = data['downfaint']*((912.0/1450.0)**0.61)
-upfaint21 = data['upfaint']*((912.0/1450.0)**0.61)
+median21 = data['median']*((912.0/1450.0)**0.61)
+up21 = data['up']*((912.0/1450.0)**0.61)
+down21 = data['down']*((912.0/1450.0)**0.61)
+
+# data = np.load('e1450_21_test.npz')
+# z21 = data['z']
[…]

### 2018-07-25 rhoqso_fit.py

@@ -29,6 +29,7 @@ def get_rhoqso(lfi, mlim, mbright=-23):
     """1450A emissivity (statistics).
 
     """
+    #np.random.seed(5)
     rindices = np.random.randint(len(lfi.samples), size=300)
     r = np.array([rhoqso(lfi.log10phi, theta, mlim, mbright=mbright)
                           for theta
@@ -56,7 +57,8 @@ def get_rhoqso_912(lfi, mlim, mbright=-30):
     """912A emissivity (statistics).
 
     """
-    
+
+    #np.random.seed(5)
     rindices = np.random.randint(len(lfi.samples), size=300)
     r = np.array([rhoqso_912(lfi.log10phi, theta, mlim, mbright=mbright)
                           for theta
@@ -69,21 +71,53 @@ def get_rhoqso_912(lfi, mlim, mbright=-30):
     lfi.rhoqso = [u, l, c] # ergs s^-1 Hz^-1 cMpc^-3
 
     
-def plot(redshifts, data, fit, filename):
+def select_data(individuals):
 
-    fig = plt.figure(figsize=(7, 7), dpi=100)
-    ax = fig.add_subplot(1, 1, 1)
+    # These redshift bins are labelled "bad" and are plotted differently.
+    reject = [0, 1, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20]
+
+    # Pick out the good data.
+    m = np.ones(len(individuals), dtype=bool)
+    m[reject] = False
+    minv = np.logical_not(m) 
+    individuals_good = [x for i, x in enumerate(individuals) if i not in set(reject)]
+    individuals_bad = [x for i, x in enumerate(individuals) if i in set(reject)]
+
+    return individuals_good
+
+def get_fits(zs, uz, lz, c, u, l):
+
+    em = c
+    em_up = u - c
+    em_low = c - l
+
+    uzerr = uz - zs
+    lzerr = zs - lz 
+        
+    def func(z, a, b, c, d, e):
+        e = 10.0**a * (1.0+z)**b * np.exp(-c*z) / (np.exp(d*z)+e)
+        return e # erg s^-1 Hz^-1 Mpc^-3
+
+    sigma = u-l
+    samples, params_bf = fit_emissivity.fit(zs, em, sigma)
+
+    nsample = 300
[…]

### 2018-07-25 rtg2.py

@@ -13,37 +13,53 @@ import gammapi
 from gammapi import get_gammapi_percentiles
 import matplotlib.patches as mpatches
 
-# These npz files generated by rhoqso_fit.py.
-
-data = np.load('e1450_18_2.npz')
+# These npz files generated by rhoqso_fit2.py.
+data = np.load('e1450_18.npz')
 z18 = data['z']
-medianbright18 = data['medianbright']
-medianfaint18 = data['medianfaint']
-downbright18 = data['downbright']
-upbright18 = data['upbright']
-downfaint18 = data['downfaint']
-upfaint18 = data['upfaint']
+median18 = data['median']
+up18 = data['up']
+down18 = data['down']
 
-data = np.load('e1450_21_2.npz')
+print 'median18=', median18[:10]
+
+data = np.load('e1450_21.npz')
 z21 = data['z']
-medianbright21 = data['medianbright']
-medianfaint21 = data['medianfaint']
-downbright21 = data['downbright']
-upbright21 = data['upbright']
-downfaint21 = data['downfaint']
-upfaint21 = data['upfaint']
+median21 = data['median']
+up21 = data['up']
+down21 = data['down']
 
-data = np.load('e912_18_2.npz')
-z18_912 = data['z']
-median18_912 = data['median']
-down18_912 = data['down']
-up18_912 = data['up']
+print 'median21=', median21[:10]
 
-data = np.load('e912_21_2.npz')
-z21_912 = data['z']
-median21_912 = data['median']
-down21_912 = data['down']
-up21_912 = data['up']
+
+
+# z18 = data['z']
+# medianbright18 = data['medianbright']
+# medianfaint18 = data['medianfaint']
+# downbright18 = data['downbright']
+# upbright18 = data['upbright']
+# downfaint18 = data['downfaint']
+# upfaint18 = data['upfaint']
+
+# data = np.load('e1450_21_2.npz')
+# z21 = data['z']
+# medianbright21 = data['medianbright']
+# medianfaint21 = data['medianfaint']
+# downbright21 = data['downbright']
+# upbright21 = data['upbright']
+# downfaint21 = data['downfaint']
[…]

### 2018-07-25 tabulate_emissivities.py

@@ -30,7 +30,7 @@ fs = (r'${:.2f}$ & ${:.2f}$ & ${:.2f}$ & ${:.2f}$ '
       r'& ${:.2f}^{{+{:.2f}}}_{{-{:.2f}}}$ '
       r'& ${:.2f}^{{+{:.2f}}}_{{-{:.2f}}}$ \\')
 
-fs2 = (r'{:.2f} & {:.2f} & {:.2f} & {:.2f} '
+fs2 = (r'{:.2f} & {:.2f} & {:.2f} '
       r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
       r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
       r'& {:.2f}^{{+{:.2f}}}_{{-{:.2f}}} '
@@ -39,7 +39,7 @@ fs2 = (r'{:.2f} & {:.2f} & {:.2f} & {:.2f} '
 
 for i in range(len(zmean)):
 
-    s = fs2.format(zmean[i], zbin[i], zmin[i], zmax[i],
+    s = fs2.format(zmean[i], zmin[i], zmax[i],
                   e912_18[i], de912_18_plus[i], de912_18_minus[i],
                   e1450_18[i], de1450_18_plus[i], de1450_18_minus[i],
                   e912_21[i], de912_21_plus[i], de912_21_minus[i],

### 2018-07-25 Paper/paper.tex

@@
          UK \\
-         $^2$Institut f\"ur Physik und Astronomie, Universit\"at
+         $^3$Institut f\"ur Physik und Astronomie, Universit\"at
          Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, D-14476 Potsdam,
@@
   \begin{minipage}{13.0cm}
-    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:mosaic}).}
+    \textsuperscript{$a$}{Redshift bin not considered in the joint QLF fit due to systematic errors (open circles in Figure~\ref{fig:evoln}).}
   \end{minipage}

### 2019-02-20 rhoqso_data.py
Add global models

@@ -9,85 +9,52 @@ mpl.rcParams['font.size'] = '16'
 import matplotlib.pyplot as plt
 from astropy.stats import knuth_bin_width  as kbw
 from astropy.stats import poisson_conf_interval as pci
-from scipy.stats import binned_statistic as bs
-import cosmolopy.distance as cd
-cosmo = {'omega_M_0':0.3,
-         'omega_lambda_0':0.7,
-         'omega_k_0':0.0,
-         'h':0.70}
 
+def f(loglf, theta, m, z, fit='individual'):
 
-"""Makes LF plots at particular redshifts.  Shows data with
-individual and composite models.  This is similar to the draw()
-function in individual.py but is more flexible.
-
-"""
-
-def lfsample(theta, n, mlims):
-
-    """
-    Return n qso magnitudes between mlims[0] and mlims[1] when the LF
-    is described by parameters theta.
-
-    """
-
-    mmin = mlims[0]
-    mmax = mlims[1]
-
-    def lnprob(x, theta):
-
-        if x < mmax and x > mmin: 
-            mag = x 
-            log10phi_star, M_star, alpha, beta = theta 
-            phi = 10.0**log10phi_star / (10.0**(0.4*(alpha+1)*(mag-M_star)) +
-                                         10.0**(0.4*(beta+1)*(mag-M_star)))
-            return np.log(phi)
-        else:
-            return -np.inf 
+    if fit == 'composite':
+        return 10.0**loglf(theta, m, z)
     
-    ndim = 1 
-    nwalkers = 250
-    dm = np.abs(mmin-mmax)
-    p0 = (np.random.rand(ndim*nwalkers)*dm + mmin).reshape((nwalkers, ndim))
+    return 10.0**loglf(theta, m)
 
-    sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=[theta])
-    pos, prob, state = sampler.run_mcmc(p0, 100)
-    sampler.reset()
-    sampler.run_mcmc(pos, 1000)
-    sample = sampler.flatchain[:,0]
 
-    return np.random.choice(sample, n)
+def rhoqso(loglf, theta, mlim, z, fit='individual', mbright=-35.0):
+
+    m = np.linspace(mbright, mlim, num=1000)
+    if fit == 'composite':
[…]

### 2019-02-21 data.py
Clean up code

@@ -63,14 +63,14 @@ def plot_data(data):
     # colorbrewer2.org.
     cs = [u'#1f77b4', u'#ff7f0e', u'#2ca02c', u'#d62728', u'#9467bd',
           u'#8c564b', u'#e377c2', u'#7f7f7f', u'#bcbd22', u'#17becf',
-          u'#77ab31']#, u'#d8b365']#, u'#cc7af4', u'#f66bad']
+          u'#77ab31']
 
     d = [x.z for x in data]
     l = [x.label for x in data]
     plt.hist(d, histtype='bar', stacked=True, rwidth=1.0,
              ec='None', bins=bins, color=cs, label=l, lw=0.0)
 
-    # Three qsos added by hand 
+    # Three z ~7 qsos have to be added by hand 
     z = 7.085
     zlim = (z-bin_width/2.0, z+bin_width/2.0)
     nbins = 1
@@ -105,7 +105,7 @@ def plot_data(data):
                frameon=False, framealpha=0.0, labelspacing=.1,
                handletextpad=0.4, borderpad=0.2,markerscale=.5)
 
-    plt.savefig('qsos4.pdf', bbox_inches='tight')
+    plt.savefig('qsos.pdf', bbox_inches='tight')
 
     return
 
@@ -159,31 +159,18 @@ l = r'CANDELS GOODS-S Giallongo et al.\ (2015)'
 s = sample(f, label=l)
 data.append(s)
 
-f = ['Data_new/jiang16main_sample.dat', 'Data_new/jiang16overlap_sample.dat', 'Data_new/jiang16s82_sample.dat']
+f = ['Data_new/jiang16main_sample.dat',
+     'Data_new/jiang16overlap_sample.dat',
+     'Data_new/jiang16s82_sample.dat']
 l = r'SDSS Jiang et al.\ (2016)'
 s = sample(f, label=l)
 data.append(s)
-
-# f = []
-# l = r'SDSS Overlap Jiang et al.\ (2016)'
-# s = sample(f, label=l)
-# data.append(s)
-
-# f = []
-# l = r'SDSS Stripe 82 Jiang et al.\ (2016)'
-# s = sample(f, label=l)
-# data.append(s)
 
 f = ['Data_new/willott10_cfhqsdeepsample.dat',
      'Data_new/willott10_cfhqsvwsample.dat']
 l = r'CFHQS Willott et al.\ (2010)'
 s = sample(f, label=l)
[…]

### 2019-02-21 kcorr.py
Clean up code

@@ -57,7 +57,6 @@ plt.text(4.7, -2.0, '$m=z_\mathrm{AB}$', fontsize=12)
 
 plt.ylim(-2.5,-0.5)
 plt.xlim(0,5.5)
-# plt.xticks(np.arange(2,6.5,1))
 
 handles, labels = ax.get_legend_handles_labels()
 plt.legend(handles, labels, loc='upper right', fontsize=14, handlelength=3,

### 2019-02-21 drawlf.py
Take all lfs as input

@@ -71,8 +71,7 @@ def plot_posterior_sample_lfs(lf, ax, maglims, **kwargs):
 
     up = np.percentile(phi, 15.87, axis=0)
     down = np.percentile(phi, 84.13, axis=0)
-    #f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
-    f = ax.fill_between(mags, down, y2=up, color='grey', alpha=0.7)
+    f = ax.fill_between(mags, down, y2=up, color='#ffbf00', alpha=0.7)
 
     return f
 
@@ -80,10 +79,7 @@ def plot_bestfit_lf(lf, ax, mags, **kwargs):
 
     bf = np.median(lf.samples, axis=0)
     phi_fit = lf.log10phi(bf, mags)
-    # ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'], label=kwargs['label'])
-    #bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
-    bf, = ax.plot(mags, phi_fit, lw=1.5, c='k', zorder=kwargs['zorder'])
-
+    bf, = ax.plot(mags, phi_fit, lw=1.5, c='#ffbf00', zorder=kwargs['zorder'])
     return bf 
 
 def binVol(self, selmap, mrange, zrange):
@@ -553,8 +549,11 @@ def render(ax, lf, composite=None, showMockSample=False, show_individual_fit=Tru
                         xerr=np.vstack((left, right)), 
                         yerr=np.vstack((uperr, downerr)),
                         fmt='None', zorder=4)
-        
-    return #(indf, indbf), (c1f, c1bf), (c2f, c2bf), (c3f, c3bf) 
+
+    if c2 is not None: 
+        return (indf, indbf), (c1f, c1bf), (c2f, c2bf), (c3f, c3bf)
+    else:
+        return 
 
 def draw(lf, composite=None, dirname='', showMockSample=False, show_individual_fit=True):
 

### 2019-02-21 gammapi.py
Update to the new fits

@@ -1059,7 +1059,7 @@ def get_gammapi_percentiles(lfi, z):
     return 
 
 
-def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
+def draw_emissivity_18(all_individuals, composite=None, select=False):
 
     """
     Calculates and plots LyC emissivity.
@@ -1110,9 +1110,8 @@ def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
                label='Kulkarni et al.\ 2018 (this work)',
                s=36, zorder=6, linewidths=1.5) 
 
-
-    # npz produced using rhoqso_fit2.py 
-    data = np.load('e1450_18.npz')
+    # npz produced using rhoqso_fit.get_fit_mcmc(). 
+    data = np.load('e1450_18_21feb.npz')
     z = data['z']
     b = data['median']*((912.0/1450.0)**0.61)
     up = data['up']*((912.0/1450.0)**0.61)
@@ -1120,7 +1119,6 @@ def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
     tw18f = ax.fill_between(z, down, y2=up, color='red', zorder=5, alpha=0.6, edgecolor='None')
     tw18, = plt.plot(z, b, lw=2, c='red', zorder=5)
     
-
     show_bad = True
     if show_bad:
         for x in individuals_bad:
@@ -1147,7 +1145,6 @@ def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
     giallongo15(ax, only18=True)
     
     e_MH15 = emissivity_MH15(z)
-    # ax.plot(z, e_MH15, lw=2, c='forestgreen', label='Madau and Haardt 2015', zorder=1)
     ax.plot(z, e_MH15, lw=1, c='darkgreen', label='Madau and Haardt 2015', zorder=1, dashes=[1,1])
 
     e_HM12 = emissivity_HM12(z)
@@ -1200,8 +1197,6 @@ def draw_emissivity_18(all_individuals, zlims, composite=None, select=False):
 
     masters12(ax, only18=True)
 
-    #bongiorno07(ax, only18=True)
-    
     handles, labels = ax.get_legend_handles_labels()
     handles.append((tw18f,tw18))
     labels.append('Kulkarni et al.\ 2018 (this work; fit)')
@@ -1406,7 +1401,7 @@ def draw_emissivity_18_talk(all_individuals, zlims, composite=None, select=False
     return
 
 
[…]

### 2019-02-21 qhe.py

@@ -20,7 +20,7 @@ if __name__ == '__main__':
     import matplotlib.pyplot as plt
     import sys
 
-data = np.load('e1450_18.npz')
+data = np.load('e1450_18_21feb.npz')
 z18 = data['z']
 median18 = data['median']*((912.0/1450.0)**0.61)
 up18 = data['up']*((912.0/1450.0)**0.61)
@@ -35,7 +35,7 @@ down18 = data['down']*((912.0/1450.0)**0.61)
 # downfaint18 = data['downfaint']*((912.0/1450.0)**0.61)
 # upfaint18 = data['upfaint']*((912.0/1450.0)**0.61)
 
-data = np.load('e1450_21.npz')
+data = np.load('e1450_21_21feb.npz')
 z21 = data['z']
 median21 = data['median']*((912.0/1450.0)**0.61)
 up21 = data['up']*((912.0/1450.0)**0.61)

### 2019-02-21 summary_fromFile.py

@@ -12,7 +12,7 @@ from scipy.optimize import curve_fit
 from scipy.interpolate import UnivariateSpline
 
 # These redshift bins are labelled "bad" and are plotted differently.
-reject = [0, 1, 7,8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20]
+reject = [0, 1, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20]
 
 # colors = ['tomato', 'forestgreen', 'goldenrod', 'saddlebrown']
 colors = ['k', 'k', 'k', 'k'] 
@@ -24,7 +24,7 @@ plot_number = 0
 zlims=(0.0,7.0)
 zmin, zmax = zlims
 z = np.linspace(zmin, zmax, num=500)
-cfit = True
+cfit = False
 
 def plot_model(composite, param_number, ax):
 
@@ -410,7 +410,7 @@ def plot_alpha(fig, composite, individuals=None, compOpt=None, sample=False, lfg
                 fmt='None', zorder=6)
     ax.scatter(zmean, c, color=colors[2], edgecolor='None', zorder=6, s=30)
 
-    cfit = True
+    cfit = False
     if cfit: 
         zc = np.linspace(0, 7, 500)
         coeffs = chebfit(zmean+1.0, c, 3)
@@ -453,19 +453,19 @@ def plot_alpha(fig, composite, individuals=None, compOpt=None, sample=False, lfg
 
     handles, labels = [], []
 
-    # handles.append((m1f,m1))
-    # labels.append('Model 1')
+    handles.append((m1f,m1))
+    labels.append('Model 1')
 
-    # handles.append((m2f,m2))
-    # labels.append('Model 2')
+    handles.append((m2f,m2))
+    labels.append('Model 2')
 
-    # handles.append((m3f,m3))
-    # labels.append('Model 3')
+    handles.append((m3f,m3))
+    labels.append('Model 3')
     
-    # plt.legend(handles, labels, loc='upper right', fontsize=10,
-    #            handlelength=3, frameon=False, framealpha=0.0,
-    #            labelspacing=.1, handletextpad=0.3, borderpad=0.1,
-    #            scatterpoints=1)
+    plt.legend(handles, labels, loc='upper right', fontsize=10,
+               handlelength=3, frameon=False, framealpha=0.0,
[…]

### 2019-02-21 Paper/paper.tex
Update

@@
 \usepackage{amssymb}
+\usepackage{xcolor}
+\definecolor{notecolor}{rgb}{0.8,0,0}
+\newcommand{\new}[1]{{\color{notecolor} #1}}
 \usepackage{pdflscape}
@@
 incidence of (partial) Lyman limit systems in the IGM
-\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}. While the BOSS DR9
-selection function considers these improvements, the uncertainty in
-the QLF remains dominated by assumptions in the selection function
-given the large sample size
-\citep{2013ApJ...773...14R}. Variability-selected quasar samples
-circumvent this issue \citep{2013ApJ...773...14R, 2013A&A...551A..29P,
-  2016A&A...587A..41P}, but may be affected by (i) single-epoch
-imaging incompleteness at the faint end \citep{2013ApJ...773...14R},
-and (ii) uncertainties in the selection function caused by the limited
-number of known $z\ga 3$ quasars not selected by variability in the
-same footprint \citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
+\citep{2009ApJ...705L.113P, 2011ApJ...728...23W}.  \new{The BOSS DR9
+selection function incorporates an improved treatment of the QSO SED
+and the IGM, including stochasticity in the colour distribution due to
+intervening Lyman-limit systems.}  While the BOSS DR9 selection
+function considers these improvements, the uncertainty in the QLF
+remains dominated by assumptions in the selection function given the
+large sample size \citep{2013ApJ...773...14R}.  Variability-selected
+quasar samples circumvent this issue \citep{2013ApJ...773...14R,
+  2013A&A...551A..29P, 2016A&A...587A..41P}, but may be affected by
+(i) single-epoch imaging incompleteness at the faint end
+\citep{2013ApJ...773...14R}, and (ii) uncertainties in the selection
+function caused by the limited number of known $z\ga 3$ quasars not
+selected by variability in the same footprint
+\citep{2013A&A...551A..29P, 2016A&A...587A..41P}.
 
@@
     \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small_global.pdf}
-    % mosaic_selected.py and drawlf_selected.py 
+    % mosaic_selected.py
   \end{center}
@@
 Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
-error are excluded from Figure~\ref{fig:mosaic_global}.  All three
-global models are in excellent agreement with the binned models,
-although Model~1 performs better.
+error are excluded from Figure~\ref{fig:mosaic_global}.  \new{All
+  three global models are in good agreement with the luminosity
+  functions in redshift bins, although Model~1 reproduces best the
+  apparent rapid evolution in the faint-end slope $\beta$ at $z>4$.
+  Given the systematic errors in the data, a quantitative model
+  selection is of limited use.}
 
@@
     \citet[dotted brown curve]{2012ApJ...746..125H}, the QSO
-    contribution in this model (dashed grey), \citet[dashed
-      brown]{2015ApJ...813L...8M}, the QSO contribution from the model
-    of \citet[dashed orange]{2015MNRAS.451L..30K}, \citet[dotted
+    contribution in this model (\new{dashed brown}),
+    \citet[\new{dotted green}]{2015ApJ...813L...8M}, the QSO
+    contribution from the model of \citet[dashed
+      orange]{2015MNRAS.451L..30K}, \citet[dotted
       grey]{2017ApJ...837..106O}, and \citet[dashed
@@
 paper can be easily compared with theoretical models or future data
-sets.  These luminosity function determinations supersede previous
-determinations by \citet{2007ApJ...654..731H} by including new data,
-by analysing unbinned data, and extending the analysis to higher
-redshifts.  Our public code can be used either to reproduce all of our
-analysis starting from the QSO catalogues, or to quickly evaluate our
-luminosity function fits at desired redshifts and luminosities.
+sets.  \new{These luminosity functions update previous determinations
+  by including new data, by analysing unbinned data, and extending the
+  analysis to higher redshifts.}  Our public code can be used either
+to reproduce all of our analysis starting from the QSO catalogues, or
+to quickly evaluate our luminosity function fits at desired redshifts
+and luminosities.
 
@@
     \citet[asterisks]{2016ApJ...829...33Y},
-    \citet[circles]{2013ApJ...773...14R}, and \citet[rightward
+    \citet[circles]{2013ApJ...773...14R},
+    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
       triangles]{2009A&A...507..781S}.  Where necessary, values from

### 2019-02-25 rtg2.py
Update legend

@@ -1320,9 +1320,9 @@ def draw_g_paper():
 
     handles, labels = ax.get_legend_handles_labels()
     handles.append((g18f,g18))
-    labels.append('Kulkarni et al.\ 2018 (this work; $M_\mathrm{1450}<-18$)')
+    labels.append('Kulkarni et al.\ 2019 (this work; $M_\mathrm{1450}<-18$)')
     handles.append((g21f,g21))
-    labels.append('Kulkarni et al.\ 2018 (this work; $M_\mathrm{1450}<-21$)')
+    labels.append('Kulkarni et al.\ 2019 (this work; $M_\mathrm{1450}<-21$)')
 
     plt.legend(handles, labels, loc='center',
                fontsize=12, handlelength=3, frameon=False,
@@ -1426,9 +1426,9 @@ def draw_g_puc():
 
     handles, labels = [], [] 
     handles.append((g18f,g18))
-    labels.append('Kulkarni et al.\ 2018 (this work; $M_\mathrm{1450}<-18$)')
+    labels.append('Kulkarni et al.\ 2019 (this work; $M_\mathrm{1450}<-18$)')
     handles.append((g21f,g21))
-    labels.append('Kulkarni et al.\ 2018 (this work; $M_\mathrm{1450}<-21$)')
+    labels.append('Kulkarni et al.\ 2019 (this work; $M_\mathrm{1450}<-21$)')
 
     l2 = plt.legend(handles, labels, loc='lower right',
                     fontsize=11, handlelength=3, frameon=False,

### 2019-02-25 qhe.py
Update references

@@ -380,7 +380,7 @@ def plotq():
     qup = np.where(qup<1.0, qup, 1.0)
 
     q18 = ax.fill_between(z, qup.flatten(), y2=qdown.flatten(), color='red', zorder=10, alpha=0.6, edgecolor='None')
-    q18bf, = plt.plot(z, q.flatten(), c='red', lw=2, label=r'Kulkarni et al.\ 2018 (this work; $M_{1450}<-18$)', zorder=10)
+    q18bf, = plt.plot(z, q.flatten(), c='red', lw=2, label=r'Kulkarni et al.\ 2019 (this work; $M_{1450}<-18$)', zorder=10)
 
     #----------
 
@@ -394,7 +394,7 @@ def plotq():
     qup = np.where(qup<1.0, qup, 1.0)
     
     q21 = ax.fill_between(z, qup.flatten(), y2=qdown.flatten(), color='blue', zorder=10, alpha=0.6, edgecolor='None')
-    q21bf, = plt.plot(z, q.flatten(), c='blue', lw=2, label=r'Kulkarni et al.\ 2018 (this work; $M_{1450}<-21$)', zorder=10)
+    q21bf, = plt.plot(z, q.flatten(), c='blue', lw=2, label=r'Kulkarni et al.\ 2019 (this work; $M_{1450}<-21$)', zorder=10)
 
     #----------
     

### 2019-02-25 Paper/paper.tex
Update Table 2
Update

@@
     \hline
-    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.62^{+0.09}_{-0.11} & -21.37^{+0.21}_{-0.23} & -2.94^{+0.09}_{-0.10} & -1.22^{+0.18}_{-0.16} \\
-    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.13^{+0.04}_{-0.04} & -23.00^{+0.08}_{-0.07} & -3.38^{+0.08}_{-0.08} & -1.36^{+0.04}_{-0.04} \\
-    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.42^{+0.09}_{-0.08} & -24.03^{+0.14}_{-0.13} & -3.56^{+0.12}_{-0.13} & -1.75^{+0.04}_{-0.04} \\
-    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.39^{+0.08}_{-0.08} & -24.50^{+0.12}_{-0.12} & -3.69^{+0.11}_{-0.11} & -1.73^{+0.06}_{-0.05} \\
-    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.54^{+0.03}_{-0.03} & -25.15^{+0.04}_{-0.04} & -4.18^{+0.08}_{-0.08} & -1.73^{+0.02}_{-0.02} \\
-    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.42^{+0.04}_{-0.04} & -25.29^{+0.06}_{-0.05} & -3.97^{+0.08}_{-0.08} & -1.74^{+0.03}_{-0.03} \\
-    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.51^{+0.03}_{-0.03} & -25.67^{+0.04}_{-0.04} & -4.28^{+0.08}_{-0.08} & -1.76^{+0.02}_{-0.02} \\
-    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.03}_{-0.03} & -25.56^{+0.05}_{-0.05} & -3.96^{+0.07}_{-0.07} & -1.60^{+0.03}_{-0.03} \\
-    1.98 & 1.80 & 2.20 & 10478 & 10876 & -6.72^{+0.03}_{-0.03} & -26.26^{+0.04}_{-0.04} & -4.21^{+0.07}_{-0.07} & -1.87^{+0.02}_{-0.02} \\
-    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.49^{+0.12}_{-0.11} & -3.34^{+0.12}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
-    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.07} & -25.86^{+0.14}_{-0.12} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
-    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.34^{+0.17}_{-0.16} & -3.32^{+0.15}_{-0.16} & -1.39^{+0.08}_{-0.07} \\
-    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.15^{+0.13}_{-0.14} & -3.12^{+0.12}_{-0.12} & -1.05^{+0.09}_{-0.08} \\
-    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.08}_{-0.07} & -25.94^{+0.15}_{-0.13} & -3.78^{+0.27}_{-0.30} & -1.34^{+0.07}_{-0.06} \\
-    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.45^{+0.11}_{-0.10} & -26.22^{+0.21}_{-0.18} & -3.61^{+0.35}_{-0.41} & -1.46^{+0.08}_{-0.07} \\
-    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.53^{+0.11}_{-0.09} & -5.05^{+0.59}_{-0.63} & -1.71^{+0.05}_{-0.04} \\
-    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.12}_{-0.11} & -4.68^{+0.44}_{-0.52} & -1.70^{+0.06}_{-0.05} \\
-    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.26^{+0.16}_{-0.11} & -27.11^{+0.22}_{-0.17} & -4.38^{+0.76}_{-1.30} & -1.96^{+0.07}_{-0.05} \\
-    3.25$^a$ & 3.20 & 3.30 & 815 & 815 & -7.34^{+0.13}_{-0.13} & -27.20^{+0.20}_{-0.22} & -4.39^{+0.69}_{-0.79} & -1.94^{+0.06}_{-0.05} \\
-    3.34$^a$ & 3.30 & 3.40 & 510 & 510 & -7.54^{+0.21}_{-0.21} & -27.39^{+0.28}_{-0.37} & -4.67^{+1.38}_{-1.44} & -2.08^{+0.09}_{-0.07} \\
-    3.44$^a$ & 3.40 & 3.50 & 155 & 155 & -6.76^{+0.19}_{-0.20} & -26.62^{+0.40}_{-0.36} & -3.67^{+0.62}_{-0.83} & -1.24^{+0.28}_{-0.23} \\
-    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.91^{+0.11}_{-0.11} & -27.26^{+0.13}_{-0.12} & -4.83^{+0.33}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
-    4.35 & 4.10 & 4.70 & 442 & 603 & -8.32^{+0.29}_{-0.25} & -27.37^{+0.37}_{-0.30} & -4.20^{+0.41}_{-0.50} & -2.21^{+0.15}_{-0.13} \\
-    4.92 & 4.70 & 5.50 & 263 & 263 & -9.02^{+0.30}_{-0.21} & -27.89^{+0.37}_{-0.26} & -4.58^{+0.71}_{-0.80} & -2.30^{+0.11}_{-0.08} \\
-    6.00 & 5.50 & 6.50 & 66 & 66 & -10.66^{+0.74}_{-1.11} & -29.21^{+1.08}_{-1.89} & -5.05^{+0.76}_{-1.18} & -2.41^{+0.10}_{-0.08} \\
+    0.31$^a$ & 0.10 & 0.40 & 3520 & 3632 & -5.72^{+0.08}_{-0.12} & -21.30^{+0.24}_{-0.29} & -2.74^{+0.09}_{-0.11} & -1.07^{+0.22}_{-0.20} \\
+    0.50$^a$ & 0.40 & 0.60 & 4555 & 4686 & -6.39^{+0.05}_{-0.05} & -23.38^{+0.10}_{-0.09} & -3.49^{+0.10}_{-0.10} & -1.55^{+0.04}_{-0.04} \\
+    0.72 & 0.60 & 0.80 & 3308 & 4684 & -6.57^{+0.14}_{-0.12} & -24.21^{+0.22}_{-0.18} & -3.55^{+0.16}_{-0.17} & -1.89^{+0.06}_{-0.05} \\
+    0.91 & 0.80 & 1.00 & 3922 & 5248 & -6.48^{+0.11}_{-0.10} & -24.60^{+0.16}_{-0.14} & -3.69^{+0.12}_{-0.13} & -1.88^{+0.07}_{-0.05} \\
+    1.10 & 1.00 & 1.20 & 6367 & 6566 & -6.62^{+0.03}_{-0.03} & -25.24^{+0.05}_{-0.05} & -4.24^{+0.09}_{-0.09} & -1.84^{+0.02}_{-0.02} \\
+    1.30 & 1.20 & 1.40 & 6479 & 7132 & -6.52^{+0.04}_{-0.04} & -25.41^{+0.06}_{-0.06} & -4.02^{+0.09}_{-0.09} & -1.88^{+0.03}_{-0.03} \\
+    1.50 & 1.40 & 1.60 & 7539 & 7771 & -6.59^{+0.03}_{-0.03} & -25.77^{+0.04}_{-0.04} & -4.35^{+0.09}_{-0.09} & -1.87^{+0.02}_{-0.02} \\
+    1.71 & 1.60 & 1.80 & 6788 & 7421 & -6.29^{+0.04}_{-0.04} & -25.56^{+0.06}_{-0.06} & -3.94^{+0.07}_{-0.08} & -1.69^{+0.03}_{-0.03} \\
+    1.98 & 1.80 & 2.20 & 10478 & 1087& -6.79^{+0.03}_{-0.03} & -26.35^{+0.04}_{-0.04} & -4.26^{+0.07}_{-0.08} & -1.98^{+0.02}_{-0.02} \\
+    2.30$^a$ & 2.20 & 2.40 & 8419 & 8419 & -6.16^{+0.07}_{-0.06} & -25.50^{+0.12}_{-0.11} & -3.34^{+0.11}_{-0.12} & -1.61^{+0.04}_{-0.04} \\
+    2.45$^a$ & 2.40 & 2.50 & 3403 & 3403 & -6.40^{+0.08}_{-0.08} & -25.86^{+0.14}_{-0.13} & -3.61^{+0.21}_{-0.22} & -1.60^{+0.05}_{-0.04} \\
+    2.55$^a$ & 2.50 & 2.60 & 2640 & 2640 & -6.15^{+0.08}_{-0.08} & -25.33^{+0.17}_{-0.16} & -3.31^{+0.15}_{-0.16} & -1.38^{+0.08}_{-0.07} \\
+    2.65$^a$ & 2.60 & 2.70 & 1883 & 1883 & -5.98^{+0.05}_{-0.06} & -25.16^{+0.13}_{-0.13} & -3.13^{+0.11}_{-0.12} & -1.05^{+0.08}_{-0.08} \\
+    2.75$^a$ & 2.70 & 2.80 & 1135 & 1135 & -6.29^{+0.07}_{-0.07} & -25.94^{+0.14}_{-0.13} & -3.78^{+0.26}_{-0.29} & -1.34^{+0.07}_{-0.06} \\
+    2.85$^a$ & 2.80 & 2.90 & 1069 & 1069 & -6.46^{+0.12}_{-0.10} & -26.22^{+0.23}_{-0.18} & -3.61^{+0.37}_{-0.43} & -1.46^{+0.08}_{-0.07} \\
+    2.95$^a$ & 2.90 & 3.00 & 1104 & 1104 & -6.76^{+0.07}_{-0.06} & -26.52^{+0.11}_{-0.09} & -5.01^{+0.58}_{-0.64} & -1.71^{+0.05}_{-0.04} \\
+    3.05$^a$ & 3.00 & 3.10 & 1127 & 1127 & -6.77^{+0.08}_{-0.07} & -26.48^{+0.11}_{-0.10} & -4.72^{+0.44}_{-0.50} & -1.70^{+0.06}_{-0.05} \\
+    3.15$^a$ & 3.10 & 3.20 & 1041 & 1041 & -7.25^{+0.15}_{-0.12} & -27.10^{+0.21}_{-0.18} & -4.39^{+0.75}_{-1.18} & -1.96^{+0.07}_{-0.05} \\
+    3.25$^a$ & 3.20 & 3.30 & 815 & 815 &  -7.33^{+0.12}_{-0.13} & -27.19^{+0.19}_{-0.21} & -4.39^{+0.66}_{-0.76} & -1.93^{+0.06}_{-0.05} \\
+    3.34$^a$ & 3.30 & 3.40 & 510 & 510 &  -7.54^{+0.22}_{-0.22} & -27.39^{+0.29}_{-0.37} & -4.76^{+1.29}_{-1.38} & -2.08^{+0.09}_{-0.07} \\
+    3.44 & 3.40 & 3.50 & 155 & 155 &  -6.78^{+0.20}_{-0.20} & -26.65^{+0.44}_{-0.34} & -3.72^{+0.68}_{-0.89} & -1.25^{+0.29}_{-0.22} \\
+    3.88 & 3.70 & 4.10 & 628 & 1204 & -7.92^{+0.12}_{-0.10} & -27.26^{+0.14}_{-0.12} & -4.84^{+0.36}_{-0.38} & -2.07^{+0.10}_{-0.09} \\
+    4.35 & 4.10 & 4.70 & 442 & 603 &  -8.32^{+0.31}_{-0.26} & -27.37^{+0.39}_{-0.32} & -4.19^{+0.43}_{-0.50} & -2.20^{+0.16}_{-0.14} \\
+    4.92 & 4.70 & 5.50 & 263 & 263 &  -9.03^{+0.29}_{-0.22} & -27.89^{+0.36}_{-0.26} & -4.55^{+0.69}_{-0.82} & -2.31^{+0.11}_{-0.09} \\
+    6.00 & 5.50 & 6.50 & 66 & 66 &  -10.66^{+0.75}_{-1.12} & -29.19^{+1.09}_{-1.89} & -5.00^{+0.73}_{-1.20} & -2.40^{+0.09}_{-0.08} \\
     \hline
@@
     regions show the three derived global models with one-sigma
-    uncertainties.  Model~1 provides a better fit, but requires a
-    rapid change in the faint-end slope at $z\sim 3.5$.}
+    uncertainties.}
   \label{fig:evoln_global}
@@
 Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
-Venemans and Stephen Warren.  GK acknowledges support from ERC
-Advanced Grant 320596 `The Emergence of Structure During the Epoch of
-Reionization'.
+Venemans and Stephen Warren.  \new{We thank the anonymous referee for
+  their comments.} GK acknowledges support from ERC Advanced Grant
+320596 `The Emergence of Structure During the Epoch of Reionization'.
 

### 2019-02-25 Paper/paper.tex
Update

@@
 Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
-Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov,
-Donald Lynden-Bell, Roberto Maiolino, Richard McMahon, Daniel
-Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
+Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Alex
+Krolewski, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
+Daniel Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
 Venemans and Stephen Warren.  \new{We thank the anonymous referee for
@@
     \hline
-    0.0 & 23.20^{+0.20}_{-0.18} & 22.96^{+0.11}_{-0.14} & 23.08^{+0.20}_{-0.18} & 22.84^{+0.11}_{-0.14} & -13.71^{+0.05}_{-0.05} & -13.86^{+0.03}_{-0.03} \\
-    0.1 & 23.43^{+0.15}_{-0.14} & 23.19^{+0.09}_{-0.11} & 23.30^{+0.15}_{-0.14} & 23.07^{+0.09}_{-0.11} & -13.51^{+0.04}_{-0.04} & -13.66^{+0.02}_{-0.03} \\
-    0.2 & 23.62^{+0.11}_{-0.11} & 23.39^{+0.07}_{-0.08} & 23.50^{+0.11}_{-0.11} & 23.27^{+0.07}_{-0.08} & -13.33^{+0.04}_{-0.04} & -13.48^{+0.02}_{-0.02} \\
-    0.3 & 23.80^{+0.07}_{-0.09} & 23.58^{+0.05}_{-0.06} & 23.68^{+0.07}_{-0.09} & 23.46^{+0.05}_{-0.06} & -13.17^{+0.03}_{-0.03} & -13.31^{+0.02}_{-0.02} \\
-    0.4 & 23.96^{+0.06}_{-0.07} & 23.75^{+0.04}_{-0.04} & 23.83^{+0.06}_{-0.07} & 23.63^{+0.04}_{-0.04} & -13.02^{+0.03}_{-0.03} & -13.16^{+0.02}_{-0.02} \\
-    0.5 & 24.10^{+0.04}_{-0.06} & 23.91^{+0.03}_{-0.03} & 23.97^{+0.04}_{-0.06} & 23.78^{+0.03}_{-0.03} & -12.89^{+0.02}_{-0.02} & -13.02^{+0.01}_{-0.01} \\
-    0.6 & 24.23^{+0.03}_{-0.04} & 24.05^{+0.02}_{-0.02} & 24.10^{+0.03}_{-0.04} & 23.93^{+0.02}_{-0.02} & -12.77^{+0.02}_{-0.02} & -12.89^{+0.01}_{-0.01} \\
-    0.7 & 24.34^{+0.02}_{-0.03} & 24.18^{+0.01}_{-0.01} & 24.22^{+0.02}_{-0.03} & 24.06^{+0.01}_{-0.01} & -12.66^{+0.02}_{-0.02} & -12.78^{+0.01}_{-0.01} \\
-    0.8 & 24.45^{+0.02}_{-0.02} & 24.30^{+0.01}_{-0.01} & 24.33^{+0.02}_{-0.02} & 24.18^{+0.01}_{-0.01} & -12.56^{+0.02}_{-0.02} & -12.67^{+0.01}_{-0.01} \\
-    0.9 & 24.55^{+0.01}_{-0.02} & 24.41^{+0.01}_{-0.01} & 24.42^{+0.01}_{-0.02} & 24.29^{+0.01}_{-0.01} & -12.47^{+0.02}_{-0.02} & -12.58^{+0.01}_{-0.01} \\
-    1.0 & 24.63^{+0.01}_{-0.02} & 24.51^{+0.01}_{-0.01} & 24.51^{+0.01}_{-0.02} & 24.39^{+0.01}_{-0.01} & -12.39^{+0.02}_{-0.02} & -12.49^{+0.01}_{-0.01} \\
-    1.1 & 24.71^{+0.01}_{-0.01} & 24.60^{+0.01}_{-0.01} & 24.59^{+0.01}_{-0.01} & 24.48^{+0.01}_{-0.01} & -12.32^{+0.02}_{-0.02} & -12.42^{+0.01}_{-0.01} \\
-    1.2 & 24.78^{+0.01}_{-0.01} & 24.68^{+0.01}_{-0.01} & 24.66^{+0.01}_{-0.01} & 24.56^{+0.01}_{-0.01} & -12.26^{+0.02}_{-0.02} & -12.35^{+0.01}_{-0.01} \\
-    1.3 & 24.84^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & 24.72^{+0.01}_{-0.01} & 24.63^{+0.01}_{-0.01} & -12.21^{+0.02}_{-0.02} & -12.30^{+0.01}_{-0.01} \\
-    1.4 & 24.90^{+0.01}_{-0.01} & 24.81^{+0.01}_{-0.01} & 24.78^{+0.01}_{-0.01} & 24.69^{+0.01}_{-0.01} & -12.16^{+0.02}_{-0.02} & -12.25^{+0.01}_{-0.01} \\
-    1.5 & 24.95^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & 24.75^{+0.01}_{-0.01} & -12.12^{+0.02}_{-0.02} & -12.21^{+0.01}_{-0.01} \\
-    1.6 & 24.99^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.87^{+0.01}_{-0.01} & 24.79^{+0.01}_{-0.01} & -12.09^{+0.02}_{-0.02} & -12.18^{+0.01}_{-0.01} \\
-    1.7 & 25.03^{+0.01}_{-0.01} & 24.95^{+0.01}_{-0.01} & 24.91^{+0.01}_{-0.01} & 24.83^{+0.01}_{-0.01} & -12.07^{+0.03}_{-0.03} & -12.16^{+0.02}_{-0.02} \\
-    1.8 & 25.06^{+0.01}_{-0.01} & 24.98^{+0.01}_{-0.01} & 24.94^{+0.01}_{-0.01} & 24.86^{+0.01}_{-0.01} & -12.05^{+0.03}_{-0.03} & -12.15^{+0.02}_{-0.02} \\
-    1.9 & 25.09^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 24.97^{+0.02}_{-0.02} & 24.88^{+0.01}_{-0.01} & -12.04^{+0.03}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
-    2.0 & 25.11^{+0.02}_{-0.02} & 25.02^{+0.01}_{-0.01} & 24.99^{+0.02}_{-0.02} & 24.90^{+0.01}_{-0.01} & -12.03^{+0.04}_{-0.04} & -12.14^{+0.02}_{-0.02} \\
-    2.1 & 25.12^{+0.03}_{-0.03} & 25.03^{+0.02}_{-0.02} & 25.00^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.02^{+0.04}_{-0.05} & -12.14^{+0.03}_{-0.03} \\
-    2.2 & 25.14^{+0.03}_{-0.03} & 25.04^{+0.02}_{-0.02} & 25.01^{+0.03}_{-0.03} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.05} & -12.15^{+0.03}_{-0.03} \\
-    2.3 & 25.14^{+0.03}_{-0.04} & 25.04^{+0.02}_{-0.02} & 25.02^{+0.03}_{-0.04} & 24.91^{+0.02}_{-0.02} & -12.03^{+0.05}_{-0.06} & -12.16^{+0.03}_{-0.03} \\
-    2.4 & 25.14^{+0.04}_{-0.05} & 25.03^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.05} & 24.91^{+0.03}_{-0.03} & -12.04^{+0.05}_{-0.07} & -12.18^{+0.04}_{-0.04} \\
-    2.5 & 25.14^{+0.04}_{-0.06} & 25.02^{+0.03}_{-0.03} & 25.02^{+0.04}_{-0.06} & 24.89^{+0.03}_{-0.03} & -12.05^{+0.06}_{-0.07} & -12.20^{+0.04}_{-0.04} \\
-    2.6 & 25.14^{+0.05}_{-0.06} & 25.00^{+0.04}_{-0.04} & 25.01^{+0.05}_{-0.06} & 24.88^{+0.04}_{-0.04} & -12.07^{+0.07}_{-0.08} & -12.23^{+0.04}_{-0.04} \\
-    2.7 & 25.13^{+0.06}_{-0.07} & 24.98^{+0.04}_{-0.04} & 25.00^{+0.06}_{-0.07} & 24.86^{+0.04}_{-0.04} & -12.09^{+0.07}_{-0.09} & -12.25^{+0.05}_{-0.05} \\
-    2.8 & 25.11^{+0.07}_{-0.07} & 24.96^{+0.04}_{-0.05} & 24.99^{+0.07}_{-0.07} & 24.84^{+0.04}_{-0.05} & -12.11^{+0.08}_{-0.09} & -12.29^{+0.05}_{-0.05} \\
-    2.9 & 25.10^{+0.07}_{-0.08} & 24.93^{+0.05}_{-0.05} & 24.98^{+0.07}_{-0.08} & 24.81^{+0.05}_{-0.05} & -12.14^{+0.08}_{-0.10} & -12.32^{+0.05}_{-0.05} \\
-    3.0 & 25.08^{+0.08}_{-0.09} & 24.91^{+0.05}_{-0.05} & 24.96^{+0.08}_{-0.09} & 24.78^{+0.05}_{-0.05} & -12.16^{+0.09}_{-0.11} & -12.36^{+0.05}_{-0.06} \\
-    3.1 & 25.06^{+0.08}_{-0.10} & 24.87^{+0.05}_{-0.05} & 24.94^{+0.08}_{-0.10} & 24.75^{+0.05}_{-0.05} & -12.20^{+0.09}_{-0.12} & -12.40^{+0.06}_{-0.06} \\
-    3.2 & 25.04^{+0.09}_{-0.11} & 24.84^{+0.06}_{-0.05} & 24.92^{+0.09}_{-0.11} & 24.72^{+0.06}_{-0.05} & -12.23^{+0.10}_{-0.13} & -12.44^{+0.06}_{-0.06} \\
-    3.3 & 25.01^{+0.09}_{-0.12} & 24.81^{+0.06}_{-0.06} & 24.89^{+0.09}_{-0.12} & 24.68^{+0.06}_{-0.06} & -12.27^{+0.10}_{-0.13} & -12.49^{+0.06}_{-0.06} \\
-    3.4 & 24.99^{+0.10}_{-0.13} & 24.77^{+0.06}_{-0.06} & 24.86^{+0.10}_{-0.13} & 24.64^{+0.06}_{-0.06} & -12.30^{+0.11}_{-0.14} & -12.54^{+0.06}_{-0.07} \\
-    3.5 & 24.96^{+0.10}_{-0.14} & 24.73^{+0.06}_{-0.06} & 24.83^{+0.10}_{-0.14} & 24.60^{+0.06}_{-0.06} & -12.34^{+0.11}_{-0.15} & -12.59^{+0.06}_{-0.07} \\
-    3.6 & 24.93^{+0.11}_{-0.15} & 24.69^{+0.06}_{-0.07} & 24.80^{+0.11}_{-0.15} & 24.56^{+0.06}_{-0.07} & -12.39^{+0.11}_{-0.16} & -12.64^{+0.06}_{-0.07} \\
-    3.7 & 24.89^{+0.11}_{-0.15} & 24.64^{+0.06}_{-0.07} & 24.77^{+0.11}_{-0.15} & 24.52^{+0.06}_{-0.07} & -12.43^{+0.12}_{-0.16} & -12.69^{+0.06}_{-0.07} \\
-    3.8 & 24.85^{+0.12}_{-0.16} & 24.60^{+0.06}_{-0.07} & 24.73^{+0.12}_{-0.16} & 24.47^{+0.06}_{-0.07} & -12.48^{+0.12}_{-0.17} & -12.74^{+0.07}_{-0.08} \\
-    3.9 & 24.81^{+0.12}_{-0.17} & 24.55^{+0.07}_{-0.07} & 24.69^{+0.12}_{-0.17} & 24.43^{+0.07}_{-0.07} & -12.53^{+0.13}_{-0.18} & -12.80^{+0.07}_{-0.08} \\
-    4.0 & 24.78^{+0.13}_{-0.18} & 24.51^{+0.07}_{-0.08} & 24.65^{+0.13}_{-0.18} & 24.38^{+0.07}_{-0.08} & -12.57^{+0.13}_{-0.19} & -12.85^{+0.07}_{-0.09} \\
-    4.1 & 24.74^{+0.13}_{-0.19} & 24.46^{+0.07}_{-0.09} & 24.61^{+0.13}_{-0.19} & 24.34^{+0.07}_{-0.09} & -12.63^{+0.14}_{-0.20} & -12.91^{+0.07}_{-0.10} \\
-    4.2 & 24.69^{+0.13}_{-0.19} & 24.41^{+0.07}_{-0.09} & 24.57^{+0.13}_{-0.19} & 24.29^{+0.07}_{-0.09} & -12.68^{+0.14}_{-0.21} & -12.97^{+0.07}_{-0.10} \\
-    4.3 & 24.65^{+0.14}_{-0.20} & 24.36^{+0.07}_{-0.10} & 24.53^{+0.14}_{-0.20} & 24.24^{+0.07}_{-0.10} & -12.73^{+0.15}_{-0.22} & -13.03^{+0.07}_{-0.11} \\
-    4.4 & 24.61^{+0.14}_{-0.21} & 24.31^{+0.07}_{-0.11} & 24.49^{+0.14}_{-0.21} & 24.19^{+0.07}_{-0.11} & -12.78^{+0.15}_{-0.23} & -13.09^{+0.08}_{-0.12} \\
-    4.5 & 24.57^{+0.15}_{-0.23} & 24.26^{+0.08}_{-0.11} & 24.44^{+0.15}_{-0.23} & 24.14^{+0.08}_{-0.11} & -12.84^{+0.16}_{-0.24} & -13.15^{+0.08}_{-0.12} \\
-    4.6 & 24.52^{+0.16}_{-0.24} & 24.21^{+0.08}_{-0.12} & 24.39^{+0.16}_{-0.24} & 24.08^{+0.08}_{-0.12} & -12.90^{+0.17}_{-0.25} & -13.22^{+0.08}_{-0.13} \\
-    4.7 & 24.47^{+0.17}_{-0.25} & 24.15^{+0.08}_{-0.13} & 24.34^{+0.17}_{-0.25} & 24.03^{+0.08}_{-0.13} & -12.96^{+0.18}_{-0.27} & -13.28^{+0.08}_{-0.14} \\
-    4.8 & 24.42^{+0.17}_{-0.27} & 24.10^{+0.08}_{-0.13} & 24.30^{+0.17}_{-0.27} & 23.98^{+0.08}_{-0.13} & -13.02^{+0.18}_{-0.28} & -13.35^{+0.08}_{-0.14} \\
-    4.9 & 24.37^{+0.18}_{-0.28} & 24.04^{+0.08}_{-0.14} & 24.25^{+0.18}_{-0.28} & 23.92^{+0.08}_{-0.14} & -13.08^{+0.19}_{-0.29} & -13.41^{+0.09}_{-0.15} \\
-    5.0 & 24.31^{+0.20}_{-0.29} & 23.99^{+0.08}_{-0.15} & 24.19^{+0.20}_{-0.29} & 23.87^{+0.08}_{-0.15} & -13.15^{+0.20}_{-0.30} & -13.48^{+0.09}_{-0.16} \\
+    0.0 & 23.13^{+0.33}_{-0.20} & 22.79^{+0.13}_{-0.15} & 23.01^{+0.33}_{-0.20} & 22.67^{+0.13}_{-0.15} & -13.66^{+0.08}_{-0.05} & -13.86^{+0.03}_{-0.03} \\
+    0.1 & 23.39^{+0.25}_{-0.16} & 23.06^{+0.10}_{-0.12} & 23.27^{+0.25}_{-0.16} & 22.94^{+0.10}_{-0.12} & -13.45^{+0.06}_{-0.05} & -13.65^{+0.03}_{-0.02} \\
+    0.2 & 23.61^{+0.18}_{-0.13} & 23.30^{+0.08}_{-0.09} & 23.49^{+0.18}_{-0.13} & 23.18^{+0.08}_{-0.09} & -13.27^{+0.05}_{-0.04} & -13.46^{+0.02}_{-0.02} \\
+    0.3 & 23.81^{+0.13}_{-0.11} & 23.52^{+0.06}_{-0.06} & 23.69^{+0.13}_{-0.11} & 23.39^{+0.06}_{-0.06} & -13.10^{+0.04}_{-0.04} & -13.29^{+0.02}_{-0.02} \\
+    0.4 & 23.99^{+0.09}_{-0.09} & 23.71^{+0.04}_{-0.04} & 23.86^{+0.09}_{-0.09} & 23.59^{+0.04}_{-0.04} & -12.95^{+0.04}_{-0.03} & -13.13^{+0.02}_{-0.02} \\
+    0.5 & 24.14^{+0.07}_{-0.07} & 23.89^{+0.03}_{-0.03} & 24.02^{+0.07}_{-0.07} & 23.76^{+0.03}_{-0.03} & -12.82^{+0.03}_{-0.03} & -12.98^{+0.01}_{-0.01} \\
+    0.6 & 24.28^{+0.05}_{-0.05} & 24.05^{+0.02}_{-0.02} & 24.16^{+0.05}_{-0.05} & 23.92^{+0.02}_{-0.02} & -12.69^{+0.03}_{-0.03} & -12.85^{+0.01}_{-0.01} \\
+    0.7 & 24.41^{+0.04}_{-0.03} & 24.19^{+0.02}_{-0.02} & 24.28^{+0.04}_{-0.03} & 24.07^{+0.02}_{-0.02} & -12.58^{+0.02}_{-0.02} & -12.74^{+0.01}_{-0.01} \\
+    0.8 & 24.52^{+0.03}_{-0.03} & 24.32^{+0.01}_{-0.01} & 24.40^{+0.03}_{-0.03} & 24.20^{+0.01}_{-0.01} & -12.48^{+0.02}_{-0.02} & -12.63^{+0.01}_{-0.01} \\
+    0.9 & 24.62^{+0.02}_{-0.02} & 24.44^{+0.01}_{-0.01} & 24.50^{+0.02}_{-0.02} & 24.31^{+0.01}_{-0.01} & -12.39^{+0.02}_{-0.02} & -12.53^{+0.01}_{-0.01} \\
+    1.0 & 24.71^{+0.02}_{-0.02} & 24.54^{+0.01}_{-0.01} & 24.59^{+0.02}_{-0.02} & 24.42^{+0.01}_{-0.01} & -12.31^{+0.02}_{-0.02} & -12.44^{+0.01}_{-0.01} \\
+    1.1 & 24.79^{+0.02}_{-0.02} & 24.64^{+0.01}_{-0.01} & 24.67^{+0.02}_{-0.02} & 24.52^{+0.01}_{-0.01} & -12.24^{+0.02}_{-0.02} & -12.37^{+0.01}_{-0.01} \\
+    1.2 & 24.87^{+0.02}_{-0.02} & 24.72^{+0.01}_{-0.01} & 24.75^{+0.02}_{-0.02} & 24.60^{+0.01}_{-0.01} & -12.17^{+0.02}_{-0.02} & -12.30^{+0.01}_{-0.01} \\
+    1.3 & 24.93^{+0.02}_{-0.02} & 24.80^{+0.01}_{-0.01} & 24.81^{+0.02}_{-0.02} & 24.68^{+0.01}_{-0.01} & -12.12^{+0.02}_{-0.02} & -12.24^{+0.01}_{-0.01} \\
+    1.4 & 24.99^{+0.02}_{-0.02} & 24.86^{+0.01}_{-0.01} & 24.87^{+0.02}_{-0.02} & 24.74^{+0.01}_{-0.01} & -12.08^{+0.02}_{-0.03} & -12.19^{+0.01}_{-0.01} \\
+    1.5 & 25.04^{+0.02}_{-0.02} & 24.92^{+0.01}_{-0.01} & 24.92^{+0.02}_{-0.02} & 24.80^{+0.01}_{-0.01} & -12.04^{+0.02}_{-0.03} & -12.15^{+0.02}_{-0.01} \\
+    1.6 & 25.08^{+0.02}_{-0.02} & 24.97^{+0.01}_{-0.01} & 24.96^{+0.02}_{-0.02} & 24.85^{+0.01}_{-0.01} & -12.01^{+0.03}_{-0.03} & -12.12^{+0.02}_{-0.02} \\
+    1.7 & 25.12^{+0.02}_{-0.02} & 25.01^{+0.01}_{-0.01} & 25.00^{+0.02}_{-0.02} & 24.89^{+0.01}_{-0.01} & -11.99^{+0.03}_{-0.03} & -12.10^{+0.02}_{-0.02} \\
+    1.8 & 25.15^{+0.02}_{-0.02} & 25.04^{+0.01}_{-0.01} & 25.03^{+0.02}_{-0.02} & 24.92^{+0.01}_{-0.01} & -11.97^{+0.03}_{-0.04} & -12.08^{+0.02}_{-0.02} \\
+    1.9 & 25.17^{+0.02}_{-0.02} & 25.07^{+0.01}_{-0.01} & 25.05^{+0.02}_{-0.02} & 24.94^{+0.01}_{-0.01} & -11.96^{+0.04}_{-0.04} & -12.07^{+0.02}_{-0.02} \\
+    2.0 & 25.19^{+0.03}_{-0.03} & 25.08^{+0.01}_{-0.01} & 25.07^{+0.03}_{-0.03} & 24.96^{+0.01}_{-0.01} & -11.95^{+0.04}_{-0.05} & -12.07^{+0.03}_{-0.03} \\
+    2.1 & 25.20^{+0.03}_{-0.04} & 25.10^{+0.02}_{-0.02} & 25.08^{+0.03}_{-0.04} & 24.97^{+0.02}_{-0.02} & -11.95^{+0.04}_{-0.05} & -12.07^{+0.03}_{-0.03} \\
+    2.2 & 25.21^{+0.03}_{-0.05} & 25.10^{+0.02}_{-0.02} & 25.09^{+0.03}_{-0.05} & 24.98^{+0.02}_{-0.02} & -11.95^{+0.05}_{-0.06} & -12.08^{+0.03}_{-0.03} \\
+    2.3 & 25.22^{+0.04}_{-0.05} & 25.10^{+0.03}_{-0.03} & 25.09^{+0.04}_{-0.05} & 24.98^{+0.03}_{-0.03} & -11.96^{+0.05}_{-0.07} & -12.09^{+0.04}_{-0.04} \\
+    2.4 & 25.22^{+0.05}_{-0.06} & 25.10^{+0.03}_{-0.03} & 25.09^{+0.05}_{-0.06} & 24.97^{+0.03}_{-0.03} & -11.97^{+0.06}_{-0.07} & -12.11^{+0.04}_{-0.04} \\
+    2.5 & 25.21^{+0.05}_{-0.06} & 25.09^{+0.04}_{-0.04} & 25.09^{+0.05}_{-0.06} & 24.97^{+0.04}_{-0.04} & -11.99^{+0.06}_{-0.08} & -12.13^{+0.05}_{-0.04} \\
+    2.6 & 25.21^{+0.05}_{-0.07} & 25.07^{+0.04}_{-0.04} & 25.08^{+0.05}_{-0.07} & 24.95^{+0.04}_{-0.04} & -12.01^{+0.07}_{-0.08} & -12.15^{+0.05}_{-0.04} \\
+    2.7 & 25.19^{+0.06}_{-0.07} & 25.05^{+0.05}_{-0.04} & 25.07^{+0.06}_{-0.07} & 24.93^{+0.05}_{-0.04} & -12.03^{+0.07}_{-0.09} & -12.18^{+0.05}_{-0.05} \\
+    2.8 & 25.18^{+0.07}_{-0.08} & 25.03^{+0.05}_{-0.05} & 25.06^{+0.06}_{-0.08} & 24.91^{+0.05}_{-0.05} & -12.05^{+0.08}_{-0.09} & -12.22^{+0.06}_{-0.05} \\
+    2.9 & 25.16^{+0.07}_{-0.09} & 25.01^{+0.05}_{-0.05} & 25.04^{+0.07}_{-0.09} & 24.89^{+0.05}_{-0.05} & -12.08^{+0.08}_{-0.10} & -12.25^{+0.06}_{-0.05} \\
+    3.0 & 25.14^{+0.08}_{-0.09} & 24.98^{+0.06}_{-0.05} & 25.02^{+0.08}_{-0.09} & 24.86^{+0.06}_{-0.05} & -12.11^{+0.09}_{-0.10} & -12.29^{+0.06}_{-0.05} \\
+    3.1 & 25.12^{+0.08}_{-0.10} & 24.95^{+0.06}_{-0.05} & 25.00^{+0.08}_{-0.10} & 24.83^{+0.06}_{-0.05} & -12.14^{+0.09}_{-0.11} & -12.33^{+0.06}_{-0.05} \\
+    3.2 & 25.09^{+0.09}_{-0.11} & 24.91^{+0.06}_{-0.05} & 24.97^{+0.09}_{-0.11} & 24.79^{+0.06}_{-0.05} & -12.18^{+0.10}_{-0.12} & -12.37^{+0.07}_{-0.06} \\
+    3.3 & 25.06^{+0.09}_{-0.11} & 24.88^{+0.06}_{-0.06} & 24.94^{+0.09}_{-0.11} & 24.75^{+0.06}_{-0.06} & -12.22^{+0.10}_{-0.12} & -12.42^{+0.07}_{-0.06} \\
+    3.4 & 25.03^{+0.10}_{-0.11} & 24.84^{+0.07}_{-0.05} & 24.91^{+0.10}_{-0.11} & 24.71^{+0.07}_{-0.05} & -12.26^{+0.11}_{-0.13} & -12.47^{+0.07}_{-0.06} \\
+    3.5 & 25.00^{+0.10}_{-0.12} & 24.80^{+0.07}_{-0.06} & 24.88^{+0.10}_{-0.12} & 24.68^{+0.07}_{-0.06} & -12.30^{+0.11}_{-0.13} & -12.52^{+0.07}_{-0.07} \\
+    3.6 & 24.97^{+0.11}_{-0.12} & 24.76^{+0.07}_{-0.07} & 24.84^{+0.11}_{-0.12} & 24.63^{+0.07}_{-0.07} & -12.34^{+0.11}_{-0.14} & -12.57^{+0.07}_{-0.07} \\
+    3.7 & 24.93^{+0.11}_{-0.13} & 24.71^{+0.07}_{-0.07} & 24.81^{+0.11}_{-0.13} & 24.59^{+0.07}_{-0.07} & -12.38^{+0.11}_{-0.15} & -12.63^{+0.07}_{-0.08} \\
+    3.8 & 24.90^{+0.11}_{-0.15} & 24.66^{+0.07}_{-0.07} & 24.78^{+0.11}_{-0.15} & 24.54^{+0.07}_{-0.07} & -12.43^{+0.12}_{-0.16} & -12.68^{+0.07}_{-0.08} \\
+    3.9 & 24.86^{+0.11}_{-0.16} & 24.61^{+0.07}_{-0.08} & 24.74^{+0.11}_{-0.16} & 24.49^{+0.07}_{-0.08} & -12.48^{+0.12}_{-0.17} & -12.74^{+0.07}_{-0.08} \\
+    4.0 & 24.83^{+0.11}_{-0.18} & 24.57^{+0.07}_{-0.08} & 24.71^{+0.11}_{-0.18} & 24.44^{+0.07}_{-0.08} & -12.52^{+0.12}_{-0.19} & -12.80^{+0.07}_{-0.09} \\
+    4.1 & 24.79^{+0.12}_{-0.19} & 24.51^{+0.07}_{-0.09} & 24.67^{+0.12}_{-0.19} & 24.39^{+0.07}_{-0.09} & -12.58^{+0.13}_{-0.19} & -12.87^{+0.07}_{-0.09} \\
+    4.2 & 24.74^{+0.13}_{-0.19} & 24.46^{+0.07}_{-0.09} & 24.62^{+0.13}_{-0.19} & 24.34^{+0.07}_{-0.09} & -12.63^{+0.14}_{-0.20} & -12.93^{+0.07}_{-0.09} \\
+    4.3 & 24.70^{+0.14}_{-0.20} & 24.40^{+0.07}_{-0.09} & 24.57^{+0.14}_{-0.20} & 24.28^{+0.07}_{-0.09} & -12.69^{+0.15}_{-0.21} & -12.99^{+0.08}_{-0.10} \\
+    4.4 & 24.65^{+0.15}_{-0.21} & 24.35^{+0.08}_{-0.10} & 24.53^{+0.15}_{-0.21} & 24.22^{+0.08}_{-0.10} & -12.75^{+0.15}_{-0.22} & -13.06^{+0.08}_{-0.11} \\
+    4.5 & 24.60^{+0.15}_{-0.22} & 24.29^{+0.08}_{-0.10} & 24.48^{+0.15}_{-0.22} & 24.17^{+0.08}_{-0.10} & -12.80^{+0.16}_{-0.23} & -13.13^{+0.08}_{-0.12} \\
+    4.6 & 24.56^{+0.15}_{-0.22} & 24.24^{+0.08}_{-0.12} & 24.43^{+0.15}_{-0.22} & 24.11^{+0.08}_{-0.12} & -12.86^{+0.16}_{-0.24} & -13.20^{+0.08}_{-0.13} \\
+    4.7 & 24.51^{+0.16}_{-0.23} & 24.17^{+0.09}_{-0.13} & 24.39^{+0.16}_{-0.23} & 24.05^{+0.09}_{-0.13} & -12.92^{+0.17}_{-0.25} & -13.27^{+0.09}_{-0.14} \\
+    4.8 & 24.46^{+0.17}_{-0.25} & 24.11^{+0.09}_{-0.14} & 24.34^{+0.17}_{-0.25} & 23.99^{+0.09}_{-0.14} & -12.98^{+0.17}_{-0.26} & -13.34^{+0.09}_{-0.15} \\
+    4.9 & 24.41^{+0.18}_{-0.26} & 24.05^{+0.09}_{-0.15} & 24.29^{+0.18}_{-0.26} & 23.93^{+0.09}_{-0.15} & -13.04^{+0.18}_{-0.27} & -13.41^{+0.09}_{-0.16} \\
+    5.0 & 24.36^{+0.17}_{-0.28} & 23.99^{+0.09}_{-0.16} & 24.24^{+0.17}_{-0.28} & 23.87^{+0.09}_{-0.16} & -13.10^{+0.18}_{-0.29} & -13.49^{+0.09}_{-0.17} \\
     \hline
@@
     \hline
-    5.1 & 24.27^{+0.20}_{-0.30} & 23.93^{+0.09}_{-0.15} & 24.14^{+0.20}_{-0.30} & 23.81^{+0.09}_{-0.15} & -13.21^{+0.21}_{-0.32} & -13.55^{+0.09}_{-0.16} \\
-    5.2 & 24.22^{+0.21}_{-0.32} & 23.88^{+0.09}_{-0.17} & 24.09^{+0.21}_{-0.32} & 23.75^{+0.09}_{-0.17} & -13.27^{+0.22}_{-0.33} & -13.62^{+0.10}_{-0.17} \\
-    5.3 & 24.16^{+0.22}_{-0.33} & 23.82^{+0.10}_{-0.18} & 24.03^{+0.22}_{-0.33} & 23.69^{+0.10}_{-0.18} & -13.34^{+0.23}_{-0.34} & -13.69^{+0.11}_{-0.18} \\
-    5.4 & 24.10^{+0.24}_{-0.34} & 23.75^{+0.11}_{-0.19} & 23.98^{+0.24}_{-0.34} & 23.63^{+0.11}_{-0.19} & -13.42^{+0.24}_{-0.36} & -13.77^{+0.11}_{-0.19} \\
-    5.5 & 24.05^{+0.24}_{-0.36} & 23.69^{+0.12}_{-0.19} & 23.93^{+0.24}_{-0.36} & 23.57^{+0.12}_{-0.19} & -13.49^{+0.25}_{-0.37} & -13.85^{+0.12}_{-0.20} \\
-    5.6 & 23.99^{+0.26}_{-0.38} & 23.63^{+0.12}_{-0.20} & 23.87^{+0.26}_{-0.38} & 23.50^{+0.12}_{-0.20} & -13.59^{+0.27}_{-0.38} & -13.95^{+0.12}_{-0.21} \\
-    5.7 & 23.93^{+0.27}_{-0.38} & 23.57^{+0.12}_{-0.22} & 23.81^{+0.27}_{-0.38} & 23.45^{+0.12}_{-0.22} & -13.69^{+0.28}_{-0.39} & -14.05^{+0.13}_{-0.22} \\
-    5.8 & 23.87^{+0.28}_{-0.40} & 23.51^{+0.13}_{-0.23} & 23.75^{+0.28}_{-0.40} & 23.39^{+0.13}_{-0.23} & -13.79^{+0.29}_{-0.40} & -14.15^{+0.13}_{-0.24} \\
-    5.9 & 23.81^{+0.29}_{-0.41} & 23.45^{+0.13}_{-0.25} & 23.69^{+0.29}_{-0.41} & 23.33^{+0.13}_{-0.25} & -13.90^{+0.30}_{-0.42} & -14.26^{+0.14}_{-0.25} \\
-    6.0 & 23.74^{+0.30}_{-0.42} & 23.38^{+0.14}_{-0.25} & 23.62^{+0.30}_{-0.42} & 23.26^{+0.14}_{-0.25} & -14.01^{+0.31}_{-0.43} & -14.38^{+0.15}_{-0.26} \\
-    6.1 & 23.68^{+0.32}_{-0.44} & 23.32^{+0.15}_{-0.26} & 23.56^{+0.32}_{-0.44} & 23.20^{+0.15}_{-0.26} & -14.13^{+0.32}_{-0.44} & -14.49^{+0.15}_{-0.27} \\
-    6.2 & 23.62^{+0.33}_{-0.46} & 23.25^{+0.16}_{-0.27} & 23.50^{+0.33}_{-0.45} & 23.13^{+0.16}_{-0.27} & -14.24^{+0.34}_{-0.46} & -14.61^{+0.16}_{-0.27} \\
-    6.3 & 23.56^{+0.35}_{-0.47} & 23.19^{+0.17}_{-0.27} & 23.44^{+0.35}_{-0.47} & 23.07^{+0.17}_{-0.27} & -14.36^{+0.35}_{-0.48} & -14.74^{+0.17}_{-0.28} \\
-    6.4 & 23.50^{+0.36}_{-0.49} & 23.12^{+0.18}_{-0.28} & 23.38^{+0.36}_{-0.49} & 23.00^{+0.18}_{-0.28} & -14.48^{+0.36}_{-0.50} & -14.87^{+0.18}_{-0.28} \\
-    6.5 & 23.45^{+0.36}_{-0.52} & 23.05^{+0.18}_{-0.29} & 23.33^{+0.36}_{-0.52} & 22.93^{+0.18}_{-0.29} & -14.60^{+0.37}_{-0.52} & -15.00^{+0.19}_{-0.29} \\
-    6.6 & 23.38^{+0.37}_{-0.53} & 22.99^{+0.19}_{-0.30} & 23.26^{+0.37}_{-0.53} & 22.86^{+0.19}_{-0.30} & -14.74^{+0.38}_{-0.54} & -15.13^{+0.20}_{-0.30} \\
-    6.7 & 23.31^{+0.39}_{-0.54} & 22.92^{+0.20}_{-0.31} & 23.19^{+0.39}_{-0.54} & 22.80^{+0.20}_{-0.31} & -14.88^{+0.40}_{-0.55} & -15.28^{+0.21}_{-0.31} \\
-    6.8 & 23.24^{+0.41}_{-0.56} & 22.85^{+0.22}_{-0.32} & 23.12^{+0.41}_{-0.56} & 22.72^{+0.22}_{-0.32} & -15.03^{+0.41}_{-0.56} & -15.42^{+0.22}_{-0.32} \\
-    6.9 & 23.17^{+0.42}_{-0.57} & 22.77^{+0.23}_{-0.33} & 23.05^{+0.42}_{-0.57} & 22.65^{+0.23}_{-0.33} & -15.18^{+0.43}_{-0.58} & -15.57^{+0.23}_{-0.33} \\
-    7.0 & 23.11^{+0.44}_{-0.59} & 22.70^{+0.24}_{-0.34} & 22.98^{+0.44}_{-0.59} & 22.58^{+0.24}_{-0.34} & -15.33^{+0.44}_{-0.59} & -15.73^{+0.24}_{-0.34} \\
-    7.1 & 23.04^{+0.45}_{-0.61} & 22.64^{+0.25}_{-0.35} & 22.91^{+0.45}_{-0.61} & 22.51^{+0.25}_{-0.35} & -15.48^{+0.46}_{-0.61} & -15.88^{+0.25}_{-0.36} \\
-    7.2 & 22.96^{+0.47}_{-0.62} & 22.57^{+0.26}_{-0.37} & 22.84^{+0.47}_{-0.62} & 22.44^{+0.26}_{-0.37} & -15.64^{+0.48}_{-0.62} & -16.03^{+0.26}_{-0.37} \\
-    7.3 & 22.89^{+0.49}_{-0.63} & 22.50^{+0.27}_{-0.38} & 22.77^{+0.49}_{-0.63} & 22.38^{+0.27}_{-0.38} & -15.79^{+0.50}_{-0.63} & -16.19^{+0.27}_{-0.38} \\
-    7.4 & 22.84^{+0.51}_{-0.65} & 22.43^{+0.28}_{-0.39} & 22.71^{+0.51}_{-0.65} & 22.31^{+0.28}_{-0.39} & -15.94^{+0.51}_{-0.65} & -16.35^{+0.28}_{-0.40} \\
-    7.5 & 22.77^{+0.51}_{-0.67} & 22.36^{+0.28}_{-0.41} & 22.65^{+0.51}_{-0.67} & 22.24^{+0.28}_{-0.41} & -16.09^{+0.52}_{-0.68} & -16.50^{+0.29}_{-0.41} \\
-    7.6 & 22.70^{+0.53}_{-0.69} & 22.29^{+0.29}_{-0.42} & 22.58^{+0.53}_{-0.69} & 22.17^{+0.29}_{-0.42} & -16.24^{+0.53}_{-0.69} & -16.66^{+0.30}_{-0.42} \\
-    7.7 & 22.63^{+0.54}_{-0.70} & 22.22^{+0.31}_{-0.43} & 22.51^{+0.54}_{-0.70} & 22.10^{+0.31}_{-0.43} & -16.40^{+0.55}_{-0.71} & -16.81^{+0.31}_{-0.44} \\
-    7.8 & 22.56^{+0.56}_{-0.72} & 22.15^{+0.31}_{-0.45} & 22.44^{+0.56}_{-0.73} & 22.03^{+0.31}_{-0.45} & -16.55^{+0.57}_{-0.73} & -16.96^{+0.31}_{-0.45} \\
-    7.9 & 22.49^{+0.58}_{-0.74} & 22.08^{+0.32}_{-0.46} & 22.36^{+0.58}_{-0.74} & 21.96^{+0.32}_{-0.46} & -16.71^{+0.59}_{-0.75} & -17.12^{+0.32}_{-0.47} \\
-    8.0 & 22.42^{+0.60}_{-0.76} & 22.01^{+0.32}_{-0.48} & 22.30^{+0.60}_{-0.76} & 21.89^{+0.32}_{-0.48} & -16.85^{+0.61}_{-0.77} & -17.27^{+0.32}_{-0.48} \\
-    8.1 & 22.35^{+0.62}_{-0.78} & 21.94^{+0.33}_{-0.49} & 22.23^{+0.62}_{-0.78} & 21.81^{+0.33}_{-0.49} & -17.00^{+0.63}_{-0.78} & -17.42^{+0.34}_{-0.50} \\
-    8.2 & 22.28^{+0.64}_{-0.80} & 21.86^{+0.34}_{-0.51} & 22.16^{+0.64}_{-0.80} & 21.74^{+0.34}_{-0.50} & -17.14^{+0.65}_{-0.81} & -17.57^{+0.35}_{-0.51} \\
-    8.3 & 22.21^{+0.67}_{-0.82} & 21.79^{+0.36}_{-0.52} & 22.09^{+0.67}_{-0.82} & 21.66^{+0.36}_{-0.52} & -17.29^{+0.67}_{-0.82} & -17.71^{+0.36}_{-0.52} \\
-    8.4 & 22.13^{+0.69}_{-0.83} & 21.72^{+0.37}_{-0.53} & 22.01^{+0.69}_{-0.83} & 21.59^{+0.37}_{-0.53} & -17.44^{+0.70}_{-0.84} & -17.86^{+0.37}_{-0.53} \\
-    8.5 & 22.06^{+0.71}_{-0.86} & 21.64^{+0.38}_{-0.54} & 21.94^{+0.71}_{-0.86} & 21.52^{+0.38}_{-0.54} & -17.58^{+0.72}_{-0.86} & -18.01^{+0.38}_{-0.54} \\
-    8.6 & 21.98^{+0.74}_{-0.87} & 21.56^{+0.39}_{-0.55} & 21.86^{+0.74}_{-0.87} & 21.44^{+0.39}_{-0.55} & -17.73^{+0.75}_{-0.88} & -18.15^{+0.39}_{-0.55} \\
-    8.7 & 21.91^{+0.76}_{-0.89} & 21.49^{+0.40}_{-0.56} & 21.79^{+0.76}_{-0.89} & 21.36^{+0.40}_{-0.56} & -17.87^{+0.77}_{-0.90} & -18.30^{+0.41}_{-0.56} \\
-    8.8 & 21.84^{+0.78}_{-0.92} & 21.41^{+0.42}_{-0.57} & 21.72^{+0.78}_{-0.92} & 21.28^{+0.42}_{-0.57} & -18.01^{+0.79}_{-0.92} & -18.44^{+0.42}_{-0.57} \\
-    8.9 & 21.76^{+0.80}_{-0.94} & 21.33^{+0.43}_{-0.58} & 21.64^{+0.80}_{-0.94} & 21.20^{+0.43}_{-0.58} & -18.15^{+0.81}_{-0.95} & -18.59^{+0.44}_{-0.58} \\
-    9.0 & 21.68^{+0.82}_{-0.96} & 21.25^{+0.45}_{-0.58} & 21.56^{+0.82}_{-0.96} & 21.12^{+0.45}_{-0.58} & -18.29^{+0.83}_{-0.96} & -18.73^{+0.46}_{-0.59} \\
-    9.1 & 21.60^{+0.85}_{-0.97} & 21.17^{+0.46}_{-0.60} & 21.48^{+0.85}_{-0.97} & 21.05^{+0.46}_{-0.60} & -18.44^{+0.86}_{-0.98} & -18.87^{+0.47}_{-0.60} \\
-    9.2 & 21.52^{+0.87}_{-0.99} & 21.09^{+0.48}_{-0.61} & 21.40^{+0.87}_{-0.99} & 20.97^{+0.48}_{-0.61} & -18.58^{+0.88}_{-1.00} & -19.01^{+0.48}_{-0.62} \\
-    9.3 & 21.45^{+0.89}_{-1.01} & 21.02^{+0.49}_{-0.63} & 21.33^{+0.89}_{-1.01} & 20.89^{+0.49}_{-0.63} & -18.71^{+0.90}_{-1.01} & -19.15^{+0.49}_{-0.63} \\
-    9.4 & 21.37^{+0.90}_{-1.02} & 20.94^{+0.50}_{-0.64} & 21.25^{+0.90}_{-1.02} & 20.82^{+0.50}_{-0.64} & -18.85^{+0.91}_{-1.03} & -19.29^{+0.50}_{-0.64} \\
-    9.5 & 21.30^{+0.92}_{-1.05} & 20.86^{+0.51}_{-0.64} & 21.18^{+0.92}_{-1.05} & 20.74^{+0.51}_{-0.64} & -18.98^{+0.93}_{-1.05} & -19.42^{+0.52}_{-0.65} \\
-    9.6 & 21.23^{+0.94}_{-1.07} & 20.78^{+0.52}_{-0.65} & 21.10^{+0.94}_{-1.07} & 20.66^{+0.52}_{-0.65} & -19.12^{+0.95}_{-1.08} & -19.56^{+0.53}_{-0.66} \\
-    9.7 & 21.15^{+0.96}_{-1.09} & 20.70^{+0.54}_{-0.67} & 21.02^{+0.96}_{-1.09} & 20.58^{+0.54}_{-0.67} & -19.25^{+0.97}_{-1.10} & -19.70^{+0.54}_{-0.67} \\
-    9.8 & 21.07^{+0.98}_{-1.11} & 20.62^{+0.55}_{-0.68} & 20.95^{+0.98}_{-1.11} & 20.50^{+0.55}_{-0.68} & -19.38^{+1.00}_{-1.12} & -19.84^{+0.55}_{-0.68} \\
-    9.9 & 20.99^{+1.01}_{-1.14} & 20.54^{+0.56}_{-0.69} & 20.87^{+1.01}_{-1.14} & 20.42^{+0.56}_{-0.69} & -19.52^{+1.02}_{-1.14} & -19.97^{+0.57}_{-0.69} \\
-    10.0 & 20.91^{+1.03}_{-1.16} & 20.46^{+0.57}_{-0.70} & 20.79^{+1.03}_{-1.16} & 20.34^{+0.57}_{-0.70} & -19.65^{+1.05}_{-1.17} & -20.10^{+0.57}_{-0.71} \\
+    5.1 & 24.31^{+0.18}_{-0.29} & 23.93^{+0.09}_{-0.17} & 24.18^{+0.18}_{-0.29} & 23.80^{+0.09}_{-0.17} & -13.17^{+0.19}_{-0.30} & -13.56^{+0.10}_{-0.17} \\
+    5.2 & 24.25^{+0.19}_{-0.30} & 23.86^{+0.10}_{-0.17} & 24.13^{+0.19}_{-0.30} & 23.74^{+0.10}_{-0.17} & -13.24^{+0.20}_{-0.31} & -13.64^{+0.11}_{-0.18} \\
+    5.3 & 24.19^{+0.20}_{-0.32} & 23.79^{+0.11}_{-0.19} & 24.07^{+0.20}_{-0.32} & 23.67^{+0.11}_{-0.19} & -13.31^{+0.21}_{-0.33} & -13.72^{+0.12}_{-0.20} \\
+    5.4 & 24.14^{+0.22}_{-0.33} & 23.73^{+0.12}_{-0.20} & 24.01^{+0.22}_{-0.33} & 23.60^{+0.12}_{-0.20} & -13.38^{+0.23}_{-0.34} & -13.80^{+0.13}_{-0.21} \\
+    5.5 & 24.08^{+0.23}_{-0.34} & 23.66^{+0.13}_{-0.21} & 23.95^{+0.23}_{-0.34} & 23.53^{+0.13}_{-0.21} & -13.47^{+0.24}_{-0.36} & -13.89^{+0.14}_{-0.22} \\
+    5.6 & 24.01^{+0.24}_{-0.36} & 23.59^{+0.14}_{-0.23} & 23.89^{+0.24}_{-0.36} & 23.47^{+0.14}_{-0.23} & -13.56^{+0.25}_{-0.37} & -14.00^{+0.14}_{-0.24} \\
+    5.7 & 23.96^{+0.25}_{-0.38} & 23.52^{+0.15}_{-0.25} & 23.84^{+0.25}_{-0.38} & 23.40^{+0.15}_{-0.25} & -13.66^{+0.26}_{-0.39} & -14.11^{+0.15}_{-0.25} \\
+    5.8 & 23.90^{+0.26}_{-0.39} & 23.45^{+0.16}_{-0.25} & 23.78^{+0.26}_{-0.39} & 23.32^{+0.16}_{-0.25} & -13.76^{+0.27}_{-0.40} & -14.22^{+0.16}_{-0.26} \\
+    5.9 & 23.83^{+0.28}_{-0.40} & 23.37^{+0.17}_{-0.26} & 23.71^{+0.28}_{-0.40} & 23.25^{+0.17}_{-0.26} & -13.88^{+0.28}_{-0.41} & -14.34^{+0.18}_{-0.26} \\
+    6.0 & 23.77^{+0.28}_{-0.42} & 23.30^{+0.18}_{-0.27} & 23.65^{+0.28}_{-0.42} & 23.17^{+0.18}_{-0.27} & -13.99^{+0.29}_{-0.43} & -14.47^{+0.19}_{-0.28} \\
+    6.1 & 23.71^{+0.30}_{-0.43} & 23.23^{+0.19}_{-0.29} & 23.59^{+0.30}_{-0.43} & 23.11^{+0.19}_{-0.29} & -14.10^{+0.30}_{-0.44} & -14.59^{+0.19}_{-0.29} \\
+    6.2 & 23.65^{+0.31}_{-0.45} & 23.15^{+0.20}_{-0.30} & 23.52^{+0.31}_{-0.45} & 23.03^{+0.20}_{-0.30} & -14.22^{+0.32}_{-0.46} & -14.72^{+0.21}_{-0.30} \\
+    6.3 & 23.59^{+0.33}_{-0.47} & 23.07^{+0.21}_{-0.31} & 23.47^{+0.33}_{-0.47} & 22.95^{+0.21}_{-0.31} & -14.33^{+0.33}_{-0.48} & -14.85^{+0.22}_{-0.32} \\
+    6.4 & 23.53^{+0.34}_{-0.50} & 23.00^{+0.22}_{-0.33} & 23.41^{+0.34}_{-0.50} & 22.88^{+0.22}_{-0.33} & -14.46^{+0.34}_{-0.50} & -14.99^{+0.23}_{-0.33} \\
+    6.5 & 23.47^{+0.35}_{-0.51} & 22.91^{+0.24}_{-0.34} & 23.34^{+0.35}_{-0.51} & 22.79^{+0.24}_{-0.34} & -14.59^{+0.36}_{-0.52} & -15.14^{+0.25}_{-0.34} \\
+    6.6 & 23.40^{+0.37}_{-0.53} & 22.83^{+0.26}_{-0.35} & 23.28^{+0.37}_{-0.53} & 22.71^{+0.26}_{-0.35} & -14.72^{+0.38}_{-0.54} & -15.29^{+0.27}_{-0.35} \\
+    6.7 & 23.33^{+0.39}_{-0.55} & 22.76^{+0.27}_{-0.37} & 23.21^{+0.39}_{-0.55} & 22.64^{+0.27}_{-0.37} & -14.86^{+0.40}_{-0.55} & -15.44^{+0.27}_{-0.38} \\
+    6.8 & 23.26^{+0.42}_{-0.56} & 22.68^{+0.28}_{-0.40} & 23.14^{+0.42}_{-0.56} & 22.56^{+0.28}_{-0.40} & -15.01^{+0.43}_{-0.56} & -15.59^{+0.28}_{-0.40} \\
+    6.9 & 23.19^{+0.44}_{-0.58} & 22.60^{+0.29}_{-0.41} & 23.07^{+0.44}_{-0.58} & 22.48^{+0.29}_{-0.41} & -15.16^{+0.45}_{-0.58} & -15.75^{+0.30}_{-0.41} \\
+    7.0 & 23.12^{+0.46}_{-0.59} & 22.52^{+0.31}_{-0.42} & 23.00^{+0.46}_{-0.59} & 22.40^{+0.31}_{-0.42} & -15.31^{+0.46}_{-0.60} & -15.91^{+0.31}_{-0.43} \\
+    7.1 & 23.05^{+0.48}_{-0.61} & 22.45^{+0.32}_{-0.44} & 22.93^{+0.48}_{-0.61} & 22.32^{+0.32}_{-0.44} & -15.47^{+0.48}_{-0.61} & -16.07^{+0.32}_{-0.45} \\
+    7.2 & 22.98^{+0.50}_{-0.62} & 22.37^{+0.33}_{-0.47} & 22.85^{+0.50}_{-0.62} & 22.24^{+0.33}_{-0.47} & -15.62^{+0.50}_{-0.62} & -16.24^{+0.33}_{-0.47} \\
+    7.3 & 22.91^{+0.52}_{-0.64} & 22.29^{+0.34}_{-0.48} & 22.78^{+0.52}_{-0.64} & 22.17^{+0.34}_{-0.48} & -15.78^{+0.52}_{-0.64} & -16.40^{+0.34}_{-0.49} \\
+    7.4 & 22.84^{+0.53}_{-0.66} & 22.21^{+0.35}_{-0.50} & 22.72^{+0.53}_{-0.66} & 22.09^{+0.35}_{-0.50} & -15.94^{+0.54}_{-0.66} & -16.57^{+0.35}_{-0.51} \\
+    7.5 & 22.77^{+0.55}_{-0.68} & 22.13^{+0.36}_{-0.52} & 22.65^{+0.55}_{-0.68} & 22.01^{+0.36}_{-0.52} & -16.09^{+0.56}_{-0.68} & -16.73^{+0.37}_{-0.53} \\
+    7.6 & 22.70^{+0.57}_{-0.69} & 22.05^{+0.38}_{-0.54} & 22.57^{+0.57}_{-0.69} & 21.93^{+0.38}_{-0.54} & -16.25^{+0.58}_{-0.70} & -16.90^{+0.38}_{-0.55} \\
+    7.7 & 22.63^{+0.59}_{-0.71} & 21.97^{+0.39}_{-0.56} & 22.51^{+0.59}_{-0.71} & 21.85^{+0.39}_{-0.56} & -16.40^{+0.60}_{-0.72} & -17.07^{+0.40}_{-0.56} \\
+    7.8 & 22.56^{+0.61}_{-0.73} & 21.89^{+0.41}_{-0.58} & 22.44^{+0.61}_{-0.73} & 21.76^{+0.41}_{-0.58} & -16.56^{+0.61}_{-0.74} & -17.23^{+0.41}_{-0.58} \\
+    7.9 & 22.49^{+0.62}_{-0.76} & 21.80^{+0.43}_{-0.60} & 22.37^{+0.62}_{-0.76} & 21.68^{+0.43}_{-0.60} & -16.71^{+0.62}_{-0.76} & -17.40^{+0.43}_{-0.61} \\
+    8.0 & 22.41^{+0.63}_{-0.77} & 21.72^{+0.44}_{-0.63} & 22.29^{+0.63}_{-0.77} & 21.60^{+0.44}_{-0.63} & -16.86^{+0.64}_{-0.78} & -17.56^{+0.44}_{-0.63} \\
+    8.1 & 22.34^{+0.65}_{-0.80} & 21.63^{+0.45}_{-0.65} & 22.22^{+0.65}_{-0.80} & 21.51^{+0.45}_{-0.65} & -17.01^{+0.66}_{-0.80} & -17.72^{+0.46}_{-0.65} \\
+    8.2 & 22.26^{+0.68}_{-0.81} & 21.55^{+0.47}_{-0.67} & 22.14^{+0.68}_{-0.81} & 21.43^{+0.47}_{-0.67} & -17.17^{+0.68}_{-0.82} & -17.88^{+0.47}_{-0.68} \\
+    8.3 & 22.19^{+0.70}_{-0.83} & 21.46^{+0.48}_{-0.70} & 22.06^{+0.70}_{-0.83} & 21.34^{+0.48}_{-0.70} & -17.31^{+0.71}_{-0.84} & -18.04^{+0.49}_{-0.70} \\
+    8.4 & 22.12^{+0.72}_{-0.86} & 21.38^{+0.50}_{-0.72} & 21.99^{+0.72}_{-0.86} & 21.25^{+0.50}_{-0.72} & -17.46^{+0.72}_{-0.86} & -18.20^{+0.51}_{-0.72} \\
+    8.5 & 22.04^{+0.73}_{-0.87} & 21.29^{+0.52}_{-0.74} & 21.92^{+0.73}_{-0.87} & 21.16^{+0.52}_{-0.74} & -17.61^{+0.74}_{-0.88} & -18.36^{+0.53}_{-0.74} \\
+    8.6 & 21.96^{+0.76}_{-0.89} & 21.20^{+0.54}_{-0.76} & 21.84^{+0.76}_{-0.89} & 21.07^{+0.54}_{-0.76} & -17.75^{+0.77}_{-0.89} & -18.52^{+0.54}_{-0.76} \\
+    8.7 & 21.88^{+0.79}_{-0.90} & 21.11^{+0.55}_{-0.78} & 21.76^{+0.79}_{-0.90} & 20.99^{+0.55}_{-0.78} & -17.90^{+0.79}_{-0.90} & -18.67^{+0.56}_{-0.79} \\
+    8.8 & 21.81^{+0.81}_{-0.91} & 21.03^{+0.57}_{-0.81} & 21.69^{+0.81}_{-0.91} & 20.91^{+0.57}_{-0.81} & -18.04^{+0.82}_{-0.92} & -18.82^{+0.57}_{-0.81} \\
+    8.9 & 21.73^{+0.83}_{-0.93} & 20.95^{+0.58}_{-0.83} & 21.61^{+0.83}_{-0.93} & 20.82^{+0.58}_{-0.83} & -18.18^{+0.84}_{-0.94} & -18.97^{+0.59}_{-0.84} \\
+    9.0 & 21.65^{+0.85}_{-0.94} & 20.86^{+0.60}_{-0.85} & 21.53^{+0.85}_{-0.94} & 20.74^{+0.60}_{-0.85} & -18.33^{+0.86}_{-0.95} & -19.12^{+0.60}_{-0.86} \\
+    9.1 & 21.57^{+0.88}_{-0.95} & 20.77^{+0.61}_{-0.87} & 21.45^{+0.88}_{-0.95} & 20.65^{+0.61}_{-0.87} & -18.47^{+0.89}_{-0.96} & -19.28^{+0.62}_{-0.88} \\
+    9.2 & 21.50^{+0.90}_{-0.97} & 20.68^{+0.63}_{-0.89} & 21.37^{+0.90}_{-0.97} & 20.56^{+0.63}_{-0.89} & -18.61^{+0.91}_{-0.98} & -19.43^{+0.63}_{-0.90} \\
+    9.3 & 21.42^{+0.92}_{-0.99} & 20.59^{+0.64}_{-0.92} & 21.30^{+0.92}_{-0.99} & 20.47^{+0.64}_{-0.92} & -18.75^{+0.93}_{-1.00} & -19.58^{+0.65}_{-0.92} \\
+    9.4 & 21.34^{+0.94}_{-1.01} & 20.50^{+0.66}_{-0.94} & 21.22^{+0.94}_{-1.01} & 20.38^{+0.65}_{-0.94} & -18.89^{+0.95}_{-1.02} & -19.72^{+0.66}_{-0.95} \\
+    9.5 & 21.26^{+0.97}_{-1.03} & 20.42^{+0.67}_{-0.96} & 21.14^{+0.97}_{-1.03} & 20.29^{+0.67}_{-0.96} & -19.02^{+0.98}_{-1.04} & -19.87^{+0.68}_{-0.97} \\
+    9.6 & 21.18^{+0.99}_{-1.05} & 20.33^{+0.68}_{-0.98} & 21.06^{+0.99}_{-1.05} & 20.20^{+0.68}_{-0.98} & -19.16^{+1.00}_{-1.05} & -20.02^{+0.69}_{-0.99} \\
+    9.7 & 21.10^{+1.02}_{-1.06} & 20.24^{+0.70}_{-1.01} & 20.97^{+1.02}_{-1.06} & 20.12^{+0.70}_{-1.01} & -19.30^{+1.03}_{-1.07} & -20.16^{+0.70}_{-1.02} \\
+    9.8 & 21.01^{+1.04}_{-1.08} & 20.15^{+0.71}_{-1.03} & 20.89^{+1.04}_{-1.08} & 20.03^{+0.71}_{-1.03} & -19.44^{+1.06}_{-1.09} & -20.31^{+0.71}_{-1.04} \\
+    9.9 & 20.93^{+1.07}_{-1.10} & 20.06^{+0.72}_{-1.06} & 20.81^{+1.07}_{-1.10} & 19.94^{+0.72}_{-1.06} & -19.58^{+1.08}_{-1.11} & -20.45^{+0.73}_{-1.07} \\
+    10.0 & 20.85^{+1.10}_{-1.12} & 19.97^{+0.73}_{-1.08} & 20.72^{+1.10}_{-1.12} & 19.85^{+0.73}_{-1.08} & -19.72^{+1.11}_{-1.12} & -20.60^{+0.74}_{-1.09} \\
     \hline
@@
     \hline
-    10.1 & 20.84^{+1.06}_{-1.18} & 20.39^{+0.58}_{-0.72} & 20.72^{+1.06}_{-1.18} & 20.26^{+0.58}_{-0.72} & -19.78^{+1.07}_{-1.19} & -20.23^{+0.58}_{-0.73} \\
-    10.2 & 20.76^{+1.08}_{-1.20} & 20.31^{+0.59}_{-0.74} & 20.63^{+1.08}_{-1.20} & 20.18^{+0.59}_{-0.74} & -19.92^{+1.10}_{-1.20} & -20.37^{+0.60}_{-0.74} \\
-    10.3 & 20.67^{+1.11}_{-1.21} & 20.23^{+0.60}_{-0.75} & 20.55^{+1.11}_{-1.21} & 20.11^{+0.60}_{-0.75} & -20.05^{+1.12}_{-1.22} & -20.50^{+0.61}_{-0.75} \\
-    10.4 & 20.59^{+1.14}_{-1.23} & 20.15^{+0.61}_{-0.76} & 20.47^{+1.14}_{-1.23} & 20.03^{+0.61}_{-0.76} & -20.19^{+1.15}_{-1.24} & -20.63^{+0.62}_{-0.77} \\
-    10.5 & 20.51^{+1.16}_{-1.25} & 20.07^{+0.62}_{-0.77} & 20.39^{+1.16}_{-1.25} & 19.95^{+0.62}_{-0.77} & -20.32^{+1.18}_{-1.26} & -20.76^{+0.63}_{-0.78} \\
-    10.6 & 20.43^{+1.18}_{-1.28} & 19.99^{+0.64}_{-0.79} & 20.31^{+1.18}_{-1.28} & 19.87^{+0.64}_{-0.79} & -20.45^{+1.20}_{-1.29} & -20.89^{+0.64}_{-0.79} \\
-    10.7 & 20.35^{+1.21}_{-1.30} & 19.91^{+0.65}_{-0.80} & 20.23^{+1.21}_{-1.30} & 19.79^{+0.65}_{-0.80} & -20.58^{+1.23}_{-1.30} & -21.02^{+0.66}_{-0.81} \\
-    10.8 & 20.26^{+1.24}_{-1.31} & 19.83^{+0.66}_{-0.82} & 20.14^{+1.24}_{-1.31} & 19.71^{+0.66}_{-0.82} & -20.72^{+1.25}_{-1.32} & -21.15^{+0.67}_{-0.82} \\
-    10.9 & 20.18^{+1.26}_{-1.33} & 19.75^{+0.68}_{-0.83} & 20.06^{+1.26}_{-1.33} & 19.63^{+0.68}_{-0.83} & -20.85^{+1.28}_{-1.34} & -21.28^{+0.68}_{-0.84} \\
-    11.0 & 20.10^{+1.29}_{-1.35} & 19.67^{+0.69}_{-0.85} & 19.98^{+1.29}_{-1.35} & 19.55^{+0.69}_{-0.85} & -20.98^{+1.30}_{-1.35} & -21.41^{+0.69}_{-0.86} \\
-    11.1 & 20.02^{+1.32}_{-1.36} & 19.60^{+0.70}_{-0.87} & 19.89^{+1.32}_{-1.36} & 19.47^{+0.70}_{-0.87} & -21.11^{+1.33}_{-1.37} & -21.53^{+0.70}_{-0.88} \\
-    11.2 & 19.93^{+1.35}_{-1.38} & 19.52^{+0.71}_{-0.88} & 19.81^{+1.35}_{-1.38} & 19.40^{+0.71}_{-0.88} & -21.25^{+1.36}_{-1.39} & -21.66^{+0.72}_{-0.89} \\
-    11.3 & 19.85^{+1.37}_{-1.40} & 19.44^{+0.72}_{-0.90} & 19.73^{+1.37}_{-1.40} & 19.32^{+0.72}_{-0.90} & -21.38^{+1.39}_{-1.42} & -21.78^{+0.73}_{-0.91} \\
-    11.4 & 19.77^{+1.40}_{-1.43} & 19.36^{+0.73}_{-0.92} & 19.64^{+1.40}_{-1.43} & 19.24^{+0.73}_{-0.92} & -21.51^{+1.41}_{-1.44} & -21.91^{+0.73}_{-0.93} \\
-    11.5 & 19.69^{+1.42}_{-1.46} & 19.29^{+0.74}_{-0.94} & 19.57^{+1.42}_{-1.46} & 19.16^{+0.74}_{-0.94} & -21.63^{+1.43}_{-1.47} & -22.03^{+0.74}_{-0.95} \\
-    11.6 & 19.60^{+1.45}_{-1.47} & 19.21^{+0.75}_{-0.96} & 19.48^{+1.45}_{-1.47} & 19.08^{+0.75}_{-0.96} & -21.76^{+1.46}_{-1.48} & -22.16^{+0.75}_{-0.97} \\
-    11.7 & 19.52^{+1.47}_{-1.49} & 19.13^{+0.76}_{-0.98} & 19.40^{+1.47}_{-1.49} & 19.00^{+0.76}_{-0.98} & -21.89^{+1.49}_{-1.50} & -22.29^{+0.76}_{-0.99} \\
-    11.8 & 19.44^{+1.50}_{-1.51} & 19.05^{+0.77}_{-1.00} & 19.32^{+1.50}_{-1.51} & 18.92^{+0.77}_{-1.00} & -22.02^{+1.51}_{-1.52} & -22.41^{+0.78}_{-1.00} \\
-    11.9 & 19.35^{+1.52}_{-1.53} & 18.96^{+0.78}_{-1.01} & 19.23^{+1.52}_{-1.53} & 18.84^{+0.78}_{-1.01} & -22.15^{+1.54}_{-1.54} & -22.54^{+0.79}_{-1.02} \\
-    12.0 & 19.27^{+1.55}_{-1.55} & 18.88^{+0.80}_{-1.03} & 19.14^{+1.55}_{-1.55} & 18.76^{+0.80}_{-1.03} & -22.28^{+1.57}_{-1.56} & -22.67^{+0.80}_{-1.04} \\
-    12.1 & 19.18^{+1.58}_{-1.57} & 18.80^{+0.81}_{-1.05} & 19.06^{+1.58}_{-1.57} & 18.68^{+0.81}_{-1.05} & -22.41^{+1.59}_{-1.58} & -22.79^{+0.81}_{-1.06} \\
-    12.2 & 19.10^{+1.60}_{-1.60} & 18.72^{+0.82}_{-1.07} & 18.98^{+1.60}_{-1.60} & 18.60^{+0.82}_{-1.07} & -22.54^{+1.62}_{-1.61} & -22.92^{+0.83}_{-1.07} \\
-    12.3 & 19.01^{+1.63}_{-1.62} & 18.64^{+0.83}_{-1.08} & 18.89^{+1.63}_{-1.62} & 18.51^{+0.83}_{-1.08} & -22.67^{+1.65}_{-1.63} & -23.04^{+0.84}_{-1.09} \\
-    12.4 & 18.92^{+1.66}_{-1.64} & 18.56^{+0.84}_{-1.09} & 18.80^{+1.66}_{-1.64} & 18.43^{+0.84}_{-1.09} & -22.80^{+1.68}_{-1.65} & -23.17^{+0.85}_{-1.10} \\
-    12.5 & 18.84^{+1.69}_{-1.66} & 18.48^{+0.85}_{-1.11} & 18.72^{+1.69}_{-1.66} & 18.35^{+0.85}_{-1.11} & -22.93^{+1.70}_{-1.68} & -23.29^{+0.86}_{-1.12} \\
-    12.6 & 18.76^{+1.71}_{-1.69} & 18.39^{+0.86}_{-1.13} & 18.64^{+1.71}_{-1.69} & 18.27^{+0.86}_{-1.12} & -23.05^{+1.73}_{-1.70} & -23.42^{+0.87}_{-1.13} \\
-    12.7 & 18.68^{+1.74}_{-1.72} & 18.31^{+0.88}_{-1.14} & 18.56^{+1.74}_{-1.72} & 18.19^{+0.88}_{-1.14} & -23.18^{+1.75}_{-1.73} & -23.54^{+0.88}_{-1.15} \\
-    12.8 & 18.59^{+1.76}_{-1.74} & 18.23^{+0.89}_{-1.16} & 18.47^{+1.76}_{-1.74} & 18.11^{+0.89}_{-1.16} & -23.30^{+1.78}_{-1.75} & -23.67^{+0.90}_{-1.16} \\
-    12.9 & 18.51^{+1.78}_{-1.76} & 18.15^{+0.90}_{-1.17} & 18.39^{+1.78}_{-1.76} & 18.02^{+0.90}_{-1.17} & -23.43^{+1.80}_{-1.78} & -23.79^{+0.91}_{-1.18} \\
-    13.0 & 18.43^{+1.81}_{-1.79} & 18.06^{+0.91}_{-1.19} & 18.31^{+1.81}_{-1.79} & 17.94^{+0.91}_{-1.19} & -23.55^{+1.82}_{-1.81} & -23.92^{+0.92}_{-1.19} \\
-    13.1 & 18.34^{+1.83}_{-1.82} & 17.98^{+0.93}_{-1.20} & 18.22^{+1.83}_{-1.82} & 17.86^{+0.93}_{-1.20} & -23.68^{+1.85}_{-1.83} & -24.04^{+0.93}_{-1.21} \\
-    13.2 & 18.25^{+1.86}_{-1.84} & 17.90^{+0.94}_{-1.22} & 18.13^{+1.86}_{-1.84} & 17.77^{+0.94}_{-1.22} & -23.81^{+1.88}_{-1.85} & -24.16^{+0.95}_{-1.23} \\
-    13.3 & 18.17^{+1.89}_{-1.86} & 17.82^{+0.95}_{-1.23} & 18.05^{+1.89}_{-1.86} & 17.69^{+0.95}_{-1.23} & -23.94^{+1.91}_{-1.88} & -24.29^{+0.96}_{-1.24} \\
-    13.4 & 18.08^{+1.91}_{-1.89} & 17.73^{+0.96}_{-1.25} & 17.96^{+1.91}_{-1.89} & 17.61^{+0.96}_{-1.25} & -24.06^{+1.93}_{-1.90} & -24.41^{+0.97}_{-1.26} \\
-    13.5 & 17.99^{+1.94}_{-1.91} & 17.65^{+0.97}_{-1.27} & 17.87^{+1.94}_{-1.91} & 17.53^{+0.97}_{-1.27} & -24.19^{+1.96}_{-1.92} & -24.53^{+0.98}_{-1.28} \\
-    13.6 & 17.91^{+1.97}_{-1.93} & 17.57^{+0.99}_{-1.28} & 17.78^{+1.97}_{-1.93} & 17.45^{+0.99}_{-1.28} & -24.32^{+1.99}_{-1.95} & -24.66^{+1.00}_{-1.29} \\
-    13.7 & 17.82^{+2.00}_{-1.96} & 17.48^{+1.00}_{-1.30} & 17.70^{+2.00}_{-1.96} & 17.36^{+1.00}_{-1.30} & -24.45^{+2.01}_{-1.97} & -24.78^{+1.01}_{-1.31} \\
-    13.8 & 17.73^{+2.02}_{-1.98} & 17.40^{+1.02}_{-1.31} & 17.61^{+2.02}_{-1.98} & 17.28^{+1.02}_{-1.31} & -24.57^{+2.04}_{-2.00} & -24.91^{+1.03}_{-1.32} \\
-    13.9 & 17.65^{+2.05}_{-2.01} & 17.31^{+1.03}_{-1.32} & 17.53^{+2.05}_{-2.01} & 17.19^{+1.03}_{-1.32} & -24.69^{+2.06}_{-2.02} & -25.03^{+1.04}_{-1.33} \\
-    14.0 & 17.57^{+2.07}_{-2.04} & 17.23^{+1.05}_{-1.34} & 17.44^{+2.07}_{-2.04} & 17.11^{+1.05}_{-1.34} & -24.82^{+2.09}_{-2.05} & -25.16^{+1.05}_{-1.35} \\
-    14.1 & 17.48^{+2.09}_{-2.06} & 17.14^{+1.06}_{-1.35} & 17.36^{+2.09}_{-2.06} & 17.02^{+1.06}_{-1.35} & -24.94^{+2.11}_{-2.08} & -25.28^{+1.07}_{-1.36} \\
-    14.2 & 17.40^{+2.12}_{-2.09} & 17.06^{+1.07}_{-1.37} & 17.27^{+2.12}_{-2.09} & 16.94^{+1.07}_{-1.37} & -25.07^{+2.14}_{-2.10} & -25.41^{+1.08}_{-1.38} \\
-    14.3 & 17.31^{+2.14}_{-2.11} & 16.97^{+1.09}_{-1.38} & 17.19^{+2.14}_{-2.11} & 16.85^{+1.09}_{-1.38} & -25.19^{+2.16}_{-2.12} & -25.53^{+1.09}_{-1.39} \\
-    14.4 & 17.23^{+2.17}_{-2.14} & 16.89^{+1.10}_{-1.40} & 17.11^{+2.17}_{-2.14} & 16.76^{+1.10}_{-1.40} & -25.32^{+2.18}_{-2.15} & -25.66^{+1.11}_{-1.40} \\
-    14.5 & 17.14^{+2.19}_{-2.16} & 16.80^{+1.11}_{-1.41} & 17.02^{+2.19}_{-2.16} & 16.68^{+1.11}_{-1.41} & -25.44^{+2.21}_{-2.17} & -25.78^{+1.12}_{-1.42} \\
-    14.6 & 17.05^{+2.22}_{-2.18} & 16.72^{+1.13}_{-1.43} & 16.93^{+2.22}_{-2.18} & 16.59^{+1.13}_{-1.43} & -25.58^{+2.24}_{-2.19} & -25.91^{+1.14}_{-1.43} \\
-    14.7 & 16.97^{+2.25}_{-2.20} & 16.63^{+1.14}_{-1.44} & 16.84^{+2.25}_{-2.20} & 16.51^{+1.14}_{-1.44} & -25.71^{+2.26}_{-2.21} & -26.05^{+1.15}_{-1.45} \\
-    14.8 & 16.88^{+2.28}_{-2.23} & 16.54^{+1.16}_{-1.46} & 16.75^{+2.28}_{-2.23} & 16.42^{+1.16}_{-1.46} & -25.85^{+2.29}_{-2.24} & -26.19^{+1.16}_{-1.46} \\
-    14.9 & 16.79^{+2.31}_{-2.25} & 16.46^{+1.17}_{-1.47} & 16.67^{+2.31}_{-2.25} & 16.33^{+1.17}_{-1.47} & -26.01^{+2.31}_{-2.26} & -26.35^{+1.18}_{-1.47} \\
-    15.0 & 16.70^{+2.33}_{-2.28} & 16.37^{+1.19}_{-1.48} & 16.58^{+2.33}_{-2.28} & 16.25^{+1.19}_{-1.48} & -26.24^{+2.33}_{-2.28} & -26.57^{+1.19}_{-1.48} \\
+    10.1 & 20.76^{+1.12}_{-1.13} & 19.88^{+0.75}_{-1.10} & 20.64^{+1.12}_{-1.13} & 19.76^{+0.75}_{-1.10} & -19.86^{+1.14}_{-1.14} & -20.74^{+0.75}_{-1.11} \\
+    10.2 & 20.68^{+1.15}_{-1.15} & 19.80^{+0.76}_{-1.13} & 20.56^{+1.15}_{-1.15} & 19.67^{+0.76}_{-1.13} & -20.00^{+1.16}_{-1.16} & -20.88^{+0.76}_{-1.14} \\
+    10.3 & 20.60^{+1.18}_{-1.17} & 19.71^{+0.77}_{-1.15} & 20.47^{+1.18}_{-1.17} & 19.58^{+0.77}_{-1.15} & -20.13^{+1.19}_{-1.18} & -21.03^{+0.78}_{-1.16} \\
+    10.4 & 20.52^{+1.20}_{-1.20} & 19.62^{+0.78}_{-1.17} & 20.39^{+1.20}_{-1.20} & 19.49^{+0.78}_{-1.17} & -20.26^{+1.21}_{-1.21} & -21.17^{+0.79}_{-1.18} \\
+    10.5 & 20.43^{+1.22}_{-1.22} & 19.52^{+0.80}_{-1.19} & 20.31^{+1.22}_{-1.22} & 19.40^{+0.80}_{-1.19} & -20.40^{+1.23}_{-1.23} & -21.31^{+0.80}_{-1.20} \\
+    10.6 & 20.36^{+1.24}_{-1.24} & 19.43^{+0.81}_{-1.21} & 20.23^{+1.24}_{-1.24} & 19.31^{+0.81}_{-1.21} & -20.53^{+1.26}_{-1.25} & -21.46^{+0.82}_{-1.22} \\
+    10.7 & 20.27^{+1.27}_{-1.26} & 19.34^{+0.83}_{-1.23} & 20.15^{+1.27}_{-1.26} & 19.22^{+0.83}_{-1.23} & -20.66^{+1.28}_{-1.27} & -21.60^{+0.83}_{-1.24} \\
+    10.8 & 20.19^{+1.30}_{-1.28} & 19.24^{+0.84}_{-1.25} & 20.06^{+1.30}_{-1.28} & 19.12^{+0.84}_{-1.25} & -20.80^{+1.31}_{-1.29} & -21.75^{+0.85}_{-1.26} \\
+    10.9 & 20.10^{+1.33}_{-1.30} & 19.15^{+0.86}_{-1.27} & 19.98^{+1.33}_{-1.30} & 19.02^{+0.86}_{-1.27} & -20.93^{+1.34}_{-1.31} & -21.89^{+0.87}_{-1.28} \\
+    11.0 & 20.01^{+1.36}_{-1.32} & 19.05^{+0.88}_{-1.29} & 19.89^{+1.36}_{-1.32} & 18.93^{+0.88}_{-1.29} & -21.07^{+1.37}_{-1.33} & -22.04^{+0.89}_{-1.31} \\
+    11.1 & 19.93^{+1.39}_{-1.34} & 18.96^{+0.90}_{-1.32} & 19.80^{+1.39}_{-1.34} & 18.84^{+0.90}_{-1.32} & -21.21^{+1.40}_{-1.35} & -22.18^{+0.90}_{-1.33} \\
+    11.2 & 19.84^{+1.41}_{-1.36} & 18.86^{+0.91}_{-1.34} & 19.72^{+1.41}_{-1.36} & 18.74^{+0.91}_{-1.34} & -21.34^{+1.43}_{-1.37} & -22.32^{+0.92}_{-1.35} \\
+    11.3 & 19.75^{+1.44}_{-1.38} & 18.77^{+0.93}_{-1.36} & 19.63^{+1.44}_{-1.38} & 18.65^{+0.93}_{-1.36} & -21.47^{+1.46}_{-1.39} & -22.46^{+0.94}_{-1.37} \\
+    11.4 & 19.67^{+1.47}_{-1.39} & 18.67^{+0.95}_{-1.39} & 19.54^{+1.47}_{-1.39} & 18.55^{+0.95}_{-1.39} & -21.61^{+1.49}_{-1.41} & -22.61^{+0.95}_{-1.40} \\
+    11.5 & 19.58^{+1.50}_{-1.41} & 18.58^{+0.96}_{-1.41} & 19.46^{+1.50}_{-1.41} & 18.46^{+0.96}_{-1.41} & -21.74^{+1.51}_{-1.42} & -22.75^{+0.97}_{-1.42} \\
+    11.6 & 19.49^{+1.52}_{-1.44} & 18.48^{+0.98}_{-1.43} & 19.37^{+1.52}_{-1.44} & 18.36^{+0.98}_{-1.43} & -21.88^{+1.54}_{-1.45} & -22.89^{+0.99}_{-1.44} \\
+    11.7 & 19.41^{+1.55}_{-1.46} & 18.39^{+0.99}_{-1.45} & 19.28^{+1.55}_{-1.46} & 18.27^{+0.99}_{-1.45} & -22.01^{+1.57}_{-1.47} & -23.03^{+1.00}_{-1.46} \\
+    11.8 & 19.32^{+1.58}_{-1.48} & 18.29^{+1.01}_{-1.47} & 19.20^{+1.58}_{-1.48} & 18.17^{+1.01}_{-1.47} & -22.14^{+1.59}_{-1.49} & -23.17^{+1.02}_{-1.48} \\
+    11.9 & 19.23^{+1.60}_{-1.50} & 18.20^{+1.02}_{-1.49} & 19.11^{+1.60}_{-1.50} & 18.08^{+1.02}_{-1.49} & -22.27^{+1.62}_{-1.52} & -23.31^{+1.03}_{-1.50} \\
+    12.0 & 19.15^{+1.63}_{-1.53} & 18.11^{+1.04}_{-1.51} & 19.02^{+1.63}_{-1.53} & 17.98^{+1.04}_{-1.51} & -22.40^{+1.65}_{-1.54} & -23.45^{+1.05}_{-1.52} \\
+    12.1 & 19.06^{+1.66}_{-1.55} & 18.01^{+1.05}_{-1.53} & 18.94^{+1.66}_{-1.55} & 17.89^{+1.05}_{-1.53} & -22.54^{+1.67}_{-1.56} & -23.59^{+1.06}_{-1.55} \\
+    12.2 & 18.97^{+1.68}_{-1.57} & 17.92^{+1.07}_{-1.56} & 18.85^{+1.68}_{-1.57} & 17.79^{+1.07}_{-1.56} & -22.67^{+1.70}_{-1.59} & -23.73^{+1.08}_{-1.57} \\
+    12.3 & 18.89^{+1.71}_{-1.60} & 17.82^{+1.08}_{-1.58} & 18.76^{+1.71}_{-1.60} & 17.70^{+1.08}_{-1.58} & -22.80^{+1.73}_{-1.61} & -23.87^{+1.09}_{-1.60} \\
+    12.4 & 18.80^{+1.74}_{-1.62} & 17.73^{+1.10}_{-1.61} & 18.68^{+1.74}_{-1.62} & 17.61^{+1.10}_{-1.61} & -22.93^{+1.76}_{-1.63} & -24.00^{+1.11}_{-1.63} \\
+    12.5 & 18.71^{+1.76}_{-1.64} & 17.63^{+1.11}_{-1.64} & 18.59^{+1.76}_{-1.64} & 17.51^{+1.11}_{-1.64} & -23.06^{+1.79}_{-1.65} & -24.14^{+1.12}_{-1.66} \\
+    12.6 & 18.62^{+1.80}_{-1.65} & 17.54^{+1.13}_{-1.67} & 18.49^{+1.80}_{-1.65} & 17.41^{+1.13}_{-1.67} & -23.20^{+1.82}_{-1.66} & -24.28^{+1.14}_{-1.68} \\
+    12.7 & 18.52^{+1.83}_{-1.66} & 17.44^{+1.15}_{-1.69} & 18.40^{+1.83}_{-1.66} & 17.32^{+1.15}_{-1.69} & -23.34^{+1.85}_{-1.67} & -24.42^{+1.15}_{-1.71} \\
+    12.8 & 18.43^{+1.87}_{-1.68} & 17.34^{+1.16}_{-1.72} & 18.31^{+1.87}_{-1.68} & 17.22^{+1.16}_{-1.72} & -23.47^{+1.88}_{-1.69} & -24.56^{+1.17}_{-1.74} \\
+    12.9 & 18.34^{+1.89}_{-1.70} & 17.24^{+1.18}_{-1.75} & 18.22^{+1.89}_{-1.70} & 17.12^{+1.18}_{-1.75} & -23.60^{+1.91}_{-1.71} & -24.70^{+1.19}_{-1.77} \\
+    13.0 & 18.25^{+1.92}_{-1.72} & 17.15^{+1.19}_{-1.78} & 18.13^{+1.92}_{-1.72} & 17.02^{+1.19}_{-1.78} & -23.73^{+1.94}_{-1.73} & -24.84^{+1.20}_{-1.80} \\
+    13.1 & 18.17^{+1.94}_{-1.74} & 17.05^{+1.21}_{-1.81} & 18.04^{+1.94}_{-1.74} & 16.93^{+1.21}_{-1.81} & -23.86^{+1.96}_{-1.75} & -24.98^{+1.22}_{-1.82} \\
+    13.2 & 18.08^{+1.97}_{-1.76} & 16.95^{+1.23}_{-1.84} & 17.96^{+1.97}_{-1.76} & 16.83^{+1.23}_{-1.84} & -23.99^{+1.99}_{-1.77} & -25.12^{+1.24}_{-1.85} \\
+    13.3 & 17.99^{+2.00}_{-1.78} & 16.85^{+1.24}_{-1.87} & 17.86^{+2.00}_{-1.78} & 16.73^{+1.24}_{-1.87} & -24.12^{+2.02}_{-1.79} & -25.26^{+1.25}_{-1.88} \\
+    13.4 & 17.89^{+2.03}_{-1.80} & 16.75^{+1.26}_{-1.89} & 17.77^{+2.03}_{-1.80} & 16.63^{+1.26}_{-1.89} & -24.25^{+2.05}_{-1.81} & -25.40^{+1.27}_{-1.90} \\
+    13.5 & 17.80^{+2.06}_{-1.82} & 16.66^{+1.28}_{-1.91} & 17.68^{+2.06}_{-1.82} & 16.53^{+1.28}_{-1.91} & -24.38^{+2.08}_{-1.83} & -25.54^{+1.29}_{-1.93} \\
+    13.6 & 17.71^{+2.09}_{-1.84} & 16.56^{+1.29}_{-1.94} & 17.59^{+2.09}_{-1.84} & 16.44^{+1.29}_{-1.94} & -24.51^{+2.11}_{-1.86} & -25.68^{+1.31}_{-1.95} \\
+    13.7 & 17.63^{+2.11}_{-1.87} & 16.46^{+1.31}_{-1.96} & 17.50^{+2.11}_{-1.87} & 16.34^{+1.31}_{-1.96} & -24.64^{+2.13}_{-1.88} & -25.81^{+1.32}_{-1.97} \\
+    13.8 & 17.54^{+2.14}_{-1.89} & 16.36^{+1.33}_{-1.98} & 17.42^{+2.14}_{-1.89} & 16.24^{+1.33}_{-1.98} & -24.77^{+2.16}_{-1.91} & -25.95^{+1.34}_{-1.99} \\
+    13.9 & 17.45^{+2.16}_{-1.92} & 16.26^{+1.35}_{-2.00} & 17.33^{+2.16}_{-1.92} & 16.14^{+1.35}_{-2.00} & -24.89^{+2.18}_{-1.94} & -26.09^{+1.36}_{-2.02} \\
+    14.0 & 17.37^{+2.19}_{-1.95} & 16.16^{+1.37}_{-2.03} & 17.24^{+2.19}_{-1.95} & 16.04^{+1.37}_{-2.03} & -25.02^{+2.20}_{-1.96} & -26.23^{+1.38}_{-2.04} \\
+    14.1 & 17.29^{+2.21}_{-1.98} & 16.06^{+1.39}_{-2.05} & 17.16^{+2.21}_{-1.98} & 15.94^{+1.39}_{-2.05} & -25.14^{+2.22}_{-2.00} & -26.37^{+1.40}_{-2.06} \\
+    14.2 & 17.21^{+2.22}_{-2.01} & 15.96^{+1.40}_{-2.07} & 17.08^{+2.22}_{-2.01} & 15.84^{+1.40}_{-2.07} & -25.26^{+2.24}_{-2.03} & -26.51^{+1.42}_{-2.09} \\
+    14.3 & 17.12^{+2.24}_{-2.04} & 15.86^{+1.42}_{-2.10} & 17.00^{+2.24}_{-2.04} & 15.74^{+1.42}_{-2.10} & -25.38^{+2.26}_{-2.05} & -26.65^{+1.43}_{-2.11} \\
+    14.4 & 17.04^{+2.27}_{-2.07} & 15.76^{+1.44}_{-2.13} & 16.91^{+2.27}_{-2.07} & 15.64^{+1.44}_{-2.13} & -25.51^{+2.28}_{-2.08} & -26.79^{+1.45}_{-2.14} \\
+    14.5 & 16.95^{+2.29}_{-2.09} & 15.66^{+1.46}_{-2.16} & 16.83^{+2.29}_{-2.09} & 15.54^{+1.46}_{-2.16} & -25.64^{+2.31}_{-2.11} & -26.93^{+1.47}_{-2.17} \\
+    14.6 & 16.87^{+2.32}_{-2.12} & 15.56^{+1.48}_{-2.18} & 16.74^{+2.32}_{-2.12} & 15.44^{+1.48}_{-2.18} & -25.77^{+2.33}_{-2.13} & -27.07^{+1.49}_{-2.19} \\
+    14.7 & 16.78^{+2.35}_{-2.14} & 15.46^{+1.50}_{-2.21} & 16.65^{+2.35}_{-2.14} & 15.34^{+1.50}_{-2.21} & -25.90^{+2.36}_{-2.15} & -27.22^{+1.50}_{-2.22} \\
+    14.8 & 16.68^{+2.38}_{-2.16} & 15.36^{+1.51}_{-2.23} & 16.56^{+2.38}_{-2.16} & 15.24^{+1.51}_{-2.23} & -26.05^{+2.39}_{-2.17} & -27.37^{+1.52}_{-2.24} \\
+    14.9 & 16.59^{+2.41}_{-2.18} & 15.26^{+1.53}_{-2.26} & 16.47^{+2.41}_{-2.18} & 15.14^{+1.53}_{-2.26} & -26.21^{+2.42}_{-2.19} & -27.54^{+1.53}_{-2.26} \\
+    15.0 & 16.50^{+2.45}_{-2.20} & 15.16^{+1.55}_{-2.29} & 16.37^{+2.45}_{-2.20} & 15.04^{+1.55}_{-2.29} & -26.44^{+2.45}_{-2.20} & -27.78^{+1.55}_{-2.29} \\
     \hline

### 2019-02-25 Paper/paper.tex
Update

@@
 $\nu_\mathrm{em}=\nu\left(1+z^\prime\right)/\left(1+z\right)>\nu_{912}$.
-In practice, we adopt an upper limit $z^\prime_\mathrm{max}=15$ when
-integrating Equation~\eqref{eqn:flux}.  Assuming that quasars are the
-only ionizing sources and considering Equation~\eqref{eqn:sed} we have
+In practice, we adopt an upper limit $z^\prime_\mathrm{max}=7$ when
+integrating Equation~\eqref{eqn:flux}.  \new{Due to the short mean
+  free path at high redshifts $z^\prime_\mathrm{max}=7$ is sufficient
+  to give converged result.  We do not require severe extrapolation of
+  our emissivity models to high redshifts.} Assuming that quasars are
+the only ionizing sources and considering Equation~\eqref{eqn:sed} we
+have
 \begin{equation}

### 2019-02-27 croom.py
Update style

@@ -188,133 +188,133 @@ def croom(i, ax, zrange, yticklabels=False, xticklabels=False, nofirstylabel=Tru
         # Convert from M1450 to Mg(z=2) by using Equation B8 of Ross
         # et al. 2013.
         mags = mags - 1.23
-        ax.scatter(mags, logphi, c='b', edgecolor='None',
-                   zorder=2, label='Our binning (SDSS)', s=35)
-        ax.errorbar(mags, logphi, ecolor='b', capsize=0,
-                    yerr=np.vstack((uperr, downerr)),
-                    fmt='None',zorder=2)
-
+        # ax.scatter(mags, logphi, c='b', edgecolor='None',
+        #            zorder=2, label='Our binning (SDSS)', s=35)
+        # ax.errorbar(mags, logphi, ecolor='b', capsize=0,
+        #             yerr=np.vstack((uperr, downerr)),
+        #             fmt='None',zorder=2)
+        # 
     print 'i=', i
 
-    if i == 1:
-        mags = np.linspace(-16, -31)
-        p = [-6.426, -23.499, -3.382, -1.577]
-        plt.plot(mags-1.23, log10phi(p, mags), c='peru', lw=2, dashes=[7,2])
+    # if i == 1:
+    #     mags = np.linspace(-16, -31)
+    #     p = [-6.426, -23.499, -3.382, -1.577]
+    #     plt.plot(mags-1.23, log10phi(p, mags), c='peru', lw=2, dashes=[7,2])
 
-        p = [-6.341, -23.398, -3.429, -1.430]
-        plt.plot(mags-1.23, log10phi(p, mags), c='k', lw=2)
+    #     p = [-6.341, -23.398, -3.429, -1.430]
+    #     plt.plot(mags-1.23, log10phi(p, mags), c='k', lw=2)
 
-        p = [-6.467, -23.569, -3.427, -1.610]
-        plt.plot(mags-1.23, log10phi(p, mags), c='m', lw=2)
+    #     p = [-6.467, -23.569, -3.427, -1.610]
+    #     plt.plot(mags-1.23, log10phi(p, mags), c='m', lw=2)
 
-        p = [-5.944, -24.059, -3.028, -1.490]
-        plt.plot(mags, log10phi(p, mags), c='r', lw=2)
[…]

### 2019-02-27 rtg2.py
Vary zmax

@@ -12,6 +12,7 @@ import sys
 import gammapi
 from gammapi import get_gammapi_percentiles
 import matplotlib.patches as mpatches
+import matplotlib.ticker as ticker
 
 # These npz files generated by rhoqso_fit2.py.
 data = np.load('e1450_18_21feb.npz')
@@ -29,8 +30,6 @@ up21 = data['up']
 down21 = data['down']
 
 print 'median21=', median21[:10]
-
-
 
 # z18 = data['z']
 # medianbright18 = data['medianbright']
@@ -482,13 +481,16 @@ def j(emodel, loglf=None, theta=None, dz=0.1, n_ws=200, n_ws_int=100, zmax=7.0):
     ws = np.logspace(0.0, 5.0, num=n_ws)
     nu = c_angPerSec/ws 
 
-    j = np.zeros_like(nu)
-    
+    je = np.zeros_like(nu)
+
     zmin = 0.0
     n = (zmax-zmin)/dz+1
     zs = np.linspace(zmax, zmin, num=n)
     gs = []
 
+    print 'zmax=', zmax
+    print 'zmin=', zmin 
+    
     for z in zs:
 
         if loglf is not None:
@@ -496,14 +498,14 @@ def j(emodel, loglf=None, theta=None, dz=0.1, n_ws=200, n_ws_int=100, zmax=7.0):
         else:
             e = emodel(ws/(1.0+z), z)
         
-        # [j] = erg s^-1 Hz^-1 cm^-2 sr^-1
-        j = j + (e*c_mpcPerYr*np.abs(dtdz(z))*dz*cmbympc**2)/(4.0*np.pi) 
+        # [je] = erg s^-1 Hz^-1 cm^-2 sr^-1
+        je = je + (e*c_mpcPerYr*np.abs(dtdz(z))*dz*cmbympc**2)/(4.0*np.pi) 
 
         nu_rest = c_angPerSec*(1.0+z)/ws 
         t = np.array([tau_eff(x, z) for x in nu_rest])
-        j = j*np.exp(-t*dz)
+        je = je*np.exp(-t*dz)
 
-        n = 4.0*np.pi*j*(1.0+z)**3/(hplanck*nu_rest)
+        n = 4.0*np.pi*je*(1.0+z)**3/(hplanck*nu_rest)
 
         nu_int = np.logspace(np.log10(nu0), 18, num=n_ws_int)
         n_int = np.interp(nu_int, nu_rest[::-1], n[::-1])
[…]

### 2019-02-27 gammapi.py
Add legend

@@ -689,7 +689,7 @@ def bongiorno07(ax, only18=False, only21=False, style=False):
     return
     
         
-def draw_emissivity(all_individuals, zlims, composite=None, select=False):
+def draw_emissivity(all_individuals, composite=None, select=False):
 
     """
     Calculates and plots LyC emissivity.
@@ -1107,7 +1107,7 @@ def draw_emissivity_18(all_individuals, composite=None, select=False):
                 mfc='#ffffff', mec='#404040', zorder=6, mew=1,
                 ms=5)
     ax.scatter(zs, em, c='k', edgecolor='None',
-               label='Kulkarni et al.\ 2018 (this work)',
+               label='Kulkarni et al.\ 2019 (this work)',
                s=36, zorder=6, linewidths=1.5) 
 
     # npz produced using rhoqso_fit.get_fit_mcmc(). 
@@ -1199,7 +1199,7 @@ def draw_emissivity_18(all_individuals, composite=None, select=False):
 
     handles, labels = ax.get_legend_handles_labels()
     handles.append((tw18f,tw18))
-    labels.append('Kulkarni et al.\ 2018 (this work; fit)')
+    labels.append('Kulkarni et al.\ 2019 (this work; fit)')
 
     print len(handles)
     for i, x in enumerate(labels):
@@ -1449,7 +1449,7 @@ def draw_emissivity_21(all_individuals, composite=None, select=False):
                 mfc='#ffffff', mec='#404040', zorder=6, mew=1,
                 ms=5)
     ax.scatter(zs, em, c='k', edgecolor='None',
-               label='Kulkarni et al.\ 2018 (this work)',
+               label='Kulkarni et al.\ 2019 (this work)',
                s=42, zorder=6, linewidths=1.5) 
 
     # npz produced using rhoqso_fit.get_fit_mcmc().
@@ -1558,7 +1558,7 @@ def draw_emissivity_21(all_individuals, composite=None, select=False):
     
     handles, labels = ax.get_legend_handles_labels()
     handles.append((tw18f,tw18))
-    labels.append('Kulkarni et al.\ 2018 (this work; fit)')
+    labels.append('Kulkarni et al.\ 2019 (this work; fit)')
 
     # myorder = [10, 14, 9, 12, 11, 13, 7, 0, 1, 2, 3, 4, 5, 6, 8, 15]
     myorder = [9, 13, 8, 11, 10, 12, 6, 0, 1, 2, 3, 4, 5, 7, 14]

### 2019-04-25 Paper/paper.tex
Update
Resubmitted version

@@
 \begin{align}
-  &\phi_*(z) = F_0(\{c_{0,j}\}, z)\nonumber\\
+  &\log_{10}\phi_*(z) = F_0(\{c_{0,j}\}, z)\nonumber\\
   &M_*(z) = F_1(\{c_{1,j}\}, z)\nonumber\\
@@
   \begin{center}
-    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+    % \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
+    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_test2.pdf}
     % rhoqso.py -- draw_withGlobal_multiple()
   \end{center}
-  \caption{AGN number density evolution in the global model, when the
-    luminosity function is integrated (from top to bottom) down to
-    $M_\mathrm{1450}=-18, -21, -24,$ and $-27$.  Filled black circles
-    show the estimates from the our fiducual double power law
-    luminosity function models in various redshift bins, with vertical
-    error bars denoting one-sigma (68.26\%) uncertainties.  Open
-    circles show the same in redshifts bins affected by systematics.
-    Curves show the estimated density from the global models, with the
-    accompanying shaded regions denoting the one-sigma uncertainty. }
+  \caption{\new{AGN number density evolution in the global model, when
+      the luminosity function is integrated (from top to bottom) down
+      to $M_\mathrm{1450}=-21, -24, -25.5$ and $-27$.  Points show the
+      observed number density evolution, with vertical error bars
+      denoting one-sigma (68.26\%) uncertainties.}  Curves show the
+    estimated density from the global models, with the accompanying
+    shaded regions denoting the one-sigma uncertainty. }
   \label{fig:rhoqso}
@@
 Figure~\ref{fig:rhoqso} when the luminosity function is integrated
-down to different limits.  Similar to Figure~\ref{fig:evoln_global},
-symbols show the posterior median values with one-sigma uncertainties
-from the double power law fits to the data in redshift bins.  Solid
-curves and shaded regions show the global models.  This number density
-evolution again highlights the systematic error in data at $z\sim 3$.
-The number density of AGN down to the limit of the deepest
-spectroscopic surveys ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$
-at its peak.  This density rapidly increases with redshift at low
+down to different limits.  \new{Symbols show the number densities
+  derived from the data.}  Solid curves and shaded regions show the
+global models.  This number density evolution again highlights the
+systematic error in data at $z\sim 3$.  \new{The number density of AGN
+  down to the limit of the deepest spectroscopic surveys
+  ($M_{1450}<-21$) is about few times $10^{-6}$ cMpc$^{-3}$ at its
+  peak.  At higher redshifts, data go down to only about
+  $M_{1450}=-24$.} This density rapidly increases with redshift at low
 redshifts and then drops with redshift gradually at high redshifts.
@@
 $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
-$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
-spectroscopic data exist, $M_*<-21$, the number density of AGN peaks
-at a slightly lower redshift.  However, the difference between our
+$M_*<-24$ peaks at $z\sim 2$.  However, the difference between our
 three models is dramatically evident in Figure~\ref{fig:rhoqso}.
@@
 models in the literature \citep{2007ApJ...654..731H}.
-Figure~\ref{fig:rhoqso} also shows that although Models 2 and 3
-exhibit regular behaviour in the evolution of the AGN number density
-at $z\sim 3$, they do not fit the $z\sim 4$--$5$ data as well as Model
-1.
 
@@
     details and the redshift range of validity of these models.
-    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
-    preferred model.}
+    Errors indicate one-sigma (68.26\%) uncertainties. }
   \label{tab:global}
@@
     \hline 
-    $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
-    $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
-    $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
+    $c_{0,0}$&-7.798^{+0.145}_{-0.157} &   -7.432^{+0.192}_{-0.211} &   -6.942^{+0.086}_{-0.086} \\
+    $c_{0,1}$&1.128^{+0.085}_{-0.081} &    0.953^{+0.122}_{-0.107} &    0.629^{+0.046}_{-0.045} \\
+    $c_{0,2}$&-0.120^{+0.005}_{-0.006} &   -0.112^{+0.007}_{-0.008} &   -0.086^{+0.003}_{-0.003} \\ 
     \\      
-    $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
-    $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
-    $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
-    $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
+    $c_{1,0}$&-17.163^{+0.219}_{-0.226} &  -15.412^{+0.288}_{-0.318} &  -15.038^{+0.156}_{-0.150} \\
+    $c_{1,1}$&-5.512^{+0.127}_{-0.124} &   -6.869^{+0.183}_{-0.169} &   -7.046^{+0.100}_{-0.101} \\
+    $c_{1,2}$&0.593^{+0.011}_{-0.010} &    0.778^{+0.016}_{-0.015} &    0.772^{+0.013}_{-0.013} \\
+    $c_{1,3}$&-0.024^{+0.00035}_{-0.00039} &   -0.032^{+0.001}_{-0.001} &   -0.030^{+0.001}_{-0.001} \\ 
     \\       
-    $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
-    $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
+    $c_{2,0}$&-3.223^{+0.127}_{-0.121} &   -2.959^{+0.127}_{-0.143} &   -2.888^{+0.097}_{-0.093} \\
+    $c_{2,1}$&-0.258^{+0.047}_{-0.051} &   -0.351^{+0.054}_{-0.052} &   -0.383^{+0.039}_{-0.041} \\
     \\       
-    $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
-    $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
-    $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
-    $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
-    $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
+    $c_{3,0}$&-2.312^{+0.034}_{-0.032} &   -2.264^{+0.038}_{-0.036} &   -1.602^{+0.029}_{-0.028} \\
+    $c_{3,1}$&0.559^{+0.049}_{-0.045} &    0.530^{+0.054}_{-0.049} &    -0.082^{+0.009}_{-0.009} \\
+    $c_{3,2}$&3.773^{+0.017}_{-0.016} &    2.379^{+0.118}_{-0.085} &  \multicolumn{1}{c}{---} \\        
+    $c_{3,3}$&141.884^{+31.521}_{-8.832} & 12.527^{+7.349}_{-3.618} & \multicolumn{1}{c}{---} \\        
+    $c_{3,4}$&-0.171^{+0.101}_{-0.116} &   -0.229^{+0.135}_{-0.150} & \multicolumn{1}{c}{---} \\
     \hline
@@
 \begin{multline}
-  \epsilon_{1450}\left(z\right)=\left(10^{24.62}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.79}\\\times\frac{\exp(-1.23z)}{\exp(1.30z)+25.54}\quad,
+  \epsilon_{1450}\left(z\right)=\left(10^{24.72}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{8.42}\\\times\frac{\exp(-2.1z)}{\exp(1.09z)+38.56}\quad,
   \label{eqn:e912_18}
@@
  \begin{multline}
-  \epsilon_{1450}\left(z\right)=\left(10^{24.37}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{6.11}\\\times\frac{\exp(-0.4z)}{\exp(1.98z)+25.42}\quad,
+  \epsilon_{1450}\left(z\right)=\left(10^{23.91}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}\right)\left(1+z\right)^{8.26}\\\times\frac{\exp(-1.3z)}{\exp(1.62z)+13.6}\quad,
   \label{eqn:e912_21}
@@
 Ba\~nados, Manda Banerji, Tirthankar Roy Choudhury, George Efstathiou,
-Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Francesco Haardt, Martin
-Haehnelt, Paul Hewett, David Hogg, Vikram Khaire, Sergey Koposov, Alex
-Krolewski, Donald Lynden-Bell, Roberto Maiolino, Richard McMahon,
-Daniel Mortlock, Ewald Puchwein, Gordon Richards, Alberto Rorai, Bram
-Venemans and Stephen Warren.  \new{We thank the anonymous referee for
-  their comments.} GK acknowledges support from ERC Advanced Grant
-320596 `The Emergence of Structure During the Epoch of Reionization'.
+Xiaohui Fan, Andrea Ferrara, Prakash Gaikwad, Enrico Garaldi,
+Francesco Haardt, Martin Haehnelt, Paul Hewett, David Hogg, Vikram
+Khaire, Sergey Koposov, Alex Krolewski, Donald Lynden-Bell, Roberto
+Maiolino, Richard McMahon, Daniel Mortlock, Ewald Puchwein, Gordon
+Richards, Alberto Rorai, Bram Venemans and Stephen Warren.  \new{We
+  thank the anonymous referee for their comments.} GK acknowledges
+support from ERC Advanced Grant 320596 `The Emergence of Structure
+During the Epoch of Reionization'.
 
@@
     % summary_grand.py
-    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
+    \includegraphics[width=\textwidth]{evolution_grand.pdf}
   \end{center}
@@
     \hline
-    0.31$^a$ & 0.10 & 0.40 & 0.53^{+0.02}_{-0.02} & 0.70^{+0.03}_{-0.02} & 0.30^{+0.01}_{-0.01} & 0.40^{+0.01}_{-0.01} \\
-    0.50$^a$ & 0.40 & 0.60 & 0.75^{+0.01}_{-0.01} & 1.00^{+0.01}_{-0.01} & 0.59^{+0.01}_{-0.01} & 0.78^{+0.01}_{-0.01} \\
-    0.72 & 0.60 & 0.80 & 1.73^{+0.05}_{-0.05} & 2.30^{+0.07}_{-0.07} & 1.19^{+0.02}_{-0.02} & 1.57^{+0.02}_{-0.03} \\
-    0.91 & 0.80 & 1.00 & 2.84^{+0.15}_{-0.15} & 3.77^{+0.20}_{-0.20} & 2.10^{+0.05}_{-0.05} & 2.78^{+0.06}_{-0.06} \\
-    1.10 & 1.00 & 1.20 & 3.73^{+0.11}_{-0.10} & 4.94^{+0.15}_{-0.14} & 2.91^{+0.05}_{-0.04} & 3.86^{+0.06}_{-0.05} \\
-    1.30 & 1.20 & 1.40 & 5.72^{+0.25}_{-0.23} & 7.59^{+0.33}_{-0.31} & 4.46^{+0.10}_{-0.09} & 5.92^{+0.13}_{-0.12} \\
-    1.50 & 1.40 & 1.60 & 7.05^{+0.22}_{-0.22} & 9.35^{+0.29}_{-0.29} & 5.60^{+0.09}_{-0.10} & 7.43^{+0.12}_{-0.13} \\
-    1.71 & 1.60 & 1.80 & 7.71^{+0.19}_{-0.18} & 10.23^{+0.25}_{-0.24} & 6.70^{+0.10}_{-0.11} & 8.89^{+0.13}_{-0.15} \\
-    1.98 & 1.80 & 2.20 & 10.64^{+0.35}_{-0.33} & 14.11^{+0.47}_{-0.44} & 7.93^{+0.14}_{-0.16} & 10.52^{+0.19}_{-0.21} \\
-    2.30$^a$ & 2.20 & 2.40 & 10.20^{+0.24}_{-0.24} & 13.54^{+0.32}_{-0.32} & 8.91^{+0.13}_{-0.12} & 11.82^{+0.17}_{-0.16} \\
-    2.45$^a$ & 2.40 & 2.50 & 8.04^{+0.26}_{-0.22} & 10.66^{+0.34}_{-0.29} & 7.17^{+0.14}_{-0.15} & 9.51^{+0.18}_{-0.20} \\
-    2.55$^a$ & 2.50 & 2.60 & 6.63^{+0.19}_{-0.19} & 8.80^{+0.25}_{-0.25} & 6.21^{+0.12}_{-0.12} & 8.24^{+0.16}_{-0.16} \\
-    2.65$^a$ & 2.60 & 2.70 & 6.59^{+0.16}_{-0.16} & 8.74^{+0.21}_{-0.21} & 6.47^{+0.17}_{-0.15} & 8.59^{+0.22}_{-0.20} \\
-    2.75$^a$ & 2.70 & 2.80 & 7.46^{+0.20}_{-0.21} & 9.90^{+0.27}_{-0.28} & 7.20^{+0.19}_{-0.20} & 9.55^{+0.26}_{-0.27} \\
-    2.85$^a$ & 2.80 & 2.90 & 7.96^{+0.32}_{-0.33} & 10.56^{+0.43}_{-0.43} & 7.53^{+0.31}_{-0.32} & 9.99^{+0.41}_{-0.42} \\
-    2.95$^a$ & 2.90 & 3.00 & 7.93^{+0.41}_{-0.40} & 10.52^{+0.55}_{-0.53} & 6.84^{+0.20}_{-0.22} & 9.08^{+0.26}_{-0.29} \\
-    3.05$^a$ & 3.00 & 3.10 & 7.22^{+0.41}_{-0.38} & 9.58^{+0.55}_{-0.51} & 6.27^{+0.23}_{-0.22} & 8.32^{+0.31}_{-0.29} \\
-    3.15$^a$ & 3.10 & 3.20 & 9.93^{+1.12}_{-1.09} & 13.18^{+1.48}_{-1.45} & 7.03^{+0.35}_{-0.36} & 9.33^{+0.46}_{-0.48} \\
-    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.84}_{-0.96} & 11.08^{+1.12}_{-1.28} & 6.17^{+0.38}_{-0.43} & 8.19^{+0.50}_{-0.57} \\
-    3.34$^a$ & 3.30 & 3.40 & 12.23^{+2.63}_{-2.80} & 16.22^{+3.49}_{-3.71} & 7.32^{+0.67}_{-0.82} & 9.71^{+0.89}_{-1.09} \\
-    3.44$^a$ & 3.40 & 3.50 & 4.47^{+0.50}_{-0.59} & 5.93^{+0.66}_{-0.79} & 4.43^{+0.40}_{-0.53} & 5.87^{+0.53}_{-0.70} \\
-    3.88 & 3.70 & 4.10 & 4.23^{+1.33}_{-1.37} & 5.61^{+1.77}_{-1.81} & 2.52^{+0.47}_{-0.46} & 3.34^{+0.63}_{-0.61} \\
-    4.35 & 4.10 & 4.70 & 4.27^{+1.90}_{-2.17} & 5.67^{+2.52}_{-2.88} & 1.78^{+0.48}_{-0.51} & 2.36^{+0.64}_{-0.68} \\
-    4.92 & 4.70 & 5.50 & 2.58^{+0.88}_{-1.00} & 3.42^{+1.17}_{-1.33} & 0.97^{+0.19}_{-0.18} & 1.29^{+0.26}_{-0.24} \\
-    6.00 & 5.50 & 6.50 & 0.66^{+0.24}_{-0.27} & 0.87^{+0.32}_{-0.35} & 0.21^{+0.05}_{-0.04} & 0.27^{+0.06}_{-0.06} \\
+    0.31$^a$ & 0.10 & 0.40 & 0.41^{+0.01}_{-0.01} & 0.55^{+0.02}_{-0.02} & 0.27^{+0.01}_{-0.01} & 0.36^{+0.02}_{-0.01} \\
+    0.50$^a$ & 0.40 & 0.60 & 0.72^{+0.01}_{-0.01} & 0.96^{+0.02}_{-0.02} & 0.53^{+0.01}_{-0.01} & 0.70^{+0.01}_{-0.01} \\
+    0.72 & 0.60 & 0.80 & 2.03^{+0.08}_{-0.08} & 2.69^{+0.13}_{-0.11} & 1.22^{+0.02}_{-0.02} & 1.61^{+0.03}_{-0.03} \\
+    0.91 & 0.80 & 1.00 & 3.64^{+0.23}_{-0.23} & 4.87^{+0.35}_{-0.37} & 2.33^{+0.06}_{-0.06} & 3.09^{+0.08}_{-0.08} \\
+    1.10 & 1.00 & 1.20 & 4.47^{+0.16}_{-0.15} & 5.92^{+0.19}_{-0.19} & 3.18^{+0.05}_{-0.05} & 4.22^{+0.07}_{-0.07} \\
+    1.30 & 1.20 & 1.40 & 7.33^{+0.38}_{-0.39} & 9.74^{+0.53}_{-0.53} & 5.10^{+0.12}_{-0.13} & 6.79^{+0.17}_{-0.18} \\
+    1.50 & 1.40 & 1.60 & 8.84^{+0.35}_{-0.33} & 11.72^{+0.45}_{-0.48} & 6.32^{+0.13}_{-0.14} & 8.41^{+0.17}_{-0.17} \\
+    1.71 & 1.60 & 1.80 & 9.05^{+0.26}_{-0.27} & 12.01^{+0.33}_{-0.32} & 7.51^{+0.13}_{-0.14} & 9.96^{+0.15}_{-0.15} \\
+    1.98 & 1.80 & 2.20 & 14.27^{+0.53}_{-0.58} & 18.92^{+0.85}_{-0.79} & 9.40^{+0.19}_{-0.19} & 12.47^{+0.25}_{-0.24} \\
+    2.30$^a$ & 2.20 & 2.40 & 10.20^{+0.25}_{-0.24} & 13.54^{+0.31}_{-0.31} & 8.88^{+0.11}_{-0.12} & 11.78^{+0.15}_{-0.17} \\
+    2.45$^a$ & 2.40 & 2.50 & 8.05^{+0.23}_{-0.25} & 10.69^{+0.30}_{-0.30} & 7.16^{+0.14}_{-0.14} & 9.48^{+0.21}_{-0.19} \\
+    2.55$^a$ & 2.50 & 2.60 & 6.60^{+0.20}_{-0.19} & 8.80^{+0.30}_{-0.28} & 6.22^{+0.13}_{-0.12} & 8.23^{+0.16}_{-0.16} \\
+    2.65$^a$ & 2.60 & 2.70 & 6.56^{+0.16}_{-0.15} & 8.70^{+0.20}_{-0.21} & 6.44^{+0.16}_{-0.17} & 8.53^{+0.18}_{-0.22} \\
+    2.75$^a$ & 2.70 & 2.80 & 7.47^{+0.22}_{-0.20} & 9.90^{+0.29}_{-0.26} & 7.19^{+0.18}_{-0.18} & 9.50^{+0.26}_{-0.26} \\
+    2.85$^a$ & 2.80 & 2.90 & 7.90^{+0.30}_{-0.32} & 10.50^{+0.44}_{-0.43} & 7.50^{+0.28}_{-0.28} & 9.96^{+0.40}_{-0.38} \\
+    2.95$^a$ & 2.90 & 3.00 & 7.96^{+0.37}_{-0.39} & 10.55^{+0.46}_{-0.47} & 6.85^{+0.20}_{-0.19} & 9.07^{+0.26}_{-0.25} \\
+    3.05$^a$ & 3.00 & 3.10 & 7.25^{+0.42}_{-0.44} & 9.58^{+0.51}_{-0.56} & 6.22^{+0.20}_{-0.21} & 8.26^{+0.30}_{-0.29} \\
+    3.15$^a$ & 3.10 & 3.20 & 9.91^{+1.14}_{-1.11} & 13.20^{+1.41}_{-1.32} & 6.99^{+0.35}_{-0.35} & 9.29^{+0.42}_{-0.42} \\
+    3.25$^a$ & 3.20 & 3.30 & 8.35^{+0.88}_{-0.92} & 11.07^{+1.15}_{-1.26} & 6.10^{+0.36}_{-0.38} & 8.10^{+0.48}_{-0.53} \\
+    3.34$^a$ & 3.30 & 3.40 & 12.19^{+2.77}_{-2.67} & 15.99^{+3.04}_{-3.34} & 7.30^{+0.79}_{-0.74} & 9.74^{+1.01}_{-1.10} \\
+    3.44$^a$ & 3.40 & 3.50 & 4.40^{+0.51}_{-0.51} & 5.81^{+0.70}_{-0.64} & 4.28^{+0.45}_{-0.45} & 5.73^{+0.54}_{-0.61} \\
+    3.88 & 3.70 & 4.10 & 4.43^{+1.37}_{-1.50} & 5.90^{+1.69}_{-1.95} & 2.53^{+0.45}_{-0.49} & 3.34^{+0.65}_{-0.65} \\
+    4.35 & 4.10 & 4.70 & 4.17^{+2.21}_{-2.11} & 6.06^{+3.08}_{-3.01} & 1.77^{+0.43}_{-0.46} & 2.35^{+0.69}_{-0.71} \\
+    4.92 & 4.70 & 5.50 & 2.69^{+0.93}_{-1.07} & 3.38^{+1.34}_{-1.20} & 0.97^{+0.17}_{-0.16} & 1.29^{+0.29}_{-0.26} \\
+    6.00 & 5.50 & 6.50 & 0.66^{+0.26}_{-0.25} & 0.91^{+0.29}_{-0.31} & 0.21^{+0.05}_{-0.05} & 0.27^{+0.05}_{-0.05} \\
     \hline

### 2019-04-26 rhoqso.py
update

@@ -601,7 +601,7 @@ def draw_withGlobal(composite, individuals, zlims, select=False):
 
     return
 
-def draw_withGlobal_multiple(c1, c2, c3, individuals, zlims, select=False):
+def draw_withGlobal_multiple(c1, c2, c3, individuals, select=False):
 
     fig = plt.figure(figsize=(7, 11), dpi=100)
     ax = fig.add_subplot(1, 1, 1)

### 2019-04-26 rhoqso_data.py

@@ -179,7 +179,7 @@ def get_lf(lf, sid, bins, use_smooth_maps=False, use_binvol2 = False):
     ms = (bins[1:]+bins[:-1])*0.5
 
     limit = np.max(ms)
-    m = m[m<-24.0]
+    m = m[m<limit]
     # print 'bins=', bins
     #print 'limit=', limit
 
@@ -221,8 +221,8 @@ def get_lf(lf, sid, bins, use_smooth_maps=False, use_binvol2 = False):
     uperr = np.log10(nlims[1]) - logphi 
     downerr = logphi - np.log10(nlims[0])
 
-    # for a in zip(mags, n):
-    #     print '{:.2f}  {:d}'.format(a[0], a[1])
+    for a in zip(mags, n):
+        print '{:.2f}  {:d}'.format(a[0], a[1])
 
     return mags, left, right, logphi, uperr, downerr
 
@@ -328,54 +328,13 @@ def rhoqso3(lfs, mag_threshold, bins, **kwargs):
                     vals.append(logphis[j][i])
             if nonzero_counter > 0:
                 total_phi[i] = np.mean(np.array(vals))
-            # print i, total_phi[i]
-                        
-            
-
-        #     N = len(logphis)
-        # if N > 2:
-        #     print 'We have a problem: N > 2!!!'
-            
-        # if N > 1:
-        #     total_phi = logphis[0]
-        #     for ns in range(1,N):
-        #         for i, p in enumerate(logphis[ns]):
-        #             if total_phi[i] == 0.0:
-        #                 total_phi[i] = total_phi[i] + p
-        #             elif p > 0.0:
-        #                 total_phi[i] = (total_phi[i] + p)/2 
-        #     logphi = total_phi
-        # else:
-        #     logphi = np.sum(logphis, axis=0)
 
         logphi = total_phi 
         
-        #row1 = logphis[0]
-        #row2 = logphis[1]
-
-        # logphi = np.sum(logphis, axis=0)
-
-        # #logphi = total_phi 
-
-        # logphi_test = np.mean(logphis, axis=0)
-
-        #for phivalue in zip(row1, row2, logphi):
-         #   print '{:.2e}  {:.2e}  {:.2e}'.format(*phivalue)
-        
-            #print logphi 
[…]

### 2019-04-26 tiling.py

@@ -7,13 +7,22 @@ You only need to set data, z_tolerance, and mag_tolerance.
 import numpy as np
 import sys
 
-filename = sys.argv[1]
+# filename = sys.argv[1]
 #data = np.loadtxt('Data_new/croom09sgp_selfunc.dat')
-data = np.loadtxt(filename)
-z_tolerance = 0.01
-mag_tolerance = 0.001 
 
-print 'Using z_tolerance = {:.4f} and mag_tolerance = {:.4f}'.format(z_tolerance, mag_tolerance)
+
+in_file = 'smooth_maps/' + sys.argv[1]
+out_file = 'smooth_maps/' + sys.argv[1][:-4] + '_with_tiles.dat'
+print 'Reading ' + in_file
+print 'Writing to ' + out_file
+
+data = np.loadtxt(in_file)
+fl = open(out_file, 'w')
+
+z_tolerance = 0.0001
+mag_tolerance = 0.00001 
+
+fl.write('# Using z_tolerance = {:.4f} and mag_tolerance = {:.4f}\n'.format(z_tolerance, mag_tolerance))
 
 def is_same_z(z1, z2):
 
@@ -127,10 +136,20 @@ for i, tile in enumerate(data):
     dzs.append(dz)
     dmags.append(dmag)
     
-    print '{:>5d}  {:.3f}  {:.2f}  {:.5f}  {:.4f}  {:.3f}'.format(i+1, z, mag, p, dz, dmag)
+    fl.write('{:>5d}  {:.3f}  {:.2f}  {:.5f}  {:.4f}  {:.3f}\n'.format(i+1, z, mag, p, dz, dmag))
 
 dzs = np.array(dzs)
 dmags = np.array(dmags)
     
-print '# dzs =', np.unique(dzs.round(decimals=4))
-print '# dmags =', np.unique(dmags.round(decimals=4))
+fl.write('# dzs = ' + str(np.unique(dzs.round(decimals=4))) + '\n')
+fl.write('# dmags = ' + str(np.unique(dmags.round(decimals=4))) + '\n') 
+
+fl.close()
+
+print '# dzs = ' + str(np.unique(dzs.round(decimals=4)))
+print '# dmags = ' + str(np.unique(dmags.round(decimals=4)))
+
+
+
+
+

### 2019-05-16 croom.py
Update for referee

@@ -150,7 +150,7 @@ def croom(i, ax, zrange, yticklabels=False, xticklabels=False, nofirstylabel=Tru
     phi_lerr = -phi_err_low[sel] # Values in table have minus sign
     phi_uerr = phi_err_up[sel]
     dm = 0.15*np.ones(m.size)
-    ax.scatter(m, phi, c='#ffffff', s=30, label='Croom et al.\ 2009',
+    ax.scatter(m, phi, c='#ffffff', s=30, label='Croom09 (2SLAQ + SDSS DR3)$^1$',
                edgecolor='r', zorder=2)
     ax.errorbar(m, phi, ecolor='r', capsize=0, 
                 yerr=np.vstack((phi_lerr, phi_uerr)), fmt='None', zorder=1)
@@ -188,18 +188,25 @@ def croom(i, ax, zrange, yticklabels=False, xticklabels=False, nofirstylabel=Tru
         # Convert from M1450 to Mg(z=2) by using Equation B8 of Ross
         # et al. 2013.
         mags = mags - 1.23
-        # ax.scatter(mags, logphi, c='b', edgecolor='None',
-        #            zorder=2, label='Our binning (SDSS)', s=35)
-        # ax.errorbar(mags, logphi, ecolor='b', capsize=0,
-        #             yerr=np.vstack((uperr, downerr)),
-        #             fmt='None',zorder=2)
-        # 
+        ax.scatter(mags, logphi, c='b', edgecolor='None',
+                   zorder=2, label='Our binning (SDSS DR7)', s=35)
+        ax.errorbar(mags, logphi, ecolor='b', capsize=0,
+                    yerr=np.vstack((uperr, downerr)),
+                    fmt='None',zorder=2)
+        
     print 'i=', i
 
-    # if i == 1:
-    #     mags = np.linspace(-16, -31)
-    #     p = [-6.426, -23.499, -3.382, -1.577]
-    #     plt.plot(mags-1.23, log10phi(p, mags), c='peru', lw=2, dashes=[7,2])
+    if i == 1:
+        mags = np.linspace(-16, -31)
+
+        p = [-5.944, -24.059, -3.028, -1.490]
+        plt.plot(mags, log10phi(p, mags), c='r', lw=2)
+
+        p = [-6.467, -23.570, -3.424, -1.610]
[…]

### 2019-05-16 rhoqso_data.py
Clean up

@@ -598,8 +598,98 @@ def test(c1, c2, c3, individuals, **kwargs):
 
     return
 
+def sift(vals, reject):
 
-def test2(c1, c2, c3, individuals, **kwargs):
+    good = [x for i, x in enumerate(vals) if i not in set(reject)]
+    bad = [x for i, x in enumerate(vals) if i in set(reject)]
+
+    return good, bad
+
+
+def plot_globals_using_npz(ax, npz_globals):
+
+    nzs = 500
+    z = np.linspace(0, 7, nzs)
+    data = np.load(npz_globals[0])
+    c = data['c']
+    up = data['up']
+    down = data['down']
+    m1f = ax.fill_between(z, down, y2=up,
+                          color='grey', zorder=6, alpha=0.7)
+    m1, = ax.plot(z, c, color='k', zorder=7)
+
+    data = np.load(npz_globals[1])
+    c = data['c']
+    up = data['up']
+    down = data['down']
+    m2f = ax.fill_between(z, down, y2=up,
+                          color='forestgreen', zorder=6, alpha=0.7)
+    m2, = ax.plot(z, c, color='forestgreen', zorder=7)
+
+    data = np.load(npz_globals[2])
+    c = data['c']
+    up = data['up']
+    down = data['down']
+    m3f = ax.fill_between(z, down, y2=up,
+                          color='peru', zorder=6, alpha=0.7)
+    m3, = ax.plot(z, c, color='brown', zorder=7)
+
+    return m1, m2, m3, m1f, m2f, m3f
+
+
+def error_point(ax, x, y, lx, ux, ly, uy, c='r', good=True):
+
+    if good: 
+
+        ax.errorbar(x, y, ecolor=c, capsize=0,
+                    fmt='None', elinewidth=1,
+                    yerr=np.vstack((ly, uy)), 
+                    xerr=np.vstack((lx, ux)),
+                    zorder=10, mew=1, ms=5)
+        ax.scatter(x, y, c=c, edgecolor=c, s=42, zorder=10,
+                   linewidths=1)
+
+    else:
+
+        ax.errorbar(x, y, ecolor=c, capsize=0,
+                    fmt='None', elinewidth=1,
+                    yerr=np.vstack((ly, uy)), 
+                    xerr=np.vstack((lx, ux)),
+                    zorder=10, mew=1, ms=5)
[…]

### 2019-05-16 summary_grand.py
Update style

@@ -14,15 +14,15 @@ LFs.
 
 """
 
-clr = { 'croom09': 'gold',
+clr = { 'croom09': '#1f77b4', 
         'masters12': 'dodgerblue',
         'glikman11': 'dodgerblue',
-        'kulkarni19': '#1f77b4',
+        'kulkarni19': 'gold',
         'masters12': '#ffffff', # was '#2ca02c'
         'jiang16': '#ffffff', # was '#d62728'
         'onoue17': '#ffffff', # was '#7f7f7f'
         'schulze09': '#ffffff', # was '#bcbd22'
-        'mcgreer13': 'dodgerblue',
+        'mcgreer13': '#ffffff', # was 'dodgerblue'
         'giallongo15': '#ffffff' # was '#8c564b' 
 }
 
@@ -420,7 +420,7 @@ def yang16(ax, param):
     zuperr = zup-z
 
     if param == 0:
-        p = np.array([-9.07])
+        p = np.array([-8.56]) # Scale given z = 6 phi* to z = 5 and multiply by 1.1 for cosmology.
         perr = np.array([0.4])
 
     if param == 1:
@@ -466,10 +466,10 @@ def mcgreer13(ax, param):
 
     if param == 2:
         p = np.array([-4.0])
-        ax.errorbar(z, p, ecolor=clr['mcgreer13'], capsize=2,
+        ax.errorbar(z, p, ecolor='k', capsize=2,
                     xerr=np.vstack((zdownerr, zuperr)),
                     fmt='None', zorder=2, linewidths=0.5, elinewidths=0.5, capthick=0.5)
-        ax.scatter(z, p, color=clr['mcgreer13'], edgecolor='k', zorder=2, s=20, marker='x', label=r'McGreer et al.\ 2013')
+        ax.scatter(z, p, color=clr['mcgreer13'], edgecolor='k', zorder=2, s=20, marker='8', label=r'McGreer et al.\ 2013', linewidths=0.5)
         return
         
     if param == 3:
@@ -477,11 +477,11 @@ def mcgreer13(ax, param):
         puperr = np.array([0.15])
         pdownerr = np.array([0.14])
         
-    ax.errorbar(z, p, ecolor=clr['mcgreer13'], capsize=2,
+    ax.errorbar(z, p, ecolor='k', capsize=2,
                 xerr=np.vstack((zdownerr, zuperr)),
                 yerr=np.vstack((pdownerr, puperr)),
[…]

### 2019-05-16 Paper/paper.tex

@@
   we adopt a double power law to account for a possible break at
-  $z\sim 3$ that is currently not covered with credible data.  Thus we
-  write
+  $z\sim 3$ that is currently not covered with credible data \new{with
+    well-characterised selection function}.  Thus we write
   \begin{equation}
@@
 power law luminosity function from our analysis of
-Section~\ref{sec:bins} to values reported in the literature.  In
-general, our break luminosity is brighter and the faint-end slope is
-steeper than other determinations.  Note however that several results
-from the literature shown in Figure~\ref{fig:params_grand} make
-restrictive assumptions while fitting double power law models to data.
-For example, \citet{2013ApJ...768..105M} fix the bright-end slope
-$\alpha$ to $-4$ at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix
-the faint-end slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
+Section~\ref{sec:bins} to values reported in the literature.
+\new{There is significant disagreement between various inferences.
+  The break magnitude and the luminosity function amplitudes are
+  particularly severely discordant towards the higher-redshift end of
+  Figure~\ref{fig:params_grand}, although the disagreement is
+  appreciable at other redshifts too.  The slopes are in conflict at
+  all redshifts.} In general, our break luminosity is brighter and the
+faint-end slope is steeper than other determinations.
+
+Several results from the literature shown in
+Figure~\ref{fig:params_grand} make restrictive assumptions while
+fitting double power law models to data.  For example,
+\citet{2013ApJ...768..105M} fix the bright-end slope $\alpha$ to $-4$
+at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix the faint-end
+slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
 \citet{2017ApJ...847L..15O} fix the bright-end slope $\alpha$ to
@@
 faint-end slope and the break luminosity in their highest-redshift bin
-($z=5.0$--$6.5$).  The choice of data sets is also often different.
+($z=5.0$--$6.5$).  \new{This biases the inference of other parameters
+  and may also underestimate their uncertainties.}
+
+The choice of data sets is also often different.
 For instance, \citet{2015AA...578A..83G} do not include the SDSS
@@
 analysis.  (We discuss the results of \citet{2015AA...578A..83G} in
-greater detail in Appendix~\ref{sec:conv}.)  Of the remaining
-determinations, our parameter values are closest to those reported by
-\citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.
+greater detail in Appendix~\ref{sec:conv}.)
+
+\new{The uncertainties reported by \citet{2012ApJ...755..169M} are
+  unphysical.  At $z\sim 4$, the uncertainty reported by these authors
+  on $\phi_*$ spans negative values.  It is unclear if the double
+  power law model was fit to data after binning in magnitude and how
+  the uncertainties were derived.  At lower redshifts, our fits to the
+  $z<2$ luminosity function have steeper faint ends than those
+  reported by \citet{2009MNRAS.399.1755C}.  Upon closer inspection, we
+  found that our binned luminosity functions differ systematically
+  from those of \citet{2009MNRAS.399.1755C} in one or two faintest
+  bins at all redshifts.  Unfortunately, \citet{2009MNRAS.399.1755C}
+  do not provide enough detail for us to deduce the causes behind this
+  difference, but one possibility is that these authors made specific
+  interpolation choices while integrating over the completeness map.
+  At intermediate redshifts, some of the parameter values reported
+  \citet{2013ApJ...773...14R} also have unphysical uncertainties.
+  Uncertainties for these values do not enclose the measurement.
+  While our disagreement with \citet{2013ApJ...773...14R} in
+  Figure~\ref{fig:params_grand} is relatively minor, we note that this
+  is in a redshift range where the data suffer from severe systematic
+  errors.  The reason our parameter values disagree with those given
+  by \citet{2011ApJ...728L..26G} is also unclear.  The selection
+  function provided by these authors had completeness values that
+  exceeded 100\%, perhaps due to extrapolation errors.  When this
+  happened we assumed 100\% completeness.  \citet{2018PASJ...70S..34A}
+  report very flat faint-end slope that is inconsistent with our
+  inference at all redshifts.  As discussed in
+  Section~\ref{sec:reion}, this could be because of missing AGN faint
+  population $M_{1450} > -23.5$ due to point source selection and
+  partly also because of photometric redshift errors.  Thus, of the
+  five determinations in the literature with unconstrainted double
+  power law fits,} our parameter values are closest to those reported
+by \citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.
+
+\new{In sum, Figure~\ref{fig:params_grand} suggests that it is
+  incorrect to fix QLF parameters while fitting QLF models and one
+  should only fit models if data actually span the magnitude range.
+  In order to emphasize this, we have shown inferences without
+  errorbars as open symbols.  Note that the formal statistical
+  uncertainty of our inferences in often smaller than the symbol size
+  in Figure~\ref{fig:params_grand}.}
 
@@
     % summary_grand.py
-    \includegraphics[width=\textwidth]{evolution_grand.pdf}
+    \includegraphics[width=\textwidth]{/Users/girish/Desktop/evolution_grand.pdf}
   \end{center}
   \caption{A comparison of our inferred double power law parameter
-    values with those reported in the literature.  Black points show
-    our determinations from Figure~\ref{fig:evoln}.  Blue points show
-    other values, from \citet[triangles]{2012ApJ...755..169M},
+    values with those reported in the literature.  Yellow points show
+    our determinations from Figure~\ref{fig:evoln}.  \new{(Our
+      statistical errors are often smaller than the symbol size.)}
+    Other data points show values from
+    \citet[triangles]{2012ApJ...755..169M},
     \citet[squares]{2016ApJ...833..222J},
@@
     \citet[circles]{2013ApJ...773...14R},
-    \new{\citet[hexagons]{2009MNRAS.399.1755C}} and \citet[rightward
-      triangles]{2009A&A...507..781S}.  Where necessary, values from
-    the literature have been converted to our cosmology.
+    \citet[hexagons]{2009MNRAS.399.1755C} and \citet[rightward
+      triangles]{2009A&A...507..781S}.  \new{Measurements for which no
+      error bars are available are shown using open symbols.}  Where
+    necessary, values from the literature have been converted to our
+    cosmology.
     \label{fig:params_grand}}
